### 2014-11-22 doc/HH4b_Documentation.tex
Add analysis documentation

%  sample eprint article in LaTeX           --- M. Peskin, 9/7/00
\documentclass[12pt]{article}
\usepackage{graphicx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% basic data for the eprint:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textwidth=6.0in  \textheight=8.25in

%%  Adjust these for your printer:
\leftmargin=-0.3in   \topmargin=-0.20in

%% preprint number data:
\newcommand\pubnumber{DRAFT-001}
\newcommand\pubdate{\today}

%%  address and funding acknowledgement data:
\def\oxford{}
\def\support{\footnote{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   document style macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\Title#1{\begin{center} {\Large #1 } \end{center}}
\def\Author#1{\begin{center}{ \sc #1} \end{center}}
\def\Address#1{\begin{center}{ \it #1} \end{center}}
\def\andauth{\begin{center}{and} \end{center}}
\def\submit#1{\begin{center}Submitted to {\sl #1} \end{center}}
\newcommand\pubblock{\rightline{\begin{tabular}{l} \pubnumber\\
         \pubdate  \end{tabular}}}
\newenvironment{Abstract}{\begin{quotation}  }{\end{quotation}}
\def\Acknowledgements{\bigskip  \bigskip \begin{center} \begin{large}
             \bf ACKNOWLEDGEMENTS \end{large}\end{center}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  personal abbreviations and macros
%    the following package contains macros which can be used in this document:
%\input econfmacros.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{titlepage}
\hspace{-1.4cm}\pubblock

\vfill
\Title{Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$}
\vfill
\Author{}
\Address{}
\vfill
\begin{Abstract}
This is a feasibility study for the final state $hh\rightarrow (b\bar{b})(b\bar{b})$ using reconstruction techniques for both resolved
and boosted topologies as well as multivariate methods.
\end{Abstract}
\vfill
\end{titlepage}
\def\thefootnote{\fnsymbol{footnote}}
\setcounter{footnote}{0}
%

\section{Introduction}

\section{Samples}

\section{Object and Event Selection}

\subsection{Resolved Topology}

The resolved selection requires the presence of at least four b-tagged anti-$k_T$ $R=0.4$ jets with $p_T >$25~GeV and $|\eta|>2.5$.
\textit{Pre-cut} histograms are written out for various kinematic distributions for all events with at least four b-tagged jets but before applying
further kinematic cuts. \textit{Post-cut} histograms contain only events where the four jets also pass the above kinematic cuts.

The di-Higgs system is reconstructed by considering all possibilities of forming two pairs of jets with invariant masses $m_{j1j2}$ and 
$m_{j3j4}$, respectively, and chosing the configuration that minimises their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
are considered here.

\subsection{Boosted Topology}\label{sec:Boosted_FR}

In the boosted topology, the decay products of each Higgs boson are merged into a single large-$R$ jet with a two-prong substructure. 
These Higgs jets are reconstructed as anti-$k_T$ $R=1.0$ jets for which two substructure variables, the first $k_T$ splitting scale $d_{12}$
and the 2-subjettiness ratio $\tau_{21}$, are calculated.
\textit{Pre-cut} histograms are written out after requiring the presence of at least two large-$R$ in the event but without applying any further
kinematic cuts. \textit{Post-cut} histograms are filled after the following additional cuts: 
Both jets are required to have $p_T >$100~GeV and $|\eta|>2.5$. Moreover, each jet is required to have at least two b-tagged anti-$k_T$ $R=0.3$ 
jets matched to it via \textit{ghost association}: 
To this end, the constituents of a given large-$R$ jet is reclustered using the jet algorithm 
and radius parameter of the original jet and so-called \textit{ghost jets}, each corresponding to a small-$R$ jet in the event, 
are added to the input for the cluster sequence. The 4-vector of a ghost jet is obtained from a given small-$R$ jet 
by setting its transverse momentum and mass to negligibly small values but retaining its direction in $\eta$ and $\phi$. A small-$R$ jet is 
considered matched to the large-$R$ jet if its ghost is found among the constituents of the reclustered jet. Ghost association allows to unambiguously
match small-$R$ to large-$R$ jets, even in dense environments where a simple matching based on the distance $\Delta R$ between jets 
may lead to multiple matchings.

\subsection{Boosted Topology with Variable-$R$ Jets}

The same selection as in Subsection~\ref{sec:Boosted_FR} is applied but this time using Variable-$R$ jets with the following parameters:
$\rho=500$~GeV, $R_{max}=$1.0, $R_{min}=$0.2.

\section{Multivariate Tools}

\section{Results}

\section{Conclusion}

% \Acknowledgements

\end{document}

### 2014-11-22 analysis/src/HH4b.cc

@@ -18,6 +18,7 @@
 #include "ucl_vr.h"
 #include "durham.h"
 #include "oxford_res_vr.h"
+#include "oxford_res_fr.h"
 #include "oxford_boost_vr.h"
 #include "oxford_boost_fr.h"
 #include "variableR.h"
@@ -50,13 +51,15 @@ int main()
   HH4bAnalyses.push_back(new DurhamAnalysis("total"));
   HH4bAnalyses.push_back(new UCLVRAnalysis("total"));
   HH4bAnalyses.push_back(new OxfordResVRAnalysis("total"));
+  HH4bAnalyses.push_back(new OxfordResFRAnalysis("total"));
   HH4bAnalyses.push_back(new OxfordBoostVRAnalysis("total"));
- HH4bAnalyses.push_back(new OxfordBoostFRAnalysis("total"));
+  HH4bAnalyses.push_back(new OxfordBoostFRAnalysis("total"));
 
   signalAnalyses.push_back(new UCLAnalysis("signal"));
   signalAnalyses.push_back(new DurhamAnalysis("signal"));
   signalAnalyses.push_back(new UCLVRAnalysis("signal"));
   signalAnalyses.push_back(new OxfordResVRAnalysis("signal"));
+  signalAnalyses.push_back(new OxfordResFRAnalysis("signal"));
   signalAnalyses.push_back(new OxfordBoostVRAnalysis("signal"));
   signalAnalyses.push_back(new OxfordBoostFRAnalysis("signal"));
 
@@ -64,6 +67,7 @@ int main()
   backgroundAnalyses.push_back(new DurhamAnalysis("background"));
   backgroundAnalyses.push_back(new UCLVRAnalysis("background"));
   backgroundAnalyses.push_back(new OxfordResVRAnalysis("background"));
+  backgroundAnalyses.push_back(new OxfordResFRAnalysis("background"));
   backgroundAnalyses.push_back(new OxfordBoostVRAnalysis("background"));
   backgroundAnalyses.push_back(new OxfordBoostFRAnalysis("background"));
 
@@ -195,6 +199,7 @@ int main()
     sampleAnalyses.push_back(new DurhamAnalysis(samplename));
     sampleAnalyses.push_back(new UCLVRAnalysis(samplename));
     sampleAnalyses.push_back(new OxfordResVRAnalysis(samplename));
+    sampleAnalyses.push_back(new OxfordResFRAnalysis(samplename));
[…]

### 2015-01-11 doc/HH4b_Documentation.tex
Added sample runcards to documentation

@@
 \section{Samples}
+\subsection{Background}
+All background samples are generated with the {\tt SHERPA} event generator, version 2.1.1. For the explicit runcards used in the generation, see Appendix~\ref{app:runcards}.
+
+The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples.
+At the generator level the following basic cuts are applied.
+Each final state particle must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
+Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ (in hindsight, $H_T/4$ would probably have made more sense).
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\clearpage
+\appendix
+\section{Event sample runcards}
+\label{app:runcards}
+\subsection {Background: QCD 4b}
+\begin{verbatim}
+(run){
+  EVENTS 3M;
+  EVENT_GENERATION_MODE U;
+  ME_SIGNAL_GENERATOR Comix;
+
+  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_4b];
+
+  BEAM_1 2212; BEAM_ENERGY_1 7000;
+  BEAM_2 2212; BEAM_ENERGY_2 7000;
+
+  FRAGMENTATION=Off # disable hadronisation
+  MI_HANDLER=None # disable multiple parton interactions
+
+  SCF:=1; ### default scale factor
+  SCALES VAR{SCF*H_T2/2};
+
+  PDF_LIBRARY LHAPDFSherpa;
+  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
+  PDF_SET_VERSION 0;
+
+  MASSIVE[5] 1;
+  MASS[5] 4.75;
+
+}(run);
+(processes){
+  Process 93 93 -> 5 -5 5 -5;
+  Order_EW 0;
+  End process;
+
+}(processes);
+(selector){
+  PT 5 20 7000
+  PT -5 20 7000
+  PseudoRapidity 5 -3.0 3.0
+  PseudoRapidity -5 -3.0 3.0
+}(selector);
+\end{verbatim}
+
+\subsection {Background: QCD 2b2j}
+\begin{verbatim}
+(run){
+  EVENTS 3M;
+  EVENT_GENERATION_MODE U;
+  ME_SIGNAL_GENERATOR Comix;
+
+  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_2b2j];
+
+  BEAM_1 2212; BEAM_ENERGY_1 7000;
+  BEAM_2 2212; BEAM_ENERGY_2 7000;
+
+  FRAGMENTATION=Off # disable hadronisation
+  MI_HANDLER=None # disable multiple parton interactions
+
+  SCF:=1; ### default scale factor
+  SCALES VAR{SCF*H_T2/2};
+
+  PDF_LIBRARY LHAPDFSherpa;
+  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
+  PDF_SET_VERSION 0;
+
+  MASSIVE[5] 1;
+  MASS[5] 4.75;
+
+}(run);
+(processes){
+  Process 93 93 -> 93 93 5 -5;
+  Order_EW 0;
+  End process;
+
+}(processes);
+(selector){
+  PT 5 20 7000
+  PT -5 20 7000
+  PseudoRapidity 5 -3 3
+  PseudoRapidity 5 -3 3
+
+  PT 93 20 7000
+  PseudoRapidity 93 -3 3
+}(selector);
+\end{verbatim}
+
+\subsection {Background: QCD 4j}
+\begin{verbatim}
+(run){
+  EVENTS 3M;
+  EVENT_GENERATION_MODE U;
+  ME_SIGNAL_GENERATOR Comix;
+
+  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_4j];
+
+  BEAM_1 2212; BEAM_ENERGY_1 7000;
+  BEAM_2 2212; BEAM_ENERGY_2 7000;
+
+  FRAGMENTATION=Off # disable hadronisation
+  MI_HANDLER=None # disable multiple parton interactions
+
+  SCF:=1; ### default scale factor
+  SCALES VAR{SCF*H_T2/2};
+
+  PDF_LIBRARY LHAPDFSherpa;
+  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
+  PDF_SET_VERSION 0;
+
+  MASSIVE[5] 1;
+  MASS[5] 4.75;
+
+}(run);
+(processes){
+  Process 93 93 -> 93 93 93 93;
+  Order_EW 0;
+  End process;
+
+}(processes);
+(selector){
+  PT 93 20 7000
+  PseudoRapidity 93 -3 3
+}(selector);
+\end{verbatim}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2015-01-20 doc/HH4b_Documentation.tex
Updated documentation

@@
 \usepackage{graphicx}
+
+\usepackage{geometry}
+\geometry{margin=1.5in}
+
+%\usepackage{chngcntr}
+%\counterwithin{table}{section}
 
@@
 
-\textwidth=6.0in  \textheight=8.25in
+% \textwidth=6.0in  \textheight=8.25in
 
 %%  Adjust these for your printer:
-\leftmargin=-0.3in   \topmargin=-0.20in
+% \leftmargin=-0.3in   \topmargin=-0.20in
 
@@
 \section{Samples}
+\label{sec:samples}
 \subsection{Background}
@@
 Each final state particle must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
-Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ (in hindsight, $H_T/4$ would probably have made more sense).
+Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$.
+Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.
 
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Process & Filename & Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
+\hline
+\hline
+$pp \to HH$ & HH\_sm\_eft\_100K.lhe & MG5\_aMC@NLO & 100K & $1.729\times10^{-2}$ pb \\
+\hline
+$pp \to b\bar{b}b\bar{b}$ & SHERPA\_QCD\_4b.hepmc & SHERPA 2.1.1 & 3M &$1.016 \times10^3$ pb \\
+$pp \to b\bar{b}jj$ & SHERPA\_QCD\_2b2j.hepmc & SHERPA 2.1.1 & 3M & $4.076 \times 10^5$ pb\\
+$pp \to jjjj$ & Running & SHERPA 2.1.1 & 3M  & ??? \\
+$pp \to t\bar{t}$ &  & &  & \\
+\hline
+\end{tabular}
+\caption{Summary of generated samples to date} \label{tab:samples}
+\end{center}
+\end{table}%
+
+Although suffering from a large theory uncertainty, we can compare the result of our background samples against those presented in the MG5\_aMC@NLO paper~\cite{Alwall:2014hca}.
+Here for comparison we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV.
+All jets must be within an acceptance of $|\eta| \le 2.5 $.
+In the case of the samples with $b$ quarks in the final state, these requirements are extended to the appropriate number of $b$-jets.
+For example, in the 2$b$2$j$ sample there must be at least two $b$-jets that pass the cuts outlined above.
+
+In Table~\ref{tab:xsecs} this comparison is summarised for the $2b2j$ and $4b$ samples. Considering the large theory errors, agreement is reasonable in both instances.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|}
+\hline
+Process & $\sigma$ aMC@NLO & $\sigma$ Oxford (SHERPA) \\
+\hline\hline
+$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $3.473\times10^{-1}$ pb \\ 
+$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$5.193 \times 10^2$ pb \\ 
+\hline
+\end{tabular}
+\caption{Comparison of LO Oxford SHERPA cross-sections with those of the aMC@NLO paper. The aMC@NLO cross-sections come with a quoted $~50\%$ theory uncertainty.} \label{tab:xsecs}
+\end{center}
+\end{table}%
 \section{Object and Event Selection}
@@
 The di-Higgs system is reconstructed by considering all possibilities of forming two pairs of jets with invariant masses $m_{j1j2}$ and 
-$m_{j3j4}$, respectively, and chosing the configuration that minimises their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
+$m_{j3j4}$, respectively, and choosing the configuration that minimises their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
 are considered here.
+
+\subsubsection{Resolved $b$-jet tagging efficiencies}
+In order to perform an initial validation of the b-tagging procedure used in our resolved analysis we consider first a simple flat b-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$.
+In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_l\epsilon^2_b$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.
+
+In practice we have found with these simple efficiencies, that the actual selection efficiencies differ considerably from the naive factors of $\epsilon_b^{n_b}\epsilon_l^{n_l}$.
+In Table~\ref{tab:btageff1} the results of this simple b-tagging test are demonstrated.
+Shown in the table are the total cross-sections before and after the application of the described b-tagging procedure, the resulting percentage of the cross-section passing the b-tag, and the naive selection percentage that would result from applying powers of $\epsilon_{b/l}$ to the total cross-section.
+The pass rate for samples with four $b$ quarks in the final state is therefore considerably lower in practice than one would naively expect, and the pass rate for the $2b2j$ sample considerably higher.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Process & $\sigma_{\mathrm{tot}}$ & After b-tag & \% selected & \% Naive selection \\
+\hline \hline
+$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.565\times 10^{-3}$ pb & \textbf{9.050\%} & 40.96\% \\
+\hline
+$b\bar{b}b\bar{b}$ & $1.016 \times10^3$ pb & $93.46$ pb & \textbf{9.199\%} & 40.96\%\\
+$b\bar{b}jj$ &  $4.076 \times 10^5$ pb & 103.904 pb & \textbf{0.026\%} & 0.0064\% \\
+\hline
+\end{tabular}
+\end{center}
+\caption{$b$-tagging analysis performed upon the samples described in Section~\ref{sec:samples}.
+Cross-sections are given for the samples before and after the application of the b-tagging procedure whereby the four hardest jets in the event are used, and the flat selection efficiency and mis-tag rates applied.
+The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison.} \label{tab:btageff1}
+\end{table}%
+
+These differences are due to the choices made in the selection procedure.
+In practice the four hardest jets in the event often do not correspond directly to the four parton level final state particles.
+In Table~\ref{tab:nbjets} the number of true $b$-jets (that is, prior to the application of selection efficiencies and fake rates) present in the hardest four jets per event is shown.
+Indeed, for the samples with four $b$-quarks in the parton level final state, the most common scenario has only three $b$-jets in the hardest four jets, significantly affecting the selection efficiency.
+
+ A more accurate estimation for the passing cross-section may be obtained by multiplying the various fractions of $b$-jets by the corresponding efficiencies, for example the 3 $b$-jet rate by $\epsilon_b^{3}\epsilon_l^{1}$.
+Summing the various scenarios we then have a better estimate for the percentage of cross-section passing the selection, shown in the final column of Table~\ref{tab:nbjets}.
+This agrees well with the observed rates shown in Table~\ref{tab:btageff1}.
+
+\begin{table}[htdp]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|c||c|}
+\hline
+Process & 0 $b$-jets & 1 $b$-jet & 2 $b$-jets & 3 $b$-jets & 4 $b$-jets & \% selected \\
+\hline\hline
+$H\bar{H}$ & 0.049\% &  2.448\% &  23.49\% & 52.58\% &  21.43\% & \textbf{9.050\%}\\
+\hline
+$b\bar{b}b\bar{b}$ & 0.429\% & 5.477\%   & 25.53\% & 46.67\%  &  21.89\% & \textbf{9.208\%} \\
+$b\bar{b}jj$ & 6.213\%  &40.56\%  &51.93\%  &  1.227\% & 0.072\% & \textbf{0.039\%}\\
+\hline
+\end{tabular}
+\end{center}
+\caption{Breakdown of the number of true $b$-jets in the hardest four clustered jets for various samples.
+The final column shows the predicted pass rate for the $b$-tagging given the distribution of events in the preceding columns.}\label{tab:nbjets}
+\end{table}%
+
+\subsubsection{$b$-jet tagging efficiencies with UCL-style selection}
+In the UCL analysis their jet selection does not proceed as described in the previous section, presumably as requiring the four hardest jets in the event to be b-Tagged cuts too aggressively upon the signal process.
+Rather, the selection proceeds by taking all anti-$k_T$ $R=0.5$ jets with $p_T > 40$ GeV and running the b-Tagging algorithm on them.
+The four hardest successfully b-tagged jets are then selected for further analysis.
+With such a method implemented for our samples and with our previous selection efficiencies and fake rates, Table \ref{tab:UCLbtag} summarises the results.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & \% selected  \\
+\hline \hline
+$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & 7.467\% \\
+\hline
+$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & 5.472\% \\
+$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & 0.0224\% \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Summary of the $b$-tagging procedure of the UCL analysis.
+Presented as in Table~\ref{tab:btageff1}.
+In this case the total cross-sections are presented after a cut requiring four anti-$k_T$ R=0.5 jets with $p_T>40$ GeV in the final state.
+The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.}\label{tab:UCLbtag}
+\end{table}%
+
+Once again, it is clear that more of the $bbjj$ sample is making it past the $b$-tagging selection than originally expected.
+It seems unlikely that this background can be neglected in the resolved analysis based upon a simple factor of $\epsilon_b^{2}\epsilon_l^{2}$ as used by the UCL group.
 
@@
 % \Acknowledgements
+
+\begin{thebibliography}{1}
+
+%\cite{Alwall:2014hca}
+\bibitem{Alwall:2014hca}
+  J.~Alwall, R.~Frederix, S.~Frixione, V.~Hirschi, F.~Maltoni, O.~Mattelaer, H.-S.~Shao and T.~Stelzer {\it et al.},
+  %``The automated computation of tree-level and next-to-leading order differential cross sections, and their matching to parton shower simulations,''
+  JHEP {\bf 1407} (2014) 079
+  [arXiv:1405.0301 [hep-ph]].
+  %%CITATION = ARXIV:1405.0301;%%
+  %168 citations counted in INSPIRE as of 19 Jan 2015
+
+%\cite{Wardrope:2014kya}
+\bibitem{Wardrope:2014kya}
+  D.~Wardrope, E.~Jansen, N.~Konstantinidis, B.~Cooper, R.~Falla and N.~Norjoharuddeen,
+  ``Non-resonant Higgs pair production in the $b\overline{b}b\overline{b}$ final state at the LHC,''
+  arXiv:1410.2794 [hep-ph].
+  %%CITATION = ARXIV:1410.2794;%%
+
+  \end{thebibliography}
 

### 2015-01-20 doc/HH4b_Documentation.tex
small updates

@@
 \subsubsection{Resolved $b$-jet tagging efficiencies}
-In order to perform an initial validation of the b-tagging procedure used in our resolved analysis we consider first a simple flat b-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$.
+In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$.
 In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_l\epsilon^2_b$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.
@@
 In practice we have found with these simple efficiencies, that the actual selection efficiencies differ considerably from the naive factors of $\epsilon_b^{n_b}\epsilon_l^{n_l}$.
-In Table~\ref{tab:btageff1} the results of this simple b-tagging test are demonstrated.
-Shown in the table are the total cross-sections before and after the application of the described b-tagging procedure, the resulting percentage of the cross-section passing the b-tag, and the naive selection percentage that would result from applying powers of $\epsilon_{b/l}$ to the total cross-section.
+In Table~\ref{tab:btageff1} the results of this simple $b$-tagging test are demonstrated.
+Shown in the table are the total cross-sections before and after the application of the described $b$-tagging procedure, the resulting percentage of the cross-section passing the b-tag, and the naive selection percentage that would result from applying powers of $\epsilon_{b/l}$ to the total cross-section.
 The pass rate for samples with four $b$ quarks in the final state is therefore considerably lower in practice than one would naively expect, and the pass rate for the $2b2j$ sample considerably higher.
@@
 \subsubsection{$b$-jet tagging efficiencies with UCL-style selection}
-In the UCL analysis their jet selection does not proceed as described in the previous section, presumably as requiring the four hardest jets in the event to be b-Tagged cuts too aggressively upon the signal process.
-Rather, the selection proceeds by taking all anti-$k_T$ $R=0.5$ jets with $p_T > 40$ GeV and running the b-Tagging algorithm on them.
-The four hardest successfully b-tagged jets are then selected for further analysis.
+In the UCL analysis their jet selection does not proceed as described in the previous section, presumably as requiring the four hardest jets in the event to be $b$-tagged cut too aggressively into the signal process.
+Rather, the selection proceeds by taking all anti-$k_T$ $R=0.5$ jets with $p_T > 40$ GeV and running the $b$-tagging algorithm on them.
+The four hardest successfully $b$-tagged jets are then selected for further analysis.
 With such a method implemented for our samples and with our previous selection efficiencies and fake rates, Table \ref{tab:UCLbtag} summarises the results.

### 2015-01-22 doc/HH4b_Documentation.tex

@@
 At the generator level the following basic cuts are applied.
-Each final state particle must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
+Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
 Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$.
@@
 In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$.
-In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_l\epsilon^2_b$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.
+In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_b\epsilon^2_l$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.
 

### 2015-01-22 doc/HH4b_Documentation.tex
added s/b to b-tagging exercise

@@
 \hline
+\textbf{S/B} & $4.23 \times 10^{-8}$ & $7.93 \times 10^{-6}$& \multicolumn{2}{c}{}\\
+\cline{1-3}
+\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $4.68 \times 10^{-2}$ & $1.93 \times 10^{-1}$& \multicolumn{2}{c}{}\\
+\cline{1-3}
 \end{tabular}
@@
 Cross-sections are given for the samples before and after the application of the b-tagging procedure whereby the four hardest jets in the event are used, and the flat selection efficiency and mis-tag rates applied.
-The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison.} \label{tab:btageff1}
+The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison.
+Finally, the signal-to-background ratio and significance are given both before and after the b-tagging, for $\mathcal{L}=$ 3 ab$^{-1}$.} \label{tab:btageff1}
 \end{table}%
@@
 \hline
+\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& \multicolumn{1}{c}{}\\
+\cline{1-3}
+\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& \multicolumn{1}{c}{}\\
+\cline{1-3}
 \end{tabular}

### 2015-01-30 doc/HH4b_Documentation.tex
Updated docs

@@
 Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
+All final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
 Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$.
@@
 \hline
-Process & Filename & Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
+Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
 \hline
 \hline
-$pp \to HH$ & HH\_sm\_eft\_100K.lhe & MG5\_aMC@NLO & 100K & $1.729\times10^{-2}$ pb \\
+$pp \to HH$ &  MG5\_aMC@NLO & 100K & $1.729\times10^{-2}$ pb \\
 \hline
-$pp \to b\bar{b}b\bar{b}$ & SHERPA\_QCD\_4b.hepmc & SHERPA 2.1.1 & 3M &$1.016 \times10^3$ pb \\
-$pp \to b\bar{b}jj$ & SHERPA\_QCD\_2b2j.hepmc & SHERPA 2.1.1 & 3M & $4.076 \times 10^5$ pb\\
-$pp \to jjjj$ & Running & SHERPA 2.1.1 & 3M  & ??? \\
-$pp \to t\bar{t}$ &  & &  & \\
+$pp \to b\bar{b}b\bar{b}$ &  SHERPA 2.1.1 & 3M &$9.298 \times10^2$ pb \\
+$pp \to b\bar{b}jj$ &  SHERPA 2.1.1 & 3M & $2.208 \times 10^5$ pb\\
+$pp \to jjjj$ &  SHERPA 2.1.1 & 3M  & $9.709\times 10^6$ pb \\
+$pp \to t\bar{t}$ (had) &  SHERPA 2.1.1 & 100K & $2.511\times 10^3$ pb \\
 \hline
@@
 \hline\hline
-$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $3.473\times10^{-1}$ pb \\ 
-$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$5.193 \times 10^2$ pb \\ 
+$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $3.492\times10^{-1}$ pb \\ 
+$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$4.209 \times 10^2$ pb \\ 
+$jjjj$ & -  & $4.450\times 10^4$ pb \\
 \hline
@@
 
-\subsubsection{Resolved $b$-jet tagging efficiencies}
+\subsubsection{Resolved $b$-jet tagging efficiencies} \label{sec:btagtest}
 In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$.
@@
 \hline \hline
-$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.565\times 10^{-3}$ pb & \textbf{9.050\%} & 40.96\% \\
+$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.460\times 10^{-3}$ pb & \textbf{8.444\%} & 40.96\% \\
 \hline
-$b\bar{b}b\bar{b}$ & $1.016 \times10^3$ pb & $93.46$ pb & \textbf{9.199\%} & 40.96\%\\
-$b\bar{b}jj$ &  $4.076 \times 10^5$ pb & 103.904 pb & \textbf{0.026\%} & 0.0064\% \\
+$b\bar{b}b\bar{b}$ & $9.298 \times10^2$ pb & $78.32$ pb & \textbf{8.423\%} & 40.96\%\\
+$b\bar{b}jj$ &  $2.208 \times 10^5$ pb & $84.80$ pb & \textbf{0.038\%} & 0.0064\% \\
+$jjjj$ & $9.709\times 10^6$ pb & $20.85$ pb & \textbf{2.147 $\times$ 10$^{-4}$\%} & $1.0\times 10^{-6}$\%\\
 \hline
-\textbf{S/B} & $4.23 \times 10^{-8}$ & $7.93 \times 10^{-6}$& \multicolumn{2}{c}{}\\
+\textbf{S/B} & $1.74 \times 10^{-9}$ & $7.94 \times 10^{-6}$& \multicolumn{2}{c}{}\\
 \cline{1-3}
-\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $4.68 \times 10^{-2}$ & $1.93 \times 10^{-1}$& \multicolumn{2}{c}{}\\
+\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $9.50 \times 10^{-3}$ & $1.86 \times 10^{-1}$& \multicolumn{2}{c}{}\\
 \cline{1-3}
@@
 \hline\hline
-$H\bar{H}$ & 0.049\% &  2.448\% &  23.49\% & 52.58\% &  21.43\% & \textbf{9.050\%}\\
+$H\bar{H}$ & 0.083\% & 2.599\% &  24.712\% &   52.651\% &  19.955\% & \textbf{8.445\%}\\
 \hline
-$b\bar{b}b\bar{b}$ & 0.429\% & 5.477\%   & 25.53\% & 46.67\%  &  21.89\% & \textbf{9.208\%} \\
-$b\bar{b}jj$ & 6.213\%  &40.56\%  &51.93\%  &  1.227\% & 0.072\% & \textbf{0.039\%}\\
+$b\bar{b}b\bar{b}$ & 0.858\% &  7.606\% &  27.523\% &  43.977\% &   20.036\% & \textbf{8.434\%} \\
+$b\bar{b}jj$ & 9.115\% &    41.792\% &    47.806\% &     1.216\% &  0.071\% & \textbf{0.038\%}\\
+$jjjj$ & 95.668\% &   3.789\% &  0.531\% & 0.011\%  & 3.00E-4\%& \textbf{2.17$\times 10^{-4}$\%}\\
 \hline
@@
 In this case the total cross-sections are presented after a cut requiring four anti-$k_T$ R=0.5 jets with $p_T>40$ GeV in the final state.
-The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.}\label{tab:UCLbtag}
+The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.
+\textbf{Needs to be updated to newer samples}.}\label{tab:UCLbtag}
 \end{table}%
@@
 It seems unlikely that this background can be neglected in the resolved analysis based upon a simple factor of $\epsilon_b^{2}\epsilon_l^{2}$ as used by the UCL group.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\textwidth]{plots/m4b_ucl_preCut.pdf}
+\caption{Contributions from the various samples to the observed four $b$ invariant mass system after applying the $b$-tagging procedure outlined in Section~\ref{sec:btagtest}.}
+\end{center}
+\end{figure}
 
@@
   PseudoRapidity -5 -3.0 3.0
+
+  DeltaR 5 5 0.1 10000
+  DeltaR 5 -5 0.1 10000
+  DeltaR -5 -5 0.1 10000
 }(selector);
@@
   PseudoRapidity 5 -3 3
-  PseudoRapidity 5 -3 3
+  PseudoRapidity -5 -3 3
 
@@
   PseudoRapidity 93 -3 3
+
+  DeltaR 93 93 0.1 10000
+  DeltaR 5 93 0.1 10000
+  DeltaR -5 93 0.1 10000
+  DeltaR 5 5 0.1 10000
+  DeltaR -5 5 0.1 10000
+  DeltaR -5 -5 0.1 10000
 }(selector);
@@
 
+\subsection {Background: QCD ttbar}
+\begin{verbatim}
+(run){
+  EVENTS 3M;
+  EVENT_GENERATION_MODE U;
+  ME_SIGNAL_GENERATOR Comix;
+
+  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_ttbar];
+
+  BEAM_1 2212; BEAM_ENERGY_1 7000;
+  BEAM_2 2212; BEAM_ENERGY_2 7000;
+
+  FRAGMENTATION=Off # disable hadronisation
+  MI_HANDLER=None # disable multiple parton interactions
+
+  SCF:=1; ### default scale factor
+  SCALES VAR{SCF*H_T2/4};
+
+  PDF_LIBRARY LHAPDFSherpa;
+  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
+  PDF_SET_VERSION 0;
+
+  MASSIVE[5] 1;
+  MASS[5] 4.75;
+
+  # Stable mode 0 specified that both particle and antiparticle are unstable
+  STABLE[6] = 0;
+  STABLE[24] = 0;
+
+  # Enable only fully hadronic decay modes
+  HARD_DECAYS=1;   
+  HDH_NO_DECAY={24,12,-11}|{24,14,-13}|{24,16,-15}|{-24,-12,11}|{-24,-14,13}|{-24,-16,15};
+
+}(run);
+
+(processes){
+  Process 93 93 -> 6 -6;
+  Order_EW 0;
+  End process;
+}(processes);
+
+(selector){
+  PT 6 20 7000
+  PT -6 20 7000
+  PseudoRapidity 6 -3 3
+  PseudoRapidity -6 -3 3
+  DeltaR 6 -6 0.1 10000
+}(selector);
+\end{verbatim}
+
+\clearpage
+\section{Decay tables for $t\bar{t}$}
+
+\begin{verbatim}
+Decay table for : W+.
+Total width:                  2.10561 GeV
+Flavour width:                2.06 GeV
+----------------------------------------
+{24,2,-1}         W+ --> u db              0.702203   GeV, BR= 33.3492 %
+{24,4,-3}         W+ --> c sb              0.701546   GeV, BR= 33.318 %
+{24,12,-11}       W+ --> nu_e e+           0.234068   GeV, BR= 11.1164 %
+{24,14,-13}       W+ --> nu_mu mu+         0.234066   GeV, BR= 11.1163 %
+{24,16,-15}       W+ --> nu_tau tau+       0.233725   GeV, BR= 11.1001 %
+----------------------------------------
+
+Decay table for : W-.
+Total width:                  2.10561 GeV
+Flavour width:                2.06 GeV
+----------------------------------------
+{-24,-2,1}        W- --> ub d              0.702203   GeV, BR= 33.3492 %
+{-24,-4,3}        W- --> cb s              0.701546   GeV, BR= 33.318 %
+{-24,-12,11}      W- --> nu_eb e-          0.234068   GeV, BR= 11.1164 %
+{-24,-14,13}      W- --> nu_mub mu-        0.234066   GeV, BR= 11.1163 %
+{-24,-16,15}      W- --> nu_taub tau-      0.233725   GeV, BR= 11.1001 %
+----------------------------------------
+
+Decay table for : t.
+Total width:                  1.59689 GeV
+Flavour width:                1.5 GeV
+----------------------------------------
+{6,24,5}          t --> W+ b               1.59689    GeV, BR= 100   %
+----------------------------------------
+
+Decay table for : tb.
+Total width:                  1.59689 GeV
+Flavour width:                1.5 GeV
+----------------------------------------
+{-6,-24,-5}       tb --> W- bb             1.59689    GeV, BR= 100   %
+
+\end{verbatim}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-02-06 doc/HH4b_Documentation.tex
updated docs

@@
 \hline
-$pp \to b\bar{b}b\bar{b}$ &  SHERPA 2.1.1 & 3M &$9.298 \times10^2$ pb \\
-$pp \to b\bar{b}jj$ &  SHERPA 2.1.1 & 3M & $2.208 \times 10^5$ pb\\
+$pp \to b\bar{b}b\bar{b}$ &  SHERPA 2.1.1 & 3M &$1.121 \times10^3$ pb \\
+$pp \to b\bar{b}jj$ &  SHERPA 2.1.1 & 3M & $2.659 \times 10^5$ pb \\
 $pp \to jjjj$ &  SHERPA 2.1.1 & 3M  & $9.709\times 10^6$ pb \\
-$pp \to t\bar{t}$ (had) &  SHERPA 2.1.1 & 100K & $2.511\times 10^3$ pb \\
+$pp \to t\bar{t}$ &  SHERPA 2.1.1 & 3M & $2.514\times 10^3$ pb \\
 \hline
 \end{tabular}
-\caption{Summary of generated samples to date} \label{tab:samples}
+\caption{Summary of generated samples to date. All {\tt SHERPA} samples have a MC error of $0.05\%$.} \label{tab:samples}
 \end{center}
@@
 \hline\hline
-$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $3.492\times10^{-1}$ pb \\ 
-$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$4.209 \times 10^2$ pb \\ 
+$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $4.123\times10^{-1}$ pb \\ 
+$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$4.239 \times 10^2$ pb \\ 
 $jjjj$ & -  & $4.450\times 10^4$ pb \\
@@
 The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison.
-Finally, the signal-to-background ratio and significance are given both before and after the b-tagging, for $\mathcal{L}=$ 3 ab$^{-1}$.} \label{tab:btageff1}
+Finally, the signal-to-background ratio and significance are given both before and after the b-tagging, for $\mathcal{L}=$ 3 ab$^{-1}$.} \label{tab:btageff1}.
+Note, older samples have been used here with different generator cuts.
 \end{table}%
@@
 The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.
-\textbf{Needs to be updated to newer samples}.}\label{tab:UCLbtag}
+Note, older samples have been used here with different generator cuts.}\label{tab:UCLbtag}
 \end{table}%
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \begin{center}
@@
 
+\clearpage
 \section{Results}
+\subsection{Example resolved analysis}
+In this section we present the results of a resolved style analysis upon the full set of available samples for the purposes of illustration.
+The cuts used in this example analysis are as so.
+\emph{b-tag} cuts those events which fail to tag four anti-$k_T$ $R=0.5$ $b$-jets with $b$ quark $p_T > 15$ GeV.
+Flat $b$-jet efficiencies and mistag rates of 80\% and 1\% respectively.
+A $c$ mistag rate of $17\%$ is also applied.
+\emph{jet $p_T$,$\eta$} requires that the four jets each have $p_T>40$ GeV and $|\eta|< 2.5$.
+\emph{di-jet $p_T$} requires that each dijet pair representing a higgs candidate has $p_T>150 $ GeV.
+\emph{di-jet $\Delta\eta$} requires that the two dijets are separated by no more than 1.5 units in $\eta$.
+Finally \emph{$m_H$ window} requires that the invariant mass of each dijet is within 15 GeV of $m_H$.
+The remaining cross-section after each of these cuts, along with $S/B$ and $S/\sqrt{B}$ are given in Table ~\ref{tab:resCutflow}.
+
+\begin{table}[htdp]
+\begin{center}
+\begin{tabular}{|c||c||c|c|c|c||c|c|}
+\hline
+Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
+\hline
+b-tag    	& 1.516 &      102271         & 135255        & 42934  	&	202.9	&5.40E-6	& 0.157\\
+jet $p_T,\eta$         & 0.723 &        3847      & 10676       & 5045 	&	122.7	&3.67E-5	& 0.282\\
+di-jet $p_T$           	& 0.371&      553.7        & 1838	  & 926.0	&	22.45	&1.11E-4	& 0.352\\
+di-jet $\Delta\eta$   & 0.336&       324.8       & 991.4 	  & 312.6		&	16.39	&2.04E-4	& 0.454\\
+\hline
+$m_H$ window   &0.190 &          7.632      & 13.60	  & 0.502	&	2.675	&7.78E-3	& 2.106\\
+\hline
+\end{tabular}
+\end{center}
+\caption{Table demonstrating the cutflow of an example resolved analysis applied to the full sample set.  $S/\sqrt{B}$ is given for HL-LHC luminosities.}
+\label{tab:resCutflow}
+\end{table}%
+
+\subsection{Example boosted analysis}
+Here we shall discuss an example boosted analysis.
+In this case \emph{Fatjet cuts} refers to the requirement of two $R=1$ anti-$k_T$ jets with $p_T>250$ GeV and $|\eta| < 2.5$.
+\emph{2 Subjets} requires two anti-$k_T$ $R=0.3$ subjects in each fat jet.
+\emph{b-Tagging} cuts those events in which the two hardest subjets are not successfully $b$-tagged.
+Here efficiency and mistag factors are applied for $b$ and $c$ jets as a function of subjet $p_T$.
+\emph{Mass-drop } requires that the two fat jets pass a BDRS mass-drop tagger with parameters $\mu = 0.67$ and $y_{\mathrm{cut}} = 0.09$.
+Finally \emph{$m_H$ window} only passes events where the two fat jet masses are within $15$ GeV of $m_H$.
+In Table~\ref{tab:boostedCutflow} we see the results of these cuts.
+\begin{table}[htdp]
+\begin{center}
+\begin{tabular}{|c||c||c|c|c|c||c|c|}
+\hline
+Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
+\hline
+Fatjet cuts 			&2.802           	&3045 	& 1.13E6 &	4.57E7    &       9808  & 5.98E-8 &0.022 \\
+2 Subjets  	&	2.740 	&2694	& 1.01E6	&	4.21E7 	&	9787  &6.35E-8 & 0.023\\
+b-Tagging    			& 0.070		&39.76	& 296.9		&	352.9            &      7.586 & 1.00E-5& 0.145\\
+Mass-drop  		& 0.068 		&36.84	& 256.0    	&	305.1            &	7.514 & 1.12E-4& 0.151 \\
+%\hline
+$m_H$ window       		&   0.045		& 2.134	& 10.83	& 	0.630            & 	0.438 & 3.20E-3& 0.658\\
+\hline
+\end{tabular}
+\end{center}
+\caption{Table demonstrating the cutflow of an example boosted analysis applied to the full sample set. $S/\sqrt{B}$ is given for HL-LHC luminosities.}
+\label{tab:boostedCutflow}
+\end{table}%
+
+\subsection{MVA}
+We now apply a basic MVA to the final output of the resolved and boosted analyses.
+The MVA used is a feedforward artificial neural network with $N_{\mathrm{par}}\times5\times3\times1$ architecture, where $N_{\mathrm{par}}$ is the number of input parameters for the network.
+The MVA was trained for 50,000 GA generations with a cross-entropy error function.
+In Figure~\ref{fig:nnresponse} the neural network classification of events is demonstrated for both the resolved and boosted cases.
+In Figure~\ref{fig:exampleroc} the ROC curves for the two analyses are shown, demonstrating that the neural network is able to
+perform well in both cases. Figure~\ref{fig:nnweights} shows the distribution of NN weights in both cases.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/resolved_MVA_hist.pdf}
+\includegraphics[width=0.49\textwidth]{plots/boosted_MVA_hist.pdf}
+\caption{Neural network response demonstrated for the case of the resolved (left) and boosted (right) analyses.
+The frequency of background and signal events is plotted as a function of neural network output.}
+\label{fig:nnresponse}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.95\textwidth]{plots/example_roc.pdf}
+\caption{ROC curve for the neural network discriminant in the boosted (green) and resolved (blue) cases.}
+\label{fig:exampleroc}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=1\textwidth]{plots/nnweights_res.pdf}
+\includegraphics[width=1\textwidth]{plots/nnweights_boost.pdf}
+\caption{Distribution of weights per input variable in the final ANN analysis.
+The above figure shows the weight distribution in the case of the resolved analysis, while the lower plot shows the boosted analysis.}
+\label{fig:nnweights}
+\end{center}
+\end{figure}
 
@@
   SCF:=1; ### default scale factor
-  SCALES VAR{SCF*H_T2/2};
+  SCALES VAR{SCF*H_T2/4};
 
@@
   DeltaR -5 -5 0.1 10000
+
 }(selector);
@@
 }(run);
+
 (processes){
@@
   End process;
+}(processes);
 
-}(processes);
 (selector){
@@
   PseudoRapidity 93 -3 3
+  DeltaR 93 93 0.1 10000
 }(selector);

### 2015-02-12 doc/HH4b_Documentation.tex
updated docs
Add boosted control plots to documentation

@@
 
+\subsubsection{$bb$-jet rejection for the four hardest jets}
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & After $bb$ rejection & \% selected  \\
+\hline \hline
+$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & & 7.467\% \\
+\hline
+$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & & 5.472\% \\
+$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & & 0.0224\% \\
+\hline
+\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& & \multicolumn{1}{c}{}\\
+\cline{1-3}
+\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& & \multicolumn{1}{c}{}\\
+\cline{1-3}
+\end{tabular}
+\end{center}
+\caption{Summary of the $b$-tagging and $bb$-rejection cuts on the four leading jets.}\label{tab:TestbbTag}
+\end{table}%
+
 \subsection{Boosted Topology}\label{sec:Boosted_FR}
@@
 may lead to multiple matchings.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/histo_mfj1_preCut.pdf}
+\includegraphics[width=0.49\textwidth]{plots/histo_mfj2_preCut.pdf}
+\caption{Mass distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
+\label{fig:mfj_boosted_pre}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj1_preCut.pdf}
+\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj2_preCut.pdf}
+\caption{$d_{12}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
+\label{fig:split12_fj_boosted_pre}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj1_preCut.pdf}
+\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj2_preCut.pdf}
+\caption{$\tau_{21}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
+\label{fig:tau21_fj_boosted_pre}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/histo_mfj1.pdf}
+\includegraphics[width=0.49\textwidth]{plots/histo_mfj2.pdf}
+\caption{Mass distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
+\label{fig:mfj_boosted_post}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj1.pdf}
+\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj2.pdf}
+\caption{$d_{12}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
+\label{fig:split12_fj_boosted_post}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj1.pdf}
+\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj2.pdf}
+\caption{$\tau_{21}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
+\label{fig:tau21_fj_boosted_post}
+\end{center}
+\end{figure}
 
@@
 Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
+\hline
 \hline
@@
 \hline
+\hline
 Fatjet cuts 			&2.802           	&3045 	& 1.13E6 &	4.57E7    &       9808  & 5.98E-8 &0.022 \\
@@
 Mass-drop  		& 0.068 		&36.84	& 256.0    	&	305.1            &	7.514 & 1.12E-4& 0.151 \\
-%\hline
+\hline
 $m_H$ window       		&   0.045		& 2.134	& 10.83	& 	0.630            & 	0.438 & 3.20E-3& 0.658\\

### 2015-02-13 doc/HH4b_Documentation.tex
HH4b Docs

@@
 \end{figure}
+\clearpage
+
+Figure~\ref{fig:nnweights} demonstrates that the dijet invariant mass is a crucial variable for the resolved analysis MVA.
+As no detector effects were modelled in this analysis, it is reasonable to assume that the MVA has greater discriminating power than would be feasible in a real analysis.
+To investigate this, we now consider a variant of the analysis used in Table~\ref{tab:resCutflow} where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
+Firstly the same analysis is repeated with the larger $m_H$ window.
+This is then compared to the same analysis but with a Gaussian smearing with $\sigma=10$ GeV applied to the dijet invariant mass used in the MVA.
+In the left panel of Figure~\ref{fig:invMsmear} the smearing is demonstrated.
+Despite the smearing, the MVA applied to this analysis still vastly prefers the dijet masses as discriminators, as is demonstrated in the right panel of Figure~\ref{fig:invMsmear}.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/Msmear/histo_mass_smear_precut.pdf}
+\includegraphics[width=0.49\textwidth]{plots/Msmear/nnweights.pdf}
+\caption{The left figure demonstrates the gaussian smearing applied to the dijet invariant mass distribution. The right figure demonstrates the ANN weight distribution in the MVA.}
+\label{fig:invMsmear}
+\end{center}
+\end{figure}
+
+While the MVA still derives most of it's discriminating power from the dijet masses, the smearing reduces it's effectiveness considerably.
+In Figure \ref{fig:smearedROC} the ROC curves of the MVA applied to the smeared and unsmeared distributions are shown, where it is clear that the overall performance of the MVA is significantly hampered by the smeared invariant masses.
+This is echoed in the resulting significance of the analysis as demonstrated in Figure~\ref{fig:smearedSB}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.89\textwidth]{plots/Msmear/roc.pdf}
+\caption{ROC curves of the MVA applied with the unsmeared (blue) and smeared (green) dijet invariant mass distributions.}
+\label{fig:smearedROC}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/Msmear/sb.pdf}
+\includegraphics[width=0.49\textwidth]{plots/Msmear/ssb.pdf}
+\caption{$S/B$ and $S\sqrt{B}$ (HL\-LHC) for the MVA applied to the unsmeared (blue) and smeared (green) dijet invariant mass distributions.}
+\label{fig:smearedSB}
+\end{center}
+\end{figure}
+\clearpage
 

### 2015-02-13 doc/HH4b_Documentation_kb.tex
kb docs

--- 2015-02-12 doc/HH4b_Documentation.tex
@@
 \begin{center}
-\includegraphics[width=\textwidth]{plots/m4b_ucl_preCut.pdf}
+% \includegraphics[width=\textwidth]{plots/m4b_ucl_preCut.pdf}
 \caption{Contributions from the various samples to the observed four $b$ invariant mass system after applying the $b$-tagging procedure outlined in Section~\ref{sec:btagtest}.}
@@
 \subsubsection{$bb$-jet rejection for the four hardest jets}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{plots/histo_NbConstits_4hardest.pdf}
+\includegraphics[width=\textwidth]{plots/histo_NbConstits_4hardest_afterBtag.pdf}
+\caption{.}
+\end{center}
+\end{figure}
 
@@
 \hline \hline
-$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & & 7.467\% \\
+$H\bar{H}$ & 17.2911 & 1.4655 & 1.38429 & \% \\
 \hline
-$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & & 5.472\% \\
-$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & & 0.0224\% \\
+$b\bar{b}b\bar{b}$ & 1.12149e+06 & 101152 & 95723.1 & \% \\
+$b\bar{b}jj$ & 2.65895e+08 & 98116.7 & 88956.2 & \% \\
+$jjjj$ & 1.22738e+10 & 626267 & 604.205 & \% \\
 \hline
-\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& & \multicolumn{1}{c}{}\\
+\textbf{S/B} & & & & \multicolumn{1}{c}{}\\
 \cline{1-3}
-\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& & \multicolumn{1}{c}{}\\
+\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& & & & \multicolumn{1}{c}{}\\
 \cline{1-3}
@@
 \caption{Summary of the $b$-tagging and $bb$-rejection cuts on the four leading jets.}\label{tab:TestbbTag}
+\end{table}%
+
+\subsubsection{$bb$-jet rejection for the UCL-style selection}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{plots/histo_NbConstits_UCL.pdf}
+\includegraphics[width=\textwidth]{plots/histo_NbConstits_UCL_afterBtag.pdf}
+\caption{.}
+\end{center}
+\end{figure}
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & After $bb$ rejection & \% selected  \\
+\hline \hline
+$H\bar{H}$ &10.7756 & 0.796946 & 0.744208 & 7.467\% \\
+\hline
+$b\bar{b}b\bar{b}$ & 101152 & 4789.57 & 4438.72 & \% \\
+$b\bar{b}jj$ & 1.72539e+07 & 9962.27 & 8564.06 & \% \\
+$jjjj$ & 6.10999e+08 & 1.07288e-06 & 1.07288e-06 & \% \\
+\hline
+\textbf{S/B} & & & & \multicolumn{1}{c}{}\\
+\cline{1-3}
+\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$} & & & & \multicolumn{1}{c}{}\\
+\cline{1-3}
+\end{tabular}
+\end{center}
+\caption{Summary of the $b$-tagging and $bb$-rejection cuts on the four leading jets.}\label{tab:TestbbTagUCL}
 \end{table}%

### 2015-02-13 doc/HH4b_Documentation.tex
HH4b docs

@@
 
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{plots/histo_NbConstits_4hardest.pdf}
+\includegraphics[width=\textwidth]{plots/histo_NbConstits_4hardest_afterBtag.pdf}
+\caption{.}
+\end{center}
+\end{figure}
+
 \begin{table}[h]

### 2015-04-23 doc/talk_beamer.tex
Added talk code

\documentclass[svgnames]{beamer}

%to get rid of font size warnings
\let\Tiny=\tiny

\definecolor{beamer@blendedblue}{rgb}{0.137,0.466,0.741}
\usetheme{Warsaw}
\usecolortheme[named=beamer@blendedblue]{structure}
\setbeamercolor{structure}{fg=beamer@blendedblue}

\usepackage{xcolor}

\graphicspath{{figures/}}

% \usepackage{epstopdf}
\usepackage{beamerthemesplit,framed,amssymb,amsmath,graphicx,enumerate,array}
\usepackage{multirow}
\usepackage{color}
\usepackage{xcolor}
\usepackage{ngerman}  %Umlaute mit ü = "u
% \usepackage[latin1]{inputenc} 
% \usepackage{mathrsfs}
\usepackage{lmodern}
\usepackage[T1,OT1]{fontenc}
\usepackage[absolute,overlay]{textpos}

\definecolor{darkgreen}{rgb}{0,0.7,0}
 \definecolor{lightblue}{rgb}{0.63, 0.79, 0.95}

\usepackage{tikz}
\usetikzlibrary{trees}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.markings}

\tikzset{
    W/.style={decorate, decoration={snake}, draw=black},
    fermion/.style={draw=black, postaction={decorate}, decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    antifermion/.style={draw=black, postaction={decorate}, decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    gluon/.style={decorate, draw=black, decoration={coil,amplitude=4pt, segment length=5pt}} 
}

\parindent0pt % Legt die Einrück-Tiefe der ersten Zeile für alle folgenden Absätze fest

\setbeamertemplate{navigation symbols}{}
% \setbeamertemplate{footline}{
% \insertpagenumber}

\newcommand{\wipW}[2]{\begin{flushright}\vspace*{-#1cm}\mbox{\begin{scriptsize}\centering{\includegraphics[height=15pt]{/home/k/Katharina.Behr/Talks/DPG_2012/pictures/atlas_small_w.png}}~\color{black}simulation: work-in-progress\color{black}\makebox[#2cm][l]{}\end{scriptsize}}\\
\vspace*{#1cm}\end{flushright}}
\newcommand{\wipWs}[2]{\begin{flushright}\vspace*{-#1cm}\mbox{\begin{tiny}\centering{\includegraphics[height=10pt]{/home/k/Katharina.Behr/Talks/DPG_2012/pictures/atlas_small_w.png}}~\color{black}simulation: work-in-progress\color{black}\makebox[#2cm][l]{}\end{tiny}}\\
\vspace*{#1cm}\end{flushright}}
\newcommand{\wipWR}{\begin{flushright}\wipW\end{flushright}}
\newcommand{\wipWRs}{\begin{flushright}\wipWs\end{flushright}}

% \renewcommand{\arraystretch}{1.2} %adjust vertical spacing in tables

\setbeamertemplate{footline}{%
\begin{beamercolorbox}[wd=0.5\textwidth,ht=3ex,dp=1.5ex,leftskip=.5em,rightskip=.5em]{author
in head/foot}%
\usebeamerfont{author in head/foot}%
\insertframenumber/4\hfill\insertshortauthor%
\end{beamercolorbox}%

\vspace*{-4.5ex}\hspace*{0.5\textwidth}%
\begin{beamercolorbox}[wd=0.5\textwidth,ht=3ex,dp=1.5ex,left,leftskip=.5em]{title
in head/foot}%
\usebeamerfont{title in head/foot}%
\insertshorttitle%
\end{beamercolorbox}% 
}

%\beamersetuncovermixins{\opaqueness<1>{25}}{\opaqueness<2->{15}} 		% \beamersetuncovermixins{hnot yet listi}{honce more listi}: The hnot yet listi specifies how to render covered items that have not yet been uncovered. The honce more listi specifies how to render covered items that have once more been covered. If you leave one of the specifications empty, the corresponding covered items are completely covered, that is, they are invisible.

%define author BEFORE begin{document} to get rid of hyperref warning ``Option `pdfauthor’ has already been used''
% \author[Katharina Behr]{Katharina Behr}
\author[Katharina Behr]{\texorpdfstring{\bf Katharina Behr}{Katharina Behr}}

% \author[Katharina Behr (LMU M\"unchen)]{\texorpdfstring{\textbf{Katharina Behr} \newline \scriptsize{supervised by Otmar Biebel}}{Katharina Behr (LMU M\"unchen)}}
%\author[für unten]{\texorpdfstring wegen Sonderformat --> in HypeRef (Links) dürfen keine Formeln}
% \institute{LS Schaile, LMU M\"unchen}

\input{talk.tex}

### 2015-04-24 paper/HH4b.tex
Added latex template of paper

\documentclass[a4paper,11pt]{article}
\usepackage{jheppub}
\usepackage{graphicx}% Include figure files
\usepackage{graphics}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{epstopdf}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage[pdftex]{hyperref}
\usepackage{natbib}

\def\bs{\boldsymbol}
\def\del{\partial}

%\def\p{{\boldsymbol p}_{\perp }}
%\def\pb{\bar {\boldsymbol p}_{\perp }}
%\def\pp{{\boldsymbol p}_{\perp }}
\def\p{{\boldsymbol p}}
\def\pb{\bar {\boldsymbol p}}
\def\pp{{\boldsymbol p}}
%\def\q{{\boldsymbol q}_\perp}
\def\q{{\boldsymbol q}}
\def\l{{\boldsymbol l}_\perp}
%\def\k{{\boldsymbol k}_\perp}
\def\k{{\boldsymbol k}}
\def\m{{\boldsymbol m}_\perp}
%\def\x{{\boldsymbol x}_\perp}
\def\x{{\boldsymbol x}}
\def\y{{\boldsymbol y}_\perp}
\def\X{{\boldsymbol X}_\perp}
\def\Y{{\boldsymbol Y}_\perp}
\def\D{{\boldsymbol D}_\perp}
\def\r{{\boldsymbol r}_\perp}
\def\z{{\boldsymbol z}_\perp}
%\def\v{{\boldsymbol v}_\perp}
\def\v{{\boldsymbol v}}
\def\w{{\boldsymbol w}_\perp}
\def\b{{\boldsymbol b}_\perp}
\def\Q{{\boldsymbol Q}_\perp}
\def\M{{\boldsymbol M}_\perp}
%\def\bkappa{{\boldsymbol \kappa}_\perp}
%\def\bbkappa{\bar{\boldsymbol \kappa}_\perp}
\def\bkappa{{\boldsymbol \kappa}}
\def\bbkappa{\bar{\boldsymbol \kappa}}
\def\bnu{{\boldsymbol \nu}_\perp}
\def\V{\hat{\boldsymbol v}_{1\perp}}
\def\K{\hat{\boldsymbol k}_{1\perp}}
\def\bV{\hat{\boldsymbol v}_{2\perp}}
\def\bK{\hat{\boldsymbol k}_{2\perp}}
\def\qqb{{q\bar q}}
\def\sM{{\scriptscriptstyle M}}

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\nn}{\nonumber\\ }
\newcommand{\labe}{\label}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}

\bibliographystyle{JHEP}
\usepackage{multirow}

\title{Boosting Higgs Pair Production in the $4b$ Channel at the LHC with Multivariate Techniques}

\author[a]{Katharina Behr, Nurfiki Bin Norjoharuddeen, Daniela Bortoletto, James Frost, Nathan P. Hartland, Cigdem Issever and Juan Rojo}

\affiliation[a]{Physics Department, 1 Keble Road, University of Oxford, United Kingdom }

\emailAdd{juan.rojo@physics.ox.ac.uk}

\preprint{OUTP-15-aaa}

\abstract{
A nice abstract
}

\begin{document} 
\maketitle

\flushbottom

% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Monte Carlo samples
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-mcsamples}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% analysis strategy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Main results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% MVA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-mva}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Conclusions and outlook
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{sec-conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{HH4b}

\end{document}

### 2015-04-24 paper/sec-analysis.tex
Added latex template of paper

\section{Analysis strategy}
\label{sec:analysis}

Describe the 3 different kinematic regimes: resolved, semi-boosted and boosted and selection cuts. Show table with numbers. How often do events end up in these categories.

Table 1: how many events we see from Signal and background in each category. Indicate also the overlap between the categories. This table should have also the S/B and S/sqrtB numbers. We need also the S/B and S/sqrtB numbers without the 2b2j and 4j backgrounds in order to compare with the UCL paper in this table.

Figure 1: Higgs pt, eta distributions

Figure 2: b-jet pt distributions

Figure 3: delta R distributions

Figure 4: mass distributions

Table 2: S/B and S/sqrtB table with
All these figures should have the backgrounds overlaid.

This section would show that the 2b2j and 4j backgrounds are important and that control of the fakes is necessary.

This section should also identify which of the different regimes is the most important for the measurement.

### 2015-04-24 paper/sec-intro.tex
Added latex template of paper

\section{Introduction}

Describe the importance of the 2H channel and its connection to the self-coupling.
Stress the importance of self-coupling measurement and refer to previous studies which estimated the amount data needed for when this will be possible at the LHC.
Discuss the different decay channels of the Higgs and point to the fact that given the fact how low the SM di-Higgs cross section is that the 4b channels would give rates which would be by factors of xx larger than the other channels.
But previous studies show that xx fb-1 are needed due to the high backgrounds.
We refer to UCL paper and its results and say that our studies point to the fact that fake rate from the 2b2j and 4j background are not negligible. We have studied this and will present ways to mitigate this impact and present also new techniques to analyse this channel which improve the signal to background ratio.

The measurement of double Higgs production will be one of the main
physics goals of the LHC program in its upcoming high-energy and high-luminosity phase, as
well as of the program of any future high-energy collider.
%
Double Higgs production is directly sensitive to the Higgs trilinear coupling, and thus 
provides information on the scalar potential responsible for electroweak symmetry breaking.
It is also sensitive to the underlying strength of the Higgs interactions
at high energies, and can test the composite nature of the 
Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.

In the Standard Model (SM), the dominant mechanism for the production of two Higgs bosons at the LHC is 
gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production.
For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the recently computed next-to-next to leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea}.
%
Feasibility studies in the case of a light Higgs boson have been performed for several different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Gouzevitch:2013qca,Cooper:2013kia,Wardrope:2014kya,deLima:2014dta}.
%

The structure of this paper is the following.

### 2015-04-24 paper/sec-mcsamples.tex
Added latex template of paper

\section{Monte Carlo samples}

Here we descrive the generation of the MC samples that
we are using in this work

### 2015-04-24 paper/sec-results.tex
Added latex template of paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}

\label{sec:results}

Study S/B, S/sqrt B vs b-tagging efficiency, background rejection and signal efficiency

This section would show how S/B is correlated with the different efficiencies. It would give the reader a feel for which of these sources the analysers would need to attack to make the 4b channel a competitive channel with regard to other channels.

### 2015-04-24 paper/sec-mcsamples.tex
MC Chapter
I have added the text from the analysis summary tex-file on the MC
samples to this section. I will need work on this later.

@@
 
-Here we descrive the generation of the MC samples that
-we are using in this work
+\subsection{Signal}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Background}
+All background samples are generated with the {\tt SHERPA} event generator, version 2.1.1. For the explicit runcards used in the generation, see Appendix~\ref{app:runcards}.
+
+The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples.
+At the generator level the following basic cuts are applied.
+Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
+All final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
+Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$.
+Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
+\hline
+\hline
+$pp \to HH$ &  MG5\_aMC@NLO & 100K & $1.729\times10^{-2}$ pb \\
+\hline
+$pp \to b\bar{b}b\bar{b}$ &  SHERPA 2.1.1 & 3M &$1.121 \times10^3$ pb \\
+$pp \to b\bar{b}jj$ &  SHERPA 2.1.1 & 3M & $2.659 \times 10^5$ pb \\
+$pp \to jjjj$ &  SHERPA 2.1.1 & 3M  & $9.709\times 10^6$ pb \\
+$pp \to t\bar{t}$ &  SHERPA 2.1.1 & 3M & $2.514\times 10^3$ pb \\
+\hline
+\end{tabular}
+\caption{Summary of generated samples to date. All {\tt SHERPA} samples have a MC error of $0.05\%$.} \label{tab:samples}
+\end{center}
+\end{table}%
+
+Although suffering from a large theory uncertainty, we can compare the result of our background samples against those presented in the MG5\_aMC@NLO paper~\cite{Alwall:2014hca}.
+Here for comparison we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV.
+All jets must be within an acceptance of $|\eta| \le 2.5 $.
+In the case of the samples with $b$ quarks in the final state, these requirements are extended to the appropriate number of $b$-jets.
+For example, in the 2$b$2$j$ sample there must be at least two $b$-jets that pass the cuts outlined above.
+
+In Table~\ref{tab:xsecs} this comparison is summarised for the $2b2j$ and $4b$ samples. Considering the large theory errors, agreement is reasonable in both instances.
+
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|}
+\hline
+Process & $\sigma$ aMC@NLO & $\sigma$ Oxford (SHERPA) \\
+\hline\hline
+$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $4.123\times10^{-1}$ pb \\ 
+$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$4.239 \times 10^2$ pb \\ 
+$jjjj$ & -  & $4.450\times 10^4$ pb \\
+\hline
+\end{tabular}
+\caption{Comparison of LO Oxford SHERPA cross-sections with those of the aMC@NLO paper. The aMC@NLO cross-sections come with a quoted $~50\%$ theory uncertainty.} \label{tab:xsecs}
+\end{center}
+\end{table}%

### 2015-05-31 doc/HH4b_Documentation.tex
Updated documentation

@@
 
+\subsection{Object Definition and Selection}
+
+All jets are clustered using all final state particles after the parton shower (but before hadronisation) as input.
+
+Small-$R$ jets are anti-$k_T$ $R=0.4$ jets. They are required to have $p_T > 40$~GeV and $|\eta|<2.5$.
+
+Small-$R$ subjets are anti-$k_T$ $R=0.3$ jets. They are required to have $p_T > 50$~GeV and $|\eta|<2.5$.
+
+Large-$R$ jets are anti-$k_T$ $R = 1.0$ jets with $p_T > 200$~GeV and $|\eta|<2.0$ (the smaller pseudorapidity is an experimental requirement related to the trackjet-based calibration).
+They are also required to be mass-drop tagged using the FastJet default parameters: $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
+
+Small-$R$ jets are $b$-tagged as follows: True $b$-jets, which have at least one $b$-quark among their constituents, have a 80\% $b$-tagging probability.
+For all other jets, a mistag rate of 0.01 is used.
+
+Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$ (selected as above) to the large-$R$ jets.
+A large-$R$ jets is considered $bb$-tagged if the leading and subleading $p_T$ associated subjets are $b$-tagged.
+
 \subsection{Resolved Topology}
 
-The resolved selection requires the presence of at least four b-tagged anti-$k_T$ $R=0.4$ jets with $p_T >$25~GeV and $|\eta|>2.5$.
-\textit{Pre-cut} histograms are written out for various kinematic distributions for all events with at least four b-tagged jets but before applying
-further kinematic cuts. \textit{Post-cut} histograms contain only events where the four jets also pass the above kinematic cuts.
+The resolved selection requires the presence of at least four $b$-tagged, selected anti-$k_T$ $R=0.4$ jets.
 
@@
 are considered here.
+
+\subsection{Boosted Topology}
+
+The boosted selection requires the presence of at least two $bb$-tagged, selected anti-$k_T$ $R=1.0$ jets which are taken as the two Higgs boson candidates.
+
+\subsection{Intermediate Topology}
+
+The intermediate topology requires the presence of at least one $bb$-tagged, selected anti-$k_T$ $R = 1.0$ jet.
+If there is more than one, the leading one is taken as the first Higgs boson candidate.
+In addition, there must be at least two anti-$k_T$ $R=0.4$ jets with a separation $\Delta R > 1.0$ with respect to the large-$R$ jet
+that is selected as a Higgs boson candidate. The second Higgs boson candidate is reconstructed from the two small-$R$ jets that minimise the difference $|m_{fj} - m_{j1j2}|$.
+
+\subsection{Higgs Mass Window Cut}
+
+All Higgs candidates are required to meet the following Higgs mass window cut: $|m_{H} - 125| < 40$~GeV
+
+[THE INFORMATION BELOW HAS NOT BEEN UPDATED YET]
 

### 2015-06-01 paper/sec-analysis.tex
Working on sect 3

@@
 \label{sec:analysis}
+
+In this section we describe our analysis strategy, and in particular
+the classification of each individual event into
+different categories according to the event topology.
+
+The starting point is clustering all final state particles in each
+event,  after the parton shower (but before hadronization).
+%
+We adopt the following terminology for the different types of jets
+that we will use in this work
+\begin{itemize}
+\item {\it Small-$R$ jets} are jets constructed with the
+  anti-$k_T$ clustering algorithm with $R=0.4$ radius.
+  %
+  Only jets with transverse momentum $p_T > 40$~GeV within
+  the central acceptance $|\eta|<2.5$ can be considered.
+
+\item {\it Small-$R$ subjets} are anti-$k_T$ $R=0.3$ jets.
+%
+  They are required to have $p_T > 50$~GeV and $|\eta|<2.5$.
+
+\item {\it Large-$R$ jets}  are jets constructed with the
+  anti-$k_T$ clustering algorithm with $R=1.0$ radius.
+  %
+  We require that these large-$R$ jets satisfy  $p_T > 200$~GeV and
+  $|\eta|<2.0$.
+  %
+  The smaller range in pseudo-rapidity, as compared to the small-$R$ jets,
+  is motivated by mimicking the  experimental requirements
+  related to the track-jet-based calibration).
+  %
+  On top of the basic $p_T$ and $\eta$ cuts, only large-$R$ jets
+  that satisfy the BDRS mass-drop tagger condition will be kept, else
+  the jet is discarded.
+  %
+  For the BDRS mass-drop tagger, we use the {\tt FastJet} default
+  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
+  \end{itemize}
+
+Small-$R$ jets are $b$-tagged as follows: True $b$-jets, which have at least one $b$-quark among their constituents, have a 80\% $b$-tagging probability.
+For all other jets, a mistag rate of 0.01 is used.
+
+Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$ (selected as above) to the large-$R$ jets.
+A large-$R$ jets is considered $bb$-tagged if the leading and subleading $p_T$ associated subjets are $b$-tagged.
+
+The resolved selection requires the presence of at least four $b$-tagged, selected anti-$k_T$ $R=0.4$ jets.
+
+The di-Higgs system is reconstructed by considering all possibilities of forming two pairs of jets with invariant masses $m_{j1j2}$ and 
+$m_{j3j4}$, respectively, and choosing the configuration that minimizes their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
+are considered here.
+
+The boosted selection requires the presence of at least two $bb$-tagged, selected anti-$k_T$ $R=1.0$ jets which are taken as the two Higgs boson candidates.
+
+The intermediate topology requires the presence of at least one $bb$-tagged, selected anti-$k_T$ $R = 1.0$ jet.
+If there is more than one, the leading one is taken as the first Higgs boson candidate.
+In addition, there must be at least two anti-$k_T$ $R=0.4$ jets with a separation $\Delta R > 1.0$ with respect to the large-$R$ jet
+that is selected as a Higgs boson candidate. The second Higgs boson candidate is reconstructed from the two small-$R$ jets that minimize the difference $|m_{fj} - m_{j1j2}|$.
+
+All Higgs candidates are required to meet the following Higgs mass window cut: $|m_{H} - 125| < 40$~GeV
+
+{\bf BELOW: outline of the section}\\
 

### 2015-06-01 paper/HH4b.tex
changed front page
Some work on the draft

@@
 
-\title{Boosting Higgs Pair Production in the $4b$ Channel at the LHC with Multivariate Techniques}
+\title{Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques}
 
@@
 
-\emailAdd{juan.rojo@physics.ox.ac.uk}
+\emailAdd{cigdem.issever@physics.ox.ac.uk}
 
@@
 \abstract{
-A nice abstract
+  The measurement of Higgs pair production is one of the cornerstones of
+  the LHC program for the next years.
+  %
+  Double Higgs production provides a unique window to the full electroweak
+  symmetry breaking potential, in particular to the Higgs trilinear coupling.
+  %
+  In this work we study the feasibility of measuring the production of
+  Higgs boson pairs at the High-Luminosity LHC using the
+  $bb\bar{b}\bar{b}$ final state.
+  %
+  While the signal in this channel
+  is enhanced by the large branching fraction of Higgs to
+  $b\bar{b}$ pairs, this measurement is extremely challenging due to the
+  overwhelming QCD background.
+  %
+  By combining the cintribution from resolved, boosted and intermediate
+  topologies, and enhancing the signal over background ratio
+  using multivariaty techniques, we find that a significance of AAA
+  can be obtained at 14 TeV with 3000 fb$^{-1}$.
 }

### 2015-06-01 paper/sec-conclusions.tex
Some work on the draft

\section{Conclusions and outlook}

In this work we have presented a detailed study of the feasibility
of the measurement of Higgs pair production in the $bb\bar{b}\bar{b}$
final state at the High-Luminosity LHC....

\bigskip
\bigskip
\begin{center}
\rule{5cm}{.1pt}
\end{center}
\bigskip
\bigskip

{\bf\noindent  Acknowledgments \\}
We thank A.~Papaefstathiou for useful discussions on this project.
%
J.~R. is supported by an STFC Rutherford Fellowship ST/K005227/1.
%
J.~R. and N.~H. are
supported by an European Research Council Starting Grant "PDF4BSM".
%

### 2015-06-01 paper/sec-intro.tex
Updated introduction

@@
 
-Describe the importance of the 2H channel and its connection to the self-coupling.
-Stress the importance of self-coupling measurement and refer to previous studies which estimated the amount data needed for when this will be possible at the LHC.
-Discuss the different decay channels of the Higgs and point to the fact that given the fact how low the SM di-Higgs cross section is that the 4b channels would give rates which would be by factors of xx larger than the other channels.
-But previous studies show that xx fb-1 are needed due to the high backgrounds.
-We refer to UCL paper and its results and say that our studies point to the fact that fake rate from the 2b2j and 4j background are not negligible.
-We have studied this and will present ways to mitigate this impact and present also new techniques to analyse this channel which improve the signal to background ratio.
-
 The measurement of double Higgs production will be one of the main
-physics goals of the LHC program in its upcoming high-energy and high-luminosity phase, as
+physics goals of the LHC program in its recently started high-energy
+phase, as well as for its future high-luminosity phase, as
 well as of the program of any future high-energy collider.
@@
 provides information on the scalar potential responsible for electroweak symmetry breaking.
+%
 It is also sensitive to the underlying strength of the Higgs interactions
@@
 gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production.
-For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the recently computed next-to-next to leading order (NNLO)
+For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the recently computed next-to-next to
+leading order (NNLO)
 total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea}.
@@
 %
+While these various studies differ in their qualitative conclusions, it is clear
+that the ultimate precision in the determination of the Higgs trilinear
+will be provided by the combination of various final states.
+%
+
+The advantage of the $b\bar{b}b\bar{b}$ final state is the the signal yield
+is enhanced by the large branching fraction of Higgs bosons into bottom-anti-bottom
+pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
+%
+However, this channel needs to deal with an overwhelming QCD multi-jet background,
+which makes this measurement very challenging.
+%
+Previous studies of Higgs pair production in this
+channel~\cite{Wardrope:2014kya,deLima:2014dta}, considering
+only the $4b$ irreducible QCD background, estimate that with a luminosity of
+3000 fb$^{-1}$ a signal significance of $S/\sqrt{B}=$AAA can be obtained.
+%
+However, as show in this work, neglecting other QCD backgrounds such as $bbjj$ and
+$jjjj$, with some of these light jets mistagged as $b$-jets, cannot be neglected, making
+this measurement even more difficult.
+
+Despite these large backgrounds, by combining the contribution of different final state
+topologies, resolved, boosted and intermediate, with a careful optimization
+of the analysis strategy, we find that it is possible to obtain a reasonable
+good signal discrimination.
+%
+To further enhance the significance of the measurements, signal and background events
+are processed using a Multivariate Analysis (in particular a feed-forward neural
+network), that further enhance $S\sqrt{B}$ up to a value of AAA.
+%
+Therefore, we are able to rescue the potential of this final state in a realistic
+analysis setup.
+
+One of the original motivations of this study was to provide guidance to the experiments
+concerning which aspects of the measurement should be particularly optimized
+to increase the signal significance in this channel.
+%
+In this respect, the study the dependence on our results on the $b$-tagging mistag
+efficiency and the light and charm jet mistag rate, the jet energy and transverse
+momentum resolution, or the Higgs invariant mass resolution.
+%
+In each of these cases, we determine the significance  $S/sqrt{B}$ of the
+measurement in both conservative and optimistic assumptions of these
+parameters.
 

### 2015-06-01 paper/sec-intro.tex
more work on text

@@
 The structure of this paper is the following.
+%
+In Sect.~\ref{mcgeneration} we discuss the generation of the signal
+and background Monte Carlo samples.
+%
+Then in Sect.~\ref{sec:analysis}
+we describe our analysis strategy, and in particular
+the classification of each individual event into
+different categories according to the event topology.
+%
+The results for our traditional cut-based analysis
+are presented in Sect.~\ref{sec:results}, and in
+Sect.~\ref{sec:mva} we show how we can enhance signal
+significance by means of multivariate techniques.
+%
+Finally in Sect.~\ref{sec:conclusions} we conclude and outline
+possible future developements for Higgs pair production
+in the $b\bar{b}b\bar{b}$ final state.

### 2015-06-01 paper/sec-mva.tex
more work on text

--- 2015-02-13 doc/HH4b_Documentation.tex
@@
-%  sample eprint article in LaTeX           --- M. Peskin, 9/7/00
-\documentclass[12pt]{article}
-\usepackage{graphicx}
+\section{Multivariate analysis}
+\label{sec:mva}
 
-\usepackage{geometry}
-\geometry{margin=1.5in}
+After the traditional cut-based analysis presented in the previous section,
+and combining the significance of the different event categories,
+we end up with a $S/\sqrt{B}$ value of AAA.
+%
+Taking into account our more realistic simulation of the QCD background as
+compared to previous studies, this is not too bad.
+%
+However, the attentive reader might have noticed that we have used
+relatively 
+loose kinematics cuts, for example in the Higgs mass window.
+%
+The motivation for this is that the $n$-tuples of signal and background
+events, after our basic selection, are processed though a multivariate
+analysis with the motivation to increase the signal over background
+significance.
 
-%\usepackage{chngcntr}
-%\counterwithin{table}{section}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% basic data for the eprint:
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \textwidth=6.0in  \textheight=8.25in
-
-%%  Adjust these for your printer:
-% \leftmargin=-0.3in   \topmargin=-0.20in
-
-%% preprint number data:
-\newcommand\pubnumber{DRAFT-001}
-\newcommand\pubdate{\today}
-
-%%  address and funding acknowledgement data:
-\def\oxford{}
-\def\support{\footnote{}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%   document style macros
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\Title#1{\begin{center} {\Large #1 } \end{center}}
-\def\Author#1{\begin{center}{ \sc #1} \end{center}}
-\def\Address#1{\begin{center}{ \it #1} \end{center}}
-\def\andauth{\begin{center}{and} \end{center}}
-\def\submit#1{\begin{center}Submitted to {\sl #1} \end{center}}
-\newcommand\pubblock{\rightline{\begin{tabular}{l} \pubnumber\\
-         \pubdate  \end{tabular}}}
-\newenvironment{Abstract}{\begin{quotation}  }{\end{quotation}}
-\def\Acknowledgements{\bigskip  \bigskip \begin{center} \begin{large}
-             \bf ACKNOWLEDGEMENTS \end{large}\end{center}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%  personal abbreviations and macros
-%    the following package contains macros which can be used in this document:
-%\input econfmacros.tex
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{document}
-\begin{titlepage}
-\hspace{-1.4cm}\pubblock
-
-\vfill
-\Title{Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$}
-\vfill
-\Author{}
-\Address{}
-\vfill
-\begin{Abstract}
-This is a feasibility study for the final state $hh\rightarrow (b\bar{b})(b\bar{b})$ using reconstruction techniques for both resolved
-and boosted topologies as well as multivariate methods.
-\end{Abstract}
-\vfill
-\end{titlepage}
-\def\thefootnote{\fnsymbol{footnote}}
-\setcounter{footnote}{0}
-%
-
-\section{Introduction}
-
-\section{Samples}
-\label{sec:samples}
-\subsection{Background}
-All background samples are generated with the {\tt SHERPA} event generator, version 2.1.1. For the explicit runcards used in the generation, see Appendix~\ref{app:runcards}.
-
-The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples.
-At the generator level the following basic cuts are applied.
-Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
-All final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
-Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$.
-Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
-\hline
-\hline
-$pp \to HH$ &  MG5\_aMC@NLO & 100K & $1.729\times10^{-2}$ pb \\
-\hline
-$pp \to b\bar{b}b\bar{b}$ &  SHERPA 2.1.1 & 3M &$1.121 \times10^3$ pb \\
-$pp \to b\bar{b}jj$ &  SHERPA 2.1.1 & 3M & $2.659 \times 10^5$ pb \\
-$pp \to jjjj$ &  SHERPA 2.1.1 & 3M  & $9.709\times 10^6$ pb \\
-$pp \to t\bar{t}$ &  SHERPA 2.1.1 & 3M & $2.514\times 10^3$ pb \\
-\hline
-\end{tabular}
-\caption{Summary of generated samples to date. All {\tt SHERPA} samples have a MC error of $0.05\%$.} \label{tab:samples}
-\end{center}
-\end{table}%
-
-Although suffering from a large theory uncertainty, we can compare the result of our background samples against those presented in the MG5\_aMC@NLO paper~\cite{Alwall:2014hca}.
-Here for comparison we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV.
-All jets must be within an acceptance of $|\eta| \le 2.5 $.
-In the case of the samples with $b$ quarks in the final state, these requirements are extended to the appropriate number of $b$-jets.
-For example, in the 2$b$2$j$ sample there must be at least two $b$-jets that pass the cuts outlined above.
-
-In Table~\ref{tab:xsecs} this comparison is summarised for the $2b2j$ and $4b$ samples. Considering the large theory errors, agreement is reasonable in both instances.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|c|c|c|}
-\hline
-Process & $\sigma$ aMC@NLO & $\sigma$ Oxford (SHERPA) \\
-\hline\hline
-$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $4.123\times10^{-1}$ pb \\ 
-$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$4.239 \times 10^2$ pb \\ 
-$jjjj$ & -  & $4.450\times 10^4$ pb \\
-\hline
-\end{tabular}
-\caption{Comparison of LO Oxford SHERPA cross-sections with those of the aMC@NLO paper. The aMC@NLO cross-sections come with a quoted $~50\%$ theory uncertainty.} \label{tab:xsecs}
-\end{center}
-\end{table}%
-\section{Object and Event Selection}
-
-\subsection{Resolved Topology}
-
-The resolved selection requires the presence of at least four b-tagged anti-$k_T$ $R=0.4$ jets with $p_T >$25~GeV and $|\eta|>2.5$.
-\textit{Pre-cut} histograms are written out for various kinematic distributions for all events with at least four b-tagged jets but before applying
-further kinematic cuts. \textit{Post-cut} histograms contain only events where the four jets also pass the above kinematic cuts.
-
-The di-Higgs system is reconstructed by considering all possibilities of forming two pairs of jets with invariant masses $m_{j1j2}$ and 
-$m_{j3j4}$, respectively, and choosing the configuration that minimises their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
-are considered here.
-
-\subsubsection{Resolved $b$-jet tagging efficiencies} \label{sec:btagtest}
-In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$.
-In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_b\epsilon^2_l$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.
-
-In practice we have found with these simple efficiencies, that the actual selection efficiencies differ considerably from the naive factors of $\epsilon_b^{n_b}\epsilon_l^{n_l}$.
-In Table~\ref{tab:btageff1} the results of this simple $b$-tagging test are demonstrated.
-Shown in the table are the total cross-sections before and after the application of the described $b$-tagging procedure, the resulting percentage of the cross-section passing the b-tag, and the naive selection percentage that would result from applying powers of $\epsilon_{b/l}$ to the total cross-section.
-The pass rate for samples with four $b$ quarks in the final state is therefore considerably lower in practice than one would naively expect, and the pass rate for the $2b2j$ sample considerably higher.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-Process & $\sigma_{\mathrm{tot}}$ & After b-tag & \% selected & \% Naive selection \\
-\hline \hline
-$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.460\times 10^{-3}$ pb & \textbf{8.444\%} & 40.96\% \\
-\hline
-$b\bar{b}b\bar{b}$ & $9.298 \times10^2$ pb & $78.32$ pb & \textbf{8.423\%} & 40.96\%\\
-$b\bar{b}jj$ &  $2.208 \times 10^5$ pb & $84.80$ pb & \textbf{0.038\%} & 0.0064\% \\
-$jjjj$ & $9.709\times 10^6$ pb & $20.85$ pb & \textbf{2.147 $\times$ 10$^{-4}$\%} & $1.0\times 10^{-6}$\%\\
-\hline
-\textbf{S/B} & $1.74 \times 10^{-9}$ & $7.94 \times 10^{-6}$& \multicolumn{2}{c}{}\\
-\cline{1-3}
-\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $9.50 \times 10^{-3}$ & $1.86 \times 10^{-1}$& \multicolumn{2}{c}{}\\
-\cline{1-3}
-\end{tabular}
-\end{center}
-\caption{$b$-tagging analysis performed upon the samples described in Section~\ref{sec:samples}.
-Cross-sections are given for the samples before and after the application of the b-tagging procedure whereby the four hardest jets in the event are used, and the flat selection efficiency and mis-tag rates applied.
-The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison.
-Finally, the signal-to-background ratio and significance are given both before and after the b-tagging, for $\mathcal{L}=$ 3 ab$^{-1}$.} \label{tab:btageff1}.
-Note, older samples have been used here with different generator cuts.
-\end{table}%
-
-These differences are due to the choices made in the selection procedure.
-In practice the four hardest jets in the event often do not correspond directly to the four parton level final state particles.
-In Table~\ref{tab:nbjets} the number of true $b$-jets (that is, prior to the application of selection efficiencies and fake rates) present in the hardest four jets per event is shown.
-Indeed, for the samples with four $b$-quarks in the parton level final state, the most common scenario has only three $b$-jets in the hardest four jets, significantly affecting the selection efficiency.
-
- A more accurate estimation for the passing cross-section may be obtained by multiplying the various fractions of $b$-jets by the corresponding efficiencies, for example the 3 $b$-jet rate by $\epsilon_b^{3}\epsilon_l^{1}$.
-Summing the various scenarios we then have a better estimate for the percentage of cross-section passing the selection, shown in the final column of Table~\ref{tab:nbjets}.
-This agrees well with the observed rates shown in Table~\ref{tab:btageff1}.
-
-\begin{table}[htdp]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|c||c|}
-\hline
-Process & 0 $b$-jets & 1 $b$-jet & 2 $b$-jets & 3 $b$-jets & 4 $b$-jets & \% selected \\
-\hline\hline
-$H\bar{H}$ & 0.083\% & 2.599\% &  24.712\% &   52.651\% &  19.955\% & \textbf{8.445\%}\\
-\hline
-$b\bar{b}b\bar{b}$ & 0.858\% &  7.606\% &  27.523\% &  43.977\% &   20.036\% & \textbf{8.434\%} \\
-$b\bar{b}jj$ & 9.115\% &    41.792\% &    47.806\% &     1.216\% &  0.071\% & \textbf{0.038\%}\\
-$jjjj$ & 95.668\% &   3.789\% &  0.531\% & 0.011\%  & 3.00E-4\%& \textbf{2.17$\times 10^{-4}$\%}\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Breakdown of the number of true $b$-jets in the hardest four clustered jets for various samples.
-The final column shows the predicted pass rate for the $b$-tagging given the distribution of events in the preceding columns.}\label{tab:nbjets}
-\end{table}%
-
-\subsubsection{$b$-jet tagging efficiencies with UCL-style selection}
-In the UCL analysis their jet selection does not proceed as described in the previous section, presumably as requiring the four hardest jets in the event to be $b$-tagged cut too aggressively into the signal process.
-Rather, the selection proceeds by taking all anti-$k_T$ $R=0.5$ jets with $p_T > 40$ GeV and running the $b$-tagging algorithm on them.
-The four hardest successfully $b$-tagged jets are then selected for further analysis.
-With such a method implemented for our samples and with our previous selection efficiencies and fake rates, Table \ref{tab:UCLbtag} summarises the results.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & \% selected  \\
-\hline \hline
-$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & 7.467\% \\
-\hline
-$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & 5.472\% \\
-$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & 0.0224\% \\
-\hline
-\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& \multicolumn{1}{c}{}\\
-\cline{1-3}
-\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& \multicolumn{1}{c}{}\\
-\cline{1-3}
-\end{tabular}
-\end{center}
-\caption{Summary of the $b$-tagging procedure of the UCL analysis.
-Presented as in Table~\ref{tab:btageff1}.
-In this case the total cross-sections are presented after a cut requiring four anti-$k_T$ R=0.5 jets with $p_T>40$ GeV in the final state.
-The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.
-Note, older samples have been used here with different generator cuts.}\label{tab:UCLbtag}
-\end{table}%
-
-Once again, it is clear that more of the $bbjj$ sample is making it past the $b$-tagging selection than originally expected.
-It seems unlikely that this background can be neglected in the resolved analysis based upon a simple factor of $\epsilon_b^{2}\epsilon_l^{2}$ as used by the UCL group.
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=\textwidth]{plots/m4b_ucl_preCut.pdf}
-\caption{Contributions from the various samples to the observed four $b$ invariant mass system after applying the $b$-tagging procedure outlined in Section~\ref{sec:btagtest}.}
-\end{center}
-\end{figure}
-
-\subsubsection{$bb$-jet rejection for the four hardest jets}
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & After $bb$ rejection & \% selected  \\
-\hline \hline
-$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & & 7.467\% \\
-\hline
-$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & & 5.472\% \\
-$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & & 0.0224\% \\
-\hline
-\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& & \multicolumn{1}{c}{}\\
-\cline{1-3}
-\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& & \multicolumn{1}{c}{}\\
-\cline{1-3}
-\end{tabular}
-\end{center}
-\caption{Summary of the $b$-tagging and $bb$-rejection cuts on the four leading jets.}\label{tab:TestbbTag}
-\end{table}%
-
-\subsection{Boosted Topology}\label{sec:Boosted_FR}
-
-In the boosted topology, the decay products of each Higgs boson are merged into a single large-$R$ jet with a two-prong substructure. 
-These Higgs jets are reconstructed as anti-$k_T$ $R=1.0$ jets for which two substructure variables, the first $k_T$ splitting scale $d_{12}$
-and the 2-subjettiness ratio $\tau_{21}$, are calculated.
-\textit{Pre-cut} histograms are written out after requiring the presence of at least two large-$R$ in the event but without applying any further
-kinematic cuts. \textit{Post-cut} histograms are filled after the following additional cuts: 
-Both jets are required to have $p_T >$100~GeV and $|\eta|>2.5$. Moreover, each jet is required to have at least two b-tagged anti-$k_T$ $R=0.3$ 
-jets matched to it via \textit{ghost association}: 
-To this end, the constituents of a given large-$R$ jet is reclustered using the jet algorithm 
-and radius parameter of the original jet and so-called \textit{ghost jets}, each corresponding to a small-$R$ jet in the event, 
-are added to the input for the cluster sequence. The 4-vector of a ghost jet is obtained from a given small-$R$ jet 
-by setting its transverse momentum and mass to negligibly small values but retaining its direction in $\eta$ and $\phi$. A small-$R$ jet is 
-considered matched to the large-$R$ jet if its ghost is found among the constituents of the reclustered jet. Ghost association allows to unambiguously
-match small-$R$ to large-$R$ jets, even in dense environments where a simple matching based on the distance $\Delta R$ between jets 
-may lead to multiple matchings.
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/histo_mfj1_preCut.pdf}
-\includegraphics[width=0.49\textwidth]{plots/histo_mfj2_preCut.pdf}
-\caption{Mass distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
-\label{fig:mfj_boosted_pre}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj1_preCut.pdf}
-\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj2_preCut.pdf}
-\caption{$d_{12}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
-\label{fig:split12_fj_boosted_pre}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj1_preCut.pdf}
-\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj2_preCut.pdf}
-\caption{$\tau_{21}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets before the applying the boosted selection.}
-\label{fig:tau21_fj_boosted_pre}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/histo_mfj1.pdf}
-\includegraphics[width=0.49\textwidth]{plots/histo_mfj2.pdf}
-\caption{Mass distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
-\label{fig:mfj_boosted_post}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj1.pdf}
-\includegraphics[width=0.49\textwidth]{plots/histo_split12_fj2.pdf}
-\caption{$d_{12}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
-\label{fig:split12_fj_boosted_post}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj1.pdf}
-\includegraphics[width=0.49\textwidth]{plots/histo_tau21_fj2.pdf}
-\caption{$\tau_{21}$ distributions for the leading and subleading anti-$k_T$ $R=1.0$ jets after the applying the boosted selection.}
-\label{fig:tau21_fj_boosted_post}
-\end{center}
-\end{figure}
-
-\subsection{Boosted Topology with Variable-$R$ Jets}
-
-The same selection as in Subsection~\ref{sec:Boosted_FR} is applied but this time using Variable-$R$ jets with the following parameters:
-$\rho=500$~GeV, $R_{max}=$1.0, $R_{min}=$0.2.
-
-\section{Multivariate Tools}
-
-\clearpage
-\section{Results}
-\subsection{Example resolved analysis}
-In this section we present the results of a resolved style analysis upon the full set of available samples for the purposes of illustration.
-The cuts used in this example analysis are as so.
-\emph{b-tag} cuts those events which fail to tag four anti-$k_T$ $R=0.5$ $b$-jets with $b$ quark $p_T > 15$ GeV.
-Flat $b$-jet efficiencies and mistag rates of 80\% and 1\% respectively.
-A $c$ mistag rate of $17\%$ is also applied.
-\emph{jet $p_T$,$\eta$} requires that the four jets each have $p_T>40$ GeV and $|\eta|< 2.5$.
-\emph{di-jet $p_T$} requires that each dijet pair representing a higgs candidate has $p_T>150 $ GeV.
-\emph{di-jet $\Delta\eta$} requires that the two dijets are separated by no more than 1.5 units in $\eta$.
-Finally \emph{$m_H$ window} requires that the invariant mass of each dijet is within 15 GeV of $m_H$.
-The remaining cross-section after each of these cuts, along with $S/B$ and $S/\sqrt{B}$ are given in Table ~\ref{tab:resCutflow}.
-
-\begin{table}[htdp]
-\begin{center}
-\begin{tabular}{|c||c||c|c|c|c||c|c|}
-\hline
-Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
-\hline
-\hline
-b-tag    	& 1.516 &      102271         & 135255        & 42934  	&	202.9	&5.40E-6	& 0.157\\
-jet $p_T,\eta$         & 0.723 &        3847      & 10676       & 5045 	&	122.7	&3.67E-5	& 0.282\\
-di-jet $p_T$           	& 0.371&      553.7        & 1838	  & 926.0	&	22.45	&1.11E-4	& 0.352\\
-di-jet $\Delta\eta$   & 0.336&       324.8       & 991.4 	  & 312.6		&	16.39	&2.04E-4	& 0.454\\
-\hline
-$m_H$ window   &0.190 &          7.632      & 13.60	  & 0.502	&	2.675	&7.78E-3	& 2.106\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Table demonstrating the cutflow of an example resolved analysis applied to the full sample set.  $S/\sqrt{B}$ is given for HL-LHC luminosities.}
-\label{tab:resCutflow}
-\end{table}%
-
-\subsection{Example boosted analysis}
-Here we shall discuss an example boosted analysis.
-In this case \emph{Fatjet cuts} refers to the requirement of two $R=1$ anti-$k_T$ jets with $p_T>250$ GeV and $|\eta| < 2.5$.
-\emph{2 Subjets} requires two anti-$k_T$ $R=0.3$ subjects in each fat jet.
-\emph{b-Tagging} cuts those events in which the two hardest subjets are not successfully $b$-tagged.
-Here efficiency and mistag factors are applied for $b$ and $c$ jets as a function of subjet $p_T$.
-\emph{Mass-drop } requires that the two fat jets pass a BDRS mass-drop tagger with parameters $\mu = 0.67$ and $y_{\mathrm{cut}} = 0.09$.
-Finally \emph{$m_H$ window} only passes events where the two fat jet masses are within $15$ GeV of $m_H$.
-In Table~\ref{tab:boostedCutflow} we see the results of these cuts.
-\begin{table}[htdp]
-\begin{center}
-\begin{tabular}{|c||c||c|c|c|c||c|c|}
-\hline
-Cut 					& $HH$ [fb] & $4b$ [fb] & $2b2j$ [fb] & $4j$ [fb] & $t\bar{t}$ [fb] & $S/B$ & $S/\sqrt{B}$ \\
-\hline
-\hline
-Fatjet cuts 			&2.802           	&3045 	& 1.13E6 &	4.57E7    &       9808  & 5.98E-8 &0.022 \\
-2 Subjets  	&	2.740 	&2694	& 1.01E6	&	4.21E7 	&	9787  &6.35E-8 & 0.023\\
-b-Tagging    			& 0.070		&39.76	& 296.9		&	352.9            &      7.586 & 1.00E-5& 0.145\\
-Mass-drop  		& 0.068 		&36.84	& 256.0    	&	305.1            &	7.514 & 1.12E-4& 0.151 \\
-\hline
-$m_H$ window       		&   0.045		& 2.134	& 10.83	& 	0.630            & 	0.438 & 3.20E-3& 0.658\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Table demonstrating the cutflow of an example boosted analysis applied to the full sample set. $S/\sqrt{B}$ is given for HL-LHC luminosities.}
-\label{tab:boostedCutflow}
-\end{table}%
-
-\subsection{MVA}
 We now apply a basic MVA to the final output of the resolved and boosted analyses.
-The MVA used is a feedforward artificial neural network with $N_{\mathrm{par}}\times5\times3\times1$ architecture, where $N_{\mathrm{par}}$ is the number of input parameters for the network.
+The MVA used is a feed-forward artificial neural network with $N_{\mathrm{par}}\times5\times3\times1$ architecture, where $N_{\mathrm{par}}$ is the number of input parameters for the network.
 The MVA was trained for 50,000 GA generations with a cross-entropy error function.
@@
 Figure~\ref{fig:nnweights} demonstrates that the dijet invariant mass is a crucial variable for the resolved analysis MVA.
-As no detector effects were modelled in this analysis, it is reasonable to assume that the MVA has greater discriminating power than would be feasible in a real analysis.
+As no detector effects were modeled in this analysis, it is reasonable to assume that the MVA has greater discriminating power than would be feasible in a real analysis.
 To investigate this, we now consider a variant of the analysis used in Table~\ref{tab:resCutflow} where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/Msmear/histo_mass_smear_precut.pdf}
-\includegraphics[width=0.49\textwidth]{plots/Msmear/nnweights.pdf}
-\caption{The left figure demonstrates the gaussian smearing applied to the dijet invariant mass distribution. The right figure demonstrates the ANN weight distribution in the MVA.}
-\label{fig:invMsmear}
-\end{center}
-\end{figure}
-
 While the MVA still derives most of it's discriminating power from the dijet masses, the smearing reduces it's effectiveness considerably.
@@
 This is echoed in the resulting significance of the analysis as demonstrated in Figure~\ref{fig:smearedSB}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.89\textwidth]{plots/Msmear/roc.pdf}
-\caption{ROC curves of the MVA applied with the unsmeared (blue) and smeared (green) dijet invariant mass distributions.}
-\label{fig:smearedROC}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/Msmear/sb.pdf}
-\includegraphics[width=0.49\textwidth]{plots/Msmear/ssb.pdf}
-\caption{$S/B$ and $S\sqrt{B}$ (HL\-LHC) for the MVA applied to the unsmeared (blue) and smeared (green) dijet invariant mass distributions.}
-\label{fig:smearedSB}
-\end{center}
-\end{figure}
-\clearpage
-
-\section{Conclusion}
-
-% \Acknowledgements
-
-\begin{thebibliography}{1}
-
-%\cite{Alwall:2014hca}
-\bibitem{Alwall:2014hca}
-  J.~Alwall, R.~Frederix, S.~Frixione, V.~Hirschi, F.~Maltoni, O.~Mattelaer, H.-S.~Shao and T.~Stelzer {\it et al.},
-  %``The automated computation of tree-level and next-to-leading order differential cross sections, and their matching to parton shower simulations,''
-  JHEP {\bf 1407} (2014) 079
-  [arXiv:1405.0301 [hep-ph]].
-  %%CITATION = ARXIV:1405.0301;%%
-  %168 citations counted in INSPIRE as of 19 Jan 2015
-
-%\cite{Wardrope:2014kya}
-\bibitem{Wardrope:2014kya}
-  D.~Wardrope, E.~Jansen, N.~Konstantinidis, B.~Cooper, R.~Falla and N.~Norjoharuddeen,
-  ``Non-resonant Higgs pair production in the $b\overline{b}b\overline{b}$ final state at the LHC,''
-  arXiv:1410.2794 [hep-ph].
-  %%CITATION = ARXIV:1410.2794;%%
-
-  \end{thebibliography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\clearpage
-\appendix
-\section{Event sample runcards}
-\label{app:runcards}
-\subsection {Background: QCD 4b}
-\begin{verbatim}
-(run){
-  EVENTS 3M;
-  EVENT_GENERATION_MODE U;
-  ME_SIGNAL_GENERATOR Comix;
-
-  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_4b];
-
-  BEAM_1 2212; BEAM_ENERGY_1 7000;
-  BEAM_2 2212; BEAM_ENERGY_2 7000;
-
-  FRAGMENTATION=Off # disable hadronisation
-  MI_HANDLER=None # disable multiple parton interactions
-
-  SCF:=1; ### default scale factor
-  SCALES VAR{SCF*H_T2/4};
-
-  PDF_LIBRARY LHAPDFSherpa;
-  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
-  PDF_SET_VERSION 0;
-
-  MASSIVE[5] 1;
-  MASS[5] 4.75;
-
-}(run);
-(processes){
-  Process 93 93 -> 5 -5 5 -5;
-  Order_EW 0;
-  End process;
-
-}(processes);
-(selector){
-  PT 5 20 7000
-  PT -5 20 7000
-  PseudoRapidity 5 -3.0 3.0
-  PseudoRapidity -5 -3.0 3.0
-
-  DeltaR 5 5 0.1 10000
-  DeltaR 5 -5 0.1 10000
-  DeltaR -5 -5 0.1 10000
-
-}(selector);
-\end{verbatim}
-
-\subsection {Background: QCD 2b2j}
-\begin{verbatim}
-(run){
-  EVENTS 3M;
-  EVENT_GENERATION_MODE U;
-  ME_SIGNAL_GENERATOR Comix;
-
-  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_2b2j];
-
-  BEAM_1 2212; BEAM_ENERGY_1 7000;
-  BEAM_2 2212; BEAM_ENERGY_2 7000;
-
-  FRAGMENTATION=Off # disable hadronisation
-  MI_HANDLER=None # disable multiple parton interactions
-
-  SCF:=1; ### default scale factor
-  SCALES VAR{SCF*H_T2/4};
-
-  PDF_LIBRARY LHAPDFSherpa;
-  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
-  PDF_SET_VERSION 0;
-
-  MASSIVE[5] 1;
-  MASS[5] 4.75;
-
-}(run);
-(processes){
-  Process 93 93 -> 93 93 5 -5;
-  Order_EW 0;
-  End process;
-
-}(processes);
-(selector){
-  PT 5 20 7000
-  PT -5 20 7000
-  PseudoRapidity 5 -3 3
-  PseudoRapidity -5 -3 3
-
-  PT 93 20 7000
-  PseudoRapidity 93 -3 3
-
-  DeltaR 93 93 0.1 10000
-  DeltaR 5 93 0.1 10000
-  DeltaR -5 93 0.1 10000
-  DeltaR 5 5 0.1 10000
-  DeltaR -5 5 0.1 10000
-  DeltaR -5 -5 0.1 10000
-}(selector);
-\end{verbatim}
-
-\subsection {Background: QCD 4j}
-\begin{verbatim}
-(run){
-  EVENTS 3M;
-  EVENT_GENERATION_MODE U;
-  ME_SIGNAL_GENERATOR Comix;
-
-  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_4j];
-
-  BEAM_1 2212; BEAM_ENERGY_1 7000;
-  BEAM_2 2212; BEAM_ENERGY_2 7000;
-
-  FRAGMENTATION=Off # disable hadronisation
-  MI_HANDLER=None # disable multiple parton interactions
-
-  SCF:=1; ### default scale factor
-  SCALES VAR{SCF*H_T2/4};
-
-  PDF_LIBRARY LHAPDFSherpa;
-  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
-  PDF_SET_VERSION 0;
-
-  MASSIVE[5] 1;
-  MASS[5] 4.75;
-
-}(run);
-
-(processes){
-  Process 93 93 -> 93 93 93 93;
-  Order_EW 0;
-  End process;
-}(processes);
-
-(selector){
-  PT 93 20 7000
-  PseudoRapidity 93 -3 3
-  DeltaR 93 93 0.1 10000
-}(selector);
-\end{verbatim}
-
-\subsection {Background: QCD ttbar}
-\begin{verbatim}
-(run){
-  EVENTS 3M;
-  EVENT_GENERATION_MODE U;
-  ME_SIGNAL_GENERATOR Comix;
-
-  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_ttbar];
-
-  BEAM_1 2212; BEAM_ENERGY_1 7000;
-  BEAM_2 2212; BEAM_ENERGY_2 7000;
-
-  FRAGMENTATION=Off # disable hadronisation
-  MI_HANDLER=None # disable multiple parton interactions
-
-  SCF:=1; ### default scale factor
-  SCALES VAR{SCF*H_T2/4};
-
-  PDF_LIBRARY LHAPDFSherpa;
-  PDF_SET NNPDF30_lo_as_0118_nf_4.LHgrid;
-  PDF_SET_VERSION 0;
-
-  MASSIVE[5] 1;
-  MASS[5] 4.75;
-
-  # Stable mode 0 specified that both particle and antiparticle are unstable
-  STABLE[6] = 0;
-  STABLE[24] = 0;
-
-  # Enable only fully hadronic decay modes
-  HARD_DECAYS=1;   
-  HDH_NO_DECAY={24,12,-11}|{24,14,-13}|{24,16,-15}|{-24,-12,11}|{-24,-14,13}|{-24,-16,15};
-
-}(run);
-
-(processes){
-  Process 93 93 -> 6 -6;
-  Order_EW 0;
-  End process;
-}(processes);
-
-(selector){
-  PT 6 20 7000
-  PT -6 20 7000
-  PseudoRapidity 6 -3 3
-  PseudoRapidity -6 -3 3
-  DeltaR 6 -6 0.1 10000
-}(selector);
-\end{verbatim}
-
-\clearpage
-\section{Decay tables for $t\bar{t}$}
-
-\begin{verbatim}
-Decay table for : W+.
-Total width:                  2.10561 GeV
-Flavour width:                2.06 GeV
-----------------------------------------
-{24,2,-1}         W+ --> u db              0.702203   GeV, BR= 33.3492 %
-{24,4,-3}         W+ --> c sb              0.701546   GeV, BR= 33.318 %
-{24,12,-11}       W+ --> nu_e e+           0.234068   GeV, BR= 11.1164 %
-{24,14,-13}       W+ --> nu_mu mu+         0.234066   GeV, BR= 11.1163 %
-{24,16,-15}       W+ --> nu_tau tau+       0.233725   GeV, BR= 11.1001 %
-----------------------------------------
-
-Decay table for : W-.
-Total width:                  2.10561 GeV
-Flavour width:                2.06 GeV
-----------------------------------------
-{-24,-2,1}        W- --> ub d              0.702203   GeV, BR= 33.3492 %
-{-24,-4,3}        W- --> cb s              0.701546   GeV, BR= 33.318 %
-{-24,-12,11}      W- --> nu_eb e-          0.234068   GeV, BR= 11.1164 %
-{-24,-14,13}      W- --> nu_mub mu-        0.234066   GeV, BR= 11.1163 %
-{-24,-16,15}      W- --> nu_taub tau-      0.233725   GeV, BR= 11.1001 %
-----------------------------------------
-
-Decay table for : t.
-Total width:                  1.59689 GeV
-Flavour width:                1.5 GeV
-----------------------------------------
-{6,24,5}          t --> W+ b               1.59689    GeV, BR= 100   %
-----------------------------------------
-
-Decay table for : tb.
-Total width:                  1.59689 GeV
-Flavour width:                1.5 GeV
-----------------------------------------
-{-6,-24,-5}       tb --> W- bb             1.59689    GeV, BR= 100   %
-
-\end{verbatim}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}

### 2015-06-04 paper/sec-mva.tex
work on MVA section

@@
 significance.
+%
+Multivariate techniques are by now a common tool to enhance signal
+significance in HEP analysis.
 
-We now apply a basic MVA to the final output of the resolved and boosted analyses.
-The MVA used is a feed-forward artificial neural network with $N_{\mathrm{par}}\times5\times3\times1$ architecture, where $N_{\mathrm{par}}$ is the number of input parameters for the network.
-The MVA was trained for 50,000 GA generations with a cross-entropy error function.
+\subsection{MVA strategy}
+
+The final step of our analysis is to process our three exclusive
+categories of events (boosted, intermediate and resolved) though
+a Multivariate Analysis.
+%
+The particular tool that we adopt is
+a feed-forward artificial neural network.\footnote{This is the
+  same type of neural networks as those used in the
+  NNPDF analysis of parton distributions~\cite{Ball:2010de}.}
+%
+The architecture of the neural network is
+\be
+N_{\mathrm{var}}\times5\times3\times1 \, ,
+\ee
+with $N_{\mathrm{par}}$ the number of input variables for the MVA.
+%
+Therefore, we have two hidden layers and a single output variable, which
+is the value of the discriminant to separate signal and background.\footnote{Note that in the MVA literature artificial neural networks with several hidden
+  layers are known as {\it deep neural networks}.}
+%
+Below we list the variables that are given as input to the MVA in each
+different category.
+%
+The MVA has trained using a Genetic Algorithm during 50K iterations,
+and the figure of merit to be minimized is the cross-entropy function.
+%
+This figure of merit is defined as
+\be
+\bf DEF
+\ee
+
+For both signal and background events, the variables that we input
+to the MVA are the following.
+%
+For the boosted category we have
+\begin{itemize}
+\item The invariant mass of the two mass-drop-tagged jets, $m_{\rm jet}$
+\item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$
+\item The rapidity of the two mass-drop-tagged jets, $y_{\rm jet}$
+\item The invariant mass of the leading Higgs candidate, $m_{h,1}$
+\item The invariant mass of the sub-leading Higgs candidate, $m_{h,2}$
+\item The splitting scale of the first Higgs
+\item The splitting scale of the second Higgs
+\item The subjetiness variable $\tau_{21,h1}$ of the leading Higgs candidate
+\item The subjetiness variable $\tau_{21,h2}$
+  of the sub-leading Higgs candidate
+ \item The angular separation between the two tagged jets, $\Delta R_{1,2}$ 
+\end{itemize}
+For completeness, we give here the definition of the various substructure variables.
+%
+The splitting scale is defined as
+\be
+\bf DEF
+\ee
+while the $\tau_{1,2}$ subjetiness variable is defined as
+\be
+\bf DEF
+\ee
+The other variables are more conventional.
+
+For the resolved analysis instead, the $N_{\rm var}$ kinematic variables
+that are given as input to the MVA are the following
+\begin{itemize}
+
+  \end{itemize}
+
+\subsection{Enhancing signal discrimination with the MVA}
+
 In Figure~\ref{fig:nnresponse} the neural network classification of events is demonstrated for both the resolved and boosted cases.

### 2015-06-04 paper/sec-mva.tex
more work in MVA section

@@
 \be
+\label{eq:nn1}
 N_{\mathrm{var}}\times5\times3\times1 \, ,
@@
 The other variables are more conventional.
+%
+As will be shown below, the addition of the jet substructure variables,
+the splitting scales and the subjetiness,
+enhances substantially the signal significance, as compared
+to using only jet variables without substructure information.
 
@@
 \begin{itemize}
-
+\item The invariant mass of the four $b$-tagged leading jets (that
+  is, of the di-Higgs system), $m_{4b}$
+\item The transverse momentum of the di-Higgs system, $p_{4b}$
+\item The rapidity of the di-Higgs system $y_{4b}$
+\item The invariant mass of the leading Higgs candidate $m_{h,1}$
+\item The invariant mass of the subleading Higgs candidate $m_{h,1}$
+\item The angular separation between each of the four
+  $b$-tagged leading jets in the event: $\Delta R_{b1,b2}$,
+  $\Delta R_{b1,b3}$, $\Delta R_{b1,b4}$, $\Delta R_{b2,b3}$,
+  $\Delta R_{b2,b4}$, $\Delta R_{b3,b4}$
 \end{itemize}
+As will be shown below, of all these variables, the invariant mass of the
+Higgs candidates is the one that carries as higher discrimination
+power.
 
@@
 
-In Figure~\ref{fig:nnresponse} the neural network classification of events is demonstrated for both the resolved and boosted cases.
+Now we show the results of the MVA training on the signal and
+background samples.
+%
+First of all in Fig.~\ref{fig:nnresponse} we show
+the neural network classification of events is demonstrated for both the resolved and boosted cases.
+%
+In this figure, we show which is the distribution of the neural network
+response, that is, the value of the outer layer in Eq.~(\ref{eq:nn1}),
+for signal and background events.
+%
+For the MVA discrimination to be successful, one needs to find
+distinct distributions for the two types of events.
+%
+As can be seen from  Fig.~\ref{fig:nnresponse}, both
+in the boosted and in the resolved cases signal and background
+distributions are noticeably different: we can use this property
+to introduce the final cut in our analysis, a cut in the value
+of the neural network output.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/resolved_MVA_hist.pdf}
+\includegraphics[width=0.48\textwidth]{plots/boosted_MVA_hist.pdf}
+\caption{\small Neural network response demonstrated for the case of the resolved (left) and boosted (right) analyses.
+The frequency of background and signal events is plotted as a function of neural network output.
+{\bf what is the y axis??}
+}
+\label{fig:nnresponse}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+The result of the signal selection efficiency as a function of the
+background rejection rate as the value on the cut on the NN output
+is varied is known as the Receiver Operating Characteristic (ROC)
+curve.
+%
+It is clear that we can achieve a very high signal efficiency but using
+a low value of the threshold, but this will have a poor background
+rejection.
+%
+Using a higher value of the cut will increase background rejection at the
+cost of dropping signal efficiency.
+%
+The usefulness of ROC curves is that they allow to determine the
+optimal cut value that removes enough background without degrading too much the signal efficiency.
+
 In Figure~\ref{fig:exampleroc} the ROC curves for the two analyses are shown, demonstrating that the neural network is able to
@@
 
-\begin{figure}[h]
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=0.49\textwidth]{plots/resolved_MVA_hist.pdf}
-\includegraphics[width=0.49\textwidth]{plots/boosted_MVA_hist.pdf}
-\caption{Neural network response demonstrated for the case of the resolved (left) and boosted (right) analyses.
-The frequency of background and signal events is plotted as a function of neural network output.}
-\label{fig:nnresponse}
-\end{center}
-\end{figure}
-
-\begin{figure}[h]
-\begin{center}
-\includegraphics[width=0.95\textwidth]{plots/example_roc.pdf}
-\caption{ROC curve for the neural network discriminant in the boosted (green) and resolved (blue) cases.}
+\includegraphics[width=0.65\textwidth]{plots/example_roc.pdf}
+\caption{\small ROC curve for the neural network discriminant in the boosted (green) and resolved (blue) cases.}
 \label{fig:exampleroc}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-06-04 paper/sec-mva.tex
more work on mva sec

@@
 
-In Figure~\ref{fig:exampleroc} the ROC curves for the two analyses are shown, demonstrating that the neural network is able to
-perform well in both cases. Figure~\ref{fig:nnweights} shows the distribution of NN weights in both cases.
+In Fig.~\ref{fig:exampleroc} the ROC curves for the
+boosted, intermediate and resolved categories are found.
+%
+As could already be inferred from the distribution of neural
+networks output in Fig.~\ref{fig:nnresponse}, we find
+that the neural network MVA is reasonably efficient
+in discriminating signal over background.
+%
+The performance is slightly better in the case of the boosted
+topology, in particular thanks to the information provided
+by the substructure variables.
+%
+In both cases we see that with a moderate reduction of signal
+efficiency of $\sim 0.8$, one can reduce the background by 80\%,
+which translates into an improvement factor of the pre-MVA $S/\sqrt{B}$
+of almost $\sim 1.8$.
 
@@
 
-\begin{figure}[h]
+In order to gain physical insight of which are the variables that
+contribute the most to the MVA discrimination it is useful
+to show the distribution of NN weights for each of the
+input variables.
+%
+This distributions is a measure of the correlation between
+each input variable and the Neural Network output: the higher
+the value, the stronger the impact of this variable in
+separating signal from the background.
+%
+In Fig.~\ref{fig:nnweights} we show
+the distribution of NN weights for the resolved and boosted categories.
+
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=1\textwidth]{plots/nnweights_res.pdf}
-\includegraphics[width=1\textwidth]{plots/nnweights_boost.pdf}
-\caption{Distribution of weights per input variable in the final ANN analysis.
+\includegraphics[width=0.48\textwidth]{plots/nnweights_res.pdf}
+\includegraphics[width=0.48\textwidth]{plots/nnweights_boost.pdf}
+\caption{\small Distribution of weights per input variable in the final ANN analysis.
 The above figure shows the weight distribution in the case of the resolved analysis, while the lower plot shows the boosted analysis.}

### 2015-06-04 paper/sec-mva.tex
more work in MVA section

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
@@
 \end{figure}
-\clearpage
+%%%%%%%%%%%%%%%%%%%%%%%
 
-Figure~\ref{fig:nnweights} demonstrates that the dijet invariant mass is a crucial variable for the resolved analysis MVA.
-As no detector effects were modeled in this analysis, it is reasonable to assume that the MVA has greater discriminating power than would be feasible in a real analysis.
-To investigate this, we now consider a variant of the analysis used in Table~\ref{tab:resCutflow} where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
-Firstly the same analysis is repeated with the larger $m_H$ window.
+The results of Fig.~\ref{fig:nnweights} clearly illustrate which variables
+are more discriminative between the signal and the background.
+%
+For instance, in the case of the resolved analysis, the variables that show
+a higher discrimination power is the invariant mass of the Higgs candidate dijets.
+%
+Note that as explained in Sect.~\ref{sec:analysis}, we have applied a realistic
+smearing of the four-momentum of all reconstructed jets, but still is clear that the
+distribution of invariant mass of the Higgs candidates will be very different
+in the signal and in the backgrounds.
+%
+We discussed below the impact of smearing has.
+%
+Other variables do not seem to have a dramatic effect, although of course one of the
+advantages of the MVA technique is that it does not hurt to add redundant
+information.
+%
+In particular the angular distances between the four leading $b$-jets does not
+provide additional information.
+
+The corresponding analysis for the boosted category is also
+shown in Fig.~\ref{fig:nnweights}.
+%
+Here we see that there is a more even distributions of weights, in that many
+variables help in a similar amount in the discrimination.
+%
+The invariant mass of the Higgs candidate of course still carries a lot of weight,
+but now we see that the substructure variables really carry  a lot of information,
+in particular the splitting scales and the subjetiness $\tau_{12}$.
+%
+We have verified that signal significance in the boosted category is substantially
+degraded if substructure variables are not used.
+
+\subsection{Impact of smearing in the MVA discrimination}
+
+Accounting for a suitable smearing of the final-state momenta of the reconstructed
+jets is essential to be able to draw any realistic conclusions in analysis like
+this one that are based on a large number of jets.
+%
+It is therefore interesting how the MVA discrimination changes if one did not account
+for smearing - of course in this case differences between signal and background distributions
+would be enhanced.
+
+To investigate this, we now consider a variant of the analysis used in
+Table~\ref{tab:resCutflow} where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
+%
+Firstly the same analysis is repeated with the larger $m_H$ window, with no smearing at all.
+%
 This is then compared to the same analysis but with a Gaussian smearing with $\sigma=10$ GeV applied to the dijet invariant mass used in the MVA.
-In the left panel of Figure~\ref{fig:invMsmear} the smearing is demonstrated.
-Despite the smearing, the MVA applied to this analysis still vastly prefers the dijet masses as discriminators, as is demonstrated in the right panel of Figure~\ref{fig:invMsmear}.
+%
+In the left panel of Fig.~\ref{fig:invMsmear} the smearing is demonstrated.
+%
+Both with and without smearing, the  invariant mass distribution of the
+Higgs candidates is still the most discriminative variable.
+%
+This can be seen by comparing with   with the corresponding distribution with smearing in
+  Fig.~\ref{fig:nnweights}.
+
+%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/Msmear/histo_mass_smear_precut.pdf}
+\includegraphics[width=0.49\textwidth]{plots/Msmear/nnweights.pdf}
+\caption{\small Left plot: the invariant mass distribution of the
+  Higgs candidates without (red) and with (blue) smearing.
+  %
+  Right plot: the strength of the NN weights in the resolved case when no smearing
+  is applied.
+  %
+  It should be compared with the corresponding distribution with smearing in
+  Fig.~\ref{fig:nnweights}.
+  %
+  As expected, the discrimination power of the invariant mass distribution is
+  enhanced if there is no smearing.}
+\label{fig:invMsmear}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%
 
 While the MVA still derives most of it's discriminating power from the dijet masses, the smearing reduces it's effectiveness considerably.
-In Figure \ref{fig:smearedROC} the ROC curves of the MVA applied to the smeared and unsmeared distributions are shown, where it is clear that the overall performance of the MVA is significantly hampered by the smeared invariant masses.
-This is echoed in the resulting significance of the analysis as demonstrated in Figure~\ref{fig:smearedSB}
+%
+In Fig.~\ref{fig:smearedROC} the ROC curves of the MVA applied to the smeared and unsmeared distributions are shown, where it is clear that the overall performance of the MVA is significantly hampered by the smeared invariant masses.
+%
+For example, if we require the same signal efficiency as before, 0.8, the background rejection
+is degraded from 80\% down to 60\%.
+%
+Therefore, we can conclude that it is important to include smearing to draw realistic
+conclusions, though the qualitative information of which are the most relevant
+discriminative variables is not changed by this conclusion.
+
+%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.50\textwidth]{plots/Msmear/roc.pdf}
+\caption{\small ROC curves of the MVA applied with the unsmeared (blue) and smeared (green) dijet invariant mass distributions.}
+\label{fig:smearedROC}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%

### 2015-07-01 paper/HH4b.tex
work on MVA section
Work on the paper

--- 2015-04-24 paper/HH4b.tex
@@
 
-\emailAdd{juan.rojo@physics.ox.ac.uk}
+\emailAdd{cigdem.issever@physics.ox.ac.uk}
 
-\preprint{OUTP-15-aaa}
+\preprint{OUTP-15-14P}
 
 \abstract{
-A nice abstract
+  The measurement of Higgs pair production is one of the cornerstones of
+  the LHC program for the next years.
+  %
+  Double Higgs production provides a unique window to the electroweak
+  symmetry breaking mechanism, in particular to the Higgs trilinear coupling.
+  %
+  In this work we study the feasibility of the observation of the production of
+  Higgs boson pairs at the High-Luminosity LHC using the
+  $bb\bar{b}\bar{b}$ final state.
+  %
+  While the signal in this channel
+  is enhanced by the large branching fraction of Higgs bosons to
+  $b\bar{b}$ pairs, this measurement is  challenging due to the
+  overwhelming QCD multijet background.
+  %
+  Our analysis is based on the combination of traditional cut-based
+  methods and modern multivariate techniques, which lead to a substantial
+  enhacement of the signal significance.
+  %
+  By combining the contribution from the boosted, intermediate and resolved
+  topologies we achieve $S/\sqrt{B}=3.8$.
+  %
+  Therefore, we demonstrate that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
+  should allow to claim evidence of the observation of double Higgs production.
 }
@@
 
-% Introduction
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{sec-intro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{sec-mcsamples}
+\input{sec-analysis}
+\input{sec-results}
+\input{sec-mva}
+\input{sec-conclusions}
 
-% Monte Carlo samples
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{sec-mcsamples}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% analysis strategy
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{sec-analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Main results
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{sec-results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% MVA
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{sec-mva}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Conclusions and outlook
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\input{sec-conclusions}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+\section{sec-appendix-overlap}
 

### 2015-07-01 paper/sec-analysis.tex
Work on the paper

--- 2015-04-24 paper/sec-analysis.tex
@@
 \label{sec:analysis}
+
+In section we describe our analysis strategy, and in particular
+the classification of each individual event into
+different categories according to the event topology.
+
+{\bf needs flow chart}
+
+First of all we discuss the settings and nomenclature that
+we will use for jet clustering in this work.
+%
+Then we move to discuss how $b$-tagging is simulated,
+following closely the ATLAS techniques.
+%
+Then we discuss the categorisation of events between different
+topologies, and how we can prioritise among them.
+
+\subsection{Jet reconstruction}
+
+In our analysis we will use different types of jet definitions,
+depending of the type of analysis that needs to be performed.
+%
+Therefore, we being by enumerating the choices that we make.
+%
+The starting point after the parton shower is the clustering
+of all final state particles.
+%
+In this work all the jet reconstruction algorithms
+are obtained from the {\tt FastJet} program~\cite{Cacciari:2011ma},
+v3.1.0.
+%
+We adopt the following terminology for the different types of jets
+that we will use in this work:
+
+\begin{itemize}
+\item {\it Small-$R$ jets}.
+
+  These are jets  reconstructed with the
+  anti-$k_T$ clustering algorithm~\cite{Cacciari:2008gp} with $R=0.4$ radius.
+  %
+  When reconstructing small-$R$ jets, we will keep only
+  those with transverse momentum $p_T \ge 40$~GeV
+  and pseudo-rapidity $|\eta|<2.5$ within the central
+  acceptance of ATLAS and CMS, jets that fail to satisfy these
+  conditions are discarded
+
+  They are required to have $p_T > 50$~GeV and $|\eta|<2.5$.
+
+\item {\it Large-$R$ jets}.
+
+  These jets are also constructed with the
+  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
+  %
+  In order to be accepted, these large-$R$ jets should
+  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range by
+  $|\eta|<2.0$.
+  %
+  If these conditions are not satisfied, the jet is discarded.
+  %
+  The more restrictive range  in pseudo-rapidity
+  as compared to the small-$R$ jets,
+  is motivated by mimicking the  experimental requirements
+  in ATLAS and CMS
+  related to the track-jet-based calibration.
+
+  In addition to the basic $p_T$ and $\eta$
+  selection requirements, large-$R$ jets should also
+  satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
+  conditions, in order
+  to enhance the discrimination of the signal over the background
+  events.
+  %
+  For the BDRS mass-drop tagger, we use the {\tt FastJet} default
+  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
+
+\item {\it Small-$R$ subjets}.
+
+  Once we have reconstructed a suitable large-$R$ jet, important
+  information can be obtained by looking at the kinematics of
+  the small-$R$ subjets.
+  %
+  These subjets will be obtained by reclustering the constituents
+  of the large-$R$ jet, always with the  anti-$k_T$ algorithm,
+  but this time with a smaller radius parameter $R=0.3$.
+  %
+  As we will discuss below, these small-$R$ subjets are the key of
+  the $b$-tagging in the boosted category.
+%
+  \end{itemize}
+
+\subsection{$b$-tagging}
+
+Given the final state that needs to be reconstructed, the
+optimisation of the $b$-tagging capabilities of the
+LHC experiments is an essential requirement.
+%
+The $b$-tagging used in this feasibility study is inspired
+in the current and projected ATLAS settings, and below
+we also comment on the differences and similarities with the
+corresponding CMS strategy.
+%
+For each type of jet defined above, a different
+$b$-tagging strategy is used, as we discuss now.
+
+\begin{itemize}
+
+\item {\it Small-$R$ jets}.
+
+  These are $b$-tagged as follows.
+  %
+  If a small-$R$ jet has at least one $b$-quark among their constituents,
+  it will be tagged as a $b$-jet with probability $f_b$.
+  %
+  If no $b$-quarks are found among the constituents
+  of this jet, it can be still be tagged as a $b$-jet with
+  a mistag rate of $f_l$.
+  %
+  Note that the probability of tagging a jet is not increased
+  if more than one $b$-quark is found among the jet constituents.
+
+  \item {\it Large-$R$ jets}.
+
+    Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$
+    subjets (defined as above) to the original large-$R$ jets.
+    %
+    In particular,
+    a large-$R$ jet is considered  double-$b$-tagged if both
+    the leading and subleading subjets (where the ordering
+    is done in the subjet $p_T$) are both individually $b$-tagged.
+    %
+    Note that we only attempt to $b$-tag the two leading subjets:
+    trying to $b$-tag all subjets above the $p_T$ cut degrades
+    the signal significance due to the increase in combinatorics.
+
+    Therefore, in this work we will exploit the capabilities of
+    the LHC experiment of double-$b$-tagging inside large-$R$ jets.
+    %
+    Below we comment on the dependence of our results if single-$b$-tagging
+    would be performed also for the large-$R$ jets, as done
+    for the small-$R$ jets.
+
+    Concerning the $b$-tagging probabilities and the
+    light jet mistag probabilities, there are taken
+    the same as for small-$R$ jets.
+    %
+    Therefore, a large-$R$ jet where the two leading
+    subjets have at least one $b$-quark will be tagged
+    with probability $f_b^2$, if only one of the two leading
+    subjets has a $b$-quark then the tagging probability is
+    $2f_bf_l$, and if none of the two have $b$-quarks
+    as constituents, the mistag rate will be
+    $f_l^2$.
+
+\end{itemize}
+
+Concerning the actual values of the $b$-tag probability $f_b$ and
+the $b$-mistag probability of light jets $f_l$, in this work
+we adopt as baseline the values $f_b=0.8$ and $f_l=0.01$.
+%
+In Sect.~\ref{sec:optimisation} we study the dependence of
+our results against variations of $f_b$ and $f_l$ both
+using more conservative and more aggressive values.
+%
+There we also study the dependence of the results
+on other analysis settings related to the performance of
+the experiments, for example by varying the momentum smearing.
+
+\subsection{Event categorisation and cut flow}
+
+In Table~\ref{sec:categorisation} we summarize the definitions of each
+category
+
+The di-Higgs system is reconstructed by considering all possibilities of forming two pairs of jets with invariant masses $m_{j1j2}$ and 
+$m_{j3j4}$, respectively, and choosing the configuration that minimizes their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
+are considered here.
+
+The boosted selection requires the presence of at least two $bb$-tagged, selected anti-$k_T$ $R=1.0$ jets which are taken as the two Higgs boson candidates.
+
+The intermediate topology requires the presence of at least one $bb$-tagged, selected anti-$k_T$ $R = 1.0$ jet.
+If there is more than one, the leading one is taken as the first Higgs boson candidate.
+In addition, there must be at least two anti-$k_T$ $R=0.4$ jets with a separation $\Delta R > 1.0$ with respect to the large-$R$ jet
+that is selected as a Higgs boson candidate. The second Higgs boson candidate is reconstructed from the two small-$R$ jets that minimize the difference $|m_{fj} - m_{j1j2}|$.
+
+The resolved selection requires the presence of at least four $b$-tagged, selected anti-$k_T$ $R=0.4$ jets.
+
+All Higgs candidates are required to meet the following Higgs mass window cut: $|m_{H} - 125| < 40$~GeV
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h]
+  \centering
+  \small
+  \begin{tabular}{c|c|c|c}
+    \hline
+    &  Boosted  &  Intermediate  &  Resolved  \\
+    \hline
+    \hline 
+    Jets  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
+    jets  &  $\ge$ 4 small-$R$ jets \\
+    Cuts on jets  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
+    &  $p_T \ge 40$ GeV \\
+    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
+    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
+    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
+    \hline
+    \end{tabular}
+  \caption{\small Definition of the three event categories used in this
+    work, together with the corresponding basic kinematical cuts.
+\label{sec:categorisation}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-01 paper/sec-mcsamples.tex
more work on text
Work on the paper

--- 2015-04-24 paper/sec-mcsamples.tex
@@
 \section{Monte Carlo samples}
+\label{mcgeneration}
 
-Here we descrive the generation of the MC samples that
-we are using in this work
+First of all in this section we discuss the details of the
+Monte Carlo generation of the signal and background
+events used in this work.
+
+\subsection{Signal}
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Higgs pair production is simulated at leading order using
+{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
+account.\footnote{We thank Eleni Vrodynou for assistance here.}
+%
+We use the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
+$\alpha_S(m_Z^2)=0.118$
+as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
+%
+We use the default settings of the renormalization and factorization
+scale of the model.
+%
+The Higgs boson parameters are also the same in the default model,
+in particular we use $m_H=125$ GeV, consistent with the latest
+measurements from ATLAS and CMS.
+
+%
+Parton level events are then showered with the {\tt Pythia8} Monte
+Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, in particular with {\tt v8.201}.
+%
+We use the default settings in the parton shower, in particular
+we use the Monash 2013 tune~\cite{Skands:2014pea}, based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
+%
+We have switched off hadronisation, since this allows a more transparent modeling of
+$b$-tagging.
+%
+A complete simulation of $b$-tagging at the hadron level is difficult to achieve without a full
+detector simulator, which is beyond the scope of this paper.
+%
+For a similar reason, we don't consider underlying event, multiple parton interactions and
+pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp}.
+
+The signal samples are rescaled so that the integrated cross-section matches that of the
+NNLO calculation~\cite{deFlorian:2013jea}: this corresponds to using a $K$-factor $\sigma_{NNLO}/sigma_{LO}=2.3$.
+%
+Let us note that resummed NNLO+NNLL calculations for Higgs pair production have also become available recently~\cite{deFlorian:2015moa},
+leading to a moderate enhancement as compared to the fixed-order NNLO calculation.
+
+\subsection{Background}
+
+Now we turn to discuss the Monte Carlo generation of the relevant background processes.
+%
+All background samples are generated with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, v2.1.1.
+%
+As in the case of the signal generation, the NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples.
+Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$.
+
+Samples!!!!
+
+At the generation level the following basic cuts are applied.
+%
+Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
+All final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
+%
+We have checked that the generator-level cuts are loose enough as compared to the actual
+analysis cuts.
+%
+Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.
+
+%%%%%%%%%%%%%%%%%%%
+\begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
+\hline
+\hline
+$pp \to HH$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.729\times10^{-2}$ pb \\
+\hline
+\hline
+$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.121 \times10^3$ pb \\
+$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.659 \times 10^5$ pb \\
+$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.709\times 10^6$ pb \\
+$pp \to t\bar{t}$ &  {\tt SHERPA}v2.1.1 & 3M & $2.514\times 10^3$ pb \\
+\hline
+\end{tabular}
+\caption{\small Summary of signal and background samples generated in this work,
+together with the corresponding generator-level cross-section.} \label{tab:samples}
+\end{center}
+\end{table}%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+As a cross-check of the background cross-sections reported in Table~\ref{tab:samples}, we have produced multi-jet samples
+using the {\tt MadGraph5\_aMC@NLO} program, and compared with the results for the same processes reported in
+Ref.~\cite{Alwall:2014hca}.
+%
+For comparison with the latter numbers, 
+we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV.
+%
+All jets must be within an acceptance of $|\eta| \le 2.5 $.
+%
+In the case of the samples with $b$ quarks in the final state, these requirements are extended to the appropriate number of $b$-jets.
+For example, in the 2$b$2$j$ sample there must be at least two $b$-jets that pass the cuts outlined above.
+%
+We find agreement, within the scale uncertainties, between the {\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
+backgrounds, so we can be confident that the set-up that we will use in this analysis is robust enough.

### 2015-07-01 paper/sec-analysis.tex
Work on paper

@@
 different categories according to the event topology.
-
-{\bf needs flow chart}
 
@@
   parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
+  %
+  Before the mass-drop tagger is applied, the large-$R$ jet
+  constituents are reclustered with the Cambridge/Aachen
+  algorithm.
 
@@
 
+After having introduced the types of jet reconstruction
+that we will use, as well as the $b$-tagging strategy,
+we need to discuss the analysis strategy, including
+the event categorization and the cut flow.
+
+The basic idea of this work is the same as in Ref.~\cite{Gouzevitch:2013qca}:
+rather than selecting only a specific event topology, such as boosted
+or resolved, we aim to consistently combine the information from
+the three possible event topologies: boosted, intermediate and
+resolved, which we define now.
+%
+An important difference as compared to~\cite{Gouzevitch:2013qca}
+is that here each category is optimised separately, and then
+a exclusive categorisation is defined starting from the topology
+where the signal significance is the largest.
+
+Let us therefore define the three event categories that
+we use in this work:
+\begin{itemize}
+\item {\it Boosted category}.
+
+  A given event is assigned to the boosted category if it
+  contains at least two large-$R$ jets, defined as above,
+  and of the tow leading large-$R$ jets have been double-$b$-tagged.
+  %
+ Therefore, each of these two large-$R$ $b$-tagged jets correspond to the
+ decay products of one Higgs boson candidate.
+
+\item {\it Intermediate category}.
+
+  An event is assigned to the intermediate category if
+  at least one large $R$ $b$-tagged jet is present.
+  %
+  If more than one is found, then the leading large-$R$ jet
+  is assigned to be the first Higgs candidate.
+  %
+  In addition, we require at least two small-$R$ jets,
+  which must be separated with respect to the large-$R$
+  jet by at least an angular separation of $\Delta R\ge 1.0$.
+  %
+  The small-$R$ jets must be $b$-tagged as well.
+  %
+  Then, the second Higgs boson candidate is reconstructed
+  by selecting the two small-$R$ jets that minimize the difference
+  between the invariant mass of the large-$R$ jet, $m_{lR}$,
+  with the invariant mass of the sum of the two small-$R$ jets,
+  $m_{sR_1+sR_2}$, that is, ${\rm min}\lp m_{lR} -
+  m_{sR_1+sR_2}\rp$.
+
+\item {\it Resolved category}.
+
+  Finally, let us define the resolved category.
+  %
+  An event is assigned to this category
+  if at least
+  four $b$-tagged small-$R$ jets are present.
+  %
+  The two Higgs candidates are then reconstructed out of the
+  leading four small-$R$ jets in the event
+  by considering all possibilities of forming two pairs of jets
+  with invariant masses $m_{sR_1+sR_2}$ and 
+$m_{sR_3+sR_4}$, respectively, and choosing the configuration that minimizes their difference $|m_{sR_1+sR_2} - m_{sR_3+sR_4}|$. 
+  %
+  The requirement of restricting this selection to only the four
+  leading small-$R$ jets arises from the need to reducing the
+  combinatorics from the fakes.
+\end{itemize}
+
+In addition, events from each category need to satisfy the usual
+Higgs mass window cut, defined by
+the following condition
+\be
+|m_{h,j} - 125| < 40~{\rm GeV} \, , j=1,2 \, ,
+\ee
+where $m_{h,j}$ is the invariant mass of the two Higgs candidates
+reconstructed as explained above.
+%
+We note that this cut is substantially looser as the corresponding
+cut used in the ATLAS and CMS $h\to b\bar{b}$ analysis: the motivation
+for this is that the MVA will take care of the optimisation of each cut.
+
 In Table~\ref{sec:categorisation} we summarize the definitions of each
-category
-
-The di-Higgs system is reconstructed by considering all possibilities of forming two pairs of jets with invariant masses $m_{j1j2}$ and 
-$m_{j3j4}$, respectively, and choosing the configuration that minimizes their difference $|m_{j1j2} - m_{j3j4}|$. Only the four leading-$p_T$ jets
-are considered here.
-
-The boosted selection requires the presence of at least two $bb$-tagged, selected anti-$k_T$ $R=1.0$ jets which are taken as the two Higgs boson candidates.
-
-The intermediate topology requires the presence of at least one $bb$-tagged, selected anti-$k_T$ $R = 1.0$ jet.
-If there is more than one, the leading one is taken as the first Higgs boson candidate.
-In addition, there must be at least two anti-$k_T$ $R=0.4$ jets with a separation $\Delta R > 1.0$ with respect to the large-$R$ jet
-that is selected as a Higgs boson candidate. The second Higgs boson candidate is reconstructed from the two small-$R$ jets that minimize the difference $|m_{fj} - m_{j1j2}|$.
-
-The resolved selection requires the presence of at least four $b$-tagged, selected anti-$k_T$ $R=0.4$ jets.
-
-All Higgs candidates are required to meet the following Higgs mass window cut: $|m_{H} - 125| < 40$~GeV
+category.
+%
+We emphasize that each category is not exclusive of the others,
+and in general there can be a substantial overlap
+between the different categories.
 
@@
     \hline 
-    Jets  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
+    Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
     jets  &  $\ge$ 4 small-$R$ jets \\
-    Cuts on jets  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
+    \hline
+    Jet cuts  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
     &  $p_T \ge 40$ GeV \\
@@
     &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
+    \hline
+    $b$-tagging  & 2 double-$b$-tags  & 1 double-$b$-tag & 4 single-$b$-tags \\
+      &  & and 2 single-$b$-tags  &  \\
     \hline
@@
 
-Describe the 3 different kinematic regimes: resolved, semi-boosted and boosted and selection cuts. Show table with numbers. How often do events end up in these categories.
+We now justify some of the cuts that we are using.
+%
+As mentioned before, the cuts in each category are separately
+optimised in an inclusive analysis: it is only we have determined
+which is the dominant category that the analysis is made exclusive.
+%
+We begin with the boosted category.
+%
+In Fig.~\ref{fig:cutplots1} we show
+the $p_T$ distribution of the
+  leading large-$R$ jet in the boosted category, comparing
+  the shapes of the distribution in signal and background events.
+  %
+  All distributions have been normalized to their total integral.
 
-Table 1: how many events we see from Signal and background in each category.
-Indicate also the overlap between the categories.
-This table should have also the S/B and S/sqrtB numbers.
-We need also the S/B and S/sqrtB numbers without the 2b2j and 4j backgrounds in order to compare with the UCL paper in this table.
-
-Figure 1: Higgs pt, eta distributions
-
-Figure 2: b-jet pt distributions
-
-Figure 3: delta R distributions
-
-Figure 4: mass distributions
-
-Table 2: S/B and S/sqrtB table with
-All these figures should have the backgrounds overlaid.
-
-This section would show that the 2b2j and 4j backgrounds are important and that control of the fakes is necessary.
-
-This section should also identify which of the different regimes is the most important for the measurement.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/pt_H0_res_C1_boost.pdf}
+\caption{\small Left plot: the $p_T$ distribution of the
+  leading large-$R$ jet in the boosted category, comparing
+  the shapes of the distribution in signal and background events.
+  %
+  All distributions have been normalized to their total integral.
+}
+\label{fig:cutplots1}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-01 paper/sec-appendix-overlap.tex
Work on paper

\section{On the role of the overlap between different categories}
\label{sec:overlap}

In this appendix we discuss the role of the overlap
between  different categories.

### 2015-07-01 paper/sec-mcsamples.tex
Work on paper

@@
 
-Samples!!!!
+We consider all the relevant samples that can lead to the event
+being tagged as a $HH\to 4b$ candidate.
+%
+First of all QCD $4b$ multi-jet production of course.
+%
+But also we generate QCD $2b2j$ and $4j$ multi-jet samples,
+that can lead to the even being tagged in the case of multiple light
+jets being mistagged as $b$-quarks.
+%
+While the light jet mistag probability is small, we find that
+in general the $2b2j$ and $4j$ backgrounds cannot be neglected because
+of their large cross-sections and enhancement from combinatorics, that
+increase their contribution as compared to the naive estimate.
 

### 2015-07-01 paper/sec-optimisation.tex
Work on paper

\section{Optimisation}
\label{sec:optimisation}

One important motivation of this work was to quantify which aspects
of the performance of the LHC detectors needs to be improved
the most in order to maximise the significance of the observation
of double Higgs production in the $4b$ final state.
%
In this section we explore how the results with the baseline settings,
summarized in the previous section, are modified when some of
these settings are changed.
%
In particular we will explore the dependence of the results on
the $b$-tagging probability $f_b$, the light jet mistag rate
$f_l$, as well on the momentum smearing fraction.
%
The variations of the analysis
settings that we will explore are collected in
Table~\ref{sec:variations}.

%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|}
\hline
    Scenario  &  $f_b$  &  $f_l$  &  $\Delta p_T$ \\
    \hline
    \hline
    Baseline  &  0.8   &   0.01  &  5\% \\
    \hline
    A        &  0.9   &   0.01  &  5\% \\
    B        &  0.7   &   0.01  &  5\% \\
    C        &  0.8   &   0.005  &  5\% \\
    D        &  0.8   &   0.02  &  5\% \\
    E        &  0.9   &   0.005  &  2\% \\   
    \hline
  \end{tabular}
  \caption{\small The baseline settings for the $b$-jet
    tagging probability, the light jet mistag rate $f_l$
    and the $p_T$ resolution $\Delta p_T$, compared
    to the various scenarios that we discusse in this section.
\label{sec:variations}
  }
  \end{table}
%%%%%%%%%%%%%%%%%%%

### 2015-07-03 paper/sec-results.tex
work on paper

@@
 
-\section{Results}
+\section{Cut-based analysis results}
 
@@
 
-Study S/B, S/sqrt B vs b-tagging efficiency, background rejection and signal efficiency
+In this section we discuss the results of the traditional
+cut-based analysis, using the strategy presented in the previous
+section.
+%
+We compare our results with other recent related studies,
+and in particular we study how the signal significance
+is modified if only the $4b$ QCD background is taken into account,
+but the $2b2j$ and $jjjj$ backgrounds are neglected, as done
+in previous work.
+%
+Then in the next section we show how using multivariate techniques
+one can substantially improve the signal significance as compared
+to the cut-based analysis.
 
-This section would show how S/B is correlated with the different efficiencies.
-It would give the reader a feel for which of these sources the analysers would need to attack to make the 4b channel a competitive channel with regard to other channels.
+\subsection{Signal significance}
+
+We now study the basic results of our cut based analysis, with
+all backgrounds properly taken into account.
+
+We begin by showing the cut-flow at various levels of the analysis.
+%
+Here we consider all backgrounds at the same time, and below
+we comment on the role of the individual backgrounds.
+
+We consider the following levels of the cut-flow
+\begin{itemize}
+\item {\bf C0}: these are the cross-sections at the generator
+  level, before any analysis cuts
+\item {\bf C1}: results after the basic jet selection
+  and related cuts, but before $b$-tagging.
+\item {\bf C2}: results after the $b$-tagging, but
+  before applying the invariant mass window cut
+\item {\bf C3}: final results of the cut-based
+  analysis
+  \end{itemize}
+We consider the results for the individual categories, using the
+exclusive priorisation discussed in the previous section.
+%
+In Appendix.~\ref{sec:overlap} we comment
+interplay of the overlap between the various categories.
+%
+At each stage of the cut flow, we also provide the number
+of events that would be expected at the HL-LHC with
+an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
+the signal significance $S/\sqrt{B}$ and the signal
+over background ratio $S/B$.
+%
+Results are shown both for the signal and for all backgrounds
+combined.
+
+Let's begin with the discussion of the boosted category,
+Table~\ref{table:cutflowboosted}, that as we have explained
+is the one that benefits from a higher signal significance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c|c|c|c|c}
+    \hline
+    \multicolumn{7}{c}{Boosted category}\\
+    \hline
+    \hline
+    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
+    &   $S/\sqrt{B}$  & $S/B$\\
+      &    Signal & Back   &  Signal  & Back
+    &   & \\
+    \hline
+        {\bf C0}  &  AAA  & AAA & AAA & AAA  &  AAA & AAA\\
+        {\bf C1}  &       &     &     &      &      &   \\
+        {\bf C2}  &       &     &     &      &      &   \\
+        {\bf C3}  &       &     &     &      &      &   \\
+        \hline
+  \end{tabular}
+  \caption{\small Cut-flow for the analysis of the boosted
+    category.
+    %
+    At each level we indicate the cross-sections and the number of
+    expected events at the HL-LHC both for
+    signal and for all the backgrounds combined,
+    as well as the signal significance $S/\sqrt{B}$ and the signal
+    over background ratio $S/B$.
+    \label{table:cutflowboosted}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c|c|c|c|c}
+    \hline
+    \multicolumn{7}{c}{Intermediate category}\\
+    \hline
+    \hline
+    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
+    &   $S/\sqrt{B}$  & $S/B$\\
+      &    Signal & Back   &  Signal  & Back
+    &   & \\
+    \hline
+        {\bf C0}  &  AAA  & AAA & AAA & AAA  &  AAA & AAA\\
+        {\bf C1}  &       &     &     &      &      &   \\
+        {\bf C2}  &       &     &     &      &      &   \\
+        {\bf C3}  &       &     &     &      &      &   \\
+        \hline
+  \end{tabular}
+  \caption{\small Same as Table~\ref{table:cutflowboosted} now for
+    the intermediate category.
+    \label{table:cutflowintermediate}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c|c|c|c|c}
+    \hline
+    \multicolumn{7}{c}{Intermediate category}\\
+    \hline
+    \hline
+    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
+    &   $S/\sqrt{B}$  & $S/B$\\
+      &    Signal & Back   &  Signal  & Back
+    &   & \\
+    \hline
+        {\bf C0}  &  AAA  & AAA & AAA & AAA  &  AAA & AAA\\
+        {\bf C1}  &       &     &     &      &      &   \\
+        {\bf C2}  &       &     &     &      &      &   \\
+        {\bf C3}  &       &     &     &      &      &   \\
+        \hline
+  \end{tabular}
+  \caption{\small Same as Table~\ref{table:cutflowboosted} now for
+    the boosted category.
+    \label{table:cutflowresolved}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From the results of Tables~\label{table:cutflowboosted}--\ref{table:cutflowresolved}
+we see that after the cut-based analysis, the significance of the Higgs pair production
+observation in the $4b$ channel using the boosted topology is ... and that the combination
+of the boosted, intermediate and resolved categories gives ....
+%
+We discuss in the next section of this significance can be enhanced by means
+of multivariate analysis.
+
+\subsection{Comparison with previous work}
+
+We now compare with two recent studies that have also studied the
+feasibility of SM Higgs pair production in the $4b$ final state,
+those of the UCL group~\cite{Wardrope:2014kya} and of the
+Durham group~\cite{deLima:2014dta}.
+%
+In order to perform a meaningful comparison, we will only consider
+here the $4b$ QCD and $t\bar{t}$ backgrounds, as was done
+in these two studies.
+
+{\bf paragraph about UCL strategy}
+
+{\bf paragraph about Durham strategy}

### 2015-07-06 paper/sec-mva.tex
MVA

@@
 
-The final step of our analysis is to process our three exclusive
-categories of events (boosted, intermediate and resolved) though
-a Multivariate Analysis.
-%
-The particular tool that we adopt is
-a feed-forward artificial neural network.\footnote{This is the
-  same type of neural networks as those used in the
-  NNPDF analysis of parton distributions~\cite{Ball:2010de}.}
-%
-The architecture of the neural network is
+The classification of events as arising from either signal or
+background processess via the use of a multivariate analysis is a common
+technique in high energy physics.
+
+In order to investigate the potential efficacy of an MVA in an $HH\to 4b$
+measurement, we process the events remaining after the cut-based analysis 
+through a standard feed-forward artificial neural network with architecture
+
 \be
@@
 \ee
-with $N_{\mathrm{par}}$ the number of input variables for the MVA.
-%
-Therefore, we have two hidden layers and a single output variable, which
-is the value of the discriminant to separate signal and background.\footnote{Note that in the MVA literature artificial neural networks with several hidden
-  layers are known as {\it deep neural networks}.}
-%
-Below we list the variables that are given as input to the MVA in each
-different category.
-%
-The MVA has trained using a Genetic Algorithm during 50K iterations,
-and the figure of merit to be minimized is the cross-entropy function.
-%
-This figure of merit is defined as
+where $N_{\mathrm{par}}$ represents the number of input variables for the MVA.
+All neural-network layers use a sigmoid activation function, allowing for a probabilistic
+interpretation of the neural-network output.
+
+The input variables for the MVA differ between our three categories, based upon
+the availability in each analysis of substructure information on fat jets. For all
+three analyses, the following common variables are used:
+
+\begin{itemize}
+\item The transverse momenta of the leading and subleading Higgs candidates, $p_{T,H_0}$, $p_{T,H_1}$.
+\item The transverse momentum of the reconstructed Higgs pair, $p_{T,HH}$
+\item The invariant masses of the leading and sub-leading Higgs candidates, $m_{H,1}$, $m_{H,2}$.
+\item The invariant mass of the reconstructed Higgs pair, $m_{HH}$.
+\item The separation in $R$ of the two Higgs candidates, $\Delta R_{HH}$.
+\item The separation in $\phi$ of the two Higgs candidates, $\Delta \phi_{HH}$.
+\item The separation in $\eta$ of the two Higgs candidates, $\Delta \eta_{HH}$.
+\item The transverse momenta of the leading Higgs candidate subjets, $p_{T,H_{0,0}}$, $p_{T,H_{0,1}}$
+\item The transverse momenta of the sub-leading Higgs candidate subjets, $p_{T,H_{1,0}}$, $p_{T,H_{1,1}}$
+\end{itemize}
+
+For analyses including the reconstruction of fat jets, the following variables are included for
+every fat jet Higgs candidate present in the analysis.
+
+\begin{itemize}
+\item The $k_T$ splitting scale of the fat-jet (Reference).
+\item The ratio of 2-to-1-Subjettiness $\tau_{2}/\tau_{1}$ of the fat-jet (Reference).
+\item The fat-jet energy correlation function double-ratio $C_2$ (Reference).
+\item The fat-jet energy correlation function double-ratio $D_2$ (Reference).
+\end{itemize}
+
+Therefore there are in total $N_{\mathrm{var}}=13$ variables for the resolved analysis, 17 for the semi-resolved, and 21 for the boosted category.
+
+Given the above set of kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ as the probability that the event $i$ originates from the signal process,
+\be y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} ), \ee
+where $y_i^\prime$ represents the true classification of the event $i$, i.e $y^\prime_{\text{signal}} = 1$ and $y^\prime_{\text{background}} = 0$.
+With this interpretation, our general classification probability including background events is given by
 \be
-\bf DEF
+P(y_i^\prime|\{k\}_i, \{\omega\}) = y_i^{y^\prime_i}(1-y_i)^{1-y^\prime_i}.
 \ee
+ Correspondingly the negative log-liklihood cost function to be used in the neural network training is the cross-entropy error
+\be E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right) = \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)}. \ee
 
-For both signal and background events, the variables that we input
-to the MVA are the following.
-%
-For the boosted category we have
-\begin{itemize}
-\item The invariant mass of the two mass-drop-tagged jets, $m_{\rm jet}$
-\item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$
-\item The rapidity of the two mass-drop-tagged jets, $y_{\rm jet}$
-\item The invariant mass of the leading Higgs candidate, $m_{h,1}$
-\item The invariant mass of the sub-leading Higgs candidate, $m_{h,2}$
-\item The splitting scale of the first Higgs
-\item The splitting scale of the second Higgs
-\item The subjetiness variable $\tau_{21,h1}$ of the leading Higgs candidate
-\item The subjetiness variable $\tau_{21,h2}$
-  of the sub-leading Higgs candidate
- \item The angular separation between the two tagged jets, $\Delta R_{1,2}$ 
-\end{itemize}
-For completeness, we give here the definition of the various substructure variables.
-%
-The splitting scale is defined as
-\be
-\bf DEF
-\ee
-while the $\tau_{1,2}$ subjetiness variable is defined as
-\be
-\bf DEF
-\ee
-The other variables are more conventional.
-%
-As will be shown below, the addition of the jet substructure variables,
-the splitting scales and the subjetiness,
-enhances substantially the signal significance, as compared
-to using only jet variables without substructure information.
-
-For the resolved analysis instead, the $N_{\rm var}$ kinematic variables
-that are given as input to the MVA are the following
-\begin{itemize}
-\item The invariant mass of the four $b$-tagged leading jets (that
-  is, of the di-Higgs system), $m_{4b}$
-\item The transverse momentum of the di-Higgs system, $p_{4b}$
-\item The rapidity of the di-Higgs system $y_{4b}$
-\item The invariant mass of the leading Higgs candidate $m_{h,1}$
-\item The invariant mass of the subleading Higgs candidate $m_{h,1}$
-\item The angular separation between each of the four
-  $b$-tagged leading jets in the event: $\Delta R_{b1,b2}$,
-  $\Delta R_{b1,b3}$, $\Delta R_{b1,b4}$, $\Delta R_{b2,b3}$,
-  $\Delta R_{b2,b4}$, $\Delta R_{b3,b4}$
-\end{itemize}
-As will be shown below, of all these variables, the invariant mass of the
-Higgs candidates is the one that carries as higher discrimination
-power.
-
+Using the cross-entropy cost function, the neural networks are trained with a basic genetic algorithm (GA) over 50,000 generations.
+(Do we need to specifiy GA params etc?).
 \subsection{Enhancing signal discrimination with the MVA}

### 2015-07-06 paper/sec-results.tex
work on paper

@@
 combined.
+%
+The results for the three categories have been collected in
+Table~\ref{table:cutflowboosted}.
 
-Let's begin with the discussion of the boosted category,
-Table~\ref{table:cutflowboosted}, that as we have explained
+We emphasize that it is important not only to achieve a good signal
+significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
+if the latter is too small, a measurement of the background with an unfeasibly small
+systematic uncertainty would be required.
+
+Let's begin with the discussion of the boosted category, that as we have explained
 is the one that benefits from a higher signal significance.
+%
+We see that after all the cuts, including $b$-tagging,
+we end up with almost 200 signal events at the HL-LHC, and
+still a substantial background of around $40k$ events.
+%
+The signal significance is around one at the end of the
+cut-based analysis.
+%
+Note that it is easy to compute the corresponding numbers
+for the end of Run II at the LHC with
+$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: we have only
+19 signal events, and the signal significance drops down to
+$S/\sqrt{B}\sim 0.3$.
+%
+We will discuss in the next section what are the Run II prospects
+once we include the effects of the MVA in the analysis.
 
@@
   \centering
-  \begin{tabular}{c|c|c|c|c|c|c}
+  \begin{tabular}{c|c|c||c|c||c|c}
     \hline
@@
     \hline
-    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
+    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
     &   $S/\sqrt{B}$  & $S/B$\\
@@
     \hline
-        {\bf C0}  &  AAA  & AAA & AAA & AAA  &  AAA & AAA\\
-        {\bf C1}  &       &     &     &      &      &   \\
-        {\bf C2}  &       &     &     &      &      &   \\
-        {\bf C3}  &       &     &     &      &      &   \\
+        {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
+        {\bf C1}  &  0.46    & $1.3\,10^6$    &  $1.4\,10^3$   & $3.9\,10^9$     & 0.022     &  $3.5\,10^{-7}$ \\
+        {\bf C2}  &  0.064     &  12.6     &  193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$ \\
         \hline
   \end{tabular}
-  \caption{\small Cut-flow for the analysis of the boosted
-    category.
-    %
-    At each level we indicate the cross-sections and the number of
-    expected events at the HL-LHC both for
-    signal and for all the backgrounds combined,
-    as well as the signal significance $S/\sqrt{B}$ and the signal
-    over background ratio $S/B$.
-    \label{table:cutflowboosted}
-  }
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
-  \centering
+  $\,$\\
+  \vspace{0.4cm}
   \begin{tabular}{c|c|c|c|c|c|c}
@@
     \hline
-        {\bf C0}  &  AAA  & AAA & AAA & AAA  &  AAA & AAA\\
-        {\bf C1}  &       &     &     &      &      &   \\
-        {\bf C2}  &       &     &     &      &      &   \\
-        {\bf C3}  &       &     &     &      &      &   \\
+         {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
+        {\bf C1}  &   1.44    &   $1.1\,10^{7}$  &  $4.3\,10^3$   &  $3.3\,10^{10}$    &  0.024    &  $1.3\,10^{-7}$ \\
+        {\bf C2}  &   0.22    &  722   &  660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ \\
         \hline
   \end{tabular}
-  \caption{\small Same as Table~\ref{table:cutflowboosted} now for
-    the intermediate category.
-    \label{table:cutflowintermediate}
-  }
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
-  \centering
+  $\,$\\
+  \vspace{0.4cm}
+  \noindent
   \begin{tabular}{c|c|c|c|c|c|c}
     \hline
-    \multicolumn{7}{c}{Intermediate category}\\
+    \multicolumn{7}{c}{Resolved category}\\
     \hline
@@
     \hline
-        {\bf C0}  &  AAA  & AAA & AAA & AAA  &  AAA & AAA\\
-        {\bf C1}  &       &     &     &      &      &   \\
-        {\bf C2}  &       &     &     &      &      &   \\
-        {\bf C3}  &       &     &     &      &      &   \\
+       {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
+        {\bf C1}  &   3.34    & $7.5\,10^{7}$    & $1.1\,10^4$    & $3.3\,10^{10}$     & 0.021     & $4.5\,10^{-8}$  \\
+        {\bf C2}  &   0.54    &  $3.5\,10^{3}$   &  $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$ \\
         \hline
   \end{tabular}
-  \caption{\small Same as Table~\ref{table:cutflowboosted} now for
-    the boosted category.
-    \label{table:cutflowresolved}
+  \caption{\small Cut-flow for the analysis of the boosted (top),
+    intermediate (middle) and resolved (bottom)
+    categories.
+    %
+    At each level of the cut-flow, we indicate the cross-sections and the number of
+    expected events at the HL-LHC for $\mathcal{L}_{\rm int}=3$ ab$^{-1}$, both for
+    signal events and for all the backgrounds combined.
+    %
+    We also provide in each case the
+    signal significance $S/\sqrt{B}$ and the signal
+    over background ratio $S/B$.
+    %
+    The first row {\bf C0} is the generator-level result and thus is common
+    to all three categories.
+    %
+    See text for more details.
+    \label{table:cutflowboosted}
   }
@@
 
-From the results of Tables~\label{table:cutflowboosted}--\ref{table:cutflowresolved}
+Both the intermediate and resolved categories benefit from higher signal yields,
+specially in the resolved category, but this enhancement is cancellend by the stronger
+increase in the QCD multijet background.
+%
+We see that in both cases the signal significance is around half of that in the boosted category,
+with in addition $S/B$ being an order of magnitude smaller.
+%
+Therefore, the boosted category is clearly determined to be the most useful category,
+specially due to the significant suppression of the QCD multijet background.
+%
+And we still have not exploited all the rich information contained on the jet
+substructure, as we will do in the next section.
+
+From the results of Table~\label{table:cutflowboosted}
 we see that after the cut-based analysis, the significance of the Higgs pair production
@@
 {\bf paragraph about Durham strategy}
+
+In order to compare with previous results, it is interesting to
+study how our results change if we consider only the QCD $4b$
+multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
+that is, we ignore the contribution from the fakes.
+%
+For the boosted category, the results are shown in
+Table~\ref{table:cutflowboosted4B}, which is the analog of
+Table~\ref{table:cutflowboosted} but with only the QCD
+$4b$ background taken into account.
+%
+As we can see, these results indicate that given the similarity of the final states
+in signal and background events in these cases, the signal significance is
+relatively stable at various stages of the cut-flow.
+%
+As compared to the case in which all backgrounds are taken into account, we
+now get a factor two smaller backgrounds: we conclude that in the boosted category
+the effect of the fakes is non-negligible, with their contribution being
+comparable to that of the irreducible $4b$ QCD multi-jet background.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c||c|c||c|c}
+    \hline
+    \multicolumn{7}{c}{Boosted category}\\
+    \hline
+    \hline
+    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
+    &   $S/\sqrt{B}$  & $S/B$\\
+      &    Signal & Back   &  Signal  & Back
+    &   & \\
+    \hline
+        {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
+        {\bf C1}  &  0.46    & $1.0\,10^2$    &  $1.4\,10^3$   & $3.1\,10^5$     & 2.48     &  $4.4\,10^{-3}$ \\
+        {\bf C2}  &  0.064     &  7.1     &  193   &  $2.1\,10^4$    &  1.30    &  $9.1\,10^{-3}$ \\
+        \hline
+  \end{tabular}
+  \caption{\small Same as Table~\ref{table:cutflowboosted}, but now
+    only with the QCD $4b$ multi-jet background taken into account.
+    %
+    \label{table:cutflowboosted4B}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-06 paper/sec-analysis.tex
work on paper

@@
   All distributions have been normalized to their total integral.
+  %
+  We see that the background distribution
+  falls off rather steeply than the signal, therefore
+  suggesting that the boosted region should be
+  advantageous to suppress the background.
 
@@
   \includegraphics[width=0.48\textwidth]{plots/pt_H0_res_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1_boost.pdf}
 \caption{\small Left plot: the $p_T$ distribution of the
@@
   All distributions have been normalized to their total integral.
+  %
+  Right plot: the invariant mass of the leading Higgs
+  candidate.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+In Fig.~\ref{fig:cutplots1} we also show the distribution
+of the invariant mass of the leading Higgs candidates.
+%
+The signal is of course well peaked at $m_h=125$ GeV, the physical
+mass, while the background does not display any structure.
+%
+Note that the smearing, which mimics detector resolution effects,
+leads to a rather broad distribution which reduces the usefulness
+of the Higgs mass window cut.
+%
+However, the information of the different shape of the $m_{h}$
+distribution will still be exploited by the MVA.
+
+As explained above, in the boosted category we also require the two
+leasing subjets of the large-$R$ jet to be relatively
+hard.
+%
+In Fig ...

### 2015-07-06 paper/sec-conclusions.tex
more work on text
work on paper

@@
 \section{Conclusions and outlook}
+\label{sec:conclusions}
 
@@
 of the measurement of Higgs pair production in the $bb\bar{b}\bar{b}$
-final state at the High-Luminosity LHC....
+final state at the High-Luminosity LHC.
+%
+As opposed to previous works, we have combined a traditional
+cut-based analysis with a modern multivariate analysis,
+which allows one to significantly improve the signal significance.
+%
+A careful analysis of the different possible methods to reconstruct
+Higgs pairs finds that the boosted category is the most efficient
+one, but that additional complementary information can also be provided
+by the intermediate and resolved categories.
+%
+Our analysis includes all relevant backgrounds, including the
+effects from fake $b$-tags, neglected in previous works,
+which turn out to be quite important specially
+in the boosted and in the resolved categories.
+
+Thanks for the MVA improvements, and combining the information
+from the three exclusive categories, we find a signal significance
+of 3.8.
+%
+Therefore, we can conclude that, already on the $4b$ channel along,
+it should be possible to observe evidence for this process at
+the HL-LHC.
+%
+A combination with other decay channels, like $b\bar{b}\gamma\gamma$
+and $b\bar{b}\tau\tau$ would still be required in order
+to claim discovery of Higgs pair production.
+
+One important implication of our results is which is the accuracy
+that can be achieved for a measurement of the
+Higgs trilinear coupling $\lambda$ from a measurement
+of the $4b$ final state.
+%
+We plan to quantify this in future work.
+%
+In addition,
+in this work we have considered only SM production mechanism,
+but it is well known that many BSM scenarios predict deviations
+in Higgs pair production, both at the level of rates,
+for instance when the trilinear coupling $\lambda$, and of
+shapes of the distributions, when higher-order effective
+operators are included in the theory~\cite{Azatov:2015oxa}.
+%
+In this respect, we plan to study which are the constraints
+on BSM physics that can be obtained from measurements
+of Higgs pair production in the $4b$ channel.
+%
+This however will be a computationally intensive task since in
+general BSM physics modify the shapes of the Higgs kinematical
+distributions, and thus each different point in the parameter
+space would require a re-optimization via a new training
+of the MVA.
 
@@
 {\bf\noindent  Acknowledgments \\}
-We thank A.~Papaefstathiou for useful discussions on this project.
+We thank R.~Contino, A.~Papaefstathiou and
+G.~Salam for useful discussions on the topic
+of Higgs pair production.
 %
@@
 %
+N.~B.~N. is supported by a PhD scholarship from the Malaysia
+government.
+K.~B. is supported by a studentships from the Rhodes Foundation.
+%
+J.~F. and C.~I. are supported by the STFC.

### 2015-07-06 paper/sec-mcsamples.tex
work on paper

@@
 backgrounds, so we can be confident that the set-up that we will use in this analysis is robust enough.
+
+\subsection{Smearing}
+
+It is beyong the scope of this work to perform a complete study of the impact of
+detector effects in this process.
+%
+However, it is still important to include some form of rough estimate of detector
+effects in the analysis.
+%
+In this work we simulate the finite momentum resolution of the ATLAS and CMS
+hadronic calorimenters by ....

### 2015-07-06 paper/sec-mva.tex
work on paper

@@
 The classification of events as arising from either signal or
-background processess via the use of a multivariate analysis is a common
+background processes via the use of a multivariate analysis is a common
 technique in high energy physics.
@@
 \item The $k_T$ splitting scale of the fat-jet (Reference).
-\item The ratio of 2-to-1-Subjettiness $\tau_{2}/\tau_{1}$ of the fat-jet (Reference).
+\item The ratio of 2-to-1-Subjetiness $\tau_{2}/\tau_{1}$ of the fat-jet (Reference).
 \item The fat-jet energy correlation function double-ratio $C_2$ (Reference).
@@
 \ee
- Correspondingly the negative log-liklihood cost function to be used in the neural network training is the cross-entropy error
+ Correspondingly the negative log-likelihood cost function to be used in the neural network training is the cross-entropy error
 \be E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right) = \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)}. \ee
@@
 Using the cross-entropy cost function, the neural networks are trained with a basic genetic algorithm (GA) over 50,000 generations.
-(Do we need to specifiy GA params etc?).
+(Do we need to specify GA params etc?).
 \subsection{Enhancing signal discrimination with the MVA}
@@
 
+\subsection{Another look at jet substructure variables}
+
+It is now worth trying to understand where does the increase in signal significance
+achieved after the MVA comes from.
+%
+As we will show now, the MVA has correctly identified which of the substructure
+variables are more discriminant between signal and background distributions,
+and combined this information to determine an optimal cut to maximize signal
+significance.
+
+For instance, in the boosted category, the analyses of the
+size of the neural network weights clearly indicates that the subjetiness
+$\tau_{12}$ and the energy correlations $C_2$ are two of the most useful
+variables.
+%
+To verify that indeed these two variables are quite different between signal
+and background events, in Fig.~\ref{fig:mva_substructure_1}
+we show the subjetiness $\tau_{12}$ and the energy correlation between
+signal and background.
+%
+We indeed verify that the two shapes are quite different,
+reflecting the differences in the internal structure of jets
+between QCD jets and jets originated from the Higgs decays.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_H0_res_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_H0_res_C1_boost.pdf}
+  \caption{\small Left plot: subjetiness.
+    Right plot: energy correlations.
+}
+\label{fig:mva_substructure_1}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Impact of smearing in the MVA discrimination}

### 2015-07-06 paper/sec-optimisation.tex
work on paper

@@
     and the $p_T$ resolution $\Delta p_T$, compared
-    to the various scenarios that we discusse in this section.
+    to the various scenarios that we discussed in this section.
 \label{sec:variations}
@@
 %%%%%%%%%%%%%%%%%%%
+
+We also study how the signal significance is modified as a function
+of the systematic uncertainty that needs to be obtained
+in the measurement of the background processes.
+%
+This is specially important in a process like this one where
+the signal over background ratio $S/B$ is small, and thus were
+it is essential to measure the backgrounds as accurately
+as possible.

### 2015-07-06 paper/sec-results.tex
work on paper

@@
 The results for the three categories have been collected in
-Table~\ref{table:cutflowboosted}.
+Table~\ref{table:cutflow}.
 
@@
 significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
-if the latter is too small, a measurement of the background with an unfeasibly small
+if the latter is too small, a measurement of the background with an infeasible small
 systematic uncertainty would be required.
@@
     See text for more details.
-    \label{table:cutflowboosted}
+    \label{table:cutflow}
   }
@@
 Both the intermediate and resolved categories benefit from higher signal yields,
-specially in the resolved category, but this enhancement is cancellend by the stronger
-increase in the QCD multijet background.
+specially in the resolved category, but this enhancement is canceled by the stronger
+increase in the QCD multi-jet background.
 %
@@
 Therefore, the boosted category is clearly determined to be the most useful category,
-specially due to the significant suppression of the QCD multijet background.
+specially due to the significant suppression of the QCD multi-jet background.
 %
@@
 
+Concerning the other categories, we see that that ignoring the fakes can lead to a substantial
+distortion of the results.
+%
+In the intermediate category, the signal significance is now much better, with $S/sqrt{B}$ increasing from
+0.5 with all the backgrounds to $1.57$ if only $4b$ are accounted for, a factor 3 improvement.
+%
+Also the resolved category improves substantially, with signal significance increasing by a factor 2.
+%
+Therefore, we conclude that a careful modeling of the fakes is very important to truly quantify
+the feasibility of Higgs pair production in the $4b$ channel, though for the most
+important category, the boosted category, the results are relatively stable.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \end{tabular}
-  \caption{\small Same as Table~\ref{table:cutflowboosted}, but now
+   $\,$\\
+  \vspace{0.4cm}
+  \begin{tabular}{c|c|c|c|c|c|c}
+    \hline
+    \multicolumn{7}{c}{Intermediate category}\\
+    \hline
+    \hline
+    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
+    &   $S/\sqrt{B}$  & $S/B$\\
+      &    Signal & Back   &  Signal  & Back
+    &   & \\
+    \hline
+ {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
+        {\bf C1}  &  0.46    & $7.2\,10^2$    &  $1.4\,10^3$   & $2.2\,10^6$     & 2.91     &  $1.9\,10^{-3}$ \\
+        {\bf C2}  &  0.064     &  58.8     &  193   &  $1.8\,10^5$    &  1.57    &  $3.7\,10^{-3}$ \\
+        \hline
+  \end{tabular}
+  $\,$\\
+  \vspace{0.4cm}
+  \noindent
+  \begin{tabular}{c|c|c|c|c|c|c}
+    \hline
+    \multicolumn{7}{c}{Resolved category}\\
+    \hline
+    \hline
+    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
+    &   $S/\sqrt{B}$  & $S/B$\\
+      &    Signal & Back   &  Signal  & Back
+    &   & \\
+    \hline
+ {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
+        {\bf C1}  &  0.46    & $9.0\,10^3$    &  $1.4\,10^3$   & $2.7\,10^7$     & 1.92     &  $3.7\,10^{-4}$ \\
+        {\bf C2}  &  0.064     &  986     &  193   &  $2.9\,10^6$    &  0.95  &  $5.5\,10^{-4}$ \\
+        \hline
+  \end{tabular}
+  \caption{\small Same as Table~\ref{table:cutflow}, but now
     only with the QCD $4b$ multi-jet background taken into account.
     %
-    \label{table:cutflowboosted4B}
+    \label{table:cutflow4B}
   }

### 2015-07-06 paper/plotscripts/plotHist_boosted_C2_fj1.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "EEC_C2_H0_res_C1_boost"
+
+# Datafiles
+datafiles.append("../plotdata/oxford_combined_rw/signal/histo_C2_fj1_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/background/histo_C2_fj1_boost_C1.dat")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+# Axis labels
+xLabel = "Energy Correlation in leading jet"
+yLabel = "A. U."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,0.5])
+ax.set_ylim([1e-2,10])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
+      xhi.append(float(linesplit[1]))
[…]

### 2015-07-06 paper/plotscripts/plotHist_boosted_m_H0.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_H0_res_C1_boost"
+
+# Datafiles
+datafiles.append("../plotdata/oxford_combined_rw/signal/histo_m_H0_inter_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/background/histo_m_H0_inter_C1.dat")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+# Axis labels
+xLabel = "Leading Higgs candiate $m_h$ (GeV)"
+yLabel = "A. U."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([85,170])
+ax.set_ylim([1e-3,0.1])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
+      xhi.append(float(linesplit[1]))
[…]

### 2015-07-06 paper/sec-mva.tex
work on paper

@@
 To investigate this, we now consider a variant of the analysis used in
-Table~\ref{tab:resCutflow} where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
+Table  where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
 %

### 2015-07-06 paper/sec-results.tex
work on paper

@@
 For the boosted category, the results are shown in
-Table~\ref{table:cutflowboosted4B}, which is the analog of
-Table~\ref{table:cutflowboosted} but with only the QCD
+Table~\ref{table:cutflow4B}, which is the analog of
+Table~\ref{table:cutflow} but with only the QCD
 $4b$ background taken into account.

### 2015-07-06 paper/sec-analysis.tex
work on paper

@@
 
+\subsection{Kinematic distributions}
+
 We now justify some of the cuts that we are using.
@@
 %
-In Fig ...
+In Fig ... we show the distribution in $p_T$ of the leading
+and subleading jets.
+%
+It is clear from the comparison that
+
+Let's now consider the resolved category.
+%
+To begin with, here it is important to understand the $p_T$ distribution
+of the four leading small-$R$ jets of the event.
+%
+Given that in general the boost from the Higgs decays is moderate,
+the two subleading jets might be not too hard, and thus it
+should be important to ensure that our $p_T^{\rm min}$ cut
+is not too strong.
+%
+In Fig. we show ....
+
+Also, it is useful to show the distribution in rapidity of the
+individual jets
+
+Finally, we show in
+Fig.~\ref{fig:mhh} the invariant mass distribution of the Higgs pairs,
+comparing the resolved category (left) with the boosted category (right)
+%
+This is interesting since it determines the degree of boost that the two
+Higgs candidates will have after non-resonant production.
+%
+In the resolved case, we see that the distribution
+in $m_{hh}$ is rather harder for the signal as for the background,
+and thus one expects that cutting in $m_{hh}$ would help signal
+discrimination: we will verify this with the MVA in the next section.
+%
+For the boosted category the trend of the $m_{hh}$ distribution
+is very different because of the selection, with the
+distribution now peaking at much higher values.
+%
+In this case signal and background distributions
+look reasonably similar.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{plots/m_HH_res_C1.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/m_HH_boost_C1.pdf}
+  \caption{\small Left plot: the invariant mass distribution of the Higgs
+    pair candidates, $m_{hh}$, comparing signal and background events,
+    in the resolved category.
+    %
+    Right plot: same for the boosted category.
+}
+\label{fig:mhh}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-06 paper/sec-mcsamples.tex
work on paper

--- 2015-07-01 paper/sec-mcsamples.tex
@@
 
-First of all in this section we discuss the details of the
+First of all in this section we discuss the settings of the
 Monte Carlo generation of the signal and background
 events used in this work.
+%
+We also discuss how we study the effects of finite detector
+resolution by means of an smearing of the final-state
+particles four-momentum.
 
-\subsection{Signal}
+\subsection{Higgs pair production}
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 in particular we use $m_H=125$ GeV, consistent with the latest
-measurements from ATLAS and CMS.
+measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
+%
+The value of the Higgs trilinear coupling $\lambda$ is set to its
+Standard Model value.
+%
+The calculation is performed in the
+$N_f$=4 scheme and thus
+takes into account the finite mass of the $b$-quarks.
+
+The signal samples are rescaled so that the integrated cross-section matches that of the
+NNLO calculation of the inclusive cross-section from Ref.~\cite{deFlorian:2013jea}:
+this corresponds to using a $K$-factor $\sigma_{\rm NNLO}/\sigma_{\rm LO}=2.3$.
+%
+Let us note that resummed NNLO+NNLL calculations for Higgs pair production have also become available recently~\cite{deFlorian:2015moa},
+leading to a moderate enhancement as compared to the fixed-order NNLO calculation.
 
@@
 pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp}.
+%
+The same applies to the background samples, which we discuss now
 
-The signal samples are rescaled so that the integrated cross-section matches that of the
-NNLO calculation~\cite{deFlorian:2013jea}: this corresponds to using a $K$-factor $\sigma_{NNLO}/sigma_{LO}=2.3$.
-%
-Let us note that resummed NNLO+NNLL calculations for Higgs pair production have also become available recently~\cite{deFlorian:2015moa},
-leading to a moderate enhancement as compared to the fixed-order NNLO calculation.
-
-\subsection{Background}
+\subsection{Backgrounds: QCD multijet and $t\bar{t}$ production}
 
@@
 %
-All background samples are generated with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, v2.1.1.
+All background samples are generated at leading-order
+with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, v2.1.1.
 %
-As in the case of the signal generation, the NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples.
-Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$.
+As in the case of the signal generation, the NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S(m_Z^2)=0.118$ is used for all samples.
+%
+Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ for all
+the samples.
 
-Samples!!!!
+We have considered all the relevant samples that can lead to the event
+being tagged as a $HH\to 4b$ candidate.
+%
+First of all QCD we have $4b$ multi-jet production of course.
+%
+But also we generate QCD $2b2j$ and $4j$ multi-jet samples,
+that can lead to the event being tagged in the case of multiple light
+jets being mistagged as $b$-quarks.
+%
+While the light jet mistag probability is small, we find that
+in general the $2b2j$ and $4j$ backgrounds cannot be neglected because
+of their large cross-sections and enhancement from combinatorics, that
+increase their contribution as compared to a naive estimate.
+%
+Neglecting the  $2b2j$ and $4j$ backgrounds is particularly
+important for the resolved and intermediate categories, but less
+so for the boosted one.
+%
+We don't include the NLO $K$-factor for the backgrounds but instead assume
+a given experimental overall systematic uncertainties common to all backgrounds.
 
-At the generation level the following basic cuts are applied.
+In addition to the QCD multijet, we also generate $t\bar{t}$ samples
+in the fully hadronic final state, which lead to a $2b4j$ signature that can
+contribute to the fake rates, and that has a similar topology that
+the corresponding QCD sample.
 %
-Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$.
-All final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
+We have used a value of the top quark mass of $m_t=173.2$ GeV.
+%
+Semileptonic decays of top quarks can be easily removed by requiring
+a lepton veto.
+
+At the generation level the following basic cuts are applied to
+background events.
+%
+Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
+in the central region with
+$| \eta | \le 3.0$.
+%
+In addition, at the matrix element level
+all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
 %
@@
 %
+
 Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.
+%
+First of all we see that the $t\bar{t}$ and QCD $4b$ samples are of
+the same order of magnitude.
+%
+The $bbjj$ cross-section is more than a factor 200 as compared to the
+$4b$ result, so in principle it should be subleading taking into
+account the mistag rate, but as we will show below,
+this is not true due to combinatoric.
+%
+ For top quark production, only the hadronic final state is generated.
+  %
+The $hh$ cross-section includes the NNLO $K$-factor.
 
@@
 \hline
-Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
+Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ (pb) \\
 \hline
 \hline
-$pp \to HH$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.729\times10^{-2}$ pb \\
+$pp \to HH$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $3.87\times10^{-2}$  \\
 \hline
 \hline
-$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.121 \times10^3$ pb \\
-$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.659 \times 10^5$ pb \\
-$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.709\times 10^6$ pb \\
-$pp \to t\bar{t}$ &  {\tt SHERPA}v2.1.1 & 3M & $2.514\times 10^3$ pb \\
+$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.121 \times10^3$  \\
+$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.659 \times 10^5$  \\
+$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.709\times 10^6$  \\
+$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.514\times 10^3$ \\
 \hline
@@
 \caption{\small Summary of signal and background samples generated in this work,
-together with the corresponding generator-level cross-section.} \label{tab:samples}
+  together with the corresponding generator-level cross-section.
+  %
+  For top quark production, only the hadronic final state is generated.
+  %
+The $hh$ cross-section includes the NNLO $K$-factor.  
+} \label{tab:samples}
 \end{center}
@@
 
-As a cross-check of the background cross-sections reported in Table~\ref{tab:samples}, we have produced multi-jet samples
+As a cross-check of the background cross-sections reported in Table~\ref{tab:samples}, we have produced leading order
+multi-jet samples
 using the {\tt MadGraph5\_aMC@NLO} program, and compared with the results for the same processes reported in
@@
 For comparison with the latter numbers, 
-we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV.
-%
-All jets must be within an acceptance of $|\eta| \le 2.5 $.
-%
-In the case of the samples with $b$ quarks in the final state, these requirements are extended to the appropriate number of $b$-jets.
-For example, in the 2$b$2$j$ sample there must be at least two $b$-jets that pass the cuts outlined above.
+we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV, and
+also that all jets must be within an acceptance of $|\eta| \le 2.5 $.
 %
@@
 backgrounds, so we can be confident that the set-up that we will use in this analysis is robust enough.
+
+Finally, let us discuss the smearing applied to signal
+and background samples.
+%
+It is beyond the scope of this work to perform a complete study of the impact of
+detector effects in this process.
+%
+However, it is still important to include some form of rough estimate of detector
+effects in the analysis, to properly estimate for example the impact
+of the Higgs mass window cuts.
+%
+In this work we simulate the finite momentum resolution of the ATLAS and CMS
+hadronic calorimeters by applying a Gaussian smearing to the four components
+of the four-momentum $p$, with mean zero and standard deviation $\Delta p$.
+%
+We take as baseline value a smearing of $\Delta p=5\%$, and in
+Sect.~\ref{sec:optimisation} we explore how our results change
+if a more optimistic or pessimistic value is assumed for the momentum
+resolution in the LHC detectors.

### 2015-07-06 paper/sec-mva.tex

@@
 %
-However, the attentive reader might have noticed that we have used
+however, the attentive reader might have noticed that we have used
 relatively 
@@
 technique in high energy physics.
-
-In order to investigate the potential efficacy of an MVA in an $HH\to 4b$
+%
+In order to investigate the potential efficacy of an MVA in an $hh\to 4b$
 measurement, we process the events remaining after the cut-based analysis 
-through a standard feed-forward artificial neural network with architecture
-
+through a feed-forward artificial neural network with architecture
 \be
@@
 \ee
-where $N_{\mathrm{par}}$ represents the number of input variables for the MVA.
-All neural-network layers use a sigmoid activation function, allowing for a probabilistic
+where $N_{\mathrm{var}}$ represents the number of input variables for the MVA.
+All neural-network layers use a sigmoid activation function, allowing
+for a probabilistic
 interpretation of the neural-network output.
 
-The input variables for the MVA differ between our three categories, based upon
-the availability in each analysis of substructure information on fat jets. For all
-three analyses, the following common variables are used:
-
-\begin{itemize}
-\item The transverse momenta of the leading and subleading Higgs candidates, $p_{T,H_0}$, $p_{T,H_1}$.
-\item The transverse momentum of the reconstructed Higgs pair, $p_{T,HH}$
-\item The invariant masses of the leading and sub-leading Higgs candidates, $m_{H,1}$, $m_{H,2}$.
-\item The invariant mass of the reconstructed Higgs pair, $m_{HH}$.
-\item The separation in $R$ of the two Higgs candidates, $\Delta R_{HH}$.
-\item The separation in $\phi$ of the two Higgs candidates, $\Delta \phi_{HH}$.
-\item The separation in $\eta$ of the two Higgs candidates, $\Delta \eta_{HH}$.
-\item The transverse momenta of the leading Higgs candidate subjets, $p_{T,H_{0,0}}$, $p_{T,H_{0,1}}$
-\item The transverse momenta of the sub-leading Higgs candidate subjets, $p_{T,H_{1,0}}$, $p_{T,H_{1,1}}$
-\end{itemize}
-
-For analyses including the reconstruction of fat jets, the following variables are included for
-every fat jet Higgs candidate present in the analysis.
-
-\begin{itemize}
-\item The $k_T$ splitting scale of the fat-jet (Reference).
-\item The ratio of 2-to-1-Subjetiness $\tau_{2}/\tau_{1}$ of the fat-jet (Reference).
-\item The fat-jet energy correlation function double-ratio $C_2$ (Reference).
-\item The fat-jet energy correlation function double-ratio $D_2$ (Reference).
-\end{itemize}
-
-Therefore there are in total $N_{\mathrm{var}}=13$ variables for the resolved analysis, 17 for the semi-resolved, and 21 for the boosted category.
-
-Given the above set of kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ as the probability that the event $i$ originates from the signal process,
+Given a set of $N_{\mathrm{var}}$  kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ as the probability that the event $i$ originates from the signal process,
 \be y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} ), \ee
@@
 \ee
- Correspondingly the negative log-likelihood cost function to be used in the neural network training is the cross-entropy error
-\be E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right) = \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)}. \ee
+ Correspondingly the negative log-likelihood cost function to be used in the neural network training is the cross-entropy error, defined as
+ \bea
+ E(\{\omega\}) &=& -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right)\nonumber\\
+ &=&
+ \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)} \, ,
+ \label{cross-entropy}
+ \eea
+ where $N_{\text{evt}}$ is the number of
+ Monte Carlo events that we have generated.
 
-Using the cross-entropy cost function, the neural networks are trained with a basic genetic algorithm (GA) over 50,000 generations.
-(Do we need to specify GA params etc?).
+ The training of the neural networks consist on the
+ minimization of the cross-entropy error,
+ Eq.~\ref{cross-entropy}, which is achieved using a
+ Genetic Algorithm.
+ %
+ Since given the large number of events the probability of
+ over-fitting is tiny, we just train the MVA for a very long
+ number of generations, in this case $N_{\rm gen}=50k$.
+ %
+ We have verified that if a larger number of generations
+ are used the results are unchanged.
+
+ \subsection{MVA input}
+
+ To identify the most discriminatory variables, we have to train
+ the MVA using a large number of kinematic distributions for
+ signal and background events.
+%
+In our $hh\to 4b$ case,
+the input variables for the MVA differ between our three categories,
+since in the case of large-$R$ jet reconstruction we want to exploit
+the richness of substructure information.
+
+For the three categories, boosted, intermediate and resolved,
+the following common variables are used as input to the MVA
+\begin{itemize}
+\item The transverse momenta of the leading and subleading Higgs candidates, $p_{T,h_1}$, $p_{T,h_2}$.
+\item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$
+\item The invariant masses of the leading and sub-leading Higgs candidates, $m_{h,1}$, $m_{h,2}$.
+\item The invariant mass of the reconstructed Higgs pair, $m_{hh}$.
+\item The separation in $R$ of the two Higgs candidates, $\Delta R_{hh}$.
+\item The separation in $\phi$ of the two Higgs candidates, $\Delta \phi_{hh}$.
+\item The separation in $\eta$ of the two Higgs candidates, $\Delta \eta_{hh}$.
+\item The transverse momenta of the leading Higgs candidate subjets, $p_{T,h_{1,1}}$, $p_{T,h_{1,2}}$
+\item The transverse momenta of the sub-leading Higgs candidate subjets, $p_{T,h_{2,1}}$, $p_{T,h_{2,1}}$
+\end{itemize}
+Note that in the case of a large-$R$ jet, the subjets are defined
+with the anti-$k_t$ algorithm with $R=0.3$.
+%
+In the resolved case, the subjets are instead replaced by the two
+small-$R$ jets that constitute each Higgs candidate.
+
+For analyses involving the use of large-$R$ jets,
+namely for the boosted and intermediate categories,
+the following variables are included for
+every large-$R$ jet,
+we use in addition a number of substructure variables~\cite{Aad:2013gja},
+in particular:
+\begin{itemize}
+\item The $k_T$ splitting scale~\cite{Butterworth:2008iy}
+\item The ratio of 2-to-1-Subjetiness $\tau_{2}/\tau_{1}$~\cite{Thaler:2010tr}
+\item The energy correlation function double-ratio $C_2$~\cite{Larkoski:2013eya}
+\item The energy correlation function double-ratio $D_2$~\cite{Larkoski:2013eya}
+\end{itemize}
+The implementation of all these substructure variables follows
+closely the original ATLAS implementation summarized in Ref.~\cite{Aad:2013gja}.
+
+Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the resolved analysis, 17 for the semi-resolved, and 21 for the boosted category.
+%
+Given that the MVA is able to identify the most discriminatory variables
+and to ignore those that have smaller effect, it is advantageous to
+include as many substructure variables as possible.
+
 \subsection{Enhancing signal discrimination with the MVA}
@@
 %
-Here we see that there is a more even distributions of weights, in that many
+here we see that there is a more even distributions of weights, in that many
 variables help in a similar amount in the discrimination.
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{plots/tau21_H0_res_C1_boost.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_H0_res_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_res_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_res_C1_boost.pdf}
   \caption{\small Left plot: subjetiness.
@@
 To investigate this, we now consider a variant of the analysis used in
-Table  where the $m_H$ window criterion has been relaxed to $80 < m_H < 170$.
+Table  where the $m_h$ window criterion has been relaxed to $80 < m_h < 170$.
 %
-Firstly the same analysis is repeated with the larger $m_H$ window, with no smearing at all.
+Firstly the same analysis is repeated with the larger $m_h$ window, with no smearing at all.
 %

### 2015-07-07 paper/sec-analysis.tex
work on paper

@@
 different categories according to the event topology.
-
+%
 First of all we discuss the settings and nomenclature that
@@
 
-In our analysis we will use different types of jet definitions,
-depending of the type of analysis that needs to be performed.
+In our study we will use different types of jet definitions,
+depending of the type of analysis that needs to be performed, optimized
+for the various possible event topologies.
 %
@@
   When reconstructing small-$R$ jets, we will keep only
-  those with transverse momentum $p_T \ge 40$~GeV
+  those jets with transverse momentum $p_T \ge 40$~GeV
   and pseudo-rapidity $|\eta|<2.5$ within the central
   acceptance of ATLAS and CMS, jets that fail to satisfy these
-  conditions are discarded
-
-  They are required to have $p_T > 50$~GeV and $|\eta|<2.5$.
+  conditions are discarded.
+  %
 
@@
   In addition to the basic $p_T$ and $\eta$
-  selection requirements, large-$R$ jets should also
+  acceptance requirements, large-$R$ jets should also
   satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
@@
   %
-  Before the mass-drop tagger is applied, the large-$R$ jet
+  As required, before the mass-drop tagger is applied, the large-$R$ jet
   constituents are reclustered with the Cambridge/Aachen
@@
   %
+  Small-$R$ subjets are required to have $p_T > 50$~GeV and $|\eta|<2.5$,
+  else they are discarded.
+
   \end{itemize}
@@
 
-Given the final state that needs to be reconstructed, the
+Given the final state that needs to be reconstructed in our case, the
 optimisation of the $b$-tagging capabilities of the
-LHC experiments is an essential requirement.
+LHC experiments is an essential requirement to optimise
+the prospects for the observation of Higgs pair production.
 %
@@
 we also comment on the differences and similarities with the
-corresponding CMS strategy.
+corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}.
 %
@@
   %
-  Note that the probability of tagging a jet is not increased
+  Note that the probability of tagging a jet is not modified
   if more than one $b$-quark is found among the jet constituents.
+
+  We only attempt to $b$-tag the four (two) hardest small-$R$ jets
+  in the resolved (intermediate) category.
+  %
+  We find that
+  trying to $b$-tag all
+  small-$R$ jets that satisfy the acceptance cuts worsens the performance
+  due to combinatorics.
 
@@
 
-The basic idea of this work is the same as in Ref.~\cite{Gouzevitch:2013qca}:
-rather than selecting only a specific event topology, such as boosted
+The basic idea of this work is similar to that in Ref.~\cite{Gouzevitch:2013qca}:
+rather than concentrating only a specific event topology, such as boosted
 or resolved, we aim to consistently combine the information from
@@
 a exclusive categorisation is defined starting from the topology
-where the signal significance is the largest.
+where the signal significance is the best.
 
@@
 
-  A given event is assigned to the boosted category if it
+  A given event is assigned to the {\it boosted} category if it
   contains at least two large-$R$ jets, defined as above,
-  and of the tow leading large-$R$ jets have been double-$b$-tagged.
+  and where  the two leading large-$R$ jets have been
+  successfully double-$b$-tagged.
   %
- Therefore, each of these two large-$R$ $b$-tagged jets correspond to the
+ Therefore, each of these two large-$R$ double-$b$-tagged jets corresponds to the
  decay products of one Higgs boson candidate.
@@
 
-  An event is assigned to the intermediate category if
-  at least one large $R$ $b$-tagged jet is present.
+  An event is assigned to the {\it intermediate} category if
+  at least one large $R$ double-$b$-tagged jet is present.
   %
@@
   %
-  The small-$R$ jets must be $b$-tagged as well.
-  %
+  These small-$R$ jets must be $b$-tagged as well.
+
   Then, the second Higgs boson candidate is reconstructed
-  by selecting the two small-$R$ jets that minimize the difference
-  between the invariant mass of the large-$R$ jet, $m_{lR}$,
+  by selecting the two $b$-tagged small-$R$ jets that minimize the difference
+  between the invariant mass of the large-$R$ jet, $m_{lR_1}$,
   with the invariant mass of the sum of the two small-$R$ jets,
   $m_{sR_1+sR_2}$, that is, ${\rm min}\lp m_{lR} -
-  m_{sR_1+sR_2}\rp$.
+  m_{sR_1+sR_2}\rp$, where $lR_1$ indicates the leading large-$R$ jet
+  and $sR_1$ and $sR_2$ indicate the small-$R$ jets.m
 
@@
 
-  Finally, let us define the resolved category.
+  Finally, let us define the {\it resolved} category.
   %
@@
 \end{itemize}
+Note that in principle these three categories are not exclusive:
+a given even can be assigned to more than one category, for
+example, satisfying both the requirements of the boosted and resolved
+categories at the same time.
 
-In addition, events from each category need to satisfy the usual
+Once a pair of Higgs boson candidates has been identified,
+then events from each category are required to satisfy the usual
 Higgs mass window cut, defined by
@@
 We note that this cut is substantially looser as the corresponding
-cut used in the ATLAS and CMS $h\to b\bar{b}$ analysis: the motivation
-for this is that the MVA will take care of the optimisation of each cut.
+cut used in the typical ATLAS and CMS $h\to b\bar{b}$
+analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
+for this is that the MVA will take care of the optimisation of these
+and other cuts that are not explicitly performed.
 
@@
 %
-We emphasize that each category is not exclusive of the others,
+We emphasize again that each category is not exclusive of the others,
 and in general there can be a substantial overlap
 between the different categories.
+%
+In particular, this overlap is a direct consequence that
+the different categories are optimised separately, as opposed
+to the approach of~\cite{Gouzevitch:2013qca}, where optimisation
+was performed simultaneously in the combination of exclusive categories.
 
@@
     &  & and 2 single-$b$-tags  &  \\
+       & $\ge 2$ small-$R$ subjets  & &  \\
+    &  $p_T^{\rm sj}\ge 50$ GeV &   &  \\
     \hline
@@
     work, together with the corresponding basic kinematical cuts.
+    %
+    The categories are not exclusive, and each event can satisfy the
+    requirements of more than one category at the same time.  
 \label{sec:categorisation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+As we will show now, the selection requirement and the kinematic cuts
+for each of the categories in Table~\ref{sec:categorisation} have
+been optimised independently.
+%
+First of all we have performed a inclusive analysis, and optimised
+$S/\sqrt{B}$ in each of the three categories separately, including
+the MVA.
+%
+We find that, in terms of signal significance, the ordering of
+the categories is
+\begin{enumerate}
+\item Boosted 
+\item Intermediate
+  \item Resolved
+  \end{enumerate}
+and therefore for the final analysis we turn to an exclusive approach:
+if an event satisfies the boosted requirements, it is kept for
+these category, else we check if it suits the intermediate
+requirements, and failing also this, the event is attempted
+in the resolved categories.
+%
+The resulting exclusive event samples are then separately processes
+through the MVA, as discussed in the next section.
+%
+This allows us to combine the significance of the dominant topology
+(boosted) with that of the sub-leading categories, intermediate
+and resolved.
 

### 2015-07-07 paper/sec-analysis.tex
analysis section

@@
 
-\subsection{Kinematic distributions}
+\subsection{Cut optimisation}
 
-We now justify some of the cuts that we are using.
+In this section we motivate the various
+kinematical cuts for the various categories.
 %
-As mentioned before, the cuts in each category are separately
-optimised in an inclusive analysis: it is only we have determined
+As mentioned before, the cuts in each category have been separately
+optimised in an inclusive analysis: it is only once we have determined
 which is the dominant category that the analysis is made exclusive.
 %
-We begin with the boosted category.
+In this work, the results for each category have been derived
+from the inclusive analysis,
+and we show the various kinematic distributions immediately
+below the corresponding cut has been applied.
+
+In this section we only show a representative subset of
+all available kinematic distributions, the complete
+set of comparison plots can be found in the following
+webpage:
+\begin{center}
+\url{http://www2.physics.ox.ac.uk/HH4b}
+  \end{center}
+In this webpage we also show the distribution of all
+kinematic variables, including jet substructure variables,
+which we don't cut explicitly but that are provided as
+input to the multivariate analysis.
 %
-In Fig.~\ref{fig:cutplots1} we show
+Also, we show here results for the boosted and resolved categories,
+a comparison which allows to understand the cuts used for the
+intermediate category as well.
+
+\subsubsection{Boosted category}
+
+We begin with the boosted category, which is the one that leads
+to a higher signal significance.
+%
+First of all,
+in Fig.~\ref{fig:cutplots1} we show
 the $p_T$ distribution of the
@@
 As explained above, in the boosted category we also require the two
-leasing subjets of the large-$R$ jet to be relatively
-hard.
+leading subjets of the large-$R$ jet to be relatively
+hard, in particular that should satisfy $p_T \ge $ 50 GeV.
 %
-In Fig ... we show the distribution in $p_T$ of the leading
-and subleading jets.
+To motivate this cut, in Fig ... we show the distribution in $p_T$ of the leading
+and subleading sub-jets in the leading large-$R$ jet in events
+of the boosted category.
 %
-It is clear from the comparison that
+It is clear from the comparison that the subjet $p_T$ spectrum is
+relatively harder in the signal with respect to the background,
+motivating our cut.
+
+{\bf missing plots: pt subjet distribution}
+
+\subsubsection{Resolved category}
 
@@
 %
-In Fig. we show ....
-
+In Fig. we show the distribution in $p_T$ of the four leading
+small-$R$ jets in signal and background events.
+%
+We see that the third and four leading jets are relatively soft.
+%
 Also, it is useful to show the distribution in rapidity of the
@@
 
-Finally, we show in
+{\bf missing plots: pt jet distribution, rapidity distribution}
+
+Next, we show in
 Fig.~\ref{fig:mhh} the invariant mass distribution of the Higgs pairs,

### 2015-07-07 paper/sec-analysis.tex
work on the paper

@@
   constituents are reclustered with the Cambridge/Aachen
-  algorithm.
+  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}.
 
@@
 \subsection{Event categorisation and cut flow}
+\label{sec:categorisation}
 
@@
 \be
+\label{higgsmasswindow}
 |m_{h,j} - 125| < 40~{\rm GeV} \, , j=1,2 \, ,
@@
     requirements of more than one category at the same time.  
-\label{sec:categorisation}
+\label{sec:categorisationTable}
   }
@@
 As we will show now, the selection requirement and the kinematic cuts
-for each of the categories in Table~\ref{sec:categorisation} have
+for each of the categories in Table~\ref{sec:categorisationTable} have
 been optimised independently.

### 2015-07-07 paper/sec-mcsamples.tex
work on the paper

@@
 account.\footnote{We thank Eleni Vrodynou for assistance here.}
+%
+This tailored {\tt MadGraph5\_aMC@NLO} model  simulates
+gluon-gluon-fusion Higgs boson pair production including the effects
+of the
+exact form factors for the top triangle and box loops at leading
+order, obtained from~\cite{Plehn:1996wb}.\footnote{Note that since recently it is possible to compute also
+loop-induced processes as well without the need of special
+models~\cite{Hirschi:2015iia}.}
 %

### 2015-07-07 paper/sec-mva.tex
work on the paper

@@
 and combining the significance of the different event categories,
-we end up with a $S/\sqrt{B}$ value of AAA.
+we end up with a $S/\sqrt{B}$ value around $1.2$.
 %
-Taking into account our more realistic simulation of the QCD background as
-compared to previous studies, this is not too bad.
+This is not enough to claim observation in this channel.
 %
@@
 Multivariate techniques are by now a common tool to enhance signal
-significance in HEP analysis.
+significance in HEP analysis, and rightly so,
+since they open a new window to improve the performance
+of many physics analysis and searches.
+%
+For instance, the UCL $hh\to 4b$ analysis~\cite{Wardrope:2014kya}
+uses a Boosted
+Decision Tree MVA to improve signal discrimination.
 
-\subsection{MVA strategy}
+\subsection{MVA strategy: deep neural networks}
 
@@
 background processes via the use of a multivariate analysis is a common
-technique in high energy physics.
+technique in high energy physics~\cite{Baldi:2014pta,Wardrope:2014kya}.
 %
-In order to investigate the potential efficacy of an MVA in an $hh\to 4b$
-measurement, we process the events remaining after the cut-based analysis 
-through a feed-forward artificial neural network with architecture
+In our work we use a specific type of  MVA to
+disentangle signal and background events in the $hh\to 4b$ process,
+in particular we use a feed-forward artificial neural network (ANN).
+%
+The basic idea is that the ANN is given both all MC signal and background
+events which satisfy the basic selection cuts {\bf C1}, allowing to identify
+which are the most relevant variables to discriminate between the two.
+
+In this work, the ANN that we use has the following architecture.
 \be
@@
 for a probabilistic
-interpretation of the neural-network output.
+interpretation of the neural-network output, including in the final layer.
+%
+In Fig.~\ref{fig:nnarch} we show an example of the ANN that we use in this work, corresponding here
+to the case of the resolved category.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+      \vspace{-1cm}
+  \includegraphics[width=0.80\textwidth]{plots/res_nnarch.pdf}
+  \vspace{-1cm}
+\caption{\small Architecture of the ANN used for the analysis of the resolved
+  category, with $N_{\rm var}=13$ input variables and thus the same number of neurons
+in the first layer.}
+\label{fig:nnarch}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-07 paper/sec-results.tex
work on the paper

@@
 
-\section{Cut-based analysis results}
+\section{Results for the cut-based analysis}
 
@@
 In this section we discuss the results of the traditional
-cut-based analysis, using the strategy presented in the previous
+cut-based analysis, using the analysis strategy presented in the previous
 section.
@@
 is modified if only the $4b$ QCD background is taken into account,
-but the $2b2j$ and $jjjj$ backgrounds are neglected, as done
-in previous work.
+but the $2b2j$ and $jjjj$ backgrounds are neglected.
 %
@@
 
-We now study the basic results of our cut based analysis, with
-all backgrounds properly taken into account.
+First of all we compare the cross-sections at various
+analysis levels for the three categories, for signal and background,
+by providing a detailed cut-flow.
+%
+Here we consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
+and below we discuss how results are modified if only the $4b$
+multijet background is used.
+%
+In particular,
+we consider the following levels of the cut-flow
+\begin{itemize}
+\item {\bf C0}: cross-sections at the generator
+  level, before any analysis cuts.
+\item {\bf C1}:  cross-sections after the basic jet acceptance selection
+  cuts, but before $b$-tagging.
+\item {\bf C2}: cross-sections after after the $b$-tagging.
+\end{itemize}
+Note that {\bf C1} already includes the effect of the Higgs mass
+window cut, Eq.~(\ref{higgsmasswindow}).
+%
+Of course at the {\bf C0} level the numbers will be the same
+for the three individual categories.
 
-We begin by showing the cut-flow at various levels of the analysis.
-%
-Here we consider all backgrounds at the same time, and below
-we comment on the role of the individual backgrounds.
-
-We consider the following levels of the cut-flow
-\begin{itemize}
-\item {\bf C0}: these are the cross-sections at the generator
-  level, before any analysis cuts
-\item {\bf C1}: results after the basic jet selection
-  and related cuts, but before $b$-tagging.
-\item {\bf C2}: results after the $b$-tagging, but
-  before applying the invariant mass window cut
-\item {\bf C3}: final results of the cut-based
-  analysis
-  \end{itemize}
-We consider the results for the individual categories, using the
-exclusive priorisation discussed in the previous section.
+In the following, results are presented for the exclusive
+categorisation, as discussed in Sect.~\ref{sec:categorisation}.
 %
@@
 an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
+as well as 
 the signal significance $S/\sqrt{B}$ and the signal
@@
 %
-Results are shown both for the signal and for all backgrounds
-combined.
-%
-The results for the three categories have been collected in
-Table~\ref{table:cutflow}.
-
 We emphasize that it is important not only to achieve a good signal
@@
 systematic uncertainty would be required.
-
-Let's begin with the discussion of the boosted category, that as we have explained
-is the one that benefits from a higher signal significance.
-%
-We see that after all the cuts, including $b$-tagging,
-we end up with almost 200 signal events at the HL-LHC, and
-still a substantial background of around $40k$ events.
-%
-The signal significance is around one at the end of the
-cut-based analysis.
-%
-Note that it is easy to compute the corresponding numbers
-for the end of Run II at the LHC with
-$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: we have only
-19 signal events, and the signal significance drops down to
-$S/\sqrt{B}\sim 0.3$.
-%
-We will discuss in the next section what are the Run II prospects
-once we include the effects of the MVA in the analysis.
 
@@
 
+The results for the three categories have been collected in
+Table~\ref{table:cutflow}.
+%
+Let us begin with the discussion of the boosted category, that as we have explained
+is the one that benefits from a higher signal significance.
+%
+We see that after all the cuts, including $b$-tagging,
+we end up with almost 200 signal events at the HL-LHC, and
+still a substantial background of around $40k$ events.
+%
+The signal significance is around 1.0 at the end of the
+cut-based analysis.
+%
+While it should have been possible to increase this significance
+but using more aggressive cuts, we have refrained doing so
+since we prefer this optimisation to per performed by
+the MVA.
+
+Note that from the results of Table~\ref{table:cutflow}
+it is easy to compute the corresponding numbers
+for the end of Run II at the LHC with
+$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: in the boosted category,
+we have only
+19 signal events, and the signal significance drops down to
+$S/\sqrt{B}\sim 0.3$.
+%
+We will discuss in the next section what are the Run II prospects
+once we include the effects of the MVA in the analysis, but
+it is clear already at this level that, unless rates are
+increased by new BSM dynamics, one really needs the full
+integrated luminosity of the HL-LHC to be able to observe
+the Higgs pair production process.
+
 Both the intermediate and resolved categories benefit from higher signal yields,
@@
 
-From the results of Table~\label{table:cutflowboosted}
+From the results of Table~\ref{table:cutflow}
 we see that after the cut-based analysis, the significance of the Higgs pair production
-observation in the $4b$ channel using the boosted topology is ... and that the combination
-of the boosted, intermediate and resolved categories gives ....
+observation in the $4b$ channel using the boosted topology
+is $S/\sqrt{B}=0.99$,
+and that the combination
+of the boosted, intermediate and resolved categories gives a slightly higher
+value, around 1.20.
 %
-We discuss in the next section of this significance can be enhanced by means
+We discuss in the next section how this significance can be enhanced by means
 of multivariate analysis.
@@
 
-We now compare with two recent studies that have also studied the
+The feasibility of Higgs pair production at the HL-LHC in different
+final-state channels
+has been explored various groups~\cite{Baur:2003gp,Barger:2013jfa,
+  Baur:2003gpa,Barr:2013tda,Dolan:2013rja,
+  Dolan:2012rv,Papaefstathiou:2012qe,Gouzevitch:2013qca,Cooper:2013kia,Wardrope:2014kya,deLima:2014dta}, though
+the $4b$ final state has received less attention than other final states,
+due to the complexity of disentangling the signal over the large
+QCD multijet background.
+%
+Now we compare with two recent studies that have also studied the
 feasibility of SM Higgs pair production in the $4b$ final state,
@@
 
-{\bf paragraph about UCL strategy}
+First of all let us briefly summarize these two studies.
+%
+In the UCL group study~\cite{Wardrope:2014kya} is based
+on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
+in the central acceptance with $p_T \ge 40$ GeV, which are
+then used to form dijets (Higgs candidates) with
+$p_T \ge 150$ GeV, $85 \le m_{\rm dijet} \le 140$ GeV
+and $\Delta R \le 1.5$ between the two jets that form
+each dijet system.
+%
+In addition to the basic selection cuts, a large number
+of additional variables are combined using a
+Boosted Decision Tree (BDT) discriminant.
+%
+This study considers the $b\bar{b}b\bar{b}$ and
+$b\bar{b}c\bar{c}$ QCD multijets as well as
+$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$.
+%
+Their final significance is found to the $S/\sqrt{B}=2.1$ at the HL-LHC.
 
-{\bf paragraph about Durham strategy}
+The Durham group study~\cite{deLima:2014dta} requires events
+to have two $R=1.2$ C/A jets with $p_T\ge 200$ GeV, with
+two $b$-tagged subjets inside each large-$R$ jet with
+$p_T \ge$ 40 GeV.
+%
+To improve the signal over background separation, both the BDRS
+method and the Shower Deconstruction (SD)~\cite{Soper:2011cr,Soper:2012pb}
+technique are applied.
+%
+The background considered are QCD $4b$ as well as $Zb\bar{b}$, $hZ$ and
+$hW$, but no $t\bar{t}$, $2b2j$ or $4j$.
+%
+At the HL-LHC, the best performance is obtained by requiring two
+SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\sim 2.1$,
+with BDRS similar but slightly inferior performance.
+%
+Therefore, both the Durham and the UCL groups conclude that a signal
+significance $S/\sqrt{B}$ slightly above two can  be obtained
+in this channel at the HL-LHC.
 
-In order to compare with previous results, it is interesting to
-study how our results change if we consider only the QCD $4b$
+Since we find that the $2b2j$ and $4j$ backgrounds cannot
+be neglected, and previous works did not considered them,
+it is interesting to
+study how our results are modified if we consider only the QCD $4b$
 multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
@@
 %
-For the boosted category, the results are shown in
+These results are shown in
 Table~\ref{table:cutflow4B}, which is the analog of
@@
 %
-In the intermediate category, the signal significance is now much better, with $S/sqrt{B}$ increasing from
+In the intermediate category, the signal significance is now much better, with $S/\sqrt{B}$ increasing from
 0.5 with all the backgrounds to $1.57$ if only $4b$ are accounted for, a factor 3 improvement.
@@
 important category, the boosted category, the results are relatively stable.
+%
+Moreover, we find that the effect of the multijet fake background is of
+the same size of the higher-order QCD corrections to $4b$ production~\cite{Binoth:2009rv}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In summary, we find that the results of our cut-based analysis are roughly
+consistent with the results of previous related studies.
+%
+As we show next, once the MVA is used, we manage to outperform these previous
+works.

### 2015-07-07 paper/plotscripts/plotMVAdat.py

@@ -131,7 +131,7 @@ for idat in xrange(0,len(datafiles)):
 			sigprob.append( float(line.split()[3]) )
 
 	#### ROC Curve and S/B plot
-	thresholds = numpy.linspace(0, 1, 150)
+	thresholds = numpy.linspace(0, 1, 5)
 	falsepos = []
 	truepos = []
 

### 2015-07-07 paper/sec-mva.tex
work on MVA section

@@
 
-Given a set of $N_{\mathrm{var}}$  kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ as the probability that the event $i$ originates from the signal process,
-\be y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} ), \ee
+The training of the ANN for the signal/background classification task
+proceeds as follows.
+%
+Given a set of $N_{\mathrm{var}}$  kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ (that is, the activation state of the
+neuron in the last layer)
+as the probability that the event $i$ originates from the signal process,
+\be
+y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} )\, ,
+\ee
 where $y_i^\prime$ represents the true classification of the event $i$, i.e $y^\prime_{\text{signal}} = 1$ and $y^\prime_{\text{background}} = 0$.
@@
 \be
-P(y_i^\prime|\{k\}_i, \{\omega\}) = y_i^{y^\prime_i}(1-y_i)^{1-y^\prime_i}.
+P(y_i^\prime|\{k\}_i, \{\omega\}) = y_i^{y^\prime_i}(1-y_i)^{1-y^\prime_i} \, ,
 \ee
- Correspondingly the negative log-likelihood cost function to be used in the neural network training is the cross-entropy error, defined as
+which implies that the  negative log-likelihood cost function
+that needs to be minimized during the ANN training is 
+the cross-entropy error, defined as
  \bea
@@
  Monte Carlo events that we have generated.
+ %
+ The ANN is trained both on the signal and background MC events,
+ in each case using the information $y_i'$ of the true nature
+ of the event.
+ %
+ To be stable against statistical fluctuations, it is important to use
+ a large enough MC sample both of signal and of background events
+ for the MVA training.
 
- The training of the neural networks consist on the
+ Therefore, the training of the neural networks consist on the
  minimization of the cross-entropy error,
- Eq.~\ref{cross-entropy}, which is achieved using a
+ Eq.~\ref{cross-entropy}, which in this work is achieved using a
  Genetic Algorithm.
@@
  are used the results are unchanged.
+ %
+ We have also verified that using a cross-validation stopping
+ criterion as in the NNPDF3.0 fits does not affect the results.
 
- \subsection{MVA input}
+ \subsection{Input kinematical variables for the MVA}
 
@@
 For the three categories, boosted, intermediate and resolved,
-the following common variables are used as input to the MVA
+the following common variables are used as input to the MVA:
 \begin{itemize}
-\item The transverse momenta of the leading and subleading Higgs candidates, $p_{T,h_1}$, $p_{T,h_2}$.
+\item The transverse momenta of the leading and subleading Higgs, $p_{T,h_1}$ and $p_{T,h_2}$.
 \item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$
-\item The invariant masses of the leading and sub-leading Higgs candidates, $m_{h,1}$, $m_{h,2}$.
+\item The invariant masses of the leading and sub-leading Higgs candidates, $m_{h,1}$ and $m_{h,2}$.
 \item The invariant mass of the reconstructed Higgs pair, $m_{hh}$.
-\item The separation in $R$ of the two Higgs candidates, $\Delta R_{hh}$.
-\item The separation in $\phi$ of the two Higgs candidates, $\Delta \phi_{hh}$.
-\item The separation in $\eta$ of the two Higgs candidates, $\Delta \eta_{hh}$.
-\item The transverse momenta of the leading Higgs candidate subjets, $p_{T,h_{1,1}}$, $p_{T,h_{1,2}}$
-\item The transverse momenta of the sub-leading Higgs candidate subjets, $p_{T,h_{2,1}}$, $p_{T,h_{2,1}}$
+\item The separation in $R$ between the two Higgs candidates, $\Delta R_{hh}$.
+\item The separation in $\phi$  between the two Higgs candidates, $\Delta \phi_{hh}$.
+\item The separation in $\eta$  between the two Higgs candidates, $\Delta \eta_{hh}$.
+\item In the boosted category,
+  the transverse momenta of the leading, $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and
+  sub-leading, $p_{T,h_{2,1}}$ and $p_{T,h_{2,1}}$, Higgs candidate subjets.
+  %
+  In the resolved category instead, we use the transverse momenta $p_{T,i}$ of the four leading 
+   $b$-tagged small-$R$ jets in the event. 
 \end{itemize}
-Note that in the case of a large-$R$ jet, the subjets are defined
-with the anti-$k_t$ algorithm with $R=0.3$.
-%
-In the resolved case, the subjets are instead replaced by the two
-small-$R$ jets that constitute each Higgs candidate.
+Therefore, we have a total of 13 variables which are common to the three categories.
 
@@
 namely for the boosted and intermediate categories,
-the following variables are included for
-every large-$R$ jet,
-we use in addition a number of substructure variables~\cite{Aad:2013gja},
-in particular:
+a number of jet substructure variables~\cite{Aad:2013gja} is used
+for every large-$R$ jet that is used for the Higgs reconstruction.
+%
+In particular we include in the MVA training for each large-$R$ jet
 \begin{itemize}
-\item The $k_T$ splitting scale~\cite{Butterworth:2008iy}
-\item The ratio of 2-to-1-Subjetiness $\tau_{2}/\tau_{1}$~\cite{Thaler:2010tr}
-\item The energy correlation function double-ratio $C_2$~\cite{Larkoski:2013eya}
-\item The energy correlation function double-ratio $D_2$~\cite{Larkoski:2013eya}
+\item The $k_T$ splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}.
+
+  This variable is defined by reclustering the constituents of a jet with the
+  $k_t$ algorithm, which usually clusters last the harder constituents, and then
+  taking the $k_t$ distance measure between the two subjets at the final stage of the recombination
+  \be
+\sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, ,
+\ee
+where one can also define related variables like $\sqrt{d_{23}}$ that corresponds to the
+splitting scale in the second-to-last clustering.
+
+\item The ratio of 2-to-1-Subjetiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
+
+  The $N$-subjettiness variables $\tau_N$ are defined by clustering the constituents
+  of a jet with the exclusive $k_t$ algorithm and requiring that $N$ subjets are found,
+  \be
+  \tau_N \equiv \frac{1}{d_0} \sum_k p_{T,k}\cdot {\rm min}\lp \delta R_{1k}, \ldots,
+  \delta R_{Nk}\rp \, , \qquad d_0\equiv \sum_k p_{T,k}\cdot R \, ,
+  \ee
+  with $ p_{T,k}$ the $p_T$ of the constituent $k$ and $\delta R_{ik}$ the distance from
+  subjet $i$ to constituent $k$.
+  %
+  In this work in particular we use as input to the MVA
+  \be
+\tau_{21} \equiv \frac{\tau_2}{\tau_1} \, ,
+  \ee
+  which provide good discrimination between QCD jets and jets arising from the decay of
+  a heavy resonance.
+
+\item The energy correlation function double-ratios $C_2$ and $D_2$~\cite{Larkoski:2013eya}.
+
+  The energy correlation double ratio $C_2$ is defined
+  as
+  \be
+C_2^{\beta} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{{\rm ECF}(2,\beta)} \, ,
+  \ee
+  where the energy correlation functions ${\rm ECF}(3,\beta)$ are defined
+  in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
+  are sensitive to $N$-prong substructure.
+
 \end{itemize}
-The implementation of all these substructure variables follows
-closely the original ATLAS implementation summarized in Ref.~\cite{Aad:2013gja}.
-
-Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the resolved analysis, 17 for the semi-resolved, and 21 for the boosted category.
+%
+Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the resolved analysis,
+17 for the semi-resolved, and 21 for the boosted category.
 %
@@
 include as many substructure variables as possible.
+%
+As we will show, the use of substructure variables in the MVA is the key to increase the signal
+significance in the boosted category.
 
-\subsection{Enhancing signal discrimination with the MVA}
+\subsection{Enhancing signal discrimination with MVA}
 
-Now we show the results of the MVA training on the signal and
-background samples.
+Let us now present the results of the MVA applied to the event samples
+that satisfy the cut-based analysis discussed in the previous section.
 %
-First of all in Fig.~\ref{fig:nnresponse} we show
-the neural network classification of events is demonstrated for both the resolved and boosted cases.
+First of all in Fig.~\ref{fig:nnresponse} we show the distribution of
+the ANN output, after the training for signal and background events, for the three
+exclusive categories.
 %
-In this figure, we show which is the distribution of the neural network
-response, that is, the value of the outer layer in Eq.~(\ref{eq:nn1}),
-for signal and background events.
+All distributions have been normalized, so that their integral
+  adds up to one.
 %
-For the MVA discrimination to be successful, one needs to find
-distinct distributions for the two types of events.
-%
-As can be seen from  Fig.~\ref{fig:nnresponse}, both
-in the boosted and in the resolved cases signal and background
-distributions are noticeably different: we can use this property
-to introduce the final cut in our analysis, a cut in the value
-of the neural network output.
+Given that the final separation between signal and background will be achieving by introducing
+a cut in the ANN output, the more separated that the two distributions are, the more efficient
+the MVA discrimination will be.
 
@@
 \begin{center}
-\includegraphics[width=0.48\textwidth]{plots/resolved_MVA_hist.pdf}
-\includegraphics[width=0.48\textwidth]{plots/boosted_MVA_hist.pdf}
-\caption{\small Neural network response demonstrated for the case of the resolved (left) and boosted (right) analyses.
-The frequency of background and signal events is plotted as a function of neural network output.
-{\bf what is the y axis??}
+\includegraphics[width=0.65\textwidth]{plots/Boosted_disc.pdf}
+\includegraphics[width=0.48\textwidth]{plots/Intermediate_disc.pdf}
+\includegraphics[width=0.48\textwidth]{plots/Resolved_disc.pdf}
+\caption{\small The distribution as a function of the ANN output
+  for the signal and background MC events in the three categories:
+  boosted (upper plot), intermediate (lower left plot) and
+  resolved (lower right plot).
+  %
+  All distributions are normalized so that their integral
+  adds up to one.
 }
@@
 
-The result of the signal selection efficiency as a function of the
-background rejection rate as the value on the cut on the NN output
-is varied is known as the Receiver Operating Characteristic (ROC)
+From Fig.~\ref{fig:nnresponse} we see that in the boosted category the MVA manages
+to achieve a clear discrimination between signal and background, with the two distributions
+nicely peaking at 1 and at 0 respectively.
+%
+This indicates that introducing a suitable cut in the ANN output will substantially reduce the background,
+while keeping a reasonable signal efficiency.
+%
+The performance of the MVA discrimination is similar though slightly worse in the intermediate
+category, and it is markedly worse in the resolved category.
+%
+We have traced back these differences to the use of jet substructure variables
+in the boosted and intermediate categories, which induce the maximum
+discrimination between signal and background events.
+
+The results for the signal selection efficiency and the 
+background rejection rate as a function of the cut in the ANN output
+define the so-called  Receiver-Operating Characteristic (ROC)
 curve.
 %
-It is clear that we can achieve a very high signal efficiency but using
-a low value of the threshold, but this will have a poor background
+It is clear that we can achieve a very high signal efficiency by using
+a small value of the cut in the ANN output, but this choice will be
+affected from a poor background
 rejection.
 %
-Using a higher value of the cut will increase background rejection at the
+Conversely, using a higher value of the cut will increase background rejection at the
 cost of dropping signal efficiency.
@@
 optimal cut value that removes enough background without degrading too much the signal efficiency.
+%
+In addition, it is important to select a value of the cut in ANN output so that
+the number of expected signal events is still large enough.
 
-In Fig.~\ref{fig:exampleroc} the ROC curves for the
-boosted, intermediate and resolved categories are found.
+In Fig.~\ref{fig:exampleroc} the
+we show the ROC curve for the background rejection rate as a function of the signal
+  selection efficiency as the cut in the ANN output is varied.
+  %
+  We show the results for the three exclusive categories: boosted, intermediate
+  and resolved.
 %
@@
 %
-The performance is slightly better in the case of the boosted
-topology, in particular thanks to the information provided
-by the substructure variables.
+The performance is best in the case of the boosted category,
+decreasing then for the intermediate and finally for the
+resolved categories, consistent with the distributions in
+Fig.~\ref{fig:exampleroc}.
 %
-In both cases we see that with a moderate reduction of signal
-efficiency of $\sim 0.8$, one can reduce the background by 80\%,
-which translates into an improvement factor of the pre-MVA $S/\sqrt{B}$
-of almost $\sim 1.8$.
 
@@
 \begin{center}
-\includegraphics[width=0.65\textwidth]{plots/example_roc.pdf}
-\caption{\small ROC curve for the neural network discriminant in the boosted (green) and resolved (blue) cases.}
+\includegraphics[width=0.65\textwidth]{plots/roc.pdf}
+\caption{\small ROC curve for the background rejection rate as a function of the signal
+  selection efficiency as the cut in the ANN output is varied.
+  %
+  We show the results for the three exclusive categories: boosted, intermediate
+  and resolved.
+}
 \label{fig:exampleroc}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From Fig.~\ref{fig:exampleroc} we see that, always starting from the signal
+and background events that survive the basic cut-based analysis,
+one can achieve a  signal
+efficiency of $\sim 80\%$ while reducing the background by
+$60\%$, $55\%$ and $45\%$ in the boosted, intermediate and resolved
+categories respectively.
+%
+It is easy to translate these factors into an  improvement factor of the pre-MVA
+signal significance $S/\sqrt{B}$.
+%
+For example, requiring a signal efficiency of 90\%, we find a background rejection
+rate of $40\%$, $30\%$ and $20\%$ respectively, which corresponds to an increase
+in $S/\sqrt{B}$ of 1.2, 1.1 and 1.0 respectively.
+
+Of course, and important restriction on the range of allowed cuts in the ANN output
+is that the cut cannot be so hard that the actual number of signal events expected
+at the HL-LHC becomes unreasonably small.
+%
+To verify how many signal and background events are left after the MVA cut,
+we show in Fig.~\ref{fig:nev2} the number of signal (dashed lines) and background (solid lines)
+  events expected at the HL-LHC as a function of the cut in the ANN output,
+  for the three separate categories.
+  %
+  Note that the value of the cut in the ANN cut can be separately optimised in the three
+  categories, even if here we plot them together for easiness of presentation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{plots/nev2.pdf}
+\caption{\small Number of signal (dashed lines) and background (solid lines)
+  events expected at the HL-LHC as a function of the cut in the ANN output,
+  for the three separate categories.
+}
+\label{fig:nev2}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+As can be seen from Fig.~\ref{fig:nev2}, in the boosted category
+event with a cut in the ANN output as hard as 0.9 we are still left
+with around 100 events at the HL-LHC, which is a reasonable number,
+which the background being reduced substantially to around
+500 events.
+%
+A similar cut would work fine for the intermediate category, though here
+the backgrounds are much larger and thus the expected signal significance smaller.
+%
+For the resolved case, the signal significance would be only slightly
+improved for any value of the cut.
 

### 2015-07-07 paper/sec-mva.tex
working on MVA section

@@
  \subsection{Input kinematical variables for the MVA}
+ \label{sec:input}
 
@@
 Therefore, we have a total of 13 variables which are common to the three categories.
+%
 
@@
 
-In order to gain physical insight of which are the variables that
-contribute the most to the MVA discrimination it is useful
-to show the distribution of NN weights for each of the
-input variables.
+A very useful property of MVA's such as the one used in this work
+is that they provide direct  physical insight about which of the
+input variables contribute the most to the signal over background
+separation.
 %
-This distributions is a measure of the correlation between
-each input variable and the Neural Network output: the higher
-the value, the stronger the impact of this variable in
-separating signal from the background.
+In the case of ANNs, this can be quantified by computing the sum
+of the absolute value of al the weights connected to a given
+input neuron $i$, that is
+\be
+\label{eq:totweight}
+\omega^{\rm tot}_i \equiv \sum_{k=1}^5 \Big|\omega^{(2)}_{ki}\Big| \, ,
+\qquad i=1,\ldots,N_{\rm var} \, ,
+\ee
+with $\omega^{(2)}_{ki}$ the value of the weight connecting
+the $k$-th neutron of the second layer with the $i$-th neuron of
+the first (input) layer.
+%
+The input variables with a larger value of $\omega^{\rm tot}_i$ will those
+be the ones that play a dominant role in enhancing the signal
+discrimination using the MVA.
+
 %
 In Fig.~\ref{fig:nnweights} we show
-the distribution of NN weights for the resolved and boosted categories.
+the distribution of the total associated weight,
+Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
+variables of the resolved (left plot) and boosted (right plot) categories.
+%
+The notation for the various kinematic variables is the same
+as in Sect.~\ref{sec:input}.
+%
+The scale of the $y$ axis is arbitrary, and the important information
+is contained in the relative strengths of the total associated weight
+for each of the input variables.
 
@@
 \begin{center}
-\includegraphics[width=0.48\textwidth]{plots/nnweights_res.pdf}
-\includegraphics[width=0.48\textwidth]{plots/nnweights_boost.pdf}
-\caption{\small Distribution of weights per input variable in the final ANN analysis.
-The above figure shows the weight distribution in the case of the resolved analysis, while the lower plot shows the boosted analysis.}
+\includegraphics[width=0.48\textwidth]{plots/res_wgthist.pdf}
+\includegraphics[width=0.48\textwidth]{plots/boosted_wgthist.pdf}
+\caption{\small
+Distribution of the total associated weight,
+Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
+variables of the resolved (left plot) and boosted (right plot) categories.
+%
+See Sect.~\ref{sec:input} for a description of each of the input
+variables to the MVA in the two cases.
+}
 \label{fig:nnweights}
@@
 %
-For instance, in the case of the resolved analysis, the variables that show
-a higher discrimination power is the invariant mass of the Higgs candidate dijets.
+Let's begin discussing the resolved analysis.
 %
-Note that as explained in Sect.~\ref{sec:analysis}, we have applied a realistic
-smearing of the four-momentum of all reconstructed jets, but still is clear that the
-distribution of invariant mass of the Higgs candidates will be very different
-in the signal and in the backgrounds.
+In this category, the variables that lead to
+a higher discrimination power
+are the $p_T$ of the two reconstructed Higgs, and then on a similar
+footing other variables like the $p_T$ of the individual jets
+and the mass of the di-Higgs system.
 %
-We discussed below the impact of smearing has.
+The only variable which seems to contain to information at all
+is the $\Delta \phi_{hh}$ separation between the two
+Higgs candidates.
+
+For the boosted category, we see that substructure variables
+are the most helpful ones, in particular the $k_t$ splitting scales
+$\sqrt{d_{12}}$ and the subjetiness ratio $\tau_{12}$.
 %
-Other variables do not seem to have a dramatic effect, although of course one of the
-advantages of the MVA technique is that it does not hurt to add redundant
-information.
+The ratio of energy correlations $D_2$ and $C_2$ also help,
+in particular the former.
 %
-In particular the angular distances between the four leading $b$-jets does not
-provide additional information.
-
-The corresponding analysis for the boosted category is also
-shown in Fig.~\ref{fig:nnweights}.
+From the more traditional variables, the angular
+separation between the two large-$R$ jets $\Delta R_{hh}$,
+the invariant mass of the di-Higgs system $m_{hh}$ and the various
+$p_T$ also have discrimination power.
 %
-here we see that there is a more even distributions of weights, in that many
-variables help in a similar amount in the discrimination.
-%
-The invariant mass of the Higgs candidate of course still carries a lot of weight,
-but now we see that the substructure variables really carry  a lot of information,
-in particular the splitting scales and the subjetiness $\tau_{12}$.
+Other variables provide limited information, in particular the invariant
+mass of the Higgs candidates, $m_{h_1}$ and $m_{h_2}$, due to the realistic
+simulation of detector resolution introduced with the smearing.
 %
 We have verified that signal significance in the boosted category is substantially
-degraded if substructure variables are not used.
+degraded if substructure variables are not used, emphasizing that
+in the boosted category jet substructure provides the best handle
+to separate signal and background.
+
+At this point we have all the ingredients that we need to determine the optimal
+value of the MVA output cut and quantify the final values of the signal
+significance $S/\sqrt{B}$ and $S/B$ in our three categories.
+%
+These optimal values are determining by the maximisation of $S/\sqrt{B}$,
+ensuring that the number of events which is left at the HL-LHC is large
+enough, and also that the actual number of MC events used for the ANN training
+is still large enough to avoid the biases of a small training sample.
+%
+The post-MVA results for $S/\sqrt{B}$ and $S/B$ as a function of the cut
+in the ANN output for each of the three categories are shown in
+Fig.~\ref{fig:sb_mva}.
+%
+As mentioned before, the optimal cuts are determined independently for each
+category.
+%
+Note that the values of $S/\sqrt{B}$ and $S/B$ in the three cases should correspond
+to the same values at the end of the cut-based analysis, as
+can be verified by looking at the {\bf C2} row of Table~\ref{table:cutflow}.
+%
+Indeed, at the end of the cut based analysis $S/\sqrt{B}$ is approximately
+1.0, 0.5 and 0.5 for the boosted, intermediate and resolved
+categories, as can be seen from Fig.~\ref{fig:sb_mva}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/ssb.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb.pdf}
+\caption{\small
+  The values of the signal significance $S/\sqrt{B}$ and of the
+  signal over background ratio $S/B$ for the boosted, intermediate
+  and resolved categories.
+  %
+  Note that the optimal cuts are determined independently for each
+  category.
+  %
+  The no-cut values correspond to the  cut-based analysis
+  results from Table~\ref{table:cutflow}.
+}
+\label{fig:sb_mva}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+The results of Fig.~\ref{fig:sb_mva} are interesting in that they show
+that for the resolved and boosted categories the improvement in signal
+significance arising from the MVA is rather moderate, less that a factor two
+in the two cases.
+%
+For no value of the cut the $S/\sqrt{B}$ value in these two categories
+goes above one.
+%
+The real usefulness of the MVA can be seen for the resolved category,
+where the signal significance rises from around 1.0 in the cut-based
+analysis to above 3.0 for values of the ANN output cut above 0.85.
+%
+This value of the cut seems reasonable, since we know from Fig.~\ref{fig:nev2}
+that the number of signal events at the HL-LHC is still quite substantial,
+of the order of 100.
+%
+Therefore, thanks to the MVA, we predict that one should be able
+to find evidence for the production of Higgs boson pairs
+at the HL-LHC using the $4b$ channel alone.
+
+Another very important benefit of the MVA applied to the boosted
+category is that fact that the background is substantially
+reduced so that $S/B$ can be as large as 10\% for the optimal
+values of the ANN output cut.
+%
+Note that this is not true for the other two categories,
+where $S/B$ is roughly constant.
+%
+A reasonably large value of $S/B$ is extremely beneficial
+from the experimental point of view, since it indicates
+that the measurement is feasible even if the
+systematic uncertainties are not very small.
+
+Our final results are summarized in Table, where we indicate
+the value of the optimal cut in each category,
+the number of signal and background events $N_{\rm ev}$,
+and also $S/\sqrt{B}$ and $S/B$.
+%
+For completeness, we also include the results after the cut-based
+analysis.
+%
+Given that the signal significance is much larger in the boosted as
+compared to the other two categories, no additional information
+could be obtained by combining the significance of the three
+categories, and it seems more efficient to perform
+the analysis exclusively in the boosted category.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Impact of smearing in the MVA discrimination}
-
-Accounting for a suitable smearing of the final-state momenta of the reconstructed
-jets is essential to be able to draw any realistic conclusions in analysis like
-this one that are based on a large number of jets.
-%
-It is therefore interesting how the MVA discrimination changes if one did not account
-for smearing - of course in this case differences between signal and background distributions
-would be enhanced.
-
-To investigate this, we now consider a variant of the analysis used in
-Table  where the $m_h$ window criterion has been relaxed to $80 < m_h < 170$.
-%
-Firstly the same analysis is repeated with the larger $m_h$ window, with no smearing at all.
-%
-This is then compared to the same analysis but with a Gaussian smearing with $\sigma=10$ GeV applied to the dijet invariant mass used in the MVA.
-%
-In the left panel of Fig.~\ref{fig:invMsmear} the smearing is demonstrated.
-%
-Both with and without smearing, the  invariant mass distribution of the
-Higgs candidates is still the most discriminative variable.
-%
-This can be seen by comparing with   with the corresponding distribution with smearing in
-  Fig.~\ref{fig:nnweights}.
-
-%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/Msmear/histo_mass_smear_precut.pdf}
-\includegraphics[width=0.49\textwidth]{plots/Msmear/nnweights.pdf}
-\caption{\small Left plot: the invariant mass distribution of the
-  Higgs candidates without (red) and with (blue) smearing.
-  %
-  Right plot: the strength of the NN weights in the resolved case when no smearing
-  is applied.
-  %
-  It should be compared with the corresponding distribution with smearing in
-  Fig.~\ref{fig:nnweights}.
-  %
-  As expected, the discrimination power of the invariant mass distribution is
-  enhanced if there is no smearing.}
-\label{fig:invMsmear}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%
-
-While the MVA still derives most of it's discriminating power from the dijet masses, the smearing reduces it's effectiveness considerably.
-%
-In Fig.~\ref{fig:smearedROC} the ROC curves of the MVA applied to the smeared and unsmeared distributions are shown, where it is clear that the overall performance of the MVA is significantly hampered by the smeared invariant masses.
-%
-For example, if we require the same signal efficiency as before, 0.8, the background rejection
-is degraded from 80\% down to 60\%.
-%
-Therefore, we can conclude that it is important to include smearing to draw realistic
-conclusions, though the qualitative information of which are the most relevant
-discriminative variables is not changed by this conclusion.
-
-%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.50\textwidth]{plots/Msmear/roc.pdf}
-\caption{\small ROC curves of the MVA applied with the unsmeared (blue) and smeared (green) dijet invariant mass distributions.}
-\label{fig:smearedROC}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%

### 2015-07-07 paper/plotscripts/plotMVAdat.py

@@ -72,19 +72,19 @@ rocax.yaxis.grid(True)
 # Setup s/b plot
 sb, sbax = plt.subplots()
 sbax.set_ylabel("S/B")
-sbax.set_xlabel("NN Discriminant")
+sbax.set_xlabel("ANN output cut")
 
 # Setup s/sqrt(b) plot
 ssb, ssbax = plt.subplots()
 ssbax.set_ylabel("S/sqrt(B)")
-ssbax.set_xlabel("NN Discriminant")
+ssbax.set_xlabel("ANN output cut")
 
 # Setup N_evt plots
 nev, nevax = plt.subplots()
 nevax2 = nevax.twinx()
 nevax.set_ylabel("Number of signal events")
 nevax2.set_ylabel("Number of background events")
-nevax.set_xlabel("NN Discriminant")
+nevax.set_xlabel("ANN output cut")
 
 nev3, nevax3 = plt.subplots()
 nevax3.set_ylabel("Number of events after MVA cut expected at HL-LHC")
@@ -93,6 +93,9 @@ nevax3.set_xlabel("ANN output cut")
 # Gridlines
 sbax.xaxis.grid(True)
 sbax.yaxis.grid(True)
+sbax.set_yscale('log')
+
+
 ssbax.xaxis.grid(True)
 ssbax.yaxis.grid(True)
 nevax.xaxis.grid(True)
@@ -133,7 +136,7 @@ for idat in xrange(0,len(datafiles)):
 			sigprob.append( float(line.split()[3]) )
 
 	#### ROC Curve and S/B plot
-	thresholds = numpy.linspace(0, 1, 25)
+	thresholds = numpy.linspace(0, 1, 60)
 	falsepos = []
 	truepos = []
 
@@ -183,8 +186,8 @@ for idat in xrange(0,len(datafiles)):
 
 	# Plot ROC curve, s/b, s/sqrt(b)
 	rocax.plot(truepos, falsepos, color=colours[idat],linestyle=linestyles[idat], label = basename)
-	sbax.plot(thresholds, soverb, color=colours[idat], label = basename)
-	ssbax.plot(thresholds, soversb, color=colours[idat], label = basename)
+	sbax.plot(thresholds, soverb, color=colours[idat], linestyle=linestyles[idat], label = basename)
+	ssbax.plot(thresholds, soversb, color=colours[idat],linestyle=linestyles[idat], label = basename)
 
 	# Plot number of events per discriminant cut
[…]

### 2015-07-07 paper/sec-mva.tex
work on mva section

@@
 
-Our final results are summarized in Table, where we indicate
+Our final results are summarized in Table~\ref{table:cutflowMVA}, where we indicate
 the value of the optimal cut in each category,
@@
 the analysis exclusively in the boosted category.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Boosted category}\\
+    \hline
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+      193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$  &  &  &  & \\
+        \hline
+  \end{tabular}
+   $\,$\\
+  \vspace{0.4cm}
+  \noindent
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Intermediate category}\\
+    \hline
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+      660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ &  &  &  & \\
+        \hline
+  \end{tabular}
+    $\,$\\
+  \vspace{0.4cm}
+  \noindent
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Resolved category}\\
+    \hline
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+      $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$   &  &  &  & \\
+        \hline
+  \end{tabular}
+  \caption{\small The results for the number of signal and
+    background events
+    at the HL-LHC for both the cut-based analysis and after the
+    optimal MVA cut, as well as the $S/\sqrt{B}$ and $S/B$
+    values in the two cases.
+    %
+    From top to bottom we show the results for boosted,
+    intermediate and resolved categories.
+    %
+    Note that the optimal value of the MVA cut
+    is different in each of the three categories.
+    \label{table:cutflowMVA}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-08 paper/sec-conclusions.tex
work on paper

@@
 
+Finally, it would be important to estimate the prospects for
+Higgs pair production in the $4b$ at a Future Circular
+Collider with a center of mass energy of 100 TeV, along the lines
+of similar studies~\cite{Barr:2014sga}.
+%
+While signal yields would be certainly increased, also the QCD
+multijet background would grow, so it is necessary to repeat
+our analysis, including full background simulation, for 100 TeV,
+in order to be able to draw any definite conclusion here.
+
 \bigskip

### 2015-07-08 paper/sec-mva.tex
work on paper

@@
   \be
+  \label{eq:ktsplitting}
 \sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, ,
@@
   \be
+  \label{eq:tau21}
 \tau_{21} \equiv \frac{\tau_2}{\tau_1} \, ,
@@
   \be
+  \label{eq:c2}
 C_2^{\beta} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{{\rm ECF}(2,\beta)} \, ,
@@
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
+    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.86$}\\
     \hline
@@
     \hline
-      193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$  &  &  &  & \\
+      193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$  & 107 & 1040 & 3.31  & 0.10\\
         \hline
@@
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
+    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.49$}\\
     \hline
@@
     \hline
-      660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ &  &  &  & \\
+      660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ & 480  & $3.2\,10^5$ & 0.85  & $1.5\,10^{-3}$ \\
         \hline
@@
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.85$}\\
+    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.17$}\\
     \hline
@@
     \hline
-      $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$   &  &  &  & \\
+    $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$   & 968 &
+    $1.2\,10^{6}$  & 0.90 & $8.2\,10^{-4}$ \\
         \hline
@@
 
-\subsection{Another look at jet substructure variables}
+From Table~\ref{table:cutflowMVA} we see that after the
+MVA the signal significance in the boosted category increases
+from 0.99 to 3.31, with $S/B$ increasing from $0.005$ to $0.10$,
+with still more that 100 signal events at the HL-LHC.
+%
+Table~\ref{table:cutflowMVA} also shows that for the intermediate
+and resolved categories, the improvement due to the use
+of the MVA is rather moderate, and signal significance is always
+small since backgrounds are still very large.
 
-It is now worth trying to understand where does the increase in signal significance
-achieved after the MVA comes from.
+Table~\ref{fig:sb_mva} contains the main result of this paper:
+at the HL-LHC, it should be possible to claim evidence of
+Higgs pair production using only the $4b$ final state.
 %
-As we will show now, the MVA has correctly identified which of the substructure
-variables are more discriminant between signal and background distributions,
-and combined this information to determine an optimal cut to maximize signal
-significance.
+Needless to say, to claim discovery and to improve the accuracy
+of the measurement of the trilinear coupling it would still
+be needed to combine this channel with others like
+$b\bar{b}\gamma\gamma$ and $b\bar{b}\tau\tau$, but in any case
+it is always important to have solid evidence from
+individual channels.
 
-For instance, in the boosted category, the analyses of the
-size of the neural network weights clearly indicates that the subjetiness
-$\tau_{12}$ and the energy correlations $C_2$ are two of the most useful
-variables.
+From Table~\ref{fig:sb_mva} it is also possible to
+extract the signal significance that would be obtained
+at the end of Run II with $\mathcal{L}_{\rm int}=300$ fb$^{-1}$:
+in the boosted category we expect 11 signal events and 100 background
+events, leading to a $S\sqrt{B}=1.1$, too small specially accounting
+for realistic systematic experimental uncertainties.
 %
-To verify that indeed these two variables are quite different between signal
-and background events, in Fig.~\ref{fig:mva_substructure_1}
-we show the subjetiness $\tau_{12}$ and the energy correlation between
-signal and background.
+So the full luminosity of the HL-LHC is really needed to exploit
+the information contained in this final state.
+
+In the next section we discuss how the expectations for the HL-LHC
+summarized in  Table~\ref{fig:sb_mva} are modified in different
+conservative and aggressive scenarios for the performance of the
+ATLAS and CMS experiments, in particular how the results depend
+on the $b$-tagging performance and in the detector momentum
+resolution.
 %
-We indeed verify that the two shapes are quite different,
+But before that let's illustrate how the improvement in $S/\sqrt{B}$
+obtained from the MVA arises from the power of the jet
+substructure variables.
+
+\subsection{Another look at the jet substructure variables}
+
+The power of the MVA applied to the boosted category lies
+on the information contained on the various substructure variables
+used.
+%
+From the distribution of total associated ANN weights in the
+boosted category shown in Fig.~\ref{fig:nnweights} we see that
+all substructure variables contain useful information,
+but specially the $k_t$ splitting scale $\sqrt{d_{12}}$ of the
+subleading Higgs candidate, the $\tau_{21}$ subjettiness variable for
+the leading Higgs
+and the ratio of energy correlators $D_2$ of both the leading
+and subleading Higgs candidates.
+%
+Interestingly, other substructure variables like $\tau_{21}$ for
+the subleading Higgs seem to contain less information (or perhaps
+redundant as compared to the other variables).
+
+The information contained Fig.~\ref{fig:nnweights} should be
+reflected in the corresponding distributions of these substructure
+variables: those with a higher discrimination power should show
+clear differences in shape between the signal and background events,
+while those that carry less information should have similar
+shapes for signal and background.
+%
+There is also the possibility of redundant variables, where signal
+and background are quite different but the same information
+is already provided by other input variables.
+
+In Fig.~\ref{fig:mva_substructure_1}
+we show these substructure variables: the
+$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}) for
+the subleading Higgs, the subjettiness ratio $\tau_{12}$
+Eq.~(\ref{eq:tau21})
+for the leading Higgs,
+and the energy correlation double ratio $D_2$
+Eq.~\ref{eq:c2}
+for the leading and subleading Higgs.
+%
+We can indeed verify that the shapes of the signal
+and background distributions are quite different,
 reflecting the differences in the internal structure of jets
 between QCD jets and jets originated from the Higgs decays.
+%
+This is true for all variables considered here.
+%
+As before, all the distributions in
+Fig.~\ref{fig:mva_substructure_1}
+have been normalized to unity.
+%
+All the distributions shown in this section refer to the boosted category.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
   \begin{center}
+    \includegraphics[width=0.48\textwidth]{plots/split12_H1_res_C1_boost.pdf} 
   \includegraphics[width=0.48\textwidth]{plots/tau21_h0_res_C1_boost.pdf}
   \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_res_C1_boost.pdf}
-  \caption{\small Left plot: subjetiness.
-    Right plot: energy correlations.
+  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_res_C1_boost.pdf}
+  \caption{\small Distribution of substructure variables
+    in the boosted category at the end of the cut-based
+    analysis, used as input to the MVA.
+    %
+    From top to bottom and from left to right we show  the
+$k_t$ splitting scale for
+the subleading Higgs, the subjettiness ratio $\tau_{12}$
+for the leading Higgs,
+and the energy correlation double ratio $D_2$
+for the leading and subleading Higgs.
+%
+All distributions have been normalized to unity.
 }
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Finally, let us show the distributions of those kinematic variables
+that according to the MVA provide a small amount of discrimination
+between signal and background, either because there is no real information or
+because it is redundant.
+
+{\bf add missing histograms}

### 2015-07-08 paper/plotscripts/plotHist_boosted_D2_fj1.py

@@ -7,24 +7,21 @@ import numpy as np
 datafiles = []
 plotnames = []
 
-from matplotlib import rc
-rc('text', usetex=True)
-
 ############################## Settings ###############################
 
 # Output filename
-outfile = "tau21_H0_res_C1_boost"
+outfile = "EEC_D2_H1_res_C1_boost"
 
 # Datafiles
-datafiles.append("../plotdata/oxford_combined_rw/signal/histo_tau21_fj1_boost_C1.dat")
-datafiles.append("../plotdata/oxford_combined_rw/background/histo_tau21_fj1_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/signal/histo_D2_fj2_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/background/histo_D2_fj2_boost_C1.dat")
 
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = r"Subjettiness Ratio $\tau_{12}$ for leading Higgs candidate"
+xLabel = r"Energy Correlation Ratio $D_2$ in for subleading Higgs candidate"
 yLabel = "A. U."
 
 # Log axes
@@ -50,14 +47,11 @@ if xLog == True:
 if yLog == True:
   ax.set_yscale('log')
 
-
-plt.rc('text', usetex=True)
-  
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([0,1])
-ax.set_ylim([1e-3,10])
+ax.set_xlim([0,1.0])
+ax.set_ylim([1e-4,100])
 
 for idat in xrange(0,len(datafiles)):
 
@@ -115,8 +109,7 @@ for idat in xrange(0,len(datafiles)):
     xvals = [xlo[x], xhi[x]]
     yvalsup = [CVup[x], CVup[x]]
     yvalsdn = [CVdn[x], CVdn[x]]
-   # ax.fill_between(xvals, yvalsup, yvalsdn, facecolor=colours[icol], alpha = 0.4, linewidth = 1, color = colours[icol])
-
+  
   # Insert lower x-values
   xhi.insert(0,xlo[0])
   yval.insert(0,yval[0])

### 2015-07-08 paper/sec-mcsamples.tex
work on paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.90\textwidth]{plots/hhFeyn.pdf}
+  \caption{\small Representative Feynman diagrams
+    for Higgs pair production in gluon fusion at
+    leading order.
+    %
+    Only the left diagram is sensitive to the trilinear coupling
+    $\lambda$.
+}
+\label{fig:hhFeyn}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 leading to a moderate enhancement as compared to the fixed-order NNLO calculation.
+
+In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
+    for Higgs pair production in gluon fusion at
+    leading order.
+    %
+    The non-trivial interplay between the heavy quark loop and
+    the trilinear it is not immediate how to the extract
+    $\lambda$ from the observation of Higgs pair
+    production cross-section.
 

### 2015-07-08 paper/sec-optimisation.tex
work on paper

@@
 as possible.
+
+Given that we have found in the previous section that the
+only category with real discrimination power is the boosted one,
+in this section we concentrate only on this one,
+by comparing our baseline results from Table~\ref{table:cutflowMVA}
+with the new scenarios.
+%
+When necessary, the MVA has been retrained to optimise the
+new information contained in the various scenarios.
+
+The results of this optimisation study are collected in
+Table~\ref{table:cutflowMVAoptimisation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c||c|c|c|c}
+    \hline
+    \multicolumn{5}{c}{Boosted category}\\
+    \hline
+    \hline
+ Scenario &    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$ \\
+       &   Signal & Back   &     &    \\
+ \hline
+ \hline
+   Baseline   & 107 & 1040 & 3.31  & 0.10\\
+   \hline
+   &  &   &   &   \\
+   &  &   &   &   \\
+   &  &   &   &   \\
+   &  &   &   &   \\
+         &  &   &   &   \\
+   \hline
+  \end{tabular}
+  \caption{\small The details of the various scenarios have been collected in
+    Table~\ref{sec:variations}.
+    \label{table:cutflowMVAoptimisation}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-08 paper/sec-appendix-overlap.tex
work on paper

@@
-\section{On the role of the overlap between different categories}
+\section{Overlap between different categories}
 \label{sec:overlap}
 
+As has been discussed in Sect.~\ref{sec:analysis}, while the optimization of each
+category is performed in an inclusive analysis, after having determine the order
+of significance of the categories we turn to a exclusive analysis, in order that
+we can combine consistently the results from the various topologies.
+%
 In this appendix we discuss the role of the overlap
-between  different categories.
+between  different categories, which is of course ignored in the final exclusive
+analyses.
+%
+The idea is to understand how significant the information is on which events satisfy the requirements
+of more than one category at the same time.
+
+To illustrate the role of the overlap between the different categories, in
+Fig.~\ref{fig:categorisationHisto} we show the fraction of events that satisfy the requirements
+of one or more categories, for signal and background events.
+%
+We consider the following cases
+\begin{itemize}
+\item Events that satisfy the requirements of the resolved category only,
+\item boosted category only
+\item Intermediate category only
+\item Both the resolved and the intermediate category
+  \item Both the boosted and the intermediate category
+\end{itemize}
+As we can see from Fig.~\ref{fig:categorisationHisto}, an overwhelming majority of the events
+below to the resolved category, specially in the background case.
+%
+Signal events are dominant in both the intermediate and the resolved categories.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
+\caption{\small The fraction of events that satisfy the requirements
+  of one or more categories, for signal and background events.
+}
+\label{fig:categorisationHisto}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+bin 0: resolved only
+bin 1: intermediate only
+bin 2: boosted only
+bin 3: resolved-intermediate overlap
+bin 4: resolved-boosted overlap
+bin 5: intermediate-boosted overlap (should be empty due to orthogonal jet multiplicity cuts)

### 2015-07-08 paper/sec-mcsamples.tex
work on paper

--- 2015-07-06 paper/sec-mcsamples.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.90\textwidth]{plots/hhFeyn.pdf}
+  \caption{\small Representative Feynman diagrams
+    for Higgs pair production in gluon fusion at
+    leading order.
+    %
+    Only the left diagram is sensitive to the trilinear coupling
+    $\lambda$.
+}
+\label{fig:hhFeyn}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 Higgs pair production is simulated at leading order using
@@
 account.\footnote{We thank Eleni Vrodynou for assistance here.}
+%
+We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
+gluon-gluon-fusion Higgs boson pair production including the effects
+of the
+exact form factors for the top triangle and box loops at leading
+order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
+loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
+models~\cite{Hirschi:2015iia}.}
 %
@@
 The Higgs boson parameters are also the same in the default model,
-in particular we use $m_H=125$ GeV, consistent with the latest
+in particular we use $m_h=125$ GeV, consistent with the latest
 measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
@@
 
-The signal samples are rescaled so that the integrated cross-section matches that of the
-NNLO calculation of the inclusive cross-section from Ref.~\cite{deFlorian:2013jea}:
-this corresponds to using a $K$-factor $\sigma_{\rm NNLO}/\sigma_{\rm LO}=2.3$.
+In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
+    for Higgs pair production in gluon fusion at
+    leading order.
     %
-Let us note that resummed NNLO+NNLL calculations for Higgs pair production have also become available recently~\cite{deFlorian:2015moa},
-leading to a moderate enhancement as compared to the fixed-order NNLO calculation.
+    The non-trivial interplay between the diagram with a heavy quark box
+    and that of the triangle (that can lead to constructive or destructive interference)
+    complicated the extraction of
+    the trilinear coupling
+    $\lambda$ from the measurement of the Higgs pair
+    production cross-section.
+
+The resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
+leading to a moderate enhancement of the order of
+few percent as compared to the fixed-order NNLO calculation.
+%
+Therefore, to achieve the correct higher-order value of the  integrated cross-section,
+we rescale our signal sample using the
+NNLO inclusive calculation from Ref.~\cite{deFlorian:2013jea} accounting the threshold resummed
+NNLL effects, which corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
+in Table.~\ref{tab:samples}
 
@@
 %
-The same applies to the background samples, which we discuss now
+The same applies to the background samples, which we discuss now.
 
@@
 %
-As in the case of the signal generation, the NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S(m_Z^2)=0.118$ is used for all samples.
+As in the case of the signal generation, the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
+$\alpha_S(m_Z^2)=0.118$ is used for all samples.
 %
@@
 
-We have considered all the relevant samples that can lead to the event
-being tagged as a $HH\to 4b$ candidate.
+We have considered the most relevant background
+processes that can lead to an event
+being tagged as a $hh\to 4b$ candidate.
 %
-First of all QCD we have $4b$ multi-jet production of course.
-%
-But also we generate QCD $2b2j$ and $4j$ multi-jet samples,
+First of all we have QCD $4b$ multi-jet production of course, but
+we also generate QCD $2b2j$ and $4j$ multi-jet samples,
 that can lead to the event being tagged in the case of multiple light
@@
 %
+In addition, we find that there is an important contribution from the radiation
+of $b$-quarks off light partons during the parton shower, which enhances the contribution
+of parton-level $2b2j$ and $4j$ events being tagged as signal events.
+%
 Neglecting the  $2b2j$ and $4j$ backgrounds is particularly
@@
 so for the boosted one.
-%
-We don't include the NLO $K$-factor for the backgrounds but instead assume
-a given experimental overall systematic uncertainties common to all backgrounds.
 
@@
 a lepton veto.
+
+The LO cross-section of the background samples has been rescaled so that the integrated
+distributions reproduce known higher-order QCD results.
+%
+For the $4b$ and $2b2j$ samples, a NLO/LO $K$-factor has been determined
+using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, which turns out to be 1.6 and 1.3
+respectively.
+%
+For the $4j$ sample, we rescale it using the {\tt BLACKHAT}~\cite{Bern:2011ep}
+results that indicates
+a NLO/LO $K$-factor of 0.6.
+%
+Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
+to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, which leads
+to a $K$-factor of 1.4.
+%
+The $K$-factors that we use to rescale all the background samples have been collected in
+Table~\ref{tab:samples}.
 
@@
 account the mistag rate, but as we will show below,
-this is not true due to combinatoric.
+this is not true due both to combinatorics and to $b$-quark radiation
+during the parton shower.
 %
@@
  %
-The $hh$ cross-section includes the NNLO $K$-factor.
+ We also provide in each case the corresponding inclusive $K$-factor
+  that is applied in each case to correctly normalize the distribution to the known
+  higher-order results.
 
@@
 \begin{table}[h]
+  \small
 \begin{center}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|}
 \hline
-Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ (pb) \\
+Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
 \hline
 \hline
-$pp \to HH$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $3.87\times10^{-2}$  \\
+$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.71\times10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
 \hline
 \hline
-$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.121 \times10^3$  \\
-$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.659 \times 10^5$  \\
-$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.709\times 10^6$  \\
-$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.514\times 10^3$ \\
+$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.12 \times10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
+$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.66 \times 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
+$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.71\times 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
+$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.51\times 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
 \hline
@@
 \caption{\small Summary of signal and background samples generated in this work,
-  together with the corresponding generator-level cross-section.
+  together with the corresponding generator-level LO cross-sections.
   %
@@
   %
-The $hh$ cross-section includes the NNLO $K$-factor.  
-} \label{tab:samples}
+We also provide in each case the corresponding inclusive $K$-factor
+  that is applied in each case to correctly normalize the distribution to the known
+  higher-order results. \label{tab:samples}
+} 
 \end{center}
@@
 
-As a cross-check of the background cross-sections reported in Table~\ref{tab:samples}, we have produced leading order
+As a cross-check of the {\tt SHERPA}
+background cross-sections reported in Table~\ref{tab:samples}, we have produced leading order
 multi-jet samples

### 2015-07-08 paper/sec-intro.tex
work on the paper

@@
 %
+Remarkably, searches for the production of Higgs pairs, whose rates
+could be enhanced by BSM effects have already been performed
+by ATLAS~\cite{Aad:2015uka} and CMS~\cite{Khachatryan:2015yea},
+though the sensitivity of these searches is still far from
+that required for a SM production mechanism.
 
@@
 only the $4b$ irreducible QCD background, estimate that with a luminosity of
-3000 fb$^{-1}$ a signal significance of $S/\sqrt{B}=$AAA can be obtained.
+3000 fb$^{-1}$ a signal significance of around $S/\sqrt{B}=2.0$ can be obtained.
+%
+Both studies were based on exploiting the differences between signal and background
+using techniques that account for a large number of variables, Boosted Decision Trees
+and Shower Reconstruction respectively.
 %
@@
 are processed using a Multivariate Analysis (in particular a feed-forward neural
-network), that further enhance $S\sqrt{B}$ up to a value of AAA.
+network), that further enhance $S/\sqrt{B}$ up to a value of 3.0
 %
@@
 Finally in Sect.~\ref{sec:conclusions} we conclude and outline
-possible future developements for Higgs pair production
+possible future developments for Higgs pair production
 in the $b\bar{b}b\bar{b}$ final state.

### 2015-07-08 paper/sec-mva.tex
work on the paper

@@
       \vspace{-1cm}
-  \includegraphics[width=0.80\textwidth]{plots/res_nnarch.pdf}
+  \includegraphics[width=0.90\textwidth]{plots/res_nnarch.pdf}
   \vspace{-1cm}
@@
   category, with $N_{\rm var}=13$ input variables and thus the same number of neurons
-in the first layer.}
+  in the first layer.
+  %
+  The color code in the neuron connections (the weights) is a heat map,
+  with red indicating large values and black small values.
+}
 \label{fig:nnarch}
@@
 
-\item The ratio of 2-to-1-Subjetiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
+\item The ratio of 2-to-1-subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
 
@@
 
-\item The energy correlation function double-ratios $C_2$ and $D_2$~\cite{Larkoski:2013eya}.
+\item The energy correlation function double-ratios $C_2$ and $D_2$~\cite{Larkoski:2013eya,Larkoski:2014gra}.
 
-  The energy correlation double ratio $C_2$ is defined
-  as
+  The energy correlation double ratios  $C_2^{\beta}$
+  and $D_2^{\beta}$ are defined
+  as follows
   \be
   \label{eq:c2}
-C_2^{\beta} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{{\rm ECF}(2,\beta)} \, ,
+C_2^{\beta} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
 \ee
-  where the energy correlation functions ${\rm ECF}(3,\beta)$ are defined
+ \be
+  \label{eq:d2}
+D_2^{\beta} \equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(2,\beta)\rc^3} \, ,
+  \ee
+  where the energy correlation functions ${\rm ECF}(N,\beta)$ are defined
   in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
   are sensitive to $N$-prong substructure.
+  %
+  The free parameter $\beta$ is set to a value of $\beta=2$,
+  as recommended by the authors of~\cite{Larkoski:2013eya,Larkoski:2014gra}.
 
@@
 
+Finally, let us briefly comment on our results would be affected
+if we take into account the systematic uncertainty in the measurement
+of the backgrounds, in addition to the statistical uncertainty.
+%
+Assuming an optimistic value of a total 3\% systematic uncertainty in the
+multijet background measurement, we find that the signal significance is
+modified as....
+{\bf complete}
+
 \subsection{Another look at the jet substructure variables}

### 2015-07-09 paper/sec-analysis.tex
work on paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Overlap between different categories}
+\label{sec:overlap}
+
+As has been discussed in Sect.~\ref{sec:analysis}, while the optimization of each
+category is performed in an inclusive analysis, after having determine the order
+of significance of the categories we turn to a exclusive analysis, in order that
+we can combine consistently the results from the various topologies.
+%
+In this appendix we discuss the role of the overlap
+between  different categories, which is of course ignored in the final exclusive
+analyses.
+%
+The idea is to understand how significant the information is on which events satisfy the requirements
+of more than one category at the same time.
+
+To illustrate the role of the overlap between the different categories, in
+Fig.~\ref{fig:categorisationHisto} we show the fraction of events that satisfy the requirements
+of one or more categories, for signal and background events.
+%
+We consider the following cases
+\begin{itemize}
+\item Events that satisfy the requirements of the resolved category only,
+\item boosted category only
+\item Intermediate category only
+\item Both the resolved and the intermediate category
+  \item Both the boosted and the intermediate category
+\end{itemize}
+As we can see from Fig.~\ref{fig:categorisationHisto}, an overwhelming majority of the events
+below to the resolved category, specially in the background case.
+%
+Signal events are dominant in both the intermediate and the resolved categories.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
+\caption{\small The fraction of events that satisfy the requirements
+  of one or more categories, for signal and background events.
+}
+\label{fig:categorisationHisto}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+bin 0: resolved only
+bin 1: intermediate only
+bin 2: boosted only
+bin 3: resolved-intermediate overlap
+bin 4: resolved-boosted overlap
+bin 5: intermediate-boosted overlap (should be empty due to orthogonal jet multiplicity cuts)

### 2015-07-09 paper/sec-intro.tex
work on paper

--- 2015-06-01 paper/sec-intro.tex
@@
 physics goals of the LHC program in its recently started high-energy
-phase, as well as for its future high-luminosity phase, as
-well as of the program of any future high-energy collider.
+phase, as well as for its future high-luminosity upgrade (HL-LHC),
+which aims to accumulate a total integrated
+luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta}.
 %
-Double Higgs production is directly sensitive to the Higgs trilinear coupling, and thus 
-provides information on the scalar potential responsible for electroweak symmetry breaking.
+Higgs pair production is directly sensitive to the
+Higgs trilinear coupling $\lambda$~\cite{baglio}, and thus 
+provides crucial
+information on the electroweak symmetry breaking mechanism.
 %
 It is also sensitive to the underlying strength of the Higgs interactions
-at high energies, and can test the composite nature of the 
+at high energies, and can be used to test the composite nature of the 
 Higgs boson~\cite{Giudice:2007fh,Contino:2010mh}.
+%
+In addition, Higgs pair production will also be a central process at
+any future high-energy 
+collider, either at a 100 TeV circular machine~\cite{Barr:2014sga} or at
+a linear or circular electron-positron collider~\cite{Contino:2013gna}.
 
 In the Standard Model (SM), the dominant mechanism for the production of two Higgs bosons at the LHC is 
-gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production.
-For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the recently computed next-to-next to
-leading order (NNLO)
-total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea}.
+gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production~\cite{Dittmaier:2012vm}.
 %
-Feasibility studies in the case of a light Higgs boson have been performed for several different final states, including
+For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the next-to-next-to-leading order (NNLO)
+total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
+which is increased by a further few percent once NNLL corrections
+are accounted for~\cite{deFlorian:2015moa}.
+%
+Feasibility studies in the case of a SM-like Higgs boson
+in gluon fusion have been performed for several different final states, including
 $b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
@@
 $b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
-$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Gouzevitch:2013qca,Cooper:2013kia,Wardrope:2014kya,deLima:2014dta}.
+$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta}.
 %
-While these various studies differ in their qualitative conclusions, it is clear
+While these studies differ in their qualitative conclusions,
+a consistent picture emerges 
 that the ultimate precision in the determination of the Higgs trilinear
-will be provided by the combination of various final states.
+will only be achieved from the combination of various final states.
+
+In addition to the gluon-fusion production mode, Higgs pairs
+can be also produced in the vector-boson fusion
+channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja},
+the associated production modes $hhW$ and $hhZ$, and also in association
+with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
+%
+All these channels are extremely challenging due to the small production
+rates: at 14 TeV, the inclusive total cross-sections are
+2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
+0.5 fb for $W(Z)hh$~\cite{baglio}
+and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
+%
+Concentrating on the SM production dynamics of Higgs pair
+production in the various channels, several studies
+have investigate the interplay of various kinematical
+distributions towards the optimisation of the
+extraction of $\lambda$ from the measured
+cross-sections, as well as the improvement
+in the signal modeling taking into account
+higher-order corrections and theoretical
+uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza}
 %
 
-The advantage of the $b\bar{b}b\bar{b}$ final state is the the signal yield
+While the SM production rates for Higgs
+pair production are small in all production modes,
+and require the full integrated luminosity of the HL-LHC phase
+to be accessed, double Higgs production rates can be substantially
+enhanced in a variety of Beyond the SM (BSM) scenarios.
+%
+Feasibility studies of Higgs pair production in New Physics
+models have been performed in a number of different frameworks,
+including effective theories with higher-dimensional
+operators and anomalous values of the
+Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
+in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa},as well as
+in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
+
+%
+In many of these scenarios, the production rates are enhanced
+and Higgs pair production becomes accessible already at
+Run II, while still being consistent with current limits on BSM searches
+and single Higgs coupling measurements.
+%
+With this motivation, searches for the production of Higgs pairs, whose rates
+could be enhanced by BSM effects have already been performed
+by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
+and $b\bar{b}\gamma\gamma$~\cite{Aad:2014yja} final states,
+and by
+and CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
+and $b\bar{b}\gamma\gamma$~\cite{Chatrchyan:2011wt} final
+states.
+%
+though the sensitivity of these searches is still far from
+that required for a SM production mechanism.
+%
+However, one should note that in general BSM dynamics modify substantially
+the kinematic distributions of the Higgs decay products, for
+instance boosting the di-Higgs system, and therefore
+different analysis strategies would be requires in BSM
+Higgs pair searches as compared to SM production measurements.
+
+In the context of SM production,
+the main advantage of the $b\bar{b}b\bar{b}$ final state is the the signal yield
 is enhanced by the large branching fraction of Higgs bosons into bottom-anti-bottom
@@
 %
-However, this channel needs to deal with an overwhelming QCD multi-jet background,
-which makes this measurement very challenging.
+However, a measurement in this channel
+needs to deal with an overwhelming QCD multi-jet background,
+which makes it very challenging.
 %
 Previous studies of Higgs pair production in this
-channel~\cite{Wardrope:2014kya,deLima:2014dta}, considering
-only the $4b$ irreducible QCD background, estimate that with a luminosity of
-3000 fb$^{-1}$ a signal significance of $S/\sqrt{B}=$AAA can be obtained.
+channel~\cite{Wardrope:2014kya,deLima:2014dta}
+estimate that with a luminosity of
+3000 fb$^{-1}$ a signal significance of around $S/\sqrt{B}\sim 2.0$ can be obtained.
 %
-However, as show in this work, neglecting other QCD backgrounds such as $bbjj$ and
-$jjjj$, with some of these light jets mistagged as $b$-jets, cannot be neglected, making
-this measurement even more difficult.
+Both studies were based on exploiting the differences between signal and background
+using techniques that account for a large number of kinematic
+variables, Boosted Decision Trees
+and Shower Reconstruction~\cite{Soper:2011cr} respectively.
+%
+Concerning the QCD multijet backgrounds, Refs.~\cite{Wardrope:2014kya,deLima:2014dta} the light-jet processes $bbjj$ and
+$jjjj$,
+which can fake the signal when 
+some of the light jets are mistagged as $b$-jets.
+%
+As will show, this is not a good approximation since both due to
+combinatorics and to $b$-quark radiation in the shower, the
+contribution of $2b2j$ and $4j$ can become comparable
+to that of $4b$.
 
-Despite these large backgrounds, by combining the contribution of different final state
+In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
+in the $4b$ final state.
+%
+Our analysis is based on exploiting the differences between a large
+number of kinematic variables in signal and background events.
+%
+Despite these large QCD multijet backgrounds, by combining the contribution of different final state
 topologies, resolved, boosted and intermediate, with a careful optimization
@@
 are processed using a Multivariate Analysis (in particular a feed-forward neural
-network), that further enhance $S\sqrt{B}$ up to a value of AAA.
+network), that further enhance $S/\sqrt{B}$ up to a value of slightly above 3.0
 %
@@
 %
-In each of these cases, we determine the significance  $S/sqrt{B}$ of the
+In each of these cases, we determine the significance
+$S/\sqrt{B}$ of the
 measurement in both conservative and optimistic assumptions of these

### 2015-07-09 paper/sec-analysis.tex
work on paper

@@
   of one or more categories, for signal and background events.
+  %
+  By construction, there is no overlap between the boosted
+  and intermediate categories due to the
+   orthogonal jet multiplicity cuts.
 }
@@
 bin 4: resolved-boosted overlap
+
+Note that
 bin 5: intermediate-boosted overlap (should be empty due to orthogonal jet multiplicity cuts)

### 2015-07-09 paper/sec-intro.tex
work on paper

@@
 are processed using a Multivariate Analysis (in particular a feed-forward neural
-network), that further enhance $S/\sqrt{B}$ up to a value of slightly above 3.0
+network), that further enhance $S/\sqrt{B}$ up to a value of slightly above 3.0.
 %

### 2015-07-10 paper/sec-mva.tex
work on paper

@@
 
-\item The energy correlation function double-ratios $C_2$ and $D_2$~\cite{Larkoski:2013eya,Larkoski:2014gra}.
+\item The ratios of energy correlation functions (EDFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
+  $D_2^{(\beta)}$~\cite{Larkoski:2014gra}.
 
-  The energy correlation double ratios  $C_2^{\beta}$
-  and $D_2^{\beta}$ are defined
-  as follows
+  The ratio of energy correlation functions $C_2^{\beta}$ is defined as
   \be
   \label{eq:c2}
-C_2^{\beta} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
+C_2^{(\beta)} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
 \ee
+while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is
 \be
+e_3^{(\beta)}\equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(1,\beta)\rc^3} \, , \quad
+  e_2^{(\beta)}\equiv \frac{ {\rm ECF}(2,\beta)}{\lc {\rm ECF}(1,\beta)\rc^2} \, , \quad
   \label{eq:d2}
-D_2^{\beta} \equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(2,\beta)\rc^3} \, ,
+D_2^{(\beta)} \equiv \frac{ e_3^{(\beta)})}{\lp e_2^{(\beta)} \rp^3} \, .
 \ee
-  where the energy correlation functions ${\rm ECF}(N,\beta)$ are defined
+The energy correlation functions ${\rm ECF}(N,\beta)$ are defined
   in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
@@
   The free parameter $\beta$ is set to a value of $\beta=2$,
-  as recommended by the authors of~\cite{Larkoski:2013eya,Larkoski:2014gra}.
-
+  as recommended by the authors of Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
 \end{itemize}

### 2015-07-10 paper/plotscripts/plotHist_boosted_etaj.py

@@ -1,0 +1,130 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_H0_res_C1_boost"
+
+# Datafiles
+datafiles.append("~/Dropbox/HH4bMC/plots_09July15/oxford_combined_rw/signal/")
+datafiles.append("~/Dropbox/HH4bMC/plots_09July15/oxford_combined_rw/background/")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+# Axis labels
+xLabel = "Leading Jet $p_{T}$ (GeV)"
+# yLabel = "$d^2\sigma$/$dp_{T}$ (fb)"
+yLabel = "A. U."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([200,500])
+ax.set_ylim([1e-4,0.05])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2015-07-10 paper/sec-results.tex
work on paper

@@
 works.
+
+\subsection{Overlap between different categories}
+\label{sec:overlap}
+
+As has been discussed in Sect.~\ref{sec:analysis}, while the optimization of each
+category is performed in an inclusive analysis, after having determined the order
+of significance of the separate categories. we turn to a exclusive analysis,
+in order that
+we can combine consistently the results from the various topologies without double
+counting.
+%
+Here we discuss the role of the overlap
+between  different categories, which is of course ignored in the final exclusive
+analyses.
+%
+The idea is to understand how significant the information is on which events satisfy the requirements
+of more than one category at the same time.
+
+To illustrate the role of the overlap between the different categories, in
+Fig.~\ref{fig:categorisationHisto} we show the fraction of events that satisfy the requirements
+of one or more categories, for signal and background events.
+%
+We consider the following cases:
+\begin{itemize}
+\item events that satisfy the requirements of one category (resolved,
+  intermediate or boosted),
+\item events that satisfy the conditions of both the resolved and the intermediate categories,
+\item and the same for events that fall both
+  into the resolved and boosted categories.
+\end{itemize}
+ Note that by construction, there is no overlap between the boosted
+  and intermediate categories due to the
+ orthogonal jet multiplicity cuts.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
+\caption{\small The fraction of events that satisfy the requirements
+  of one or more categories, for signal and background events.
+  %
+  By construction, there is no overlap between the boosted
+  and intermediate categories due to the
+   orthogonal jet multiplicity cuts.
+}
+\label{fig:categorisationHisto}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+As we can see from Fig.~\ref{fig:categorisationHisto}, an large majority of the events
+belong to the resolved category, specially in the background case ($\sim 90\%$) but
+also a large part of the signal ($\sim 60\%$).
+%
+In all the other categories, including
+the overlaps, signal events are more likely to belong to them than
+background events.
+%
+In the intermediate category, we have around $\sim$30\% of the signal
+events and $\sim$10\% of the background events.
+%
+For the boosted case, we find $\sim$ 6\% of signal events and
+$\sim$2\% of background events.
+%
+We also find that the overlap between the boosted and the other categories
+is small: none with the intermediate (by construction), and then $\sim$3\%
+($\sim$0.05\%) of the signal (background) events.
+%
+The overlap between the resolved and the intermediate is also smaller
+than the two categories separately: $\sim$7\%
+($\sim$ 3\%) for signal (background) events.
+
+Therefore, from the results of Fig.~\ref{fig:categorisationHisto}
+we can conclude that the effect of the overlap between categories would
+be small correction with respect to the exclusive selection approach
+that we use in this work.
+%
+Note also that while the majority of signal events are in the resolved
+category, since the fraction of background events is also larger,
+it is advantageous to use the small fraction of events in the boosted category
+since the suppression of the background in this category is larger
+than in the others.
+
+\section{Background decomposition}
+
+Up to now we have considered the effects of all backgrounds added
+together, except in Table~\ref{table:cutflow4B} and the corresponding
+discussion where we have studies how our
+results are modified if only the QCD $4b$ background is included.
+%
+In this section we study the decomposition of the background in each
+of its individual components, for the three different categories
+of events used in this work.

### 2015-07-10 paper/plotscripts/plotHist_overlap.py

@@ -7,6 +7,8 @@ import numpy as np
 datafiles = []
 plotnames = []
 
+
+
 ############################## Settings ###############################
 
 # Output filename
@@ -37,6 +39,7 @@ if len(datafiles)!=len(plotnames):
   print "Error: datafile and plotname arrays are different lengths!"
   exit()
 
+linestyles = [ 'solid', 'dashed']
 colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
 icol = 0
 
@@ -114,17 +117,18 @@ for idat in xrange(0,len(datafiles)):
   xhi.insert(0,xlo[0])
   yval.insert(0,yval[0])
 
-  ax.plot(xhi,yval/norm,ls = "steps-pre", color = colours[icol], label=plotnames[idat])
+  ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat], linestyle=linestyles[idat],linewidth=2)
   icol=icol+1
 
 # Gridlines
 ax.yaxis.grid(True)
 
+plt.rcParams.update({'font.size': 15})
+linestyles = ['solid','dashed']
 kinematics= [ 'RES','INT','BOOST','RES+INT','RES+BOOST' ]
 
-plt.xticks(rotation=-20)
+plt.xticks(rotation=-15)
 plt.xlabel('')
-plt.ylabel('Total associated weight (A.U.)')
 plt.xticks(np.arange(len(kinematics)) + 0.5, kinematics)
 
 # Legend

### 2015-07-10 paper/sec-results.tex
work on paper

@@
 
-\section{Background decomposition}
+\subsection{Background decomposition}
 
@@
 of events used in this work.
+%
+
+In Table~\ref{table:cutflowBack}   we show the results for the cross-sections for the different
+backgrounds that we consider at the end of the cut-based analysis, for each
+of the three categories.
+%
+All the backgrounds have been normalized to known higher-order results,
+as summarized in Table~\ref{tab:samples}.
+%
+As we can see from this comparison, as opposed that what naively one would expect,
+the QCD $2b2j$ background turns out not to be negligible as compared to the $4b$
+multijets in any of the categories.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c|c}
+    \hline
+    Background  &    \multicolumn{3}{c}{$\sigma$ (fb)}   \\
+    \hline
+  &    Resolved  &  Intermediate  &   Boosted \\
+    \hline
+    \hline
+  QCD $4b$   &   $9.9\,10^{2}$       &  $59$       &   $7.1$        \\
+  QCD $2b2j$ &   $2.4\,10^{3}$       &  $6.4\,10^{2}$       &   $3.5$        \\
+  QCD $4j$ &     $1.7\,10^{2}$       &   $22$      &    $2.1$        \\
+  $t\bar{t}$ &   $3.6$       &  $2.2$       &   $4.5\,10^{-2}$        \\
+  \hline
+  \hline
+Total     &    $3.6\,10^{3}$      &   $7.2\,10^{2}$      &     $13$      \\
+\hline
+\end{tabular}
+    \caption{\small The cross-sections for each of the individual background
+      components (and their total sum) at the end of the cut-based
+      analysis, for each of three categories.
+    \label{table:cutflowBack}
+    }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
+irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
+to the case where only $4b$ is accounted for.
+%
+This effect is more dramatic in the intermediate and resolved categories: in the former,
+$2b2j$ completely dominates the background (thus the increase in $S/sqrt{B}$ noted in
+Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
+it is comparable to $4b$.
+%
+Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
+an essential component of this analyses, and that complete QCD multijet samples
+should be included.
+
+  {\bf add plots BKG}
+
+  One might ask why the $2b2j$ process
+  is not subdominant as compared to $4b$: while its generator-level cross-section is
+  much larger, $\sigma_{2b2j} \simeq 240\sigma_{4b}$, one expects a suppression
+  of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
+  would be identified as a Higgs candidate.
+  %
+  We have checked that this expectation is true only at parton level: once parton shower effects
+  are accounted for, both the radiation of $b\bar{b}$ pairs from the shower and combinatorics increase
+  the number of $b$ quarks in the final state, enhancing substantially the $2b2j$ rates as compared
+  to the naive parton level expectation.
+  %
+  To verify this, we plot the number of $b$-quarks.....

### 2015-07-10 analysis/res/genCutFlows_JR.py

@@ -7,7 +7,7 @@ regimes = ['res', 'inter','boost']
 folder = "../../paper/plotdata/oxford_combined_rw/"
 print folder
 
-recursive_folders = ['signal', 'background', 'SHERPA_QCD4b', 'SHERPA_QCD2b2j', 'SHERPA_QCD4j']
+recursive_folders = ['signal', 'background', 'SHERPA_QCD4b', 'SHERPA_QCD2b2j', 'SHERPA_QCD4j', 'SHERPA_QCDttbar']
 file_types = ['res', 'inter', 'boost']
 
 new_data = {}

### 2015-07-10 paper/sec-results.tex

@@
 
+\subsection{Background decomposition}
+
+Up to now we have considered the effects of all backgrounds added
+together, except in Table~\ref{table:cutflow4B} and the corresponding
+discussion where we have studies how our
+results are modified if only the QCD $4b$ background is included.
+%
+In this section we study the decomposition of the background in each
+of its individual components, for the three different categories
+of events used in this work.
+%
+
+In Table~\ref{table:cutflowBack}   we show the results for the cross-sections for the different
+backgrounds that we consider at the end of the cut-based analysis, for each
+of the three categories.
+%
+All the backgrounds have been normalized to known higher-order results,
+as summarized in Table~\ref{tab:samples}.
+%
+As we can see from this comparison, as opposed that what naively one would expect,
+the QCD $2b2j$ background turns out not to be negligible as compared to the $4b$
+multijets in any of the categories.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c|c}
+    \hline
+    Background  &    \multicolumn{3}{c}{$\sigma$ (fb)}   \\
+    \hline
+  &    Resolved  &  Intermediate  &   Boosted \\
+    \hline
+    \hline
+  QCD $4b$   &   $9.9\,10^{2}$       &  $59$       &   $7.1$        \\
+  QCD $2b2j$ &   $2.4\,10^{3}$       &  $6.4\,10^{2}$       &   $3.5$        \\
+  QCD $4j$ &     $1.7\,10^{2}$       &   $22$      &    $2.1$        \\
+  $t\bar{t}$ &   $3.6$       &  $2.2$       &   $4.5\,10^{-2}$        \\
+  \hline
+  \hline
+Total     &    $3.6\,10^{3}$      &   $7.2\,10^{2}$      &     $13$      \\
+\hline
+\end{tabular}
+    \caption{\small The cross-sections for each of the individual background
+      components (and their total sum) at the end of the cut-based
+      analysis, for each of three categories.
+    \label{table:cutflowBack}
+    }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
+irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
+to the case where only $4b$ is accounted for.
+%
+This effect is more dramatic in the intermediate and resolved categories: in the former,
+$2b2j$ completely dominates the background (thus the increase in $S/\sqrt{B}$ noted in
+Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
+it is comparable to $4b$.
+%
+Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
+an essential component of this analyses, and that complete QCD multijet samples
+should be included.
+
+In Fig.~\ref{fig:histoBack} we show the decomposition of the background for one important kinematical
+distribution, the $p_T$ of the leading reconstructed Higgs candidate, various background
+components, for both the boosted and the resolved categories.
+%
+In the same figure we also show the results of the corresponding comparison
+at the level of the $p_T^{hh}$ of the
+reconstructed di-Higgs system.
+%
+The histograms correspond to the distributions at the end of the cut-based
+analysis.
+%
+The results are consistent with those summarized in
+Table~\ref{table:cutflowBack}: in the boosted case we see how $4b$ is the most important
+component of the background, with $2b2j$ being of the same order of magnitude, while
+for the resolved category we see that $2b2j$ dominates instead.
+%
+So the effect of the fakes is certainly important, but fortunately it is not a limiting factor
+in the resolved category, the one that leads to higher signal significance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_boost_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_boost_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_res_back.pdf}
+  \caption{\small
+    Upper plots: the decomposition of the QCD multijet background in its various
+    components, $4b$, $2b2j$ and $4j$, for the $p_T$ of the leading
+    Higgs candidate in the boosted (left plot) and resolved (right plot) categories.
+    %
+    Lower plots: the same comparison this time for the $p_T^{hh}$ of the
+    reconstructed di-Higgs system.
+}
+\label{fig:histoBack}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+  One might ask why the $2b2j$ process
+  is not subdominant as compared to $4b$: while its generator-level cross-section is
+  much larger, $\sigma_{2b2j} \simeq 240\sigma_{4b}$, one expects a suppression
+  of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
+  would be identified as a Higgs candidate.
+  %
+  We have checked that this expectation is true only at parton level: once parton shower effects
+  are accounted for, both the radiation of $b\bar{b}$ pairs from the shower and combinatorics increase
+  the number of $b$ quarks in the final state, enhancing substantially the $2b2j$ rates as compared
+  to the naive parton level expectation.
+  %
+  To verify this, we plot the number of $b$-quarks.....
+
   \subsection{Overlap between different categories}
@@
 than in the others.
-
-\subsection{Background decomposition}
-
-Up to now we have considered the effects of all backgrounds added
-together, except in Table~\ref{table:cutflow4B} and the corresponding
-discussion where we have studies how our
-results are modified if only the QCD $4b$ background is included.
-%
-In this section we study the decomposition of the background in each
-of its individual components, for the three different categories
-of events used in this work.
-%
-
-In Table~\ref{table:cutflowBack}   we show the results for the cross-sections for the different
-backgrounds that we consider at the end of the cut-based analysis, for each
-of the three categories.
-%
-All the backgrounds have been normalized to known higher-order results,
-as summarized in Table~\ref{tab:samples}.
-%
-As we can see from this comparison, as opposed that what naively one would expect,
-the QCD $2b2j$ background turns out not to be negligible as compared to the $4b$
-multijets in any of the categories.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
-  \centering
-  \begin{tabular}{c|c|c|c}
-    \hline
-    Background  &    \multicolumn{3}{c}{$\sigma$ (fb)}   \\
-    \hline
-  &    Resolved  &  Intermediate  &   Boosted \\
-    \hline
-    \hline
-  QCD $4b$   &   $9.9\,10^{2}$       &  $59$       &   $7.1$        \\
-  QCD $2b2j$ &   $2.4\,10^{3}$       &  $6.4\,10^{2}$       &   $3.5$        \\
-  QCD $4j$ &     $1.7\,10^{2}$       &   $22$      &    $2.1$        \\
-  $t\bar{t}$ &   $3.6$       &  $2.2$       &   $4.5\,10^{-2}$        \\
-  \hline
-  \hline
-Total     &    $3.6\,10^{3}$      &   $7.2\,10^{2}$      &     $13$      \\
-\hline
-\end{tabular}
-    \caption{\small The cross-sections for each of the individual background
-      components (and their total sum) at the end of the cut-based
-      analysis, for each of three categories.
-    \label{table:cutflowBack}
-    }
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
-irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
-to the case where only $4b$ is accounted for.
-%
-This effect is more dramatic in the intermediate and resolved categories: in the former,
-$2b2j$ completely dominates the background (thus the increase in $S/sqrt{B}$ noted in
-Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
-it is comparable to $4b$.
-%
-Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
-an essential component of this analyses, and that complete QCD multijet samples
-should be included.
-
-  {\bf add plots BKG}
-
-  One might ask why the $2b2j$ process
-  is not subdominant as compared to $4b$: while its generator-level cross-section is
-  much larger, $\sigma_{2b2j} \simeq 240\sigma_{4b}$, one expects a suppression
-  of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
-  would be identified as a Higgs candidate.
-  %
-  We have checked that this expectation is true only at parton level: once parton shower effects
-  are accounted for, both the radiation of $b\bar{b}$ pairs from the shower and combinatorics increase
-  the number of $b$ quarks in the final state, enhancing substantially the $2b2j$ rates as compared
-  to the naive parton level expectation.
-  %
-  To verify this, we plot the number of $b$-quarks.....

### 2015-07-13 paper/sec-analysis.tex
added comments
work on paper

--- 2015-07-07 paper/sec-analysis.tex
@@
 
+Another important kinematical distribution of this process is the invariant mass
+of the di-Higgs system.
+%
+First of all because this is a direct measure of the boost of the system,
+and also because in many BSM scenarios this distribution can be substantially
+modified as compared to the SM case.
+%
 Next, we show in
@@
 look reasonably similar.
+%
+Note that the $m_{HH}$ distribution as a kinematical
+cut-off at $m_{HH}^{\rm min}=250$ GeV.
 

### 2015-07-13 paper/sec-analysis.tex
plots for the paper

@@
 
-\subsubsection{Boosted category}
+We will compare kinematic variables at each step of the analysis
+for the boosted and for the resolved categories.
+%
+The corresponding plots for the intermediate category can be found in the webpage
+mentioned above.
+%
+In the following comparisons, we compare related
+kinematical distributions in the two categories.
 
-We begin with the boosted category, which is the one that leads
-to a higher signal significance.
-%
 First of all,
@@
 the $p_T$ distribution of the 
-  leading large-$R$ jet in the boosted category, comparing
+of the
+  leading and subleading large-$R$ jet in the boosted category, comparing
   the shapes of the distribution in signal and background events.
   %
-  All distributions have been normalized to their total integral.
+  As we will do in all this section,
+  all distributions have been normalized to their total integral.
   %
@@
   advantageous to suppress the background.
+  %
+  This is true both for the leading and the subleading
+  large-$R$ jets.
+  %
+  These distributions justify our choice of $p_T \ge 200$ GeV
+  for the large-$R$ jets in the boosted category.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{plots/pt_H0_res_C1_boost.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1_boost.pdf}
-\caption{\small Left plot: the $p_T$ distribution of the
-  leading large-$R$ jet in the boosted category, comparing
-  the shapes of the distribution in signal and background events.
+ \includegraphics[width=0.48\textwidth]{plots/pt_H0_boost_C1.pdf}
+ \includegraphics[width=0.48\textwidth]{plots/pt_H1_boost_C1.pdf}
+\caption{\small  The $p_T$ distribution of the
+  leading (left plot) and
+  subleading (right plot) large-$R$ jet in the boosted category.
   %
-  All distributions have been normalized to their total integral.
-  %
-  Right plot: the invariant mass of the leading Higgs
-  candidate.
+  We comparing
+  the shapes of the distribution in signal and background events,
+  where both
+  distributions have been normalized to their total integral.
 }
@@
 
-\subsubsection{Resolved category}
-
 Let's now consider the resolved category.
@@
 {\bf missing plots: pt jet distribution, rapidity distribution}
+
+Next in Fig.~\ref{fig:mHHinv} we show the invariant mass
+of the leading Higgs candidates, before the Higgs mass window
+cut is applied, for the resolved and boosted categories.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/m_H0_boost_C1.pdf}
+  \caption{\small The invariant mass distribution of the leading
+    Higgs candidates on the resolved (left plot) and boosted (right
+    plot) categories.
+}
+\label{fig:mHHinv}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-13 paper/plotscripts/plotHist_boosted_ptj2.py

@@ -10,25 +10,25 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "m_H0_boost_C1"
+outfile = "pt_H1_boost_C1"
 
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/oxford_combined_rw/signal/histo_m_H0_boost_C1.dat")
-datafiles.append("../plotdata/oxford_combined_rw/background/histo_m_H0_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/signal/histo_pt_H1_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/background/histo_pt_H1_boost_C1.dat")
 
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = "Leading Higgs Candidate Mass (GeV)"
+xLabel = "Subleading large-R Jet $p_{T}$ (GeV)"
 yLabel = "A. U."
 
 # Log axes
 xLog = False
-yLog = False
+yLog = True
 
 # Normalise histograms
 normalise = True
@@ -52,8 +52,8 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([80,170])
-ax.set_ylim([5e-4,0.025])
+ax.set_xlim([150,600])
+ax.set_ylim([1e-4,0.02])
 
 for idat in xrange(0,len(datafiles)):
 
@@ -117,7 +117,6 @@ for idat in xrange(0,len(datafiles)):
   yval.insert(0,yval[0])
 
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
-
   icol=icol+1
 
 # Gridlines

### 2015-07-13 paper/plotscripts/plotHist_res_mHH.py

@@ -16,6 +16,8 @@ outfile = "m_HH_res_C1"
 datafiles.append("../plotdata/oxford_combined_rw/signal/histo_m_HH_res_C1.dat")
 datafiles.append("../plotdata/oxford_combined_rw/background/histo_m_HH_res_C1.dat")
 
+linestyles = [ 'solid', 'dashed']
+
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
@@ -114,7 +116,7 @@ for idat in xrange(0,len(datafiles)):
   xhi.insert(0,xlo[0])
   yval.insert(0,yval[0])
 
-  ax.plot(xhi,yval/norm,ls = "steps-pre", color = colours[icol], label=plotnames[idat])
+  ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
   icol=icol+1
 
 # Gridlines

### 2015-07-13 paper/sec-analysis.tex
work on the settings section

@@
 In this section we motivate the various
-kinematical cuts for the various categories.
+kinematical cuts applied to the different categories.
 %
-As mentioned before, the cuts in each category have been separately
-optimised in an inclusive analysis: it is only once we have determined
-which is the dominant category that the analysis is made exclusive.
+These cuts have been separately
+optimised in an inclusive analysis, since it is only
+once we have determined
+the dominant category that the analysis is made exclusive.
 %
-In this work, the results for each category have been derived
-from the inclusive analysis,
-and we show the various kinematic distributions immediately
+Here we show the various kinematic distributions immediately
 below the corresponding cut has been applied.
-
-In this section we only show a representative subset of
-all available kinematic distributions, the complete
-set of comparison plots can be found in the following
-webpage:
+%
+Only a representative subset of
+all available kinematic distributions will be shown here, the complete
+set of plots, including the distribution of all substructure
+variables used in the MVA later, have been collected
+in this webpage:
 \begin{center}
@@
   \end{center}
-In this webpage we also show the distribution of all
-kinematic variables, including jet substructure variables,
-which we don't cut explicitly but that are provided as
-input to the multivariate analysis.
-%
-Also, we show here results for the boosted and resolved categories,
-a comparison which allows to understand the cuts used for the
-intermediate category as well.
-
-We will compare kinematic variables at each step of the analysis
-for the boosted and for the resolved categories.
-%
-The corresponding plots for the intermediate category can be found in the webpage
-mentioned above.
-%
-In the following comparisons, we compare related
-kinematical distributions in the two categories.
+In this section we restrict to the discussion of the
+kinematic distributions of the boosted
+and resolved categories, the corresponding results for the
+intermediate category are collected in the same webpage.
 
@@
 of the
-  leading and subleading large-$R$ jet in the boosted category, comparing
+  leading and subleading large-$R$ jets in the boosted category, comparing
   the shapes of the distribution in signal and background events.
   %
-  As we will do in all this section,
-  all distributions have been normalized to their total integral.
+  Distributions have been normalized to their total integral.
   %
   We see that the background distribution
-  falls off rather steeply than the signal, therefore
-  suggesting that the boosted region should be
-  advantageous to suppress the background.
+  falls off rather steeply than the signal at large $p_T$
+  values, therefore
+  providing evidence that exploiting the boosted region will be
+  advantageous to enhance the signal over background ratio.
   %
@@
   leading (left plot) and
-  subleading (right plot) large-$R$ jet in the boosted category.
+  subleading (right plot) large-$R$ jets in the boosted category.
   %
@@
 
-In Fig.~\ref{fig:cutplots1} we also show the distribution
-of the invariant mass of the leading Higgs candidates.
-%
-The signal is of course well peaked at $m_h=125$ GeV, the physical
-mass, while the background does not display any structure.
-%
-Note that the smearing, which mimics detector resolution effects,
-leads to a rather broad distribution which reduces the usefulness
-of the Higgs mass window cut.
-%
-However, the information of the different shape of the $m_{h}$
-distribution will still be exploited by the MVA.
+{\bf Add missing plots here: pt of subjets(boosted), pt of
+  small-R jets (resolved), rapidity of the large-$R$ jets,
+rapidity of the small-$R$ jets.}
 
-As explained above, in the boosted category we also require the two
+In the boosted category we require the two
 leading subjets of the large-$R$ jet to be relatively
@@
 %
-To motivate this cut, in Fig ... we show the distribution in $p_T$ of the leading
+To motivate this cut, in FigAAA
+we show the distribution in $p_T$ of the leading
 and subleading sub-jets in the leading large-$R$ jet in events
@@
 relatively harder in the signal with respect to the background,
-motivating our cut.
+motivating our choice of subjet $p_T$ cut.
 
-{\bf missing plots: pt subjet distribution}
-
-Let's now consider the resolved category.
-%
-To begin with, here it is important to understand the $p_T$ distribution
+In the intermediate category,
+it is important to understand the $p_T$ distribution
 of the four leading small-$R$ jets of the event.
@@
 %
+This also has important implications for the experimental
+trigger requirements in this category.
+%
 In Fig. we show the distribution in $p_T$ of the four leading
@@
 %
+Therefore, we can conclude that....
+
+Another important distribution is the rapidity of the large-$R$
+(in the boosted category) and the small-$R$ (in the resolved
+category) jets.
+%
+We want to understand by how much the signal efficiency is reduced
+by the restriction of the central region, and how would
+the signal yield be enhanced if tracking could be extended
+to forward rapidities in ATLAS and CMS.
+%
 Also, it is useful to show the distribution in rapidity of the
-individual jets
-
-{\bf missing plots: pt jet distribution, rapidity distribution}
+individual jets in the resolved category.
+%
+This comparison is shown in FigAAA.
 
 Next in Fig.~\ref{fig:mHHinv} we show the invariant mass
-of the leading Higgs candidates, before the Higgs mass window
+of the leading reconstructed Higgs candidates, before the Higgs mass window
 cut is applied, for the resolved and boosted categories.
+%
+The signal distribution is of course peaked at the
+nominal Higgs mass of $m_h=125$ GeV.
+%
+In the boosted category, the background shows no particular
+structure, while remarkable in the resolved category the background
+also shows a peak-like structure, artificially induced by the
+acceptance kinematical cuts on the jets.
+%
+Note that the applied smearing, which mimics detector resolution effects,
+leads to a rather broad distribution which reduces the usefulness
+of the Higgs mass window cut.
+%
+While our Higgs mass window cut is relatively loose,
+information of the different shape of the $m_{h}$
+distribution will still be exploited by the MVA.
+%
+In Sect.~\ref{sec:optimisation} we discuss how the results
+of the analysis is modified if a more aggressive
+detector resolution is assumed (corresponding
+to a smaller value of the smearing).
 
@@
 and also because in many BSM scenarios this distribution can be substantially
-modified as compared to the SM case.
+modified as compared to the SM case, for example in the presence
+of certain dimension-6 EFT operators~\cite{Azatov:2015oxa}.
 %
-Next, we show in
-Fig.~\ref{fig:mhh} the invariant mass distribution of the Higgs pairs,
-comparing the resolved category (left) with the boosted category (right)
+Indeed, one important advantage of the $4b$ final state for
+di-Higgs production is that it significantly increases the reach
+in $m_{hh}$ as compared to other channels with smaller branching rations,
+such as $2b2\gamma$.
 %
-This is interesting since it determines the degree of boost that the two
-Higgs candidates will have after non-resonant production.
-%
+With this motivation, we show in
+Fig.~\ref{fig:mhh} the invariant mass distribution of the
+reconstructed Higgs pairs,
+comparing the resolved category (left) with the boosted category (right).
+
 In the resolved case, we see that the distribution
@@
 and thus one expects that cutting in $m_{hh}$ would help signal
-discrimination: we will verify this with the MVA in the next section.
+discrimination: we will verify this with the help of the MVA.
 %
 For the boosted category the trend of the $m_{hh}$ distribution
-is very different because of the selection, with the
-distribution now peaking at much higher values.
+is different because of the jet selection cuts, with the
+distribution now peaking at higher values.
 %
@@
 %
-Note that the $m_{HH}$ distribution as a kinematical
-cut-off at $m_{HH}^{\rm min}=250$ GeV.
+Note that at parton-level the $m_{hh}$ distribution as a kinematical
+cut-off at $m_{hh}^{\rm min}=250$ GeV, which is modified by both
+shower effects and by detector resolution effects.
+%
+While we don't cut in this quantity, it is
+one of the inputs for the MVA to help to improve signal discrimination.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+Another interesting distribution is the transverse momentum of
+the di-Higgs system.
+%
+In Fig.~\ref{fig:pthh} we show the $p_T^{hh}$
+distribution
+for the resolved and boosted categories.
+%
+Note that in our LO simulation this distribution is generated purely
+by the parton shower - a more refined calculation would require
+either the matching with higher-multiplicity matrix elements~\cite{Maierhofer:2013sha} or
+the full NLO calculation~\cite{Frederix:2014hta}, to treat properly the first hard emission.
+%
+Again we see that the background has a steeper $p_T^{hh}$ distribution
+that the signal, in both categories, thus this variable
+should provide some additional discrimination power, and therefore
+we will use it as another of the MVA inputs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{plots/pt_HH_res_C1.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/pt_HH_boost_C1.pdf}
+  \caption{\small Left plot: the invariant mass distribution of the Higgs
+    pair candidates, $m_{hh}$, comparing signal and background events,
+    in the resolved category.
+    %
+    Right plot: same for the boosted category.
+}
+\label{fig:pthh}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-13 paper/sec-intro.tex
work on the settings section

@@
 higher-order corrections and theoretical
-uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza}
+uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha}
 %

### 2015-07-13 paper/HH4b.tex
Work on paper
work on paper
Updated common plot style

--- 2015-04-24 paper/HH4b.tex
@@
 
-\title{Boosting Higgs Pair Production in the $4b$ Channel at the LHC with Multivariate Techniques}
+\title{Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with
+  Multivariate Techniques}
 
-\author[a]{Katharina Behr, Nurfiki Bin Norjoharuddeen, Daniela Bortoletto, James Frost, Nathan P. Hartland, Cigdem Issever and Juan Rojo}
+\author{Katharina Behr, Nurfiki Bin Norjoharuddeen, Daniela Bortoletto, James Frost, Nathan P. Hartland, Cigdem Issever and Juan Rojo}
 
-\affiliation[a]{Physics Department, 1 Keble Road, University of Oxford, United Kingdom }
+\affiliation{Physics Department, 1 Keble Road, University of Oxford, United Kingdom }
 
-\emailAdd{juan.rojo@physics.ox.ac.uk}
-
-\preprint{OUTP-15-aaa}
+\preprint{OUTP-15-14P}
 
 \abstract{
-A nice abstract
+  The measurement of Higgs pair production is one of the cornerstones of
+  the LHC program for the next years.
+  %
+  Double Higgs production provides a unique window to the electroweak
+  symmetry breaking mechanism, and in particular it allows
+  to access the Higgs trilinear coupling.
+  %
+  In this work we study the feasibility of the observation of the production of
+  Higgs boson pairs at the High-Luminosity LHC (HL-LHC) in the
+  $b\bar{b}b\bar{b}$ final state.
+  %
+  While the signal in this channel
+  is enhanced by the large branching fraction of Higgs bosons to
+  $b\bar{b}$ pairs, the measurement is  challenging due to the
+  overwhelming QCD multijet background.
+  %
+  Our analysis is based on a combination of traditional cut-based
+  methods with modern multivariate techniques, which lead to a substantial
+  enhacement of the signal discrimination.
+  %
+  We account for  all relevant
+  backgrounds, including the contribution from light jet fakes that is found
+  to be as important or even dominant over the irreducible $4b$ QCD background.
+  %
+  By combining the contribution from the boosted, intermediate and resolved
+  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
+  %
+  We therefore demonstrate that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
+  should allow to claim evidence of the observation of double Higgs production.
 }
@@
 
-% Introduction
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{sec-intro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Monte Carlo samples
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{sec-mcsamples}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% analysis strategy
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{sec-analysis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Main results
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{sec-results}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% MVA
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \input{sec-mva}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Conclusions and outlook
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{sec-optimisation}
 \input{sec-conclusions}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-07-13 paper/sec-analysis.tex
Updated common plot style

@@
   in ATLAS and CMS
-  related to the track-jet-based calibration.
+  related to the track-jet-based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.
 
@@
 
-    Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$
-    subjets (defined as above) to the original large-$R$ jets.
+    Large-$R$ jets are $b$-tagged by
+    ghost-associating anti-$k_T$ $R=0.3$
+    subjets (defined as above) to the original large-$R$
+    jets~\cite{Cacciari:2007fd,Aad:2013gja,
+      ATLAS-CONF-2014-004}.\footnote{This is the same
+    method used in the recent ATLAS $hh\to 4b$ search~\cite{Aad:2015uka}.}
     %

### 2015-07-13 paper/sec-mcsamples.tex
Updated common plot style

@@
     %
-    Only the left diagram is sensitive to the trilinear coupling
+    Only the quark triangle diagram (left) is sensitive to the Higgs trilinear coupling
     $\lambda$.
+    %
+    In the SM, the fermion loops are dominated by the top quark contribution.
 }
@@
 {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
-account.\footnote{We thank Eleni Vrodynou for assistance here.}
+account.\footnote{We thank Eleni Vrodynou for assistance with di-Higgs production
+  in {\tt MadGraph5\_aMC@NLO}.}
 %
@@
 NNLL effects, which corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
-in Table.~\ref{tab:samples}
+in Table~\ref{tab:samples}.
 
@@
 For a similar reason, we don't consider underlying event, multiple parton interactions and
-pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp}.
+pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia}.
 %

### 2015-07-13 paper/sec-mva.tex
Updated common plot style

@@
 %
-Assuming an optimistic value of a total 3\% systematic uncertainty in the
-multijet background measurement, we find that the signal significance is
-modified as....
-{\bf complete}
+While there is no unique definition of how signal significance is modified
+by experimental systematic uncertainties~\cite{Bityukov:2002eq}, here we estimate
+this effect with the simple correction
+\be
+\frac{S}{\sqrt{B}} \, \to \, \frac{S}{\sqrt{B}} \frac{1}{\sqrt{1+\lp \sigma^{\rm sys}\rp^2\cdot B}} \, ,
+\ee
+which corresponds to adding in quadrature to the statistical uncertainty  a single
+uncorrelated systematic uncertainty $\sigma^{\rm sys}$.
+%
+Assuming an optimistic value of a total 2\% systematic uncertainty in the
+multijet background measurement, we find that the signal significance would be
+reduced in the boosted category from 3.31 to 2.8.
+%
+However, it is beyond the scope of this work to estimate realistically
+the systematic uncertainties on QCD multijet distributions (and their bin-by-bin correlation)
+that will be achieved at HL-LHC, and in the following we only consider the statistical
+uncertainties on the background.
+%
+But this quick estimate emphasizes the crucial need of an experimentally accurate
+measurement of multijet backgrounds at the LHC to fully exploit the $4b$ channel.
 
@@
 
-The power of the MVA applied to the boosted category lies
-on the information contained on the various substructure variables
-used.
+It is possible to verify that the usefulness of the MVA when
+applied to the boosted category arises from the 
+the information contained on the various jet substructure variables.
 %
 From the distribution of total associated ANN weights in the
-boosted category shown in Fig.~\ref{fig:nnweights} we see that
-all substructure variables contain useful information,
-but specially the $k_t$ splitting scale $\sqrt{d_{12}}$ of the
-subleading Higgs candidate, the $\tau_{21}$ subjettiness variable for
-the leading Higgs
-and the ratio of energy correlators $D_2$ of both the leading
-and subleading Higgs candidates.
+boosted category, shown in Fig.~\ref{fig:nnweights}, we see that
+all substructure variables contain useful information:
+the $k_t$ splitting scales $\sqrt{d_{12}}$,
+the $\tau_{21}$ subjettiness ratio, and the ECF ratios
+$C_2^{{\beta}}$ and $D_2^{{\beta}}$.
 %
-Interestingly, other substructure variables like $\tau_{21}$ for
-the subleading Higgs seem to contain less information (or perhaps
-redundant as compared to the other variables).
+Interestingly, for some substructure variables, such as $\tau_{21}$,
+the total associated weight turns out to be stronger in the leading
+than in the sub-leading Higgs candidate (or vice-versa), indicating some
+degree of redundancy when the same variable is used for the two Higgs candidates
+at the same time.
 
-The information contained Fig.~\ref{fig:nnweights} should be
+Indeed, the information contained Fig.~\ref{fig:nnweights} should be
 reflected in the corresponding distributions of these substructure
@@
 %
-There is also the possibility of redundant variables, where signal
-and background are quite different but the same information
+The third possibility is that of of redundant variables, where signal
+and background exhibit different shapes but the same information
 is already provided by other input variables.
-
+%
+To illustrate these points,
 In Fig.~\ref{fig:mva_substructure_1}
-we show these substructure variables: the
+we show the distributions of some of
+these substructure variables for the boosted category: the
 $k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}) for
-the subleading Higgs, the subjettiness ratio $\tau_{12}$
+the subleading Higgs,
+the energy correlation double ratio $D_2^{(\beta)}$
+Eq.~(\ref{eq:d2}) for the leading Higgs,
+and then 
+the subjettiness ratio $\tau_{12}$
 Eq.~(\ref{eq:tau21})
-for the leading Higgs,
-and the energy correlation double ratio $D_2$
-Eq.~\ref{eq:c2}
-for the leading and subleading Higgs.
+for both the leading and subleading Higgs candidates.
 %
-We can indeed verify that the shapes of the signal
-and background distributions are quite different,
-reflecting the differences in the internal structure of jets
-between QCD jets and jets originated from the Higgs decays.
-%
-This is true for all variables considered here.
-%
-As before, all the distributions in
-Fig.~\ref{fig:mva_substructure_1}
-have been normalized to unity.
-%
-All the distributions shown in this section refer to the boosted category.
 
@@
   \begin{center}
-    \includegraphics[width=0.48\textwidth]{plots/split12_H1_res_C1_boost.pdf} 
-  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_res_C1_boost.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_res_C1_boost.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_res_C1_boost.pdf}
+    \includegraphics[width=0.48\textwidth]{plots/split12_h1_C1_boost.pdf} 
+  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_h1_C1_boost.pdf}
   \caption{\small Distribution of substructure variables
@@
 
-Finally, let us show the distributions of those kinematic variables
+From Fig.~\ref{fig:mva_substructure_1}
+we can observe that for all variables the shapes of the signal
+and background distributions are quite different,
+reflecting the inherent differences in the internal structure of jets
+between QCD jets and jets originated from the Higgs decays.
+%
+Note that as before, all the distributions in
+Fig.~\ref{fig:mva_substructure_1}
+have been normalized to unity.
+%
+Importantly, we observe that signal and background distributions peak
+in different regions: for example, the $k_t$ splitting scale $\sqrt{d_{12}}$
+peaks around 80 GeV (50 GeV) for signal (background) events, while
+the ECF ratio $D_2^{(\beta)}$ peaks at much lower values for signal than
+for background events.
+%
+From Fig.~\ref{fig:mva_substructure_1} we also see
+the distributions of the subjettiness ratio $\tau_{12}$ are quite similar
+in the leading and in the subleading jets, therefore adding the value
+of  $\tau_{12}$ from the two Higgs candidates at the MVA at the same time
+is redundant, explaining why in these cases either one or the other
+variable from a Higgs candidate is assigned higher weight.
+
+Finally, let us show the distributions of kinematic variables
 that according to the MVA provide a small amount of discrimination
-between signal and background, either because there is no real information or
-because it is redundant.
+between signal and background, and where the should not be an issue
+of redundancy.
+%
+In Fig.~\ref{fig:mva_substructure_2}
+we show the kinematic variable that carries less weight in the MVA,
+    the azimuthal angle separation between the two Higgs candidates
+    $\Delta\phi_{hh}$, for the resolved and boosted categories:
+    according to Fig.~\ref{fig:nnweights}, no much discrimination power
+    is obtained here, and indeed the shapes of the two signal
+    and background
+    are very similar here.
+    %
+    From Fig.~\ref{fig:nnweights} we also saw that the
+    invariant mass distributions $m_h$ carry little information,
+    and this was verified from 
+the corresponding
+distributions in $m_{hh}$ from Fig.~\ref{fig:mHHinv}.
+%
+As explained before, the reason for this is
+the  smearing of jet four-momenta introduced to mimic
+realistically detector resolution.
 
-{\bf add missing histograms}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+  \includegraphics[width=0.48\textwidth]{plots/DeltaPhi_HH_C1_res.pdf} 
+  \includegraphics[width=0.48\textwidth]{plots/DeltaPhi_HH_C1_boosted.pdf} 
+  \caption{\small Same as Fig.~\ref{fig:mva_substructure_1},
+    now for the kinematic variable that carries less weight in the MVA,
+    the azimuthal angle separation between the two Higgs candidates
+    $\Delta\phi_{hh}$, for the resolved and boosted categories.
+}
+\label{fig:mva_substructure_2}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-13 paper/sec-results.tex
Updated common plot style

@@
 %
-In Appendix.~\ref{sec:overlap} we comment
+In Sect.~\ref{sec:overlap} we comment
 interplay of the overlap between the various categories.
@@
 We emphasize that it is important not only to achieve a good signal
-significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
+significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$:
 if the latter is too small, a measurement of the background with an infeasible small

### 2015-07-13 paper/plotscripts/plotAll.sh

@@ -1,0 +1,9 @@
+
+rm -rf *.pdf
+
+python2.7 ./plotHist_boosted_tau21_fj1.py
+python2.7 ./plotHist_boosted_tau21_fj2.py
+python2.7 ./plotHist_boosted_d12_fj2.py
+python2.7 ./plotHist_boosted_C2_fj1.py
+
+cp *.pdf ../plots/

### 2015-07-13 paper/plotscripts/plotHist_boosted_deltaPhi.py

@@ -7,23 +7,24 @@ import numpy as np
 datafiles = []
 plotnames = []
 
-linestyles = [ 'solid', 'dashed']
-
 ############################## Settings ###############################
 
 # Output filename
-outfile = "tau21_H0_C1_boost"
+outfile = "DeltaPhi_HH_C1_boosted"
+
+
+linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/oxford_combined_rw/signal/histo_tau21_fj1_boost_C1.dat")
-datafiles.append("../plotdata/oxford_combined_rw/background/histo_tau21_fj1_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/signal/histo_dPhi_HH_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/background/histo_dPhi_HH_boost_C1.dat")
 
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = r"Subjettiness Ratio $\tau_{12}$ for leading Higgs candidate"
+xLabel = r"$\Delta \phi_{hh}$"
 yLabel = "A. U."
 
 # Log axes
@@ -49,12 +50,11 @@ if xLog == True:
 if yLog == True:
   ax.set_yscale('log')
 
-  
 ax.set_ylabel(yLabel)
-ax.set_xlabel(xLabel)
+ax.set_xlabel(xLabel,fontsize=16)
 
-ax.set_xlim([0,1])
-ax.set_ylim([1e-3,10])
+ax.set_xlim([0.0,3.15159])
+ax.set_ylim([0.008,2])
 
 for idat in xrange(0,len(datafiles)):
 
@@ -112,14 +112,12 @@ for idat in xrange(0,len(datafiles)):
     xvals = [xlo[x], xhi[x]]
     yvalsup = [CVup[x], CVup[x]]
     yvalsdn = [CVdn[x], CVdn[x]]
-  
 
   # Insert lower x-values
   xhi.insert(0,xlo[0])
   yval.insert(0,yval[0])
 
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
-   
   icol=icol+1
 
 # Gridlines

### 2015-07-13 paper/plotscripts/plotHist_boosted_ptj2.py

@@ -10,13 +10,13 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "pt_H1_boost_C1"
+outfile = "pt_H1_res_C1"
 
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/oxford_combined_rw/signal/histo_pt_H1_boost_C1.dat")
-datafiles.append("../plotdata/oxford_combined_rw/background/histo_pt_H1_boost_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/signal/histo_pt_H1_res_C1.dat")
+datafiles.append("../plotdata/oxford_combined_rw/background/histo_pt_H1_res_C1.dat")
 
 # Plot labels
 plotnames.append("Signal")

### 2015-07-13 paper/sec-intro.tex

--- 2015-07-09 paper/sec-intro.tex
@@
 which aims to accumulate a total integrated
-luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta}.
+luminosity of 3 ab$^{-1}$~\cite{ATLAS:2013hta,CMS:2013xfa}.
 %
@@
 %
+While Standard Model (SM) cross-sections are small,
+many Beyond the SM (BSM)
+scenarios predict enhanced rates for double Higgs production, and
+thus searches for this process have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
+and will continue at Run II.
+%
 In addition, Higgs pair production will also be a central process at
 any future high-energy 
-collider, either at a 100 TeV circular machine~\cite{Barr:2014sga} or at
+collider, either at a 100 TeV circular machine~\cite{Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
 a linear or circular electron-positron collider~\cite{Contino:2013gna}.
 
-In the Standard Model (SM), the dominant mechanism for the production of two Higgs bosons at the LHC is 
+As in the case of single Higgs production,
+in the SM the dominant mechanism for the production of a pair of Higgs bosons at the LHC is 
 gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production~\cite{Dittmaier:2012vm}.
@@
 that the ultimate precision in the determination of the Higgs trilinear
+coupling $\lambda$
 will only be achieved from the combination of various final states.
@@
 can be also produced in the vector-boson fusion
-channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja},
-the associated production modes $hhW$ and $hhZ$, and also in association
+channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
+  Brooijmans:2014eja},
+the associated production modes $hhW$ and $hhZ$~\cite{Barger:1988jk,baglio}
+(also known as Higgs-Strahlung),
+and also in association
 with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
 %
-All these channels are extremely challenging due to the small production
+All these channels are challenging due to the small production
 rates: at 14 TeV, the inclusive total cross-sections are
@@
 %
-Concentrating on the SM production dynamics of Higgs pair
-production in the various channels, several studies
+Concentrating on the SM dynamics of Higgs pair production
+in different channels, several studies
 have investigate the interplay of various kinematical
@@
 higher-order corrections and theoretical
-uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza}
+uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
+  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha}.
 %
@@
 Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
-in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa},as well as
+in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, as well as
 in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
@@
 %
-With this motivation, searches for the production of Higgs pairs, whose rates
-could be enhanced by BSM effects have already been performed
+With this motivation, searches for the production of Higgs pair
+have already been performed at Run I
 by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
@@
 and by
-and CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
+CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
 and $b\bar{b}\gamma\gamma$~\cite{Chatrchyan:2011wt} final
@@
 %
-though the sensitivity of these searches is still far from
-that required for a SM production mechanism.
-%
-However, one should note that in general BSM dynamics modify substantially
+One should note that in general BSM dynamics modify substantially
 the kinematic distributions of the Higgs decay products, for
@@
 In the context of SM production,
-the main advantage of the $b\bar{b}b\bar{b}$ final state is the the signal yield
-is enhanced by the large branching fraction of Higgs bosons into bottom-anti-bottom
+the main advantage of the $b\bar{b}b\bar{b}$ final state is the
+enhancement of the signal yield
+from the large branching fraction of Higgs bosons into bottom-anti-bottom
 pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
@@
 However, a measurement in this channel
-needs to deal with an overwhelming QCD multi-jet background,
-which makes it very challenging.
+needs to deal with an overwhelming QCD multi-jet background.
 %
-Previous studies of Higgs pair production in this
+Recent studies of Higgs pair production in this
 channel~\cite{Wardrope:2014kya,deLima:2014dta}
 estimate that with a luminosity of
-3000 fb$^{-1}$ a signal significance of around $S/\sqrt{B}\sim 2.0$ can be obtained.
+$\mathcal{L}_{\rm int}$=3000 fb$^{-1}$ a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
 %
-Both studies were based on exploiting the differences between signal and background
+These studies are
+based on exploiting the differences between signal and background
 using techniques that account for a large number of kinematic
@@
 %
-Concerning the QCD multijet backgrounds, Refs.~\cite{Wardrope:2014kya,deLima:2014dta} the light-jet processes $bbjj$ and
-$jjjj$,
-which can fake the signal when 
+A limitation of these works is that
+they do not account
+ for the light-jet background processes $bbjj$ and
+$jjjj$, which can fake the signal when 
 some of the light jets are mistagged as $b$-jets.
@@
 contribution of $2b2j$ and $4j$ can become comparable
-to that of $4b$.
+to that of the irreducible $4b$ component.
 
@@
 %
-Our analysis is based on exploiting the differences between a large
-number of kinematic variables in signal and background events.
+ Our analysis is based on a combination of traditional cut-based
+ methods with modern multivariate techniques
+ (in particular feed-forward multi-layer neural networks),
+ which lead to a substantial
+  enhancement of the signal discrimination.
   %
-Despite these large QCD multijet backgrounds, by combining the contribution of different final state
-topologies, resolved, boosted and intermediate, with a careful optimization
-of the analysis strategy, we find that it is possible to obtain a reasonable
-good signal discrimination.
+  We account for  all relevant
+  backgrounds, including the contribution from light jet fakes.
   %
-To further enhance the significance of the measurements, signal and background events
-are processed using a Multivariate Analysis (in particular a feed-forward neural
-network), that further enhance $S/\sqrt{B}$ up to a value of slightly above 3.0
+  By combining the contribution from the boosted, intermediate and resolved
+  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
 %
-Therefore, we are able to rescue the potential of this final state in a realistic
-analysis setup.
+  Therefore, our strategy allow us to improve the
+  potential of this final state even when considering a
+  more realistic background modeling.
 
-One of the original motivations of this study was to provide guidance to the experiments
+  One of the original motivations of this study was to provide guidance to the
+  LHC experiments
 concerning which aspects of the measurement should be particularly optimized
-to increase the signal significance in this channel.
+to increase the signal significance in the $4b$ channel.
 %
-In this respect, the study the dependence on our results on the $b$-tagging mistag
-efficiency and the light and charm jet mistag rate, the jet energy and transverse
-momentum resolution, or the Higgs invariant mass resolution.
+In this respect, we study the dependence on our results on the $
+b$-tagging mistag
+efficiency, the light-jet mistag rate and the 
+momentum resolution.
 %
-In each of these cases, we determine the significance
+In each of these cases, we determine the signal significance
 $S/\sqrt{B}$ of the
 measurement in both conservative and optimistic assumptions of these
-parameters.
+analysis settings.
 
@@
 %
-In Sect.~\ref{mcgeneration} we discuss the generation of the signal
-and background Monte Carlo samples.
+In Sect.~\ref{mcgeneration} we discuss the modeling of the signal
+and background processes using Monte Carlo event generators.
 %
-Then in Sect.~\ref{sec:analysis}
-we describe our analysis strategy, and in particular
+In Sect.~\ref{sec:analysis}
+we introduce our analysis strategy, and in particular
 the classification of each individual event into
-different categories according to the event topology.
+different categories according to their topology.
 %
-The results for our traditional cut-based analysis
+The results for the traditional cut-based analysis
 are presented in Sect.~\ref{sec:results}, and in
 Sect.~\ref{sec:mva} we show how we can enhance signal
-significance by means of multivariate techniques.
+significance using multivariate techniques.
+%
+The robustness of our results as function of our assumptions
+on the $b$-tag rate, mistag probability and momentum
+resolution in quantified in Ref.~\ref{sec:optimisation}.
 %
 Finally in Sect.~\ref{sec:conclusions} we conclude and outline
-possible future developments for Higgs pair production
-in the $b\bar{b}b\bar{b}$ final state.
+how our results can be extended to estimate the accuracy
+in the determination of $\lambda$ and the constraints on
+BSM scenarios in an EFT framework.

### 2015-07-13 paper/sec-mcsamples.tex

@@
-\section{Monte Carlo samples}
+\section{Theoretical modeling of signal and background processes}
 \label{mcgeneration}
@@
 Higgs pair production is simulated at leading order using
-{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
-account.\footnote{We thank Eleni Vrodynou for assistance with di-Higgs production
-  in {\tt MadGraph5\_aMC@NLO}.}
+{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
 %
@@
 %
-We use the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
+We adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
 $\alpha_S(m_Z^2)=0.118$
@@
 For a similar reason, we don't consider underlying event, multiple parton interactions and
-pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia}.
+pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba}.
 %
@@
 \end{tabular}
-\caption{\small Summary of signal and background samples generated in this work,
+\caption{\small Summary of signal and background samples generated,
   together with the corresponding generator-level LO cross-sections.

### 2015-07-13 paper/sec-intro.tex
work in the paper

@@
 models have been performed in a number of different frameworks,
-including effective theories with higher-dimensional
+including Effective Field
+Theories (EFTs) with higher-dimensional
 operators and anomalous values of the
@@
 %
- Our analysis is based on a combination of traditional cut-based
- methods with modern multivariate techniques
+ Our strategy is based on a combination of traditional cut-based
+ methods with modern multivariate analysis (MVA)
  (in particular feed-forward multi-layer neural networks),

### 2015-07-13 paper/plotscripts/plotHist_boosted_ptHH.py

@@ -124,7 +124,7 @@ ax.xaxis.grid(True)
 ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.33,0.96,"Boosted category", fontsize=20)
+fig.text(0.33,0.92,"Boosted category", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-07-13 paper/sec-analysis.tex
work in the paper

--- 2015-07-13 paper/sec-analysis.tex
@@
 the classification of each individual event into
-different categories according to the event topology.
+different categories according to its topology.
 %
 First of all we discuss the settings and nomenclature that
-we will use for jet clustering in this work.
-%
-Then we move to discuss how $b$-tagging is simulated,
-following closely the ATLAS techniques.
+we will use for jet clustering, and then we move to discuss how $b$-tagging is simulated.
 %
 Then we discuss the categorisation of events between different
-topologies, and how we can prioritise among them.
+topologies, and how we prioritise among them.
+%
+Finally, we motivate our choice of analysis cuts by comparing signal and background
+for the relevant kinematic distributions.
 
@@
 
-In our study we will use different types of jet definitions,
-depending of the type of analysis that needs to be performed, optimized
-for the various possible event topologies.
-%
-Therefore, we being by enumerating the choices that we make.
-%
 The starting point after the parton shower is the clustering
-of all final state particles.
-%
-In this work all the jet reconstruction algorithms
+of all final state particles using the
+jet reconstruction algorithms
 are obtained from the {\tt FastJet} program~\cite{Cacciari:2011ma},
@@
 %
-We adopt the following terminology for the different types of jets
-that we will use in this work:
+In our study use different types of jet definitions,
+which we enumerate now:
+%
 
@@
   %
-  When reconstructing small-$R$ jets, we will keep only
+  When reconstructing small-$R$ jets, we keep only
   those jets with transverse momentum $p_T \ge 40$~GeV
   and pseudo-rapidity $|\eta|<2.5$ within the central
-  acceptance of ATLAS and CMS, jets that fail to satisfy these
-  conditions are discarded.
+  acceptance of ATLAS and CMS.
 %
+  Jets that fail to satisfy these acceptance
+  requirements are discarded.
+  %
+  The restriction to the central rapidity region is a
+  requisite for $b$-tagging.
 
@@
   The more restrictive range  in pseudo-rapidity
-  as compared to the small-$R$ jets,
+  as compared to the small-$R$ jets
   is motivated by mimicking the  experimental requirements
   in ATLAS and CMS
-  related to the track-jet-based calibration.
+  related to the track-jet-based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.
 
@@
   %
-  As we will discuss below, these small-$R$ subjets are the key of
+  These small-$R$ subjets will be the input of
   the $b$-tagging in the boosted category.
@@
   else they are discarded.
+  %
+\end{itemize}
 
-  \end{itemize}
+Let us mention that we explored the possible improvements
+in the analysis from using variable-$R$ jets~\cite{Krohn:2009zg}, but found that these made
+a small difference as compared to fixed-$R$ jets.
+%
+This is not unexpected, since variable-$R$ jets are more suitable when
+the degree of boost of the final state being reconstructed can span
+a wide range, such as in heavy resonance searches~\cite{Aad:2015fna}.
 
@@
 
-Given the final state that needs to be reconstructed in our case, the
+Given the $4b$ final state that needs to be reconstructed, the
 optimisation of the $b$-tagging capabilities of the
-LHC experiments is an essential requirement to optimise
-the prospects for the observation of Higgs pair production.
+LHC experiments is an essential requirement to improve
+the prospects for the observation of Higgs pair production in this channel.
 %
 The $b$-tagging used in this feasibility study is inspired
-in the current and projected ATLAS settings, and below
-we also comment on the differences and similarities with the
-corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}.
+in the current and projected ATLAS settings~\cite{Aad:2013gja},
+though
+it is not too different from
+ the corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}.
 %
 For each type of jet defined above, a different
-$b$-tagging strategy is used, as we discuss now.
+$b$-tagging strategy is used:
 
@@
   %
-  Note that the probability of tagging a jet is not modified
+  The probability of tagging a jet is not modified
   if more than one $b$-quark is found among the jet constituents.
@@
   We find that
-  trying to $b$-tag all
+  attempting to $b$-tag all
   small-$R$ jets that satisfy the acceptance cuts worsens the performance
-  due to combinatorics.
+  due to combinatorics after the parton shower.
 
@@
 
-    Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$
-    subjets (defined as above) to the original large-$R$ jets.
+    Large-$R$ jets are $b$-tagged by
+    ghost-associating anti-$k_T$ $R=0.3$
+    subjets to the original large-$R$
+    jets~\cite{Cacciari:2007fd,Aad:2013gja,
+      ATLAS-CONF-2014-004}.\footnote{The same
+    method was used in the recent ATLAS $hh\to 4b$ search~\cite{Aad:2015uka}.}
     %
@@
     the signal significance due to the increase in combinatorics.
-
-    Therefore, in this work we will exploit the capabilities of
-    the LHC experiment of double-$b$-tagging inside large-$R$ jets.
-    %
-    Below we comment on the dependence of our results if single-$b$-tagging
-    would be performed also for the large-$R$ jets, as done
-    for the small-$R$ jets.
 
@@
 Concerning the actual values of the $b$-tag probability $f_b$ and
-the $b$-mistag probability of light jets $f_l$, in this work
+the $b$-mistag probability of light jets $f_l$, 
 we adopt as baseline the values $f_b=0.8$ and $f_l=0.01$.
@@
 %
-There we also study the dependence of the results
-on other analysis settings related to the performance of
-the experiments, for example by varying the momentum smearing.
 
-\subsection{Event categorisation and cut flow}
+\subsection{Event categorisation}
 \label{sec:categorisation}
 
-After having introduced the types of jet reconstruction
-that we will use, as well as the $b$-tagging strategy,
-we need to discuss the analysis strategy, including
-the event categorization and the cut flow.
-
-The basic idea of this work is similar to that in Ref.~\cite{Gouzevitch:2013qca}:
+The basic idea of our analysis strategy is similar to that in Ref.~\cite{Gouzevitch:2013qca}:
 rather than concentrating only a specific event topology, such as boosted
@@
 the three possible event topologies: boosted, intermediate and
-resolved, which we define now.
+resolved.
 %
@@
 is that here each category is optimised separately, and then
-a exclusive categorisation is defined starting from the topology
-where the signal significance is the best.
+a exclusive categorisation is defined starting from the category
+with the highest signal significance.
+%
+An advantage of our approach is that the analysis strategy would be unchanged
+if the underlying production model is varied, for example in the case of
+BSM dynamics.
 
 Let us therefore define the three event categories that
-we use in this work:
+we use:
 \begin{itemize}
@@
 
-  A given event is assigned to the {\it boosted} category if it
+  An event is assigned to the {\it boosted} category if it
   contains at least two large-$R$ jets, defined as above,
   and where  the two leading large-$R$ jets have been
-  successfully double-$b$-tagged.
+   double-$b$-tagged.
   %
@@
   An event is assigned to the {\it intermediate} category if
-  at least one large $R$ double-$b$-tagged jet is present.
-  %
-  If more than one is found, then the leading large-$R$ jet
-  is assigned to be the first Higgs candidate.
+  one and only one large $R$ double-$b$-tagged jet is present,
+  which corresponds to the the first Higgs candidate.
   %
@@
 
-  Then, the second Higgs boson candidate is reconstructed
+  The second Higgs boson candidate is reconstructed
   by selecting the two $b$-tagged small-$R$ jets that minimize the difference
@@
   m_{sR_1+sR_2}\rp$, where $lR_1$ indicates the leading large-$R$ jet
-  and $sR_1$ and $sR_2$ indicate the small-$R$ jets.m
+  and $sR_1$ and $sR_2$ indicate the small-$R$ jets.
 
 \item {\it Resolved category}.
-
-  Finally, let us define the {\it resolved} category.
   %
-  An event is assigned to this category
+  An event is assigned to the {\it resolved} category
   if at least
@@
 \end{itemize}
-Note that in principle these three categories are not exclusive:
+Note that these three categories are not exclusive:
 a given even can be assigned to more than one category, for
@@
 categories at the same time.
+%
+The exception is the boosted and intermediate categories, which have
+orthogonal jet selection requirements.
 
-Once a pair of Higgs boson candidates has been identified,
-then events from each category are required to satisfy the usual
-Higgs mass window cut, defined by
-the following condition
+Once a Higgs boson candidate has been identified,
+its invariant mass is required to be within a fixed window
+around the nominal Higgs boson mass.
+%
+In particular we require the condition
 \be
 \label{higgsmasswindow}
-|m_{h,j} - 125| < 40~{\rm GeV} \, , j=1,2 \, ,
+|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
 \ee
-where $m_{h,j}$ is the invariant mass of the two Higgs candidates
-reconstructed as explained above.
+where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
 %
-We note that this cut is substantially looser as the corresponding
+This cut is substantially looser as the corresponding
 cut used in the typical ATLAS and CMS $h\to b\bar{b}$
 analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
-for this is that the MVA will take care of the optimisation of these
+for this choice is that the MVA will take care of the optimisation of these
 and other cuts that are not explicitly performed.
+%
+Only events where the two Higgs candidates satisfy the
+condition in Eq.~(\ref{higgsmasswindow}) are classified as signal events.
 
@@
 %
-We emphasize again that each category is not exclusive of the others,
-and in general there can be a substantial overlap
+We emphasize again that each category is not exclusive,
+and in general there will be a substantial overlap
 between the different categories.
 %
-In particular, this overlap is a direct consequence that
-the different categories are optimised separately, as opposed
-to the approach of~\cite{Gouzevitch:2013qca}, where optimisation
-was performed simultaneously in the combination of exclusive categories.
+This overlap is a direct consequence that
+the different categories are optimised separately.
 
@@
     Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
-    jets  &  $\ge$ 4 small-$R$ jets \\
+    jets  &  $\ge$ 4 small-$R$ jets \\[0.2cm]
     \hline
@@
     &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
-    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
+    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\[0.2cm]
     \hline
@@
     &  & and 2 single-$b$-tags  &  \\
-       & $\ge 2$ small-$R$ subjets  & &  \\
-    &  $p_T^{\rm sj}\ge 50$ GeV &   &  \\
+    & and $\ge 2$ small-$R$ subjets  &  and $\ge 2$ small-$R$ subjets  &  \\
+     &  in large-$R$ jets  &  in large-$R$ jet &  \\
+    &  $p_T^{\rm sj}\ge 50$ GeV & $p_T^{\rm sj}\ge 50$ GeV   &  \\[0.2cm]
+    \hline
+    Mass-Drop Tag  &  Two leading large-$R$ jets  &  Large-$R$ jet &   \\
     \hline
@@
 
-As we will show now, the selection requirement and the kinematic cuts
+The selection requirements and the kinematic cuts
 for each of the categories in Table~\ref{sec:categorisationTable} have
@@
 %
-First of all we have performed a inclusive analysis, and optimised
+First of all we have performed a inclusive analysis, and optimised the
+signal significance
 $S/\sqrt{B}$ in each of the three categories separately, including
@@
 %
-We find that, in terms of signal significance, the ordering of
-the categories is
-\begin{enumerate}
-\item Boosted 
-\item Intermediate
-  \item Resolved
-  \end{enumerate}
-and therefore for the final analysis we turn to an exclusive approach:
+We find that the category with higher significance turns out to be the boosted,
+followed by the intermediate and the resolved ones.
+%
+Therefore for the final analysis we turn to an exclusive approach:
 if an event satisfies the boosted requirements, it is kept for
 these category, else we check if it suits the intermediate
-requirements, and failing also this, the event is attempted
-in the resolved categories.
+requirements, and failing also this, the event is attempted to
+be classified in the
+resolved category.
 %
 The resulting exclusive event samples are then separately processes
-through the MVA, as discussed in the next section.
+through the MVA.
 %
@@
 (boosted) with that of the sub-leading categories, intermediate
-and resolved.
+and resolved, without the problem of the double counting.
 
-\subsection{Cut optimisation}
+\subsection{Optimisation of kinematical cuts}
 
-In this section we motivate the various
+We now motivate the values of
 kinematical cuts applied to the different categories.
@@
 %
-Here we show the various kinematic distributions immediately
-below the corresponding cut has been applied.
+Here we show the various kinematic distributions 
+before the corresponding cut has been applied.
 %
-Only a representative subset of
-all available kinematic distributions will be shown here, the complete
-set of plots, including the distribution of all substructure
-variables used in the MVA later, have been collected
-in this webpage:
-\begin{center}
-\url{http://www2.physics.ox.ac.uk/HH4b}
-  \end{center}
-In this section we restrict to the discussion of the
+For illustration purposes,
+only a representative subset of
+all available kinematic distributions will be shown here.
+%
+For simplicity,
+we restrict to the discussion of the
 kinematic distributions of the boosted
-and resolved categories, the corresponding results for the
-intermediate category are collected in the same webpage.
+and resolved categories.
 
@@
 
-In the intermediate category,
+In the resolved category,
 it is important to understand the $p_T$ distribution
@@
 %
-Given that in general the boost from the Higgs decays is moderate,
+As noted in~\cite{deLima:2014dta}
+given that in general the boost from the Higgs decays is moderate,
 the two subleading jets might be not too hard, and thus it
@@
 
-Next in Fig.~\ref{fig:mHHinv} we show the invariant mass
+Next, in Fig.~\ref{fig:mHHinv} we show the invariant mass
 of the leading reconstructed Higgs candidates, before the Higgs mass window
-cut is applied, for the resolved and boosted categories.
+cut Eq.~(\ref{higgsmasswindow})
+  is applied, for the resolved and boosted categories.
 %
@@
     Higgs candidates on the resolved (left plot) and boosted (right
-    plot) categories.
+    plot) categories. {\bf redo boosted case with correct axes range}
 }
@@
 %
-While we don't cut in this quantity, it is
+While we don not cut in this quantity, it is
 one of the inputs for the MVA to help to improve signal discrimination.
@@
 %
+Again we see that the background has a steeper $p_T^{hh}$ distribution
+that the signal, in both categories, thus this variable
+should provide some additional discrimination power, and therefore
+we will use it as another of the MVA inputs.
+%
 Note that in our LO simulation this distribution is generated purely
@@
 %
-Again we see that the background has a steeper $p_T^{hh}$ distribution
-that the signal, in both categories, thus this variable
-should provide some additional discrimination power, and therefore
-we will use it as another of the MVA inputs.
+Nevertheless, the MVA shows only limited sensitivity to this variable, so its
+modelling appears not to be crucial in our case.
 
@@
   \includegraphics[width=0.48\textwidth]{plots/pt_HH_boost_C1.pdf}
-  \caption{\small Left plot: the invariant mass distribution of the Higgs
-    pair candidates, $m_{hh}$, comparing signal and background events,
-    in the resolved category.
-    %
-    Right plot: same for the boosted category.
+  \caption{\small Same as Fig.~\ref{fig:mhh} for the transverse momentum
+    distribution of the di-Higgs system $p_T^{hh}$.
 }

### 2015-07-13 paper/sec-mva.tex
Work on paper

@@
 
-After the traditional cut-based analysis presented in the previous section,
-and combining the significance of the different event categories,
-we end up with a $S/\sqrt{B}$ value around $1.2$.
+From the cut-based analysis,
+combining the significance of the three categories,
+we end up with a signal significance $S/\sqrt{B}\simeq 1.2(2.3)$
+with all backgrounds (only QCD $4b$) taken into account,
+which is not enough to be able to claim observation
+of Higgs pair production
+in this channel, and even less to extract the trilinear Higgs  coupling
+$\lambda$.
 %
-This is not enough to claim observation in this channel.
-%
-however, the attentive reader might have noticed that we have used
-relatively 
-loose kinematics cuts, for example in the Higgs mass window.
-%
-The motivation for this is that the $n$-tuples of signal and background
-events, after our basic selection, are processed though a multivariate
-analysis with the motivation to increase the signal over background
+We now process  the $n$-tuples of the signal and background
+events that survive the cut-based
+analysis by means of a multivariate
+analysis, in order increase the signal over background
 significance.
@@
 Multivariate techniques are by now a common tool to enhance signal
-significance in HEP analysis, and rightly so,
+significance in HEP analysis, and this is fully justified
 since they open a new window to improve the performance
@@
 Decision Tree MVA to improve signal discrimination.
+
+In this section first of all we present the specific MVA that we use,
+based on feed-forward multi-layer neural networks.
+%
+We then describe the input variable to the MVA, including the jet substructure
+variables, and then present the results of $S/sqrt{B}$ including
+the MVA effects.
+%
+Since we find that jet substructure variables are a crucial input
+to the MVA, we end this section showing various kinematic distributions
+of these variables.
+
+{\bf add more refs from ATLAS and CMS}
 
@@
 disentangle signal and background events in the $hh\to 4b$ process,
-in particular we use a feed-forward artificial neural network (ANN).
+in particular we use a multi-layer feed-forward artificial neural network (ANN),
+also known as a {\it perceptron}.\footnote{This type of ANNs are the same
+  as those used to parametrize Parton Distribution Functions
+in the NNPDF global analyses~\cite{DelDebbio:2004qj,Ball:2008by,Ball:2011mu,Ball:2010de}.}
 %
-The basic idea is that the ANN is given both all MC signal and background
-events which satisfy the basic selection cuts {\bf C1}, allowing to identify
+The basic idea is that the ANN is trained on an input composed on
+all  signal and background
+events which satisfy the
+cut-based analysis, allowing to identify in an automated way
 which are the most relevant variables to discriminate between the two.
@@
  minimization of the cross-entropy error,
- Eq.~\ref{cross-entropy}, which in this work is achieved using a
+ Eq.~(\ref{cross-entropy}), which in this work is achieved using a
  Genetic Algorithm.
@@
  We have also verified that using a cross-validation stopping
- criterion as in the NNPDF3.0 fits does not affect the results.
+ criterion (in particular, the same one as
+ that used in the NNPDF3.0 fit~\cite{Ball:2014uwa})
+ does not modify the results.
 
@@
 the input variables for the MVA differ between our three categories,
-since in the case of large-$R$ jet reconstruction we want to exploit
+and in particular in the case of large-$R$ jets we want to exploit
 the richness of substructure information.
@@
 \item The transverse momenta of the leading and subleading Higgs, $p_{T,h_1}$ and $p_{T,h_2}$.
-\item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$
+\item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$.
 \item The invariant masses of the leading and sub-leading Higgs candidates, $m_{h,1}$ and $m_{h,2}$.
@@
 \item The separation in $\eta$  between the two Higgs candidates, $\Delta \eta_{hh}$.
-\item In the boosted category,
+\end{itemize}
+In addition, in the boosted category we use
   the transverse momenta of the leading, $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and
@@
   %
-  In the resolved category instead, we use the transverse momenta $p_{T,i}$ of the four leading 
+  In the resolved category instead,
+  the corresponding variables are
+  the transverse momenta $p_{T,i}$ of the four leading 
   $b$-tagged small-$R$ jets in the event.
-\end{itemize}
+  %
+  In the intermediate category, we use the
+  transverse momenta of the subjets
+  from the large-$R$ jet $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and the
+ transverse momenta $p_{T,i}$ of the two leading 
+  $b$-tagged small-$R$ jets.
+  %
 Therefore, we have a total of 13 variables which are common to the three categories.
@@
 namely for the boosted and intermediate categories,
-a number of jet substructure variables~\cite{Aad:2013gja} is used
-for every large-$R$ jet that is used for the Higgs reconstruction.
+a number of jet substructure variables~\cite{Salam:2009jx,Aad:2013gja} is used
+for every large-$R$ jet that is classified as a Higgs candidate.
 %
-In particular we include in the MVA training for each large-$R$ jet
+In particular we include in the MVA training for each large-$R$ jet the following
+substructure variables:
 \begin{itemize}
-\item The $k_T$ splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}.
+\item The $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}.
 
@@
   \label{eq:ktsplitting}
-\sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, ,
+\sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, .
 \ee
-where one can also define related variables like $\sqrt{d_{23}}$ that corresponds to the
-splitting scale in the second-to-last clustering.
+It is also possible to define related variables like $\sqrt{d_{23}}$
+that corresponds to the
+splitting scale in the second-to-last clustering, though we do not use
+it here since it is only relevant for three-prong decays.
 
@@
   The $N$-subjettiness variables $\tau_N$ are defined by clustering the constituents
-  of a jet with the exclusive $k_t$ algorithm and requiring that $N$ subjets are found,
+  of a jet with the exclusive $k_t$ algorithm~\cite{Catani:1993hr}
+  and requiring that $N$ subjets are found,
   \be
@@
   \ee
-  with $ p_{T,k}$ the $p_T$ of the constituent $k$ and $\delta R_{ik}$ the distance from
+  with $p_{T,k}$ is the $p_T$ of the constituent particle $k$ and $\delta R_{ik}$ the distance from
   subjet $i$ to constituent $k$.
   %
-  In this work in particular we use as input to the MVA
+  In this work we use as input to the MVA the ratio of 2-subjettiness to 1-subjettiness
   \be
@@
   \ee
-  which provide good discrimination between QCD jets and jets arising from the decay of
+  which provides good discrimination power
+  between QCD jets and jets arising from the decay of
   a heavy resonance.
 
-\item The ratios of energy correlation functions (EDFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
+\item The ratios of energy correlation functions (ECFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
   $D_2^{(\beta)}$~\cite{Larkoski:2014gra}.
@@
 %
-As we will show, the use of substructure variables in the MVA is the key to increase the signal
-significance in the boosted category.
 
-\subsection{Enhancing signal discrimination with MVA}
+\subsection{Signal significance after the MVA}
 
@@
 \label{eq:totweight}
-\omega^{\rm tot}_i \equiv \sum_{k=1}^5 \Big|\omega^{(2)}_{ki}\Big| \, ,
+\omega^{\rm tot}_i \equiv \sum_{k=1}^{n^{(2)}} \Big|\omega^{(2)}_{ki}\Big| \, ,
 \qquad i=1,\ldots,N_{\rm var} \, ,
@@
 the $k$-th neutron of the second layer with the $i$-th neuron of
-the first (input) layer.
+the first (input) layer, and $n^{(2)}=5$ the number of
+neurons in the second layer.
 %

### 2015-07-13 paper/sec-results.tex
Work on paper

@@
 
-\section{Results for the cut-based analysis}
+\section{Results of the cut-based analysis}
 
@@
 
-In this section we discuss the results of the traditional
-cut-based analysis, using the analysis strategy presented in the previous
-section.
+In this section we present the results of the 
+cut-based analysis and
+compare our results with other recent related studies.
 %
-We compare our results with other recent related studies,
-and in particular we study how the signal significance
-is modified if only the $4b$ QCD background is taken into account,
-but the $2b2j$ and $jjjj$ backgrounds are neglected.
+We study how the signal significance
+is modified if only the $4b$ component of the
+QCD multi-jet background is taken into account,
+but the $2b2j$ and $4j$ components are neglected.
 %
-Then in the next section we show how using multivariate techniques
-one can substantially improve the signal significance as compared
-to the cut-based analysis.
+We also study the role of the overlap
+between the different categories.
 
-\subsection{Signal significance}
+\subsection{Cut flow and signal significance}
 
 First of all we compare the cross-sections at various
-analysis levels for the three categories, for signal and background,
+analysis levels for the three categories, for signal and background events,
 by providing a detailed cut-flow.
 %
-Here we consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
-and below we discuss how results are modified if only the $4b$
-multijet background is used.
+We consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
+then we discuss how results are modified if only the $4b$
+component is kept.
 %
-In particular,
 we consider the following levels of the cut-flow
@@
 %
-Of course at the {\bf C0} level the numbers will be the same
+At the {\bf C0} level the numbers will be the same
 for the three individual categories.
@@
 In the following, results are presented for the exclusive
-categorisation, as discussed in Sect.~\ref{sec:categorisation}.
+categorisation defined in Sect.~\ref{sec:categorisation}.
 %
-In Sect.~\ref{sec:overlap} we comment
-interplay of the overlap between the various categories.
 %
@@
 of events that would be expected at the HL-LHC with
-an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
+an integrated luminosity of $\mathcal{L}_{\rm int}
+=3000$ fb$^{-1}$,
 as well as 
@@
 significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$:
-if the latter is too small, a measurement of the background with an infeasible small
+if the latter is too small, a very accurate
+measurement of the background with an infeasible small
 systematic uncertainty would be required.
@@
     %
-    See text for more details.
     \label{table:cutflow}
@@
 %
-Let us begin with the discussion of the boosted category, that as we have explained
-is the one that benefits from a higher signal significance.
+Let us begin with the discussion of the boosted category, the one that
+leads to a higher signal significance.
 %
 We see that after all the cuts, including $b$-tagging,
-we end up with almost 200 signal events at the HL-LHC, and
+we end up with almost 200 signal events at the HL-LHC, with
 still a substantial background of around $40k$ events.
@@
 but using more aggressive cuts, we have refrained doing so
-since we prefer this optimisation to per performed by
+since we prefer this optimisation to be performed at the level of
 the MVA.
 
-Note that from the results of Table~\ref{table:cutflow}
-it is easy to compute the corresponding numbers
+From the results of Table~\ref{table:cutflow}
+it is possible to compute the corresponding numbers
 for the end of Run II at the LHC with
@@
 once we include the effects of the MVA in the analysis, but
-it is clear already at this level that, unless rates are
-increased by new BSM dynamics, one really needs the full
+it is clear already at this level that one really needs the full
 integrated luminosity of the HL-LHC to be able to observe
-the Higgs pair production process.
+the Higgs pair production process, unless  of course production rates are
+increased by new BSM dynamics
 
 Both the intermediate and resolved categories benefit from higher signal yields,
-specially in the resolved category, but this enhancement is canceled by the stronger
+specially in the resolved category, but this enhancement is washed out by the stronger
 increase in the QCD multi-jet background.
 %
-We see that in both cases the signal significance is around half of that in the boosted category,
+In both cases the signal significance is around half of that in the boosted category,
 with in addition $S/B$ being an order of magnitude smaller.
@@
 %
-We discuss in the next section how this significance can be enhanced by means
-of multivariate analysis.
 
@@
 %
-As we show next, once the MVA is used, we manage to outperform these previous
-works.
+Indeed, combining the signal significance in the three categories, we end
+up with a final $S/\sqrt{B}\simeq 2.3$.
+%
+As we show next, once the MVA is used, we achieve a substantial
+improvement
+over previous works, even after taking into account our rather more
+complete modelling of the QCD multijet background.
 
@@
 %
-All the backgrounds have been normalized to known higher-order results,
+Recall that all the backgrounds have been normalized to known higher-order results,
 as summarized in Table~\ref{tab:samples}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
+\begin{table}[h]
   \centering
@@
 should be included.
+%
+On the other hand, we find that the hadronic $t\bar{t}$ component of the backround
+is smaller than the QCD multijet one.
 
@@
 \begin{center}
+ \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_back.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_boost_back.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_back.pdf}
+   \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_res_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_boost_back.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_res_back.pdf}
   \caption{\small
@@
 
-  \subsection{Overlap between different categories}
+  {\bf compare parton level with hadron level distributions}
+
+  \subsection{The role of the overlap between different categories}
 \label{sec:overlap}
@@
   and intermediate categories due to the
-   orthogonal jet multiplicity cuts.
+   orthogonal jet multiplicity cuts. {\bf update including event weights}
 }

### 2015-07-13 paper/plotscripts/plotHist_boost_ptHH_back.py

@@ -47,7 +47,7 @@ icol = 0
 
 # Setup figure
 fig, ax = plt.subplots()
-fig.text(0.33,0.96,"Boosted category", fontsize=20)
+fig.text(0.33,0.92,"Boosted category", fontsize=20)
 if xLog == True:
   ax.set_xscale('log')
 if yLog == True:

### 2015-07-13 paper/sec-mva.tex
small additions to bibliography

@@
 background processes via the use of a multivariate analysis is a common
-technique in high energy physics~\cite{Baldi:2014pta,Wardrope:2014kya}.
+technique in high energy physics~\cite{Baldi:2014pta,Wardrope:2014kya,Chatrchyan:2013zna}.
 %

### 2015-07-14 paper/sec-mva.tex
work on the paper

--- 2015-07-13 paper/sec-mva.tex
@@
-\section{Multivariate analysis}
+\section{Results from the multivariate analysis}
 \label{sec:mva}
@@
 combining the significance of the three categories,
-we end up with a signal significance $S/\sqrt{B}\simeq 1.2(2.3)$
-with all backgrounds (only QCD $4b$) taken into account,
-which is not enough to be able to claim observation
+we end up with a signal significance of $S/\sqrt{B}\simeq 1.2(2.3)$
+with all backgrounds (only QCD $4b$) taken into account.
+%
+This does not seem
+to be enough to be able to claim observation
 of Higgs pair production
 in this channel, and even less to extract the trilinear Higgs  coupling
-$\lambda$.
+$\lambda$ with good precision.
 %
-We now process  the $n$-tuples of the signal and background
-events that survive the cut-based
-analysis by means of a multivariate
-analysis, in order increase the signal over background
-significance.
+In this section we show how the signal significance for
+our process can
+be substantially improved when
+applying a multivariate analysis (MVA) to the events
+ that survive the cut-based
+ analysis.
+
 %
@@
 %
-For instance, the UCL $hh\to 4b$ analysis~\cite{Wardrope:2014kya}
-uses a Boosted
-Decision Tree MVA to improve signal discrimination.
+In particular, the classification of events as arising from either signal or
+background processes via the use of a multivariate analysis is becoming
+a mature
+technique in LHC
+applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
+  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.
+%
+For instance, the CMS $Vh(\to b\bar{b})$ analysis~\cite{Chatrchyan:2013zna}
+is based on a Boosted Decision Tree (BDT) MVA, and the UCL $hh\to 4b$
+feasibility study~\cite{Wardrope:2014kya}
+also used  a BDT to improve signal discrimination.
 
-In this section first of all we present the specific MVA that we use,
+In this section, first of all we present the specific MVA that we use,
 based on feed-forward multi-layer neural networks.
 %
-We then describe the input variable to the MVA, including the jet substructure
-variables, and then present the results of $S/sqrt{B}$ including
+We then introduce the input variables that are
+used the MVA, including the jet substructure
+variables, and then present the results of $S/\sqrt{B}$ including
 the MVA effects.
@@
 
-{\bf add more refs from ATLAS and CMS}
-
 \subsection{MVA strategy: deep neural networks}
 
-The classification of events as arising from either signal or
-background processes via the use of a multivariate analysis is a common
-technique in high energy physics~\cite{Baldi:2014pta,Wardrope:2014kya}.
 %
@@
 disentangle signal and background events in the $hh\to 4b$ process,
-in particular we use a multi-layer feed-forward artificial neural network (ANN),
+a multi-layer feed-forward artificial neural network (ANN),
 also known as a {\it perceptron}.\footnote{This type of ANNs are the same
@@
 %
+This family of ANNs is sometimes known as {\it deep} neural networks.
+%
 The basic idea is that the ANN is trained on an input composed on
 all  signal and background
-events which satisfy the
-cut-based analysis, allowing to identify in an automated way
+events which satisfy the requirements of the
+cut-based analysis.
+%
+The main result of the trained ANN is identifying, in a fully automated way,
 which are the most relevant variables to discriminate between the two.
@@
 
-Let us now present the results of the MVA applied to the event samples
-that satisfy the cut-based analysis discussed in the previous section.
+In Fig.~\ref{fig:nnresponse} we show the distribution of
+the ANN output at the end of the training, for the exclusive
+boosted, intermediate and resolved categories.
 %
-First of all in Fig.~\ref{fig:nnresponse} we show the distribution of
-the ANN output, after the training for signal and background events, for the three
-exclusive categories.
-%
-All distributions have been normalized, so that their integral
+The distributions are normalized so that their integral
   adds up to one.
 %
-Given that the final separation between signal and background will be achieving by introducing
-a cut in the ANN output, the more separated that the two distributions are, the more efficient
+The  separation between signal and background is achieving by introducing
+a cut, $y_{\rm cut}$, in the ANN output, so that MC events with $y_i\ge
+y_{\rm cut}$ are classified as signal events, and those with
+ $y_i <
+y_{\rm cut}$ as background events.
+%
+Therefore,
+the more separated that the two distributions are, the more efficient
 the MVA discrimination will be.
@@
 %
-This indicates that introducing a suitable cut in the ANN output will substantially reduce the background,
+This indicates that introducing a suitable cut
+$y_{\rm cut}$
+in the ANN output will substantially reduce the background,
 while keeping a reasonable signal efficiency.
@@
 We have traced back these differences to the use of jet substructure variables
-in the boosted and intermediate categories, which induce the maximum
+in the boosted and intermediate categories, whose use substantially
+improves the
 discrimination between signal and background events.
@@
 background rejection rate as a function of the cut in the ANN output
+$y_{\rm cut}$
 define the so-called  Receiver-Operating Characteristic (ROC)
@@
 %
-It is clear that we can achieve a very high signal efficiency by using
+It is clear that we can achieve  high signal efficiency by using
 a small value of the cut in the ANN output, but this choice will be
@@
 %
-The usefulness of ROC curves is that they allow to determine the
+The usefulness of ROC curves is that they allow to determine and
 optimal cut value that removes enough background without degrading too much the signal efficiency.
 %
-In addition, it is important to select a value of the cut in ANN output so that
-the number of expected signal events is still large enough.
+Another important requirement on the value of $y_{\rm cut}$ is that
+the  number of expected  signal events (the physical
+events for a given integrated
+luminosity, not the MC events used for the ANN training)
+after the cut is large enough.
 
@@
 \caption{\small ROC curve for the background rejection rate as a function of the signal
-  selection efficiency as the cut in the ANN output is varied.
+  selection efficiency, as the cut in the ANN output is varied.
   %
@@
 one can achieve a  signal
-efficiency of $\sim 80\%$ while reducing the background by
-$60\%$, $55\%$ and $45\%$ in the boosted, intermediate and resolved
+efficiency of $\sim 90\%$ while reducing the background by
+$80\%$, $60\%$ and $50\%$ in the boosted, intermediate and resolved
 categories respectively.
@@
 %
-For example, requiring a signal efficiency of 90\%, we find a background rejection
-rate of $40\%$, $30\%$ and $20\%$ respectively, which corresponds to an increase
-in $S/\sqrt{B}$ of 1.2, 1.1 and 1.0 respectively.
+As an illustration, if a signal efficiency of 90\%
+is required, we find that the MVA improves $S/\sqrt{B}$
+by  approximately 2.0, 1.4 and 1.3  in the three categories respectively.
 
-Of course, and important restriction on the range of allowed cuts in the ANN output
-is that the cut cannot be so hard that the actual number of signal events expected
+As mentioned above, an
+ important restriction on the range of allowed cuts in the ANN output
+ is that $y_{\rm cut}$
+ cannot be so hard that the actual number of signal events expected
 at the HL-LHC becomes unreasonably small.
@@
 we show in Fig.~\ref{fig:nev2} the number of signal (dashed lines) and background (solid lines)
-  events expected at the HL-LHC as a function of the cut in the ANN output,
-  for the three separate categories.
+  events expected at the HL-LHC as a function of $y_{\rm cut}$,
+  for the three exclusive categories.
   %
-  Note that the value of the cut in the ANN cut can be separately optimised in the three
-  categories, even if here we plot them together for easiness of presentation.
+  Note that the value of the cut in the ANN cut is separately optimised in the three
+  categories.
 
@@
 As can be seen from Fig.~\ref{fig:nev2}, in the boosted category
-event with a cut in the ANN output as hard as 0.9 we are still left
+event with a cut in the ANN output as hard as $y_{\rm cut}\simeq 0.9$
+we are still left
 with around 100 events at the HL-LHC, which is a reasonable number,
@@
 
-A very useful property of MVA's such as the one used in this work
+A very useful property of MVAs such as the one used in this work
 is that they provide direct  physical insight about which of the
@@
 
-\subsection{Another look at the jet substructure variables}
+\subsection{Another look at jet substructure variables}
 
@@
 the $\tau_{21}$ subjettiness ratio, and the ECF ratios
-$C_2^{{\beta}}$ and $D_2^{{\beta}}$.
+$C_2^{(\beta)}$ and $D_2^{(\beta)}$.
 %

### 2015-07-14 paper/sec-mva.tex
work on paper

@@
 which the background being reduced substantially to around
-500 events.
+1000 events.
 %
@@
 
-A very useful property of MVAs such as the one used in this work
+A useful property of MVAs such as the one used in this work
 is that they provide direct  physical insight about which of the
-input variables contribute the most to the signal over background
-separation.
+input variables contribute the most to the separation of
+signal over background.
 %
@@
 %
-The scale of the $y$ axis is arbitrary, and the important information
+The important information
 is contained in the relative strengths of the total associated weight
 for each of the input variables.
+%
+The results of Fig.~\ref{fig:nnweights} illustrate which variables
+are more discriminative between the signal and the background.
+%
+For instance, in the 
+resolved category, the variables that lead to
+a higher discrimination power
+are the $p_T$ of the two reconstructed Higgs candidates, and then on a similar
+footing other variables like the $p_T$ of the individual jets
+and the mass of the di-Higgs system.
+%
+The only variable which seems to contain to information at all
+is the $\Delta \phi_{hh}$ separation between the two
+Higgs candidates.
 
@@
 \begin{center}
-\includegraphics[width=0.48\textwidth]{plots/res_wgthist.pdf}
-\includegraphics[width=0.48\textwidth]{plots/boosted_wgthist.pdf}
+\includegraphics[width=0.49\textwidth]{plots/res_wgthist.pdf}
+\includegraphics[width=0.49\textwidth]{plots/boosted_wgthist.pdf}
+\vspace{-0.5cm}
 \caption{\small
@@
 See Sect.~\ref{sec:input} for a description of each of the input
-variables to the MVA in the two cases.
+variables to the MVA.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-
-The results of Fig.~\ref{fig:nnweights} clearly illustrate which variables
-are more discriminative between the signal and the background.
-%
-Let's begin discussing the resolved analysis.
-%
-In this category, the variables that lead to
-a higher discrimination power
-are the $p_T$ of the two reconstructed Higgs, and then on a similar
-footing other variables like the $p_T$ of the individual jets
-and the mass of the di-Higgs system.
-%
-The only variable which seems to contain to information at all
-is the $\Delta \phi_{hh}$ separation between the two
-Higgs candidates.
 

### 2015-07-14 paper/plotscripts/plotMVAdat.py

@@ -43,20 +43,20 @@ def plotDiscriminantHisto(name, signal, background):
 	bins = numpy.linspace(0, 1, 20) # Binning density
 	fig, ax = plt.subplots()
 
-	ax.hist(signal, bins, color='r', alpha=0.5, normed=True, label = "Signal")
-	ax.hist(background, bins, color='b', alpha=0.5, normed=True, label = "Background")
+	ax.hist(signal, bins, color='r', alpha=0.8, normed=True, label = "Signal",linewidth=2)
+	ax.hist(background, bins, color='b',fill=False, alpha=0.8, edgecolor='b',normed=True, label = "Background",hatch="//",linewidth=2)
 
-	ax.set_ylim([0,8])
+	ax.set_ylim([0,10])
 	ax.set_xlabel("ANN Output")
         ax.set_ylabel("A. U.")
 
 	# Legend
-	legend = ax.legend(fontsize=14, loc='best')
-	legend.get_frame().set_alpha(0.7)
+	legend = ax.legend(fontsize=18, loc='best')
+	legend.get_frame().set_alpha(0.8)
 
 	numpoints = str( len(background) + len(signal) ) + " events: " + str(len(signal)) + " signal, " + str(len(background)) + " background."
 	# fig.text(0.13,0.92,numpoints, fontsize=12)
-	fig.text(0.13,0.96,"MVA for "+ name + " category", fontsize=16)
+	fig.text(0.35,0.92,name + " category", fontsize=19)
 
 	figname = name + "_"+Histout+".pdf"
 	fig.savefig(figname)
@@ -145,7 +145,7 @@ for idat in xrange(0,len(datafiles)):
 			total_sigweight = total_sigweight + float(line.split()[2]) # Weight
 
 	#### ROC Curve and S/B plot
-	thresholds = numpy.linspace(0, 1, 100)
+	thresholds = numpy.linspace(0, 1, 2)
 	falsepos = []
 	truepos = []
 
@@ -206,6 +206,7 @@ for idat in xrange(0,len(datafiles)):
 ################################### Finish up ########################################
 
 # Legends
+plt.rcParams.update({'font.size': 19})
 rlegend = rocax.legend(loc='best')
 rlegend.get_frame().set_alpha(0.8)
 slegend = sbax.legend(loc='best')

### 2015-07-14 paper/plotscripts/plotNetwork_res.py

@@ -124,11 +124,13 @@ plt.xticks(rotation=-25)
 plt.bar(numpy.arange(len(kinematics)), sumw, alpha=0.6)
 plt.subplots_adjust(bottom=0.20)
 
-plt.xlabel('Input Variable')
-plt.ylabel('Total associated weight (A.U.)')
 plt.xticks(numpy.arange(len(kinematics)) + 0.5, kinematics)
 
-plt.text(4,10.4,"Resolved category", fontsize=20)
+plt.xlabel('ANN Input Variable',fontsize=18)
+plt.ylabel('Total associated weight',fontsize=18)
+
+
+plt.text(4,10.3,"Resolved category", fontsize=20)
 
 plt.savefig(histout+".pdf")
 plt.clf()

### 2015-07-14 paper/sec-mva.tex
more work on paper

@@
 footing other variables like the $p_T$ of the individual jets
-and the mass of the di-Higgs system.
+and the mass of the di-Higgs system $m_{hh}$.
 %
@@
 For the boosted category, we see that substructure variables
-are the most helpful ones, in particular the $k_t$ splitting scales
-$\sqrt{d_{12}}$ and the subjetiness ratio $\tau_{12}$.
+are the most helpful ones, in particular the $k_t$-splitting scale
+$\sqrt{d_{12}}$ and the subjettiness ratio $\tau_{12}$.
 %
-The ratio of energy correlations $D_2$ and $C_2$ also help,
-in particular the former.
+The ratio of ECFs $D_2^{(\beta)}$ and
+$C_2^{(\beta)}$ also seems to provide
+useful discrimination power.
 %
-From the more traditional variables, the angular
+Concerning other kinematic variables, the angular
 separation between the two large-$R$ jets $\Delta R_{hh}$,
@@
 Other variables provide limited information, in particular the invariant
-mass of the Higgs candidates, $m_{h_1}$ and $m_{h_2}$, due to the realistic
+mass of the Higgs candidates, $m_{h_1}$ and $m_{h_2}$: this
+is due to the realistic
 simulation of detector resolution introduced with the smearing.
 %
-We have verified that signal significance in the boosted category is substantially
-degraded if substructure variables are not used, emphasizing that
-in the boosted category jet substructure provides the best handle
-to separate signal and background.
+We have verified that the post-MVA
+signal significance in the boosted category is substantially
+degraded if substructure variables are not used.
 
 At this point we have all the ingredients that we need to determine the optimal
-value of the MVA output cut and quantify the final values of the signal
-significance $S/\sqrt{B}$ and $S/B$ in our three categories.
+value of the MVA output cuts $y_{\rm cut}$
+and quantify the final values of the signal
+significance $S/\sqrt{B}$ and $S/B$ in the three categories.
 %
-These optimal values are determining by the maximisation of $S/\sqrt{B}$,
-ensuring that the number of events which is left at the HL-LHC is large
-enough, and also that the actual number of MC events used for the ANN training
-is still large enough to avoid the biases of a small training sample.
+These optimal values are determined from the maximisation of $S/\sqrt{B}$,
+ensuring that the number of events $N_{\rm ev}$
+which would be expected at the HL-LHC is large
+enough.
 %
+In addition, we also require when fixing $y_{\rm cut}$
+that the actual number of MC events used for the ANN training
+is large enough to avoid the biases of a small training sample.
+
 The post-MVA results for $S/\sqrt{B}$ and $S/B$ as a function of the cut
@@
 %
-As mentioned before, the optimal cuts are determined independently for each
-category.
+Note that the values of $S/\sqrt{B}$ and $S/B$
+for $y_{\rm cut}=0$ correspond to the values at
+the end of the cut-based analysis, see
+the {\bf C2} row of Table~\ref{table:cutflow}.
 %
-Note that the values of $S/\sqrt{B}$ and $S/B$ in the three cases should correspond
-to the same values at the end of the cut-based analysis, as
-can be verified by looking at the {\bf C2} row of Table~\ref{table:cutflow}.
-%
-Indeed, at the end of the cut based analysis $S/\sqrt{B}$ is approximately
+Indeed, at the end of the cut based analysis $S/\sqrt{B}$ was
+approximately
 1.0, 0.5 and 0.5 for the boosted, intermediate and resolved
 categories, as can be seen from Fig.~\ref{fig:sb_mva}.
+%
+The same applies to $S/B$.
 
@@
   signal over background ratio $S/B$ for the boosted, intermediate
-  and resolved categories.
+  and resolved categories as  function of the cut
+  $y_{\rm cut}=0$ in the ANN output.
   %
-  Note that the optimal cuts are determined independently for each
-  category.
-  %
-  The no-cut values correspond to the  cut-based analysis
+  The $y_{\rm cut}=0$
+  values correspond to the  cut-based analysis
   results from Table~\ref{table:cutflow}.
@@
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.86$}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.86$}\\
     \hline
@@
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.49$}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
     \hline
@@
     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm mva}=0$} & \multicolumn{4}{c}{$y_{\rm mva}=0.17$}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.17$}\\
     \hline
@@
     %
-    Note that the optimal value of the MVA cut
-    is different in each of the three categories.
+    The optimal value of the MVA cut $y_{\rm cut}$
+    is optimised separately in the
+    three categories.
     \label{table:cutflowMVA}

### 2015-07-14 paper/sec-mva.tex
work on paper

@@
 %
-The ratio of ECFs $D_2^{(\beta)}$ and
+The ratios of ECFs $D_2^{(\beta)}$ and
 $C_2^{(\beta)}$ also seems to provide
@@
 %
-For no value of the cut the $S/\sqrt{B}$ value in these two categories
-goes above one.
+Even after the MVA, $S/\sqrt{B}$ never grows above 1.0.
 %
-The real usefulness of the MVA can be seen for the resolved category,
+The real power of the MVA can be seen for the boosted category,
 where the signal significance rises from around 1.0 in the cut-based
-analysis to above 3.0 for values of the ANN output cut above 0.85.
+analysis to above 3.0 for values of the ANN output cut $y_{\rm cut}\ge0.85$.
 %
 This value of the cut seems reasonable, since we know from Fig.~\ref{fig:nev2}
-that the number of signal events at the HL-LHC is still quite substantial,
-of the order of 100.
+that the signal yield at the HL-LHC is still quite substantial,
+of the order of 100 event.
 %
@@
 
-Another very important benefit of the MVA applied to the boosted
+Another important benefit of the MVA applied to the boosted
 category is that fact that the background is substantially
@@
 %
-A reasonably large value of $S/B$ is extremely beneficial
+A reasonably large value of $S/B$ is beneficial
 from the experimental point of view, since it indicates
@@
 Our final results are summarized in Table~\ref{table:cutflowMVA}, where we indicate
-the value of the optimal cut in each category,
-the number of signal and background events $N_{\rm ev}$,
+the value of the optimal ANN output
+cut in each category,
+the number of signal and background events $N_{\rm ev}$ expected
+at the HL-LHC,
 and also $S/\sqrt{B}$ and $S/B$.
 %
-For completeness, we also include the results after the cut-based
+For reference, we also include the results at the end of
+the cut-based
 analysis.
 %
-Given that the signal significance is much larger in the boosted as
-compared to the other two categories, no additional information
-could be obtained by combining the significance of the three
-categories, and it seems more efficient to perform
-the analysis exclusively in the boosted category.
 
@@
     %
-    The optimal value of the MVA cut $y_{\rm cut}$
+    The value of the ANN output cut $y_{\rm cut}$
     is optimised separately in the
@@
 of the MVA is rather moderate, and signal significance is always
-small since backgrounds are still very large.
+small since backgrounds are still  large.
+%
+The combination of the signal significance of the
+three categories leads to a $S/\sqrt{B}=3.53$, and compared
+to 3.31 using only the boosted category.
 
@@
 $b\bar{b}\gamma\gamma$ and $b\bar{b}\tau\tau$, but in any case
-it is always important to have solid evidence from
+it is always important to have robust evidence from
 individual channels.
@@
 So the full luminosity of the HL-LHC is really needed to exploit
-the information contained in this final state.
+the information contained in this final state, unless of course
+new BSM dynamics enhance the di-Higgs production rates.
 
-In the next section we discuss how the expectations for the HL-LHC
-summarized in  Table~\ref{fig:sb_mva} are modified in different
-conservative and aggressive scenarios for the performance of the
-ATLAS and CMS experiments, in particular how the results depend
-on the $b$-tagging performance and in the detector momentum
-resolution.
+The results of Table~\ref{table:cutflowMVA} include
+only the statistical uncertainty in the determination of
+the background number of events.
 %
-But before that let's illustrate how the improvement in $S/\sqrt{B}$
-obtained from the MVA arises from the power of the jet
-substructure variables.
-
-Finally, let us briefly comment on our results would be affected
-if we take into account the systematic uncertainty in the measurement
-of the backgrounds, in addition to the statistical uncertainty.
+We  briefly comment now how these results would be affected
+if we also take into account the systematic experimental
+uncertainty in the measurement
+of the multijet backgrounds distributions.
 %
@@
 %
-Assuming an optimistic value of a total 2\% systematic uncertainty in the
-multijet background measurement, we find that the signal significance would be
-reduced in the boosted category from 3.31 to 2.8.
+Assuming an aggressive value of $\sigma^{\rm sys}=2\%$,
+we find that the combined signal significance would be
+reduced from 3.51 to 3.03.
 %
-However, it is beyond the scope of this work to estimate realistically
+While this quick estimate emphasizes the critical
+importance of an experimentally accurate
+measurement of multijet backgrounds at the LHC to fully exploit the $4b$
+channel,
+it is beyond the scope of this work to estimate realistically
 the systematic uncertainties on QCD multijet distributions (and their bin-by-bin correlation)
-that will be achieved at HL-LHC, and in the following we only consider the statistical
-uncertainties on the background.
+that will be achieved at HL-LHC.
+
+In the next section we discuss how the expectations for the HL-LHC
+summarized in  Table~\ref{fig:sb_mva} are modified in different
+conservative and aggressive scenarios for the performance of the
+ATLAS and CMS experiments, in particular how the results depend
+on the $b$-tagging performance and in the detector momentum
+resolution.
 %
-But this quick estimate emphasizes the crucial need of an experimentally accurate
-measurement of multijet backgrounds at the LHC to fully exploit the $4b$ channel.
+But before that let us illustrate how the improvement in $S/\sqrt{B}$
+obtained from the MVA in the boosted
+category arises from the information contained in the
+jet substructure variables.
 

### 2015-07-14 paper/sec-analysis.tex
small additions to bibliography
more work on paper

@@
   %
+  In order to be considered in the $b$-tagging algorithm,
+   $b$-quarks should satisfy $p_T \ge 15$ GeV.
+  %
   If no $b$-quarks are found among the constituents
   of this jet, it can be still be tagged as a $b$-jet with
-  a mistag rate of $f_l$.
+  a mistag rate of $f_l$, unless a charm quark is found,
+  when the mistag rate is $f_c$.
+  %
+  Only jets which contain at least one constituent
+  with $p_T \ge 15$ GeV can lead to fake $b$-tags.
   %
@@
     %
+    As in the case
+    of small-$R$ jets, in
+    order to be considered in the $b$-tagging algorithm,
+   $b$-quarks should satisfy $p_T \ge 15$ GeV.
+    %
     Note that we only attempt to $b$-tag the two leading subjets:
@@
 Concerning the actual values of the $b$-tag probability $f_b$ and
-the $b$-mistag probability of light jets $f_l$, 
-we adopt as baseline the values $f_b=0.8$ and $f_l=0.01$.
+the $b$-mistag probability of light and charm jets $f_l$ and  $f_c$, 
+we adopt as baseline the values $f_b=0.8$, $f_l=0.01$
+and  $f_c=0.1$.
 %

### 2015-07-14 paper/sec-mva.tex
more work on paper

@@
 
-It is possible to verify that the usefulness of the MVA when
-applied to the boosted category arises from the 
-the information contained on the various jet substructure variables.
 %
@@
 all substructure variables contain useful information:
-the $k_t$ splitting scales $\sqrt{d_{12}}$,
+the $k_t$-splitting scales $\sqrt{d_{12}}$,
 the $\tau_{21}$ subjettiness ratio, and the ECF ratios
@@
 
-Indeed, the information contained Fig.~\ref{fig:nnweights} should be
-reflected in the corresponding distributions of these substructure
+The information reflected in Fig.~\ref{fig:nnweights} should also be
+apparent from the corresponding distributions of these substructure
 variables: those with a higher discrimination power should show
@@
 To illustrate these points,
-In Fig.~\ref{fig:mva_substructure_1}
+in Fig.~\ref{fig:mva_substructure_1}
 we show the distributions of some of
 these substructure variables for the boosted category: the
-$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}) for
+$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), for
 the subleading Higgs,
-the energy correlation double ratio $D_2^{(\beta)}$
-Eq.~(\ref{eq:d2}) for the leading Higgs,
+the energy correlation double ratio $D_2^{(\beta)}$,
+Eq.~(\ref{eq:d2}), for the leading Higgs,
 and then 
-the subjettiness ratio $\tau_{12}$
-Eq.~(\ref{eq:tau21})
+the subjettiness ratio $\tau_{12}$,
+Eq.~(\ref{eq:tau21}),
 for both the leading and subleading Higgs candidates.
@@
 From Fig.~\ref{fig:mva_substructure_1}
-we can observe that for all variables the shapes of the signal
-and background distributions are quite different,
+we can observe that for these substructure variables the shapes of the signal
+and background distributions show important differences,
 reflecting the inherent differences in the internal structure of jets
 between QCD jets and jets originated from the Higgs decays.
-%
-Note that as before, all the distributions in
-Fig.~\ref{fig:mva_substructure_1}
-have been normalized to unity.
 %
@@
 the distributions of the subjettiness ratio $\tau_{12}$ are quite similar
-in the leading and in the subleading jets, therefore adding the value
-of  $\tau_{12}$ from the two Higgs candidates at the MVA at the same time
+in the leading and in the subleading jets, therefore adding
+$\tau_{12}$ from the two Higgs candidates to the MVA at the same time
 is redundant, explaining why in these cases either one or the other
@@
 
-Finally, let us show the distributions of kinematic variables
+It is also interesting to show the distributions of kinematic variables
 that according to the MVA provide a small amount of discrimination
@@
     $\Delta\phi_{hh}$, for the resolved and boosted categories:
-    according to Fig.~\ref{fig:nnweights}, no much discrimination power
-    is obtained here, and indeed the shapes of the two signal
+    according to Fig.~\ref{fig:nnweights}, essentially no discrimination power
+    should be obtained from this variable, and indeed the shapes of the two signal
     and background
@@
     From Fig.~\ref{fig:nnweights} we also saw that the
-    invariant mass distributions $m_h$ carry little information,
-    and this was verified from 
+    invariant mass distributions $m_h$ carry little information
+    to discriminate signal over background:
+    this was already verified from 
 the corresponding
-distributions in $m_{hh}$ from Fig.~\ref{fig:mHHinv}.
+distributions in Fig.~\ref{fig:mHHinv}.
 %
-As explained before, the reason for this is
+As explained before, the reduced discrimination power arises
+from 
 the  smearing of jet four-momenta introduced to mimic
-realistically detector resolution.
+realistically detector resolution.\footnote{We have verified that
+  if no smearing is applied, the $m_h$ distributions for the leading
+  and subleading Higgs candidates become the most
+important variables in the MVA.}
 

### 2015-07-14 paper/sec-optimisation.tex
more work on paper

@@
-\section{Optimisation}
+\section{Analysis optimisation}
 \label{sec:optimisation}
 
-One important motivation of this work was to quantify which aspects
+One motivation for this work was to quantify which aspects
 of the performance of the LHC detectors needs to be improved
@@
 %
-In this section we explore how the results with the baseline settings,
+In this section we explore how the post-MVA
+results with the baseline settings,
 summarized in the previous section, are modified when some of
@@
 the $b$-tagging probability $f_b$, the light jet mistag rate
-$f_l$, as well on the momentum smearing fraction.
+$f_l$, as well on the four-momentum smearing fraction $\Delta p$.
 %
@@
 
-We also study how the signal significance is modified as a function
-of the systematic uncertainty that needs to be obtained
-in the measurement of the background processes.
-%
-This is specially important in a process like this one where
-the signal over background ratio $S/B$ is small, and thus were
-it is essential to measure the backgrounds as accurately
-as possible.
-
 Given that we have found in the previous section that the
@@
 new information contained in the various scenarios.
+%
+This is important since for example, when we vary $f_b$
+or $f_l$, the relative composition of the multijet
+background will change, and this can translate into
+modifications of the kinematical variables used for
+the MVA training.
+%
+Similarly, if the momentum resolution is modified,
+the weight of the different variables in the MVA
+will be altered, in particular the invariant mass
+of Higgs candidates $m_h$.
 
 The results of this optimisation study are collected in
-Table~\ref{table:cutflowMVAoptimisation}
+Table~\ref{table:cutflowMVAoptimisation}.
+%
+There we compare the results for the number of signal
+and background events $N_{\rm ev}$ expected at the
+HL-LHC, the signal significance and the $S/B$ ratio
+for our nominal settings and for the variations
+of the analysis settings.
 
@@
   \end{tabular}
-  \caption{\small The details of the various scenarios have been collected in
-    Table~\ref{sec:variations}.
+  \caption{\small
+Number of signal
+and background events $N_{\rm ev}$ expected at the
+HL-LHC, signal significance and $S/B$ ratio
+for the nominal settings and for the variations
+of the analysis settings, summarized
+in  Table~\ref{sec:variations}.
  \label{table:cutflowMVAoptimisation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Neglecting the
+contribution from light jet fakes,
+it is easy to estimate how $S/\sqrt{B}$ should
+scale with $f_b$: since we have two double-$b$-tagged jets
+both in signal and background events, one should find that
+\be
+\frac{S}{\sqrt{B}}\Bigg|_{f_b}\Bigg/
+\frac{S}{\sqrt{B}}\Bigg|_{f_b'}
+\simeq \frac{f_b^2}{f_b'^2} \, .
+\ee
+By comparing this expectations with the numbers of
+Table~\ref{table:cutflowMVAoptimisation}, we see that there
+is a reasonable agreement in the boosted category,
+as expected since it is dominated by the irreducible
+$4b$ component.

### 2015-07-15 paper/sec-mcsamples.tex
Sect 2.3

@@
 
-\subsection{Higgs pair production}
+\subsection{Higgs pair production by gluon-fusion}
 %%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 detector simulator, which is beyond the scope of this paper.
-%
-For a similar reason, we don't consider underlying event, multiple parton interactions and
-pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba}.
-%
-The same applies to the background samples, which we discuss now.
 
@@
 
-Finally, let us discuss the smearing applied to signal
-and background samples.
+\subsection{Mimicking detector resolution}
+
+While it is beyond the scope of this work to perform a full
+detector simulation, it is still important to include an estimate of detector
+effects in the analysis, in particular for the finite resolution
+in energy and momentum, which will affect some kinematical variables, in particular
+the invariant mass of the Higgs candidates.
 %
-It is beyond the scope of this work to perform a complete study of the impact of
-detector effects in this process.
+For example, in the absence of any four-momentum smearing, the impact of the $m_h$
+distributions of the Higgs candidates in the MVA
+would be unrealistically large.
+
+In this work we simulate the finite momentum resolution of the ATLAS and CMS
+hadronic calorimeters by applying a Gaussian smearing
+with mean zero and standard deviation $\sigma_E$.
 %
-However, it is still important to include some form of rough estimate of detector
-effects in the analysis, to properly estimate for example the impact
-of the Higgs mass window cuts.
+In particular, we rescale the four-momentum of all
+final-state particles, before jet clustering, using
+a common factor for the energy $E$ and the length of the
+three-momentum $\vec{p}$, while keeping the direction unchanged:
 %
-In this work we simulate the finite momentum resolution of the ATLAS and CMS
-hadronic calorimeters by applying a Gaussian smearing to the four components
-of the four-momentum $p$, with mean zero and standard deviation $\Delta p$.
+\be
+E_i \, \to \, E'_i= \lp 1+ r_i\cdot\sigma_E \rp\, E_i \, ,\quad
+\vec{p}_i \, \to \, \vec{p}'_i= \lp 1+ r_i\cdot\sigma_E \rp\, \vec{p}_i \, , \quad
+i=1,\ldots,N_{\rm part} \, ,
+\ee
+with $r_i$ an univariate Gaussian random number which is different for each
+of the $N_{\rm part}$ particles in the event.
+
+This smearing reflects the fact that the angular resolution of the LHC detectors
+is better than the energy resolution.
 %
-We take as baseline value a smearing of $\Delta p=5\%$, and in
+We take as baseline value a momentum smearing
+factor of $\sigma_E=5\%$, and in
 Sect.~\ref{sec:optimisation} we explore how our results change
-if a more optimistic or pessimistic value is assumed for the momentum
+if a more optimistic or pessimistic value is assumed for this value
+of the momentum
 resolution in the LHC detectors.
+
+It is also beyond the scope of this paper to
+consider
+the effects in our analysis of  Underlying Event (UE),
+Multiple Parton Interactions (MPI) and in
+particular
+pile-up (PU).
+%
+While PU will be be one of the major problems at the HL-LHC, fortunately
+a number of powerful methods for the subtraction of  UE, MPI and PU
+effects 
+have been developed recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
+%
+For these reasons, in our Monte Carlo analysis we switch off MPI and PU,
+and postpone to a future work a full detector simulation
+to quantify the robustness
+of our analysis strategy with respect to the inclusion
+(and its subtraction) of the large PU
+expected at the HL-LHC.
+
+We note that while substructure variables can be affected by PU, event after its
+subtraction, our analysis should be relatively robust since we do not cut
+over any specific variables, but input the full distributions to the MVA.
+%
+In particular, if after PU suppression a given variable is modified
+but in the same way for signal and background samples, it should not
+affect MVA discrimination.

### 2015-07-15 paper/sec-conclusions.tex
Updated common plot style
work on the conclusions

--- 2015-06-01 paper/sec-conclusions.tex
@@
-\section{Conclusions and outlook}
+\section{Summary and outlook}
+\label{sec:conclusions}
 
 In this work we have presented a detailed study of the feasibility
-of the measurement of Higgs pair production in the $bb\bar{b}\bar{b}$
-final state at the High-Luminosity LHC....
+of a measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
+final state at the High-Luminosity LHC.
+%
+Our strategy is based on the combination of a traditional
+cut-based analysis with modern multivariate techniques,
+which allows us to improve the signal significance of this channel
+as compared to previous studies.
+%
+Following a careful optimisation of the
+signal reconstruction strategy for different event topologies,
+we find that the highest significance is obtained
+in the 
+boosted category, and that complementary information is also provided
+by the intermediate and resolved categories.
+%
+
+Our analysis is based on a complete simulation of
+all relevant backgrounds, in particular
+of QCD multijets.
+%
+We include not only the irreducible $4b$ component, but
+also the $2b2j$ and $4j$ backgrounds, which contribute
+to the yield of reconstructed Higgs candidates
+when light partons are mistagged as $b$-quarks.
+%
+We show that neglecting the contribution
+from these fakes is a poor approximation
+in general, specially for the resolved and intermediate
+categories, and that the origin of this is that
+the impact of fakes
+is substantially enhanced when compared to a naive parton
+level estimate due to combinatorics and $b\bar{b}$
+pair radiation during the parton shower.
+
+The combination of the three categories leads to a total
+signal significance of $S/\sqrt{B}\simeq 3.2$.
+%
+Therefore, we can conclude that, already from the $4b$ channel alone,
+it should be possible to claim evidence for Higgs pair production at
+the HL-LHC.
+%
+We have estimated the robustness of these estimates by varying some
+of the analysis settings, such as the $b$-quark tagging efficiency
+or the momentum resolution, finding that one could achieve
+a signal significance of up to $S/\sqrt{B}\simeq 4.2$ in
+the most aggressive scenarios.
+%
+However, it is also clear that in order
+to claim discovery of Higgs pair production
+(with the traditional 5-$\sigma$ criterion)
+a combination with other decay channels
+would still be required.
+%
+In this respect, the 
+ $b\bar{b}\gamma\gamma$
+and $b\bar{b}\tau\tau$ final states are the most
+promising, since while having
+smaller rates as compared to $4b$
+they
+benefit from reduced backgrounds.
+%
+We also find that an observation of Higgs pair production at the
+LHC Run II is very difficult unless the rates are enhanced
+by BSM dynamics.
+
+The main limitation of this work is the lack a full
+detector simulation, and the assumption that the large PU
+expected at the HL-LHC can be removed using
+available background
+suppression methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba} without modifying significantly the
+kinematic variables that we input to the MVA.
+%
+While these are reasonable approximations (and we mimic to some
+extent the detector resolution with the smearing), they need
+to be validated in a complete detector simulation with realistic
+PU effects.
+%
+In addition, it would be desirable, having established the
+value of the $4b$ channel for the study of
+Higgs pair production, to revisit and improve the
+theoretical modeling of signal and background simulation,
+in particular using NLO calculations matched to
+parton showers both for signal~\cite{Frederix:2014hta,Maierhofer:2013sha}
+and for backgrounds~\cite{Alwall:2014hca,Gleisberg:2008ta}.
+%
+We plan to address these two issues in a follow-up
+publication.
+
+One important application of our results
+would be to quantify the accuracy on the extraction of
+the Higgs trilinear coupling $\lambda$
+that could be achieved from
+a measurement of the
+$\sigma\lp hh\to 4b\rp$ cross-section.
+%
+This is however not straightforward since
+the determination of the trilinear coupling
+requires not only to regenerate signal samples
+for a wide range values of  $\lambda$, but also to
+redo the analysis
+optimisation (including the MVA training) for each
+of these values.
+%
+We plan to explore this possibility in the future, and to
+compare with the precision in the determination of
+$\lambda$ that has been claimed in other final states.
+
+In addition,
+in this work we have considered only the SM production mechanism,
+but many BSM scenarios predict deviations
+in Higgs pair production, both at the level of total rates
+and of
+differential distributions.
+%
+In the absence of new explicit degrees of freedom,
+deviations from the SM can be parametrized in
+the EFT framework using higher-order
+operators~\cite{Azatov:2015oxa,Goertz:2014qta}.
+%
+We thus plan to study which are the constraints
+on the coefficients of these effective
+operators that can be obtained from measurements
+of various $hh\to 4b$ distributions.
+%
+Note that the higher rates of the $4b$ final state as compared to
+say $b\bar{b}\gamma\gamma$ allow to better constrain operators
+that modify the high-energy behavior
+of the theory, in particular
+since it becomes possible
+to access the tail of the $m_{hh}$ distribution.
+
+As in the case of the extraction of $\lambda$, such study
+would be a computationally intensive task, since
+BSM dynamics will modify the shapes of the kinematical
+distributions, and thus in principle each point in the EFT parameter
+space would require a re-optimization with a new training
+of the MVA.
+%
+In order to explore efficiency the BSM parameters
+without having to redo a full analysis
+for each point, modern techniques
+such as the cluster analysis proposed
+in Ref.~\cite{Dall'Osso:2015aia} should be very useful.
+
+Finally, it would be important to estimate the prospects for
+Higgs pair production in the $4b$  final
+state at a Future Circular
+Collider (FCC) with a center of mass energy of
+100 TeV~\cite{Barr:2014sga,Azatov:2015oxa,Papaefstathiou:2015iba}.
+%
+While signal yields would be certainly increased, also the QCD
+multijet background would grow, so it is necessary to repeat
+our analysis, including full background simulation, at 100 TeV,
+and assess if the accuracy in the extraction of the trilinear $\lambda$
+is improved or degraded as compared to the 14 TeV case.
+%
+This study should address both SM and BSM
+production mechanisms.
 
@@
 {\bf\noindent  Acknowledgments \\}
-We thank A.~Papaefstathiou for useful discussions on this project.
+We thank R.~Contino, A.~Papaefstathiou and
+G.~Salam for useful discussions on the topic
+of Higgs pair production.
+%
+We thank E.~Vrodynou for assistance with di-Higgs production
+  in {\tt MadGraph5\_aMC@NLO}.
 %

### 2015-07-15 paper/sec-optimisation.tex
writing of paper completed

@@
 One motivation for this work was to quantify which aspects
-of the performance of the LHC detectors needs to be improved
+of the performance of the LHC detectors need to be improved
 the most in order to maximise the significance of the observation
@@
 summarized in the previous section, are modified when some of
-these settings are changed.
+these settings are modified.
 %
@@
 the $b$-tagging probability $f_b$, the light jet mistag rate
-$f_l$, as well on the four-momentum smearing fraction $\Delta p$.
+$f_l$, as well on the four-momentum smearing fraction $\sigma_E$,
+see Eq.~(\ref{eq:smearing}).
 %
@@
 \hline
-    Scenario  &  $f_b$  &  $f_l$  &  $\Delta p_T$ \\
+    Scenario  &  $f_b$  &  $f_l$  &  $\sigma_E$ \\
     \hline
@@
     D        &  0.8   &   0.02  &  5\% \\
-    E        &  0.9   &   0.005  &  2\% \\   
+    E        &  0.9   &   0.005  &  3\% \\
+    F        &  0.9   &   0.005  &  7\% \\   
     \hline
@@
     tagging probability, the light jet mistag rate $f_l$
-    and the $p_T$ resolution $\Delta p_T$, compared
+    and the momentum resolution $\sigma_E$, compared
     to the various scenarios that we discussed in this section.
@@
 Given that we have found in the previous section that the
-only category with real discrimination power is the boosted one,
-in this section we concentrate only on this one,
+category with highest discrimination power is the boosted one,
+in this section we concentrate on it,
 by comparing our baseline results from Table~\ref{table:cutflowMVA}
@@
 %
-When necessary, the MVA has been retrained to optimise the
+Each time of the parameters in Table~\ref{sec:variations}
+ has been changed, the MVA has been retrained to optimise the
 new information contained in the various scenarios.
@@
 and background events $N_{\rm ev}$ expected at the
-HL-LHC, the signal significance and the $S/B$ ratio
+HL-LHC, the signal significance, and the $S/B$ ratio,
 for our nominal settings and for the variations
@@
 \be
-\frac{S}{\sqrt{B}}\Bigg|_{f_b}\Bigg/
-\frac{S}{\sqrt{B}}\Bigg|_{f_b'}
+\lp \frac{S}{\sqrt{B}} \rp _{f_b}\Bigg/
+\lp \frac{S}{\sqrt{B}} \rp_{f_b'}
 \simeq \frac{f_b^2}{f_b'^2} \, .
@@
 as expected since it is dominated by the irreducible
-$4b$ component.
+$4b$ component of the QCD multijet background.
+
+The most aggressive scenario is the one in which the $b$-tagging
+is improved up an efficiency $f_b=0.9$, while at the same
+time the light jet fake rate is reduced down to $0.5\%$, while
+at the same time the momentum resolution has been decreased
+to $\sigma_E=3\%$.
+%
+In this scenario, the signal significance of the boosted category
+increases to AAA, to be compared to BBB with the baseline settings.

### 2015-09-01 paper/sec-intro.tex
small mods to intro

@@
 uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
-  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha}.
+  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
 %

### 2015-11-10 paper/HH4b.tex
new section on PU

@@
   %
-  We therefore demonstrate that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
+  We demonstrate the robustness of our analysis under realistic
+  pile-up conditions expected at the HL-LHC
+  %
+  We therefore conclude
+  that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
   should allow to claim evidence of the observation of double Higgs production.
@@
 \input{sec-mva}
-\input{sec-optimisation}
+\input{sec-pileup}
 \input{sec-conclusions}

### 2015-11-10 paper/sec-pileup.tex

\section{Robustness under realistic pile-up conditions}

\label{sec:pileup}

The discussion so far has not included the effects of
pile-up, under realistic conditions of the HL-LHC.
%
In this section we show how our qualitative results, in particular
the enhanced discrimination provided by the MVA, are robust
even when realistic pile-up conditions are accounted for.

### 2015-11-10 paper/sec-analysis.tex
More work on draft

@@
 and  $f_c=0.1$.
-%
-In Sect.~\ref{sec:optimisation} we study the dependence of
-our results against variations of $f_b$ and $f_l$ both
-using more conservative and more aggressive values.
 %
@@
 %
-In Sect.~\ref{sec:optimisation} we discuss how the results
-of the analysis is modified if a more aggressive
-detector resolution is assumed (corresponding
-to a smaller value of the smearing).
 

### 2015-11-10 paper/sec-mcsamples.tex
writing of paper completed
More work on draft

@@
 \be
+\label{eq:smearing}
 E_i \, \to \, E'_i= \lp 1+ r_i\cdot\sigma_E \rp\, E_i \, ,\quad
@@
 of the $N_{\rm part}$ particles in the event.
-
+%
 This smearing reflects the fact that the angular resolution of the LHC detectors
@@
 We take as baseline value a momentum smearing
-factor of $\sigma_E=5\%$, and in
-Sect.~\ref{sec:optimisation} we explore how our results change
-if a more optimistic or pessimistic value is assumed for this value
-of the momentum
-resolution in the LHC detectors.
+factor of $\sigma_E=5\%$.
 

### 2015-11-10 paper/sec-pileup.tex
More work on draft

@@
 even when realistic pile-up conditions are accounted for.
+%
+First of all we describe the simulation of realistic
+pile-up conditions at the HL-LHC, and the corresponding
+subtraction using {\tt SoftKiller}.
+%
+Then we present the validation of the pile-up subtraction,
+and compare a number of distributions, including substructure variables,
+with and without PU.
+%
+Finally we revisit the MVA analysis of Sect.~\ref{sec:mva}, and
+show that our qualitative conclusions are unchanged even
+in the presence of realistic PU conditions.
+
+\subsection{Pile-up subtraction with {\tt SoftKiller}}
+
+With this motivation, a large number
+of minimum bias events have been added to the various signal
+and background samples described in Sect.~\ref{mcgeneration}.
+%
+We have explored two scenarios for the amount of pile-up expected
+at the HL-LHC, one with a mean number of
+PU vertices of $\la n_{\rm PU}\ra=80$, and another
+with $\la n_{\rm PU}\ra=150$.
+%
+Minimum bias events have been generated with {\tt Pythia8} using
+the Monash 2013 tunes.
+%
+We have generated a total of 100M minimum-bias events, which are
+then superimposed to the hard-scattering events in a random way.
+
+In order to subtract the pile-up, a number of techniques
+have been developed recently. While PU will be be one of the major problems at the HL-LHC, fortunately
+a number of powerful methods for the subtraction of  UE, MPI and PU
+effects 
+have been developed recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
+%
+While a complete optimization of the PU subtraction strategy is beyond
+the scope of this work, here we will use the {\tt SoftKiller}
+method~\cite{Cacciari:2014gra}
+as implemented in {\tt FastJet}.
+
+The idea underlying {\tt SoftKiller} is based on eliminating particles
+below a given cut-off in transverse momentum, $p_T^{\rm cut}$, whose
+value is dynamically determined in a way that makes the event-wide
+transverse-momentum flow density $\rho$
+\be
+\rho={\rm median} \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\}
+\ee
+where the median is computed over all the patches $i$ with area
+$A_i$ and transverse momentum $p_{Ti}$ in which the event is partitioned.
+%
+The size and number of these patches is a free parameter of the algorithm -
+in this work we will use a value $a=0.4$ for the length of these
+patches.
+%
+We restrict ourselves to the rapidity interval
+$\eta \in \lc -2.5, 2.5\rc$ for the estimation of the
+$p_T$ flow density $\rho$, since only the central region
+is used in this analysis.
+%
+In this work, the {\tt SoftKiller} method is applied
+to the particles at the end of the parton shower, before
+they are clustered into the anti-$k_t$ jets.
+
+\subsection{Validation of pile-up subtraction}
+
+Now we turn to validate our PU subtraction strategy.
+%
+To this end, we compare various kinematical distributions in three
+cases:
+\begin{itemize}
+\item without any pile-up,
+\item with pile-up, but without any PU subtraction,
+  \item with pile-up and with {\tt SoftKiller} subtraction.
+\end{itemize}
+As we will show now, some substructure variables in the boosted
+regime are particularly robust against PU effects, and this
+will have the important consequence that the MVA discrimination
+will not be substantially affected.
+
+{\bf add plots of these various distributions}
+
+In Fig.~\ref{fig: pu-vs-nopu-comparison-d2} we
+compare the distribution of the $D_2^{(\beta)}$
+    substructure variable, Eq.~(\ref{eq:d2}), for the
+    boosted category in two cases: without PU, and
+    with $\la n_{\rm PU}\ra=150$ PU events.
+    %
+    In the latter case, PU has been subtracted using
+    {\tt SoftKiller}.
+    %
+    We see that the distribution is relatively unaffected by PU.
+    %
+    Note that by construction $D_2^{(\beta)}$ has been designed
+    to be insensitive to PU, so this agreement is an important
+    cross-check.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+      \vspace{-1cm}
+  \includegraphics[width=0.60\textwidth]{plots/pu-vs-nopu-comparison-d2.pdf}
+  \caption{\small
+    Comparison of the distribution of the $D_2^{(\beta)}$
+    substructure variable, Eq.~(\ref{eq:d2}), for the
+    boosted category in two cases: without PU, and
+    with $\la n_{\rm PU}\ra=150$ PU events.
+    %
+    In the latter case, PU has been subtracted using
+    {\tt SoftKiller}.
+    %
+    See text for more details.
+}
+\label{fig: pu-vs-nopu-comparison-d2}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Signal significance in the presence of PU}
+
+Finally, we revisit how the signal significance after the MVA
+is affected by the inclusion of realistic PU effects.

### 2015-11-10 paper/sec-pileup.tex
more work on paper

@@
 is affected by the inclusion of realistic PU effects.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/ssb_pu.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb_pu.pdf}
+\caption{\small
+  Same as Fig.~\ref{fig:sb_mva} this time for the analysis including
+  effects of PU, with $\la n_{\rm PU}\ra=150$.
+}
+\label{fig:sb_mva_pu}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+In Fig.~\ref{fig:sb_mva_pu} we show the signal significance,
+$S/\sqrt{B}$, as well as the signal over background ratio,
+$S/B$, as a function of the NN discriminant, in the case
+of the analysis including the effects of PU
+with $\la n_{\rm PU}\ra=150$.
+%
+The corresponding results in the case without PU were shown in
+Fig.~\ref{fig:sb_mva}.
+%
+As can be seen, the MVA-driven enhancement is robust event in the
+presence of PU, and a total signal significance of
+almost $S/\sqrt{B}\simeq 3$ is also obtained in this case.
+%
+Therefore, we conclude that the qualitative results obtained
+in the previous section are robust even in the presence
+of realistic PU effects.
+%
+Note that no specific effort has been performed to
+optimize PU subtraction (for example by tuning the value
+of the patch length $a$ in {\tt SoftKiller}), so there is
+certainly still room for improvement.

### 2015-11-17 paper/sec-pileup.tex
More work in the PU section

@@
 
-{\bf add plots of these various distributions}
-
 In Fig.~\ref{fig: pu-vs-nopu-comparison-d2} we
@@
 }
-\label{fig: pu-vs-nopu-comparison-d2}
+\label{fig:pu-vs-nopu-comparison-d2}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+We now compare a number of signal distributions with
+and without PU.
+%
+In Fig.~\ref{fig:m_H_PU} we show first of all the invariant mass distribution
+of the leading and subleading Higgs candidates in the boosted
+and resolved categories.
+%
+These distributions are plotted after the $b$-tagging,
+before they are used as input to the MVA.
+%
+As we can see, in the boosted category, the residual effects of PU
+after the SoftKiller subtraction are very mild in this
+distribution.
+%
+The effects are more important for the resolved category, where PU
+shifts the Higgs peak by am amount $\Delta m_h \simeq 5$ GeV.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+      \vspace{-1cm}
+      \includegraphics[width=0.49\textwidth]{plots/m_H0_res_comp.pdf}
+      \includegraphics[width=0.49\textwidth]{plots/m_H1_res_comp.pdf}
+      \includegraphics[width=0.49\textwidth]{plots/m_H0_bst_comp.pdf}
+      \includegraphics[width=0.49\textwidth]{plots/m_H1_bst_comp.pdf}
+  \caption{\small
+    Comparison of the invariant mass distributions of the leading (left plots)
+    and subleading (right plots) Higgs candidates in the resolved
+    (upper plots) and boosted (lower plots) categories,
+    without PU and with $\la n_{PU}\ra=80$ subtracted with SoftKiller.
+}
+\label{fig:m_H_PU}
 \end{center}

### 2015-11-17 paper/paperscripts/plotHist_m_H1_res_comp.py

@@ -10,13 +10,13 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "m_H0_bst_comp"
+outfile = "m_H1_res_comp"
 
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H0_boost_C2.dat")
-datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_H0_boost_C2.dat")
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H1_res_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_H1_res_C2.dat")
 
 
 # Plot labels
@@ -24,7 +24,7 @@ plotnames.append("no PU")
 plotnames.append("$n_{PU}=80$ + SK")
 
 # Axis labels
-xLabel = "Leading Higgs Candidate Invariant Mass (GeV)"
+xLabel = "Sub-Leading Higgs Candidate Invariant Mass (GeV)"
 yLabel = "a. u."
 
 # Log axes
@@ -125,7 +125,7 @@ ax.xaxis.grid(True)
 ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.23,0.93,"Signal events, Boosted category", fontsize=20)
+fig.text(0.23,0.93,"Signal events, Resolved category", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-11-17 paper/sec-pileup.tex
More work on the PU section

@@
 
+Next we consider how PU affects kinematical distributions
+in the boosted category.
+%
+In the following we assess the effect of PU in four additional
+distributions: the transverse momentum of the leading Higgs
+candidate, $p_t^{h_1}$, the invariant mass of the di-Higgs system
+$m_{hh}$, and two substructure variables, the subjetiness
+$\tau_{21}$ and $D_2$ of the leading Higgs candidate.
+%
+This comparison is illustrated in Fig.~\ref{fig:mHH_PU}.
+%
+Therefore, as we can see, the substructure variables, which
+as demonstrated before carry a very substantial
+discrimination power, are relatively unaffected by PU.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
+  \caption{\small
+    Comparison of the transverse momentum $p_T^h$ of the leading
+    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
+    of the di-Higgs system (lower plots) in the resolved
+    (left plots) and boosted (right plots) categories,
+    without PU and with $\la n_{PU}\ra=80$ subtracted with SoftKiller.
+}
+\label{fig:mHH_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Next we assess the impact of PU in some of the substructure variables
+used as input to the MVA in the boosted category.
+%
+In particular $m_{hh}$, and two substructure variables, the subjetiness
+$\tau_{21}$ and $D_2$ of the leading Higgs candidate.
+%
+This comparison is illustrated in Fig.~\ref{fig:substructure_PU}.
+%
+Therefore, as we can see, the substructure variables, which
+as demonstrated before carry a very substantial
+discrimination power, are relatively unaffected by PU.
+
+Up to know we have restricted ourselves to the study of the impact of PU
+on signal distributions.
+%
+We now assess how the signal over background discrimination can be affected
+in the presence of realistic PU conditions.
+
 \subsection{Signal significance in the presence of PU}

### 2015-11-17 paper/paperscripts/plotHist_mHH_bst_comp.py

@@ -1,0 +1,133 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_HH_C2_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_HH_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_HH_boost_C2.dat")
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append("$n_{PU}=80$ + SK")
+
+# Axis labels
+xLabel = "di-Higgs Invariant Mass $m_{hh}$ (GeV)"
+yLabel = "A. U."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([200,650])
+ax.set_ylim([1e-4,0.05])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-11-17 paper/sec-pileup.tex
More work on PU section

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/tau21_h0_bst_comp.pdf}
+   \caption{\small
+     Comparison of the substructure variables $D_2^{(\beta)}$
+     and $\tau_{21}$ for the leading Higgs candidate in the boosted category,
+   without PU and with $\la n_{PU}\ra=80$ subtracted with SoftKiller.
+}
+\label{fig:Substructure_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 Up to know we have restricted ourselves to the study of the impact of PU
@@
 in the presence of realistic PU conditions.
+
+{\bf add plots signal vs background with PU}
 

### 2015-11-17 paper/paperscripts/plotHist_D2_h0_bst_comp.py

@@ -1,0 +1,133 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "D2_h0_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_D2_fj1_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_D2_fj1_boost_C2.dat")
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append("$n_{PU}=80$ + SK")
+
+# Axis labels
+xLabel = r"Energy Correlation Ratio $D_2^{(\beta)}$ in leading Higgs candidate"
+yLabel = "A. U."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,1])
+ax.set_ylim([0,2.5])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-11-17 paper/sec-optimisation.tex
deleted old plots

@@
 increases to AAA, to be compared to BBB with the baseline settings.
+
+  \subsection{The role of the overlap between different categories}
+\label{sec:overlap}
+
+As has been discussed in Sect.~\ref{sec:analysis}, while the optimization of each
+category is performed in an inclusive analysis, after having determined the order
+of significance of the separate categories. we turn to a exclusive analysis,
+in order that
+we can combine consistently the results from the various topologies without double
+counting.
+%
+Here we discuss the role of the overlap
+between  different categories, which is of course ignored in the final exclusive
+analyses.
+%
+The idea is to understand how significant the information is on which events satisfy the requirements
+of more than one category at the same time.
+
+To illustrate the role of the overlap between the different categories, in
+Fig.~\ref{fig:categorisationHisto} we show the fraction of events that satisfy the requirements
+of one or more categories, for signal and background events.
+%
+We consider the following cases:
+\begin{itemize}
+\item events that satisfy the requirements of one category (resolved,
+  intermediate or boosted),
+\item events that satisfy the conditions of both the resolved and the intermediate categories,
+\item and the same for events that fall both
+  into the resolved and boosted categories.
+\end{itemize}
+ Note that by construction, there is no overlap between the boosted
+  and intermediate categories due to the
+ orthogonal jet multiplicity cuts.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+%\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
+\caption{\small The fraction of events that satisfy the requirements
+  of one or more categories, for signal and background events.
+  %
+  By construction, there is no overlap between the boosted
+  and intermediate categories due to the
+   orthogonal jet multiplicity cuts. {\bf update including event weights}
+}
+\label{fig:categorisationHisto}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+As we can see from Fig.~\ref{fig:categorisationHisto}, an large majority of the events
+belong to the resolved category, specially in the background case ($\sim 90\%$) but
+also a large part of the signal ($\sim 60\%$).
+%
+In all the other categories, including
+the overlaps, signal events are more likely to belong to them than
+background events.
+%
+In the intermediate category, we have around $\sim$30\% of the signal
+events and $\sim$10\% of the background events.
+%
+For the boosted case, we find $\sim$ 6\% of signal events and
+$\sim$2\% of background events.
+%
+We also find that the overlap between the boosted and the other categories
+is small: none with the intermediate (by construction), and then $\sim$3\%
+($\sim$0.05\%) of the signal (background) events.
+%
+The overlap between the resolved and the intermediate is also smaller
+than the two categories separately: $\sim$7\%
+($\sim$ 3\%) for signal (background) events.
+
+Therefore, from the results of Fig.~\ref{fig:categorisationHisto}
+we can conclude that the effect of the overlap between categories would
+be small correction with respect to the exclusive selection approach
+that we use in this work.
+%
+Note also that while the majority of signal events are in the resolved
+category, since the fraction of background events is also larger,
+it is advantageous to use the small fraction of events in the boosted category
+since the suppression of the background in this category is larger
+than in the others.

### 2015-11-17 paper/sec-results.tex
deleted old plots

@@
 %
-We also study the role of the overlap
-between the different categories.
 
@@
   {\bf compare parton level with hadron level distributions}
-
-  \subsection{The role of the overlap between different categories}
-\label{sec:overlap}
-
-As has been discussed in Sect.~\ref{sec:analysis}, while the optimization of each
-category is performed in an inclusive analysis, after having determined the order
-of significance of the separate categories. we turn to a exclusive analysis,
-in order that
-we can combine consistently the results from the various topologies without double
-counting.
-%
-Here we discuss the role of the overlap
-between  different categories, which is of course ignored in the final exclusive
-analyses.
-%
-The idea is to understand how significant the information is on which events satisfy the requirements
-of more than one category at the same time.
-
-To illustrate the role of the overlap between the different categories, in
-Fig.~\ref{fig:categorisationHisto} we show the fraction of events that satisfy the requirements
-of one or more categories, for signal and background events.
-%
-We consider the following cases:
-\begin{itemize}
-\item events that satisfy the requirements of one category (resolved,
-  intermediate or boosted),
-\item events that satisfy the conditions of both the resolved and the intermediate categories,
-\item and the same for events that fall both
-  into the resolved and boosted categories.
-\end{itemize}
- Note that by construction, there is no overlap between the boosted
-  and intermediate categories due to the
- orthogonal jet multiplicity cuts.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
-\caption{\small The fraction of events that satisfy the requirements
-  of one or more categories, for signal and background events.
-  %
-  By construction, there is no overlap between the boosted
-  and intermediate categories due to the
-   orthogonal jet multiplicity cuts. {\bf update including event weights}
-}
-\label{fig:categorisationHisto}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-As we can see from Fig.~\ref{fig:categorisationHisto}, an large majority of the events
-belong to the resolved category, specially in the background case ($\sim 90\%$) but
-also a large part of the signal ($\sim 60\%$).
-%
-In all the other categories, including
-the overlaps, signal events are more likely to belong to them than
-background events.
-%
-In the intermediate category, we have around $\sim$30\% of the signal
-events and $\sim$10\% of the background events.
-%
-For the boosted case, we find $\sim$ 6\% of signal events and
-$\sim$2\% of background events.
-%
-We also find that the overlap between the boosted and the other categories
-is small: none with the intermediate (by construction), and then $\sim$3\%
-($\sim$0.05\%) of the signal (background) events.
-%
-The overlap between the resolved and the intermediate is also smaller
-than the two categories separately: $\sim$7\%
-($\sim$ 3\%) for signal (background) events.
-
-Therefore, from the results of Fig.~\ref{fig:categorisationHisto}
-we can conclude that the effect of the overlap between categories would
-be small correction with respect to the exclusive selection approach
-that we use in this work.
-%
-Note also that while the majority of signal events are in the resolved
-category, since the fraction of background events is also larger,
-it is advantageous to use the small fraction of events in the boosted category
-since the suppression of the background in this category is larger
-than in the others.

### 2015-11-17 paper/sec-pileup.tex
deleted old plots
work on PU section

--- 2015-11-17 paper/sec-pileup.tex
@@
-\section{Robustness under realistic pile-up conditions}
+\section{Impact of pile-up}
 
@@
 
-The discussion so far has not included the effects of
-pile-up, under realistic conditions of the HL-LHC.
+The discussion so far has not accounted for the effects of
+pile-up (PU), which are known to be very important at the HL-LHC.
 %
-In this section we show how our qualitative results, in particular
+In this section, we show how our qualitative results, in particular
 the enhanced discrimination provided by the MVA, are robust
-even when realistic pile-up conditions are accounted for.
+in the presence of realistic PU conditions.
+
+First of all we describe the simulation of realistic
+PU conditions at the HL-LHC, and discuss the settings of
+the PU subtraction strategy that we adopt.
 %
-First of all we describe the simulation of realistic
-pile-up conditions at the HL-LHC, and the corresponding
-subtraction using {\tt SoftKiller}.
-%
-Then we present the validation of the pile-up subtraction,
+Then we present the validation of the PU subtraction,
 and compare a number of distributions, including substructure variables,
@@
 Finally we revisit the MVA analysis of Sect.~\ref{sec:mva}, and
-show that our qualitative conclusions are unchanged even
+show that our qualitative conclusions are robust
 in the presence of realistic PU conditions.
+%
+As we will show now, a signal significance for
+Higgs production in the $4b$ final state
+of up to $S/\sqrt{B}\simeq 4$
+can be achieved at the HL-LHC even accounting for PU.
 
-\subsection{Pile-up subtraction with {\tt SoftKiller}}
+\subsection{PU subtraction with {\tt SoftKiller}}
 
-With this motivation, a large number
-of minimum bias events have been added to the various signal
+To study the impact of PU in our analysis,
+a large number
+of Minimum Bias (MB) events,
+including Multiple Parton Interactions (MPI),
+have been added to the signal
 and background samples described in Sect.~\ref{mcgeneration}.
 %
-We have explored two scenarios for the amount of pile-up expected
+We have explored two scenarios for the amount of PU expected
 at the HL-LHC, one with a mean number of
@@
 %
-Minimum bias events have been generated with {\tt Pythia8} using
-the Monash 2013 tunes.
+MB events have been generated with {\tt Pythia8} using
+the Monash 2013 tune.
 %
 We have generated a total of 100M minimum-bias events, which are
-then superimposed to the hard-scattering events in a random way.
+then randomly superimposed to the hard-scattering events.
 
-In order to subtract the pile-up, a number of techniques
-have been developed recently. While PU will be be one of the major problems at the HL-LHC, fortunately
-a number of powerful methods for the subtraction of  UE, MPI and PU
-effects 
-have been developed recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
+In order to subtract the PU, a large number of techniques
+have been proposed recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
 %
-While a complete optimization of the PU subtraction strategy is beyond
-the scope of this work, here we will use the {\tt SoftKiller}
-method~\cite{Cacciari:2014gra}
-as implemented in {\tt FastJet}.
+In this work, PU  will be subtracted by means
+of the the {\tt SoftKiller}
+method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
+%
+Let us note however that
+a systematic optimization of the PU subtraction strategy is beyond
+the scope of this work, and in particular that further
+improvements over the results presented below is feasible
+with further tuning of the PU subtraction.
 
 The idea underlying {\tt SoftKiller} is based on eliminating particles
-below a given cut-off in transverse momentum, $p_T^{\rm cut}$, whose
+below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
 value is dynamically determined in a way that makes the event-wide
-transverse-momentum flow density $\rho$
+transverse-momentum flow density $\rho$ vanish.
+%
+This $p_T$ flow density is defined as
 \be
-\rho={\rm median} \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\}
+\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
 \ee
 where the median is computed over all the patches $i$ with area
-$A_i$ and transverse momentum $p_{Ti}$ in which the event is partitioned.
+$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
+is partitioned.
 %
+From its definition, we observe that the value of $p_T^{(\rm cut)}$
+will be dynamically raised until half of the patches have $\rho=0$.
+
 The size and number of these patches is a free parameter of the algorithm -
-in this work we will use a value $a=0.4$ for the length of these
-patches.
+here we will use square patched with length $a=0.4$.
 %
-We restrict ourselves to the rapidity interval
-$\eta \in \lc -2.5, 2.5\rc$ for the estimation of the
-$p_T$ flow density $\rho$, since only the central region
-is used in this analysis.
+We restrict ourselves to the central rapidity interval,
+$\eta \in \lc -2.5, 2.5\rc$, for the estimation of the
+$p_T$ flow density $\rho$, which is the region relevant
+for the present analysis.
 %
 In this work, the {\tt SoftKiller} method is applied
-to the particles at the end of the parton shower, before
-they are clustered into the anti-$k_t$ jets.
+to particles at the end of the parton shower, before
+the jet clustering stage.
 
-\subsection{Validation of pile-up subtraction}
+\subsection{Validation of the PU subtraction}
 
@@
 %
-To this end, we compare various kinematical distributions in three
+To this end, we compare different kinematical distributions
+in the three relevant cases:
 cases:
 \begin{itemize}
-\item without any pile-up,
-\item with pile-up, but without any PU subtraction,
-  \item with pile-up and with {\tt SoftKiller} subtraction.
+\item without any PU,
+\item adding PU, but without any PU subtraction,
+  \item adding PU, followed by the {\tt SoftKiller} subtraction.
 \end{itemize}
-As we will show now, some substructure variables in the boosted
-regime are particularly robust against PU effects, and this
-will have the important consequence that the MVA discrimination
-will not be substantially affected.
+As we will show now, {\tt SoftKiller} exhibits a reasonable
+performance in PU subtraction.
+%
+We will also see that the boosted category is less affected
+by PU than the resolved category, as expected from the higher
+$p_T$ threshold in the corresponding selection cuts.
 
-In Fig.~\ref{fig: pu-vs-nopu-comparison-d2} we
-compare the distribution of the $D_2^{(\beta)}$
-    substructure variable, Eq.~(\ref{eq:d2}), for the
-    boosted category in two cases: without PU, and
-    with $\la n_{\rm PU}\ra=150$ PU events.
+Let us begin by comparing
+a number of signal distributions with
+and without PU, with $\la n_{\rm PU}\ra=80$ in the former
+case.
 %
-    In the latter case, PU has been subtracted using
-    {\tt SoftKiller}.
-    %
-    We see that the distribution is relatively unaffected by PU.
-    %
-    Note that by construction $D_2^{(\beta)}$ has been designed
-    to be insensitive to PU, so this agreement is an important
-    cross-check.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-  \begin{center}
-      \vspace{-1cm}
-  \includegraphics[width=0.60\textwidth]{plots/pu-vs-nopu-comparison-d2.pdf}
-  \caption{\small
-    Comparison of the distribution of the $D_2^{(\beta)}$
-    substructure variable, Eq.~(\ref{eq:d2}), for the
-    boosted category in two cases: without PU, and
-    with $\la n_{\rm PU}\ra=150$ PU events.
-    %
-    In the latter case, PU has been subtracted using
-    {\tt SoftKiller}.
-    %
-    See text for more details.
-}
-\label{fig:pu-vs-nopu-comparison-d2}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-We now compare a number of signal distributions with
-and without PU.
-%
-In Fig.~\ref{fig:m_H_PU} we show first of all the invariant mass distribution
-of the leading and subleading Higgs candidates in the boosted
+In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
+of the leading and subleading Higgs candidates. in the boosted
 and resolved categories.
 %
-These distributions are plotted after the $b$-tagging,
+These distributions are plotted after the $b$-tagging, that is,
 before they are used as input to the MVA.
@@
 As we can see, in the boosted category, the residual effects of PU
-after the SoftKiller subtraction are very mild in this
-distribution.
+after the {\tt SoftKiller} subtraction are very mild in these
+distributions, with the position of the Higgs mass peaks essentially
+unchanged.
 %
 The effects are more important for the resolved category, where PU
-shifts the Higgs peak by am amount $\Delta m_h \simeq 5$ GeV.
+shifts the Higgs peak by an amount $\Delta m_h \simeq 5$ GeV.
 
@@
     (upper plots) and boosted (lower plots) categories,
-    without PU and with $\la n_{PU}\ra=80$ subtracted with SoftKiller.
+    without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+Next we compare the transverse momentum of the leading Higgs
+candidate, $p_t^{h_1}$ and the invariant mass of the di-Higgs system
+$m_{hh}$, in Fig.~\ref{fig:mHH_PU}, both for the boosted and
+for the resolved categories.
+%
+In the case of the $p_T$, the differences between the resolved
+and boosted selection cuts can be clearly observed.
+%
+The effect of PU is negligible in the boosted case, and small
+in the resolved case, except for large $p_T$ values.
+%
+For the case of the $m_{hh}$ distribution, similar conclusions
+apply.
+%
+Note that this latter observable is particularly sensitive
+of BSM dynamics.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
+  \caption{\small
+    Comparison of the transverse momentum $p_T^h$ of the leading
+    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
+    of the di-Higgs system (lower plots) in the resolved
+    (left plots) and boosted (right plots) categories,
+    without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
+}
+\label{fig:mHH_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Then we assess the impact of PU in some of the substructure variables
+used as input to the MVA in the boosted category.
+%
+In particular we consider the subjetiness variable,
+$\tau_{21}$, and the ratio
+of energy correlation functions $D_2^{(\beta)}$,
+corresponding to the the leading Higgs candidate.
+%
+This comparison is illustrated in Fig.~\ref{fig:Substructure_PU}.
+%
+As can be seen, these substructure variables, which
+as demonstrated before carry a very substantial
+discrimination power, are relatively unaffected by PU.
+%
+Therefore, we don't expect a substantial loss of discrimination
+power due to PU effects in our analysis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/tau21_h0_bst_comp.pdf}
+   \caption{\small
+     Comparison of the substructure variables $D_2^{(\beta)}$ (left)
+     and $\tau_{21}$ (right)
+     for the leading Higgs candidate in the boosted category,
+   without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
+}
+\label{fig:Substructure_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Up to know we have restricted ourselves to the study of the impact of PU
+on signal distributions.
+%
+We now assess how the signal over background discrimination can be affected
+in the presence of realistic PU conditions.
+
+{\bf add plots signal vs background with PU}
 

### 2015-11-17 paper/sec-pileup.tex
more work on paper

@@
 In this work, PU  will be subtracted by means
-of the the {\tt SoftKiller}
+of the the {\tt SoftKiller} (SK)
 method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
@@
 
-\subsection{Signal significance in the presence of PU}
+\subsection{MVA revisited with PU effects}
 
-Finally, we revisit how the signal significance after the MVA
-is affected by the inclusion of realistic PU effects.
+After having discussed in some detail which are the effects
+of PU in the various kinematic distributions that are used
+as input to the MVA, we now revisit the analysis
+of Sect.~\ref{sec:mva} now with PU included.
 
-%%%%%%%%%%%%%%%%%%%%%%%%
+First of all we compare the distribution of the ANN output for the
+signal and background MC events in the boosted and resolved categories,
+the analogous comparison in the case without PU was shown
+in Fig.~\ref{fig:nnresponse}.
+%
+As we can see in Fig.~\ref{fig:nnresponse_PU}, there is a clear discrimination
+between signal and background in the two categories, also
+in the case of PU included.
+%
+However, by comparing with Fig.~\ref{fig:nnresponse} we see
+that some of the most distinguishing features that separate signal
+and background in the ANN output are reduced when PU effects
+are included.
+%
+For instance, in the boosted category, there is a trend of the distribution
+for signal events to move towards smaller values of the
+ANN discriminant.
+%
+This in turn will entail a reduction of the signal significance as
+compared to the case without PU.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[t]
   \begin{center}
-\includegraphics[width=0.48\textwidth]{plots/ssb_pu.pdf}
-\includegraphics[width=0.48\textwidth]{plots/sb_pu.pdf}
-\caption{\small
-  Same as Fig.~\ref{fig:sb_mva} this time for the analysis including
-  effects of PU, with $\la n_{\rm PU}\ra=150$.
+\includegraphics[width=0.49\textwidth]{plots/Resolved_disc_SKPU80.pdf}
+\includegraphics[width=0.49\textwidth]{plots/Boosted_disc_SKPU80.pdf}
+\caption{\small Same as Fig.~\ref{fig:nnresponse},
+  this time with $\la n_{\rm PU}\ra=80$ PU events per bunch crossing
+  and SK subtraction, for the resolved (left) and boosted
+  (right) categories.
+  %
+  The corresponding comparison without PU was shown in
+  Fig.~\ref{fig:nnresponse}.
 }
-\label{fig:sb_mva_pu}
+\label{fig:nnresponse_PU}
 \end{center}
@@
 
-In Fig.~\ref{fig:sb_mva_pu} we show the signal significance,
+Next we consider the number of signal and background events that
+are expected at the HL-LHC as a function of the ANN discriminant -
+the corresponding results without PU are those of
+Fig.~\ref{fig:nev2}.
+%
+As we can see from Fig.~\ref{fig:nev2_PU}, the trends are
+similar as in the no PU case, for instance, in the boosted
+category we are left with around 200 events for the optimal value
+of the ANN cut.
+%
+Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we also observe
+that the intermediate category is substantially degraded once PU
+is included, since a reduced number of events fall into this
+category now.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{plots/nev2_SKPU80.pdf}
+\caption{\small Same as Fig.~\ref{fig:nev2} now
+  with  $\la n_{\rm PU}\ra=80$ PU events 
+  and SK subtraction.
+}
+\label{fig:nev2_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Now we can finally revisit the post-MVA signal significance,
+$S/sqrt{B}$, and he signal over background ratio, $S/B$,
+in the case of PU, and compare with the corresponding
+no PU results shown in Fig.~\ref{fig:sb_mva}.
+%
+
+In Fig.~\ref{fig:sb_mva_PU} we show the signal significance,
 $S/\sqrt{B}$, as well as the signal over background ratio,
@@
 certainly still room for improvement.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/ssb_SKPU80.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb_SKPU80.pdf}
+\caption{\small Same as Fig.~\ref{fig:sb_mva}
+  now
+  with  $\la n_{\rm PU}\ra=80$ PU events 
+  and SK subtraction.
+}
+\label{fig:sb_mva_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+To conclude, it is illustrative to quantify which of the input variables
+to the MVA are most significant in the case of PU,
+and compare it with the corresponding
+results without PU.
+%
+We use the same estimator as in Sect.~\ref{sec:signalsignificance},
+namely the sum
+of the absolute value of all the weights connected to a given
+input neuron $i$, Eq.~(\ref{eq:totweight}).
+%
+The results for the resolved and boosted categories are shown
+on Fig. ...
+%
+As we can see

### 2015-11-17 paper/paperscripts/plotMVAdat_noPU.py

@@ -15,6 +15,8 @@ datafiles=[ "../plotdata/results_noPU/MVA/nn_12X5X3X1_50000-Gen_noPU_res.dat",
 			"../plotdata/results_noPU/MVA/nn_21X5X3X1_50000-Gen_noPU_bst.dat"]
 
 datanames=[ "Resolved","Intermediate","Boosted"]
+titlenames=[ "Resolved Category","Intermediate Category",\
+             "Boosted Category"]
 
 
 # HL-LHC luminosity
@@ -32,13 +34,11 @@ SSBout = "ssb_noPU"	  # S/Sqrt(B) curve
 NeVout = "nev_noPU"	  # Number of events (twin axes)
 NeV2out = "nev2_noPU"  # Number of events (single axis)
 
-
- 
  
 #############################################################################
 
 # Plot the individual discriminant histograms
-def plotDiscriminantHisto(name, signal, background):
+def plotDiscriminantHisto(name, signal, background,title):
         plt.rcParams.update({'font.size': 16})
 	bins = numpy.linspace(0, 1, 20) # Binning density
 	fig, ax = plt.subplots()
@@ -48,15 +48,14 @@ def plotDiscriminantHisto(name, signal, background):
 
 	ax.set_ylim([0,10])
 	ax.set_xlabel("ANN Output")
-        ax.set_ylabel("A. U.")
+        ax.set_ylabel("a. u.")
 
 	# Legend
 	legend = ax.legend(fontsize=18, loc='best')
 	legend.get_frame().set_alpha(0.8)
 
 	numpoints = str( len(background) + len(signal) ) + " events: " + str(len(signal)) + " signal, " + str(len(background)) + " background."
-	# fig.text(0.13,0.92,numpoints, fontsize=12)
-	fig.text(0.35,0.92,name + " category", fontsize=19)
+	fig.text(0.33,0.93,title, fontsize=19)
 
 	figname = name + "_"+Histout+".pdf"
 	fig.savefig(figname)
@@ -78,7 +77,7 @@ rocax.yaxis.grid(True)
 sb, sbax = plt.subplots()
 sbax.set_ylabel("$S/B$",fontsize=19)
 sbax.set_xlabel("ANN output cut")
-sbax.set_ylim([0.00001,10])
+sbax.set_ylim([0.0001,1])
 sbax.set_xlim([0,0.95])
 
[…]

### 2015-11-17 paper/sec-mva.tex
more work on paper
Even more work on paper

@@
       \vspace{-1cm}
-  \includegraphics[width=0.90\textwidth]{plots/res_nnarch.pdf}
+  \includegraphics[width=0.90\textwidth]{plots/bst_nnarch_noPU.pdf}
   \vspace{-1cm}
-\caption{\small Architecture of the ANN used for the analysis of the resolved
-  category, with $N_{\rm var}=13$ input variables and thus the same number of neurons
+  \caption{\small Architecture of the ANN used for the analysis of the
+    boosted
+    category, with $N_{\rm var}=21$ input variables and thus
+    the same number of neurons
   in the first layer.
@@
 \subsection{Signal significance after the MVA}
+\label{sec:signalsignificance}
 
@@
 \begin{center}
-\includegraphics[width=0.65\textwidth]{plots/Boosted_disc.pdf}
-\includegraphics[width=0.48\textwidth]{plots/Intermediate_disc.pdf}
-\includegraphics[width=0.48\textwidth]{plots/Resolved_disc.pdf}
+\includegraphics[width=0.65\textwidth]{plots/Boosted_disc_noPU.pdf}
+\includegraphics[width=0.48\textwidth]{plots/Intermediate_disc_noPU.pdf}
+\includegraphics[width=0.48\textwidth]{plots/Resolved_disc_noPU.pdf}
 \caption{\small The distribution as a function of the ANN output
@@
 \begin{center}
-\includegraphics[width=0.65\textwidth]{plots/nev2.pdf}
+\includegraphics[width=0.65\textwidth]{plots/nev2_noPU.pdf}
 \caption{\small Number of signal (dashed lines) and background (solid lines)
@@
 \begin{center}
-\includegraphics[width=0.49\textwidth]{plots/res_wgthist.pdf}
-\includegraphics[width=0.49\textwidth]{plots/boosted_wgthist.pdf}
+\includegraphics[width=0.49\textwidth]{plots/res_wgthist_noPU.pdf}
+\includegraphics[width=0.49\textwidth]{plots/bst_wgthist_noPU.pdf}
 \vspace{-0.5cm}
@@
 \begin{center}
-\includegraphics[width=0.48\textwidth]{plots/ssb.pdf}
-\includegraphics[width=0.48\textwidth]{plots/sb.pdf}
+\includegraphics[width=0.48\textwidth]{plots/ssb_noPU.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb_noPU.pdf}
 \caption{\small

### 2015-11-17 paper/sec-pileup.tex
Even more work on paper

@@
 The results for the resolved and boosted categories are shown
-on Fig. ...
+on Fig.~\ref{fig:nnweights_PU}.
 %
-As we can see
+As we can see by comparing to the corresponding
+results without PU in Fig.~\ref{fig:nnweights}, we see that
+in the boosted category, the discrimination power of the invariant
+mass of Higgs candidates is decreased and that of the various substructure
+variables, in particular $C_2$ and $D^{{\rm rm}}$, is conversely
+increased.
+%
+This reflects the fact that these substructure variables are
+relatively robust against PU contamination.
+
+In the case of the resolved category, in the case without PU the highest
+values of the weight sum were found for the $p_T$ of the leading
+Higgs and for the Higgs invariant masses.
+%
+This is also true in the case with PU, but now the rapidity difference
+between the two Higgs candidates, $\Delta y_{hh}$ increases its
+importance, again reflecting that this variable is relatively
+insensitive to PU effects.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/res_wgthist_SKPU80.pdf}
+\includegraphics[width=0.49\textwidth]{plots/bst_wgthist_SKPU80.pdf}
+\vspace{-0.5cm}
+\caption{\small
+Same as Fig.~\ref{fig:nnweights} in the case of PU.
+}
+\label{fig:nnweights_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Combined results}
+
+Finally, we now combine the three categories, resolved,
+intermediate and boosted, and determine the signal
+significance taking into account all event topologies.
+%
+First of all, in Table~\ref{table:cutflowMVA_PU}
+we provide the  the number of signal and
+    background events at the HL-LHC, as well as the $S/\sqrt{B}$ and $S/B$,
+    for both the cut-based analysis (corresponding
+    to $y_{\rm cut}=0$) and after the
+    optimal MVA cut.
+    %
+    These numbers corresponding to the simulations
+    with $\la n_{\rm PU}\ra=80$
+    and SK subtraction.
+    %
+    The corresponding results without PU were collected
+    in Table.~\ref{table:cutflowMVA}.
+    %
+    The value of the optimal MVA cut $y_{\rm cut}$ is determined
+    as the one leading to highest signal significance, with
+    the constraint that number of MC events left is still large
+    enough to tame statistical fluctuations.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Boosted category, $\la n_{\rm PU}\ra=80$+SK}\\
+    \hline
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.84$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+    362  &  $1.4\cdot 10^6$     & 0.31       &  $3\cdot 10^{-4}$ &
+    248     &   7250             &  2.9       & 0.034 \\
+        \hline
+  \end{tabular}
+   $\,$\\
+  \vspace{0.4cm}
+  \noindent
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Intermediate category,  $\la n_{\rm PU}\ra=80$+SK}\\
+    \hline
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.72$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+    146  &    $9\cdot 10^5$   & 0.15        &  $2\cdot 10^{-4}$      &
+  53  &  2547        & 1.1        &  0.02 \\
+        \hline
+  \end{tabular}
+    $\,$\\
+  \vspace{0.4cm}
+  \noindent
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Resolved category,  $\la n_{\rm PU}\ra=80$+SK}\\
+    \hline
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+  1123  &    $8.5\cdot 10^6$   & 0.40       &  $1.3\cdot 10^{-4}$       &
+  432  &  $3\cdot 10^4$        &   2.5      & 0.15 \\
+        \hline
+  \end{tabular}
+  \caption{\small The results for the number of signal and
+    background events
+    at the HL-LHC for both the cut-based analysis and after the
+    optimal MVA cut, as well as the $S/\sqrt{B}$ and $S/B$
+    values in the two cases, in the case of $\la n_{\rm PU}\ra=80$
+    and SK subtraction.
+    %
+    The corresponding results without PU were collected
+    in Fig.~\ref{table:cutflowMVA}.
+        \label{table:cutflowMVA_PU}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From Table~\ref{table:cutflowMVA_PU} we see that, thanks
+to the MVA, we can improve the signal significance and the
+signal over background ratio from 0.31 and $3\cdot 10^{-4}$
+(0.40 and $1.3\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
+in the boosted (resolved) category.
+%
+The intermediate category exhibits a lower value of $S/\sqrt{B}$
+for the optimal $y_{\rm cut}$ value, around unity.
+%
+We thus conclude that the boosted category is the most promising
+one for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
+at the HL-LHC, with however useful information also provided
+by the resolved category.
+
+In summary, in this section we have demonstrated the robustness
+of our results under the presence of PU conditions as those
+expected at the HL-LHC.

### 2015-11-17 paper/sec-conclusions.tex
More work on the paper

--- 2015-07-06 paper/sec-conclusions.tex
@@
 
-In this work we have presented a detailed study of the feasibility
-of the measurement of Higgs pair production in the $bb\bar{b}\bar{b}$
+In this work, we have presented a detailed study of the feasibility
+of the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
 final state at the High-Luminosity LHC.
 %
-As opposed to previous works, we have combined a traditional
-cut-based analysis with a modern multivariate analysis,
-which allows one to significantly improve the signal significance.
+Our strategy is based on the combination of a traditional
+cut-based analysis with modern multivariate analyses,
+which allows improving the signal significance of this channel
+as compared to previous studies.
 %
-A careful analysis of the different possible methods to reconstruct
-Higgs pairs finds that the boosted category is the most efficient
-one, but that additional complementary information can also be provided
+Following a careful optimisation of the
+signal reconstruction strategy for different event topologies,
+we find that the highest significance is obtained
+in the 
+boosted category, while complementary information is also provided
 by the intermediate and resolved categories.
 %
-Our analysis includes all relevant backgrounds, including the
-effects from fake $b$-tags, neglected in previous works,
-which turn out to be quite important specially
-in the boosted and in the resolved categories.
 
-Thanks for the MVA improvements, and combining the information
-from the three exclusive categories, we find a signal significance
-of 3.8.
+Our analysis takes into account 
+all relevant backgrounds, in particular
+the dominant QCD multijets.
 %
-Therefore, we can conclude that, already on the $4b$ channel along,
-it should be possible to observe evidence for this process at
+We include not only the irreducible $4b$ component, but
+also the $2b2j$ and $4j$ backgrounds, which contribute
+to the yield of reconstructed Higgs candidates
+when light partons are mistagged as $b$-quarks.
+%
+We show that neglecting the contribution
+from  fakes is a poor approximation, specially for the resolved and intermediate
+categories.
+%
+The reason is that
+the impact of fakes
+can be substantially enhanced, when compared to a naive parton
+level estimate, due to combinatorics and $b\bar{b}$
+pair radiation during the parton shower.
+
+A major difficulty in measurements involving relatively low $p_T$
+jets at the HL-LHC is the large
+amount of PU expected.
+%
+To account for this, we have simulated realistic PU conditions
+and used the recently developed {\tt SoftKiller} method to reduce
+the PU contamination.
+%
+We find that, especially in the boosted category, the impact of
+PU after its subtraction is rather mild, and in particular the jet
+substructure variables, which carry substantial
+discrimination information, are reasonably robust against PU effects.
+
+For a PU of $\la n_{\rm PU}\ra=150$, along what is expected
+at the HL-LHC, our main result is that the combined
+signal significance for the three categories is $S/\sqrt{B}\simeq 4.0$,
+substantially improving previous studies.
+%
+Therefore, we conclude that, already from the $b\bar{b}b\bar{b}$
+final state alone,
+it should be possible to claim evidence for Higgs pair production at
 the HL-LHC.
 %
-A combination with other decay channels, like $b\bar{b}\gamma\gamma$
-and $b\bar{b}\tau\tau$ would still be required in order
-to claim discovery of Higgs pair production.
+This  estimate for $S/\sqrt{B}$  could
+be further enhanced,
+in particular following an optimization of the PU subtraction
+strategy.
 
-One important implication of our results is which is the accuracy
-that can be achieved for a measurement of the
-Higgs trilinear coupling $\lambda$ from a measurement
-of the $4b$ final state.
+One important implication of our study is that it should
+be possible to improve  the accuracy on the extraction of
+the Higgs trilinear coupling $\lambda$ from
+a measurement of the
+$\sigma\lp hh\to b\bar{b}b\bar{b}\rp$ cross-section, as compared
+to existing estimates.
 %
-We plan to quantify this in future work.
+A determination of $\lambda$ in our approach would require
+ however a substantial
+ amount of work, involving
+ not only regenerating signal samples
+ for a wide range of values of  $\lambda$, but also
+ repeating the analysis
+optimisation, including the MVA training, for each
+of these values.
 %
-In addition,
-in this work we have considered only SM production mechanism,
-but it is well known that many BSM scenarios predict deviations
-in Higgs pair production, both at the level of rates,
-for instance when the trilinear coupling $\lambda$, and of
-shapes of the distributions, when higher-order effective
-operators are included in the theory~\cite{Azatov:2015oxa}.
+This study is left to a future
+publication, where we will also
+compare with the corresponding  precision 
+that has been obtained in other final states.
 %
-In this respect, we plan to study which are the constraints
-on BSM physics that can be obtained from measurements
-of Higgs pair production in the $4b$ channel.
+It will be in particular interesting to contrast
+with the extraction of $\lambda$ from the
+ $b\bar{b}\gamma\gamma$
+and $b\bar{b}\tau\tau$ final states, that, while having
+smaller rates as compared to $b\bar{b}b\bar{b}$,
+benefit from reduced backgrounds.
 %
-This however will be a computationally intensive task since in
-general BSM physics modify the shapes of the Higgs kinematical
-distributions, and thus each different point in the parameter
-space would require a re-optimization via a new training
+
+Our analysis relies on the careful modeling of kinematical
+distributions of signal and background events, since these provide
+the inputs to the MVA discriminant.
+%
+In this respect, it would be important, having established the key
+relevance of the $b\bar{b}b\bar{b}$ channel for the study of
+Higgs pair production, to revisit and improve the
+theoretical modeling of our signal and background simulation,
+in particular using NLO calculations matched to
+parton showers both for signal~\cite{Frederix:2014hta,Maierhofer:2013sha}
+and for backgrounds~\cite{Alwall:2014hca,Gleisberg:2008ta}.
+%
+
+In this work we have considered only the SM production mechanism,
+but many BSM scenarios predict deviations
+in Higgs pair production, both at the level of total rates
+and of
+differential distributions.
+%
+In the absence of new explicit degrees of freedom,
+deviations from the SM can be parametrized in
+the EFT framework using higher-order
+operators~\cite{Azatov:2015oxa,Goertz:2014qta}.
+%
+We thus plan to study which are the constraints
+on the coefficients of these effective
+operators that can be obtained from measurements
+of various $hh\to b\bar{b}b\bar{b}$ distributions.
+%
+Note that the higher rates of the $b\bar{b}b\bar{b}$ final state as compared to
+other final states, such as
+$b\bar{b}\gamma\gamma$, allow to better constrain operators
+that modify the high-energy behavior
+of the theory, in particular
+since it becomes possible
+to access the tail of the $m_{hh}$ distribution.
+
+As in the case of the extraction of the Higgs
+trilinear coupling $\lambda$, such study
+would be a computationally intensive task, since
+BSM dynamics will modify the shapes of the kinematical
+distributions, and thus in principle each point in the EFT parameter
+space would require a re-optimization with a new training
 of the MVA.
+%
+In order to explore efficiency the BSM parameters
+without having to repeat the full analysis
+for each point, modern techniques
+such as the Cluster Analysis method proposed
+in Ref.~\cite{Dall'Osso:2015aia} could be useful.
+
+Finally, it would be interesting to estimate the prospects for
+Higgs pair production in the $b\bar{b}b\bar{b}$  final
+state at a Future Circular
+Collider (FCC) with a center of mass energy of
+100 TeV~\cite{Barr:2014sga,Azatov:2015oxa,Papaefstathiou:2015iba}.
+%
+While signal yields would be certainly increased, also the QCD
+multijet background would grow, so it would necessary to repeat
+our analysis, including full background simulation, at 100 TeV,
+and assess if the accuracy in the extraction of the trilinear $\lambda$
+is improved or degraded as compared to the 14 TeV case.
+%
 
@@
 %
-J.~R. is supported by an STFC Rutherford Fellowship ST/K005227/1.
+We thank E.~Vrodynou and M.~Zaro for assistance with di-Higgs production
+  in {\tt MadGraph5\_aMC@NLO}.
+%
+  J.~R. is supported by an STFC Rutherford Fellowship and
+  Grant ST/K005227/1 and ST/M003787/1.
 %
 J.~R. and N.~H. are
-supported by an European Research Council Starting Grant "PDF4BSM".
+supported by an European Research Council Starting Grant ``PDF4BSM".
 %
@@
 government.
+%
 K.~B. is supported by a studentships from the Rhodes Foundation.

### 2015-11-17 paper/sec-mva.tex
More work on the paper

@@
   \includegraphics[width=0.90\textwidth]{plots/bst_nnarch_noPU.pdf}
-  \vspace{-1cm}
-  \caption{\small Architecture of the ANN used for the analysis of the
+  \vspace{-2cm}
+  \caption{\small Architecture of the Artificial
+    Neural Network
+    used for the analysis of the
     boosted

### 2015-11-17 paper/sec-pileup.tex
More work on the paper

@@
 
+Adding in quadrature the signal significance from the three
+(exclusive) categories, our final combined result is
+\be
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0 \, ,
+\ee
+far above the threshold for {\it evidence}, and close to the
+requirement for {\it discovery}.
+%
+In addition, it should be emphasized that there is still
+room for improvement, in particular by means of a tailored
+study dedicated to optimize PU subtraction in this process.
+
 In summary, in this section we have demonstrated the robustness
@@
 expected at the HL-LHC.
+%
+With a signal significance of $S/\sqrt{B}\sim 4$, is clear that
+the $b\bar{b}b\bar{b}$ final state can be used to claim evidence
+for Higgs pair production at the HL-LHC without the need
+to combine with any other final state.
+%
+It will be important now to quantify the precision of
+a extraction of the Higgs trilinear coupling $\lambda$ using
+the techniques presented here, but this is left for future work.

### 2015-11-17 paper/sec-analysis.tex
more work on draft

@@
 
+In Table~\ref{tab:cutflowdetails}
+we summarize the details of the cut flow of the present analysis,
+separated into the exclusive boosted, intermediate
+    and resolved categories.
+    %
+    From top to bottom, additional cuts are required in addition
+    to the previous ones.
+    %
+    As we can see ....
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \begin{tabular}{|c|c|c|c|}
+\hline
+&  Boosted  &   Intermediate &  Resolved  \\
+\hline
+\hline
+C0 &  Generator level &  Generator level & Generator level \\
+\hline
+C1A & $N_{\rm jets}^{R}\ge 2$ & $N_{\rm jets}^{r}\ge 2$, $N_{\rm jets}^{R}=1$  &
+ $N_{\rm jets}^{r}\ge 4$ \\
+ C1B & +$p_T$ cuts & +$p_T$ cuts
+ & +$p_T$ cuts \\
+ C1C & + rapidity cuts &  + rapidity cuts &
+ + rapidity cuts \\
+ C1D & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
+  Higgs reco possible \\
+C1E & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
+\hline
+C2 & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
+\hline
+  \end{tabular}
+  \caption{\small Details of the cut flow of the present analysis in the boosted, intermediate
+    and resolved categories.
+    %
+    See text for more details.
+    \label{tab:cutflowdetails}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Optimisation of kinematical cuts}

### 2015-11-17 paper/sec-pileup.tex
more work on draft

@@
 in the presence of realistic PU conditions.
+%
+First of all let us consider the boosted category.
+%
+In Fig.~\ref{fig:signal-vs-back-boosted} we compare
+various kinematical distributions for signal and background events,
+     with and without PU: the invariant mass and the $p_T$ of the leading
+     Higgs candidate, and the $\tau_{21}$ and $D^{(\beta)}_2$ substructure variables.
+     %
+     All these distributions correspond to the boosted category.
+     %
+     While for signal distributions the effects of PU after SK subtraction are small,
+     differences are more marked for the background distributions, where
+     the shapes of the distributions with and without background can be substantially
+     different.
+     %
+     We note however that the fact that signal and background distribution exhibit
+     rather different behaviors is maintained in the presence of PU.
 
-{\bf add plots signal vs background with PU}
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_h0_bst_comp_back.pdf}
+   \includegraphics[width=0.49\textwidth]{plots/tau21_h1_bst_comp_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp_back.pdf}
+   \caption{\small
+     Comparison of kinematical distributions for signal and background events,
+     with and without PU: the invariant mass and the $p_T$ of the leading
+     Higgs candidate, and the $\tau_{21}$ and $D^{(\beta)}_2$ substructure variables.
+     %
+     All these distributions correspond to the boosted category.
+}
+\label{fig:signal-vs-back-boosted}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Now we perform a similar comparison this time for
+the resolved category.
 

### 2015-11-17 paper/sec-pileup.tex
a first complete version of the paper

@@
 the resolved category.
+%
+In Fig.~\ref{fig:signal-vs-back-resolved} we compare
+the kinematical distributions for signal and background events,
+     with and without PU, for the invariant mass and the $p_T$ of the leading
+     Higgs candidate.
+     %
+     Here the PU-subtracted background distributions appear reasonably close
+     to their no PU counterparts.
+     %
+     Differences between signal and background distributions are maintained after PU
+     has been accounted for - we have checked that this is the case
+     in general.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/m_h0_res_comp_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_h0_res_comp_back.pdf}
+     \caption{\small
+       Same as Fig.~\ref{fig:signal-vs-back-boosted} for the resolved category,
+       this time without the jet substructure variables.
+}
+\label{fig:signal-vs-back-resolved}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-11-17 paper/paperscripts/plotHist_m_h0_res_comp_back.py

@@ -1,0 +1,141 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_h0_res_comp_back"
+
+linestyles = [ 'solid', 'dashed','solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H0_res_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_H0_res_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_m_H0_res_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/background/histo_m_H0_res_C1e.dat")
+
+# Plot labels
+plotnames.append("Signal, no PU")
+plotnames.append("Signal, $n_{PU}=80$ + SK")
+plotnames.append("Background, no PU")
+plotnames.append("Background, $n_{PU}=80$ + SK")
+
+# Axis labels
+xLabel = "Leading Higgs Candidate Invariant Mass (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'r', 'b', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+
+ax.set_xlim([90,175])
+ax.set_ylim([1e-3,0.1])
+
+
+
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
[…]

### 2015-11-27 paper/paperscripts/getCutFlows_check.py
Added tables with cut flow

@@ -4,9 +4,14 @@ import math
 import yoda
 from tabulate import tabulate
 
-###################################################################
+##################################################################
+
 
 root = "../../paper/plotdata/results_noPU/"
+labeltag="noPU"
+
+#root = "../../paper/plotdata/results_SK_PU80/"
+#labeltag="SKPU80"
 
 folders = ['diHiggs/', 'background/', 'SHERPA_QCD4b/', 'SHERPA_QCD2b2j/', 'SHERPA_QCD4j/', 'SHERPA_QCDttbar/']
 names = ['signal', 'total bkg', '4b', '2b2j', '4j', 'ttbar']
@@ -93,11 +98,18 @@ for key in operations:
 			else:
 				row = op(signal,cutflows[folder+regime])
 				CFtable.append(row)
-
+                                
 		CFtable=zip(*CFtable)
-		tables.append(tabulate(CFtable, header,numalign="right", floatfmt=".4E", tablefmt=tablefmt))
+		tables.append(tabulate(CFtable, header,numalign="center", floatfmt=".1E", tablefmt=tablefmt))
 
 ######################### Print tables #########################
 
+i=1
 for table in tables:
-	print table,'\n'
+        f = open('table_'+labeltag+"_"+str(i)+'.tex', 'w')
+        i = i + 1
+        for row in table:
+                s=str(row)
+                f.write(s)
+
+        f.close()

### 2015-11-27 paper/sec-pileup.tex
More work in the paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Cut-flow}
+
+The corresponding cut-flow tables in the case
+of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
+are shown in Tables~\ref{tab:cutflow_SKPU80_1},
+\ref{tab:cutflow_SKPU80_2} and~\ref{tab:cutflow_SKPU80_3},
+for the total cross-sections, number of events expected and
+signal significance at the HL-LHC, respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \scriptsize
+  \input{tables/table_SKPU80_1.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+  \input{tables/table_SKPU80_2.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+    \input{tables/table_SKPU80_3.tex}
+    \caption{\small
+      Same as Table~\ref{tab:cutflow_noPU_1}, for the analysis
+      including PU with $\la n_{\rm PU}\ra=80$ and SK substraction.
+      \label{tab:cutflow_SKPU80_1}}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-11-27 paper/sec-results.tex
More work in the paper

@@
 
-\subsection{Cut flow and signal significance}
+\subsection{Cut-flow and signal significance}
 
-First of all we compare the cross-sections at various
+First of all, we compare the cross-sections at various
 analysis levels for the three categories, for signal and background events,
@@
 We consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
-then we discuss how results are modified if only the $4b$
+and also discuss how results are modified if only the $4b$
 component is kept.
 %
-we consider the following levels of the cut-flow
-\begin{itemize}
-\item {\bf C0}: cross-sections at the generator
-  level, before any analysis cuts.
-\item {\bf C1}:  cross-sections after the basic jet acceptance selection
-  cuts, but before $b$-tagging.
-\item {\bf C2}: cross-sections after after the $b$-tagging.
-\end{itemize}
-Note that {\bf C1} already includes the effect of the Higgs mass
-window cut, Eq.~(\ref{higgsmasswindow}).
+At each stage of the cut-flow, we also provide the
+the signal significance, $S/\sqrt{B}$, and the signal
+over background ratio, $S/B$, for the case of the
+ HL-LHC with
+an integrated luminosity of $\mathcal{L}_{\rm int}
+=3000$ fb$^{-1}$.
 %
-At the {\bf C0} level the numbers will be the same
-for the three individual categories.
-
-In the following, results are presented for the exclusive
-categorisation defined in Sect.~\ref{sec:categorisation}.
-%
-%
-At each stage of the cut flow, we also provide the number
-of events that would be expected at the HL-LHC with
-an integrated luminosity of $\mathcal{L}_{\rm int}
-=3000$ fb$^{-1}$,
-as well as 
-the signal significance $S/\sqrt{B}$ and the signal
-over background ratio $S/B$.
 %
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[t]
   \centering
-  \begin{tabular}{c|c|c||c|c||c|c}
+  \begin{tabular}{|c|c|c|c|}
 \hline
-    \multicolumn{7}{c}{Boosted category}\\
+&  Boosted  &   Intermediate &  Resolved  \\
 \hline
 \hline
-    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
-    &   $S/\sqrt{B}$  & $S/B$\\
-      &    Signal & Back   &  Signal  & Back
-    &   & \\
+C0 &  Generator level &  Generator level & Generator level \\
 \hline
-        {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
-        {\bf C1}  &  0.46    & $1.3\,10^6$    &  $1.4\,10^3$   & $3.9\,10^9$     & 0.022     &  $3.5\,10^{-7}$ \\
-        {\bf C2}  &  0.064     &  12.6     &  193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$ \\
+C1a & $N_{\rm jets}^{R}\ge 2$ & $N_{\rm jets}^{r}\ge 2$, $N_{\rm jets}^{R}=1$  &
+ $N_{\rm jets}^{r}\ge 4$ \\
+ C1b & +$p_T$ cuts & +$p_T$ cuts
+ & +$p_T$ cuts \\
+ C1c & + rapidity cuts &  + rapidity cuts &
+ + rapidity cuts \\
+ C1d & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
+  Higgs reco possible \\
+C1e & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
+\hline
+C2 & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
 \hline
   \end{tabular}
-  $\,$\\
-  \vspace{0.4cm}
-  \begin{tabular}{c|c|c|c|c|c|c}
-    \hline
-    \multicolumn{7}{c}{Intermediate category}\\
-    \hline
-    \hline
-    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
-    &   $S/\sqrt{B}$  & $S/B$\\
-      &    Signal & Back   &  Signal  & Back
-    &   & \\
-    \hline
-         {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
-        {\bf C1}  &   1.44    &   $1.1\,10^{7}$  &  $4.3\,10^3$   &  $3.3\,10^{10}$    &  0.024    &  $1.3\,10^{-7}$ \\
-        {\bf C2}  &   0.22    &  722   &  660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ \\
-        \hline
-  \end{tabular}
-  $\,$\\
-  \vspace{0.4cm}
-  \noindent
-  \begin{tabular}{c|c|c|c|c|c|c}
-    \hline
-    \multicolumn{7}{c}{Resolved category}\\
-    \hline
-    \hline
-    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
-    &   $S/\sqrt{B}$  & $S/B$\\
-      &    Signal & Back   &  Signal  & Back
-    &   & \\
-    \hline
-       {\bf C0}  &  36.9  & $9.9\,10^{9}$ & $1.1\,10^5$ & $3.0\,10^{13}$  &  0.020 & $3.7\,10^{-9}$\\
-        {\bf C1}  &   3.34    & $7.5\,10^{7}$    & $1.1\,10^4$    & $3.3\,10^{10}$     & 0.021     & $4.5\,10^{-8}$  \\
-        {\bf C2}  &   0.54    &  $3.5\,10^{3}$   &  $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$ \\
-        \hline
-  \end{tabular}
-  \caption{\small Cut-flow for the analysis of the boosted (top),
-    intermediate (middle) and resolved (bottom)
+  \caption{\small Details of the cut-flow of the present analysis in the boosted, intermediate
+    and resolved categories.
+    %
+    See text for more details.
+    \label{tab:cutflowdetails}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To begin with,
+in Table~\ref{tab:cutflowdetails}
+we summarize the details of the cut-flow of the present analysis,
+separated into the exclusive boosted, intermediate
+    and resolved categories.
+    %
+    From top to bottom, additional cuts are required in addition
+    to the previous ones.
+    %
+    The various cuts
+    are defined as follows
+    \begin{itemize}
+    \item {\bf C0}: these are the generator level cross-sections, with
+      mild generation cuts in the case of the background processes.
+    \item {\bf C1a}: at this level, we only check that we have at least
+      two large-$R$ jets (in the boosted case),
+      one large-$R$ jet and at least 2 small-$R$ jets (in the intermediate
+      case) and at least four small-$R$ jets (in the resolved case).
+      %
+      No acceptance requirements are imposed here.
+    \item {\bf C1b}: Same as C1a, but now the jets should
+      satisfy the corresponding $p_T$ thresholds:
+      $p_T \ge 200$ GeV for large-$R$ jets,
+      $p_T \ge 50$ GeV for small-$R$ jets.
+    \item {\bf C1c}: in addition, the above jets must satisfy the
+      rapidity acceptance requirement.
+    \item {\bf C1d}: at this level, large-$R$ jets must satisfy the
+      mass-drop tag condition.
+    \item {\bf C1e}: after the two Higgs candidate jets have been reconstructed,
+      their invariant masses are required to lie within the
+      $m_H$ window, namely
+    \item {\bf C2}: finally, this is the level of the analysis
+      after $b$-tagging has been performed.
+      \end{itemize}
+    Signal and background events that survive the C2 level cuts
+    are then used as input for the MVA training, as described
+    in Sect.~\ref{sec:mva}.
+
+    %
+    In Table~\ref{tab:cutflow_noPU_1} we provide
+    the values of cross-sections in fb
+     for the signal
+      and the various background
+      components as a function of the
+      cut-flow, for the resolved,
+      boosted and intermediate
       categories.
       %
-    At each level of the cut-flow, we indicate the cross-sections and the number of
-    expected events at the HL-LHC for $\mathcal{L}_{\rm int}=3$ ab$^{-1}$, both for
-    signal events and for all the backgrounds combined.
+      We see that although of course
+      $b$-tagging suppressed very substantially the $2b2j$ and
+      $4j$ backgrounds, it does not completely
+      eliminate them.
+
+\begin{table}[t]
+  \centering
+  \scriptsize
+  \input{tables/table_noPU_1.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+  \input{tables/table_noPU_2.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+    \input{tables/table_noPU_3.tex}
+    \caption{\small The cross-sections, in pb,
+      for the signal and the various background
+      processes at different points of the
+      cut-flow, for the resolved (upper table),
+      intermediate (middle table) and boosted
+      (lower table) categories, for the analysis
+      without PU.
       %
-    We also provide in each case the
-    signal significance $S/\sqrt{B}$ and the signal
-    over background ratio $S/B$.
-    %
-    The first row {\bf C0} is the generator-level result and thus is common
-    to all three categories.
-    %
-    \label{table:cutflow}
-  }
+      In each case, we also provide the signal over
+      background ratio, $S/B$, and the signal
+      significance, $S/\sqrt{B}$, considering either
+      the total background or only the $4b$ component.
+ \label{tab:cutflow_noPU_1}}
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The results for the three categories have been collected in
-Table~\ref{table:cutflow}.
 %
@@
 
-From the results of Table~\ref{table:cutflow}
+From the results of Table~\ref{tab:cutflow_noPU_1}
 it is possible to compute the corresponding numbers
@@
 
-From the results of Table~\ref{table:cutflow}
-we see that after the cut-based analysis, the significance of the Higgs pair production
-observation in the $4b$ channel using the boosted topology
+We observe
+that after the cut-based analysis, the significance of the Higgs pair production
+observation in the $b\bar{b}b\bar{b}$ channel using the boosted topology
 is $S/\sqrt{B}=0.99$,
@@
 %
-These results are shown in
-Table~\ref{table:cutflow4B}, which is the analog of
-Table~\ref{table:cutflow} but with only the QCD
-$4b$ background taken into account.
-%
-As we can see, these results indicate that given the similarity of the final states
+As we can seen before in Table~\ref{tab:cutflow_noPU_1},
+these results indicate that given the similarity of the final states
 in signal and background events in these cases, the signal significance is
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
-  \centering
-  \begin{tabular}{c|c|c||c|c||c|c}
-    \hline
-    \multicolumn{7}{c}{Boosted category}\\
-    \hline
-    \hline
-    &    \multicolumn{2}{c||}{$\sigma$ (fb)}   &  \multicolumn{2}{c||}{$N_{\rm ev}$}
-    &   $S/\sqrt{B}$  & $S/B$\\
-      &    Signal & Back   &  Signal  & Back
-    &   & \\
-    \hline
-        {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
-        {\bf C1}  &  0.46    & $1.0\,10^2$    &  $1.4\,10^3$   & $3.1\,10^5$     & 2.48     &  $4.4\,10^{-3}$ \\
-        {\bf C2}  &  0.064     &  7.1     &  193   &  $2.1\,10^4$    &  1.30    &  $9.1\,10^{-3}$ \\
-        \hline
-  \end{tabular}
-   $\,$\\
-  \vspace{0.4cm}
-  \begin{tabular}{c|c|c|c|c|c|c}
-    \hline
-    \multicolumn{7}{c}{Intermediate category}\\
-    \hline
-    \hline
-    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
-    &   $S/\sqrt{B}$  & $S/B$\\
-      &    Signal & Back   &  Signal  & Back
-    &   & \\
-    \hline
- {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
-        {\bf C1}  &  0.46    & $7.2\,10^2$    &  $1.4\,10^3$   & $2.2\,10^6$     & 2.91     &  $1.9\,10^{-3}$ \\
-        {\bf C2}  &  0.064     &  58.8     &  193   &  $1.8\,10^5$    &  1.57    &  $3.7\,10^{-3}$ \\
-        \hline
-  \end{tabular}
-  $\,$\\
-  \vspace{0.4cm}
-  \noindent
-  \begin{tabular}{c|c|c|c|c|c|c}
-    \hline
-    \multicolumn{7}{c}{Resolved category}\\
-    \hline
-    \hline
-    &    \multicolumn{2}{c|}{$\sigma$ (fb)}   &  \multicolumn{2}{c|}{$N_{\rm ev}$}
-    &   $S/\sqrt{B}$  & $S/B$\\
-      &    Signal & Back   &  Signal  & Back
-    &   & \\
-    \hline
- {\bf C0}  &  36.9  & $1.1\,10^{6}$ & $1.1\,10^5$ & $3.3\,10^{9}$  &  1.90 & $3.3\,10^{-5}$\\
-        {\bf C1}  &  0.46    & $9.0\,10^3$    &  $1.4\,10^3$   & $2.7\,10^7$     & 1.92     &  $3.7\,10^{-4}$ \\
-        {\bf C2}  &  0.064     &  986     &  193   &  $2.9\,10^6$    &  0.95  &  $5.5\,10^{-4}$ \\
-        \hline
-  \end{tabular}
-  \caption{\small Same as Table~\ref{table:cutflow}, but now
-    only with the QCD $4b$ multi-jet background taken into account.
-    %
-    \label{table:cutflow4B}
-  }
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In summary, we find that the results of our cut-based analysis are roughly
@@
 
-\subsection{Background decomposition}
-
-Up to now we have considered the effects of all backgrounds added
-together, except in Table~\ref{table:cutflow4B} and the corresponding
-discussion where we have studies how our
-results are modified if only the QCD $4b$ background is included.
-%
-In this section we study the decomposition of the background in each
-of its individual components, for the three different categories
-of events used in this work.
-%
-
-In Table~\ref{table:cutflowBack}   we show the results for the cross-sections for the different
+In Table~\ref{tab:cutflow_noPU_1}   we show the results for the cross-sections for the different
 backgrounds that we consider at the end of the cut-based analysis, for each
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
-  \centering
-  \begin{tabular}{c|c|c|c}
-    \hline
-    Background  &    \multicolumn{3}{c}{$\sigma$ (fb)}   \\
-    \hline
-  &    Resolved  &  Intermediate  &   Boosted \\
-    \hline
-    \hline
-  QCD $4b$   &   $9.9\,10^{2}$       &  $59$       &   $7.1$        \\
-  QCD $2b2j$ &   $2.4\,10^{3}$       &  $6.4\,10^{2}$       &   $3.5$        \\
-  QCD $4j$ &     $1.7\,10^{2}$       &   $22$      &    $2.1$        \\
-  $t\bar{t}$ &   $3.6$       &  $2.2$       &   $4.5\,10^{-2}$        \\
-  \hline
-  \hline
-Total     &    $3.6\,10^{3}$      &   $7.2\,10^{2}$      &     $13$      \\
-\hline
-\end{tabular}
-    \caption{\small The cross-sections for each of the individual background
-      components (and their total sum) at the end of the cut-based
-      analysis, for each of three categories.
-    \label{table:cutflowBack}
-    }
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
@@
 This effect is more dramatic in the intermediate and resolved categories: in the former,
-$2b2j$ completely dominates the background (thus the increase in $S/\sqrt{B}$ noted in
-Table~\ref{table:cutflow4B}  when only the $4b$ component is kept), and in the latter
+$2b2j$ completely dominates the background (thus the increase in $S/\sqrt{B}$
+obtained when only the $4b$ component is kept), and in the latter
 it is comparable to $4b$.
@@
 %
-On the other hand, we find that the hadronic $t\bar{t}$ component of the backround
+On the other hand, we find that the hadronic $t\bar{t}$ component of the background
 is smaller than the QCD multijet one.
@@
   is not subdominant as compared to $4b$: while its generator-level cross-section is
-  much larger, $\sigma_{2b2j} \simeq 240\sigma_{4b}$, one expects a suppression
+  much larger, $\sigma_{2b2j} \simeq 240\cdot \sigma_{4b}$, one expects a suppression
   of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
@@
   %
-  To verify this, we plot the number of $b$-quarks.....
 
-  {\bf compare parton level with hadron level distributions}
+  In the section section we show how Multivariate Analysis can be used
+  to substantially improve the signal significance obtained in the
+  cut-based analysis.

### 2015-11-30 paper/sec-mva.tex
Added plots of Higgs mass resolution

@@
 the end of the cut-based analysis, see
-the {\bf C2} row of Table~\ref{table:cutflow}.
+the {\bf C2} row of Table~\ref{tab:cutflow_noPU_1}.
 %
@@
   values correspond to the  cut-based analysis
-  results from Table~\ref{table:cutflow}.
+  results from Table~\ref{tab:cutflow_noPU_1}.
 }

### 2015-11-30 paper/sec-pileup.tex
Added plots of Higgs mass resolution

--- 2015-11-17 paper/sec-pileup.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+Finally, it is interesting to compare how the Higgs peak mass resolution is degraded
+in the case of PU.
+%
+In Fig.~\ref{fig:higgs-mass-resolution} we show the invariant mass distributions of the leading
+    Higgs candidate in signal events for the resolved category, without
+    PU (left plot) and with PU ($\la n_{\rm PU}\ra=80$+SK, right plot).
+    %
+    In both cases a Gaussian fit is used to determine the mass resolution.
+    %
+    In the case without PU, we find a mass resolution of about 8\%, corresponding
+    to around 10 GeV for the Higgs mass.
+    %
+    This mass resolution arises both from the smearing we introduce to mimic detector
+    effects as well as from ISR and FSR.
+    %
+    In the case of PU, the mass resolution is increased to around 11\%, corresponding to
+    14 GeV.
+    %
+    These values are similar to the current and prospected mass resolutions in ATLAS and CMS.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_noPU.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_PU80.pdf}
+  \caption{\small The invariant mass distributions of the leading
+    Higgs candidate in signal events for the resolved category, without
+    PU (left plot) and with PU ($\la n_{\rm PU}\ra=80$+SK, right plot).
+    %
+    In both cases a Gaussian fit is used to determine the mass resolution.
+    %
+    See text for more details.
+}
+\label{fig:higgs-mass-resolution}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Cut-flow}
+
+The corresponding cut-flow tables in the case
+of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
+are shown in Table~\ref{tab:cutflow_SKPU80_1},
+for the total cross-sections, number of events expected and
+signal significance at the HL-LHC, respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \scriptsize
+  \input{tables/table_SKPU80_1.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+  \input{tables/table_SKPU80_2.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+    \input{tables/table_SKPU80_3.tex}
+    \caption{\small
+      Same as Table~\ref{tab:cutflow_noPU_1}, for the analysis
+      including PU with $\la n_{\rm PU}\ra=80$ and SK subtraction.
+      \label{tab:cutflow_SKPU80_1}}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-11-30 paper/sec-results.tex
Added plots of Higgs mass resolution

@@
 \hline
-C0 &  Generator level &  Generator level & Generator level \\
+{\bf C0} &  Generator level &  Generator level & Generator level \\
 \hline
-C1a & $N_{\rm jets}^{R}\ge 2$ & $N_{\rm jets}^{r}\ge 2$, $N_{\rm jets}^{R}=1$  &
- $N_{\rm jets}^{r}\ge 4$ \\
- C1b & +$p_T$ cuts & +$p_T$ cuts
+{\bf C1a} & $N_{\rm jets}^{R10}\ge 2$ & $N_{\rm jets}^{R04}\ge 2$, $N_{\rm jets}^{R10}=1$  &
+ $N_{\rm jets}^{R04}\ge 4$ \\
+{\bf  C1b} & +$p_T$ cuts & +$p_T$ cuts
  & +$p_T$ cuts \\
- C1c & + rapidity cuts &  + rapidity cuts &
+ {\bf C1c} & + rapidity cuts &  + rapidity cuts &
  + rapidity cuts \\
- C1d & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
+ {\bf C1d} & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
   Higgs reco possible \\
-C1e & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
+{\bf C1e} & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
 \hline
-C2 & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
+{\bf C2} & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
 \hline
@@
 %
-The results are consistent with those summarized in
-Table~\ref{table:cutflowBack}: in the boosted case we see how $4b$ is the most important
+The results are consistent with those summarized
+before in the boosted case we see how $4b$ is the most important
 component of the background, with $2b2j$ being of the same order of magnitude, while

### 2015-11-30 paper/sec-results.tex
more work on paper

@@
 In this section we present the results of the 
-cut-based analysis and
-compare our results with other recent related studies.
+cut-based analysis.
 %
-We study how the signal significance
+We present a detailed cut-flow for the various steps
+of the analysis.
+%
+We
+compare our results with other recent related studies, in particular
+we study how the signal significance
 is modified if only the $4b$ component of the
@@
 the signal significance, $S/\sqrt{B}$, and the signal
-over background ratio, $S/B$, for the case of the
+over background ratio, $S/B$, corresponding to the case of the
  HL-LHC with
@@
 =3000$ fb$^{-1}$.
-%
 %
@@
 \hline
-{\bf C0} &  Generator level &  Generator level & Generator level \\
+{\bf C0} &  \multicolumn{3}{c|}{Generator level} \\
 \hline
@@
 $N_{\rm jets}^{R04}\ge 4$ \\
-{\bf  C1b} & +$p_T$ cuts & +$p_T$ cuts
- & +$p_T$ cuts \\
- {\bf C1c} & + rapidity cuts &  + rapidity cuts &
- + rapidity cuts \\
- {\bf C1d} & + Mass-Drop tag required & $N_{\rm jets}^{R}=1$ with MDT  &
-  Higgs reco possible \\
-{\bf C1e} & $m_H$ window cut & $m_H$ window cut & $m_H$ window cut  \\
 \hline
-{\bf C2} & $b$-tagging  &  $b$-tagging &  $b$-tagging \\
+{\bf  C1b} & \multicolumn{3}{c|}{+$p_T$ cuts} \\
+{\bf C1c} & \multicolumn{3}{c|}{+rapidity cuts}\\
+\hline
+ {\bf C1d} & +$N_{\rm MDT}\ge 2$ & $N_{\rm jets}^{R10}=1$ with MDT  &
+ Higgs reconstruction \\
+ \hline
+{\bf C1e} & \multicolumn{3}{c|}{ $m_H$ window cut} \\
+\hline
+{\bf C2} & \multicolumn{3}{c|}{$b$-tagging}    \\
 \hline
@@
     %
-    See text for more details.
       \label{tab:cutflowdetails}
@@
     \item {\bf C0}: these are the generator level cross-sections, with
-      mild generation cuts in the case of the background processes.
+      mild generation cuts in the case of the background processes, and no cuts
+      for the signal events.
+      %
     \item {\bf C1a}: at this level, we only check that we have at least
@@
       No acceptance requirements are imposed here.
-    \item {\bf C1b}: Same as C1a, but now the jets should
+    \item {\bf C1b}: in addition, now the jets should
       satisfy the corresponding $p_T$ thresholds:
@@
       rapidity acceptance requirement.
-    \item {\bf C1d}: at this level, large-$R$ jets must satisfy the
-      mass-drop tag condition.
+    \item {\bf C1d}: at this level, the two leading large-$R$ jets must
+      be mass-drop tagged in the boosted category.
+      %
+      In the intermediate category, the large-$R$ jet must also be mass-drop tagged.
+      %
     \item {\bf C1e}: after the two Higgs candidate jets have been reconstructed,
-      their invariant masses are required to lie within the
-      $m_H$ window, namely
-    \item {\bf C2}: finally, this is the level of the analysis
-      after $b$-tagging has been performed.
+      their invariant masses are required to lie a window around $m_H$,
+      in particular between 100 and 150 GeV.
+          \item {\bf C2}: This is the level of the analysis
+            after $b$-tagging has been performed, using the strategy discussed
+            in Sect.~\ref{sec:btagging}.
       \end{itemize}
-    Signal and background events that survive the C2 level cuts
-    are then used as input for the MVA training, as described
+    The signal and background events that satisfy all the analysis cut up to the
+    C2 level
+    are then used as input for the MVA training, as described next
     in Sect.~\ref{sec:mva}.
@@
     In Table~\ref{tab:cutflow_noPU_1} we provide
-    the values of cross-sections in fb
+    the values of cross-sections, in femtobarns,
      for the signal
@@
       %
-      We see that although of course
-      $b$-tagging suppressed very substantially the $2b2j$ and
-      $4j$ backgrounds, it does not completely
-      eliminate them.
+       In each case, we also provide the signal over
+      background ratio, $S/B$, and the signal
+      significance, $S/\sqrt{B}$, at the HL-LHC, considering either
+      the total background or only the $4b$ component.
+     %
+      A first important observation from Table~\ref{tab:cutflow_noPU_1}
+      is the role of the fake component of the QCD background.
+      %
+      We see that, even after $b$-tagging, the reducible $2b2j$ background
+      is comparable or even larger, than the irreducible
+      $4b$ component.
+      %
+      This is specially marked in the boosted category.
+      %
+      Therefore, at this level of the analysis, the signal significance
+      can be artificially increased by up to a factor 2 if only the
+      $4b$ background is considered.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[t]
@@
     \input{tables/table_noPU_3.tex}
-    \caption{\small The cross-sections, in pb,
+    \caption{\small The cross-sections, in femtobarns,
       for the signal and the various background
-      processes at different points of the
+      processes at different steps of the
       cut-flow, for the resolved (upper table),
@@
       the total background or only the $4b$ component.
+      %
+      The different levels of the cut-flow are summarized
+      in Table~\ref{tab:cutflowdetails}.
  \label{tab:cutflow_noPU_1}}
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %
-Let us begin with the discussion of the boosted category, the one that
-leads to a higher signal significance.
+In the boosted category, we see that after all the cuts, including $b$-tagging,
+we end up with more than 1000 signal events at the HL-LHC, however swamped in a total
+background of almost 1M QCD events.
 %
-We see that after all the cuts, including $b$-tagging,
-we end up with almost 200 signal events at the HL-LHC, with
-still a substantial background of around $40k$ events.
-%
-The signal significance is around 1.0 at the end of the
+This leads to a signal significance of around 1.0 at the end of the
 cut-based analysis.
@@
 the MVA.
+%
+We also note that $S/B$ is at the per-mille level, requiring a extremely accurate
+measurement of the QCD background.
 
@@
 we have only
-19 signal events, and the signal significance drops down to
+120 signal events, and the signal significance drops down to
 $S/\sqrt{B}\sim 0.3$.
@@
 Both the intermediate and resolved categories benefit from higher signal yields,
-specially in the resolved category, but this enhancement is washed out by the stronger
+specially in the resolved category, but this enhancement is compensated by the stronger
 increase in the QCD multi-jet background.
 %
-In both cases the signal significance is around half of that in the boosted category,
-with in addition $S/B$ being an order of magnitude smaller.
+In both cases the signal significance is similar to that of the boosted category,
+with the additional drawback in the resolved case that the signal over background ratio
+is one order to magnitude smaller.
 %
-Therefore, the boosted category is clearly determined to be the most useful category,
-specially due to the significant suppression of the QCD multi-jet background.
-%
-And we still have not exploited all the rich information contained on the jet
-substructure, as we will do in the next section.
-
-We observe
-that after the cut-based analysis, the significance of the Higgs pair production
-observation in the $b\bar{b}b\bar{b}$ channel using the boosted topology
-is $S/\sqrt{B}=0.99$,
-and that the combination
-of the boosted, intermediate and resolved categories gives a slightly higher
-value, around 1.20.
-%
+Overall, we observe that 
+that after the cut-based analysis,
+the combination
+of the boosted, intermediate and resolved categories yields
+to total significance for the observation of the Higgs pair production
+observation in the $b\bar{b}b\bar{b}$ final
+state of around $S/\sqrt{B}=1.70$.
 

### 2015-11-30 paper/sec-intro.tex
More work on draft
more work on paper

@@
 $b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
-$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta}.
+$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
 %
@@
 %
-The robustness of our results as function of our assumptions
-on the $b$-tag rate, mistag probability and momentum
-resolution in quantified in Ref.~\ref{sec:optimisation}.
+The robustness of our results under realistic pile-up
+conditions expected at the HL-LHC is illustrated in
+ Sect.~\ref{sec:pileup}.
 %

### 2015-11-30 paper/sec-mva.tex
more work on paper

@@
-\section{Results from the multivariate analysis}
+\section{Multivariate analysis}
 \label{sec:mva}
@@
 combining the significance of the three categories,
-we end up with a signal significance of $S/\sqrt{B}\simeq 1.2(2.3)$
+we obtain a signal significance of $S/\sqrt{B}\simeq 1.7 (3.5)$
 with all backgrounds (only QCD $4b$) taken into account.
 %
-This does not seem
+This is clearly
 to be enough to be able to claim observation
@@
 in this channel, and even less to extract the trilinear Higgs  coupling
-$\lambda$ with good precision.
+$\lambda$, in particular
+taking into account the that $S/B$ is at the permille level.
 %
-In this section we show how the signal significance for
-our process can
-be substantially improved when
-applying a multivariate analysis (MVA) to the events
- that survive the cut-based
- analysis.
+In this section we now show how this signal significance for
+ can
+be significance improved when
+applying a multivariate analysis (MVA) subsequently
+to the cut-based analysis.
 
 %
-Multivariate techniques are by now a common tool to enhance signal
-significance in HEP analysis, and this is fully justified
-since they open a new window to improve the performance
+Multivariate techniques are by now a mature tool to enhance signal
+significance in HEP analysis, allowing
+to open a new window to improve the performance
 of many physics analysis and searches.
@@
 In particular, the classification of events as arising from either signal or
-background processes via the use of a multivariate analysis is becoming
-a mature
-technique in LHC
+background processes via the use of a multivariate analysis is a
+commonly applied strategy in LHC
 applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
@@
 Since we find that jet substructure variables are a crucial input
-to the MVA, we end this section showing various kinematic distributions
+to the MVA, we finally show various kinematic distributions
 of these variables.
@@
 %
-In our work we use a specific type of  MVA to
-disentangle signal and background events in the $hh\to 4b$ process,
+The specific type of  MVA that we use here, to
+disentangle signal and background events in the $hh\to 4b$ process, will be
 a multi-layer feed-forward artificial neural network (ANN),
@@
 %
-This family of ANNs is sometimes known as {\it deep} neural networks.
+This family of ANNs is sometimes known as {\it deep} neural networks, since they have
+a richer architecture with hidden layers.
 %
@@
 The main result of the trained ANN is identifying, in a fully automated way,
-which are the most relevant variables to discriminate between the two.
+which are the most relevant variables to discriminate between the two classes
+of events.
 
@@
 \ee
-where $N_{\mathrm{var}}$ represents the number of input variables for the MVA.
+where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
+which is specific of the analysis category: resolved, intermediate, or boosted.
+%
 All neural-network layers use a sigmoid activation function, allowing
@@
 In Fig.~\ref{fig:nnarch} we show an example of the ANN that we use in this work, corresponding here
-to the case of the resolved category.
+to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).
 
@@
  %
- Since given the large number of events the probability of
- over-fitting is tiny, we just train the MVA for a very long
- number of generations, in this case $N_{\rm gen}=50k$.
+ The GA training is performed for a very large 
+ number of generations, in this case $N_{\rm gen}=50k$, to avoid
+ under-training.
  %
@@
  We have also verified that using a cross-validation stopping
- criterion (in particular, the same one as
- that used in the NNPDF3.0 fit~\cite{Ball:2014uwa})
+ criterion, in particular, the same one as
+ that used in the NNPDF3.0 analysis~\cite{Ball:2014uwa}
  does not modify the results.
+ %
+ This cross-validation entails dividing the input MC dataset into two disjoint sets,
+ and use one for the training and the other for the validation: the optimal
+ stopping point is then indicated by the minimum of the error function
+ Eq.~(\ref{cross-entropy}) for the validation sub-sample.
 
@@
 
- To identify the most discriminatory variables, we have to train
+ To identify the variables with higher discriminatory power,
+ we need to train
  the MVA using a large number of kinematic distributions for
@@
 the input variables for the MVA differ between our three categories,
-and in particular in the case of large-$R$ jets we want to exploit
+and in particular in the case of large-$R$ jets (for the boosted
+and intermediate categories) we want to exploit
 the richness of substructure information.
@@
 \item The invariant mass of the reconstructed Higgs pair, $m_{hh}$.
-\item The separation in $R$ between the two Higgs candidates, $\Delta R_{hh}$.
+\item The separation in the $\phi$--$\eta$ plane
+  between the two Higgs candidates, $\Delta R_{hh}$.
+  \item The separation in $\eta$  between the two Higgs candidates, $\Delta \eta_{hh}$.
 \item The separation in $\phi$  between the two Higgs candidates, $\Delta \phi_{hh}$.
-\item The separation in $\eta$  between the two Higgs candidates, $\Delta \eta_{hh}$.
 \end{itemize}
@@
 %
+This is one of the main advantages of ANNs in this context: they are inherently redundant, so
+adding additional information, even if carries very little weight, will never degrade
+the classification power of the MVA.
 
@@
 \includegraphics[width=0.48\textwidth]{plots/Resolved_disc_noPU.pdf}
-\caption{\small The distribution as a function of the ANN output
+\caption{\small The distributions, at the end of the
+  GA training, 
   for the signal and background MC events in the three categories:
   boosted (upper plot), intermediate (lower left plot) and
-  resolved (lower right plot).
+  resolved (lower right plot), as a function of the ANN output.
   %
-  All distributions are normalized so that their integral
-  adds up to one.
+  All distributions are normalized so that their integrals
+  add up to one.
 }
@@
 
+These results are summarized in Table~\ref{table:cutflowMVA}, where we indicate
+the value of the optimal ANN output
+cut in each category,
+the number of signal and background events $N_{\rm ev}$ expected
+at the HL-LHC,
+and also $S/\sqrt{B}$ and $S/B$.
+%
+For reference, we also include the results at the end of
+the cut-based
+analysis.
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \small
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Boosted category}\\
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.82$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+      1070   &  $7.6\cdot 10^5$    &  1.2    &  $1.4\cdot 10^{-3}$  & 790 & $2.2\cdot 10^4$ & 5.4  & 0.034\\
+      \hline
+      \multicolumn{8}{c}{$\quad$}\\
+    \hline
+    \multicolumn{8}{c}{Intermediate category}\\
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.80$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+      670   &   $5.3\cdot 10^5$   &   0.9   &  $1.2\cdot 10^{-3}$ & 360  & $5.5\cdot 10^3$ & 4.8  & $0.06$ \\
+      \hline
+      \multicolumn{8}{c}{$\quad$}\\
+    \hline
+    \multicolumn{8}{c}{Resolved category}\\
+    \hline
+      \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.65$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+    $3700$   &   $1.5\cdot 10^{7}$   & 1.0     &  $3\cdot 10^{-4}$   & $1.3\cdot 10^{3}$ &
+    $8.3\cdot 10^{4}$  & 4.5 & 0.01 \\
+        \hline
+  \end{tabular}
+  \caption{\small Post-MVA results, for the optimal value of the
+    ANN discriminant, in the three categories, compared with the
+    result of the cut-based analysis.
+    %
+    We indicate the number of signal and
+    background events
+    at the HL-LHC, as well as the signal significance $S/\sqrt{B}$ and
+    the signal over background ratio $S/B$.
+    %
+    The value of the ANN output cut $y_{\rm cut}$
+    is optimised separately in the
+    three categories.
+    %
+    The $y_{\rm cut}=0$ value corresponds to row C2 in Table~\ref{tab:cutflow_noPU_1}.
+    \label{table:cutflowMVA}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The post-MVA results for $S/\sqrt{B}$ and $S/B$ as a function of the cut
@@
 the end of the cut-based analysis, see
-the {\bf C2} row of Table~\ref{tab:cutflow_noPU_1}.
+the C2 row of Table~\ref{tab:cutflow_noPU_1}.
 %
-Indeed, at the end of the cut based analysis $S/\sqrt{B}$ was
-approximately
-1.0, 0.5 and 0.5 for the boosted, intermediate and resolved
-categories, as can be seen from Fig.~\ref{fig:sb_mva}.
+Indeed, at the end of the cut based analysis, the
+signal significance $S/\sqrt{B}$ was
+1.2, 0.9 and 1.0 for the boosted, intermediate and resolved
+categories respectively, consistent with Fig.~\ref{fig:sb_mva}.
 %
-The same applies to $S/B$.
+The same applies to the signal over background ratio $S/B$.
 
@@
 
-The results of Fig.~\ref{fig:sb_mva} are interesting in that they show
-that for the resolved and boosted categories the improvement in signal
-significance arising from the MVA is rather moderate, less that a factor two
-in the two cases.
+The results of Fig.~\ref{fig:sb_mva}  show that
+for all categories the  improvement in signal
+significance arising from the MVA is substantial, growing from around 1
+to around 5 in the three cases.
 %
-Even after the MVA, $S/\sqrt{B}$ never grows above 1.0.
-%
-The real power of the MVA can be seen for the boosted category,
-where the signal significance rises from around 1.0 in the cut-based
-analysis to above 3.0 for values of the ANN output cut $y_{\rm cut}\ge0.85$.
-%
-This value of the cut seems reasonable, since we know from Fig.~\ref{fig:nev2}
-that the signal yield at the HL-LHC is still quite substantial,
-of the order of 100 event.
+The optimal values of $y_{\rm cut}$ ensure that the
+number of events at the HL-LHC is still well appreciable: we obtain
+1300, 360 and 800 events in the resolved, intermediate, and
+boosted categories respectively.
 %
@@
 systematic uncertainties are not very small.
-
-Our final results are summarized in Table~\ref{table:cutflowMVA}, where we indicate
-the value of the optimal ANN output
-cut in each category,
-the number of signal and background events $N_{\rm ev}$ expected
-at the HL-LHC,
-and also $S/\sqrt{B}$ and $S/B$.
-%
-For reference, we also include the results at the end of
-the cut-based
-analysis.
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
-  \centering
-  \begin{tabular}{c|c|c|c||c|c|c|c}
-    \hline
-    \multicolumn{8}{c}{Boosted category}\\
-    \hline
-    \hline
-    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.86$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-      193   &  $3.8\,10^4$    &  0.99    &  $5.1\,10^{-3}$  & 107 & 1040 & 3.31  & 0.10\\
-        \hline
-  \end{tabular}
-   $\,$\\
-  \vspace{0.4cm}
-  \noindent
-  \begin{tabular}{c|c|c|c||c|c|c|c}
-    \hline
-    \multicolumn{8}{c}{Intermediate category}\\
-    \hline
-    \hline
-    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-      660   &   $2.2\,10^6$   &   0.45   &  $3.1\,10^{-4}$ & 480  & $3.2\,10^5$ & 0.85  & $1.5\,10^{-3}$ \\
-        \hline
-  \end{tabular}
-    $\,$\\
-  \vspace{0.4cm}
-  \noindent
-  \begin{tabular}{c|c|c|c||c|c|c|c}
-    \hline
-    \multicolumn{8}{c}{Resolved category}\\
-    \hline
-    \hline
-    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.17$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-    $1.6\,10^{3}$   &   $1.1\,10^{7}$   & 0.50     &  $1.5\,10^{-4}$   & 968 &
-    $1.2\,10^{6}$  & 0.90 & $8.2\,10^{-4}$ \\
-        \hline
-  \end{tabular}
-  \caption{\small The results for the number of signal and
-    background events
-    at the HL-LHC for both the cut-based analysis and after the
-    optimal MVA cut, as well as the $S/\sqrt{B}$ and $S/B$
-    values in the two cases.
-    %
-    From top to bottom we show the results for boosted,
-    intermediate and resolved categories.
-    %
-    The value of the ANN output cut $y_{\rm cut}$
-    is optimised separately in the
-    three categories.
-    \label{table:cutflowMVA}
-  }
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-From Table~\ref{fig:sb_mva} it is also possible to
-extract the signal significance that would be obtained
-at the end of Run II with $\mathcal{L}_{\rm int}=300$ fb$^{-1}$:
-in the boosted category we expect 11 signal events and 100 background
-events, leading to a $S\sqrt{B}=1.1$, too small specially accounting
-for realistic systematic experimental uncertainties.
+These remarkable results are however subject to an obvious criticism:
+at the HL-LHC the intense PU is know to substantially affect
+kinematical distributions, and in particular, it is expected to degrade
+in some extent the results of the present analysis.
 %
-So the full luminosity of the HL-LHC is really needed to exploit
-the information contained in this final state, unless of course
-new BSM dynamics enhance the di-Higgs production rates.
-
-The results of Table~\ref{table:cutflowMVA} include
-only the statistical uncertainty in the determination of
-the background number of events.
-%
-We  briefly comment now how these results would be affected
-if we also take into account the systematic experimental
-uncertainty in the measurement
-of the multijet backgrounds distributions.
-%
-While there is no unique definition of how signal significance is modified
-by experimental systematic uncertainties~\cite{Bityukov:2002eq}, here we estimate
-this effect with the simple correction
-\be
-\frac{S}{\sqrt{B}} \, \to \, \frac{S}{\sqrt{B}} \frac{1}{\sqrt{1+\lp \sigma^{\rm sys}\rp^2\cdot B}} \, ,
-\ee
-which corresponds to adding in quadrature to the statistical uncertainty  a single
-uncorrelated systematic uncertainty $\sigma^{\rm sys}$.
-%
-Assuming an aggressive value of $\sigma^{\rm sys}=2\%$,
-we find that the combined signal significance would be
-reduced from 3.51 to 3.03.
-%
-While this quick estimate emphasizes the critical
-importance of an experimentally accurate
-measurement of multijet backgrounds at the LHC to fully exploit the $4b$
-channel,
-it is beyond the scope of this work to estimate realistically
-the systematic uncertainties on QCD multijet distributions (and their bin-by-bin correlation)
-that will be achieved at HL-LHC.
-
-In the next section we discuss how the expectations for the HL-LHC
-summarized in  Table~\ref{fig:sb_mva} are modified in different
-conservative and aggressive scenarios for the performance of the
-ATLAS and CMS experiments, in particular how the results depend
-on the $b$-tagging performance and in the detector momentum
-resolution.
+To preempt this criticism, in the next section
+we discuss how the expectations for the HL-LHC
+summarized in  Table~\ref{fig:sb_mva} are modified in the presence
+of PU expected at the HL-LHC.
 %

### 2015-11-30 paper/sec-pileup.tex
more work on paper

@@
   \centering
+  \small
   \begin{tabular}{c|c|c|c||c|c|c|c}
@@
     \multicolumn{8}{c}{Boosted category, $\la n_{\rm PU}\ra=80$+SK}\\
-    \hline
     \hline
@@
     \hline
-  \end{tabular}
-   $\,$\\
-  \vspace{0.4cm}
-  \noindent
-  \begin{tabular}{c|c|c|c||c|c|c|c}
+       \multicolumn{8}{c}{$\quad$}\\
     \hline
     \multicolumn{8}{c}{Intermediate category,  $\la n_{\rm PU}\ra=80$+SK}\\
-    \hline
     \hline
@@
   \hline
-  \end{tabular}
-    $\,$\\
-  \vspace{0.4cm}
-  \noindent
-  \begin{tabular}{c|c|c|c||c|c|c|c}
+  \multicolumn{8}{c}{$\quad$}\\
     \hline
     \multicolumn{8}{c}{Resolved category,  $\la n_{\rm PU}\ra=80$+SK}\\
-    \hline
     \hline
@@
   \end{tabular}
-  \caption{\small The results for the number of signal and
-    background events
-    at the HL-LHC for both the cut-based analysis and after the
-    optimal MVA cut, as well as the $S/\sqrt{B}$ and $S/B$
-    values in the two cases, in the case of $\la n_{\rm PU}\ra=80$
-    and SK subtraction.
-    %
-    The corresponding results without PU were collected
-    in Fig.~\ref{table:cutflowMVA}.
+  \caption{\small Same as Table~\ref{table:cutflowMVA} in the case
+    of PU+SK, with $\la n_{\rm PU}\ra=80$.
         \label{table:cutflowMVA_PU}

### 2015-11-30 paper/sec-results.tex
more work on paper

@@
 
-\subsection{Comparison with previous work}
+\subsection{The role of light jet mistags}
 
-The feasibility of Higgs pair production at the HL-LHC in different
-final-state channels
-has been explored various groups~\cite{Baur:2003gp,Barger:2013jfa,
-  Baur:2003gpa,Barr:2013tda,Dolan:2013rja,
-  Dolan:2012rv,Papaefstathiou:2012qe,Gouzevitch:2013qca,Cooper:2013kia,Wardrope:2014kya,deLima:2014dta}, though
-the $4b$ final state has received less attention than other final states,
-due to the complexity of disentangling the signal over the large
-QCD multijet background.
+One of the main differences of the present study as compared
+to previous works is the simulation of both irreducible
+and reducible background components, which allows
+to study the impact of the modeling of light and charm jet mistags. 
 %
-Now we compare with two recent studies that have also studied the
+Now we compare our results with two recent studies that have also studied the
 feasibility of SM Higgs pair production in the $4b$ final state,
@@
 Durham group~\cite{deLima:2014dta}.
-%
-In order to perform a meaningful comparison, we will only consider
-here the $4b$ QCD and $t\bar{t}$ backgrounds, as was done
-in these two studies.
-
-First of all let us briefly summarize these two studies.
 %
@@
   %
-
-  In the section section we show how Multivariate Analysis can be used
-  to substantially improve the signal significance obtained in the
-  cut-based analysis.

### 2015-11-30 paper/paperscripts/plotMVAdat_noPU.py

@@ -10,8 +10,8 @@ print "Warning: This script might take a minute or two depending on the density 
 ################################ Settings ###################################
 
 # Source files
-datafiles=[ "../plotdata/results_noPU/MVA/nn_12X5X3X1_50000-Gen_noPU_res.dat",
-			"../plotdata/results_noPU/MVA/nn_16X5X3X1_50000-Gen_noPU_int.dat",
+datafiles=[ "../plotdata/results_noPU/MVA/nn_13X5X3X1_50000-Gen_noPU_res.dat",
+			"../plotdata/results_noPU/MVA/nn_17X5X3X1_50000-Gen_noPU_int.dat",
 			"../plotdata/results_noPU/MVA/nn_21X5X3X1_50000-Gen_noPU_bst.dat"]
 
 datanames=[ "Resolved","Intermediate","Boosted"]
@@ -148,7 +148,7 @@ for idat in xrange(0,len(datafiles)):
 			total_sigweight = total_sigweight + float(line.split()[2]) # Weight
 
 	#### ROC Curve and S/B plot
-	thresholds = numpy.linspace(0, 1, 50)
+	thresholds = numpy.linspace(0, 1, 100)
 	falsepos = []
 	truepos = []
 

### 2015-11-30 paper/sec-intro.tex
work on the intro

@@
 in the SM the dominant mechanism for the production of a pair of Higgs bosons at the LHC is 
-gluon fusion (see Ref.~\cite{baglio} and references therein), analogously to single Higgs production~\cite{Dittmaier:2012vm}.
+gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and references therein), analogously to single
+Higgs production~\cite{Dittmaier:2012vm}.
 %
@@
 Recent studies of Higgs pair production in this
-channel~\cite{Wardrope:2014kya,deLima:2014dta}
-estimate that with a luminosity of
-$\mathcal{L}_{\rm int}$=3000 fb$^{-1}$ a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
+final state~\cite{Wardrope:2014kya,deLima:2014dta}
+estimate that, for an integrated
+luminosity of
+$\mathcal{L}_{\rm int}$=3000 fb$^{-1}$,
+a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
 %
@@
 variables, Boosted Decision Trees
-and Shower Reconstruction~\cite{Soper:2011cr} respectively.
+and Shower Deconstruction~\cite{Soper:2011cr} respectively.
 %
-A limitation of these works is that
-they do not account
- for the light-jet background processes $bbjj$ and
+While irreducible backgrounds, such as $4b$ and
+$t\bar{t}$, are included, the contribution
+from reducible processes, such as $bbjj$ and
 $jjjj$, which can fake the signal when 
-some of the light jets are mistagged as $b$-jets.
+light jets are mistagged as $b$-jets, are not accounted for.
 %
-As will show, this is not a good approximation since both due to
+As will show, this approximation is not justified since, both due to
 combinatorics and to $b$-quark radiation in the shower, the
-contribution of $2b2j$ and $4j$ can become comparable
-to that of the irreducible $4b$ component.
+contribution of the $2b2j$ and $4j$ backgrounds can become comparable or even larger
+than the irreducible $4b$ component.
 
-In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
-in the $4b$ final state.
+In this work, we revisit the feasibility of SM Higgs pair production by gluon-fusion
+in the $b\bar{b}b\bar{b}$ final state.
 %
  Our strategy is based on a combination of traditional cut-based
- methods with modern multivariate analysis (MVA)
- (in particular feed-forward multi-layer neural networks),
- which lead to a substantial
+ methods with modern multivariate analysis (MVA),
+ leading to a substantial
   enhancement of the signal discrimination.
@@
   %
+  We also model the impact of the pile-up (PU) effects expected at the
+  HL-LHC by means of modern PU subtraction techniques.
+  %
   By combining the contribution from the boosted, intermediate and resolved
-  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
+  topologies we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
+  for $\mathcal{L}_{\rm int}$=3000 fb$^{-1}$.
 %
-  Therefore, our strategy allow us to improve the
-  potential of this final state even when considering a
-  more realistic background modeling.
-
-  One of the original motivations of this study was to provide guidance to the
-  LHC experiments
-concerning which aspects of the measurement should be particularly optimized
-to increase the signal significance in the $4b$ channel.
-%
-In this respect, we study the dependence on our results on the $
-b$-tagging mistag
-efficiency, the light-jet mistag rate and the 
-momentum resolution.
-%
-In each of these cases, we determine the signal significance
-$S/\sqrt{B}$ of the
-measurement in both conservative and optimistic assumptions of these
-analysis settings.
+  These results emphasize the crucial importance that the $b\bar{b}b\bar{b}$ final state
+  has for studies of Higgs pair production and for the determination of
+  $\lambda$, as well as the advantages of the use of modern statistical
+  analysis methods.
 
@@
 %
-Finally in Sect.~\ref{sec:conclusions} we conclude and outline
+Finally, in Sect.~\ref{sec:conclusions} we conclude and outline
 how our results can be extended to estimate the accuracy
-in the determination of $\lambda$ and the constraints on
-BSM scenarios in an EFT framework.
+in the determination of trilinear coupling $\lambda$ and the constraints on
+BSM scenarios.

### 2015-11-30 paper/sec-pileup.tex
work on the intro

@@
 
-\subsection{MVA revisited with PU effects}
+\subsection{MVA revisited in the presence of PU}
 
-After having discussed in some detail which are the effects
-of PU in the various kinematic distributions that are used
+After this discussion of the effects 
+of PU in the various kinematic distributions
+that are used
 as input to the MVA, we now revisit the analysis
-of Sect.~\ref{sec:mva} now with PU included.
-
-First of all we compare the distribution of the ANN output for the
-signal and background MC events in the boosted and resolved categories,
+of Sect.~\ref{sec:mva} this time with PU included.
+%
+First of all we compare in Fig.~\ref{fig:nnresponse_PU}
+the distribution of the ANN output for the
+signal and background MC events in the boosted and resolved categories --
 the analogous comparison in the case without PU was shown
@@
 %
-As we can see in Fig.~\ref{fig:nnresponse_PU}, there is a clear discrimination
-between signal and background in the two categories, also
-in the case of PU included.
+We observe that the clear MVA discrimination
+between signal and background events in the two categories is robust
+when PU is included.
 %
-However, by comparing with Fig.~\ref{fig:nnresponse} we see
+However, by comparing with Fig.~\ref{fig:nnresponse}, we see
 that some of the most distinguishing features that separate signal
@@
 
-Next we consider the number of signal and background events that
-are expected at the HL-LHC as a function of the ANN discriminant -
-the corresponding results without PU are those of
-Fig.~\ref{fig:nev2}.
-%
-As we can see from Fig.~\ref{fig:nev2_PU}, the trends are
-similar as in the no PU case, for instance, in the boosted
-category we are left with around 200 events for the optimal value
-of the ANN cut.
-%
-Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we also observe
-that the intermediate category is substantially degraded once PU
-is included, since a reduced number of events fall into this
-category now.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.65\textwidth]{plots/nev2_SKPU80.pdf}
-\caption{\small Same as Fig.~\ref{fig:nev2} now
-  with  $\la n_{\rm PU}\ra=80$ PU events 
-  and SK subtraction.
-}
-\label{fig:nev2_PU}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Now we can finally revisit the post-MVA signal significance,
-$S/sqrt{B}$, and he signal over background ratio, $S/B$,
-in the case of PU, and compare with the corresponding
-no PU results shown in Fig.~\ref{fig:sb_mva}.
-%
-
-In Fig.~\ref{fig:sb_mva_PU} we show the signal significance,
-$S/\sqrt{B}$, as well as the signal over background ratio,
-$S/B$, as a function of the NN discriminant, in the case
-of the analysis including the effects of PU
-with $\la n_{\rm PU}\ra=150$.
-%
-The corresponding results in the case without PU were shown in
-Fig.~\ref{fig:sb_mva}.
-%
-As can be seen, the MVA-driven enhancement is robust event in the
-presence of PU, and a total signal significance of
-almost $S/\sqrt{B}\simeq 3$ is also obtained in this case.
-%
-Therefore, we conclude that the qualitative results obtained
-in the previous section are robust even in the presence
-of realistic PU effects.
-%
-Note that no specific effort has been performed to
-optimize PU subtraction (for example by tuning the value
-of the patch length $a$ in {\tt SoftKiller}), so there is
-certainly still room for improvement.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.48\textwidth]{plots/ssb_SKPU80.pdf}
-\includegraphics[width=0.48\textwidth]{plots/sb_SKPU80.pdf}
-\caption{\small Same as Fig.~\ref{fig:sb_mva}
-  now
-  with  $\la n_{\rm PU}\ra=80$ PU events 
-  and SK subtraction.
-}
-\label{fig:sb_mva_PU}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-To conclude, it is illustrative to quantify which of the input variables
-to the MVA are most significant in the case of PU,
-and compare it with the corresponding
-results without PU.
-%
-We use the same estimator as in Sect.~\ref{sec:signalsignificance},
-namely the sum
-of the absolute value of all the weights connected to a given
-input neuron $i$, Eq.~(\ref{eq:totweight}).
-%
-The results for the resolved and boosted categories are shown
-on Fig.~\ref{fig:nnweights_PU}.
-%
-As we can see by comparing to the corresponding
-results without PU in Fig.~\ref{fig:nnweights}, we see that
-in the boosted category, the discrimination power of the invariant
-mass of Higgs candidates is decreased and that of the various substructure
-variables, in particular $C_2$ and $D^{{\rm rm}}$, is conversely
-increased.
-%
-This reflects the fact that these substructure variables are
-relatively robust against PU contamination.
-
-In the case of the resolved category, in the case without PU the highest
-values of the weight sum were found for the $p_T$ of the leading
-Higgs and for the Higgs invariant masses.
-%
-This is also true in the case with PU, but now the rapidity difference
-between the two Higgs candidates, $\Delta y_{hh}$ increases its
-importance, again reflecting that this variable is relatively
-insensitive to PU effects.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/res_wgthist_SKPU80.pdf}
-\includegraphics[width=0.49\textwidth]{plots/bst_wgthist_SKPU80.pdf}
-\vspace{-0.5cm}
-\caption{\small
-Same as Fig.~\ref{fig:nnweights} in the case of PU.
-}
-\label{fig:nnweights_PU}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Combined results}
-
-Finally, we now combine the three categories, resolved,
-intermediate and boosted, and determine the signal
-significance taking into account all event topologies.
-%
-First of all, in Table~\ref{table:cutflowMVA_PU}
+In Table~\ref{table:cutflowMVA_PU}
 we provide the  the number of signal and
@@
     %
-    The value of the optimal MVA cut $y_{\rm cut}$ is determined
-    as the one leading to highest signal significance, with
-    the constraint that number of MC events left is still large
-    enough to tame statistical fluctuations.
+    From Table~\ref{table:cutflowMVA_PU} we see that, thanks
+to the MVA, we can improve the signal significance and the
+signal over background ratio from 0.31 and $3\cdot 10^{-4}$
+(0.40 and $1.3\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
+in the boosted (resolved) category.
+%
+The intermediate category exhibits a lower value of $S/\sqrt{B}$
+for the optimal $y_{\rm cut}$ value, around unity.
+%
+We thus conclude that the boosted category is the most promising
+one for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
+at the HL-LHC, with however useful information also provided
+by the resolved category.
 
@@
 
-From Table~\ref{table:cutflowMVA_PU} we see that, thanks
-to the MVA, we can improve the signal significance and the
-signal over background ratio from 0.31 and $3\cdot 10^{-4}$
-(0.40 and $1.3\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
-in the boosted (resolved) category.
+Next we show the results
+as a function of the optimal ANN cut $y_{\rm cut}$.
 %
-The intermediate category exhibits a lower value of $S/\sqrt{B}$
-for the optimal $y_{\rm cut}$ value, around unity.
+In Fig.~\ref{fig:nev2_PU}
+we show the number of signal and background events that
+are expected at the HL-LHC as a function of the ANN discriminant -
+the corresponding results without PU are those of
+Fig.~\ref{fig:nev2}.
 %
-We thus conclude that the boosted category is the most promising
-one for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
-at the HL-LHC, with however useful information also provided
-by the resolved category.
+As we can see from Fig.~\ref{fig:nev2_PU}, the trends are
+similar as those in the case without PU.
+%
+Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we also observe
+that the intermediate category is substantially degraded once PU effects
+are accounted for, the reason being a reduction in the number of signal
+events that are now assigned to this category.
+%
+This shows that the definition of the intermediate category is seriously
+affected by PU, as opposed to the resolved and boosted selections.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{plots/nev2_SKPU80.pdf}
+\caption{\small Same as Fig.~\ref{fig:nev2} now
+  with  $\la n_{\rm PU}\ra=80$ PU events 
+  and SK subtraction.
+}
+\label{fig:nev2_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Fig.~\ref{fig:sb_mva_PU} we show the signal significance,
+$S/\sqrt{B}$, as well as the signal over background ratio,
+$S/B$, as a function of the ANN discriminant $y_{\rm cut}$, in the case
+of the analysis including the effects of PU
+with $\la n_{\rm PU}\ra=80$.
+%
+The corresponding results in the case without PU were shown in
+Fig.~\ref{fig:sb_mva}.
+%
+As can be seen, the MVA-driven enhancement is robust in the
+presence of PU.
+%
+While unsurprisingly there us a degradation as compared to the case wo PU,
+we still manage to achieve a signal significance of
+around $S/\sqrt{B}\simeq 2.5$ separately for the boosted and resolved
+categories.
+%
+On the other hand, the intermediate category becomes irrelevant.
+%
+We conclude that the qualitative conclusions drawn in
+Sect.~\ref{sec:mva} are robust in the presence
+of realistic PU effects.
+%
+Note that no specific effort has been performed to
+optimize PU subtraction, for example by tuning the value
+of the patch length $a$ in {\tt SoftKiller}, so there is
+still room for improvement in this respect.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/ssb_SKPU80.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb_SKPU80.pdf}
+\caption{\small Same as Fig.~\ref{fig:sb_mva}
+  now
+  with  $\la n_{\rm PU}\ra=80$ PU events 
+  and SK subtraction.
+}
+\label{fig:sb_mva_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+It is illustrative to quantify which of the input variables
+to the MVA are most significant in the case of PU,
+and compare it with the corresponding
+results without PU.
+%
+We use the same estimator as in Sect.~\ref{sec:signalsignificance},
+namely the sum
+of the absolute value of all the weights connected to a given
+input neuron $i$, Eq.~(\ref{eq:totweight}).
+%
+The results for the resolved and boosted categories are shown
+on Fig.~\ref{fig:nnweights_PU}.
+%
+As we can see by comparing to the corresponding
+results without PU in Fig.~\ref{fig:nnweights}, we see that
+in the boosted category, the discrimination power of the invariant
+mass of Higgs candidates is decreased and that of the various substructure
+variables, in particular $C_2^{\beta}$ and
+$D^{{\beta}}$, is conversely
+increased.
+%
+This reflects the fact that these substructure variables are
+relatively robust against PU contamination.
+
+In the case of the resolved category, in the case without PU the highest
+values of the weight sum were found for the $p_T$ of the leading
+Higgs and for the Higgs invariant masses.
+%
+This is also true in the case with PU, but now the rapidity difference
+between the two Higgs candidates, $\Delta y_{hh}$ increases its
+importance, again reflecting that this variable is relatively
+insensitive to PU effects.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/res_wgthist_SKPU80.pdf}
+\includegraphics[width=0.49\textwidth]{plots/bst_wgthist_SKPU80.pdf}
+\vspace{-0.5cm}
+\caption{\small
+Same as Fig.~\ref{fig:nnweights} in the case of PU.
+}
+\label{fig:nnweights_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Finally, we now combine the three categories, resolved,
+intermediate and boosted, and determine the signal
+significance taking into account all event topologies.
+%
 Adding in quadrature the signal significance from the three
-(exclusive) categories, our final combined result is
+(exclusive) categories for the corresponding
+optimal value of $y_{\rm cut}$, our final combined result is
 \be
@@
 \ee
-far above the threshold for {\it evidence}, and close to the
-requirement for {\it discovery}.
+that is, well
+above the threshold for evidence, and  relatively close to the
+requirement for discovery.
 %
-In addition, it should be emphasized that there is still
-room for improvement, in particular by means of a tailored
-study dedicated to optimize PU subtraction in this process.
 
@@
 %
+Our analysis certainly contains
+room for improvement, in particular by means of a tailored
+study dedicated to optimize PU subtraction in this process.
+%
 It will be important now to quantify the precision of
@@
 the techniques presented here, but this is left for future work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-30 paper/sec-intro.tex
more work on paper

@@
   We also model the impact of the pile-up (PU) effects expected at the
-  HL-LHC by means of modern PU subtraction techniques.
+  HL-LHC by means of modern PU subtraction techniques,
+  in particular the {\tt SoftKiller} method~\cite{Cacciari:2014gra}.
   %

### 2015-11-30 paper/sec-mcsamples.tex
more work on paper

--- 2015-07-13 paper/sec-mcsamples.tex
@@
 
-First of all in this section we discuss the settings of the
+In this section we discuss the settings of the
 Monte Carlo generation of the signal and background
-events used in this work.
+processes used in this analysis.
 %
-We also discuss how we study the effects of finite detector
-resolution by means of an smearing of the final-state
-particles four-momentum.
+We also discuss the modelling of finite detector
+resolution effects by means of an smearing of the final-state
+particles four-momenta.
 
-\subsection{Higgs pair production}
-%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Higgs pair production in gluon-fusion}
 
@@
 %
-We adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
-$\alpha_S(m_Z^2)=0.118$
-as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
-%
 We use the default settings of the renormalization and factorization
@@
 The calculation is performed in the
-$N_f$=4 scheme and thus
+$n_f$=4 scheme and thus
 takes into account the finite mass of the $b$-quarks.
+%
+For the input parton distribution functions, we 
+adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
+$\alpha_s(m_Z^2)=0.118$
+interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
 
@@
     The non-trivial interplay between the diagram with a heavy quark box
-    and that of the triangle (that can lead to constructive or destructive interference)
-    complicated the extraction of
+    and that of the triangle, that can lead to constructive or destructive interference,
+    complicates the extraction of
     the trilinear coupling
@@
     production cross-section.
+    %
+    Higher order corrections are dominated by gluon radiation
+    from either the initial state gluons or from the heavy quark loops.
 
-The resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
+    The total inclusive cross-section for this processes is
+    known up to NNLO~\cite{deFlorian:2013jea}.
+    %
+Resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
 leading to a moderate enhancement of the order of
@@
 %
-Therefore, to achieve the correct higher-order value of the  integrated cross-section,
-we rescale our signal sample using the
-NNLO inclusive calculation from Ref.~\cite{deFlorian:2013jea} accounting the threshold resummed
-NNLL effects, which corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
+Therefore, to achieve the correct higher-order value of the  integrated cross-section, we rescale our LO signal sample to match the
+NNLO+NNLO inclusive cross-section.
+%
+This corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
 in Table~\ref{tab:samples}.
@@
 %
-Parton level events are then showered with the {\tt Pythia8} Monte
-Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, in particular with {\tt v8.201}.
+Parton level signal events are then showered with the {\tt Pythia8} Monte
+Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea} version {\tt v8.201}.
 %
-We use the default settings in the parton shower, in particular
-we use the Monash 2013 tune~\cite{Skands:2014pea}, based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
+We use the default settings for the modeling
+of the underlying event (UE), multiple parton
+interactions (MPI) and pile-up, by means
+of the the Monash 2013 tune~\cite{Skands:2014pea},
+with the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
 %
-We have switched off hadronisation, since this allows a more transparent modeling of
+We switched off hadronisation, since this allows a more transparent
+modeling of our strategy for
 $b$-tagging.
 %
-A complete simulation of $b$-tagging at the hadron level is difficult to achieve without a full
-detector simulator, which is beyond the scope of this paper.
-%
-For a similar reason, we don't consider underlying event, multiple parton interactions and
-pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba}.
-%
-The same applies to the background samples, which we discuss now.
+A complete simulation of $b$-tagging at the hadron level is difficult
+to achieve without a full
+detector simulator, which is beyond the scope of this work.
 
@@
 All background samples are generated at leading-order
-with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, v2.1.1.
+with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, {\tt v2.1.1}.
 %
-As in the case of the signal generation, the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
-$\alpha_S(m_Z^2)=0.118$ is used for all samples.
+As in the case of the signal generation,
+the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
+$\alpha_s(m_Z^2)=0.118$ is used for all samples.
 %
 Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ for all
-the samples.
+the background processes.
 
-We have considered the most relevant background
-processes that can lead to an event
-being tagged as a $hh\to 4b$ candidate.
+We consider the most relevant background
+processes that contribute to the identification of
+ $hh\to 4b$ candidate events.
 %
-First of all we have QCD $4b$ multi-jet production of course, but
-we also generate QCD $2b2j$ and $4j$ multi-jet samples,
-that can lead to the event being tagged in the case of multiple light
-jets being mistagged as $b$-quarks.
+This includes  QCD $4b$ multi-jet production, as well as
+QCD $2b2j$ and $4j$ multi-jet samples.
+%
+The latter can lead to the event being identified
+as signal in the case of light or charm
+jets being mistagged as $b$-jets.
 %
@@
 %
-Neglecting the  $2b2j$ and $4j$ backgrounds is particularly
-important for the resolved and intermediate categories, but less
-so for the boosted one.
 
-In addition to the QCD multijet, we also generate $t\bar{t}$ samples
-in the fully hadronic final state, which lead to a $2b4j$ signature that can
-contribute to the fake rates, and that has a similar topology that
+In addition to the QCD multijet processes,
+we also generate $t\bar{t}$ samples
+in the fully hadronic final state, which lead to a
+$2b4j$ signature that can
+contribute due to light jet mistags.
+%
+This background processes leads a similar topology that
 the corresponding QCD sample.
 %
-We have used a value of the top quark mass of $m_t=173.2$ GeV.
+In this case,
+we have used a value of the top quark mass of $m_t=173.2$ GeV.
 %
-Semileptonic decays of top quarks can be easily removed by requiring
-a lepton veto.
+Leptonic decays of top quarks can be removed by requiring
+a lepton veto, and thus are not included here.
 
-The LO cross-section of the background samples has been rescaled so that the integrated
+The LO cross-sections for
+the background samples have been rescaled so that the integrated
 distributions reproduce known higher-order QCD results.
@@
 For the $4j$ sample, we rescale it using the {\tt BLACKHAT}~\cite{Bern:2011ep}
-results that indicates
+results, that indicate
 a NLO/LO $K$-factor of 0.6.
@@
 
-At the generation level the following basic cuts are applied to
+At the generation level, the following mild
+cuts are applied to
 background events.
@@
 Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
-in the central region with
+in the central  rapidity
+region with
 $| \eta | \le 3.0$.
 %
-In addition, at the matrix element level
+In addition, at the matrix-element level
 all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
 %
-We have checked that the generator-level cuts are loose enough as compared to the actual
-analysis cuts.
+We have checked that the generator-level cuts are loose enough to have
+no influence over the analysis cuts.
 %
 
-Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.
+The LO cross-sections,
+number of generated events and the higher-order $K$-factors
+applied to the signal and background
+samples are collected in Table~\ref{tab:samples}.
 %
-First of all we see that the $t\bar{t}$ and QCD $4b$ samples are of
-the same order of magnitude.
+We see that the $t\bar{t}$ and QCD $4b$ samples are of
+the same order of magnitude, however, the former can be efficiently
+reduced by using top quark reconstruction criteria.
 %
-The $bbjj$ cross-section is more than a factor 200 as compared to the
-$4b$ result, so in principle it should be subleading taking into
-account the mistag rate, but as we will show below,
-this is not true due both to combinatorics and to $b$-quark radiation
-during the parton shower.
+The $bbjj$ cross-section is around factor 200 as compared to the
+$4b$ result, however, as we will show,
+due both to combinatorics and to $b$-quark radiation
+during the parton shower it can be comparable or larger
+than the irreducible QCD background.
 %
@@
  %
- We also provide in each case the corresponding inclusive $K$-factor
-  that is applied in each case to correctly normalize the distribution to the known
-  higher-order results.
 
-%%%%%%%%%%%%%%%%%%%
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[h]
@@
 \end{tabular}
-\caption{\small Summary of signal and background samples generated,
+\caption{\small Details of the signal and background Monte
+  Carlo samples generated,
   together with the corresponding generator-level LO cross-sections.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 As a cross-check of the {\tt SHERPA}
-background cross-sections reported in Table~\ref{tab:samples}, we have produced leading order
+background cross-sections reported in Table~\ref{tab:samples}, we have produced leading-order
 multi-jet samples
-using the {\tt MadGraph5\_aMC@NLO} program, and compared with the results for the same processes reported in
+using {\tt MadGraph5\_aMC@NLO}, and
+benchmarked them with the results for the same processes reported in
 Ref.~\cite{Alwall:2014hca}.
@@
 %
-We find agreement, within the scale uncertainties, between the {\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
-backgrounds, so we can be confident that the set-up that we will use in this analysis is robust enough.
+We find good agreement, within the scale uncertainties, between the {\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
+backgrounds.
 
-Finally, let us discuss the smearing applied to signal
-and background samples.
+\subsection{Modelling of detector resolution}
+
+While it is beyond the scope of this work to perform a full
+detector simulation, it is still important to include an estimate of detector
+effects in the analysis, in particular for the finite resolution
+in energy and momentum, which will affect some kinematical variables, in particular
+the invariant mass of the Higgs candidates.
 %
-It is beyond the scope of this work to perform a complete study of the impact of
-detector effects in this process.
+For example, in the absence of any four-momentum smearing, the impact of the $m_h$
+distributions of the Higgs candidates in the MVA
+would be unrealistically large.
+
+In this work, we simulate the finite momentum resolution of the ATLAS and CMS
+hadronic calorimeters by applying a Gaussian smearing of the transverse
+momentum $p_T$ of all
+final-state particles, before jet clustering,
+with mean zero and standard deviation $\sigma_E$, that is
 %
-However, it is still important to include some form of rough estimate of detector
-effects in the analysis, to properly estimate for example the impact
-of the Higgs mass window cuts.
+\be
+\label{eq:smearing}
+p_T^{(i)} \, \to \, p_T^{(i)\prime}= \lp 1+ r_i\cdot\sigma_E \rp\, p_T^{(i)} \, , \quad
+i=1,\ldots,N_{\rm part} \, ,
+\ee
+with $r_i$ an univariate Gaussian random number, different for each
+of the $N_{\rm part}$ particles in the event.
 %
-In this work we simulate the finite momentum resolution of the ATLAS and CMS
-hadronic calorimeters by applying a Gaussian smearing to the four components
-of the four-momentum $p$, with mean zero and standard deviation $\Delta p$.
+We take as baseline value a momentum smearing
+factor of $\sigma_E=5\%$.
 %
-We take as baseline value a smearing of $\Delta p=5\%$, and in
-Sect.~\ref{sec:optimisation} we explore how our results change
-if a more optimistic or pessimistic value is assumed for the momentum
-resolution in the LHC detectors.
+
+To account for the finite angular resolution of the calorimeter,
+the $\eta$-$\phi$ plane is divided into regions of
+$\Delta \eta \times \Delta \phi=0.1$, and each final state particle
+which falls in each of these cells is set of have the same $\eta$
+and $\phi$ values of the center of the cell.
+%
+Finally, the particle's energy is recalculated from the smeared $p_T^\prime$,
+$\eta^\prime$ and $\phi^\prime$ values to satisfy the mass-shell
+condition.
+
+Our modelling of detector simulation has been motivated
+to lead to a mass resolution of
+reconstructed Higgs candidates of around 10 GeV, consistent
+with the hadronic mass resolutions of ATLAS and CMS.
+%
+In  Fig.~\ref{fig:higgs-mass-resolution} we show the
+invariant mass distributions of the leading
+Higgs candidate in signal events for the
+resolved category (see Sects.~\ref{sec:analysis}
+and~\ref{sec:results}), together with
+a Gaussian fit,
+used to determine the mass resolution.
+%
+We indeed  find a mass resolution of about 8\%, corresponding
+    to around 10 GeV for $m_H=125$ GeV.
+%
+    For completeness, in Fig.~\ref{fig:higgs-mass-resolution}
+    we also show the corresponding
+    mass distributions of Higgs candidates
+    in the case of $\la n_{\rm PU}\ra=80$ PU events
+    subtracted with {\tt SoftKiller} (see Sect.~\ref{sec:pileup}).
+    %
+    In the case of PU, the mass resolution is increased to around 11\%, corresponding to
+    14 GeV.
+    %
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_noPU.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_PU80.pdf}
+  \caption{\small The invariant mass distributions of the leading
+    Higgs candidates in signal events for the resolved category, without
+    PU (left plot) and with PU (right plot),
+    together with Gaussian fits  used to determine the mass resolution.
+    %
+    In the latter case, $\la n_{\rm PU}\ra=80$, with {\tt SoftKiller}
+     used for PU subtraction.
+}
+\label{fig:higgs-mass-resolution}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-11-30 paper/sec-pileup.tex
more work on paper

@@
 \label{fig:signal-vs-back-resolved}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, it is interesting to compare how the Higgs peak mass resolution is degraded
-in the case of PU.
-%
-In Fig.~\ref{fig:higgs-mass-resolution} we show the invariant mass distributions of the leading
-    Higgs candidate in signal events for the resolved category, without
-    PU (left plot) and with PU ($\la n_{\rm PU}\ra=80$+SK, right plot).
-    %
-    In both cases a Gaussian fit is used to determine the mass resolution.
-    %
-    In the case without PU, we find a mass resolution of about 8\%, corresponding
-    to around 10 GeV for the Higgs mass.
-    %
-    This mass resolution arises both from the smearing we introduce to mimic detector
-    effects as well as from ISR and FSR.
-    %
-    In the case of PU, the mass resolution is increased to around 11\%, corresponding to
-    14 GeV.
-    %
-    These values are similar to the current and prospected mass resolutions in ATLAS and CMS.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-  \begin{center}
-    \vspace{-1cm}
-  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_noPU.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_PU80.pdf}
-  \caption{\small The invariant mass distributions of the leading
-    Higgs candidate in signal events for the resolved category, without
-    PU (left plot) and with PU ($\la n_{\rm PU}\ra=80$+SK, right plot).
-    %
-    In both cases a Gaussian fit is used to determine the mass resolution.
-    %
-    See text for more details.
-}
-\label{fig:higgs-mass-resolution}
 \end{center}

### 2015-11-30 paper/sec-analysis.tex
More work in the paper
more work on paper
yet more work on the paper

--- 2015-11-10 paper/sec-analysis.tex
@@
 %
-First of all we discuss the settings and nomenclature that
+First of all, we discuss the settings and nomenclature that
 we will use for jet clustering, and then we move to discuss how $b$-tagging is simulated.
@@
 Finally, we motivate our choice of analysis cuts by comparing signal and background
-for the relevant kinematic distributions.
+for some representative kinematic distributions.
 
@@
 
-The starting point after the parton shower is the clustering
-of all final state particles using the
+At the end of the  parton shower, final state particles
+are clustered using the
 jet reconstruction algorithms
-are obtained from the {\tt FastJet} program~\cite{Cacciari:2011ma},
-v3.1.0.
+are obtained from the
+{\tt FastJet} program~\cite{Cacciari:2011ma,Cacciari:2005hq},
+{\tt v3.1.0}.
 %
-In our study use different types of jet definitions,
+In this study we will use different types of jet definitions,
 which we enumerate now:
@@
   those jets with transverse momentum $p_T \ge 40$~GeV
-  and pseudo-rapidity $|\eta|<2.5$ within the central
+  and pseudo-rapidity $|\eta|<2.5$, within the central rapidity
   acceptance of ATLAS and CMS.
@@
   In order to be accepted, these large-$R$ jets should
-  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range by
+  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range of
   $|\eta|<2.0$.
@@
   satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
-  conditions, in order
+  conditions, required
   to enhance the discrimination of the signal over the background
@@
   %
-  As required, before the mass-drop tagger is applied, the large-$R$ jet
+  Before the mass-drop tagger is applied, the large-$R$ jet
   constituents are reclustered with the Cambridge/Aachen
@@
  %
-  These small-$R$ subjets will be the input of
-  the $b$-tagging in the boosted category.
+  These small-$R$ subjets will be the building blocks of
+  $b$-tagging in the boosted category.
   %
@@
 
-Let us mention that we explored the possible improvements
+We have
+also explored the possible improvements
 in the analysis from using variable-$R$ jets~\cite{Krohn:2009zg}, but found that these made
@@
 \subsection{$b$-tagging}
+\label{sec:btagging}
 
-Given the $4b$ final state that needs to be reconstructed, the
+Given the final state that needs to be reconstructed, the
 optimisation of the $b$-tagging capabilities of the
@@
 %
-The $b$-tagging used in this feasibility study is inspired
+The $b$-tagging strategy used in this feasibility study is inspired
 in the current and projected ATLAS settings~\cite{Aad:2013gja},
@@
   a mistag rate of $f_l$, unless a charm quark is found,
-  when the mistag rate is $f_c$.
+  and in this case the mistag rate is $f_c$.
   %
@@
   small-$R$ jets that satisfy the acceptance cuts worsens the performance
-  due to combinatorics after the parton shower.
+  due to combinatorics.
 
@@
     is done in the subjet $p_T$) are both individually $b$-tagged.
-    %
+
     As in the case
@@
     Concerning the $b$-tagging probabilities and the
-    light jet mistag probabilities, there are taken
+    light jet  and charm jet mistag probabilities, there are taken
     the same as for small-$R$ jets.
@@
 
-Concerning the actual values of the $b$-tag probability $f_b$ and
+Concerning the values of the $b$-tag probability $f_b$ and
 the $b$-mistag probability of light and charm jets $f_l$ and  $f_c$, 
-we adopt as baseline the values $f_b=0.8$, $f_l=0.01$
+in this work we adopt as baseline the values $f_b=0.8$, $f_l=0.01$
 and  $f_c=0.1$.
-%
 
@@
 %
-An important difference as compared to~\cite{Gouzevitch:2013qca}
+However, an important difference compared to~\cite{Gouzevitch:2013qca}
 is that here each category is optimised separately, and then
@@
 An advantage of our approach is that the analysis strategy would be unchanged
-if the underlying production model is varied, for example in the case of
-BSM dynamics.
+if the underlying production model of Higgs pairs is modified, for example in the case of
+BSM dynamics, which can substantially increase the degree of boost of the final state.
 
@@
   by selecting the two $b$-tagged small-$R$ jets that minimize the difference
-  between the invariant mass of the large-$R$ jet, $m_{lR_1}$,
-  with the invariant mass of the sum of the two small-$R$ jets,
-  $m_{sR_1+sR_2}$, that is, ${\rm min}\lp m_{lR} -
-  m_{sR_1+sR_2}\rp$, where $lR_1$ indicates the leading large-$R$ jet
-  and $sR_1$ and $sR_2$ indicate the small-$R$ jets.
+  between the invariant mass of the large-$R$ jet,
+  with the invariant mass of the dijet obtained
+  from the sum of the two small-$R$ jets.
 
@@
   by considering all possibilities of forming two pairs of jets
-  with invariant masses $m_{sR_1+sR_2}$ and 
-$m_{sR_3+sR_4}$, respectively, and choosing the configuration that minimizes their difference $|m_{sR_1+sR_2} - m_{sR_3+sR_4}|$. 
+  and then choosing the configuration that minimizes the relative difference of
+  dijet masses.
   %
@@
   leading small-$R$ jets arises from the need to reducing the
-  combinatorics from the fakes.
+  combinatorics from  fakes.
 \end{itemize}
-Note that these three categories are not exclusive:
+These three categories are in principle not exclusive:
 a given even can be assigned to more than one category, for
@@
 orthogonal jet selection requirements.
+%
+The separate optimisation of the three categories needs to be performed in
+a inclusive analysis.
+%
+Since in general there will be a certain degree of overlap between categories,
+a priorisation needs to be introduced in a exclusive analysis.
+%
 
@@
 condition in Eq.~(\ref{higgsmasswindow}) are classified as signal events.
-
+%
 In Table~\ref{sec:categorisation} we summarize the definitions of each
@@
 %
-We emphasize again that each category is not exclusive,
-and in general there will be a substantial overlap
-between the different categories.
-%
-This overlap is a direct consequence that
-the different categories are optimised separately.
 
@@
 for each of the categories in Table~\ref{sec:categorisationTable} have
-been optimised independently.
+been optimised separately.
 %
@@
 
-{\bf Add missing plots here: pt of subjets(boosted), pt of
-  small-R jets (resolved), rapidity of the large-$R$ jets,
-rapidity of the small-$R$ jets.}
-
 In the boosted category we require the two
@@
 %
-To motivate this cut, in FigAAA
+To motivate this cut, in Fig.~\ref{fig:cutplots22}
 we show the distribution in $p_T$ of the leading
@@
 motivating our choice of subjet $p_T$ cut.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+ \includegraphics[width=0.48\textwidth]{plots/pt_leadSJ_fj1_noPU.pdf}
+ \includegraphics[width=0.48\textwidth]{plots/pt_subleadSJ_fj1_noPU.pdf}
+\caption{\small  The $p_T$ distribution of the
+  leading (left plot) and
+  subleading (right plot) AKT03 subjets within the leading
+  Higgs candidate in the boosted category.
+  %
+  We comparing
+  the shapes of the distribution in signal and background events,
+  where both
+  distributions have been normalized to their total integral.
+}
+\label{fig:cutplots22}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
-In Fig. we show the distribution in $p_T$ of the four leading
+In Fig.~\ref{fig:cutplots23}
+we show the distribution in $p_T$ of the four leading
 small-$R$ jets in signal and background events.
@@
 Therefore, we can conclude that....
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+ \includegraphics[width=0.48\textwidth]{plots/pt_smallRjets_res_noPU.pdf}
+ \includegraphics[width=0.48\textwidth]{plots/eta_smallRjets_res_noPU.pdf}
+ \caption{\small Same as Fig.~\ref{fig:cutplots23}, now for the
+   $p_T$ and rapidity distributions of the small-$R$
+   jets in the boosted category.
+}
+\label{fig:cutplots23}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
-This comparison is shown in FigAAA.
 
@@
     Higgs candidates on the resolved (left plot) and boosted (right
-    plot) categories. {\bf redo boosted case with correct axes range}
+    plot) categories. 
 }
@@
 di-Higgs production is that it significantly increases the reach
-in $m_{hh}$ as compared to other channels with smaller branching rations,
+in $m_{hh}$ as compared to other channels with smaller branching
+ration,
 such as $2b2\gamma$.

### 2015-11-30 paper/HH4b.tex
test
First complete version of the paper

--- 2015-07-13 paper/HH4b.tex
@@
 
-\title{Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with
+\title{Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with
   Multivariate Techniques}
 
-\author{Katharina Behr, Nurfiki Bin Norjoharuddeen, Daniela Bortoletto, James Frost, Nathan P. Hartland, Cigdem Issever and Juan Rojo}
+\author{Katharina Behr, Daniela Bortoletto, James Frost,
+  Nathan P. Hartland, Cigdem Issever and Juan Rojo}
 
@@
   %
+  We demonstrate the robustness of our analysis under realistic
+  pile-up conditions expected at the HL-LHC.
+  %
    By combining the contribution from the boosted, intermediate and resolved
-  topologies we achieve a signal significance of $S/\sqrt{B}\simeq 3.2$.
+  topologies we obtain a signal significance of $S/\sqrt{B}\simeq 4$.
   %
-  We therefore demonstrate that at the HL-LHC the $b\bar{b}b\bar{b}$ channel alone
-  should allow to claim evidence of the observation of double Higgs production.
+  Our analysis indicates
+  that the $b\bar{b}b\bar{b}$ channel 
+  should be enough claim evidence for
+  the observation of double Higgs production
+  at the HL-LHC.
 }

### 2015-11-30 paper/sec-pileup.tex
First complete version of the paper

@@
+\clearpage
 \section{Impact of pile-up}
@@
 
-The discussion so far has not accounted for the effects of
-pile-up (PU), which are known to be very important at the HL-LHC.
+The main limitation of the analysis of the previous section was that
+pile-up (PU) effects were
+not accounted for.
+%
+However, any realistic feasibility study at the HL-LHC, specially
+like the present one that relies on the detailed modeling
+of kinematic distributions, needs to assess the robustness of the conclusions
+with respect to PU.
 %
 In this section, we show how our qualitative results, in particular
-the enhanced discrimination provided by the MVA, are robust
+the enhanced signal significance provided by the MVA, are robust
 in the presence of realistic PU conditions.
-
+%
 First of all we describe the simulation of realistic
@@
 show that our qualitative conclusions are robust
-in the presence of realistic PU conditions.
-%
-As we will show now, a signal significance for
-Higgs production in the $4b$ final state
-of up to $S/\sqrt{B}\simeq 4$
-can be achieved at the HL-LHC even accounting for PU.
+in the presence of realistic PU conditions, finding
+a combined
+signal significance of $S/\sqrt{B}\simeq 4$.
 
@@
 To study the impact of PU in our analysis,
-a large number
-of Minimum Bias (MB) events,
-including Multiple Parton Interactions (MPI),
-have been added to the signal
+Minimum Bias (MB) events,
+including Multiple Parton Interactions (MPI), have been generated
+with {\tt Pythia8}, and
+superimposed to the signal
 and background samples described in Sect.~\ref{mcgeneration}.
@@
 at the HL-LHC, one with a mean number of
-PU vertices of $\la n_{\rm PU}\ra=80$, and another
+PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another
 with $\la n_{\rm PU}\ra=150$.
 %
-MB events have been generated with {\tt Pythia8} using
-the Monash 2013 tune.
-%
-We have generated a total of 100M minimum-bias events, which are
-then randomly superimposed to the hard-scattering events.
-
-In order to subtract the PU, a large number of techniques
-have been proposed recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
+In order to subtract the PU, a number of techniques
+have been developed
+recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
 %
@@
 %
-Let us note however that
-a systematic optimization of the PU subtraction strategy is beyond
-the scope of this work, and in particular that further
-improvements over the results presented below is feasible
-with further tuning of the PU subtraction.
 
@@
 %
-From its definition, we observe that the value of $p_T^{(\rm cut)}$
+From its definition in terms of the median,
+we observe that the value of $p_T^{(\rm cut)}$
 will be dynamically raised until half of the patches have $\rho=0$.
-
+%
 The size and number of these patches is a free parameter of the algorithm -
@@
 $\eta \in \lc -2.5, 2.5\rc$, for the estimation of the
-$p_T$ flow density $\rho$, which is the region relevant
-for the present analysis.
+$p_T$ flow density $\rho$.
 %
-In this work, the {\tt SoftKiller} method is applied
+In this analysis, {\tt SoftKiller} method is applied
 to particles at the end of the parton shower, before
@@
 
-\subsection{Validation of the PU subtraction}
-
-Now we turn to validate our PU subtraction strategy.
 %
-To this end, we compare different kinematical distributions
+We now compare different kinematical distributions
 in the three relevant cases:
@@
 In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
-of the leading and subleading Higgs candidates. in the boosted
+of the leading and subleading Higgs candidates, corresponding to both
+the boosted
 and resolved categories.
@@
 %
-In the case of the $p_T$, the differences between the resolved
-and boosted selection cuts can be clearly observed.
+In the case of the $p_T$ distribution, the differences between the selection
+criteria for the resolved
+and boosted categories is reflected in the rightward shift of the latter.
 %
@@
 of BSM dynamics.
+%
+These results validate the PU subtraction strategy adopted in this work.
 
@@
 
-Then we assess the impact of PU in some of the substructure variables
+Next, we assess the impact of PU in representative
+substructure variables
 used as input to the MVA in the boosted category.
@@
 $\tau_{21}$, and the ratio
-of energy correlation functions $D_2^{(\beta)}$,
+of energy correlation functions, $D_2^{(\beta)}$,
 corresponding to the the leading Higgs candidate.
@@
 %
-Therefore, we don't expect a substantial loss of discrimination
+Therefore, we do not expect a substantial loss of discrimination
 power due to PU effects in our analysis.
+%
+Note in particular that $D_2^{(\beta)}$ was constructed to be resilient
+with respect to PU contamination.
 
@@
   \begin{center}
-    \vspace{-1cm}
   \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp.pdf}
@@
 
-Up to know we have restricted ourselves to the study of the impact of PU
-on signal distributions.
 %
-We now assess how the signal over background discrimination can be affected
-in the presence of realistic PU conditions.
+We now assess how the signal over background discrimination is affected
+in the presence of PU.
 %
@@
   \begin{center}
-    \vspace{-1cm}
   \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
@@
      Differences between signal and background distributions are maintained after PU
-     has been accounted for - we have checked that this is the case
+     has been accounted for.
+   %
+     we have indeed that this is the case
      in general.
+     %
+     Therefore, we expect that the broad features of the signal/background
+     discrimination provided by the MVA in Sect.~\ref{sec:mva} will
+     be maintained also in the presence of PU.
 
@@
   \begin{center}
-    \vspace{-1cm}
    \includegraphics[width=0.49\textwidth]{plots/m_h0_res_comp_back.pdf}
@@
 
-\subsection{Cut-flow}
+\subsection{MVA revisited in the presence of PU}
 
-The corresponding cut-flow tables in the case
+The corresponding version of Table~\ref{tab:cutflow_noPU_1}, the 
+cut-flow for the cross-sections and signal significance at the various
+steps of the cut-based analysis, 
+in the case
 of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
-are shown in Table~\ref{tab:cutflow_SKPU80_1},
-for the total cross-sections, number of events expected and
-signal significance at the HL-LHC, respectively.
+is provided in Table~\ref{tab:cutflow_SKPU80_1}.
+%
+We observe that, at the end of the cut-based analysis,
+the signal significance have been  degraded
+as compared to the case without PU.
+%
+We obtain that $S\sqrt{B}$ is now 0.4, 0.3 and 0.9 in the resolved,
+intermediate and boosted categories, respectively.
+%
+The boosted category is the least affected one, since as shown
+before PU contamination is milder given the selection requirements.
 
@@
 
-\subsection{MVA revisited in the presence of PU}
-
-After this discussion of the effects 
-of PU in the various kinematic distributions
-that are used
-as input to the MVA, we now revisit the analysis
-of Sect.~\ref{sec:mva} this time with PU included.
+The MC events that satisfy the selection requirements of the cut-based
+analysis, row C2 in Table~\ref{tab:cutflow_SKPU80_1}, are then
+used as input for the MVA, 
+using the same strategy explained 
+in Sect.~\ref{sec:mva}.
 %
-First of all we compare in Fig.~\ref{fig:nnresponse_PU}
+In Fig.~\ref{fig:nnresponse_PU} we represent
 the distribution of the ANN output for the
@@
 %
-Note that no specific effort has been performed to
+Since no specific effort has been performed to
 optimize PU subtraction, for example by tuning the value
-of the patch length $a$ in {\tt SoftKiller}, so there is
+of the patch length $a$ in {\tt SoftKiller}, we expect that
+there is
 still room for improvement in this respect.
@@
 mass of Higgs candidates is decreased and that of the various substructure
-variables, in particular $C_2^{\beta}$ and
-$D^{{\beta}}$, is conversely
+variables, in particular $C_2^{(\beta)}$ and
+$D^{(\beta)}$, is conversely
 increased.

### 2015-12-04 paper/sec-results.tex
More work on the results section

@@
 In this section we present the results of the 
-cut-based analysis.
-%
-We present a detailed cut-flow for the various steps
-of the analysis.
-%
+cut-based analysis, including the corresponding
+cut-flow.
 We
-compare our results with other recent related studies, in particular
+compare our results with other recent studies,
+and in particular
 we study how the signal significance
-is modified if only the $4b$ component of the
+is affected if only the $4b$ component of the
 QCD multi-jet background is taken into account,
-but the $2b2j$ and $4j$ components are neglected.
+while the $2b2j$ and $4j$ components are neglected.
 %
@@
 the signal significance, $S/\sqrt{B}$, and the signal
-over background ratio, $S/B$, corresponding to the case of the
+over background ratio, $S/B$, corresponding to the
  HL-LHC with
-an integrated luminosity of $\mathcal{L}_{\rm int}
+an integrated luminosity of $\mathcal{L}
 =3000$ fb$^{-1}$.
 %
-We emphasize that it is important not only to achieve a good signal
-significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$:
-if the latter is too small, a very accurate
-measurement of the background with an infeasible small
-systematic uncertainty would be required.
+For this type of analysis,
+it is crucial not only to achieve a good signal
+significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$.
+%
+If the latter is too small, an unrealistically precise
+measurement of the background would be required.
+%
+In Table~\ref{tab:cutflowdetails}
+we describe this cut-flow,
+separated into the (exclusive) boosted, intermediate,
+    and resolved categories.
+    %
+    From top to bottom, additional cuts are required in addition
+    to the previous ones.
+    %
+    The various cuts
+    are defined as follows:
 
@@
 \hline
- {\bf C1d} & +$N_{\rm MDT}\ge 2$ & $N_{\rm jets}^{R10}=1$ with MDT  &
- Higgs reconstruction \\
+ {\bf C1d} & +$N_{\rm MDT}\ge 2$ & +$N_{\rm jets}^{R10}=1$ with MDT  &
+ +Higgs reconstruction \\
  \hline
-{\bf C1e} & \multicolumn{3}{c|}{ $m_H$ window cut} \\
+{\bf C1e} & \multicolumn{3}{c|}{ +$m_H$ window cut} \\
 \hline
-{\bf C2} & \multicolumn{3}{c|}{$b$-tagging}    \\
+{\bf C2} & \multicolumn{3}{c|}{+$b$-tagging}    \\
 \hline
   \end{tabular}
-  \caption{\small Details of the cut-flow of the present analysis in the boosted, intermediate
-    and resolved categories.
+  \caption{\small Cut-flow of the present analysis for the boosted, intermediate
+    and resolved selections.
     %
@@
 
-To begin with,
-in Table~\ref{tab:cutflowdetails}
-we summarize the details of the cut-flow of the present analysis,
-separated into the exclusive boosted, intermediate
-    and resolved categories.
-    %
-    From top to bottom, additional cuts are required in addition
-    to the previous ones.
-    %
-    The various cuts
-    are defined as follows
     \begin{itemize}
     \item {\bf C0}: these are the generator level cross-sections, with
-      mild generation cuts in the case of the background processes, and no cuts
+      mild generation cuts in the case of the background processes, and no
+      generation cuts
       for the signal events.
       %
-    \item {\bf C1a}: at this level, we only check that we have at least
+    \item {\bf C1a}:  we only check that we have at least
       two large-$R$ jets (in the boosted case),
@@
       %
-      No acceptance requirements are imposed here.
-    \item {\bf C1b}: in addition, now the jets should
-      satisfy the corresponding $p_T$ thresholds:
-      $p_T \ge 200$ GeV for large-$R$ jets,
+      No acceptance requirements are imposed.
+    \item {\bf C1b}: require that the above jets should
+      satisfy the corresponding $p_T$ thresholds,
+      $p_T \ge 200$ GeV for large-$R$ jets and
       $p_T \ge 50$ GeV for small-$R$ jets.
-    \item {\bf C1c}: in addition, the above jets must satisfy the
+    \item {\bf C1c}: same for the
       rapidity acceptance requirement.
-    \item {\bf C1d}: at this level, the two leading large-$R$ jets must
+    \item {\bf C1d}: the two leading large-$R$ jets must
       be mass-drop tagged in the boosted category.
@@
       %
-    \item {\bf C1e}: after the two Higgs candidate jets have been reconstructed,
+    \item {\bf C1e}: after the two Higgs candidates  have been reconstructed,
       their invariant masses are required to lie a window around $m_H$,
-      in particular between 100 and 150 GeV.
-          \item {\bf C2}: This is the level of the analysis
-            after $b$-tagging has been performed, using the strategy discussed
-            in Sect.~\ref{sec:btagging}.
+      in particular between 85 and 165 GeV.
+          \item {\bf C2}: finally, the
+            $b$-tagging conditions are
+            imposed, see
+            Sect.~\ref{sec:btagging}.
       \end{itemize}
-    The signal and background events that satisfy all the analysis cut up to the
+    Signal and background events satisfying all the analysis cut up to the
     C2 level
-    are then used as input for the MVA training, as described next
+    are then used as input for the MVA training, to be described next
     in Sect.~\ref{sec:mva}.
@@
      %
-      A first important observation from Table~\ref{tab:cutflow_noPU_1}
-      is the role of the fake component of the QCD background.
+      This separation emphasizes
+      the  importance of the reducible component of the QCD background.
       %
-      We see that, even after $b$-tagging, the reducible $2b2j$ background
-      is comparable or even larger, than the irreducible
+      Even after $b$-tagging, the reducible $2b2j$ background
+      is comparable, or even larger, than the irreducible
       $4b$ component.
       %
-      This is specially marked in the boosted category.
       %
-      Therefore, at this level of the analysis, the signal significance
-      can be artificially increased by up to a factor 2 if only the
-      $4b$ background is considered.
+      So at the end of the cut-based analysis, signal significance
+      are overestimated by up to a factor 2 if the light
+      and charm jet background is neglected.
 
@@
 %
-In the boosted category, we see that after all the cuts, including $b$-tagging,
-we end up with more than 1000 signal events at the HL-LHC, however swamped in a total
-background of almost 1M QCD events.
+In the boosted category, after all cuts,
+one ends
+up with more than 1K signal events expected
+at the HL-LHC, swamped  however in a almost 1M background events,
+leading to $S/\sqrt{B}=1.2$ and $S/B=0.0014$.
 %
-This leads to a signal significance of around 1.0 at the end of the
-cut-based analysis.
+It should have been possible to somewhat increase this significance
+but using more aggressive cuts,
+but this is not needed due to the subsequent
+optimisation  performed with the MVA.
 %
-While it should have been possible to increase this significance
-but using more aggressive cuts, we have refrained doing so
-since we prefer this optimisation to be performed at the level of
-the MVA.
-%
-We also note that $S/B$ is at the per-mille level, requiring a extremely accurate
-measurement of the QCD background.
-
-From the results of Table~\ref{tab:cutflow_noPU_1}
-it is possible to compute the corresponding numbers
-for the end of Run II at the LHC with
-$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: in the boosted category,
-we have only
-120 signal events, and the signal significance drops down to
+From  Table~\ref{tab:cutflow_noPU_1}
+it is also possible to compute the corresponding pre-MVA
+expectations for the LHC Run II with
+$\mathcal{L}=300$ fb$^{-1}$: one expects
+120 signal events, with signal significance dropping down to
 $S/\sqrt{B}\sim 0.3$.
 %
-We will discuss in the next section what are the Run II prospects
-once we include the effects of the MVA in the analysis, but
-it is clear already at this level that one really needs the full
-integrated luminosity of the HL-LHC to be able to observe
-the Higgs pair production process, unless  of course production rates are
-increased by new BSM dynamics
 
 Both the intermediate and resolved categories benefit from higher signal yields,
-specially in the resolved category, but this enhancement is compensated by the stronger
+specially in the resolved category, but this enhancement is compensated by the
+corresponding
 increase in the QCD multi-jet background.
 %
-In both cases the signal significance is similar to that of the boosted category,
-with the additional drawback in the resolved case that the signal over background ratio
+In both categories
+the signal significance is similar to that of the boosted category,
+$S\sqrt{B}=0.97(0.92)$ in the resolved
+(intermediate) categories,
+with the drawback, in the resolved case,
+that $S/B$
 is one order to magnitude smaller.
 %
-Overall, we observe that 
-that after the cut-based analysis,
-the combination
-of the boosted, intermediate and resolved categories yields
-to total significance for the observation of the Higgs pair production
-observation in the $b\bar{b}b\bar{b}$ final
-state of around $S/\sqrt{B}=1.70$.
+Combining the pre-MVA results
+from the
+of the boosted, intermediate and resolved categories,
+we obtain a significance for the observation of the Higgs pair production
+in the $b\bar{b}b\bar{b}$ final
+state at the HL-LHC of  $S/\sqrt{B}=1.8$.
 
-\subsection{The role of light jet mistags}
+\subsection{The role of light  and charm jet mistags}
 
 One of the main differences of the present study as compared
-to previous works is the simulation of both irreducible
+to previous works is the inclusion of both irreducible
 and reducible background components, which allows
@@
 %
-Now we compare our results with two recent studies that have also studied the
-feasibility of SM Higgs pair production in the $4b$ final state,
-those of the UCL group~\cite{Wardrope:2014kya} and of the
+Two recent studies that have also studied the
+feasibility of SM Higgs pair production in the $b\bar{b}b\bar{b}$
+final state are from the UCL group~\cite{Wardrope:2014kya} and from
+the
 Durham group~\cite{deLima:2014dta}.
 %
-In the UCL group study~\cite{Wardrope:2014kya} is based
+The UCL study based
 on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
-in the central acceptance with $p_T \ge 40$ GeV, which are
-then used to form dijets (Higgs candidates) with
+in central acceptance with $p_T \ge 40$ GeV, which are
+then used to construct dijets (Higgs candidates) with
 $p_T \ge 150$ GeV, $85 \le m_{\rm dijet} \le 140$ GeV
-and $\Delta R \le 1.5$ between the two jets that form
-each dijet system.
+and $\Delta R \le 1.5$ between the two components
+of the dijet.
 %
-In addition to the basic selection cuts, a large number
-of additional variables are combined using a
+In addition to the basic selection cuts, the discriminating
+power of
+additional variables is included by means of a 
 Boosted Decision Tree (BDT) discriminant.
 %
-This study considers the $b\bar{b}b\bar{b}$ and
-$b\bar{b}c\bar{c}$ QCD multijets as well as
-$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$.
-%
-Their final significance is found to the $S/\sqrt{B}=2.1$ at the HL-LHC.
+The backgrounds included are the $4b$ and
+$2b2c$ QCD multijets, as well as
+$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$,
+and a signal significance of $S/\sqrt{B}=2.1$ for the HL-LHC
+is obtained.
 
@@
 two $b$-tagged subjets inside each large-$R$ jet with
-$p_T \ge$ 40 GeV.
+$p_T \ge$ 40 GeV each.
 %
-To improve the signal over background separation, both the BDRS
+To improve the separation between
+signal over background separation, both the BDRS
 method and the Shower Deconstruction (SD)~\cite{Soper:2011cr,Soper:2012pb}
-technique are applied.
+technique are used.
 %
 The background considered are QCD $4b$ as well as $Zb\bar{b}$, $hZ$ and
-$hW$, but no $t\bar{t}$, $2b2j$ or $4j$.
+$hW$.
 %
-At the HL-LHC, the best performance is obtained by requiring two
-SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\sim 2.1$,
-with BDRS similar but slightly inferior performance.
+At the HL-LHC, the best result is obtained by requiring two
+SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\sim 2.1$, with
+ slightly inferior performance with the BDRS tagger.
  %
-Therefore, both the Durham and the UCL groups conclude that a signal
-significance $S/\sqrt{B}$ slightly above two can  be obtained
-in this channel at the HL-LHC.
 
-Since we find that the $2b2j$ and $4j$ backgrounds cannot
-be neglected, and previous works did not considered them,
-it is interesting to
-study how our results are modified if we consider only the QCD $4b$
-multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
-that is, we ignore the contribution from the fakes.
 %
-As we can seen before in Table~\ref{tab:cutflow_noPU_1},
-these results indicate that given the similarity of the final states
-in signal and background events in these cases, the signal significance is
-relatively stable at various stages of the cut-flow.
+ From the results of Table~\ref{tab:cutflow_noPU_1}, we observe
+ that the signal significance in the boosted, intermediate,
+ and resolved categories is 2.7, 1.6 and 1.6 respectively,
+ when only the QCD $4b$ background is included.
  %
-As compared to the case in which all backgrounds are taken into account, we
-now get a factor two smaller backgrounds: we conclude that in the boosted category
-the effect of the fakes is non-negligible, with their contribution being
-comparable to that of the irreducible $4b$ QCD multi-jet background.
+ Combining the signal significance in the three categories,
+ we
+ obtain  a total $S/\sqrt{B_{\rm 4b}}=3.5$, which is a factor
+ 2 improvement as compared to the result found when
+ all background components are included.
+ %
+ This should be taken into account when comparing
+ the results of this work with previous analysis.
+ %
 
-Concerning the other categories, we see that that ignoring the fakes can lead to a substantial
-distortion of the results.
+ It is interesting to compare in each category the interplay
+ between the reducible and irreducible components of the
+ QCD backgrounds.
  %
-In the intermediate category, the signal significance is now much better, with $S/\sqrt{B}$ increasing from
-0.5 with all the backgrounds to $1.57$ if only $4b$ are accounted for, a factor 3 improvement.
+ In the resolved case, the $4b$ and $2b2j$ have a similar
+ magnitude, with the latter being larger by a factor of two,
+ with $4j$ being smaller by an order of magnitude.
  %
-Also the resolved category improves substantially, with signal significance increasing by a factor 2.
+ The situation is similar in the intermediate category, while
+ in the boosted category the importance of the $2b2j$ component
+ is even more marked, being a factor four larger than the
+ $4b$ one.
  %
-Therefore, we conclude that a careful modeling of the fakes is very important to truly quantify
-the feasibility of Higgs pair production in the $4b$ channel, though for the most
-important category, the boosted category, the results are relatively stable.
+ Therefore, we conclude that, while the $4j$ component can be safely
+ neglected (given the theory uncertainties associated to the
+ modelling of the QCD background), the inclusion of the
+ $2b2j$ component is essential to robustly assess the feasibility
+ of measuring Higgs pairs in this final state.
  %
-Moreover, we find that the effect of the multijet fake background is of
-the same size of the higher-order QCD corrections to $4b$ production~\cite{Binoth:2009rv}.
+ This indicates that a promising avenue to improve the prospects
+ of this measurement would be to reduce, as much as possible,
+ the light and charm jet mistag rate, in addition to achieving
+ a higher $b$-tag efficiency.
 
-In summary, we find that the results of our cut-based analysis are roughly
-consistent with the results of previous related studies.
-%
-Indeed, combining the signal significance in the three categories, we end
-up with a final $S/\sqrt{B}\simeq 2.3$.
-%
-As we show next, once the MVA is used, we achieve a substantial
-improvement
-over previous works, even after taking into account our rather more
-complete modelling of the QCD multijet background.
-
-In Table~\ref{tab:cutflow_noPU_1}   we show the results for the cross-sections for the different
-backgrounds that we consider at the end of the cut-based analysis, for each
-of the three categories.
-%
-Recall that all the backgrounds have been normalized to known higher-order results,
-as summarized in Table~\ref{tab:samples}.
-%
-As we can see from this comparison, as opposed that what naively one would expect,
-the QCD $2b2j$ background turns out not to be negligible as compared to the $4b$
-multijets in any of the categories.
-
-In the boosted case, the sum of the $2b2j$ and $4j$ components is almost as large as the
-irreducible $4b$ background, thus increasing the total background rates by a factor 2 as compared
-to the case where only $4b$ is accounted for.
-%
-This effect is more dramatic in the intermediate and resolved categories: in the former,
-$2b2j$ completely dominates the background (thus the increase in $S/\sqrt{B}$
-obtained when only the $4b$ component is kept), and in the latter
-it is comparable to $4b$.
-%
-Therefore, we conclude that an accurate estimate of the fake $b$-tag contribution is
-an essential component of this analyses, and that complete QCD multijet samples
-should be included.
-%
-On the other hand, we find that the hadronic $t\bar{t}$ component of the background
-is smaller than the QCD multijet one.
-
-In Fig.~\ref{fig:histoBack} we show the decomposition of the background for one important kinematical
-distribution, the $p_T$ of the leading reconstructed Higgs candidate, various background
-components, for both the boosted and the resolved categories.
-%
-In the same figure we also show the results of the corresponding comparison
-at the level of the $p_T^{hh}$ of the
+ In Fig.~\ref{fig:histoBack} we show a
+ comparison
+    of the shapes of the $4b$ and $2b2j$
+components of the QCD background for the $p_T$ of the leading
+Higgs candidate in the resolved
+and boosted  categories, and the same
+ for the invariant
+mass $m_{hh}$ of the
     reconstructed di-Higgs system.
     %
-The histograms correspond to the distributions at the end of the cut-based
-analysis.
+    The two components lead to a rather similar shape
+    for the two distributions, with some interesting
+    differences, for instance in the boosted
+    category the $4b$ component is harder for the
+    $p_T^h$ distribution, while the $2b2j$ leads to a longer
+    tail at small values of the $m_{hh}$ invariant
+    mass distribution.
 %
-The results are consistent with those summarized
-before in the boosted case we see how $4b$ is the most important
-component of the background, with $2b2j$ being of the same order of magnitude, while
-for the resolved category we see that $2b2j$ dominates instead.
+    We also observe that the $2b2j$ distributions
+    are affected by somewhat larger
+    MC fluctuations as compared to $4b$, despite the large size
+of the initial sample.
 %
-So the effect of the fakes is certainly important, but fortunately it is not a limiting factor
-in the resolved category, the one that leads to higher signal significance.
+This is a consequence of the
+difficulties of an accurate modelling of the effects
+of $b$-jet mistags from a QCD multi-jets process, requiring
+very large MC samples.
 
@@
 \begin{center}
- \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_back.pdf}
- \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_boost_back.pdf}
-   \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_res_back.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/pt_HH_C2_boost_back.pdf}
+ \includegraphics[width=0.49\textwidth]{plots/pt_h0_C2_res_back_noPU.pdf}
+ \includegraphics[width=0.49\textwidth]{plots/pt_h0_C2_bst_back_noPU.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_hh_C2_res_back_noPU.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_hh_C2_bst_back_noPU.pdf}
   \caption{\small
-    Upper plots: the decomposition of the QCD multijet background in its various
-    components, $4b$, $2b2j$ and $4j$, for the $p_T$ of the leading
-    Higgs candidate in the boosted (left plot) and resolved (right plot) categories.
+    Upper plots: comparison
+    of the shapes of the $4b$ and $2b2j$
+components of the QCD background for the $p_T$ of the leading
+Higgs candidate in the resolved
+(left plot) and boosted (right plot) categories.
     %
-    Lower plots: the same comparison this time for the $p_T^{hh}$ of the
+Lower plots: the same comparison this time for the invariant
+mass $m_{hh}$ of the
     reconstructed di-Higgs system.
@@
 
-  One might ask why the $2b2j$ process
-  is not subdominant as compared to $4b$: while its generator-level cross-section is
-  much larger, $\sigma_{2b2j} \simeq 240\cdot \sigma_{4b}$, one expects a suppression
-  of the order of $f_l^2 =10^{-4}$ since only with two light jets mistagged as $b$-jets the event
-  would be identified as a Higgs candidate.
+The reason why the  $2b2j$ process
+is not negligible as compared to the $4b$ component
+is the following.
 %
-  We have checked that this expectation is true only at parton level: once parton shower effects
-  are accounted for, both the radiation of $b\bar{b}$ pairs from the shower and combinatorics increase
-  the number of $b$ quarks in the final state, enhancing substantially the $2b2j$ rates as compared
-  to the naive parton level expectation.
+In the boosted category, for example,
+the cross-sections at the C1e
+level, that is, after the mass-drop tagging but before
+$b$-tagging, is a factor 300 larger in the $2b2j$
+sample as compared to the $4b$ sample.
 %
+Now, after $b$-tagging, the naive expectation would
+be a suppression of the former by a factor $f_l^2 =10^{-4}$,
+since a total of four $b$-tags are required to classify the
+event as a Higgs candidate.
+%
+So the ratio of $2b2j$ over $4b$ should be
+around $\simeq 3\%$.
+  %
+While  we have checked that this expectation is borne
+out at parton level, before showering,
+we find that  when parton shower effects
+are accounted for, due to the radiation of $b\bar{b}$ pairs from the
+light jets as well as due to combinatorics, the
+number of  $b$ quarks in the  final state is
+increased substantially in the $2b2j$ component as compared
+to the parton level content,
+enhancing the signal efficiency and making
+it comparable to the $4b$ component.

### 2015-12-04 paper/paperscripts/plotHist_m_hh_res_back_noPU.py

@@ -1,0 +1,136 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_hh_C2_bst_back_noPU"
+
+linestyles = [ 'solid', 'dashed','dotted']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/SHERPA_QCD4b/histo_m_HH_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/SHERPA_QCD2b2j/histo_m_HH_boost_C1e.dat")
+
+
+# Plot labels
+plotnames.append("QCD 4b")
+plotnames.append("QCD 2b2j")
+
+# Axis labels
+xLabel = "Invariant mass of di-Higgs system $m_{hh}$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['k', 'r', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+
+ax.set_xlim([410,600])
+ax.set_ylim([1e-4,0.05])
+
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
[…]

### 2015-12-04 paper/paperscripts/plotHist_pt_h0_bst_back_noPU.py

@@ -1,0 +1,135 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_h0_C2_res_back_noPU"
+
+linestyles = [ 'solid', 'dashed','dotted']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/SHERPA_QCD4b/histo_pt_H0_res_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/SHERPA_QCD2b2j/histo_pt_H0_res_C1e.dat")
+
+# Plot labels
+plotnames.append("QCD 4b")
+plotnames.append("QCD 2b2j")
+
+# Axis labels
+xLabel = "Leading Higgs Candidate $p_T$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['k', 'r', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+
+ax.set_xlim([0,300])
+ax.set_ylim([1e-5,0.05])
+
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
[…]

### 2015-12-04 paper/paperscripts/plotHist_pt_h0_res_back_noPU.py

@@ -1,0 +1,135 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_h0_C2_bst_back_noPU"
+
+linestyles = [ 'solid', 'dashed','dotted']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/SHERPA_QCD4b/histo_pt_H0_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/SHERPA_QCD2b2j/histo_pt_H0_boost_C1e.dat")
+
+# Plot labels
+plotnames.append("QCD 4b")
+plotnames.append("QCD 2b2j")
+
+# Axis labels
+xLabel = "Leading Higgs Candidate $p_T$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['k', 'r', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+
+ax.set_xlim([200,500])
+ax.set_ylim([1e-5,0.05])
+
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
[…]

### 2015-12-04 paper/sec-analysis.tex
more work on paper

@@
 %
-First of all, we discuss the settings and nomenclature that
-we will use for jet clustering, and then we move to discuss how $b$-tagging is simulated.
+First of all, we discuss the settings and nomenclature
+for jet clustering, and the strategy for $b$-tagging.
 %
 Then we discuss the categorisation of events between different
-topologies, and how we prioritise among them.
+topologies and how to prioritise among them.
 %
 Finally, we motivate our choice of analysis cuts by comparing signal and background
-for some representative kinematic distributions.
+for representative kinematic distributions.
 
@@
 
-At the end of the  parton shower, final state particles
+After the  parton shower, final state particles
 are clustered using the
 jet reconstruction algorithms
-are obtained from the
-{\tt FastJet} program~\cite{Cacciari:2011ma,Cacciari:2005hq},
+obtained from
+{\tt FastJet}~\cite{Cacciari:2011ma,Cacciari:2005hq},
 {\tt v3.1.0}.
 %
-In this study we will use different types of jet definitions,
-which we enumerate now:
-%
-
+We will use different types of jet definitions:
 \begin{itemize}
@@
   %
-  When reconstructing small-$R$ jets, we keep only
-  those jets with transverse momentum $p_T \ge 40$~GeV
-  and pseudo-rapidity $|\eta|<2.5$, within the central rapidity
-  acceptance of ATLAS and CMS.
-%
-  Jets that fail to satisfy these acceptance
-  requirements are discarded.
-  %
-  The restriction to the central rapidity region is a
-  requisite for $b$-tagging.
+  These small-$R$ jets are required
+  to have transverse momentum $p_T \ge 40$~GeV
+  and pseudo-rapidity $|\eta|<2.5$, within the central 
+  acceptance of ATLAS and CMS, the region
+  where $b$-tagging is possible.
 
@@
   %
-  In order to be accepted, these large-$R$ jets should
-  satisfy  $p_T \ge 200$~GeV and lie in a pseudo-rapidity range of
+  Large-$R$ jets are required to have
+  $p_T \ge 200$~GeV and lie in a pseudo-rapidity region of
   $|\eta|<2.0$.
-  %
-  If these conditions are not satisfied, the jet is discarded.
   %
@@
   in ATLAS and CMS
-  related to the track-jet-based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.
+  related to the track-jet based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.
 
@@
   acceptance requirements, large-$R$ jets should also
-  satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
-  conditions, required
-  to enhance the discrimination of the signal over the background
-  events.
+  satisfy the  BDRS mass-drop tagger (MDT)(~\cite{Butterworth:2008iy}
+  conditions.
   %
-  For the BDRS mass-drop tagger, we use the {\tt FastJet} default
+  We use the {\tt FastJet} default
   parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
   %
-  Before the mass-drop tagger is applied, the large-$R$ jet
-  constituents are reclustered with the Cambridge/Aachen
-  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}.
+  Before applying the MDT, the large-$R$ jet
+  constituents are reclustered with the Cambridge/Aachen (C/A)
+  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}
+  with $R=1.2$.
 
@@
 
-  Once we have reconstructed a suitable large-$R$ jet, important
-  information can be obtained by looking at the kinematics of
-  the small-$R$ subjets.
+  These subjets are constructed by reclustering the constituents
+  of a large-$R$ jet, again with  anti-$k_T$ algorithm,
+  but this time with a smaller radius parameter, namely
+  $R=0.3$.
  %
-  These subjets will be obtained by reclustering the constituents
-  of the large-$R$ jet, always with the  anti-$k_T$ algorithm,
-  but this time with a smaller radius parameter $R=0.3$.
- %
-  These small-$R$ subjets will be the building blocks of
+  These small-$R$ subjets will be the main input for
   $b$-tagging in the boosted category.
   %
-  Small-$R$ subjets are required to have $p_T > 50$~GeV and $|\eta|<2.5$,
-  else they are discarded.
+  They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
   %
@@
 
-We have
+In addition, we have
 also explored the possible improvements
-in the analysis from using variable-$R$ jets~\cite{Krohn:2009zg}, but found that these made
+in the analysis from the use
+of variable-$R$ jets~\cite{Krohn:2009zg}, but found that these made
 a small difference as compared to fixed-$R$ jets.
@@
 the degree of boost of the final state being reconstructed can span
-a wide range, such as in heavy resonance searches~\cite{Aad:2015fna}.
+a wide range~\cite{Cacciari:2008gd}, such as in heavy resonance searches~\cite{Aad:2015fna},
+where where the degree of boost of the final state
+is {\it a priori} unknown.
 
-\subsection{$b$-tagging}
+\subsection{Tagging of $b$-jets}
 \label{sec:btagging}
 
-Given the final state that needs to be reconstructed, the
+It is clear that
 optimisation of the $b$-tagging capabilities of the
-LHC experiments is an essential requirement to improve
-the prospects for the observation of Higgs pair production in this channel.
+LHC experiments is an essential ingredient to improve
+the prospects for the observation of Higgs pair production in the
+$b\bar{b}b\bar{b}$ final state.
 %
-The $b$-tagging strategy used in this feasibility study is inspired
-in the current and projected ATLAS settings~\cite{Aad:2013gja},
-though
-it is not too different from
- the corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}.
+In this work, we adopt
+a $b$-tagging strategy along the lines
+of current ATLAS performance~\cite{Aad:2013gja,Aad:2015ydr},
+though differences with respect to
+the corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}
+should not affect qualitatively our results.
 %
-For each type of jet defined above, a different
-$b$-tagging strategy is used:
+For each type of jet definition used, a different
+$b$-tagging strategy is adopted:
 
@@
 
-  These are $b$-tagged as follows.
   %
@@
   In order to be considered in the $b$-tagging algorithm,
-   $b$-quarks should satisfy $p_T \ge 15$ GeV.
-  %
-  If no $b$-quarks are found among the constituents
-  of this jet, it can be still be tagged as a $b$-jet with
-  a mistag rate of $f_l$, unless a charm quark is found,
-  and in this case the mistag rate is $f_c$.
-  %
-  Only jets which contain at least one constituent
-  with $p_T \ge 15$ GeV can lead to fake $b$-tags.
+  $b$-quarks inside the small-$R$ jet
+  should satisfy $p_T \ge 15$ GeV.
   %
@@
 
-  We only attempt to $b$-tag the four (two) hardest small-$R$ jets
+  If no $b$-quarks are found among the constituents
+  of this jet, it can be still be tagged as a $b$-jet with
+  a mistag rate of $f_l$, unless a charm quark is present instead,
+  and in this case the mistag rate is $f_c$.
+  %
+  Only jets which contain at least one (light or charm)
+  constituent
+  with $p_T \ge 15$ GeV will lead to fake $b$-tags.
+
+  We only attempt to $b$-tag only the four (two) hardest small-$R$ jets
   in the resolved (intermediate) category.
   %
-  We find that
-  attempting to $b$-tag all
-  small-$R$ jets that satisfy the acceptance cuts worsens the performance
+  Trying to $b$-tag all the
+  small-$R$ jets that satisfy the acceptance cuts worsens the
+  overall performance
   due to combinatorics.
@@
     jets~\cite{Cacciari:2007fd,Aad:2013gja,
-      ATLAS-CONF-2014-004}.\footnote{The same
-    method was used in the recent ATLAS $hh\to 4b$ search~\cite{Aad:2015uka}.}
+      ATLAS-CONF-2014-004,Aad:2015uka}.
     %
-    In particular,
-    a large-$R$ jet is considered  double-$b$-tagged if both
-    the leading and subleading subjets (where the ordering
-    is done in the subjet $p_T$) are both individually $b$-tagged.
+    A large-$R$ jet will considered $b$-tagged if both
+    the leading and subleading AK03 subjets, where the ordering
+    is done in the subjet $p_T$, are both individually $b$-tagged,
+    with the same criteria as the small-$R$ jets.
 
     As in the case
-    of small-$R$ jets, in
-    order to be considered in the $b$-tagging algorithm,
-   $b$-quarks should satisfy $p_T \ge 15$ GeV.
-    %
-    Note that we only attempt to $b$-tag the two leading subjets:
-    trying to $b$-tag all subjets above the $p_T$ cut degrades
-    the signal significance due to the increase in combinatorics.
+    of small-$R$ jets, we only attempt to $b$-tag the two leading subjets,
+    else one finds a degradation of the
+    signal significance due to combinatorics.
 
-    Concerning the $b$-tagging probabilities and the
-    light jet  and charm jet mistag probabilities, there are taken
-    the same as for small-$R$ jets.
     %
@@
     with probability $f_b^2$, if only one of the two leading
-    subjets has a $b$-quark then the tagging probability is
-    $2f_bf_l$, and if none of the two have $b$-quarks
-    as constituents, the mistag rate will be
-    $f_l^2$.
+    subjets has a $b$-quark, then the tagging probability is
+    $2f_bf_l$, and if none of the two subjets include $b$-quarks,
+    the mistag rate will be $f_l^2$.
 
@@
 
-Concerning the values of the $b$-tag probability $f_b$ and
-the $b$-mistag probability of light and charm jets $f_l$ and  $f_c$, 
-in this work we adopt as baseline the values $f_b=0.8$, $f_l=0.01$
+Concerning the values of the $b$-tag probability, $f_b$, and
+the $b$-mistag probability of light and charm jets, $f_l$ and  $f_c$
+respectively,
+we used the values $f_b=0.8$, $f_l=0.01$
 and  $f_c=0.1$.
@@
 
-The basic idea of our analysis strategy is similar to that in Ref.~\cite{Gouzevitch:2013qca}:
-rather than concentrating only a specific event topology, such as boosted
+The basic idea of present analysis is similar to the
+scale-invariant resonance tagging introduced
+in Ref.~\cite{Gouzevitch:2013qca}.
+%
+rather than restricting to a specific event topology, such as boosted
 or resolved, we aim to consistently combine the information from

### 2015-12-04 paper/sec-pileup.tex
more work on paper

@@
 have been developed
-recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
+recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
+These techniques have also important applicability for the subtraction
+of UE/MPI contamination for jet reconstruction
+in heavy ion collisions~\cite{Cacciari:2010te}.
+}
 %

### 2015-12-04 paper/sec-analysis.tex
more work on paper

@@
 
-The basic idea of present analysis is similar to the
+The basic idea of the present analysis is similar to the
 scale-invariant resonance tagging introduced
@@
 %
-rather than restricting to a specific event topology, such as boosted
-or resolved, we aim to consistently combine the information from
+Rather than restricting to a specific event topology,
+we aim to consistently combine the information from
 the three possible event topologies: boosted, intermediate and
@@
 %
-However, an important difference compared to~\cite{Gouzevitch:2013qca}
-is that here each category is optimised separately, and then
+The optimal cuts for each category will be determined
+separately, and then
 a exclusive categorisation is defined starting from the category
@@
 %
-An advantage of our approach is that the analysis strategy would be unchanged
-if the underlying production model of Higgs pairs is modified, for example in the case of
-BSM dynamics, which can substantially increase the degree of boost of the final state.
-
-Let us therefore define the three event categories that
-we use:
+An advantage of our approach is that the analysis strategy
+is robust under variations of
+the underlying production model of Higgs pairs is modified,
+for instance in the case of
+BSM dynamics, which can substantially increase
+the degree of boost of the final state.
+%
+These three categories are defined as follows:
 \begin{itemize}
@@
 
-  An event is assigned to the {\it boosted} category if it
-  contains at least two large-$R$ jets, defined as above,
-  and where  the two leading large-$R$ jets have been
-   double-$b$-tagged.
+  An event which
+  contains at least two large-$R$ jets, with the two leading
+ being $b$-tagged.
  %
- Therefore, each of these two large-$R$ double-$b$-tagged jets corresponds to the
- decay products of one Higgs boson candidate.
+ Each of these two large-$R$ $b$-tagged jets are is this
+ a candidate
+ to contain the decay products of a Higgs boson.
 
@@
 
-  An event is assigned to the {\it intermediate} category if
-  one and only one large $R$ double-$b$-tagged jet is present,
-  which corresponds to the the first Higgs candidate.
+  An event with only one large-$R$ $b$-tagged jet, which
+  is assigned to be the leading Higgs candidate.
   %
-  In addition, we require at least two small-$R$ jets,
-  which must be separated with respect to the large-$R$
-  jet by at least an angular separation of $\Delta R\ge 1.0$.
+  In addition, we require at least two small-$R$ $b$-tagged jets,
+  which must be separated with respect to the large-$R$ jet
+  by $\Delta R\ge 1.0$.
   %
-  These small-$R$ jets must be $b$-tagged as well.
 
-  The second Higgs boson candidate is reconstructed
+  The subleading Higgs boson candidate is then reconstructed
   by selecting the two $b$-tagged small-$R$ jets that minimize the difference
-  between the invariant mass of the large-$R$ jet,
+  between the invariant mass of the large-$R$ jet
   with the invariant mass of the dijet obtained
@@
 \item {\it Resolved category}.
+
+ An event with at least
+  four $b$-tagged small-$R$ jets.
   %
-  An event is assigned to the {\it resolved} category
-  if at least
-  four $b$-tagged small-$R$ jets are present.
-  %
-  The two Higgs candidates are then reconstructed out of the
+  The two Higgs candidates are reconstructed out of the
   leading four small-$R$ jets in the event
@@
   %
-  The requirement of restricting this selection to only the four
-  leading small-$R$ jets arises from the need to reducing the
-  combinatorics from  fakes.
+
 \end{itemize}
-These three categories are in principle not exclusive:
-a given even can be assigned to more than one category, for
-example, satisfying both the requirements of the boosted and resolved
-categories at the same time.
-%
-The exception is the boosted and intermediate categories, which have
-orthogonal jet selection requirements.
-%
-The separate optimisation of the three categories needs to be performed in
-a inclusive analysis.
-%
-Since in general there will be a certain degree of overlap between categories,
-a priorisation needs to be introduced in a exclusive analysis.
-%
 
 Once a Higgs boson candidate has been identified,
-its invariant mass is required to be within a fixed window
+its invariant mass is required to lie within a fixed window
 around the nominal Higgs boson mass.
@@
 %
-Only events where the two Higgs candidates satisfy the
-condition in Eq.~(\ref{higgsmasswindow}) are classified as signal events.
-%
-In Table~\ref{sec:categorisation} we summarize the definitions of each
-category.
+Only events where the two Higgs candidates satisfy
+Eq.~(\ref{higgsmasswindow}) are classified as signal events.
 %
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
-  \centering
-  \small
-  \begin{tabular}{c|c|c|c}
-    \hline
-    &  Boosted  &  Intermediate  &  Resolved \\
-    \hline
-    \hline 
-    Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
-    jets  &  $\ge$ 4 small-$R$ jets \\[0.2cm]
-    \hline
-    Jet cuts  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
-    &  $p_T \ge 40$ GeV \\
-    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
-    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
-    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\[0.2cm]
-    \hline
-    $b$-tagging  & 2 double-$b$-tags  & 1 double-$b$-tag & 4 single-$b$-tags \\
-    &  & and 2 single-$b$-tags  &  \\
-    & and $\ge 2$ small-$R$ subjets  &  and $\ge 2$ small-$R$ subjets  &  \\
-     &  in large-$R$ jets  &  in large-$R$ jet &  \\
-    &  $p_T^{\rm sj}\ge 50$ GeV & $p_T^{\rm sj}\ge 50$ GeV   &  \\[0.2cm]
-    \hline
-    Mass-Drop Tag  &  Two leading large-$R$ jets  &  Large-$R$ jet &   \\
-    \hline
-    \end{tabular}
-  \caption{\small Definition of the three event categories used in this
-    work, together with the corresponding basic kinematical cuts.
+These three categories are not exclusive:
+a given event can be assigned to more than one category, for
+example, satisfying the requirements of both the intermediate
+and resolved
+categories at the same time.
 %
-    The categories are not exclusive, and each event can satisfy the
-    requirements of more than one category at the same time.  
-\label{sec:categorisationTable}
-  }
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The exception is the boosted and intermediate categories, which have
+orthogonal jet selection requirements.
+%
+The separate optimisation of the three categories needs to be performed in
+a inclusive analysis, and then we introduce a
+ priorisation starting with the category of highest signal significance.
 
-The selection requirements and the kinematic cuts
-for each of the categories in Table~\ref{sec:categorisationTable} have
-been optimised separately.
+ This is achieved as follows.
  %
-First of all we have performed a inclusive analysis, and optimised the
+First of all we perform an inclusive analysis, and optimise the
 signal significance
@@
 We find that the category with higher significance turns out to be the boosted,
-followed by the intermediate and the resolved ones.
+followed by the intermediate and the resolved ones, the two latter
+with similar significance.
 %
@@
 %
-This allows us to combine the significance of the dominant topology
-(boosted) with that of the sub-leading categories, intermediate
-and resolved, without the problem of the double counting.
+This allows a consistent combination
+of the significance of the three event categories.
 

### 2015-12-04 paper/sec-pileup.tex
more work on the paper

--- 2015-11-30 paper/sec-pileup.tex
@@
 
-The main limitation of the analysis of the previous section was that
-pile-up (PU) effects were
+The main limitation of our analysis so far is the fact that
+pile-up (PU) effects have not been accounted for
 not accounted for.
@@
 However, any realistic feasibility study at the HL-LHC, specially
-like the present one that relies on the detailed modeling
-of kinematic distributions, needs to assess the robustness of the conclusions
-with respect to PU.
+one 
+such the present that relies on the careful modeling
+of kinematic distributions,
+requires assessing the robustness of the conclusions
+with respect to the inclusion of PU.
 %
@@
 the enhanced signal significance provided by the MVA, are robust
-in the presence of realistic PU conditions.
-%
-First of all we describe the simulation of realistic
-PU conditions at the HL-LHC, and discuss the settings of
+in the presence of  PU.
+
+First of all, we describe the simulation of the 
+PU conditions  expected at the HL-LHC, and discuss the settings of
 the PU subtraction strategy that we adopt.
@@
 have been developed
-recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.
+recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
+These techniques have also important applications in the subtraction
+of the UE/MPI contamination for jet reconstruction
+in heavy ion collisions~\cite{Cacciari:2010te}.
+}
 %
@@
 The size and number of these patches is a free parameter of the algorithm -
-here we will use square patched with length $a=0.4$.
+here we will use square patches with length $a=0.4$.
 %
-We restrict ourselves to the central rapidity interval,
-$\eta \in \lc -2.5, 2.5\rc$, for the estimation of the
+We restrict ourselves to the central rapidity region,
+$|\eta| \le 2.5$, for the estimation of the
 $p_T$ flow density $\rho$.
@@
 to particles at the end of the parton shower, before
-the jet clustering stage.
+jet clustering.
 
+To validate PU subtraction,
+we now compare different kinematical distributions
+in the case without PU and in the case
+with PU subtracted with {\tt SoftKiller}.
 %
-We now compare different kinematical distributions
-in the three relevant cases:
-cases:
-\begin{itemize}
-\item without any PU,
-\item adding PU, but without any PU subtraction,
-  \item adding PU, followed by the {\tt SoftKiller} subtraction.
-\end{itemize}
-As we will show now, {\tt SoftKiller} exhibits a reasonable
-performance in PU subtraction.
+Then we will also compare some specific distributions
+also in the case where PU has not been subtracted.
 %
-We will also see that the boosted category is less affected
+We find that
+{\tt SoftKiller} exhibits a reasonable
+performance for the PU subtraction.
+%
+We  also obtain that the boosted category is less affected
 by PU than the resolved category, as expected from the higher
@@
 Let us begin by comparing
-a number of signal distributions with
-and without PU, with $\la n_{\rm PU}\ra=80$ in the former
-case.
+representative signal distributions with
+and without PU, with $\la n_{\rm PU}\ra=80$ in the
+former
+case (and SK subtraction).
 %
@@
 As we can see, in the boosted category, the residual effects of PU
-after the {\tt SoftKiller} subtraction are very mild in these
-distributions, with the position of the Higgs mass peaks essentially
-unchanged.
+after the {\tt SoftKiller} subtraction are rather mild,
+with the position of the Higgs mass peaks essentially
+unchanged, and only a moderate distortion of the
+distribution found.
 %
@@
     (upper plots) and boosted (lower plots) categories,
-    without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
+    both without PU and with
+    PU, $\la n_{PU}\ra=80$, subtracted with {\tt SoftKiller}.
 }
@@
 %
-Note that this latter observable is particularly sensitive
-of BSM dynamics.
-%
-These results validate the PU subtraction strategy adopted in this work.
+These comparisons validate the PU subtraction strategy
+adopted in this work.
 
@@
 
-Next, we assess the impact of PU in representative
+We can also assess the impact of PU in representative
 substructure variables
@@
 In particular we consider the subjetiness variable,
-$\tau_{21}$, and the ratio
+$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
 of energy correlation functions, $D_2^{(\beta)}$,
-corresponding to the the leading Higgs candidate.
+Eq.~(\ref{eq:d2}),
+corresponding to the leading Higgs candidate.
 %
@@
 As can be seen, these substructure variables, which
-as demonstrated before carry a very substantial
+as demonstrated before carry a substantial
 discrimination power, are relatively unaffected by PU.
 %
-Therefore, we do not expect a substantial loss of discrimination
+Recall that the $D_2^{(\beta)}$ variable is
+explicitly constructed~\cite{Larkoski:2013eya}
+to be resilient
+with respect to PU contamination.
+%
+Therefore, we do not expect a major loss of discrimination
 power due to PU effects in our analysis.
 %
-Note in particular that $D_2^{(\beta)}$ was constructed to be resilient
-with respect to PU contamination.
 
@@
 
+It is also interesting to quantify how
+the relative differences between
+signal over background distributions are affected in 
+the presence of PU.
 %
-We now assess how the signal over background discrimination is affected
-in the presence of PU.
-%
-First of all let us consider the boosted category.
-%
-In Fig.~\ref{fig:signal-vs-back-boosted} we compare
+Considering first of all the boosted category,
+in Fig.~\ref{fig:signal-vs-back-boosted} we compare
 various kinematical distributions for signal and background events,
      with and without PU: the invariant mass and the $p_T$ of the leading
-     Higgs candidate, and the $\tau_{21}$ and $D^{(\beta)}_2$ substructure variables.
-     %
-     All these distributions correspond to the boosted category.
+     Higgs candidate, the 2-jettines $\tau_{21}$ and $\sqrt{d_{12}}$,
+     $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),
+     for the leading Higgs candidate.
      %
@@
    \includegraphics[width=0.49\textwidth]{plots/tau21_h1_bst_comp_back.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/split12_h0_bst_comp_back.pdf}
    \caption{\small
-     Comparison of kinematical distributions for signal and background events,
-     with and without PU: the invariant mass and the $p_T$ of the leading
-     Higgs candidate, and the $\tau_{21}$ and $D^{(\beta)}_2$ substructure variables.
+     Comparison of kinematical distributions, in
+     the boosted category, for signal and background events
+     with and without PU: the invariant mass,  $p_T$,
+     and the substructure variables $\tau_{21}$ and $\sqrt{d_{12}}$
+    for the leading Higgs candidate.
      %
-     All these distributions correspond to the boosted category.
  }

### 2015-12-04 paper/sec-pileup.tex
more work on paper

@@
 
-Let us begin by comparing
-representative signal distributions with
+First of all, let us validate both the implementation of our
+simulation of PU, as well as the SK subtraction, by comparing the
+invariant mass distributions of Higgs candidates in signal
+events in the resolved category.
+%
+In Fig.~\ref{fig:PUvalidation} we show three curves: without PU,
+with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
+same but now with the SK subtraction.
+%
+As expected, if PU is not subtracted there is a large shift in the Higgs mass
+peak, by about 40 GeV.
+%
+Once SK subtraction is performed, we recover a distribution much closer
+to the original ones, with only a small shift of $\simeq 5$ GeV in the mass
+distribution.
+%
+As we will see below, the performance of SK is even better in the boosted category,
+since the effects of PU are mitigated for high $p_T$ jets.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+  \includegraphics[width=0.68\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
+    \caption{\small
+    The invariant mass distributions of Higgs candidates in signal
+events, in the resolved category, comparing the results without PU,
+with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
+corresponding results now with SK subtraction.
+}
+\label{fig:PUvalidation}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Next, we compare more
+ signal distributions with
 and without PU, with $\la n_{\rm PU}\ra=80$ in the
@@
      with and without PU: the invariant mass and the $p_T$ of the leading
-     Higgs candidate, the 2-jettines $\tau_{21}$ and $\sqrt{d_{12}}$,
+     Higgs candidate, the 2-jettiness $\tau_{21}$ and $\sqrt{d_{12}}$,
      $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),

### 2015-12-04 paper/sec-pileup.tex
updated PU section

@@
 various kinematical distributions for signal and background events,
-     with and without PU: the invariant mass and the $p_T$ of the leading
-     Higgs candidate, the 2-jettiness $\tau_{21}$ and $\sqrt{d_{12}}$,
-     $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),
-     for the leading Higgs candidate.
+     with and without PU: the invariant mass, the $p_T$,
+     the 2-jettiness $\tau_{21}$, and $\sqrt{d_{12}}$,
+     the $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),
+     all corresponding to
+     the leading Higgs candidate.
      %
-     While for signal distributions the effects of PU after SK subtraction are small,
-     differences are more marked for the background distributions, where
-     the shapes of the distributions with and without background can be substantially
-     different.
+      We observe that the most of the relevant
+      qualitative differences between signal
+      and background distributions are maintained in the presence of PU.
       %
-     We note however that the fact that signal and background distribution exhibit
-     rather different behaviors is maintained in the presence of PU.
+      This is specially clear for the substructure variables, which
+      show a similar discrimination power both with and without
+      PU.
 
@@
      %
-     Here the PU-subtracted background distributions appear reasonably close
+     Also in this
+     case the PU-subtracted background distributions appear reasonably close
      to their no PU counterparts.
      %
-     Differences between signal and background distributions are maintained after PU
-     has been accounted for.
+     Therefore, these results
+     suggest that the broad pattern of the signal over background
+     discrimination provided by the MVA in Sect.~\ref{sec:mva},
+     based on the corresponding differences between kinematical
+     distributions,
+will
+     be maintained in the presence of PU.
      %
-     we have indeed that this is the case
-     in general.
-     %
-     Therefore, we expect that the broad features of the signal/background
-     discrimination provided by the MVA in Sect.~\ref{sec:mva} will
-     be maintained also in the presence of PU.
+     In the next section we verify this expectation.
 
@@
 
+The same settings of the cut-based analysis,
+Sects.~\ref{sec:analysis} and~\ref{sec:results}, and
+the subsequent MVA optimization, Sect.~\ref{sec:mva}, have
+been applied to the samples with PU, $\la n_{\rm PU}\ra=80$,
+and SK subtraction.
+%
 The corresponding version of Table~\ref{tab:cutflow_noPU_1}, the 
@@
 of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
-is provided in Table~\ref{tab:cutflow_SKPU80_1}.
+is presented in Table~\ref{tab:cutflow_SKPU80_1}.
 %
-We observe that, at the end of the cut-based analysis,
+One immediate observation is that
+at the end of the cut-based analysis,
 the signal significance have been  degraded
@@
 %
-We obtain that $S\sqrt{B}$ is now 0.4, 0.3 and 0.9 in the resolved,
-intermediate and boosted categories, respectively.
+We now obtain values for $S\sqrt{B}$ of 0.4, 0.3 and 0.9, in the resolved,
+intermediate and boosted categories, respectively, to be compared
+with the corresponding values without PU, namely 1.6, 1.6 and 2.7.
 %
-The boosted category is the least affected one, since as shown
-before PU contamination is milder given the selection requirements.
+Therefore, the pre-MVA signal significance is degraded by a factor 4 in
+the resolved and the intermediate categories,
+and by a factor 3 in the boosted category.
+%
+The fact that the latter is the  least affected one
+can be understood from the previous comparison
+plots, which show that effects of PU contamination
+are milder due to the  selection requirements
+of the boosted category.
 
@@
 
-The MC events that satisfy the selection requirements of the cut-based
-analysis, row C2 in Table~\ref{tab:cutflow_SKPU80_1}, are then
-used as input for the MVA, 
-using the same strategy explained 
-in Sect.~\ref{sec:mva}.
-%
-In Fig.~\ref{fig:nnresponse_PU} we represent
+In Fig.~\ref{fig:nnresponse_PU} we present
 the distribution of the ANN output for the
@@
 we provide the  the number of signal and
-    background events at the HL-LHC, as well as the $S/\sqrt{B}$ and $S/B$,
+    background events expected
+    at the HL-LHC, as well as the
+    corresponding values for $S/\sqrt{B}$ and $S/B$,
     for both the cut-based analysis (corresponding
     to $y_{\rm cut}=0$) and after the
-    optimal MVA cut.
-    %
-    These numbers corresponding to the simulations
+    optimal MVA cut, for the simulations
     with $\la n_{\rm PU}\ra=80$
@@
     %
-    The corresponding results without PU were collected
-    in Table.~\ref{table:cutflowMVA}.
+    The same results without PU are those of
+    Table.~\ref{table:cutflowMVA}.
     %
@@
 to the MVA, we can improve the signal significance and the
-signal over background ratio from 0.31 and $3\cdot 10^{-4}$
-(0.40 and $1.3\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
+signal over background ratio from 0.35 and $4\cdot 10^{-4}$
+(0.25 and $1\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
 in the boosted (resolved) category.
 %
-The intermediate category exhibits a lower value of $S/\sqrt{B}$
-for the optimal $y_{\rm cut}$ value, around unity.
+The intermediate category exhibits a rather lower value of $S/\sqrt{B}$
+for the optimal $y_{\rm cut}$ value, around 1.1.
 %
-We thus conclude that the boosted category is the most promising
+We thus conclude that, as was already the case
+without PU,
+the boosted category is the most promising
 one for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
-at the HL-LHC, with however useful information also provided
-by the resolved category.
+final state
+at the HL-LHC, also when PU is included.
+%
+However, important information will also be obtained from
+the resolved category, which has a signal significance
+only slightly smaller than the boosted case.
 
@@
     \hline
-  1123  &    $8.5\cdot 10^6$   & 0.40       &  $1.3\cdot 10^{-4}$       &
+  1123  &    $8.5\cdot 10^6$   & 0.25       &  $1.3\cdot 10^{-4}$       &
   432  &  $3\cdot 10^4$        &   2.5      & 0.15 \\
@@
 
-Next we show the results
-as a function of the optimal ANN cut $y_{\rm cut}$.
+Another important result from Table~\ref{table:cutflowMVA_PU} is that,
+for the optimal MVA cut, the signal over background ratio
+is not unfeasibly small: we obtain that $S/B$ is 3.4\% (1.5\%)
+in the boosted (resolved) categories.
+%
+This is indicates that while this measurement is still very challenging,
+requiring a careful extraction from the data of the QCD
+background, it is certainty within reach.
+%
+Our analysis also indicates a possible way forward to
+further increase $S/B$: reducing the background from light and charm
+fakes, see Table~\ref{tab:cutflow_SKPU80_1}.
+
+Let us now discuss in more detail the results of the MVA
+classification, by showing various estimators as function
+of the cut $y_{\rm cut}$ in the ANN discriminant.
 %
@@
 we show the number of signal and background events that
-are expected at the HL-LHC as a function of the ANN discriminant -
+are expected at the HL-LHC as a function of
+$y_{\rm cut}$ -
 the corresponding results without PU are those of

### 2015-12-04 paper/sec-mva.tex
final touches on the PU section

@@
 the  smearing of jet four-momenta introduced to mimic
-realistically detector resolution.\footnote{We have verified that
-  if no smearing is applied, the $m_h$ distributions for the leading
-  and subleading Higgs candidates become the most
-important variables in the MVA.}
+realistically detector resolution.
 

### 2015-12-04 paper/sec-pileup.tex
final touches on the PU section

@@
-\clearpage
 \section{Impact of pile-up}
@@
 %
-As we can see from Fig.~\ref{fig:nev2_PU}, the trends are
-similar as those in the case without PU.
+As we can see, the general trends are
+similar as those without PU.
 %
@@
 that the intermediate category is substantially degraded once PU effects
-are accounted for, the reason being a reduction in the number of signal
+are accounted for, the reason being  sizable
+a reduction in the number of signal
 events that are now assigned to this category.
 %
-This shows that the definition of the intermediate category is seriously
-affected by PU, as opposed to the resolved and boosted selections.
+This shows that the selection criteria
+of the intermediate category are less
+resilient against PU contamination,
+as opposed to the resolved and boosted selections.
 
@@
 \includegraphics[width=0.65\textwidth]{plots/nev2_SKPU80.pdf}
-\caption{\small Same as Fig.~\ref{fig:nev2} now
-  with  $\la n_{\rm PU}\ra=80$ PU events 
+\caption{\small Same as Fig.~\ref{fig:nev2} in the
+case of events with PU, for
+ $\la n_{\rm PU}\ra=80$ 
   and SK subtraction.
@@
 $S/\sqrt{B}$, as well as the signal over background ratio,
-$S/B$, as a function of the ANN discriminant $y_{\rm cut}$, in the case
-of the analysis including the effects of PU
-with $\la n_{\rm PU}\ra=80$.
+$S/B$, including now the effects of PU.
 %
@@
 optimize PU subtraction, for example by tuning the value
-of the patch length $a$ in {\tt SoftKiller}, we expect that
+of the patch length $a$ in {\tt SoftKiller}, we believe that
 there is
@@
 \includegraphics[width=0.48\textwidth]{plots/sb_SKPU80.pdf}
-\caption{\small Same as Fig.~\ref{fig:sb_mva}
-  now
-  with  $\la n_{\rm PU}\ra=80$ PU events 
+\caption{\small 
+Same as Fig.~\ref{fig:sb_mva} in the
+case of events with PU, for
+ $\la n_{\rm PU}\ra=80$ 
   and SK subtraction.
@@
 
-It is illustrative to quantify which of the input variables
-to the MVA are most significant in the case of PU,
+It is important to quantify which of the input variables
+to the MVA carry the highest discrimination power
+in the case of PU,
 and compare it with the corresponding
@@
 As we can see by comparing to the corresponding
-results without PU in Fig.~\ref{fig:nnweights}, we see that
+results without PU in Fig.~\ref{fig:nnweights}, 
 in the boosted category, the discrimination power of the invariant
@@
 relatively robust against PU contamination.
-
-In the case of the resolved category, in the case without PU the highest
-values of the weight sum were found for the $p_T$ of the leading
+%
+In addition, also the $p_T$ distributions of the AK03
+subjets within the large-$R$
+jets carry important information.
+%
+In the case of the resolved category,  the highest
+values of the ANN weights without PU
+were found for the $p_T$ of the leading
 Higgs and for the Higgs invariant masses.
@@
 insensitive to PU effects.
+%
 
@@
 \caption{\small
-Same as Fig.~\ref{fig:nnweights} in the case of PU.
+Same as Fig.~\ref{fig:nnweights} in the
+case of events with PU, for
+ $\la n_{\rm PU}\ra=80$ 
+  and SK subtraction.
 }
@@
 
-Finally, we now combine the three categories, resolved,
-intermediate and boosted, and determine the signal
+At this point, we can finally combine the three categories, resolved,
+intermediate and boosted, and determine the overall signal
 significance taking into account all event topologies.
@@
 (exclusive) categories for the corresponding
-optimal value of $y_{\rm cut}$, our final combined result is
+optimal value of $y_{\rm cut}$, our final combined result, accounting
+for PU effects, is
 \be
@@
 \ee
-that is, well
-above the threshold for evidence, and  relatively close to the
-requirement for discovery.
+to be compared to the value $\lp S/\sqrt{B}\rp_{\rm tot} \simeq 8.5$
+that was obtained in the case without PU.
+%
+We conclude that, even when realistic PU effects are accounted
+for, at the HL-LHC the measurement of
+Higgs pair production in the $b\bar{b}b\bar{b}$ final state should be 
+well the threshold for evidence, and even meeting the
+requirement for discovery might be within reach.
 %

### 2015-12-07 paper/sec-analysis.tex
Divided results of PU section among independent sections

@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{PU subtraction with {\tt SoftKiller}}
+
+To study the impact of PU in our analysis,
+Minimum Bias (MB) events,
+including Multiple Parton Interactions (MPI), have been generated
+with {\tt Pythia8}, and
+superimposed to the signal
+and background samples described in Sect.~\ref{mcgeneration}.
+%
+We have explored two scenarios for the amount of PU expected
+at the HL-LHC, one with a mean number of
+PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another
+with $\la n_{\rm PU}\ra=150$.
+%
+In order to subtract the PU, a number of techniques
+have been developed
+recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
+These techniques have also important applications in the subtraction
+of the UE/MPI contamination for jet reconstruction
+in heavy ion collisions~\cite{Cacciari:2010te}.
+}
+%
+In this work, PU  will be subtracted by means
+of the the {\tt SoftKiller} (SK)
+method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
+%
+
+The idea underlying {\tt SoftKiller} is based on eliminating particles
+below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
+value is dynamically determined in a way that makes the event-wide
+transverse-momentum flow density $\rho$ vanish.
+%
+This $p_T$ flow density is defined as
+\be
+\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
+\ee
+where the median is computed over all the patches $i$ with area
+$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
+is partitioned.
+%
+From its definition in terms of the median,
+we observe that the value of $p_T^{(\rm cut)}$
+will be dynamically raised until half of the patches have $\rho=0$.
+%
+The size and number of these patches is a free parameter of the algorithm -
+here we will use square patches with length $a=0.4$.
+%
+We restrict ourselves to the central rapidity region,
+$|\eta| \le 2.5$, for the estimation of the
+$p_T$ flow density $\rho$.
+%
+In this analysis, {\tt SoftKiller} method is applied
+to particles at the end of the parton shower, before
+jet clustering.
+
+To validate PU subtraction,
+we now compare different kinematical distributions
+in the case without PU and in the case
+with PU subtracted with {\tt SoftKiller}.
+%
+Then we will also compare some specific distributions
+also in the case where PU has not been subtracted.
+%
+We find that
+{\tt SoftKiller} exhibits a reasonable
+performance for the PU subtraction.
+%
+We  also obtain that the boosted category is less affected
+by PU than the resolved category, as expected from the higher
+$p_T$ threshold in the corresponding selection cuts.
+
+First of all, let us validate both the implementation of our
+simulation of PU, as well as the SK subtraction, by comparing the
+invariant mass distributions of Higgs candidates in signal
+events in the resolved category.
+%
+In Fig.~\ref{fig:PUvalidation} we show three curves: without PU,
+with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
+same but now with the SK subtraction.
+%
+As expected, if PU is not subtracted there is a large shift in the Higgs mass
+peak, by about 40 GeV.
+%
+Once SK subtraction is performed, we recover a distribution much closer
+to the original ones, with only a small shift of $\simeq 5$ GeV in the mass
+distribution.
+%
+As we will see below, the performance of SK is even better in the boosted category,
+since the effects of PU are mitigated for high $p_T$ jets.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+  \includegraphics[width=0.68\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
+    \caption{\small
+    The invariant mass distributions of Higgs candidates in signal
+events, in the resolved category, comparing the results without PU,
+with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
+corresponding results now with SK subtraction.
+}
+\label{fig:PUvalidation}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Next, we compare more
+ signal distributions with
+and without PU, with $\la n_{\rm PU}\ra=80$ in the
+former
+case (and SK subtraction).
+%
+In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
+of the leading and subleading Higgs candidates, corresponding to both
+the boosted
+and resolved categories.
+%
+These distributions are plotted after the $b$-tagging, that is,
+before they are used as input to the MVA.
+%
+As we can see, in the boosted category, the residual effects of PU
+after the {\tt SoftKiller} subtraction are rather mild,
+with the position of the Higgs mass peaks essentially
+unchanged, and only a moderate distortion of the
+distribution found.
+%
+The effects are more important for the resolved category, where PU
+shifts the Higgs peak by an amount $\Delta m_h \simeq 5$ GeV.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+      \vspace{-1cm}
+      \includegraphics[width=0.49\textwidth]{plots/m_H0_res_comp.pdf}
+      \includegraphics[width=0.49\textwidth]{plots/m_H1_res_comp.pdf}
+      \includegraphics[width=0.49\textwidth]{plots/m_H0_bst_comp.pdf}
+      \includegraphics[width=0.49\textwidth]{plots/m_H1_bst_comp.pdf}
+  \caption{\small
+    Comparison of the invariant mass distributions of the leading (left plots)
+    and subleading (right plots) Higgs candidates in the resolved
+    (upper plots) and boosted (lower plots) categories,
+    both without PU and with
+    PU, $\la n_{PU}\ra=80$, subtracted with {\tt SoftKiller}.
+}
+\label{fig:m_H_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Next we compare the transverse momentum of the leading Higgs
+candidate, $p_t^{h_1}$ and the invariant mass of the di-Higgs system
+$m_{hh}$, in Fig.~\ref{fig:mHH_PU}, both for the boosted and
+for the resolved categories.
+%
+In the case of the $p_T$ distribution, the differences between the selection
+criteria for the resolved
+and boosted categories is reflected in the rightward shift of the latter.
+%
+The effect of PU is negligible in the boosted case, and small
+in the resolved case, except for large $p_T$ values.
+%
+For the case of the $m_{hh}$ distribution, similar conclusions
+apply.
+%
+These comparisons validate the PU subtraction strategy
+adopted in this work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \vspace{-1cm}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
+  \caption{\small
+    Comparison of the transverse momentum $p_T^h$ of the leading
+    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
+    of the di-Higgs system (lower plots) in the resolved
+    (left plots) and boosted (right plots) categories,
+    without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
+}
+\label{fig:mHH_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+We can also assess the impact of PU in representative
+substructure variables
+used as input to the MVA in the boosted category.
+%
+In particular we consider the subjetiness variable,
+$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
+of energy correlation functions, $D_2^{(\beta)}$,
+Eq.~(\ref{eq:d2}),
+corresponding to the leading Higgs candidate.
+%
+This comparison is illustrated in Fig.~\ref{fig:Substructure_PU}.
+%
+As can be seen, these substructure variables, which
+as demonstrated before carry a substantial
+discrimination power, are relatively unaffected by PU.
+%
+Recall that the $D_2^{(\beta)}$ variable is
+explicitly constructed~\cite{Larkoski:2013eya}
+to be resilient
+with respect to PU contamination.
+%
+Therefore, we do not expect a major loss of discrimination
+power due to PU effects in our analysis.
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/tau21_h0_bst_comp.pdf}
+   \caption{\small
+     Comparison of the substructure variables $D_2^{(\beta)}$ (left)
+     and $\tau_{21}$ (right)
+     for the leading Higgs candidate in the boosted category,
+   without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
+}
+\label{fig:Substructure_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+It is also interesting to quantify how
+the relative differences between
+signal over background distributions are affected in 
+the presence of PU.
+%
+Considering first of all the boosted category,
+in Fig.~\ref{fig:signal-vs-back-boosted} we compare
+various kinematical distributions for signal and background events,
+     with and without PU: the invariant mass, the $p_T$,
+     the 2-jettiness $\tau_{21}$, and $\sqrt{d_{12}}$,
+     the $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),
+     all corresponding to
+     the leading Higgs candidate.
+     %
+      We observe that the most of the relevant
+      qualitative differences between signal
+      and background distributions are maintained in the presence of PU.
+      %
+      This is specially clear for the substructure variables, which
+      show a similar discrimination power both with and without
+      PU.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+  \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_h0_bst_comp_back.pdf}
+   \includegraphics[width=0.49\textwidth]{plots/tau21_h1_bst_comp_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/split12_h0_bst_comp_back.pdf}
+   \caption{\small
+     Comparison of kinematical distributions, in
+     the boosted category, for signal and background events
+     with and without PU: the invariant mass,  $p_T$,
+     and the substructure variables $\tau_{21}$ and $\sqrt{d_{12}}$
+    for the leading Higgs candidate.
+     %
+ }
+\label{fig:signal-vs-back-boosted}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+Now we perform a similar comparison this time for
+the resolved category.
+%
+In Fig.~\ref{fig:signal-vs-back-resolved} we compare
+the kinematical distributions for signal and background events,
+     with and without PU, for the invariant mass and the $p_T$ of the leading
+     Higgs candidate.
+     %
+     Also in this
+     case the PU-subtracted background distributions appear reasonably close
+     to their no PU counterparts.
+     %
+     Therefore, these results
+     suggest that the broad pattern of the signal over background
+     discrimination provided by the MVA in Sect.~\ref{sec:mva},
+     based on the corresponding differences between kinematical
+     distributions,
+will
+     be maintained in the presence of PU.
+     %
+     In the next section we verify this expectation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+   \includegraphics[width=0.49\textwidth]{plots/m_h0_res_comp_back.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/pt_h0_res_comp_back.pdf}
+     \caption{\small
+       Same as Fig.~\ref{fig:signal-vs-back-boosted} for the resolved category,
+       this time without the jet substructure variables.
+}
+\label{fig:signal-vs-back-resolved}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-07 paper/sec-mva.tex
Divided results of PU section among independent sections

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{MVA revisited in the presence of PU}
+
+The main limitation of our analysis so far is the fact that
+pile-up (PU) effects have not been accounted for
+not accounted for.
+%
+However, any realistic feasibility study at the HL-LHC, specially
+one 
+such the present that relies on the careful modeling
+of kinematic distributions,
+requires assessing the robustness of the conclusions
+with respect to the inclusion of PU.
+%
+In this section, we show how our qualitative results, in particular
+the enhanced signal significance provided by the MVA, are robust
+in the presence of  PU.
+
+First of all, we describe the simulation of the 
+PU conditions  expected at the HL-LHC, and discuss the settings of
+the PU subtraction strategy that we adopt.
+%
+Then we present the validation of the PU subtraction,
+and compare a number of distributions, including substructure variables,
+with and without PU.
+%
+Finally we revisit the MVA analysis of Sect.~\ref{sec:mva}, and
+show that our qualitative conclusions are robust
+in the presence of realistic PU conditions, finding
+a combined
+signal significance of $S/\sqrt{B}\simeq 4$.
+
+The same settings of the cut-based analysis,
+Sects.~\ref{sec:analysis} and~\ref{sec:results}, and
+the subsequent MVA optimization, Sect.~\ref{sec:mva}, have
+been applied to the samples with PU, $\la n_{\rm PU}\ra=80$,
+and SK subtraction.
+%
+The corresponding version of Table~\ref{tab:cutflow_noPU_1}, the 
+cut-flow for the cross-sections and signal significance at the various
+steps of the cut-based analysis, 
+in the case
+of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
+is presented in Table~\ref{tab:cutflow_SKPU80_1}.
+%
+One immediate observation is that
+at the end of the cut-based analysis,
+the signal significance have been  degraded
+as compared to the case without PU.
+%
+We now obtain values for $S\sqrt{B}$ of 0.4, 0.3 and 0.9, in the resolved,
+intermediate and boosted categories, respectively, to be compared
+with the corresponding values without PU, namely 1.6, 1.6 and 2.7.
+%
+Therefore, the pre-MVA signal significance is degraded by a factor 4 in
+the resolved and the intermediate categories,
+and by a factor 3 in the boosted category.
+%
+The fact that the latter is the  least affected one
+can be understood from the previous comparison
+plots, which show that effects of PU contamination
+are milder due to the  selection requirements
+of the boosted category.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \scriptsize
+  \input{tables/table_SKPU80_1.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+  \input{tables/table_SKPU80_2.tex}
+  $\,$ \\
+  \vspace{0.5cm}
+    \input{tables/table_SKPU80_3.tex}
+    \caption{\small
+      Same as Table~\ref{tab:cutflow_noPU_1}, for the analysis
+      including PU with $\la n_{\rm PU}\ra=80$ and SK subtraction.
+      \label{tab:cutflow_SKPU80_1}}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Fig.~\ref{fig:nnresponse_PU} we present
+the distribution of the ANN output for the
+signal and background MC events in the boosted and resolved categories --
+the analogous comparison in the case without PU was shown
+in Fig.~\ref{fig:nnresponse}.
+%
+We observe that the clear MVA discrimination
+between signal and background events in the two categories is robust
+when PU is included.
+%
+However, by comparing with Fig.~\ref{fig:nnresponse}, we see
+that some of the most distinguishing features that separate signal
+and background in the ANN output are reduced when PU effects
+are included.
+%
+For instance, in the boosted category, there is a trend of the distribution
+for signal events to move towards smaller values of the
+ANN discriminant.
+%
+This in turn will entail a reduction of the signal significance as
+compared to the case without PU.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+\includegraphics[width=0.49\textwidth]{plots/Resolved_disc_SKPU80.pdf}
+\includegraphics[width=0.49\textwidth]{plots/Boosted_disc_SKPU80.pdf}
+\caption{\small Same as Fig.~\ref{fig:nnresponse},
+  this time with $\la n_{\rm PU}\ra=80$ PU events per bunch crossing
+  and SK subtraction, for the resolved (left) and boosted
+  (right) categories.
+  %
+  The corresponding comparison without PU was shown in
+  Fig.~\ref{fig:nnresponse}.
+}
+\label{fig:nnresponse_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+In Table~\ref{table:cutflowMVA_PU}
+we provide the  the number of signal and
+    background events expected
+    at the HL-LHC, as well as the
+    corresponding values for $S/\sqrt{B}$ and $S/B$,
+    for both the cut-based analysis (corresponding
+    to $y_{\rm cut}=0$) and after the
+    optimal MVA cut, for the simulations
+    with $\la n_{\rm PU}\ra=80$
+    and SK subtraction.
+    %
+    The same results without PU are those of
+    Table.~\ref{table:cutflowMVA}.
+    %
+    From Table~\ref{table:cutflowMVA_PU} we see that, thanks
+to the MVA, we can improve the signal significance and the
+signal over background ratio from 0.35 and $4\cdot 10^{-4}$
+(0.25 and $1\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
+in the boosted (resolved) category.
+%
+The intermediate category exhibits a rather lower value of $S/\sqrt{B}$
+for the optimal $y_{\rm cut}$ value, around 1.1.
+%
+We thus conclude that, as was already the case
+without PU,
+the boosted category is the most promising
+one for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
+final state
+at the HL-LHC, also when PU is included.
+%
+However, important information will also be obtained from
+the resolved category, which has a signal significance
+only slightly smaller than the boosted case.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \small
+  \begin{tabular}{c|c|c|c||c|c|c|c}
+    \hline
+    \multicolumn{8}{c}{Boosted category, $\la n_{\rm PU}\ra=80$+SK}\\
+    \hline
+     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.84$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+    362  &  $1.4\cdot 10^6$     & 0.31       &  $3\cdot 10^{-4}$ &
+    248     &   7250             &  2.9       & 0.034 \\
+    \hline
+       \multicolumn{8}{c}{$\quad$}\\
+    \hline
+    \multicolumn{8}{c}{Intermediate category,  $\la n_{\rm PU}\ra=80$+SK}\\
+    \hline
+    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.72$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+    146  &    $9\cdot 10^5$   & 0.15        &  $2\cdot 10^{-4}$      &
+  53  &  2547        & 1.1        &  0.02 \\
+  \hline
+  \multicolumn{8}{c}{$\quad$}\\
+    \hline
+    \multicolumn{8}{c}{Resolved category,  $\la n_{\rm PU}\ra=80$+SK}\\
+    \hline
+     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
+    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
+    \hline
+    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
+    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
+        Signal & Back   &     &   &  Signal & Back   &     &    \\
+    \hline
+  1123  &    $8.5\cdot 10^6$   & 0.25       &  $1.3\cdot 10^{-4}$       &
+  432  &  $3\cdot 10^4$        &   2.5      & 0.15 \\
+        \hline
+  \end{tabular}
+  \caption{\small Same as Table~\ref{table:cutflowMVA} in the case
+    of PU+SK, with $\la n_{\rm PU}\ra=80$.
+        \label{table:cutflowMVA_PU}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Another important result from Table~\ref{table:cutflowMVA_PU} is that,
+for the optimal MVA cut, the signal over background ratio
+is not unfeasibly small: we obtain that $S/B$ is 3.4\% (1.5\%)
+in the boosted (resolved) categories.
+%
+This is indicates that while this measurement is still very challenging,
+requiring a careful extraction from the data of the QCD
+background, it is certainty within reach.
+%
+Our analysis also indicates a possible way forward to
+further increase $S/B$: reducing the background from light and charm
+fakes, see Table~\ref{tab:cutflow_SKPU80_1}.
+
+Let us now discuss in more detail the results of the MVA
+classification, by showing various estimators as function
+of the cut $y_{\rm cut}$ in the ANN discriminant.
+%
+In Fig.~\ref{fig:nev2_PU}
+we show the number of signal and background events that
+are expected at the HL-LHC as a function of
+$y_{\rm cut}$ -
+the corresponding results without PU are those of
+Fig.~\ref{fig:nev2}.
+%
+As we can see, the general trends are
+similar as those without PU.
+%
+Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we also observe
+that the intermediate category is substantially degraded once PU effects
+are accounted for, the reason being  sizable
+a reduction in the number of signal
+events that are now assigned to this category.
+%
+This shows that the selection criteria
+of the intermediate category are less
+resilient against PU contamination,
+as opposed to the resolved and boosted selections.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{plots/nev2_SKPU80.pdf}
+\caption{\small Same as Fig.~\ref{fig:nev2} in the
+case of events with PU, for
+ $\la n_{\rm PU}\ra=80$ 
+  and SK subtraction.
+}
+\label{fig:nev2_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Fig.~\ref{fig:sb_mva_PU} we show the signal significance,
+$S/\sqrt{B}$, as well as the signal over background ratio,
+$S/B$, including now the effects of PU.
+%
+The corresponding results in the case without PU were shown in
+Fig.~\ref{fig:sb_mva}.
+%
+As can be seen, the MVA-driven enhancement is robust in the
+presence of PU.
+%
+While unsurprisingly there us a degradation as compared to the case wo PU,
+we still manage to achieve a signal significance of
+around $S/\sqrt{B}\simeq 2.5$ separately for the boosted and resolved
+categories.
+%
+On the other hand, the intermediate category becomes irrelevant.
+%
+We conclude that the qualitative conclusions drawn in
+Sect.~\ref{sec:mva} are robust in the presence
+of realistic PU effects.
+%
+Since no specific effort has been performed to
+optimize PU subtraction, for example by tuning the value
+of the patch length $a$ in {\tt SoftKiller}, we believe that
+there is
+still room for improvement in this respect.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/ssb_SKPU80.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb_SKPU80.pdf}
+\caption{\small 
+Same as Fig.~\ref{fig:sb_mva} in the
+case of events with PU, for
+ $\la n_{\rm PU}\ra=80$ 
+  and SK subtraction.
+}
+\label{fig:sb_mva_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+It is important to quantify which of the input variables
+to the MVA carry the highest discrimination power
+in the case of PU,
+and compare it with the corresponding
+results without PU.
+%
+We use the same estimator as in Sect.~\ref{sec:signalsignificance},
+namely the sum
+of the absolute value of all the weights connected to a given
+input neuron $i$, Eq.~(\ref{eq:totweight}).
+%
+The results for the resolved and boosted categories are shown
+on Fig.~\ref{fig:nnweights_PU}.
+%
+As we can see by comparing to the corresponding
+results without PU in Fig.~\ref{fig:nnweights}, 
+in the boosted category, the discrimination power of the invariant
+mass of Higgs candidates is decreased and that of the various substructure
+variables, in particular $C_2^{(\beta)}$ and
+$D^{(\beta)}$, is conversely
+increased.
+%
+This reflects the fact that these substructure variables are
+relatively robust against PU contamination.
+%
+In addition, also the $p_T$ distributions of the AK03
+subjets within the large-$R$
+jets carry important information.
+%
+In the case of the resolved category,  the highest
+values of the ANN weights without PU
+were found for the $p_T$ of the leading
+Higgs and for the Higgs invariant masses.
+%
+This is also true in the case with PU, but now the rapidity difference
+between the two Higgs candidates, $\Delta y_{hh}$ increases its
+importance, again reflecting that this variable is relatively
+insensitive to PU effects.
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.49\textwidth]{plots/res_wgthist_SKPU80.pdf}
+\includegraphics[width=0.49\textwidth]{plots/bst_wgthist_SKPU80.pdf}
+\vspace{-0.5cm}
+\caption{\small
+Same as Fig.~\ref{fig:nnweights} in the
+case of events with PU, for
+ $\la n_{\rm PU}\ra=80$ 
+  and SK subtraction.
+}
+\label{fig:nnweights_PU}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+At this point, we can finally combine the three categories, resolved,
+intermediate and boosted, and determine the overall signal
+significance taking into account all event topologies.
+%
+Adding in quadrature the signal significance from the three
+(exclusive) categories for the corresponding
+optimal value of $y_{\rm cut}$, our final combined result, accounting
+for PU effects, is
+\be
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0 \, ,
+\ee
+to be compared to the value $\lp S/\sqrt{B}\rp_{\rm tot} \simeq 8.5$
+that was obtained in the case without PU.
+%
+We conclude that, even when realistic PU effects are accounted
+for, at the HL-LHC the measurement of
+Higgs pair production in the $b\bar{b}b\bar{b}$ final state should be 
+well the threshold for evidence, and even meeting the
+requirement for discovery might be within reach.
+%
+
+In summary, in this section we have demonstrated the robustness
+of our results under the presence of PU conditions as those
+expected at the HL-LHC.
+%
+With a signal significance of $S/\sqrt{B}\sim 4$, is clear that
+the $b\bar{b}b\bar{b}$ final state can be used to claim evidence
+for Higgs pair production at the HL-LHC without the need
+to combine with any other final state.
+%
+Our analysis certainly contains
+room for improvement, in particular by means of a tailored
+study dedicated to optimize PU subtraction in this process.
+%
+It will be important now to quantify the precision of
+a extraction of the Higgs trilinear coupling $\lambda$ using
+the techniques presented here, but this is left for future work.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-07 paper/sec-analysis.tex
more work on analysis section

@@
 
-In section we describe our analysis strategy, and in particular
-the classification of each individual event into
-different categories according to its topology.
+In section we describe our analysis strategy.
 %
-First of all, we discuss the settings and nomenclature
-for jet clustering, and the strategy for $b$-tagging.
+First of all, we discuss the settings
+for jet clustering  and the strategy for $b$-tagging.
 %
-Then we discuss the categorisation of events between different
+Then we discuss the categorisation of events in different
 topologies and how to prioritise among them.
 %
-Finally, we motivate our choice of analysis cuts by comparing signal and background
-for representative kinematic distributions.
+We motivate our choice of analysis cuts by comparing signal and background
+for representative kinematical distributions.
+%
+Finally, we describe the simulation of PU and validate
+the PU subtraction strategy that we adopt.
 
@@
 %
-We will use different types of jet definitions:
+We use different types of jet definitions:
 \begin{itemize}
@@
   These jets are also constructed with the
-  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
+  anti-$k_T$ clustering algorithm, now using a $R=1.2$ radius.
   %
@@
   acceptance requirements, large-$R$ jets should also
-  satisfy the  BDRS mass-drop tagger (MDT)(~\cite{Butterworth:2008iy}
+  satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}
   conditions.
@@
 
-It is clear that
-optimisation of the $b$-tagging capabilities of the
-LHC experiments is an essential ingredient to improve
-the prospects for the observation of Higgs pair production in the
-$b\bar{b}b\bar{b}$ final state.
-%
-In this work, we adopt
+In this analysis we adopt
 a $b$-tagging strategy along the lines
@@
 though differences with respect to
-the corresponding CMS strategy~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}
-should not affect qualitatively our results.
+the corresponding CMS case~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}
+do not modify qualitatively our results.
 %
@@
   %
-  Only jets which contain at least one (light or charm)
+  Only jets that contain at least one (light or charm)
   constituent
-  with $p_T \ge 15$ GeV will lead to fake $b$-tags.
+  with $p_T \ge 15$ GeV can induce a fake $b$-tag.
 
-  We only attempt to $b$-tag only the four (two) hardest small-$R$ jets
+  We attempt to $b$-tag only the four (two) hardest small-$R$ jets
   in the resolved (intermediate) category.
@@
     Large-$R$ jets are $b$-tagged by
-    ghost-associating anti-$k_T$ $R=0.3$
+    ghost-associating anti-$k_T$ $R=0.3$ (AKT03)
     subjets to the original large-$R$
@@
     with the same criteria as the small-$R$ jets.
+    %
+     Therefore, a large-$R$ jet where the two leading
+    subjets have at least one $b$-quark will be tagged
+    with probability $f_b^2$.
 
@@
     signal significance due to combinatorics.
-
     %
-    Therefore, a large-$R$ jet where the two leading
-    subjets have at least one $b$-quark will be tagged
-    with probability $f_b^2$, if only one of the two leading
-    subjets has a $b$-quark, then the tagging probability is
-    $2f_bf_l$, and if none of the two subjets include $b$-quarks,
-    the mistag rate will be $f_l^2$.
+    The simulation of the fakes from light and charm jets
+    is the same as in the small-$R$ jets.
 
@@
 we aim to consistently combine the information from
-the three possible event topologies: boosted, intermediate and
+the three possible topologies: boosted, intermediate and
 resolved.
@@
 %
-An advantage of our approach is that the analysis strategy
-is robust under variations of
+An advantage of our approach
+the robustness under variations of
 the underlying production model of Higgs pairs is modified,
@@
 the degree of boost of the final state.
-%
+
 These three categories are defined as follows:
@@
   An event which
-  contains at least two large-$R$ jets, with the two leading
+  contains at least two large-$R$ jets, with the two leading jets
  being $b$-tagged.
  %
- Each of these two large-$R$ $b$-tagged jets are is this
- a candidate
+ Each of these two large-$R$, $b$-tagged, jets are 
+ thus candidates
  to contain the decay products of a Higgs boson.
@@
 
-  An event with only one large-$R$ $b$-tagged jet, which
+  An event with only one large-$R$, $b$-tagged, jet, which
   is assigned to be the leading Higgs candidate.
   %
-  In addition, we require at least two small-$R$ $b$-tagged jets,
+  In addition, we require at least two small-$R$, $b$-tagged, jets,
   which must be separated with respect to the large-$R$ jet
-  by $\Delta R\ge 1.0$.
+  by an angular distance of $\Delta R\ge 1.2$.
   %
 
-  The subleading Higgs boson candidate is then reconstructed
+  The subleading Higgs boson candidate is reconstructed
   by selecting the two $b$-tagged small-$R$ jets that minimize the difference
   between the invariant mass of the large-$R$ jet
-  with the invariant mass of the dijet obtained
+  with that of the dijet obtained
   from the sum of the two small-$R$ jets.
@@
 its invariant mass is required to lie within a fixed window
-around the nominal Higgs boson mass.
+around the nominal Higgs boson mass~\cite{Aad:2015zhl}.
 %
@@
 analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
-for this choice is that the MVA will take care of the optimisation of these
-and other cuts that are not explicitly performed.
+for this choice is that the MVA will take care of the optimisation of this,
+as well as of other cuts that are not explicitly performed.
 %
@@
 
- This is achieved as follows.
+ This has been achieved as follows.
  %
@@
 %
-Therefore for the final analysis we turn to an exclusive approach:
-if an event satisfies the boosted requirements, it is kept for
-these category, else we check if it suits the intermediate
+Therefore, for the final analysis, we turn to an exclusive approach:
+if an event satisfies the boosted requirements, it is assigned to
+this category, else we check if it suits the intermediate
 requirements, and failing also this, the event is attempted to
@@
 %
-The resulting exclusive event samples are then separately processes
-through the MVA.
-%
-This allows a consistent combination
+The resulting exclusive event samples are then separately processed
+through the MVA, allowing a consistent combination
 of the significance of the three event categories.
 
-\subsection{Optimisation of kinematical cuts}
+\subsection{Motivation for kinematical cuts}
 
 We now motivate the values of
-kinematical cuts applied to the different categories.
+kinematical cuts applied to the different categories, 
+comparing representative kinematic distributions between
+signal and background events.
 %
-These cuts have been separately
-optimised in an inclusive analysis, since it is only
-once we have determined
-the dominant category that the analysis is made exclusive.
+First to all we present results without PU, and in the next
+subsection we discuss what is the impact of PU
+on the description of the various kinematical
+distributions.
 %
-Here we show the various kinematic distributions 
-before the corresponding cut has been applied.
+In the following, all
+distributions will be normalized to their total integral.
+
 %
-For illustration purposes,
-only a representative subset of
-all available kinematic distributions will be shown here.
-%
-For simplicity,
-we restrict to the discussion of the
-kinematic distributions of the boosted
-and resolved categories.
-
-First of all,
+To begin with,
 in Fig.~\ref{fig:cutplots1} we show
@@
   %
-  Distributions have been normalized to their total integral.
-  %
   We see that the background distribution
   falls off rather steeply than the signal at large $p_T$
-  values, therefore
-  providing evidence that exploiting the boosted region will be
-  advantageous to enhance the signal over background ratio.
+  for the two Higgs candidates.
   %
-  This is true both for the leading and the subleading
-  large-$R$ jets.
+  On the other hand, the cut in $p_T$ cannot be too strong to avoid
+  a substantial degradation of signal selection efficiency,
+  specially taking into account the subleading large-$R$ jet.
   %
-  These distributions justify our choice of $p_T \ge 200$ GeV
-  for the large-$R$ jets in the boosted category.
+  This comparison justifies the cut of $p_T \ge 200$ GeV
+  for the large-$R$ jets that we impose in the boosted category.
 
@@
 \begin{center}
- \includegraphics[width=0.48\textwidth]{plots/pt_H0_boost_C1.pdf}
- \includegraphics[width=0.48\textwidth]{plots/pt_H1_boost_C1.pdf}
-\caption{\small  The $p_T$ distribution of the
+ \includegraphics[width=0.48\textwidth]{plots/pt_H0_bst_C1d_noPU.pdf}
+ \includegraphics[width=0.48\textwidth]{plots/pt_H1_bst_C1d_noPU.pdf}
+\caption{\small  Comparison of the $p_T$ distributions of the
   leading (left plot) and
-  subleading (right plot) large-$R$ jets in the boosted category.
+  subleading (right plot) large-$R$ jets in the boosted category,
+  in in signal and background events.
   %
-  We comparing
-  the shapes of the distribution in signal and background events,
-  where both
-  distributions have been normalized to their total integral.
+  Distributions have been normalized to unity.
 }
@@
 
-In the boosted category we require the two
+Also in the boosted category we require the two
 leading subjets of the large-$R$ jet to be relatively
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{plots/m_HH_res_C1.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/m_HH_boost_C1.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/m_HH_C2_res_noPU.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/m_HH_C2_bst_noPU.pdf}
   \caption{\small Left plot: the invariant mass distribution of the Higgs
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{plots/pt_HH_res_C1.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/pt_HH_boost_C1.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/pt_HH_C2_res_noPU.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/pt_HH_C2_bst_noPU.pdf}
   \caption{\small Same as Fig.~\ref{fig:mhh} for the transverse momentum
@@
 \subsection{PU subtraction with {\tt SoftKiller}}
+\label{sec:pileup}
 

### 2015-12-07 paper/paperscripts/plotHist_mHH_res_noPU.py

@@ -10,13 +10,13 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "m_HH_C2_bst_noPU"
+outfile = "m_HH_C2_res_noPU"
 
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_HH_boost_C1e.dat")
-datafiles.append("../plotdata/results_noPU/background/histo_m_HH_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_HH_res_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_m_HH_res_C1e.dat")
 
 # Plot labels
 plotnames.append("Signal")
@@ -52,7 +52,7 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([400,600])
+ax.set_xlim([200,600])
 ax.set_ylim([1e-4,0.02])
 
 for idat in xrange(0,len(datafiles)):

### 2015-12-07 paper/paperscripts/plotHist_ptHH_bst_noPU.py

@@ -10,20 +10,20 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "m_HH_C2_bst_noPU"
+outfile = "pt_HH_C2_bst_noPU"
 
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_HH_boost_C1e.dat")
-datafiles.append("../plotdata/results_noPU/background/histo_m_HH_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_HH_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_pt_HH_boost_C1e.dat")
 
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = "di-Higgs $m_{hh}$ (GeV)"
+xLabel = "di-Higgs $p^{hh}_{T}$ (GeV)"
 yLabel = "a. u."
 
 # Log axes
@@ -52,8 +52,8 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([400,600])
-ax.set_ylim([1e-4,0.02])
+ax.set_xlim([0,250])
+ax.set_ylim([1e-3,0.02])
 
 for idat in xrange(0,len(datafiles)):
 

### 2015-12-07 paper/paperscripts/plotHist_pt_H0_bst_noPU.py

@@ -10,20 +10,20 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "m_HH_C2_bst_noPU"
+outfile = "pt_H0_bst_C1d_noPU"
 
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_HH_boost_C1e.dat")
-datafiles.append("../plotdata/results_noPU/background/histo_m_HH_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_H0_boost_C1d.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_pt_H0_boost_C1d.dat")
 
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = "di-Higgs $m_{hh}$ (GeV)"
+xLabel = "Leading Higgs Candidate $p^{h}_T$ (GeV)"
 yLabel = "a. u."
 
 # Log axes
@@ -52,7 +52,7 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([400,600])
+ax.set_xlim([190,600])
 ax.set_ylim([1e-4,0.02])
 
 for idat in xrange(0,len(datafiles)):

### 2015-12-07 paper/sec-analysis.tex
more work in the analysis section

@@
 
-Also in the boosted category we require the two
-leading subjets of the large-$R$ jet to be relatively
-hard, in particular that should satisfy $p_T \ge $ 50 GeV.
+Another selection requirement for the boosted category is that the two
+leading AKT03 subjets of the large-$R$ jet must be relatively hard,
+in particular they should satisfy $p_T \ge $ 50 GeV.
 %
@@
 we show the distribution in $p_T$ of the leading
-and subleading sub-jets in the leading large-$R$ jet in events
-of the boosted category.
+and subleading AKT03 subjets in the subleading large-$R$ jet in events
+corresponding to the boosted category.
 %
 It is clear from the comparison that the subjet $p_T$ spectrum is
-relatively harder in the signal with respect to the background,
-motivating our choice of subjet $p_T$ cut.
+relatively harder in the signal with respect to the background.
+%
+On the other hand, considering the subleading AKT03 subjet, one needs that
+the cut in its  $p_T$ should not bee too large, to keep most of the signal events.
+%
+So as in the case of the $p_T$ cut in the large-$R$ jets, also in this case there
+is a compromise between suppressing backgrounds but keeping a large fraction of
+signal events.
 
@@
 \begin{center}
- \includegraphics[width=0.48\textwidth]{plots/pt_leadSJ_fj1_noPU.pdf}
- \includegraphics[width=0.48\textwidth]{plots/pt_subleadSJ_fj1_noPU.pdf}
-\caption{\small  The $p_T$ distribution of the
-  leading (left plot) and
-  subleading (right plot) AKT03 subjets within the leading
-  Higgs candidate in the boosted category.
-  %
-  We comparing
-  the shapes of the distribution in signal and background events,
-  where both
-  distributions have been normalized to their total integral.
+ \includegraphics[width=0.48\textwidth]{plots/pt_leadSJ_fj2_noPU.pdf}
+ \includegraphics[width=0.48\textwidth]{plots/pt_subleadSJ_fj2_noPU.pdf}
+ \caption{\small  Same as Fig.~\ref{fig:cutplots1} for the two leading AKT03
+   subjets in the subleading Higgs candidate large-$R$ jet.
 }
@@
 
-In the resolved category,
-it is important to understand the $p_T$ distribution
-of the four leading small-$R$ jets of the event.
+Turning to the resolved category, an important aspect to account
+in the corresponding selection
+cuts is the fact that the $p_T$ distribution
+of the four leading small-$R$ jets of the event can be relatively soft,
+specially for the subleading jets.
 %
-As noted in~\cite{deLima:2014dta}
-given that in general the boost from the Higgs decays is moderate,
-the two subleading jets might be not too hard, and thus it
-should be important to ensure that our $p_T^{\rm min}$ cut
-is not too strong.
+As noted in~\cite{deLima:2014dta}, this is a consequence of the fact
+that in general the boost from the Higgs decays is moderate.
 %
-This also has important implications for the experimental
-trigger requirements in this category.
+These considerations lead to the requirement that the $p_T$ cut
+for the small-$R$ jets cannot be too strong.
 %
@@
 we show the distribution in $p_T$ of the four leading
-small-$R$ jets in signal and background events.
+small-$R$ jets in signal and background events: we observe that both
+distributions are peaked at $p_T \le 50$ GeV, with the signal distribution
+eventually becoming dominant at large $p_T$.
 %
-We see that the third and four leading jets are relatively soft.
+The feasibility to being able to trigger on four small-$R$ jets with a relatively
+soft $p_T$ distribution is one of the experimental challenges of
+exploiting the resolved category in this final state.
 %
-Therefore, we can conclude that....
+In  Fig.~\ref{fig:cutplots23} we also show the
+rapidity distribution of the the small-$R$
+jets in the resolved category: as well know, the production
+is mostly central (more from signal since backgrounds are dominated by
+QCD $t$-channel exchange) and thus the standard rapidity cuts
+are relatively harmless.
 
@@
  \includegraphics[width=0.48\textwidth]{plots/eta_smallRjets_res_noPU.pdf}
- \caption{\small Same as Fig.~\ref{fig:cutplots23}, now for the
+ \caption{\small Same as Fig.~\ref{fig:cutplots1}, now for the
    $p_T$ and rapidity distributions of the small-$R$
-   jets in the boosted category.
+   jets corresponding to the resolved selection.
 }
@@
 
-Another important distribution is the rapidity of the large-$R$
-(in the boosted category) and the small-$R$ (in the resolved
-category) jets.
+One of the selection cuts with highest discrimination power is the requirement
+that the invariant mass of the Higgs candidate (di)jets must lie within a window
+around the nominal Higgs value.
 %
-We want to understand by how much the signal efficiency is reduced
-by the restriction of the central region, and how would
-the signal yield be enhanced if tracking could be extended
-to forward rapidities in ATLAS and CMS.
-%
-Also, it is useful to show the distribution in rapidity of the
-individual jets in the resolved category.
-%
-
-Next, in Fig.~\ref{fig:mHHinv} we show the invariant mass
+In Fig.~\ref{fig:mHHinv} we show the invariant mass
 of the leading reconstructed Higgs candidates, before the Higgs mass window
 cut Eq.~(\ref{higgsmasswindow})
-  is applied, for the resolved and boosted categories.
+  is applied, both for the resolved and boosted categories.
 %
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/m_H0_boost_C1.pdf}
-  \caption{\small The invariant mass distribution of the leading
-    Higgs candidates on the resolved (left plot) and boosted (right
-    plot) categories. 
+  \includegraphics[width=0.48\textwidth]{plots/m_H0_res_C1d_noPU.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/m_H0_bst_C1d_noPU.pdf}
+  \caption{\small Same as   Fig.~\ref{fig:cutplots1} for the invariant
+    mass distribution of the leading Higgs candidates in the resolved
+    (left plot) and boosted (right plot) selections.
 }

### 2015-12-07 paper/paperscripts/plotHist_eta_smallRjets_res.py

@@ -24,12 +24,12 @@ plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = "Small-R jet rapidity"
+xLabel = "Small-$R$ jet rapidity"
 yLabel = "a. u."
 
 # Log axes
 xLog = False
-yLog = True
+yLog = False
 
 # Normalise histograms
 normalise = True
@@ -53,8 +53,8 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([-4,4])
-ax.set_ylim([1e-2,1])
+ax.set_xlim([-3.4,3.4])
+ax.set_ylim([0,0.4])
 
 for idat in xrange(0,len(datafiles)):
 
@@ -125,7 +125,7 @@ ax.xaxis.grid(True)
 ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.32,0.93,"Resolved category", fontsize=20)
+fig.text(0.26,0.93,"Resolved category, $n_{PU}=0$", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-07 paper/paperscripts/plotHist_pt_subleadSJ_fj1_bst.py

@@ -10,22 +10,21 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "pt_smallRjets_noPU"
+outfile = "pt_subleadSJ_fj2_noPU"
 
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_smallR_res_C1a.dat")
-datafiles.append("../plotdata/results_noPU/background/histo_pt_smallR_res_C1a.dat")
-
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_subleadSJ_fj2_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_pt_subleadSJ_fj2_boost_C1e.dat")
 
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = "Subleading AKT03 subjet $p_{T}$ in Higgs candidates (GeV)"
-yLabel = "A. U."
+xLabel = "Leading AKT03 subjet $p_{T}$ for subleading large-$R$ jet (GeV)"
+yLabel = "a. u."
 
 # Log axes
 xLog = False
@@ -53,7 +52,7 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([31,500])
+ax.set_xlim([33,400])
 ax.set_ylim([1e-4,0.05])
 
 for idat in xrange(0,len(datafiles)):
@@ -125,7 +124,7 @@ ax.xaxis.grid(True)
 ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.23,0.93,"Boosted category", fontsize=20)
+fig.text(0.29,0.93,"Boosted category, $n_{PU}=0$", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-07 paper/HH4b.tex
Divided results of PU section among independent sections
Implemented comments from Nathan

@@
 \usepackage{natbib}
+\usepackage{multirow}
 
@@
 \bibliographystyle{JHEP}
-\usepackage{multirow}
 
@@
   %
-   By combining the contribution from the boosted, intermediate and resolved
+  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
+  combining the contributions from the boosted, intermediate and resolved
   topologies we obtain a signal significance of $S/\sqrt{B}\simeq 4$.
@@
   that the $b\bar{b}b\bar{b}$ channel
-  should be enough claim evidence for
-  the observation of double Higgs production
+alone should allow the observation of double Higgs production
   at the HL-LHC.
@@
 \input{sec-mva}
-\input{sec-pileup}
 \input{sec-conclusions}

### 2015-12-07 paper/sec-analysis.tex
Implemented comments from Nathan

@@
 
-\subsection{Motivation for kinematical cuts}
+\subsection{Motivation for basic kinematical cuts}
 
@@
 %
-We have explored two scenarios for the amount of PU expected
-at the HL-LHC, one with a mean number of
+We have explored two scenarios for the impact
+of PU in our analysis,
+one with a mean number of
 PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another

### 2015-12-07 paper/sec-intro.tex
Divided results of PU section among independent sections
Implemented comments from Nathan

--- 2015-11-30 paper/sec-intro.tex
@@
 %
-It is also sensitive to the underlying strength of the Higgs interactions
+It can also probe the underlying strength of the Higgs interactions
 at high energies, and can be used to test the composite nature of the 
@@
 %
-In addition, Higgs pair production will also be a central process at
+In addition, Higgs pair production will also be of
+crucial relevance at
 any future high-energy 
@@
 
-As in the case of single Higgs production,
-in the SM the dominant mechanism for the production of a pair of Higgs bosons at the LHC is 
-gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and references therein), analogously to single
-Higgs production~\cite{Dittmaier:2012vm}.
+Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
+in the SM the dominant mechanism for the production of a pair of
+Higgs bosons at the LHC is 
+gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and
+references therein).
 %
-For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the next-to-next-to-leading order (NNLO)
+For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the
+next-to-next-to-leading order (NNLO)
 total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
@@
 In addition to the gluon-fusion production mode, Higgs pairs
-can be also produced in the vector-boson fusion
+can also be produced in the vector-boson fusion
 channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
@@
 %
-These studies are
-based on exploiting the differences between signal and background
-using techniques that account for a large number of kinematic
-variables, Boosted Decision Trees
-and Shower Deconstruction~\cite{Soper:2011cr} respectively.
-%
 While irreducible backgrounds, such as $4b$ and
-$t\bar{t}$, are included, the contribution
+$t\bar{t}$, are included in these analysis, the contribution
 from reducible processes, such as $bbjj$ and
@@
 As will show, this approximation is not justified since, both due to
-combinatorics and to $b$-quark radiation in the shower, the
+combinatorics and to $b$-quark radiation in the
+parton shower, the
 contribution of the $2b2j$ and $4j$ backgrounds can become comparable or even larger
@@
  Our strategy is based on a combination of traditional cut-based
- methods with modern multivariate analysis (MVA),
+ methods with multivariate analysis (MVA),
  leading to a substantial
@@
   We account for  all relevant
-  backgrounds, including the contribution from light jet fakes.
+  backgrounds, including the contribution from mistags of
+  light and charm jets.
   %
   We also model the impact of the pile-up (PU) effects expected at the
-  HL-LHC by means of modern PU subtraction techniques.
+  HL-LHC by means of the {\tt SoftKiller} PU subtraction
+  method~\cite{Cacciari:2014gra}.
   %
-  By combining the contribution from the boosted, intermediate and resolved
-  topologies we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
+  By combining the contribution from
+ the different event categories
+  we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
   for $\mathcal{L}_{\rm int}$=3000 fb$^{-1}$.
@@
 conditions expected at the HL-LHC is illustrated in
- Sect.~\ref{sec:pileup}.
+....
 %

### 2015-12-07 paper/sec-mcsamples.tex
yet more work on the paper
Implemented comments from Nathan

@@
 exact form factors for the top triangle and box loops at leading
-order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
-loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
+order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that
+  since recently it is possible to compute also
+  loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of
+  using specific
 models~\cite{Hirschi:2015iia}.}
@@
 %
-The Higgs boson parameters are also the same in the default model,
+The Higgs boson parameters are also the same as in the default model,
 in particular we use $m_h=125$ GeV, consistent with the latest
@@
 The value of the Higgs trilinear coupling $\lambda$ is set to its
-Standard Model value.
+Standard Model value, $\lambda=m_h^2/2v^2$, with $m_h=125$ GeV
+the Higgs boson mass and $v\simeq 246$ GeV the Higgs vacuum expectation
+value (vev).
 %
@@
 Therefore, to achieve the correct higher-order value of the  integrated cross-section, we rescale our LO signal sample to match the
-NNLO+NNLO inclusive cross-section.
+NNLO+NNLL
+inclusive cross-section.
 %
@@
 in Table~\ref{tab:samples}.
-
 %
@@
 %
-We switched off hadronisation, since this allows a more transparent
-modeling of our strategy for
-$b$-tagging.
-%
-A complete simulation of $b$-tagging at the hadron level is difficult
-to achieve without a full
-detector simulator, which is beyond the scope of this work.
 
@@
 %
-In this case,
-we have used a value of the top quark mass of $m_t=173.2$ GeV.
-%
 Leptonic decays of top quarks can be removed by requiring
 a lepton veto, and thus are not included here.
+%
+Single Higgs production processes, such as $Z(\to b\bar{b})h(\to b\bar{b})$
+and $t\bar{t}h(\to b\bar{b})$, and electroweak backgrounds, such $Z(\to b\bar{b})b\bar{b}$,
+are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
+and thus not included in the present analysis.
+%
 
@@
 
-At the generation level, the following mild
+At the generation level, the following loose selection 
 cuts are applied to
@@
 %
-The $bbjj$ cross-section is around factor 200 as compared to the
+The $bbjj$ cross-section is more than two orders
+of magnitude larger as compared to the
 $4b$ result, however, as we will show,
@@
 
-In this work, we simulate the finite momentum resolution of the ATLAS and CMS
+In this work, we simulate the finite energy resolution of the ATLAS and CMS
 hadronic calorimeters by applying a Gaussian smearing of the transverse
@@
     %
-    In the case of PU, the mass resolution is increased to around 11\%, corresponding to
+    In the case of PU, the mass resolution is degraded down to
+    around 11\%, corresponding to 
     14 GeV.

### 2015-12-07 paper/sec-mva.tex
Implemented comments from Nathan

@@
 for a probabilistic
-interpretation of the neural-network output, including in the final layer.
+interpretation of the neural-network output.
 %
@@
   \caption{\small Architecture of the Artificial
-    Neural Network
+    Neural Network (ANN)
     used for the analysis of the
@@
  %
- We have also verified that using a cross-validation stopping
+
+ In order to avoid overfitting,
+ we have used a cross-validation stopping
  criterion, in particular, the same one as
@@
 
-  The ratio of energy correlation functions $C_2^{\beta}$ is defined as
+  The ratio of energy correlation functions $C_2^{(\beta)}$ is defined as
   \be
@@
 %
-Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the resolved analysis,
-17 for the semi-resolved, and 21 for the boosted category.
+Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the
+resolved analysis,
+17 for the intermediate,
+and 21 for the boosted category.
 %
@@
 %
-This is one of the main advantages of ANNs in this context: they are inherently redundant, so
-adding additional information, even if carries very little weight, will never degrade
-the classification power of the MVA.
+This is one of the main advantages of ANNs in this context: they are
+inherently redundant, so
+adding additional information, even if carries very little weight,
+should not degrade
+the classification power of the MVA (other than making the GA
+minimization less efficient).
 
@@
 %
-The usefulness of ROC curves is that they allow to determine and
-optimal cut value that removes enough background without degrading too much the signal efficiency.
-%
 Another important requirement on the value of $y_{\rm cut}$ is that
@@
 we are still left
-with around 100 events at the HL-LHC, which is a reasonable number,
+with around 100 events at the HL-LHC, 
 which the background being reduced substantially to around
@@
   \centering
-  \small
-  \begin{tabular}{c|c|c|c||c|c|c|c}
-    \hline
-    \multicolumn{8}{c}{Boosted category}\\
-    \hline
-    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.82$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-      1070   &  $7.6\cdot 10^5$    &  1.2    &  $1.4\cdot 10^{-3}$  & 790 & $2.2\cdot 10^4$ & 5.4  & 0.034\\
-      \hline
-      \multicolumn{8}{c}{$\quad$}\\
-    \hline
-    \multicolumn{8}{c}{Intermediate category}\\
-    \hline
-    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.80$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-      670   &   $5.3\cdot 10^5$   &   0.9   &  $1.2\cdot 10^{-3}$ & 360  & $5.5\cdot 10^3$ & 4.8  & $0.06$ \\
-      \hline
-      \multicolumn{8}{c}{$\quad$}\\
-    \hline
-    \multicolumn{8}{c}{Resolved category}\\
-    \hline
-      \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.65$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-    $3700$   &   $1.5\cdot 10^{7}$   & 1.0     &  $3\cdot 10^{-4}$   & $1.3\cdot 10^{3}$ &
-    $8.3\cdot 10^{4}$  & 4.5 & 0.01 \\
+  \begin{tabular}{|c|l|c|c|c|c|}
+    \hline
+    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
+    \hline
+    \hline
+    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1070 & $7.6\cdot 10^5$  & 1.2  & $1.4\cdot 10^{-3}$  \\
+    &  $y_{\rm cut}=0.82$ & 790  & $2.2\cdot 10^4$   & 5.4  & 0.034 \\
+    \hline
+    \hline
+    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  & 670   & $5.3\cdot 10^5$
+    & 0.9 & $1.2\cdot 10^{-3}$ \\
+    &  $y_{\rm cut}=0.80$ & 360  & $5.5\cdot 10^3$  & 4.8 & 0.06\\
+    \hline
+    \hline
+      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  & 3700 &  $1.5\cdot 10^{7}$ &  1.0 &$3\cdot 10^{-4}$ \\
+    &  $y_{\rm cut}=0.65$ & 1300  & $8.3\cdot 10^{4}$ & 4.5 & 0.01 \\
     \hline
@@
   \caption{\small Post-MVA results, for the optimal value of the
-    ANN discriminant, in the three categories, compared with the
-    result of the cut-based analysis.
+    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
+    corresponding
+    pre-MVA results $y_{\rm cut}=0$.
     %
@@
     background events
-    at the HL-LHC, as well as the signal significance $S/\sqrt{B}$ and
+    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$,
+    the signal significance $S/\sqrt{B}$ and
     the signal over background ratio $S/B$.
     %
-    The value of the ANN output cut $y_{\rm cut}$
-    is optimised separately in the
-    three categories.
-    %
-    The $y_{\rm cut}=0$ value corresponds to row C2 in Table~\ref{tab:cutflow_noPU_1}.
+    The pre-MVA results ($y_{\rm cut}=0$) corresponds to row C2 in
+    Table~\ref{tab:cutflow_noPU_1}.
     \label{table:cutflowMVA}
@@
 %
-Therefore, thanks to the MVA, we predict that one should be able
-to find evidence for the production of Higgs boson pairs
-at the HL-LHC using the $4b$ channel alone.
-
 Another important benefit of the MVA applied to the boosted
@@
 
-In Fig.~\ref{fig:nnresponse_PU} we present
-the distribution of the ANN output for the
-signal and background MC events in the boosted and resolved categories --
-the analogous comparison in the case without PU was shown
-in Fig.~\ref{fig:nnresponse}.
-%
-We observe that the clear MVA discrimination
-between signal and background events in the two categories is robust
-when PU is included.
-%
-However, by comparing with Fig.~\ref{fig:nnresponse}, we see
-that some of the most distinguishing features that separate signal
-and background in the ANN output are reduced when PU effects
-are included.
-%
-For instance, in the boosted category, there is a trend of the distribution
-for signal events to move towards smaller values of the
-ANN discriminant.
-%
-This in turn will entail a reduction of the signal significance as
-compared to the case without PU.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-  \begin{center}
-\includegraphics[width=0.49\textwidth]{plots/Resolved_disc_SKPU80.pdf}
-\includegraphics[width=0.49\textwidth]{plots/Boosted_disc_SKPU80.pdf}
-\caption{\small Same as Fig.~\ref{fig:nnresponse},
-  this time with $\la n_{\rm PU}\ra=80$ PU events per bunch crossing
-  and SK subtraction, for the resolved (left) and boosted
-  (right) categories.
-  %
-  The corresponding comparison without PU was shown in
-  Fig.~\ref{fig:nnresponse}.
-}
-\label{fig:nnresponse_PU}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
 In Table~\ref{table:cutflowMVA_PU}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[t]
   \centering
-  \small
-  \begin{tabular}{c|c|c|c||c|c|c|c}
-    \hline
-    \multicolumn{8}{c}{Boosted category, $\la n_{\rm PU}\ra=80$+SK}\\
-    \hline
-     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.84$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-    362  &  $1.4\cdot 10^6$     & 0.31       &  $3\cdot 10^{-4}$ &
-    248     &   7250             &  2.9       & 0.034 \\
-    \hline
-       \multicolumn{8}{c}{$\quad$}\\
-    \hline
-    \multicolumn{8}{c}{Intermediate category,  $\la n_{\rm PU}\ra=80$+SK}\\
-    \hline
-    \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.72$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-    146  &    $9\cdot 10^5$   & 0.15        &  $2\cdot 10^{-4}$      &
-  53  &  2547        & 1.1        &  0.02 \\
-  \hline
-  \multicolumn{8}{c}{$\quad$}\\
-    \hline
-    \multicolumn{8}{c}{Resolved category,  $\la n_{\rm PU}\ra=80$+SK}\\
-    \hline
-     \multicolumn{4}{c||}{no MVA cut} & \multicolumn{4}{c}{optimal MVA cut}\\
-    \multicolumn{4}{c||}{$y_{\rm cut}=0$} & \multicolumn{4}{c}{$y_{\rm cut}=0.49$}\\
-    \hline
-    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$
-    & \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$\\
-        Signal & Back   &     &   &  Signal & Back   &     &    \\
-    \hline
-  1123  &    $8.5\cdot 10^6$   & 0.25       &  $1.3\cdot 10^{-4}$       &
-  432  &  $3\cdot 10^4$        &   2.5      & 0.15 \\
+  \begin{tabular}{|c|l|c|c|c|c|}
+    \hline
+    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
+    \hline
+    \hline
+    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 360   &  $1.4\cdot 10^6$ & 0.31   &
+     $3\cdot 10^{-4}$  \\
+    &  $y_{\rm cut}=0.82$ &  250 & 7300  & 2.9    & 0.034  \\
+    \hline
+    \hline
+    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  150  & $9\cdot 10^5$    & 0.15    &
+     $2\cdot 10^{-4}$ \\
+    &  $y_{\rm cut}=0.80$ & 50 & 2600  &  1.1   & 0.02 \\
+    \hline
+    \hline
+    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  1100  & $8.5\cdot 10^6$
+    & 0.25    &  $1.3\cdot 10^{-4}$  \\
+    &  $y_{\rm cut}=0.65$ & 430  & $3\cdot 10^4$  &  2.5   & 0.15  \\
     \hline
       \end{tabular}
-  \caption{\small Same as Table~\ref{table:cutflowMVA} in the case
+  \caption{\small Same as Table~\ref{table:cutflowMVA}, now for the case
     of PU+SK, with $\la n_{\rm PU}\ra=80$.
@@
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-12-07 paper/sec-results.tex
Implemented comments from Nathan

@@
 Now, after $b$-tagging, the naive expectation would
-be a suppression of the former by a factor $f_l^2 =10^{-4}$,
+be a suppression of the former by a factor $f_l^2/f_b^2 =3\cdot 10^{-4}$,
 since a total of four $b$-tags are required to classify the
@@
 it comparable to the $4b$ component.
+
+We can make this statement more quantitative in the following way.
+%
+To first approximation, and neglecting the contribution from charm mistags, the
+overall efficiency of the $b$-tagging requirements in the resolved category will be
+given by the following expression:
+\be
+\label{btaggingeff}
+{\rm EFF}_{\rm b-tag}\simeq \sum_{j=0}^{4}n^{\rm (b-jet)}_j\cdot f_b^{j}\cdot f_l^{4-j} \, ,
+\ee
+with $n^{\rm (b-jet)}_j$ the fraction of events, satisfying all the selection cuts,
+where $j$ jets, out of the leading four jets, of the event contain $b$ quarks (with $p_T^b\ge 15$
+GeV).
+%
+Similar expressions can be derived to the boosted and intermediate categories.
+%
+The naive expectation is that all events in the $4b$ sample have $n^{\rm (b-jet)}_4\simeq 1$
+and $n^{\rm (b-jet)}_j\simeq 0$ for $j\ne 4$, while the events in the $2b2j$ sample
+should have $n^{\rm (b-jet)}_2\simeq 1$ and zero otherwise.
+%
+This leads to a ratio of overall $b$-tagging selection efficiencies
+\be
+\label{eq:naive}
+\frac{ {\rm EFF}_{\rm b-tag} \lc 2b2j \rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}
+  \simeq
+ \lp \frac{f_l}{f_b}\rp^2 \simeq 1.6\cdot 10^{-4} \, .
+\ee
+However, the actual situation is more complicated.
+%
+First of all, we will have a non-negligible fractions $n^{\rm (b-jet)}_j$
+with $j=3,4$ also in the $2b2j$ sample, due to $b$-quark pair radiation
+during the shower.
+%
+Secondly, not all events in the $4b$ sample will lead to four small-$R$ $b$-jets,
+due to a combination of selection cuts and
+parton shower effects.
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \small
+  \begin{tabular}{|c|c|c|c|c|c|c|c|}
+    \hline
+  \multicolumn{2}{|c|}{}   &  $n^{\rm (b-jet)}_0$  &  $n^{\rm (b-jet)}_1$  &  $n^{\rm (b-jet)}_2$  & $n^{\rm (b-jet)}_3$ &
+    $n^{\rm (b-jet)}_4$ & ${\rm EFF}_{\rm b-tag}$ \\
+    \hline
+    \hline
+    Signal  &  $hh\to 4b$  &   0.1\%    & 3\%     &  25\%     & 53\%     & 20\%      & 8.5\%  \\
+    \hline
+    \multirow{3}{*}{Background}  &  QCD $4b$  & 1\%      &  8\%    &   27\%   &  44\%     & 20\%       &  8.4\% \\
+     &  QCD $2b2j$  &   9\%    & 42\%     &  49\%    & 1\%     &  0.1\%     & 0.04\%  \\
+    &  QCD $4j$  &   96\%    &  3.5\%     & 0.5\%     &  0.01\%    & $3\cdot 10^{-4}$\%      &
+    $2\cdot 10^{-4}$\%\\
+    \hline
+  \end{tabular}
+  \caption{\small
+    The relative fractions  $n^{\rm (b-jet)}_j$ of events for the resolved selection
+    for which, out of the four leading small-$R$ jets, $j$ jets
+    contain at least one $b$-quark with $p_T^b\ge 15$ GeV,
+    both for signal events and for the three QCD background samples.
+    %
+    The last column indicates the overall predicted
+    selection efficiency of the $b$-tagging procedure,
+    Eq.~(\ref{btaggingeff})
+    \label{tab:btaggingcheck}
+  }
+  \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Table~\ref{tab:btaggingcheck} we collect
+the values of $n^{\rm (b-jet)}_j$ for the signal and the three QCD background samples.
+%
+Therefore, we find that, rather than the estimate Eq.~(\ref{eq:naive}),
+the correct ratio of $b$-tagging selection efficiencies is instead
+\be
+\frac{{\rm EFF}_{\rm b-tag} \lc 2b2j\rc}{{\rm EFF}_{\rm b-tag} \lc 4b\rc}=
+  \frac{0.04\%}{8.4\%} \simeq 5\cdot 10^{-3} \, .
+  \ee
+  This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
+  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
+    %
+    This explains why the $2b2j$ contribution cannot be neglected as compared
+    to the irreducible $4b$ component of the QCD background.
+    %
+    A similar calculation from the numbers of Table~\ref{tab:btaggingcheck} shows
+    that, on the other hand, the $4j$ component of the background can safely
+    be neglected.
+
+%

### 2015-12-07 paper/HH4b.tex
more work on the paper

--- 2015-11-30 paper/HH4b.tex
@@
   Double Higgs production provides a unique window to the electroweak
-  symmetry breaking mechanism, and in particular it allows
-  to access the Higgs trilinear coupling.
+  symmetry breaking mechanism due to its sensitivity
+  to the Higgs trilinear coupling.
   %
-  In this work we study the feasibility of the observation of the production of
-  Higgs boson pairs at the High-Luminosity LHC (HL-LHC) in the
-  $b\bar{b}b\bar{b}$ final state.
-  %
-  While the signal in this channel
-  is enhanced by the large branching fraction of Higgs bosons to
-  $b\bar{b}$ pairs, the measurement is  challenging due to the
-  overwhelming QCD multijet background.
+  In this work, we study the feasibility of a measurement of
+  Higgs pair production in the
+  $b\bar{b}b\bar{b}$ final state at the LHC.
   %
   Our analysis is based on a combination of traditional cut-based
-  methods with modern multivariate techniques, which lead to a substantial
-  enhacement of the signal discrimination.
+  methods with state-of-the-art
+  multivariate techniques.
   %
   We account for  all relevant
-  backgrounds, including the contribution from light jet fakes that is found
-  to be as important or even dominant over the irreducible $4b$ QCD background.
+  backgrounds, including the contribution from light and charm
+  jet mistags that is found to be comparable
+  to the irreducible $4b$ QCD background.
   %
-  We demonstrate the robustness of our analysis under realistic
-  pile-up conditions expected at the HL-LHC.
+  We demonstrate the robustness of our analysis in a high pile-up
+  environment.
   %
-   By combining the contribution from the boosted, intermediate and resolved
-  topologies we obtain a signal significance of $S/\sqrt{B}\simeq 4$.
+  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
+  an overall signal significance of  $S/\sqrt{B}\simeq 4$ is obtained.
   %
@@
   that the $b\bar{b}b\bar{b}$ channel
-  should be enough claim evidence for
-  the observation of double Higgs production
-  at the HL-LHC.
+alone should allow the observation of double Higgs production
+  at the High Luminosity LHC.
 }

### 2015-12-07 paper/sec-analysis.tex
more work on the paper

@@
 cut Eq.~(\ref{higgsmasswindow})
-  is applied, both for the resolved and boosted categories.
+  is applied, for the resolved and boosted categories.
 %
-The signal distribution is of course peaked at the
-nominal Higgs mass of $m_h=125$ GeV.
+While the signal distribution is of course peaked at the
+nominal Higgs mass, the background distributions
+show no particular
+structure.
 %
-In the boosted category, the background shows no particular
-structure, while remarkable in the resolved category the background
-also shows a peak-like structure, artificially induced by the
-acceptance kinematical cuts on the jets.
+As discussed in Sect.~\ref{sec:detectormodeling}, the
+width of the Higgs mass peak arises both from QCD effects
+like ISR and out-of-cone radiation, as well
+as from the smearing applied to final state particles.
 %
-Note that the applied smearing, which mimics detector resolution effects,
-leads to a rather broad distribution which reduces the usefulness
-of the Higgs mass window cut.
-%
-While our Higgs mass window cut is relatively loose,
+While the Higgs mass window requirements
+in the cut-based analysis are relatively loose, the
 information of the different shape of the $m_{h}$
-distribution will still be exploited by the MVA.
+distribution will still be fully exploited by the MVA.
 %
@@
 %
-First of all because this is a direct measure of the boost of the system,
-and also because in many BSM scenarios this distribution can be substantially
-modified as compared to the SM case, for example in the presence
-of certain dimension-6 EFT operators~\cite{Azatov:2015oxa}.
+This is a direct measure of the boost of the system,
+which in  BSM scenarios can be substantially
+enhanced, for example due to
+of certain $d=6$ EFT operators~\cite{Azatov:2015oxa}.
 %
-Indeed, one important advantage of the $4b$ final state for
+One important advantage of the $b\bar{b}b\bar{b}$ final state for
 di-Higgs production is that it significantly increases the reach
 in $m_{hh}$ as compared to other channels with smaller branching
-ration,
-such as $2b2\gamma$.
+ratios,
+such as $2b2\gamma$ or $2b2\tau$.
 %
@@
 reconstructed Higgs pairs,
-comparing the resolved category (left) with the boosted category (right).
+comparing the resolved and the boosted categories.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{plots/m_HH_C2_res_noPU.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/m_HH_C2_bst_noPU.pdf}
+  \caption{\small
+Same as   Fig.~\ref{fig:cutplots1} for the invariant
+mass distribution of the di-Higgs system $m_{hh}$, in
+the resolved (left plot) and boosted (right plot) categories.
+}
+\label{fig:mhh}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 In the resolved case, we see that the distribution
-in $m_{hh}$ is rather harder for the signal as for the background,
+in $m_{hh}$ is rather harder for the signal as compared
+to the background,
 and thus one expects that cutting in $m_{hh}$ would help signal
-discrimination: we will verify this with the help of the MVA.
+discrimination: we will verify this with the MVA.
 %
-For the boosted category the trend of the $m_{hh}$ distribution
+For the boosted category the overall trend of the $m_{hh}$ distribution
 is different because of the jet selection cuts, with the
-distribution now peaking at higher values.
+distribution now peaking at higher values of the invariant mass.
 %
@@
 %
-Note that at parton-level the $m_{hh}$ distribution as a kinematical
-cut-off at $m_{hh}^{\rm min}=250$ GeV, which is modified by both
-shower effects and by detector resolution effects.
+Note that at parton-level the $m_{hh}$ distribution
+for signal events has a kinematical
+cut-off at $m_{hh}^{\rm min}=250$ GeV, which is modified due to both
+the parton shower and to detector resolution effects.
 %
-While we don not cut in this quantity, it is
-one of the inputs for the MVA to help to improve signal discrimination.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{plots/m_HH_C2_res_noPU.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/m_HH_C2_bst_noPU.pdf}
-  \caption{\small Left plot: the invariant mass distribution of the Higgs
-    pair candidates, $m_{hh}$, comparing signal and background events,
-    in the resolved category.
-    %
-    Right plot: same for the boosted category.
-}
-\label{fig:mhh}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-Another interesting distribution is the transverse momentum of
-the di-Higgs system.
-%
-In Fig.~\ref{fig:pthh} we show the $p_T^{hh}$
-distribution
+Finally, in Fig.~\ref{fig:pthh} we show the transverse momentum of
+the di-Higgs system, $p_T^{hh}$,
 for the resolved and boosted categories.
@@
 that the signal, in both categories, thus this variable
-should provide some additional discrimination power, and therefore
+should provide additional discrimination power, and therefore
 we will use it as another of the MVA inputs.
 %
-Note that in our LO simulation this distribution is generated purely
-by the parton shower - a more refined calculation would require
-either the matching with higher-multiplicity matrix elements~\cite{Maierhofer:2013sha} or
-the full NLO calculation~\cite{Frederix:2014hta}, to treat properly the first hard emission.
+Note that in our LO simulation the $p_T^{hh}$ distribution is generated
+purely
+by the parton shower - a more refined treatment would require
+either the matching with higher-multiplicity
+matrix elements~\cite{Maierhofer:2013sha} or
+the full NLO calculation~\cite{Frederix:2014hta},
 %
-Nevertheless, the MVA shows only limited sensitivity to this variable, so its
+Nevertheless, as we will show,
+the MVA shows only limited sensitivity to this variable, so its
 modelling appears not to be crucial in our case.
@@
 
-\subsection{PU subtraction with {\tt SoftKiller}}
+\subsection{The impact of pile-up}
 \label{sec:pileup}
 
+The results shown so far did not accounted for the
+effects of PU.
+%
 To study the impact of PU in our analysis,
@@
 %
+While the latter is closer to the HL-LHC forecasts, since it
+is beyond the scope of this paper to fully optimize
+PU subtraction, we will adopt $\la n_{\rm PU}\ra=80$ as our baseline.
+
+%
 In order to subtract the PU, a number of techniques
@@
 In this work, PU  will be subtracted by means
-of the the {\tt SoftKiller} (SK)
+of the {\tt SoftKiller} (SK)
 method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
 %
-
 The idea underlying {\tt SoftKiller} is based on eliminating particles
@@
 %
-Then we will also compare some specific distributions
-also in the case where PU has not been subtracted.
-%
-We find that
-{\tt SoftKiller} exhibits a reasonable
-performance for the PU subtraction.
+We will find that
+{\tt SoftKiller} exhibits a good
+performance for the PU subtraction in the present case.
 %
@@
 
-First of all, let us validate both the implementation of our
-simulation of PU, as well as the SK subtraction, by comparing the
-invariant mass distributions of Higgs candidates in signal
+First of all, we compare
+in Fig.~\ref{fig:PUvalidation} the
+invariant mass distributions of Higgs candidates for signal
 events in the resolved category.
 %
-In Fig.~\ref{fig:PUvalidation} we show three curves: without PU,
-with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
+We show three curves: without PU,
+with PU $\la n_{\rm PU}\ra=80$ but without any subtraction, and the
 same but now with the SK subtraction.
@@
 %
-As we will see below, the performance of SK is even better in the boosted category,
+The performance of SK is even better in the boosted category,
 since the effects of PU are mitigated for high $p_T$ jets.
@@
 events, in the resolved category, comparing the results without PU,
-with PU $\la n_{PU}\ra=80$ but without any subtraction, and the
+with PU $\la n_{\rm PU}\ra=80$ but without any subtraction, and the
 corresponding results now with SK subtraction.
@@
 
-Next, we compare more
+Next, we compare additional
  signal distributions with
@@
 As we can see, in the boosted category, the residual effects of PU
-after the {\tt SoftKiller} subtraction are rather mild,
+after the {\tt SoftKiller} subtraction are rather moderate,
 with the position of the Higgs mass peaks essentially
@@
      to their no PU counterparts.
-     %
-     Therefore, these results
-     suggest that the broad pattern of the signal over background
-     discrimination provided by the MVA in Sect.~\ref{sec:mva},
-     based on the corresponding differences between kinematical
-     distributions,
-will
-     be maintained in the presence of PU.
-     %
-     In the next section we verify this expectation.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+These results validate our strategy for PU subtraction and indicate
+that, while there is some distortion in the shape of kinematical
+distributions as compared to the case without PU, it is certainly
+not enough to wash out the most important differences between
+signal and background events.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-07 paper/paperscripts/plotHist_mHH_res_noPU.py

@@ -124,7 +124,7 @@ ax.xaxis.grid(True)
 ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.25,0.93,"Boosted category, $n_{PU}=0$", fontsize=20)
+fig.text(0.28,0.93,"Resolved category, $n_{PU}=0$", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-07 paper/sec-analysis.tex
More work on the paper

@@
 
-In section we describe our analysis strategy.
+In this section we describe our analysis strategy.
 %
@@
   but this time with a smaller radius parameter, namely
-  $R=0.3$.
+  $R=0.3$~\cite{Aad:2015uka}.
  %
@@
 in the analysis from the use
-of variable-$R$ jets~\cite{Krohn:2009zg}, but found that these made
-a small difference as compared to fixed-$R$ jets.
+of variable-$R$ jets~\cite{Krohn:2009zg}, finding
+a similar performance as in the case of fixed-$R$ jets.
 %
-This is not unexpected, since variable-$R$ jets are more suitable when
+This is explained by the fact that
+variable-$R$ jets are more suitable when
 the degree of boost of the final state being reconstructed can span
-a wide range~\cite{Cacciari:2008gd}, such as in heavy resonance searches~\cite{Aad:2015fna},
+a wide range~\cite{Cacciari:2008gd}, such as in heavy resonance
+searches~\cite{Aad:2015fna},
 where where the degree of boost of the final state
@@
   $b$-quarks inside the small-$R$ jet
-  should satisfy $p_T \ge 15$ GeV.
+  should satisfy $p_T \ge 15$ GeV~\cite{Aad:2015ydr}.
   %
@@
     %
-    The simulation of the fakes from light and charm jets
-    is the same as in the small-$R$ jets.
+    The treatment of the $b$-jet mis-identification
+    from light and charm jets
+    is the same as for the small-$R$ jets.
 
@@
 
-  An event with only one large-$R$, $b$-tagged, jet, which
+  An event with exactly one large-$R$, $b$-tagged, jet, which
   is assigned to be the leading Higgs candidate.
@@
 its invariant mass is required to lie within a fixed window
-around the nominal Higgs boson mass~\cite{Aad:2015zhl}.
+around the nominal Higgs boson mass $m_h\simeq 125$
+GeV~\cite{Aad:2015zhl}.
 %
@@
 %
+This recently developed method has been shown to improve~\cite{Cacciari:2014gra} on the
+performance of the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
+%
+
 The idea underlying {\tt SoftKiller} is based on eliminating particles

### 2015-12-07 paper/sec-conclusions.tex
More work on the paper

@@
 
-In this work, we have presented a detailed study of the feasibility
-of the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
-final state at the High-Luminosity LHC.
+In this work we have presented a detailed feasibility study for
+ the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
+final state at the High-Luminosity LHC with $\mathcal{L}=3$ ab$^{-1}$.
 %
 Our strategy is based on the combination of a traditional
-cut-based analysis with modern multivariate analyses,
-which allows improving the signal significance of this channel
+cut-based analysis with state-of-the-art multivariate techniques,
+leading to an improved signal significance 
 as compared to previous studies.
@@
 boosted category, while complementary information is also provided
-by the intermediate and resolved categories.
+by the resolved and (to a lesser extent) intermediate categories.
 %
@@
 to the yield of reconstructed Higgs candidates
-when light partons are mistagged as $b$-quarks.
+when light and charm partons are mis-identified as $b$-quarks.
 %
 We show that neglecting the contribution
-from  fakes is a poor approximation, specially for the resolved and intermediate
-categories.
-%
-The reason is that
-the impact of fakes
-can be substantially enhanced, when compared to a naive parton
-level estimate, due to combinatorics and $b\bar{b}$
-pair radiation during the parton shower.
+from  fakes is a poor approximation for all categories, the reason
+being a combination of parton shower effects, with the associated $b$-quark
+pair radiation, and selection requirements.
 
@@
 discrimination information, are reasonably robust against PU effects.
-
-For a PU of $\la n_{\rm PU}\ra=150$, along what is expected
-at the HL-LHC, our main result is that the combined
+%
+For a PU environment with $\la n_{\rm PU}\ra=80$ we find that the combined
 signal significance for the three categories is $S/\sqrt{B}\simeq 4.0$,
-substantially improving previous studies.
 %
@@
 
-One important implication of our study is that it should
+Our study indicates possible avenues that the LHC experiments
+could explore to improve the signal significance of this
+process.
+%
+One handle could be to reduce the contribution from light and charm
+jet mis-identification, ensuring that the
+$2b2j$ component is subdominant over the $4b$ background.
+%
+Another possibility would be to improve the mass resolution of the Higgs peak
+in high-PU environments, since, as shown by the analysis without PU, this
+distribution carries high discrimination power.
+%
+These and similar improvements
+ might make possible an observation of Higgs pairs
+in the $b\bar{b}b\bar{b}$ feasible even with only
+$\mathcal{L}=300$ fb$^{-1}$.
+
+One important implication of this work is that it might
 be possible to improve  the accuracy on the extraction of
@@
 %
-N.~B.~N. is supported by a PhD scholarship from the Malaysia
-government.
-%
-K.~B. is supported by a studentships from the Rhodes Foundation.
+K.~B. is supported by a Rhodes Scholarship.
 %

### 2015-12-07 paper/sec-intro.tex
More work on the paper

@@
 total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
-which is increased by a further few percent once NNLL corrections
+which is increased by a further few percent once
+next-to-next-to-leading logarithmic
+(NNLL) corrections
 are accounted for~\cite{deFlorian:2015moa}.
@@
   Brooijmans:2014eja},
-the associated production modes $hhW$ and $hhZ$~\cite{Barger:1988jk,baglio}
+the associated production modes
+$hhW$ and $hhZ$~\cite{Barger:1988jk,baglio,Cao:2015oxx}
 (also known as Higgs-Strahlung),
@@
 While the SM production rates for Higgs
-pair production are small in all production modes,
-and require the full integrated luminosity of the HL-LHC phase
+pairs are small,
+and require the full integrated luminosity of the HL-LHC
 to be accessed, double Higgs production rates can be substantially
@@
 in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
+%
+In general, BSM dynamics modify
+the kinematic distributions of the Higgs decay products, for
+instance boosting the di-Higgs system, and therefore
+different analysis strategies would be required in BSM
+Higgs pair searches as compared to SM production measurements.
 
-%
-In many of these scenarios, the production rates are enhanced
-and Higgs pair production becomes accessible already at
-Run II, while still being consistent with current limits on BSM searches
-and single Higgs coupling measurements.
-%
-With this motivation, searches for the production of Higgs pair
-have already been performed at Run I
+Searches for the production of Higgs pairs
+have already been performed at Run I with 8 TeV
 by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
@@
 %
-One should note that in general BSM dynamics modify substantially
-the kinematic distributions of the Higgs decay products, for
-instance boosting the di-Higgs system, and therefore
-different analysis strategies would be requires in BSM
-Higgs pair searches as compared to SM production measurements.
+%
+In addition, ATLAS has presented~\cite{Aad:2015xja} a combination
+of its di-Higgs searches in the $bb\tau\tau,$
+$\gamma\gamma WW^*$, $\gamma\gamma bb$, and $bbbb$ final states.
+%
+Many other exotic searches involves Higgs pairs in the final
+state, such as the recent
+CMS searches for a heavy Higgs boson $H$~\cite{Khachatryan:2015tha}.
 
@@
 The results for the traditional cut-based analysis
-are presented in Sect.~\ref{sec:results}, and in
-Sect.~\ref{sec:mva} we show how we can enhance signal
-significance using multivariate techniques.
+are presented in Sect.~\ref{sec:results}.
 %
-The robustness of our results under realistic pile-up
-conditions expected at the HL-LHC is illustrated in
-....
+In Sect.~\ref{sec:mva} we show how we can enhance signal
+significance using multivariate techniques, and
+illustrate the robustness of our results under realistic pile-up
+conditions expected at the HL-LHC.
 %

### 2015-12-07 paper/sec-mcsamples.tex
more work on the paper
More work on the paper

@@
 We consider the most relevant background
-processes that contribute to the identification of
- $hh\to 4b$ candidate events.
+processes that can mimic the
+ $hh\to 4b$ signal process.
 %
@@
 %
-While the light jet mistag probability is small, we find that
+Although the light jet mistag probability is small, we find that
 in general the $2b2j$ and $4j$ backgrounds cannot be neglected because
@@
 of $b$-quarks off light partons during the parton shower, which enhances the contribution
-of parton-level $2b2j$ and $4j$ events being tagged as signal events.
+of parton-level $2b2j$ and $4j$ events being identified as signal events.
 %
@@
 $2b4j$ signature that can
-contribute due to light jet mistags.
+contribute due to light jet mis-identification.
 %
@@
 %
-We have checked that the generator-level cuts are loose enough to have
+We have checked that these generator-level cuts are loose enough to have
 no influence over the analysis cuts.
@@
 during the parton shower it can be comparable or larger
-than the irreducible QCD background.
+than the irreducible $4b$ QCD background.
 %
@@
 \hline
-$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.71\times10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
+$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.7\cdot10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
 \hline
 \hline
-$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.12 \times10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
-$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.66 \times 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
-$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.71\times 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
-$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.51\times 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
+$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.1 \cdot10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
+$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.7 \cdot 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
+$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.7\cdot 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
+$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.5\cdot 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
 \hline
@@
 \subsection{Modelling of detector resolution}
+\label{sec:detectormodeling}
 
@@
 Finally, the particle's energy is recalculated from the smeared $p_T^\prime$,
-$\eta^\prime$ and $\phi^\prime$ values to satisfy the mass-shell
-condition.
+$\eta^\prime$ and $\phi^\prime$ values to ensure that the resulting
+four-momentum is that of a light-like particle, since we neglect all
+hadron masses in this analysis.
 
@@
 reconstructed Higgs candidates of around 10 GeV, consistent
-with the hadronic mass resolutions of ATLAS and CMS.
+with the hadronic mass resolutions of ATLAS and CMS~\cite{Aad:2012gxa,Chatrchyan:2013zna,Aad:2014xzb}.
 %

### 2015-12-07 paper/sec-results.tex
More work on the paper

@@
 First of all, we compare the cross-sections at various
-analysis levels for the three categories, for signal and background events,
+stages of the selection
+for the three categories, for signal and background events,
 by providing a detailed cut-flow.
@@
 %
-It should have been possible to somewhat increase this significance
-but using more aggressive cuts,
+The significance in principle could have been increased
+by applying tighter selection requirements,
 but this is not needed due to the subsequent
@@
 
-\subsection{The role of light  and charm jet mistags}
+\subsection{The role of light  and charm jet mis-identification}
 
@@
 level, that is, after the mass-drop tagging but before
-$b$-tagging, is a factor 300 larger in the $2b2j$
+$b$-tagging, is more than two orders
+of magnitude larger in the $2b2j$
 sample as compared to the $4b$ sample.

### 2015-12-08 paper/HH4b.tex
more work polishing the text

@@
   %
-  Double Higgs production provides a unique window to the electroweak
-  symmetry breaking mechanism due to its sensitivity
+  Double Higgs production provides a crucial window to the electroweak
+  symmetry breaking mechanism and has unique sensitivity
   to the Higgs trilinear coupling.
@@
   backgrounds, including the contribution from light and charm
-  jet mistags that is found to be comparable
+  jet mistags, which turns out to be comparable
   to the irreducible $4b$ QCD background.
   %
-  We demonstrate the robustness of our analysis in a high pile-up
+  We demonstrate the robustness of our analysis strategy in a high pile-up
   environment.
@@
   For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
-  an overall signal significance of  $S/\sqrt{B}\simeq 4$ is obtained.
-  %
-  Our analysis indicates
+  a signal significance of  $S/\sqrt{B}\simeq 4$ is obtained,
+  indicating
   that the $b\bar{b}b\bar{b}$ channel
-alone should allow the observation of double Higgs production
+alone should allow for the observation of double Higgs production
   at the High Luminosity LHC.

### 2015-12-08 paper/sec-intro.tex
more work polishing the text

@@
 
-The measurement of double Higgs production will be one of the main
+The measurement of double Higgs production will be one of the central
 physics goals of the LHC program in its recently started high-energy
@@
 Higgs pair production is directly sensitive to the
-Higgs trilinear coupling $\lambda$~\cite{baglio}, and thus 
+Higgs trilinear coupling $\lambda$~\cite{baglio} and 
 provides crucial
@@
 %
-It can also probe the underlying strength of the Higgs interactions
+It also probes the underlying strength of the Higgs interactions
 at high energies, and can be used to test the composite nature of the 
@@
 scenarios predict enhanced rates for double Higgs production, and
-thus searches for this process have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
+thus searches for this process have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015xja,Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
 and will continue at Run II.
@@
 any future high-energy 
-collider, either at a 100 TeV circular machine~\cite{Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
+collider, either at a 100 TeV circular machine~\cite{Arkani-Hamed:2015vfh,Barr:2014sga,Papaefstathiou:2015iba,Azatov:2015oxa} or at
 a linear or circular electron-positron collider~\cite{Contino:2013gna}.
@@
 Higgs bosons at the LHC is 
-gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and
+gluon fusion (see Refs.~\cite{baglio,Frederix:2014hta} and
 references therein).
@@
 Feasibility studies in the case of a SM-like Higgs boson
-in gluon fusion have been performed for several different final states, including
+in gluon fusion at the LHC have been performed for different final states, including
 $b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
@@
 %
-While these studies differ in their qualitative conclusions,
+While these studies differ in their quantitative conclusions,
 a consistent picture emerges 
 that the ultimate precision in the determination of the Higgs trilinear
-coupling $\lambda$
-will only be achieved from the combination of various final states.
+coupling $\lambda$ requires the full integrated luminosity
+of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
+and will rely on the combination of all relevant final states.
 
@@
 rates: at 14 TeV, the inclusive total cross-sections are
-2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
+2.0 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
 0.5 fb for $W(Z)hh$~\cite{baglio}
@@
 %
-Concentrating on the SM dynamics of Higgs pair production
-in different channels, several studies
-have investigate the interplay of various kinematical
-distributions towards the optimisation of the
+The interplay between  kinematic
+distributions for the
 extraction of $\lambda$ from the measured
-cross-sections, as well as the improvement
-in the signal modeling taking into account
-higher-order corrections and theoretical
-uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
+cross-sections, and the role of the associated theoretical
+uncertainties, have been intensely scrutinized
+recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
   Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
@@
 While the SM production rates for Higgs
-pairs are small,
-and require the full integrated luminosity of the HL-LHC
-to be accessed, double Higgs production rates can be substantially
-enhanced in a variety of Beyond the SM (BSM) scenarios.
+pairs are small, these can be substantially
+enhanced in a variety of BSM scenarios.
 %
@@
 Theories (EFTs) with higher-dimensional
-operators and anomalous values of the
+operators and anomalous 
 Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
-in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, as well as
-in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
+in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, or Supersymmetry and
+Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
 %
-In general, BSM dynamics modify
+Since BSM dynamics modify
 the kinematic distributions of the Higgs decay products, for
-instance boosting the di-Higgs system, and therefore
-different analysis strategies would be required in BSM
-Higgs pair searches as compared to SM production measurements.
+instance boosting the di-Higgs system,
+different analysis strategies  might be required for BSM
+Higgs pair searches as compared to SM measurements.
 
@@
 state, such as the recent
-CMS searches for a heavy Higgs boson $H$~\cite{Khachatryan:2015tha}.
+searches for heavy Higgs bosons $H$~\cite{Khachatryan:2015tha}.
 
@@
 luminosity of
-$\mathcal{L}_{\rm int}$=3000 fb$^{-1}$,
+$\mathcal{L}$=3000 fb$^{-1}$,
 a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
@@
 from reducible processes, such as $bbjj$ and
-$jjjj$, which can fake the signal when 
-light jets are mistagged as $b$-jets, are not accounted for.
+$jjjj$, which can contribute to the signal yield when 
+light jets are mis-identified as $b$-jets,
+are not accounted for.
 %
-As will show, this approximation is not justified since, both due to
-combinatorics and to $b$-quark radiation in the
+As will show, due to both
+selection effects and $b$-quark radiation in the
 parton shower, the
-contribution of the $2b2j$ and $4j$ backgrounds can become comparable or even larger
-than the irreducible $4b$ component.
+contribution of the $2b2j$ process is actually comparable to
+the irreducible $4b$ component.
 
-In this work, we revisit the feasibility of SM Higgs pair production by gluon-fusion
-in the $b\bar{b}b\bar{b}$ final state.
+In this work, we revisit the feasibility of SM Higgs pair production in
+gluon-fusion
+in the $b\bar{b}b\bar{b}$ final state at the LHC.
 %
  Our strategy is based on a combination of traditional cut-based
- methods with multivariate analysis (MVA),
- leading to a substantial
-  enhancement of the signal discrimination.
+ methods with multivariate analysis (MVA).
   %
   We account for  all relevant
-  backgrounds, including the contribution from mistags of
+  backgrounds, including the contribution from mis-identified
   light and charm jets.
   %
-  We also model the impact of the pile-up (PU) effects expected at the
-  HL-LHC by means of the {\tt SoftKiller} PU subtraction
-  method~\cite{Cacciari:2014gra}.
+  We also assess the robustness of our analysis strategy in
+  an environment with high pile-up (PU).
   %
-  By combining the contribution from
- the different event categories
-  we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
-  for $\mathcal{L}_{\rm int}$=3000 fb$^{-1}$.
+  We find an overall signal significance of $S/\sqrt{B}\simeq 4.0$
+  for a total integrated
+  luminosity of $\mathcal{L}$=3000 fb$^{-1}$,
+   indicating
+  that the $b\bar{b}b\bar{b}$ channel
+alone should allow for the observation of double Higgs production
+  at the HL-LHC.
 %
-  These results emphasize the crucial importance that the $b\bar{b}b\bar{b}$ final state
-  has for studies of Higgs pair production and for the determination of
-  $\lambda$, as well as the advantages of the use of modern statistical
-  analysis methods.
 
@@
 %
-In Sect.~\ref{mcgeneration} we discuss the modeling of the signal
-and background processes using Monte Carlo event generators.
+In Sect.~\ref{mcgeneration} we present the modeling of the signal
+and background processes with Monte Carlo event generators.
 %
@@
 we introduce our analysis strategy, and in particular
-the classification of each individual event into
+the classification of individual events into
 different categories according to their topology.
 %
-The results for the traditional cut-based analysis
-are presented in Sect.~\ref{sec:results}.
+The results the cut-based analysis
+are then presented in Sect.~\ref{sec:results}.
 %
-In Sect.~\ref{sec:mva} we show how we can enhance signal
+In Sect.~\ref{sec:mva} we illustrate the enhancement of signal
 significance using multivariate techniques, and
-illustrate the robustness of our results under realistic pile-up
-conditions expected at the HL-LHC.
+assess the robustness of our results in a high-PU environment.
 %
-Finally, in Sect.~\ref{sec:conclusions} we conclude and outline
-how our results can be extended to estimate the accuracy
-in the determination of trilinear coupling $\lambda$ and the constraints on
+In Sect.~\ref{sec:conclusions} we conclude and outline
+future studies to extend our results to estimate the accuracy
+in the determination of trilinear coupling $\lambda$, as well as
+to provide
+ constraints in
 BSM scenarios.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-08 paper/sec-mva.tex
more work polishing the text

@@
 
-\subsection{MVA strategy: deep neural networks}
+\subsection{Deep artificial neural networks}
 
@@
 
- In order to avoid overfitting,
+ In order to avoid over-fitting,
  we have used a cross-validation stopping
@@
 
- \subsection{Input kinematical variables for the MVA}
+ \subsection{Input kinematical variables}
  \label{sec:input}
@@
 
-\subsection{Signal significance after the MVA}
+\subsection{Post-MVA signal significance}
 \label{sec:signalsignificance}
@@
 
-\subsection{MVA revisited in the presence of PU}
+\subsection{Impact of PU}
 

### 2015-12-08 paper/sec-intro.tex
more work in paper

@@
 Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
-in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, or Supersymmetry and
+in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa,Wen-Juan:2015gqg}, or Supersymmetry and
 Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.

### 2015-12-08 paper/sec-mcsamples.tex
more work in paper

@@
-\section{Theoretical modeling of signal and background processes}
+\section{Modeling of signal and background processes}
 \label{mcgeneration}
@@
 %
-We also discuss the modelling of finite detector
-resolution effects by means of an smearing of the final-state
-particles four-momenta.
+We also discuss the modelling of detector
+resolution effects.
 
 \subsection{Higgs pair production in gluon-fusion}
+
+Higgs pair production is simulated at leading order (LO) using
+{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
+%
+We use a tailored  model~\cite{Maltoni:2014eza}
+for gluon-fusion Higgs boson pair production
+which includes mass effects
+from the
+exact form factors for the top-quark triangle and box
+loops~\cite{Plehn:1996wb}.
+%
+Equivalent results can be obtained using
+the recently available functionalities
+for the calculation of loop-induced processes
+in {\tt MadGraph5\_aMC@NLO}~\cite{Hirschi:2015iia}.
+%
+The calculation is performed in the
+$n_f$=4 scheme,  accounting for  $b$-quarks mass effects,
+and the renormalization and factorization
+scales are taken to be $\mu_F=\mu_R=H_T/2$.
+%
+For the input parton distribution functions (PDFs), we 
+adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
+$\alpha_s(m_Z^2)=0.118$,
+interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
+%
+The Higgs boson couplings
+and branching ratios are set to their SM values,
+and its mass is taken to be
+$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba}.
+%
+In the SM, the Higgs trilinear coupling
+is given by $\lambda=m_h^2/2v^2$, with $m_h=125$ GeV
+the Higgs boson mass and $v\simeq 246$ GeV the Higgs vacuum expectation
+value (vev).
+%
 
@@
 
-Higgs pair production is simulated at leading order using
-{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
-%
-We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
-gluon-gluon-fusion Higgs boson pair production including the effects
-of the
-exact form factors for the top triangle and box loops at leading
-order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that
-  since recently it is possible to compute also
-  loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of
-  using specific
-models~\cite{Hirschi:2015iia}.}
-%
-We use the default settings of the renormalization and factorization
-scale of the model.
-%
-The Higgs boson parameters are also the same as in the default model,
-in particular we use $m_h=125$ GeV, consistent with the latest
-measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
-%
-The value of the Higgs trilinear coupling $\lambda$ is set to its
-Standard Model value, $\lambda=m_h^2/2v^2$, with $m_h=125$ GeV
-the Higgs boson mass and $v\simeq 246$ GeV the Higgs vacuum expectation
-value (vev).
-%
-The calculation is performed in the
-$n_f$=4 scheme and thus
-takes into account the finite mass of the $b$-quarks.
-%
-For the input parton distribution functions, we 
-adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
-$\alpha_s(m_Z^2)=0.118$
-interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
-
 In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
-    for Higgs pair production in gluon fusion at
-    leading order.
+    for LO Higgs pair production in gluon fusion.
     %
     The non-trivial interplay between the diagram with a heavy quark box
-    and that of the triangle, that can lead to constructive or destructive interference,
+    and that of the triangle, that can lead to either
+    constructive or destructive interference,
     complicates the extraction of
@@
     %
-    Higher order corrections are dominated by gluon radiation
+    Higher order corrections~\cite{deFlorian:2013jea,Frederix:2014hta}
+    are dominated by gluon radiation
     from either the initial state gluons or from the heavy quark loops.
@@
     %
-Resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
+    Resummed NNLO+NNLL calculations for Higgs pair production are
+    also available~\cite{deFlorian:2015moa},
 leading to a moderate enhancement of the order of
@@
 %
-Therefore, to achieve the correct higher-order value of the  integrated cross-section, we rescale our LO signal sample to match the
+To achieve the correct higher-order value of the
+integrated cross-section, we rescale our LO signal sample to match the
 NNLO+NNLL
-inclusive cross-section.
+inclusive calculation.
 %
-This corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
+This corresponds to
+a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
 in Table~\ref{tab:samples}.
@@
 Parton level signal events are then showered with the {\tt Pythia8} Monte
-Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea} version {\tt v8.201}.
+Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201}.
 %
@@
 of the underlying event (UE), multiple parton
-interactions (MPI) and pile-up, by means
-of the the Monash 2013 tune~\cite{Skands:2014pea},
-with the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
+interactions (MPI), and pile-up (PU), by means
+of the Monash 2013 tune~\cite{Skands:2014pea},
+based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx,Ball:2013hta}.
 %
@@
 
-Now we turn to discuss the Monte Carlo generation of the relevant background processes.
-%
-All background samples are generated at leading-order
+Background samples are generated at leading order
 with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, {\tt v2.1.1}.
@@
 the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
-$\alpha_s(m_Z^2)=0.118$ is used for all samples.
+$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
+we use as
+factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
 %
-Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ for all
-the background processes.
-
-We consider the most relevant background
+We account for the most relevant background
 processes that can mimic the
@@
 This includes  QCD $4b$ multi-jet production, as well as
-QCD $2b2j$ and $4j$ multi-jet samples.
+QCD $2b2j$ and $4j$ production, and top quark pair
+production.
 %
-The latter can lead to the event being identified
-as signal in the case of light or charm
-jets being mistagged as $b$-jets.
-%
-Although the light jet mistag probability is small, we find that
-in general the $2b2j$ and $4j$ backgrounds cannot be neglected because
-of their large cross-sections and enhancement from combinatorics, that
-increase their contribution as compared to a naive estimate.
-%
-In addition, we find that there is an important contribution from the radiation
-of $b$-quarks off light partons during the parton shower, which enhances the contribution
-of parton-level $2b2j$ and $4j$ events being identified as signal events.
-%
-
-In addition to the QCD multijet processes,
-we also generate $t\bar{t}$ samples
-in the fully hadronic final state, which lead to a
-$2b4j$ signature that can
-contribute due to light jet mis-identification.
-%
-This background processes leads a similar topology that
-the corresponding QCD sample.
-%
-Leptonic decays of top quarks can be removed by requiring
-a lepton veto, and thus are not included here.
+The latter is restricted to the fully hadronic final state,
+since 
+leptonic decays of top quarks can be removed by requiring
+a lepton veto.
 %
@@
 %
-For the $4j$ sample, we rescale it using the {\tt BLACKHAT}~\cite{Bern:2011ep}
-results, that indicate
+For the $4j$ sample, we rescale the LO
+using the {\tt BLACKHAT}~\cite{Bern:2011ep}
+calculation, that indicate
 a NLO/LO $K$-factor of 0.6.
@@
 %
-The $K$-factors that we use to rescale all the background samples have been collected in
+The $K$-factors that we use to rescale
+the signal background samples are collected in
 Table~\ref{tab:samples}.
-
-At the generation level, the following loose selection 
-cuts are applied to
-background events.
-%
-Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
-in the central  rapidity
-region with
-$| \eta | \le 3.0$.
-%
-In addition, at the matrix-element level
-all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
-%
-We have checked that these generator-level cuts are loose enough to have
-no influence over the analysis cuts.
-%
-
-The LO cross-sections,
-number of generated events and the higher-order $K$-factors
-applied to the signal and background
-samples are collected in Table~\ref{tab:samples}.
-%
-We see that the $t\bar{t}$ and QCD $4b$ samples are of
-the same order of magnitude, however, the former can be efficiently
-reduced by using top quark reconstruction criteria.
-%
-The $bbjj$ cross-section is more than two orders
-of magnitude larger as compared to the
-$4b$ result, however, as we will show,
-due both to combinatorics and to $b$-quark radiation
-during the parton shower it can be comparable or larger
-than the irreducible $4b$ QCD background.
-%
- For top quark production, only the hadronic final state is generated.
- %
 
@@
 \caption{\small Details of the signal and background Monte
-  Carlo samples generated,
-  together with the corresponding generator-level LO cross-sections.
+  Carlo samples using in this work.
   %
@@
 We also provide in each case the corresponding inclusive $K$-factor
-  that is applied in each case to correctly normalize the distribution to the known
+  that is applied to reproduce the known
   higher-order results. \label{tab:samples}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+At the generation level, the following loose selection 
+cuts are applied to
+background events.
+%
+Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
+in the central  rapidity
+region with
+$| \eta | \le 3.0$.
+%
+In addition, at the matrix-element level
+all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
+%
+We have checked that these generator-level cuts are loose enough to have
+no influence over the analysis cuts.
+%
+From Table~\ref{tab:samples}
+we see that the $t\bar{t}$ and QCD $4b$ samples are of
+the same order of magnitude, however, the former can be efficiently
+reduced by using top quark reconstruction criteria.
+%
+The $bbjj$ cross-section is more than two orders
+of magnitude larger as compared to the
+$4b$ result, but will be suppressed
+by the light and charm jet mis-identification rates,
+required to contribute to the $4b$ final state.
 
@@
 %
-We find good agreement, within the scale uncertainties, between the {\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
+Using these common settings,
+we find good agreement,
+within the scale uncertainties, between the
+{\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
 backgrounds.
@@
 While it is beyond the scope of this work to perform a full
-detector simulation, it is still important to include an estimate of detector
-effects in the analysis, in particular for the finite resolution
-in energy and momentum, which will affect some kinematical variables, in particular
+detector simulation, it is important to include an estimate of detector
+effects in the analysis, in particular for the finite energy
+and angular resolutions, which directly
+degrade the reconstruction of important kinematical variables, such as
 the invariant mass of the Higgs candidates.
 %
-For example, in the absence of any four-momentum smearing, the impact of the $m_h$
-distributions of the Higgs candidates in the MVA
-would be unrealistically large.
-
 In this work, we simulate the finite energy resolution of the ATLAS and CMS
@@
 final-state particles, before jet clustering,
-with mean zero and standard deviation $\sigma_E$, that is
+with mean zero and standard deviation $\sigma_E$, that is,
 %
@@
 %
-We take as baseline value a momentum smearing
+We take as baseline value for the transverse momentum smearing a
 factor of $\sigma_E=5\%$.
@@
 
-To account for the finite angular resolution of the calorimeter,
+In addition, to account for the finite angular resolution of the calorimeter,
 the $\eta$-$\phi$ plane is divided into regions of
@@
 which falls in each of these cells is set of have the same $\eta$
-and $\phi$ values of the center of the cell.
+and $\phi$ values of the center of the
+corresponding cell.
 %
-Finally, the particle's energy is recalculated from the smeared $p_T^\prime$,
+Finally, the  energy
+of each final-state particle
+is recalculated from the smeared $p_T^\prime$,
 $\eta^\prime$ and $\phi^\prime$ values to ensure that the resulting
@@
 
-Our modelling of detector simulation has been motivated
+Our modelling of detector simulation has been tuned
 to lead to a mass resolution of
@@
 In Fig.~\ref{fig:higgs-mass-resolution} we show the
-invariant mass distributions of the leading
+invariant mass distributions of 
 Higgs candidate in signal events for the
@@
 We indeed  find a mass resolution of about 8\%, corresponding
-    to around 10 GeV for $m_H=125$ GeV.
+    to around 10 GeV for $m_h=125$ GeV.
 %
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-08 paper/sec-analysis.tex
more work polishing the text
Changes

@@
 
+For the   boosted and intermediate categories,
+which involve the use of large-$R$ jets,
+we will use jet substructure variables~\cite{Salam:2009jx,Aad:2013gja} to
+improve the significance of the discrimination between signal and background
+events in the MVA.
+%
+In particular we will consider the following jet
+substructure variables:
+\begin{itemize}
+\item The $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}.
+
+  This variable is defined by reclustering the constituents of a jet with the
+  $k_t$ algorithm~\cite{Ellis:1993tq},
+  which usually clusters last the harder constituents, and then
+  taking the $k_t$ distance measure between the two subjets at the final stage of the recombination
+  procedure,
+  \be
+  \label{eq:ktsplitting}
+\sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, .
+\ee
+with $p_{T,1}$ and $p_{T,2}$ the transverse momenta of the two subjets merged
+in the final step of the clustering, and $\Delta R_{12}$ the corresponding
+angular separation.
+
+It is also possible to define related variables like $\sqrt{d_{23}}$
+that corresponds to the
+splitting scale in the second-to-last clustering, though these
+are mostly relevant for three-prong decays.
+
+\item The ratio of 2-to-1-subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
+
+  The $N$-subjettiness variables $\tau_N$ are defined by clustering the constituents
+  of a jet with the exclusive $k_t$ algorithm~\cite{Catani:1993hr}
+  and requiring that $N$ subjets are found,
+  \be
+  \tau_N \equiv \frac{1}{d_0} \sum_k p_{T,k}\cdot {\rm min}\lp \delta R_{1k}, \ldots,
+  \delta R_{Nk}\rp \, , \qquad d_0\equiv \sum_k p_{T,k}\cdot R \, ,
+  \ee
+  with $p_{T,k}$ is the $p_T$ of the constituent particle $k$ and $\delta R_{ik}$ the distance from
+  subjet $i$ to constituent $k$.
+  %
+  In this work we use as input to the MVA the ratio of 2-subjettiness to 1-subjettiness
+  \be
+  \label{eq:tau21}
+\tau_{21} \equiv \frac{\tau_2}{\tau_1} \, ,
+  \ee
+  which provides good discrimination power
+  between QCD jets and jets arising from the decay of
+  a heavy resonance.
+
+\item The ratios of energy correlation functions (ECFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
+  $D_2^{(\beta)}$~\cite{Larkoski:2014gra}.
+
+  The ratio of energy correlation functions $C_2^{(\beta)}$ is defined as
+  \be
+  \label{eq:c2}
+C_2^{(\beta)} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
+\ee
+while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is
+\be
+e_3^{(\beta)}\equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(1,\beta)\rc^3} \, , \quad
+  e_2^{(\beta)}\equiv \frac{ {\rm ECF}(2,\beta)}{\lc {\rm ECF}(1,\beta)\rc^2} \, , \quad
+  \label{eq:d2}
+D_2^{(\beta)} \equiv \frac{ e_3^{(\beta)})}{\lp e_2^{(\beta)} \rp^3} \, .
+\ee
+The energy correlation functions ${\rm ECF}(N,\beta)$ are defined
+  in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
+  are sensitive to $N$-prong substructure.
+  %
+  The free parameter $\beta$ is set to a value of $\beta=2$,
+  as recommended by the authors of Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
+\end{itemize}
+
 \subsection{Tagging of $b$-jets}
@@
 though differences with respect to
-the corresponding CMS case~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}
+the corresponding CMS
+settings~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}
 do not modify qualitatively our results.
@@
 its invariant mass is required to lie within a fixed window
-around the nominal Higgs boson mass $m_h\simeq 125$
-GeV~\cite{Aad:2015zhl}.
+around the nominal Higgs boson mass of $m_h= 125$
+GeV.
 %
@@
 %
-We find that the category with higher significance turns out to be the boosted,
-followed by the intermediate and the resolved ones, the two latter
+We find that the category with higher significance turns out to be
+the boosted one,
+followed by the intermediate and the resolved ones, the latter two
 with similar significance.
@@
 
-\subsection{Motivation for basic kinematical cuts}
+\subsection{Motivation for basic kinematic cuts}
 
 We now motivate the values of
-kinematical cuts applied to the different categories, 
+kinematic cuts applied to the different categories, 
 comparing representative kinematic distributions between
@@
 %
-First to all we present results without PU, and in the next
-subsection we discuss what is the impact of PU
-on the description of the various kinematical
+First to all, we present results without PU, and in the next
+subsection we discuss the impact of PU
+on the description of the various kinematic
 distributions.
@@
 in Fig.~\ref{fig:cutplots1} we show
-the $p_T$ distribution of the 
+the $p_T$ distributions
 of the
@@
 %
-On the other hand, considering the subleading AKT03 subjet, one needs that
-the cut in its  $p_T$ should not bee too large, to keep most of the signal events.
+On the other hand, considering the subleading AKT03 subjet,
+this cut in its  $p_T$
+cannot be too harsh, to maintain a high signal selection
+efficiency.
 %
-So as in the case of the $p_T$ cut in the large-$R$ jets, also in this case there
-is a compromise between suppressing backgrounds but keeping a large fraction of
-signal events.
+Therefore,
+as for the previous distribution, also here 
+a compromise between suppressing backgrounds but keeping a large fraction of
+signal events is crucial.
 
@@
 soft $p_T$ distribution is one of the experimental challenges of
-exploiting the resolved category in this final state.
+exploiting the resolved category in this final state,
+and hence the requirement that $p_T \ge 40$ GeV for
+the small-$R$ jets.
 %
@@
 jets in the resolved category: as well know, the production
-is mostly central (more from signal since backgrounds are dominated by
+is mostly central (more in the case
+of signal events, since backgrounds are dominated by
 QCD $t$-channel exchange) and thus the standard rapidity cuts
@@
 that the invariant mass of the Higgs candidate (di)jets must lie within a window
-around the nominal Higgs value.
+around the nominal Higgs value, Eq.~(\ref{higgsmasswindow}).
 %
@@
 of the leading reconstructed Higgs candidates, before the Higgs mass window
-cut Eq.~(\ref{higgsmasswindow})
+cut 
   is applied, for the resolved and boosted categories.
@@
 %
-As discussed in Sect.~\ref{sec:detectormodeling}, the
-width of the Higgs mass peak arises both from QCD effects
-like ISR and out-of-cone radiation, as well
-as from the smearing applied to final state particles.
-%
-While the Higgs mass window requirements
-in the cut-based analysis are relatively loose, the
-information of the different shape of the $m_{h}$
-distribution will still be fully exploited by the MVA.
+The
+width of the Higgs mass peak is driven both from QCD effects,
+such as initial-state radiation (ISR)
+and out-of-cone radiation, as well
+as from the four-momenta smearing applied to final state particles.
 %
@@
 
-Another important kinematical distribution of this process is the invariant mass
+Another important kinematic distribution of this process is the invariant mass
 of the di-Higgs system.
@@
 which in  BSM scenarios can be substantially
-enhanced, for example due to
-of certain $d=6$ EFT operators~\cite{Azatov:2015oxa}.
+enhanced, for instance due to
+of specific $d=6$ EFT operators~\cite{Azatov:2015oxa}.
 %
@@
 %
-With this motivation, we show in
-Fig.~\ref{fig:mhh} the invariant mass distribution of the
+In Fig.~\ref{fig:mhh} we show the invariant mass distribution of the
 reconstructed Higgs pairs,
@@
 and thus one expects that cutting in $m_{hh}$ would help signal
-discrimination: we will verify this with the MVA.
+discrimination: we will verify this using the MVA.
 %
@@
 %
-In this case signal and background distributions
+In this case, signal and background distributions
 look reasonably similar.
@@
 Note that at parton-level the $m_{hh}$ distribution
-for signal events has a kinematical
-cut-off at $m_{hh}^{\rm min}=250$ GeV, which is modified due to both
+for signal events has a kinematic
+cut-off at $m_{hh}^{\rm min}=250$ GeV, which is smeared due
+to 
 the parton shower and to detector resolution effects.
@@
 
-Finally, in Fig.~\ref{fig:pthh} we show the transverse momentum of
+In Fig.~\ref{fig:pthh} we show the transverse momentum of
 the di-Higgs system, $p_T^{hh}$,
@@
 should provide additional discrimination power, and therefore
-we will use it as another of the MVA inputs.
+this distribution will be another of the inputs for the MVA.
 %
-Note that in our LO simulation the $p_T^{hh}$ distribution is generated
-purely
-by the parton shower - a more refined treatment would require
+In our LO simulation the $p_T^{hh}$ distribution is generated
+by the parton shower, and and improved theoretical
+description would require
 either the matching with higher-multiplicity
@@
 the MVA shows only limited sensitivity to this variable, so its
-modelling appears not to be crucial in our case.
+modelling is not crucial in this specific application.
 
@@
 
-\subsection{The impact of pile-up}
+\subsection{Impact of pile-up}
 \label{sec:pileup}
 
-The results shown so far did not accounted for the
-effects of PU.
+Now we turn to discuss how the description of kinematic
+distributions for $hh\to 4b$ signal
+and background processes are
+modified in a high pile-up (PU) environment.
 %
-To study the impact of PU in our analysis,
+To study the impact of PU,
 Minimum Bias (MB) events,
 including Multiple Parton Interactions (MPI), have been generated
-with {\tt Pythia8}, and
+with {\tt Pythia8}, and then
 superimposed to the signal
@@
 %
-We have explored two scenarios for the impact
-of PU in our analysis,
+We have explored two scenarios,
 one with a mean number of
@@
 %
-While the latter is closer to the HL-LHC forecasts, since it
+While the latter is closer to the HL-LHC forecasts,
+we adopt $\la n_{\rm PU}\ra=80$ as our baseline,
+given that it
 is beyond the scope of this paper to fully optimize
-PU subtraction, we will adopt $\la n_{\rm PU}\ra=80$ as our baseline.
+PU subtraction,
 
 %
-In order to subtract the PU, a number of techniques
-have been developed
-recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
+In order to subtract PU in hadronic collisions, a number of techniques
+are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
 These techniques have also important applications in the subtraction
@@
 of the {\tt SoftKiller} (SK)
-method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
+method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
+whose performance has been shown to
+improve the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
 %
-This recently developed method has been shown to improve~\cite{Cacciari:2014gra} on the
-performance of the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
-%
-
 The idea underlying {\tt SoftKiller} is based on eliminating particles
@@
 From its definition in terms of the median,
-we observe that the value of $p_T^{(\rm cut)}$
-will be dynamically raised until half of the patches have $\rho=0$.
+it follows that the value of $p_T^{(\rm cut)}$
+will be dynamically raised until half of the patches have
+$p_{Ti}=0$.
 %
@@
 %
-In this analysis, {\tt SoftKiller} method is applied
+We apply {\tt SoftKiller}
 to particles at the end of the parton shower, before
 jet clustering.
-
-To validate PU subtraction,
-we now compare different kinematical distributions
-in the case without PU and in the case
-with PU subtracted with {\tt SoftKiller}.
-%
-We will find that
-{\tt SoftKiller} exhibits a good
-performance for the PU subtraction in the present case.
-%
-We  also obtain that the boosted category is less affected
-by PU than the resolved category, as expected from the higher
-$p_T$ threshold in the corresponding selection cuts.
-
-First of all, we compare
-in Fig.~\ref{fig:PUvalidation} the
-invariant mass distributions of Higgs candidates for signal
-events in the resolved category.
-%
-We show three curves: without PU,
-with PU $\la n_{\rm PU}\ra=80$ but without any subtraction, and the
-same but now with the SK subtraction.
-%
-As expected, if PU is not subtracted there is a large shift in the Higgs mass
-peak, by about 40 GeV.
-%
-Once SK subtraction is performed, we recover a distribution much closer
-to the original ones, with only a small shift of $\simeq 5$ GeV in the mass
-distribution.
-%
-The performance of SK is even better in the boosted category,
-since the effects of PU are mitigated for high $p_T$ jets.
 
@@
   \begin{center}
-  \includegraphics[width=0.68\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
+  \includegraphics[width=0.63\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
     \caption{\small
@@
 
+To validate PU subtraction,
+we now compare representative kinematic distributions
+in the case without PU and in the case
+with PU subtracted with {\tt SoftKiller}.
+%
+We compare first
+in Fig.~\ref{fig:PUvalidation} the
+invariant mass distributions of Higgs candidates for signal
+events in the resolved category.
+%
+We show three curves: without PU,
+with PU $\la n_{\rm PU}\ra=80$ but without any subtraction, and the
+same but now with the SK subtraction.
+%
+If PU is not subtracted there is a large shift in the Higgs mass
+peak, by about 40 GeV.
+%
+Once SK subtraction is performed, we recover a distribution much closer
+to the original ones, with only a small shift of $\simeq 5$ GeV
+and a broadening of the mass
+distribution.
+%
+
 Next, we compare additional
- signal distributions with
+ distributions with
 and without PU, with $\la n_{\rm PU}\ra=80$ in the
@@
 In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
-of the leading and subleading Higgs candidates, corresponding to both
-the boosted
-and resolved categories.
+of the leading and subleading Higgs candidates,
+this time corresponding
+to the boosted category.
 %
@@
 %
-As we can see, in the boosted category, the residual effects of PU
-after the {\tt SoftKiller} subtraction are rather moderate,
+As we can see, the residual effects of PU
+after the {\tt SoftKiller} subtraction are smaller
+in the boosted selection as compared to the resolved case,
 with the position of the Higgs mass peaks essentially
-unchanged, and only a moderate distortion of the
-distribution found.
+unchanged, and only a moderate broadening of the
+mass distribution.
 %
-The effects are more important for the resolved category, where PU
-shifts the Higgs peak by an amount $\Delta m_h \simeq 5$ GeV.
 
@@
   \begin{center}
-      \vspace{-1cm}
-      \includegraphics[width=0.49\textwidth]{plots/m_H0_res_comp.pdf}
-      \includegraphics[width=0.49\textwidth]{plots/m_H1_res_comp.pdf}
       \includegraphics[width=0.49\textwidth]{plots/m_H0_bst_comp.pdf}
@@
   \caption{\small
-    Comparison of the invariant mass distributions of the leading (left plots)
-    and subleading (right plots) Higgs candidates in the resolved
-    (upper plots) and boosted (lower plots) categories,
+    Comparison of the invariant mass distributions of the leading (left plot)
+    and subleading (right plot) Higgs candidates
+    in the boosted category,
     both without PU and with
@@
 
-Next we compare the transverse momentum of the leading Higgs
+In Fig.~\ref{fig:mHH_PU}
+we compare the transverse momentum of the leading Higgs
 candidate, $p_t^{h_1}$ and the invariant mass of the di-Higgs system
-$m_{hh}$, in Fig.~\ref{fig:mHH_PU}, both for the boosted and
+$m_{hh}$, in both for the boosted and
 for the resolved categories.
 %
-In the case of the $p_T$ distribution, the differences between the selection
+In the case of the $p_T^{h1}$ distribution, the differences between the selection
 criteria for the resolved
@@
 %
-The effect of PU is negligible in the boosted case, and small
+The effect of PU is small in the boosted case, and generally moderate
 in the resolved case, except for large $p_T$ values.
 %
-For the case of the $m_{hh}$ distribution, similar conclusions
+Similar observation can be derived for the case of
+the di-Higgs invariant mass $m_{hh}$ distribution, similar 
 apply.
 %
-These comparisons validate the PU subtraction strategy
-adopted in this work.
+Therefore, we can consider the PU subtraction strategy
+as validated for the purposes of this study, although
+there could still be room for optimisation.
 
@@
   \begin{center}
-    \vspace{-1cm}
   \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
@@
 
-We can also assess the impact of PU in representative
-substructure variables
+We can also assess the impact of PU in some of
+substructure variables that will be 
 used as input to the MVA in the boosted category.
 %
-In particular we consider the subjetiness variable,
+In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
 $\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
 of energy correlation functions, $D_2^{(\beta)}$,
-Eq.~(\ref{eq:d2}),
+Eq.~(\ref{eq:d2}), in both cases
 corresponding to the leading Higgs candidate.
 %
-This comparison is illustrated in Fig.~\ref{fig:Substructure_PU}.
+Comparing the signal distributions in the cases without PU and
+with PU subtracted with SK, we observe that both substructure variables
+are reasonably robust in a high-PU environment.
 %
-As can be seen, these substructure variables, which
-as demonstrated before carry a substantial
-discrimination power, are relatively unaffected by PU.
-%
-Recall that the $D_2^{(\beta)}$ variable is
-explicitly constructed~\cite{Larkoski:2013eya}
+The ratio of energy correlation functions $D_2^{(\beta)}$ 
+was indeed constructed~\cite{Larkoski:2013eya}
 to be resilient
 with respect to PU contamination.
-%
-Therefore, we do not expect a major loss of discrimination
-power due to PU effects in our analysis.
 %
@@
      for the leading Higgs candidate in the boosted category,
-   without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
+   without PU and with $\la n_{\rm PU}\ra=80$ subtracted with {\tt SoftKiller}.
 }
@@
 the relative differences between
-signal over background distributions are affected in 
-the presence of PU.
+signal over background distributions are modified in a high-PU
+environment.
 %
@@
 in Fig.~\ref{fig:signal-vs-back-boosted} we compare
-various kinematical distributions for signal and background events,
-     with and without PU: the invariant mass, the $p_T$,
-     the 2-jettiness $\tau_{21}$, and $\sqrt{d_{12}}$,
-     the $k_T$ splitting scale, Eq.~(\ref{eq:ktsplitting}),
-     all corresponding to
-     the leading Higgs candidate.
+various kinematic distributions for signal and background events,
+with and without PU for the leading Higgs candidate: the invariant mass, the transverse
+momentum distribution $p_T$,
+     the 2--to--1 subjettiness ratio $\tau_{21}$, and 
+     the $k_T$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}).
      %
-      We observe that the most of the relevant
+      We verify that the relevant
       qualitative differences between signal
-      and background distributions are maintained in the presence of PU.
+      and background distributions are maintained even in the presence of PU.
       %
-      This is specially clear for the substructure variables, which
-      show a similar discrimination power both with and without
+      This is specially noticeable for the substructure variables, which
+      exhibit a similar discrimination power both with and without
       PU.
@@
    \caption{\small
-     Comparison of kinematical distributions, in
+     Comparison of kinematic distributions, in
      the boosted category, for signal and background events
@@
 
-Now we perform a similar comparison this time for
+Finally, can perform a similar comparison for
 the resolved category.
@@
 In Fig.~\ref{fig:signal-vs-back-resolved} we compare
-the kinematical distributions for signal and background events,
+the kinematic distributions for signal and background events,
      with and without PU, for the invariant mass and the $p_T$ of the leading
@@
 
-These results validate our strategy for PU subtraction and indicate
-that, while there is some distortion in the shape of kinematical
-distributions as compared to the case without PU, it is certainly
-not enough to wash out the most important differences between
-signal and background events.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-08 paper/sec-mcsamples.tex
Changes

@@
 and its mass is taken to be
-$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba}.
+$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba,Aad:2015zhl}.
 %

### 2015-12-08 paper/sec-mva.tex
Changes

@@
 %
-
-For analyses involving the use of large-$R$ jets,
-namely for the boosted and intermediate categories,
-a number of jet substructure variables~\cite{Salam:2009jx,Aad:2013gja} is used
-for every large-$R$ jet that is classified as a Higgs candidate.
-%
-In particular we include in the MVA training for each large-$R$ jet the following
-substructure variables:
-\begin{itemize}
-\item The $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}.
-
-  This variable is defined by reclustering the constituents of a jet with the
-  $k_t$ algorithm, which usually clusters last the harder constituents, and then
-  taking the $k_t$ distance measure between the two subjets at the final stage of the recombination
-  \be
-  \label{eq:ktsplitting}
-\sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, .
-\ee
-It is also possible to define related variables like $\sqrt{d_{23}}$
-that corresponds to the
-splitting scale in the second-to-last clustering, though we do not use
-it here since it is only relevant for three-prong decays.
-
-\item The ratio of 2-to-1-subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
-
-  The $N$-subjettiness variables $\tau_N$ are defined by clustering the constituents
-  of a jet with the exclusive $k_t$ algorithm~\cite{Catani:1993hr}
-  and requiring that $N$ subjets are found,
-  \be
-  \tau_N \equiv \frac{1}{d_0} \sum_k p_{T,k}\cdot {\rm min}\lp \delta R_{1k}, \ldots,
-  \delta R_{Nk}\rp \, , \qquad d_0\equiv \sum_k p_{T,k}\cdot R \, ,
-  \ee
-  with $p_{T,k}$ is the $p_T$ of the constituent particle $k$ and $\delta R_{ik}$ the distance from
-  subjet $i$ to constituent $k$.
-  %
-  In this work we use as input to the MVA the ratio of 2-subjettiness to 1-subjettiness
-  \be
-  \label{eq:tau21}
-\tau_{21} \equiv \frac{\tau_2}{\tau_1} \, ,
-  \ee
-  which provides good discrimination power
-  between QCD jets and jets arising from the decay of
-  a heavy resonance.
-
-\item The ratios of energy correlation functions (ECFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
-  $D_2^{(\beta)}$~\cite{Larkoski:2014gra}.
-
-  The ratio of energy correlation functions $C_2^{(\beta)}$ is defined as
-  \be
-  \label{eq:c2}
-C_2^{(\beta)} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
-\ee
-while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is
-\be
-e_3^{(\beta)}\equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(1,\beta)\rc^3} \, , \quad
-  e_2^{(\beta)}\equiv \frac{ {\rm ECF}(2,\beta)}{\lc {\rm ECF}(1,\beta)\rc^2} \, , \quad
-  \label{eq:d2}
-D_2^{(\beta)} \equiv \frac{ e_3^{(\beta)})}{\lp e_2^{(\beta)} \rp^3} \, .
-\ee
-The energy correlation functions ${\rm ECF}(N,\beta)$ are defined
-  in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
-  are sensitive to $N$-prong substructure.
-  %
-  The free parameter $\beta$ is set to a value of $\beta=2$,
-  as recommended by the authors of Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
-\end{itemize}
-%
 Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the

### 2015-12-08 paper/paperscripts/plotHist_m_htot_res_PUnoSK.py

@@ -22,8 +22,8 @@ datafiles.append("../plotdata/20K_PU80/histo_m_H_res_C2.0.dat")
 
 # Plot labels
 plotnames.append("no PU")
-plotnames.append("$n_{PU}=80$ + SK")
-plotnames.append("$n_{PU}=80$")
+plotnames.append(r"$\langle n_{PU} \rangle =80$ + SK")
+plotnames.append(r"$\langle n_{PU} \rangle =80$")
 
 
 # Axis labels

### 2015-12-08 paper/sec-mva.tex
More work on paper

@@
   %
-  The color code in the neuron connections (the weights) is a heat map,
-  with red indicating large values and black small values.
+  The color code in the neuron connections (the weights) is a heat map obtained
+  at the end of the GA training,
+  with red indicating larger values and black smaller values.
 }
@@
 \ee
-where $y_i^\prime$ represents the true classification of the event $i$, i.e $y^\prime_{\text{signal}} = 1$ and $y^\prime_{\text{background}} = 0$.
+where $y_i^\prime$ represents the true classification of the event $i$, {\it i.e},
+$y^\prime = 1$ for signal and $y^\prime = 0$ for background events.
+%
 With this interpretation, our general classification probability including background events is given by
@@
 \ee
-which implies that the  negative log-likelihood cost function
+which implies that the  negative log-likelihood error function $E(\{\omega\})$
 that needs to be minimized during the ANN training is 
@@
  \bea
- E(\{\omega\}) &=& -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right)\nonumber\\
- &=&
+ &&E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right)\nonumber\\
+ &&=
  \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)} \, ,
@@
  Eq.~(\ref{cross-entropy}), which in this work is achieved using a
- Genetic Algorithm.
+ Genetic Algorithm (GA).
  %
@@
 %
-In our $hh\to 4b$ case,
-the input variables for the MVA differ between our three categories,
-and in particular in the case of large-$R$ jets (for the boosted
-and intermediate categories) we want to exploit
-the richness of substructure information.
+In this work we use different sets of
+input variables for the MVA for the three categories.
+%
+In particular, in the case of large-$R$ jets (for the boosted
+and intermediate categories) we are exploiting the jet
+substructure information.
 
@@
   %
-Therefore, we have a total of 13 variables which are common to the three categories.
-%
-Therefore, there are in total $N_{\mathrm{var}}=13$ variables for the
-resolved analysis,
-17 for the intermediate,
-and 21 for the boosted category.
-%
+ Therefore, we have 13 variables which are common to the three categories,
+ and a total of $N_{\mathrm{var}}=13,17$ and 21 variables for the
+resolvedm intermediate and boosted categories.
+
 Given that the MVA is able to identify the most discriminatory variables
-and to ignore those that have smaller effect, it is advantageous to
-include as many substructure variables as possible.
+and to ignore those that have smaller effects, it is advantageous to
+include as many input variables as possible.
 %
@@
 should not degrade
-the classification power of the MVA (other than making the GA
-minimization less efficient).
+the classification power of the MVA, other than making the GA
+minimization less efficient.
 
@@
 %
-The  separation between signal and background is achieving by introducing
-a cut, $y_{\rm cut}$, in the ANN output, so that MC events with $y_i\ge
+The  separation between signal and background is achieved by introducing
+a cut, $y_{\rm cut}$, on the ANN output, so that MC events with $y_i\ge
 y_{\rm cut}$ are classified as signal events, and those with
@@
 As can be seen from Fig.~\ref{fig:nev2}, in the boosted category
-event with a cut in the ANN output as hard as $y_{\rm cut}\simeq 0.9$
+events, with a cut in the ANN output as hard as $y_{\rm cut}\simeq 0.9$,
 we are still left
@@
 %
-The input variables with a larger value of $\omega^{\rm tot}_i$ will those
-be the ones that play a dominant role in enhancing the signal
+The input variables with a larger value of $\omega^{\rm tot}_i$ will be those
+that play a dominant role in enhancing the signal
 discrimination using the MVA.
@@
 %
-The only variable which seems to contain to information at all
+The only variable which seems to contain no information at all
 is the $\Delta \phi_{hh}$ separation between the two
@@
     \includegraphics[width=0.49\textwidth]{plots/res_wgthist_noPU.pdf}
-\includegraphics[width=0.49\textwidth]{plots/bst_wgthist_noPU.pdf}
+\includegraphics[width=0.49\textwidth]{plots/int_wgthist_noPU.pdf}
+\includegraphics[width=0.75\textwidth]{plots/bst_wgthist_noPU.pdf}
 \vspace{-0.5cm}
@@
 Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
-variables of the resolved (left plot) and boosted (right plot) categories.
+variables of the resolved (upper left plot),  intermediate (upper right plot)
+and boosted (lower plot)
+categories.
 %
@@
 
-At this point we have all the ingredients that we need to determine the optimal
+At this point we have all the
+information needed to determine the optimal
 value of the MVA output cuts $y_{\rm cut}$
@@
 for all categories the  improvement in signal
-significance arising from the MVA is substantial, growing from around 1
+significance as compared to the pre-MVA results
+is substantial, growing from around 1
 to around 5 in the three cases.

### 2015-12-08 paper/paperscripts/plotNetwork_int_noPU.py

@@ -10,12 +10,12 @@ import sys
 ################################ Settings ###################################
 
 # Init data
-datafile = '../plotdata/results_noPU/MVA/nn_21X5X3X1_50000-Gen_noPU_bst.net'
-dataname = "Boosted"
+datafile = '../plotdata/results_noPU/MVA/nn_17X5X3X1_50000-Gen_noPU_int.net'
+dataname = "Intermediate"
 sourcefile = os.path.expanduser(datafile)
 
-archout = "bst_nnarch_noPU"
-histout = "bst_wgthist_noPU"
+archout = "int_nnarch_noPU"
+histout = "int_wgthist_noPU"
 
 #############################################################################
 
@@ -124,13 +124,13 @@ plt.xticks(rotation=-25)
 plt.bar(numpy.arange(len(kinematics))+2, sumw, alpha=0.6)
 plt.subplots_adjust(bottom=0.15)
 
-plt.xticks(numpy.arange(len(kinematics)) + 2.5, kinematics,fontsize=7)
+plt.xticks(numpy.arange(len(kinematics)) + 2.5, kinematics,fontsize=10)
 
 
 plt.xlabel('ANN Input Variable',fontsize=17)
 plt.ylabel('Total associated weight',fontsize=17)
 
-plt.text(4,14.5,"Boosted category, no PU", fontsize=20)
+plt.text(5,9.5,"Intermediate category, no PU", fontsize=20)
 
 plt.savefig(histout+".pdf")
 plt.clf()

### 2015-12-08 paper/paperscripts/plotNetwork_res_noPU.py

@@ -1,4 +1,4 @@
-#! /usr/bin/python
+#! /usr/local/Cellar/python/2.7.10/bin/python
 import matplotlib.pyplot as plt
 import networkx as nx
 import os
@@ -130,7 +130,7 @@ plt.xticks(numpy.arange(len(kinematics)) + 2.5, kinematics,fontsize=11)
 plt.xlabel('ANN Input Variable',fontsize=17)
 plt.ylabel('Total associated weight',fontsize=17)
 
-plt.text(4,12.5,"Resolved category, no PU", fontsize=20)
+plt.text(5,10.5,"Resolved category, no PU", fontsize=20)
 
 plt.savefig(histout+".pdf")
 plt.clf()

### 2015-12-08 paper/sec-intro.tex
More work on paper

@@
 luminosity of
-$\mathcal{L}$=3000 fb$^{-1}$,
+$\mathcal{L}=3$ ab$^{-1}$,
 a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
@@
   for a total integrated
-  luminosity of $\mathcal{L}$=3000 fb$^{-1}$,
+  luminosity of $\mathcal{L}=3$ ab$^{-1}$,
    indicating

### 2015-12-08 paper/sec-results.tex
More work on paper

@@
 In this section we present the results of the 
-cut-based analysis, including the corresponding
-cut-flow.
+cut-based analysis and provide a
+cut-flow for the different analysis steps.
+%
 We
 compare our results with other recent studies,
-and in particular
-we study how the signal significance
+and assess how the signal significance
 is affected if only the $4b$ component of the
-QCD multi-jet background is taken into account,
-while the $2b2j$ and $4j$ components are neglected.
+QCD multi-jet background is taken into account but not 
+the $2b2j$ and $4j$ components.
 %
+We present now the results in the no PU scenario, the impact
+of PU will be discussed in the next section.
 
@@
 
-First of all, we compare the cross-sections at various
-stages of the selection
-for the three categories, for signal and background events,
-by providing a detailed cut-flow.
+We now compare the cross-sections for
+signal and background events at various
+stages of the analysis.
 %
-We consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
-and also discuss how results are modified if only the $4b$
+We consider all relevant backgrounds (see Sect.~\ref{mcgeneration}),
+and discuss how results are modified if only the $4b$
 component is kept.
@@
 =3000$ fb$^{-1}$.
-%
-For this type of analysis,
-it is crucial not only to achieve a good signal
-significance, $S/\sqrt{B}$, but also a good signal over background ratio $S/B$.
-%
-If the latter is too small, an unrealistically precise
-measurement of the background would be required.
-%
+
 In Table~\ref{tab:cutflowdetails}
-we describe this cut-flow,
-separated into the (exclusive) boosted, intermediate,
+we summarize the definition of the different
+levels of the cut-flow of the present analysis,
+separated into the boosted, intermediate,
     and resolved categories.
@@
     %
-    The various cuts
-    are defined as follows:
+    In more details, these different analysis levels are the following:
 
@@
   \end{tabular}
-  \caption{\small Cut-flow of the present analysis for the boosted, intermediate
+  \caption{\small Definition of the cut-flow levels for the boosted, intermediate
     and resolved selections.
@@
     \begin{itemize}
-    \item {\bf C0}: these are the generator level cross-sections, with
+    \item {\bf C0}:  generator level cross-sections, with
       mild generation cuts in the case of the background processes, and no
@@
       %
-    \item {\bf C1a}:  we only check that we have at least
+    \item {\bf C1a}:  check that we have at least
       two large-$R$ jets (in the boosted case),
@@
       in particular between 85 and 165 GeV.
-          \item {\bf C2}: finally, the
+          \item {\bf C2}: the
             $b$-tagging conditions are
@@
     in Sect.~\ref{sec:mva}.
+    %
+    In Table~\ref{tab:cutflow_noPU_1} we collect
+    the values for cross-sections for signal and background processes
+    for different levels of the cut flow.
+    %
+    Results are divided into the resolved, intermediate and boosted categories,
+    and are inclusive up to the C2 level, where exclusivity is imposed.
+    %
 
+In Table~\ref{tab:cutflow_noPU_1} we also  provide the signal over
+      background ratio, $S/B$, and the signal
+      significance, $S/\sqrt{B}$, corresponding to an integrated
+      luminosity of $\mathcal{L}=3$ ab$^{-1}$.
       %
-    In Table~\ref{tab:cutflow_noPU_1} we provide
-    the values of cross-sections, in femtobarns,
-     for the signal
-      and the various background
-      components as a function of the
-      cut-flow, for the resolved,
-      boosted and intermediate
-      categories.
+      This is done both taking into account all the background components and only
+      the $4b$ QCD background.
         %
-       In each case, we also provide the signal over
-      background ratio, $S/B$, and the signal
-      significance, $S/\sqrt{B}$, at the HL-LHC, considering either
-      the total background or only the $4b$ component.
+      We find that after $b$-tagging, the  $2b2j$ component is
+      of the same order of magnitude as the $4b$ component.
       %
-      This separation emphasizes
-      the  importance of the reducible component of the QCD background.
-      %
-      Even after $b$-tagging, the reducible $2b2j$ background
-      is comparable, or even larger, than the irreducible
-      $4b$ component.
-      %
-      %
-      So at the end of the cut-based analysis, signal significance
-      are overestimated by up to a factor 2 if the light
-      and charm jet background is neglected.
+      This means that the signal significance at the end of the cut-based
+      analysis is degraded by about a factor two due to the contribution
+      of light and charm jets being mis-identified as $b$-jets.
 
@@
       significance, $S/\sqrt{B}$, considering either
-      the total background or only the $4b$ component.
+      the total background or only the $4b$ component, for
+      a total integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
       %

### 2015-12-08 paper/sec-results.tex
More work in the results section of the paper

@@
       %
-      This means that the signal significance at the end of the cut-based
+      This implies that the signal significance at the end of the cut-based
       analysis is degraded by about a factor two due to the contribution
@@
 %
-In the boosted category, after all cuts,
-one ends
-up with more than 1K signal events expected
-at the HL-LHC, swamped  however in a almost 1M background events,
-leading to $S/\sqrt{B}=1.2$ and $S/B=0.0014$.
+In the boosted category, at the end of the cut-based
+analysis, we find that around $10^3$ events
+are expected
+at the HL-LHC, with however a very large number,
+$\simeq 10^6$, of QCD background events.
 %
-The significance in principle could have been increased
+This leads to a pre-MVA signal significance of
+$S/\sqrt{B}=1.2$ and a signal over background
+ratio of $S/B=1.4\%$.
+%
+We emphasize that such signal
+significance could have been enhanced
 by applying tighter selection requirements,
-but this is not needed due to the subsequent
+but this is not needed here thanks to the subsequent
 optimisation  performed with the MVA.
@@
 expectations for the LHC Run II with
-$\mathcal{L}=300$ fb$^{-1}$: one expects
+$\mathcal{L}=300$ fb$^{-1}$: one expects around
 120 signal events, with signal significance dropping down to
@@
 the signal significance is similar to that of the boosted category,
-$S\sqrt{B}=0.97(0.92)$ in the resolved
-(intermediate) categories,
-with the drawback, in the resolved case,
+$S\sqrt{B}\simeq 0.9$ in both categories.
+%
+An important additional
+drawback of the resolved case is
 that $S/B$
@@
 of the boosted, intermediate and resolved categories,
-we obtain a significance for the observation of the Higgs pair production
+we obtain an overall
+significance for the observation of the Higgs pair production
 in the $b\bar{b}b\bar{b}$ final
-state at the HL-LHC of  $S/\sqrt{B}=1.8$.
+state at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
+of  $S/\sqrt{B} \simeq 1.8$.
 
@@
 and reducible background components, which allows
-to study the impact of the modeling of light and charm jet mistags. 
+quantifying
+the impact of the modeling of light and charm jet mistags. 
 %
@@
 %
-The UCL study based
+The UCL study is based
 on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
@@
 %
-In addition to the basic selection cuts, the discriminating
-power of
-additional variables is included by means of a 
+In addition to the basic selection cuts, the constraints
+from additional kinematic variables are included by means of a 
 Boosted Decision Tree (BDT) discriminant.
@@
 $t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$,
-and a signal significance of $S/\sqrt{B}=2.1$ for the HL-LHC
+and a signal significance of $S/\sqrt{B}\simeq 2.1$ for the HL-LHC
 is obtained.
@@
 To improve the separation between
-signal over background separation, both the BDRS
+signal and background, both the BDRS
 method and the Shower Deconstruction (SD)~\cite{Soper:2011cr,Soper:2012pb}
@@
 %
-The background considered are QCD $4b$ as well as $Zb\bar{b}$, $hZ$ and
+The backgrounds considered are QCD $4b$ as well as $Zb\bar{b}$, $hZ$ and
 $hW$.
 %
-At the HL-LHC, the best result is obtained by requiring two
-SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\sim 2.1$, with
+At the HL-LHC, their best result is obtained by requiring two
+SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\simeq 2.1$, with
  slightly inferior performance with the BDRS tagger.
@@
 
-%
  From the results of Table~\ref{tab:cutflow_noPU_1}, we observe
- that the signal significance in the boosted, intermediate,
- and resolved categories is 2.7, 1.6 and 1.6 respectively,
+ that the signal significance for the boosted, intermediate,
+ and resolved categories is increased to 2.7, 1.6 and 1.6, respectively,
  when only the QCD $4b$ background is included.
  %
- Combining the signal significance in the three categories,
+ Combining in this
+ case the signal significance in the three categories,
  we
- obtain  a total $S/\sqrt{B_{\rm 4b}}=3.5$, which is a factor
- 2 improvement as compared to the result found when
+ obtain $S/\sqrt{B_{\rm 4b}}\simeq 3.5$, which is twice
+ as large as the result found when
  all background components are included.
  %
- This should be taken into account when comparing
- the results of this work with previous analysis.
- %
+ At this level, part of the improvement that we found as compared
+ to~\cite{deLima:2014dta,Wardrope:2014kya} arises
+ from the combination of the three exclusive event topologies,
+ as opposed the exploitation of a single specific category.
 
@@
  %
- In the resolved case, the $4b$ and $2b2j$ have a similar
- magnitude, with the latter being larger by a factor of two,
- with $4j$ being smaller by an order of magnitude.
+ In all cases, the $4b$ and $2b2j$ have comparable
+ magnitudes, taking into account the size that the higher-order QCD
+ effects could induce in
+ the corresponding normalizations.
  %
- The situation is similar in the intermediate category, while
- in the boosted category the importance of the $2b2j$ component
- is even more marked, being a factor four larger than the
- $4b$ one.
+ On the other hand, the $4j$ component
+is always smaller by at least
+ one order of magnitude.
  %
- Therefore, we conclude that, while the $4j$ component can be safely
- neglected (given the theory uncertainties associated to the
- modelling of the QCD background), the inclusion of the
+  So while the $4j$ component can be safely
+ neglected, the inclusion of the
  $2b2j$ component is essential to robustly assess the feasibility
- of measuring Higgs pairs in this final state.
+ of measuring Higgs pairs in this final state, and this is markedly
+ important
+ in the boosted category.
  %
- This indicates that a promising avenue to improve the prospects
+ This has the important
+ consequence that a promising avenue to improve the prospects
  of this measurement would be to reduce, as much as possible,
- the light and charm jet mistag rate, in addition to achieving
- a higher $b$-tag efficiency.
+ the light and charm jet mis-identification rate.
 
@@
     of the shapes of the $4b$ and $2b2j$
-components of the QCD background for the $p_T$ of the leading
+    components of the QCD background for the transverse momentum
+    $p_T$ of the leading
 Higgs candidate in the resolved
@@
     for the two distributions, with some interesting
-    differences, for instance in the boosted
+    differences, for instance, in the boosted
     category the $4b$ component is harder for the
-    $p_T^h$ distribution, while the $2b2j$ leads to a longer
+    $p_T^h$ distribution.
+  %
+    The $2b2j$ component leads to a longer
     tail at small values of the $m_{hh}$ invariant
@@
     are affected by somewhat larger
-    MC fluctuations as compared to $4b$, despite the large size
+    Monte Carlo fluctuations as compared to $4b$, despite the large size
 of the initial sample.
 %
-This is a consequence of the
-difficulties of an accurate modelling of the effects
-of $b$-jet mistags from a QCD multi-jets process, requiring
+These fluctuations illustrate the challenge
+of an accurate modelling of the effects
+of $b$-jet mis-identification in QCD processes, which requires
 very large MC samples.
@@
     %
-Lower plots: the same comparison this time for the invariant
+Lower plots:  same comparison for the invariant
 mass $m_{hh}$ of the
@@
 The reason why the  $2b2j$ process
-is not negligible as compared to the $4b$ component
+cannot be neglected as compared to the $4b$ component
 is the following.
@@
 In the boosted category, for example,
-the cross-sections at the C1e
-level, that is, after the mass-drop tagging but before
-$b$-tagging, is more than two orders
+the cross-section  before
+$b$-tagging is more than two orders
 of magnitude larger in the $2b2j$
@@
 Now, after $b$-tagging, the naive expectation would
-be a suppression of the former by a factor $f_l^2/f_b^2 =3\cdot 10^{-4}$,
+be a suppression of the former by a factor $(f_l/f_b)^2 \simeq
+1.5\cdot 10^{-4}$, as compared to the $4b$ component,
 since a total of four $b$-tags are required to classify the
@@
 So the ratio of $2b2j$ over $4b$ should be
-around $\simeq 3\%$.
+around $\simeq 3\%$, and therefore negligible.
   %
 While  we have checked that this expectation is borne
-out at parton level, before showering,
+out at the parton level,
 we find that  when parton shower effects
-are accounted for, due to the radiation of $b\bar{b}$ pairs from the
-light jets as well as due to combinatorics, the
+are accounted for, due both to radiation of $b\bar{b}$ pairs
+and from selection effects, the situation is different.
+%
+In this case,
+the
 number of  $b$ quarks in the  final state is
 increased substantially in the $2b2j$ component as compared
-to the parton level content,
-enhancing the signal efficiency and making
-it comparable to the $4b$ component.
+to the parton level content, while at the same
+time the number of events in the $4b$ sample
+with 4 $b$-jets is reduced.
 
-We can make this statement more quantitative in the following way.
+We can make these statements more quantitative in the following way.
 %
-To first approximation, and neglecting the contribution from charm mistags, the
+To first approximation, and neglecting the contribution from
+charm mis-identification,
+the
 overall efficiency of the $b$-tagging requirements in the resolved category will be
@@
 with $n^{\rm (b-jet)}_j$ the fraction of events, satisfying all the selection cuts,
-where $j$ jets, out of the leading four jets, of the event contain $b$ quarks (with $p_T^b\ge 15$
+where $j$ jets, out of the leading four jets of the event,
+contain $b$ quarks (with $p_T^b\ge 15$
 GeV).
@@
   \simeq
- \lp \frac{f_l}{f_b}\rp^2 \simeq 1.6\cdot 10^{-4} \, .
+ \lp \frac{f_l}{f_b}\rp^2 \simeq 1.5\cdot 10^{-4} \, .
 \ee
-However, the actual situation is more complicated.
+However, after the parton shower the above is not a good approximation.
 %
@@
     The relative fractions  $n^{\rm (b-jet)}_j$ of events for the resolved selection
-    for which, out of the four leading small-$R$ jets, $j$ jets
-    contain at least one $b$-quark with $p_T^b\ge 15$ GeV,
-    both for signal events and for the three QCD background samples.
+    for which, out of the four leading small-$R$ jets of the
+    event, $j$ jets
+    contain at least one $b$-quark with $p_T^b\ge 15$ GeV.
+    %
+    This information is provided
+    for the di-Higgs signal events and for the three QCD background samples.
     %
     The last column indicates the overall predicted
-    selection efficiency of the $b$-tagging procedure,
+    selection efficiency of the $b$-tagging procedure following
     Eq.~(\ref{btaggingeff})
@@
 %
-Therefore, we find that, rather than the estimate Eq.~(\ref{eq:naive}),
+We find that, rather than the estimate Eq.~(\ref{eq:naive}),
 the correct ratio of $b$-tagging selection efficiencies is instead
@@
 
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %

### 2015-12-08 paper/sec-analysis.tex
More work on paper
more work on paper

@@
 
-It is also possible to define related variables like $\sqrt{d_{23}}$
-that corresponds to the
-splitting scale in the second-to-last clustering, though these
-are mostly relevant for three-prong decays.
-
-\item The ratio of 2-to-1-subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
+\item The ratio of 2-to-1 subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
 

### 2015-12-08 paper/sec-mva.tex
more work on paper

@@
 
-From the cut-based analysis,
-combining the significance of the three categories,
+At the end of the cut-based analysis,
+combining the three categories,
 we obtain a signal significance of $S/\sqrt{B}\simeq 1.7 (3.5)$
@@
 %
-This is clearly
-to be enough to be able to claim observation
-of Higgs pair production
-in this channel, and even less to extract the trilinear Higgs  coupling
-$\lambda$, in particular
-taking into account the that $S/B$ is at the permille level.
-%
-In this section we now show how this signal significance for
- can
-be significance improved when
-applying a multivariate analysis (MVA) subsequently
-to the cut-based analysis.
-
-%
-Multivariate techniques are by now a mature tool to enhance signal
-significance in HEP analysis, allowing
-to open a new window to improve the performance
-of many physics analysis and searches.
-%
-In particular, the classification of events as arising from either signal or
-background processes via the use of a multivariate analysis is a
+We now show how this signal significance
+ can be enhanced when the cut-based analysis
+ is complemented with a multivariate analysis (MVA).
+%
+ Multivariate techniques are by now a mature tool
+ in high-energy physics data analysis, opening
+ new avenues for improving the performance
+of many measurements and searches at high-energy colliders.
+%
+In particular, the classification of events between signal and
+background processes by means of MVAs is a
 commonly applied strategy in LHC
@@
   Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.
-%
-For instance, the CMS $Vh(\to b\bar{b})$ analysis~\cite{Chatrchyan:2013zna}
-is based on a Boosted Decision Tree (BDT) MVA, and the UCL $hh\to 4b$
-feasibility study~\cite{Wardrope:2014kya}
-also used  a BDT to improve signal discrimination.
 
@@
 Since we find that jet substructure variables are a crucial input
-to the MVA, we finally show various kinematic distributions
-of these variables.
+to the MVA, we show representative kinematic distributions
+for these variables.
+%
+Finally, we assess the robustness of the MVA strategy in
+high-PU environments.
 
@@
 %
-The specific type of  MVA that we use here, to
-disentangle signal and background events in the $hh\to 4b$ process, will be
+The specific type of  MVA that we use to
+disentangle signal and background events is
 a multi-layer feed-forward artificial neural network (ANN),
-also known as a {\it perceptron}.\footnote{This type of ANNs are the same
+known as a {\it perceptron}.\footnote{This type of ANNs are the same
   as those used to parametrize Parton Distribution Functions
@@
 %
-This family of ANNs is sometimes known as {\it deep} neural networks, since they have
+This family of ANNs is also known as {\it deep} neural networks, since they have
 a richer architecture with hidden layers.
 %
-The basic idea is that the ANN is trained on an input composed on
-all  signal and background
+The input to the MVA are the
+signal and background
 events which satisfy the requirements of the
@@
 %
-The main result of the trained ANN is identifying, in a fully automated way,
-which are the most relevant variables to discriminate between the two classes
-of events.
+The output of the trained ANNs allows the identification, in a fully automated way,
+of the most relevant variables to discriminate between 
+signal and background.
 
@@
 where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
-which is specific of the analysis category: resolved, intermediate, or boosted.
+which is different in the resolved, intermediate, and boosted categories.
 %
@@
 for a probabilistic
-interpretation of the neural-network output.
-%
-In Fig.~\ref{fig:nnarch} we show an example of the ANN that we use in this work, corresponding here
+interpretation of the ANN output.
+%
+In Fig.~\ref{fig:nnarch} we show an illustrative
+example of a ANN used in this work, corresponding 
 to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).
@@
 %
-Given a set of $N_{\mathrm{var}}$  kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ (that is, the activation state of the
+Given a set of $N_{\mathrm{var}}$  kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network weight
+parameters $\{\omega\}$, we interpret the neural network output $y_i$
+(the activation state of the
 neuron in the last layer)
@@
 \ee
-which implies that the  negative log-likelihood error function $E(\{\omega\})$
+which implies that the  error function $E(\{\omega\})$
 that needs to be minimized during the ANN training is 
-the cross-entropy error, defined as
+the cross-entropy function, defined as
  \bea
- &&E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right)\nonumber\\
+ &&E(\{\omega\}) \equiv -\log\left(\prod_i^{N_{\text{ev}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right)\nonumber\\
  &&=
- \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)} \, ,
+ \sum_i^{N_{\text{ev}}} \lc y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)}\rc \, ,
  \label{cross-entropy}
  \eea
- where $N_{\text{evt}}$ is the number of
- Monte Carlo events that we have generated.
+ where $N_{\text{ev}}$ is the number of
+ Monte Carlo events that are used for the ANN training.
  %
  The ANN is trained both on the signal and background MC events,
- in each case using the information $y_i'$ of the true nature
- of the event.
- %
- To be stable against statistical fluctuations, it is important to use
- a large enough MC sample both of signal and of background events
- for the MVA training.
-
- Therefore, the training of the neural networks consist on the
+ so it is crucial to ensure that the input MC sample is large enough
+ to avoid the contamination from MC statistical fluctuations.
+
+ The training of the neural networks thus consist on the
  minimization of the cross-entropy error,
@@
  %
- The GA training is performed for a very large 
- number of generations, in this case $N_{\rm gen}=50k$, to avoid
+ Genetic Algorithms~\cite{quevedo,tau,Abel:2014xta,Nesseris:2012tt} are
+ non-deterministic
+ minimization strategies suitable for the solution
+ of complex optimization problems, for instance when a very large number
+ of quasi-equivalent minima are present.
+ %
+ GAs are inspired on natural selection processes
+ that emulate biological evolution. 
+ %
+ In our case, the GA training is performed for a very large 
+ number of generations, $N_{\rm gen}=5\cdot 10^{4}$, to avoid the risk of
  under-training.
  %
- We have verified that if a larger number of generations
- are used the results are unchanged.
+ We have verified that if a much larger number of generations
+ are used, the results are unchanged.
  %
@@
  we have used a cross-validation stopping
- criterion, in particular, the same one as
- that used in the NNPDF3.0 analysis~\cite{Ball:2014uwa}
- does not modify the results.
+ criterion, in particular the same one as
+ that used in the NNPDF3.0 analysis~\cite{Ball:2014uwa}.
  %
@@
  Eq.~(\ref{cross-entropy}) for the validation sub-sample.
+ %
+ This indicates the point where we are training on the statistical fluctuations
+ of the input MC samples, rather than in the underlying (smooth) physical
+ distributions.
 
@@
 
- To identify the variables with higher discriminatory power,
+ To ensure that we include the variables with higher discriminatory power,
  we need to train
- the MVA using a large number of kinematic distributions for
- signal and background events.
+ the MVA on a large number of kinematic distributions.
 %
 In this work we use different sets of
-input variables for the MVA for the three categories.
+input variables for the three categories.
 %
 In particular, in the case of large-$R$ jets (for the boosted
-and intermediate categories) we are exploiting the jet
+and intermediate categories), we are fully exploiting the jet
 substructure information.
@@
   the transverse momenta of the leading, $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and
-  sub-leading, $p_{T,h_{2,1}}$ and $p_{T,h_{2,1}}$, Higgs candidate subjets.
+  sub-leading, $p_{T,h_{2,1}}$ and $p_{T,h_{2,2}}$, Higgs candidate AKT03 subjets.
   %
@@
   %
- Therefore, we have 13 variables which are common to the three categories,
- and a total of $N_{\mathrm{var}}=13,17$ and 21 variables for the
-resolvedm intermediate and boosted categories.
+ Therefore, we have 13 variables which are common to the three categories.
+
+ In the boosted and intermediate categories, we also include the jet substructure
+ variables introduced in Sect.~\ref{sec:analysis} for the
+ large-$R$ jets: the $k_t$ splitting scales
+ $\sqrt{d_{12}}$, the ratio of 2-to-1 subjettiness $\tau_{12}$,
+ and the ratios of energy correlation functions $C^{(\beta)}_2$ and
+ $D_2^{(\beta)}$.
+ %
+ Therefore, we end up with
+ a total of $N_{\mathrm{var}}=13,17$ and 21 variables for the
+resolved, intermediate, and boosted categories, respectively.
 
 Given that the MVA is able to identify the most discriminatory variables
-and to ignore those that have smaller effects, it is advantageous to
+in an automated way,
+and to ignore those that have little effect, it is advantageous to
 include as many input variables as possible.
@@
 the classification power of the MVA, other than making the GA
-minimization less efficient.
-
-\subsection{Post-MVA signal significance}
+minimization somewhat less efficient.
+
+\subsection{MVA results}
 \label{sec:signalsignificance}
 
-In Fig.~\ref{fig:nnresponse} we show the distribution of
-the ANN output at the end of the training, for the exclusive
+We now present the results of the MVA, first without PU, and then
+later including the effects of PU.
+%
+First of all, in Fig.~\ref{fig:nnresponse} we show the distribution of
+the ANN output at the end of the GA minimization, for the exclusive
 boosted, intermediate and resolved categories.
 %
-The distributions are normalized so that their integral
+All distributions are normalized so that their integral
   adds up to one.
@@
 Therefore,
-the more separated that the two distributions are, the more efficient
+the more differentiated is the distribution of the ANN output
+for signal and background events, the more efficient
 the MVA discrimination will be.
@@
   resolved (lower right plot), as a function of the ANN output.
-  %
-  All distributions are normalized so that their integrals
-  add up to one.
 }
@@
 The performance of the MVA discrimination is similar though slightly worse in the intermediate
-category, and it is markedly worse in the resolved category.
-%
-We have traced back these differences to the use of jet substructure variables
-in the boosted and intermediate categories, whose use substantially
-improves the
-discrimination between signal and background events.
-
+and resolved categories.
+%
 The results for the signal selection efficiency and the 
@@
 define the so-called  Receiver-Operating Characteristic (ROC)
-curve.
+curve, shown in Fig.~\ref{fig:exampleroc}.
 %
 It is clear that we can achieve  high signal efficiency by using
-a small value of the cut in the ANN output, but this choice will be
+a small value of $y_{\rm cut}$, but this choice will be
 affected from a poor background
@@
 %
-Another important requirement on the value of $y_{\rm cut}$ is that
-the  number of expected  signal events (the physical
-events for a given integrated
-luminosity, not the MC events used for the ANN training)
-after the cut is large enough.
-
-In Fig.~\ref{fig:exampleroc} the
-we show the ROC curve for the background rejection rate as a function of the signal
-  selection efficiency as the cut in the ANN output is varied.
-  %
-  We show the results for the three exclusive categories: boosted, intermediate
-  and resolved.
-%
 As could already be inferred from the distribution of neural
 networks output in Fig.~\ref{fig:nnresponse}, we find
-that the neural network MVA is reasonably efficient
+that our MVA is reasonably efficient
 in discriminating signal over background.
@@
 The performance is best in the case of the boosted category,
-decreasing then for the intermediate and finally for the
-resolved categories, consistent with the distributions in
-Fig.~\ref{fig:exampleroc}.
+and then slightly worse in the resolved
+and intermediate categories, consistent with the distributions of
+the ANN outputs from
+Fig.~\ref{fig:nnresponse}.
 %
@@
 \begin{center}
-\includegraphics[width=0.65\textwidth]{plots/roc.pdf}
-\caption{\small ROC curve for the background rejection rate as a function of the signal
-  selection efficiency, as the cut in the ANN output is varied.
-  %
-  We show the results for the three exclusive categories: boosted, intermediate
-  and resolved.
+  \includegraphics[width=0.49\textwidth]{plots/roc_noPU.pdf}
+  \includegraphics[width=0.49\textwidth]{plots/nev2_noPU.pdf}
+\caption{\small Left: ROC curve for the background rejection rate as a function of the signal
+  selection efficiency, as the cut $y_{\rm cut}$
+  in the ANN output is varied.
+  %
+  Right: Number of signal (dashed) and background (solid)
+  events expected at the HL-LHC as a function of the $y_{\rm cut}$.
 }
 \label{fig:exampleroc}
+\label{fig:nev2}
 \end{center}
@@
   categories.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.65\textwidth]{plots/nev2_noPU.pdf}
-\caption{\small Number of signal (dashed lines) and background (solid lines)
-  events expected at the HL-LHC as a function of the cut in the ANN output,
-  for the three separate categories.
-}
-\label{fig:nev2}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-12-08 paper/paperscripts/plotMVAdat_noPU.py

@@ -55,7 +55,7 @@ def plotDiscriminantHisto(name, signal, background,title):
 	legend.get_frame().set_alpha(0.8)
 
 	numpoints = str( len(background) + len(signal) ) + " events: " + str(len(signal)) + " signal, " + str(len(background)) + " background."
-	fig.text(0.33,0.93,title, fontsize=19)
+	fig.text(0.28,0.93,title, fontsize=19)
 
 	figname = name + "_"+Histout+".pdf"
 	fig.savefig(figname)
@@ -94,7 +94,7 @@ nevax2.set_ylabel("Number of background events")
 nevax.set_xlabel("ANN output cut")
 
 nev3, nevax3 = plt.subplots()
-nevax3.set_ylabel("$N_{ev}$ at HL-LHC after MVA cut")
+nevax3.set_ylabel("$N_{ev}$ at HL-LHC",fontsize=18)
 nevax3.set_xlabel("ANN output cut")
 
 # Gridlines
@@ -209,7 +209,7 @@ for idat in xrange(0,len(datafiles)):
 ################################### Finish up ########################################
 
 # Legends
-plt.rcParams.update({'font.size': 19})
+plt.rcParams.update({'font.size': 18})
 rlegend = rocax.legend(loc='best')
 rlegend.get_frame().set_alpha(0.8)
 slegend = sbax.legend(loc='best')
@@ -224,10 +224,11 @@ nev3legend.get_frame().set_alpha(0.8)
 x1,x2,y1,y2 = ssbax.axis()
 ssbax.axis((x1,x2,0,8))
 
+roc.text(0.35,0.93,"HL-LHC, no PU", fontsize=19)
 roc.savefig(ROCout+'.pdf')
 sb.savefig(SBout+'.pdf')
 ssb.savefig(SSBout+'.pdf')
-nev.savefig(NeVout+'.pdf')
+roc.text(0.35,0.93,"HL-LHC, no PU", fontsize=19)
 nev3.savefig(NeV2out+'.pdf')
 
 

### 2015-12-08 paper/sec-analysis.tex
more work on the text

@@
 
+We now study the discrimination power to separate signal
+and background events contained in the jet substructure
+variables.
+%
+In Fig.~\ref{fig:mva_substructure_1}
+we show the distributions of some of
+these substructure variables for the boosted category: the
+$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), for
+the subleading Higgs,
+the energy correlation double ratio $D_2^{(\beta)}$,
+Eq.~(\ref{eq:d2}), for the leading Higgs,
+and then 
+the 2--to--1 subjettiness ratio $\tau_{12}$,
+Eq.~(\ref{eq:tau21}),
+for both the leading and subleading Higgs candidates.
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{plots/split12_h1_C1_boost.pdf} 
+  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_h1_C1_boost.pdf}
+  \caption{\small Distribution of representative substructure variables
+    in the boosted category at the end of the cut-based
+    analysis, used as input to the MVA.
+    %
+    From top to bottom and from left to right we show  the
+$k_t$ splitting scale for
+the subleading Higgs, the subjettiness ratio $\tau_{12}$
+for the leading Higgs,
+and the energy correlation double ratio $D_2$
+for the leading and subleading Higgs.
+%
+}
+\label{fig:mva_substructure_1}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From Fig.~\ref{fig:mva_substructure_1}
+we can observe that for these substructure variables the shapes of the signal
+and background distributions show important differences,
+reflecting the inherent differences in the internal structure of jets
+between QCD jets and jets originated from the Higgs decays.
+%
+Importantly, we observe that signal and background distributions peak
+in different regions: for example, the $k_t$ splitting scale $\sqrt{d_{12}}$
+peaks around 80 GeV (50 GeV) for signal (background) events, while
+the ECF ratio $D_2^{(\beta)}$ peaks at much smaller
+values for signal than
+for background events.
+%
+From Fig.~\ref{fig:mva_substructure_1} we also see
+the distributions of the subjettiness ratio $\tau_{12}$ are similar
+in the leading and in the subleading jets, therefore the information
+contained in
+$\tau_{12}$ from each of the two Higgs candidates  will be to some
+extent redundant.
+
+Therefore, while we don't explicitely have cuts in the substructure
+variables, their discrimination power between signal and
+background events is the motivation to include them
+as input to the MVA, as we will explain in Sect.~\ref{sec:mva}.
+
 \subsection{Impact of pile-up}

### 2015-12-08 paper/sec-mva.tex
more work on the text

@@
 
-From Fig.~\ref{fig:exampleroc} we see that, always starting from the signal
-and background events that survive the basic cut-based analysis,
-one can achieve a  signal
-efficiency of $\sim 90\%$ while reducing the background by
-$80\%$, $60\%$ and $50\%$ in the boosted, intermediate and resolved
-categories respectively.
+It important to verify, for each value of
+the cut in the ANN output $y_{\rm cut}$, how many
+signal and background events are expected at the HL-LHC,
+with an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
 %
-It is easy to translate these factors into an  improvement factor of the pre-MVA
-signal significance $S/\sqrt{B}$.
+This comparison is shown in 
+Fig.~\ref{fig:nev2}.
 %
-As an illustration, if a signal efficiency of 90\%
-is required, we find that the MVA improves $S/\sqrt{B}$
-by  approximately 2.0, 1.4 and 1.3  in the three categories respectively.
-
-As mentioned above, an
- important restriction on the range of allowed cuts in the ANN output
- is that $y_{\rm cut}$
- cannot be so hard that the actual number of signal events expected
-at the HL-LHC becomes unreasonably small.
+As can be seen,
+in the boosted category, for a value $y_{\rm cut}\simeq 0.8$
+we end up with 800 signal events and around $2\cdot 10^4$ background
+events.
 %
-To verify how many signal and background events are left after the MVA cut,
-we show in Fig.~\ref{fig:nev2} the number of signal (dashed lines) and background (solid lines)
-  events expected at the HL-LHC as a function of $y_{\rm cut}$,
-  for the three exclusive categories.
+Similar results are obtained in the intermediate and resolved
+categories: in the former we find 700 ($6\cdot 10^3$) signal (background)
+events for $y_{\rm cut}\simeq 0.8$, and in the latter
+1300 ($8\cdot 10^4$) signal (background) events for
+$y_{\rm cut}\simeq 0.65$.
 %
-  Note that the value of the cut in the ANN cut is separately optimised in the three
-  categories.
-
-As can be seen from Fig.~\ref{fig:nev2}, in the boosted category
-events, with a cut in the ANN output as hard as $y_{\rm cut}\simeq 0.9$,
-we are still left
-with around 100 events at the HL-LHC, 
-which the background being reduced substantially to around
-1000 events.
-%
-A similar cut would work fine for the intermediate category, though here
-the backgrounds are much larger and thus the expected signal significance smaller.
-%
-For the resolved case, the signal significance would be only slightly
-improved for any value of the cut.
+Note that the MVA achieves a very substantial background suppression
+with only a
+moderate reduction of signal efficiency in exchange.
 
@@
 is that they provide direct  physical insight about which of the
-input variables contribute the most to the separation of
-signal over background.
+input variables contribute the most to the separation between
+signal and background.
 %
 In the case of ANNs, this can be quantified by computing the sum
-of the absolute value of al the weights connected to a given
+of the absolute value of all the weights connected to a given
 input neuron $i$, that is
@@
 \label{eq:totweight}
-\omega^{\rm tot}_i \equiv \sum_{k=1}^{n^{(2)}} \Big|\omega^{(2)}_{ki}\Big| \, ,
+\omega^{\rm (tot)}_i \equiv \sum_{k=1}^{n^{(2)}} \Big|\omega^{(2)}_{ki}\Big| \, ,
 \qquad i=1,\ldots,N_{\rm var} \, ,
@@
 %
-The input variables with a larger value of $\omega^{\rm tot}_i$ will be those
+Those input variables with a larger value of $\omega^{\rm (tot)}_i$ will be those
 that play a dominant role in enhancing the signal
 discrimination using the MVA.
-
-%
-In Fig.~\ref{fig:nnweights} we show
-the distribution of the total associated weight,
-Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
-variables of the resolved (left plot) and boosted (right plot) categories.
-%
-The notation for the various kinematic variables is the same
-as in Sect.~\ref{sec:input}.
-%
-The important information
-is contained in the relative strengths of the total associated weight
-for each of the input variables.
-%
-The results of Fig.~\ref{fig:nnweights} illustrate which variables
-are more discriminative between the signal and the background.
-%
-For instance, in the 
-resolved category, the variables that lead to
-a higher discrimination power
-are the $p_T$ of the two reconstructed Higgs candidates, and then on a similar
-footing other variables like the $p_T$ of the individual jets
-and the mass of the di-Higgs system $m_{hh}$.
-%
-The only variable which seems to contain no information at all
-is the $\Delta \phi_{hh}$ separation between the two
-Higgs candidates.
 
@@
 Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
-variables of the resolved (upper left plot),  intermediate (upper right plot)
+variables of the resolved (upper left),  intermediate (upper right)
 and boosted (lower plot)
 categories.
-%
-See Sect.~\ref{sec:input} for a description of each of the input
-variables to the MVA.
 }
@@
 
-For the boosted category, we see that substructure variables
-are the most helpful ones, in particular the $k_t$-splitting scale
-$\sqrt{d_{12}}$ and the subjettiness ratio $\tau_{12}$.
 %
-The ratios of ECFs $D_2^{(\beta)}$ and
-$C_2^{(\beta)}$ also seems to provide
-useful discrimination power.
+In Fig.~\ref{fig:nnweights} we show
+the distribution of the total associated weight,
+Eq.~(\ref{eq:totweight}) for each of the $N_{\rm var}$ input
+variables of the three categories, using the
+notation for the various kinematic variables
+as in Sect.~\ref{sec:input}.
 %
-Concerning other kinematic variables, the angular
-separation between the two large-$R$ jets $\Delta R_{hh}$,
-the invariant mass of the di-Higgs system $m_{hh}$ and the various
-$p_T$ also have discrimination power.
+The important information
+is contained in the relative strengths of the total associated weight
+for each of the input variables.
 %
-Other variables provide limited information, in particular the invariant
-mass of the Higgs candidates, $m_{h_1}$ and $m_{h_2}$: this
-is due to the realistic
-simulation of detector resolution introduced with the smearing.
+In the 
+resolved category, the variables that carry 
+a higher discrimination power
+are the $p_T$ of the two reconstructed Higgs candidates and
+their invariant masses $m_{h1}$ and $m_{h2}$.
 %
-We have verified that the post-MVA
-signal significance in the boosted category is substantially
-degraded if substructure variables are not used.
+In the case of the boosted category, the invariant mass distribution
+of the Higgs candidates is also the most discriminatory
+variable, followed by the subjet $p_T$ distributions and
+substructure variables such as $C_2^{(\beta)}$ and
+$D_2^{(\beta)}$.
 
-At this point we have all the
-information needed to determine the optimal
-value of the MVA output cuts $y_{\rm cut}$
-and quantify the final values of the signal
-significance $S/\sqrt{B}$ and $S/B$ in the three categories.
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/ssb_noPU.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb_noPU.pdf}
+\caption{\small
+  The values of the signal significance, $S/\sqrt{B}$, and of the
+  signal over background ratio, $S/B$, for the boosted, intermediate
+  and resolved categories as  function of the cut
+  $y_{\rm cut}$ in the ANN output.
   %
-These optimal values are determined from the maximisation of $S/\sqrt{B}$,
-ensuring that the number of events $N_{\rm ev}$
-which would be expected at the HL-LHC is large
-enough.
+  The $y_{\rm cut}=0$
+  values correspond to the  cut-based analysis
+  results from Table~\ref{tab:cutflow_noPU_1}.
+}
+\label{fig:sb_mva}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+The results for the signal significance $S/\sqrt{B}$ and
+the signal over background ratio
+$S/B$ as a function of $y_{\rm cut}$
+for the three categories are
+Fig.~\ref{fig:sb_mva}.
 %
-In addition, we also require when fixing $y_{\rm cut}$
-that the actual number of MC events used for the ANN training
-is large enough to avoid the biases of a small training sample.
+The values 
+for $y_{\rm cut}=0$ correspond to those
+the end of the cut-based analysis, see
+Table~\ref{tab:cutflow_noPU_1}.
+%
+We observe how in the three
+ categories there is a marked  improvement in signal
+significance as compared to the pre-MVA results.
+%
+We also observe a substantial enhancement in $S/B$, arising
+from the background suppression indeed by the MVA, reaching
+values of 1\%, 6\% and 3.5\% in the resolved,
+intermediate and boosted categories.
+%
+This improvement in $S/B$ is crucial to ensure the feasibility
+of this measurement, since it allows systematic
+uncertainties in the background determination to
+be at the same level of a few percent level.
 
-These results are summarized in Table~\ref{table:cutflowMVA}, where we indicate
+We now have all the
+information needed to determine a suitable
+value of the MVA output cut $y_{\rm cut}$ in each
+of the three categories.
+%
+These values can be determined from the maximisation of $S/\sqrt{B}$,
+ensuring that the number of signal events $N_{\rm ev}$
+expected at the HL-LHC is not too small.
+%
+In  addition, we require
+that the number of MC events used to define the signal
+category (events with $y_i \ge y_{\rm cut}$)
+is large enough to avoid the biases and statistical
+fluctuations associated to a small training sample.
+%
+In Table~\ref{table:cutflowMVA} where we indicate
 the value of the optimal ANN output
@@
 the number of signal and background events $N_{\rm ev}$ expected
-at the HL-LHC,
-and also $S/\sqrt{B}$ and $S/B$.
+at the HL-LHC as well as $S/\sqrt{B}$ and $S/B$.
 %
@@
   \begin{tabular}{|c|l|c|c|c|c|}
+    \hline
+    \multicolumn{6}{|c|}{No PU} \\
+    \hline
     \hline
@@
 
-The post-MVA results for $S/\sqrt{B}$ and $S/B$ as a function of the cut
-in the ANN output for each of the three categories are shown in
-Fig.~\ref{fig:sb_mva}.
+From Table~\ref{table:cutflowMVA} we see that at the end of the
+MVA the signal significance in the boosted category increases
+from 1.2 to 5.4, with $S/B$ increasing from $0.14\%$ to $3.4\%$,
+with almost 800 signal events expected at the HL-LHC.
 %
-Note that the values of $S/\sqrt{B}$ and $S/B$
-for $y_{\rm cut}=0$ correspond to the values at
-the end of the cut-based analysis, see
-the C2 row of Table~\ref{tab:cutflow_noPU_1}.
+For the intermediate and resolved category, $S/\sqrt{B}$
+increases from 0.9 and 1.0 to 4.8 and 4.5, with
+the signal over background ratio raising from
+$0.12\%$ and $0.03\%$ to 6\% and 1\$, respectively.
 %
-Indeed, at the end of the cut based analysis, the
-signal significance $S/\sqrt{B}$ was
-1.2, 0.9 and 1.0 for the boosted, intermediate and resolved
-categories respectively, consistent with Fig.~\ref{fig:sb_mva}.
+The overall combined significance is thus $S\sqrt{B}\simeq 8$,
+well above the threshold for discovery.
 %
-The same applies to the signal over background ratio $S/B$.
+These remarkable results are however subject to a justified
+criticism:
+the HL-LHC will be a high-PU environment,
+which will affect the description of the various
+kinematical distributions used as input to the MVA.
+%
+Therefore, next we quantify the robustness of the
+results summarized Table~\ref{fig:sb_mva}
+in a realistic high-PU environment.
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.48\textwidth]{plots/ssb_noPU.pdf}
-\includegraphics[width=0.48\textwidth]{plots/sb_noPU.pdf}
-\caption{\small
-  The values of the signal significance $S/\sqrt{B}$ and of the
-  signal over background ratio $S/B$ for the boosted, intermediate
-  and resolved categories as  function of the cut
-  $y_{\rm cut}=0$ in the ANN output.
-  %
-  The $y_{\rm cut}=0$
-  values correspond to the  cut-based analysis
-  results from Table~\ref{tab:cutflow_noPU_1}.
-}
-\label{fig:sb_mva}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-The results of Fig.~\ref{fig:sb_mva}  show that
-for all categories the  improvement in signal
-significance as compared to the pre-MVA results
-is substantial, growing from around 1
-to around 5 in the three cases.
-%
-The optimal values of $y_{\rm cut}$ ensure that the
-number of events at the HL-LHC is still well appreciable: we obtain
-1300, 360 and 800 events in the resolved, intermediate, and
-boosted categories respectively.
-%
-Another important benefit of the MVA applied to the boosted
-category is that fact that the background is substantially
-reduced so that $S/B$ can be as large as 10\% for the optimal
-values of the ANN output cut.
-%
-Note that this is not true for the other two categories,
-where $S/B$ is roughly constant.
-%
-A reasonably large value of $S/B$ is beneficial
-from the experimental point of view, since it indicates
-that the measurement is feasible even if the
-systematic uncertainties are not very small.
-
-From Table~\ref{table:cutflowMVA} we see that after the
-MVA the signal significance in the boosted category increases
-from 0.99 to 3.31, with $S/B$ increasing from $0.005$ to $0.10$,
-with still more that 100 signal events at the HL-LHC.
-%
-Table~\ref{table:cutflowMVA} also shows that for the intermediate
-and resolved categories, the improvement due to the use
-of the MVA is rather moderate, and signal significance is always
-small since backgrounds are still  large.
-%
-The combination of the signal significance of the
-three categories leads to a $S/\sqrt{B}=3.53$, and compared
-to 3.31 using only the boosted category.
-
-Table~\ref{fig:sb_mva} contains the main result of this paper:
-at the HL-LHC, it should be possible to claim evidence of
-Higgs pair production using only the $4b$ final state.
-%
-Needless to say, to claim discovery and to improve the accuracy
-of the measurement of the trilinear coupling it would still
-be needed to combine this channel with others like
-$b\bar{b}\gamma\gamma$ and $b\bar{b}\tau\tau$, but in any case
-it is always important to have robust evidence from
-individual channels.
-
-These remarkable results are however subject to an obvious criticism:
-at the HL-LHC the intense PU is know to substantially affect
-kinematical distributions, and in particular, it is expected to degrade
-in some extent the results of the present analysis.
-%
-To preempt this criticism, in the next section
-we discuss how the expectations for the HL-LHC
-summarized in  Table~\ref{fig:sb_mva} are modified in the presence
-of PU expected at the HL-LHC.
-%
-But before that let us illustrate how the improvement in $S/\sqrt{B}$
-obtained from the MVA in the boosted
-category arises from the information contained in the
-jet substructure variables.
-
-\subsection{Another look at jet substructure variables}
-
-%
-From the distribution of total associated ANN weights in the
-boosted category, shown in Fig.~\ref{fig:nnweights}, we see that
-all substructure variables contain useful information:
-the $k_t$-splitting scales $\sqrt{d_{12}}$,
-the $\tau_{21}$ subjettiness ratio, and the ECF ratios
-$C_2^{(\beta)}$ and $D_2^{(\beta)}$.
-%
-Interestingly, for some substructure variables, such as $\tau_{21}$,
-the total associated weight turns out to be stronger in the leading
-than in the sub-leading Higgs candidate (or vice-versa), indicating some
-degree of redundancy when the same variable is used for the two Higgs candidates
-at the same time.
-
-The information reflected in Fig.~\ref{fig:nnweights} should also be
-apparent from the corresponding distributions of these substructure
-variables: those with a higher discrimination power should show
-clear differences in shape between the signal and background events,
-while those that carry less information should have similar
-shapes for signal and background.
-%
-The third possibility is that of of redundant variables, where signal
-and background exhibit different shapes but the same information
-is already provided by other input variables.
-%
-To illustrate these points,
-in Fig.~\ref{fig:mva_substructure_1}
-we show the distributions of some of
-these substructure variables for the boosted category: the
-$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), for
-the subleading Higgs,
-the energy correlation double ratio $D_2^{(\beta)}$,
-Eq.~(\ref{eq:d2}), for the leading Higgs,
-and then 
-the subjettiness ratio $\tau_{12}$,
-Eq.~(\ref{eq:tau21}),
-for both the leading and subleading Higgs candidates.
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{plots/split12_h1_C1_boost.pdf} 
-  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_C1_boost.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_C1_boost.pdf}
-  \includegraphics[width=0.48\textwidth]{plots/tau21_h1_C1_boost.pdf}
-  \caption{\small Distribution of substructure variables
-    in the boosted category at the end of the cut-based
-    analysis, used as input to the MVA.
-    %
-    From top to bottom and from left to right we show  the
-$k_t$ splitting scale for
-the subleading Higgs, the subjettiness ratio $\tau_{12}$
-for the leading Higgs,
-and the energy correlation double ratio $D_2$
-for the leading and subleading Higgs.
-%
-All distributions have been normalized to unity.
-}
-\label{fig:mva_substructure_1}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-From Fig.~\ref{fig:mva_substructure_1}
-we can observe that for these substructure variables the shapes of the signal
-and background distributions show important differences,
-reflecting the inherent differences in the internal structure of jets
-between QCD jets and jets originated from the Higgs decays.
-%
-Importantly, we observe that signal and background distributions peak
-in different regions: for example, the $k_t$ splitting scale $\sqrt{d_{12}}$
-peaks around 80 GeV (50 GeV) for signal (background) events, while
-the ECF ratio $D_2^{(\beta)}$ peaks at much lower values for signal than
-for background events.
-%
-From Fig.~\ref{fig:mva_substructure_1} we also see
-the distributions of the subjettiness ratio $\tau_{12}$ are quite similar
-in the leading and in the subleading jets, therefore adding
-$\tau_{12}$ from the two Higgs candidates to the MVA at the same time
-is redundant, explaining why in these cases either one or the other
-variable from a Higgs candidate is assigned higher weight.
-
-It is also interesting to show the distributions of kinematic variables
-that according to the MVA provide a small amount of discrimination
-between signal and background, and where the should not be an issue
-of redundancy.
-%
-In Fig.~\ref{fig:mva_substructure_2}
-we show the kinematic variable that carries less weight in the MVA,
-    the azimuthal angle separation between the two Higgs candidates
-    $\Delta\phi_{hh}$, for the resolved and boosted categories:
-    according to Fig.~\ref{fig:nnweights}, essentially no discrimination power
-    should be obtained from this variable, and indeed the shapes of the two signal
-    and background
-    are very similar here.
-    %
-    From Fig.~\ref{fig:nnweights} we also saw that the
-    invariant mass distributions $m_h$ carry little information
-    to discriminate signal over background:
-    this was already verified from 
-the corresponding
-distributions in Fig.~\ref{fig:mHHinv}.
-%
-As explained before, the reduced discrimination power arises
-from 
-the  smearing of jet four-momenta introduced to mimic
-realistically detector resolution.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-  \begin{center}
-  \includegraphics[width=0.48\textwidth]{plots/DeltaPhi_HH_C1_res.pdf} 
-  \includegraphics[width=0.48\textwidth]{plots/DeltaPhi_HH_C1_boosted.pdf} 
-  \caption{\small Same as Fig.~\ref{fig:mva_substructure_1},
-    now for the kinematic variable that carries less weight in the MVA,
-    the azimuthal angle separation between the two Higgs candidates
-    $\Delta\phi_{hh}$, for the resolved and boosted categories.
-}
-\label{fig:mva_substructure_2}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Impact of PU}
+\subsection{Impact of PU in the MVA}
 
@@
   \begin{tabular}{|c|l|c|c|c|c|}
+     \multicolumn{6}{|c|}{$\la n_{\rm PU}\ra=80$+SK} \\
     \hline

### 2015-12-08 paper/sec-mva.tex
more work on the MVA section

@@
 
-The main limitation of our analysis so far is the fact that
-pile-up (PU) effects have not been accounted for
-not accounted for.
+In this section we study how the MVA results are modified when
+signal and background events are embedded in a high-PU environment.
 %
-However, any realistic feasibility study at the HL-LHC, specially
-one 
-such the present that relies on the careful modeling
-of kinematic distributions,
-requires assessing the robustness of the conclusions
-with respect to the inclusion of PU.
+The simulation of PU and the corresponding subtraction with
+{\tt SoftKiller} have been performed as described
+in Sect.~\ref{sec:pileup}.
 %
-In this section, we show how our qualitative results, in particular
-the enhanced signal significance provided by the MVA, are robust
-in the presence of  PU.
-
-First of all, we describe the simulation of the 
-PU conditions  expected at the HL-LHC, and discuss the settings of
-the PU subtraction strategy that we adopt.
+Following this, the cut-based analysis and the subsequent
+MVA optimization have been applied using the same
+settings as in the case without PU.
 %
-Then we present the validation of the PU subtraction,
-and compare a number of distributions, including substructure variables,
-with and without PU.
+In Table~\ref{tab:cutflow_SKPU80_1} we provide the results
+of the cut-based analysis cut-flow, for the case with $\la n_{\rm PU}\ra=80$+SK.
 %
-Finally we revisit the MVA analysis of Sect.~\ref{sec:mva}, and
-show that our qualitative conclusions are robust
-in the presence of realistic PU conditions, finding
-a combined
-signal significance of $S/\sqrt{B}\simeq 4$.
-
-The same settings of the cut-based analysis,
-Sects.~\ref{sec:analysis} and~\ref{sec:results}, and
-the subsequent MVA optimization, Sect.~\ref{sec:mva}, have
-been applied to the samples with PU, $\la n_{\rm PU}\ra=80$,
-and SK subtraction.
-%
-The corresponding version of Table~\ref{tab:cutflow_noPU_1}, the 
-cut-flow for the cross-sections and signal significance at the various
-steps of the cut-based analysis, 
-in the case
-of PU subtracted with SK, for $\la n_{\rm PU}\ra=80$,
-is presented in Table~\ref{tab:cutflow_SKPU80_1}.
-%
-One immediate observation is that
-at the end of the cut-based analysis,
-the signal significance have been  degraded
+It is clear that the pre-MVA 
+signal significance have been seriously degraded
 as compared to the case without PU.
 %
-We now obtain values for $S\sqrt{B}$ of 0.4, 0.3 and 0.9, in the resolved,
+We now find values for $S/\sqrt{B}$ of 0.4, 0.3 and 0.9, in the resolved,
 intermediate and boosted categories, respectively, to be compared
@@
 %
-Therefore, the pre-MVA signal significance is degraded by a factor 4 in
-the resolved and the intermediate categories,
-and by a factor 3 in the boosted category.
-%
-The fact that the latter is the  least affected one
-can be understood from the previous comparison
-plots, which show that effects of PU contamination
-are milder due to the  selection requirements
-of the boosted category.
 
@@
 
+Following the cut-based analysis, the surviving signal and background
+MC events in the case of PU are used to re-train the MVA.
+%
 In Table~\ref{table:cutflowMVA_PU}
-we provide the  the number of signal and
+we provide  the number of signal and
     background events expected
-    at the HL-LHC, as well as the
+    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$,
+    as well as the
     corresponding values for $S/\sqrt{B}$ and $S/B$,
@@
     %
-    The same results without PU are those of
-    Table.~\ref{table:cutflowMVA}.
-    %
-    From Table~\ref{table:cutflowMVA_PU} we see that, thanks
-to the MVA, we can improve the signal significance and the
-signal over background ratio from 0.35 and $4\cdot 10^{-4}$
+    From Table~\ref{table:cutflowMVA_PU} we observe that, thanks
+to the MVA, the signal significance and the
+signal over background ratio are improved from 0.35 and $4\cdot 10^{-4}$
 (0.25 and $1\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
@@
 %
-The intermediate category exhibits a rather lower value of $S/\sqrt{B}$
-for the optimal $y_{\rm cut}$ value, around 1.1.
+The intermediate category, on the other hand, exhibits a rather lower post-MVA value of $S/\sqrt{B}$, around
+1.1.
 %
@@
 final state
-at the HL-LHC, also when PU is included.
-%
-However, important information will also be obtained from
-the resolved category, which has a signal significance
-only slightly smaller than the boosted case.
+at the HL-LHC, also for the case of a high-PU environment, and that
+important information will also be obtained from
+the resolved category, which has a comparable significance.
 
@@
   \begin{tabular}{|c|l|c|c|c|c|}
+        \hline
      \multicolumn{6}{|c|}{$\la n_{\rm PU}\ra=80$+SK} \\
+     \hline
          \hline
@@
     & 0.25    &  $1.3\cdot 10^{-4}$  \\
-    &  $y_{\rm cut}=0.65$ & 430  & $3\cdot 10^4$  &  2.5   & 0.15  \\
+    &  $y_{\rm cut}=0.65$ & 430  & $3\cdot 10^4$  &  2.5   & 0.015  \\
     \hline
@@
 %
-Our analysis also indicates a possible way forward to
-further increase $S/B$: reducing the background from light and charm
-fakes, see Table~\ref{tab:cutflow_SKPU80_1}.
+As in the case without PU, 
+this analysis  indicates that a substantial increase in both
+$S/B$ and $S/\sqrt{B}$ could be achieved by reducing the background component
+that arises from the mis-identification of light and charm
+fakes, compare for in particular the columns $S/\sqrt{B_{\rm tot}}$
+and  $S/\sqrt{B_{\rm 4b}}$ in  Table~\ref{tab:cutflow_SKPU80_1}.
 
-Let us now discuss in more detail the results of the MVA
-classification, by showing various estimators as function
-of the cut $y_{\rm cut}$ in the ANN discriminant.
-%
 In Fig.~\ref{fig:nev2_PU}
@@
 are expected at the HL-LHC as a function of
-$y_{\rm cut}$ -
-the corresponding results without PU are those of
-Fig.~\ref{fig:nev2}.
+$y_{\rm cut}$ and the corresponding ROC curve
 %
-As we can see, the general trends are
-similar as those without PU.
-%
-Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we also observe
+Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we observe
 that the intermediate category is substantially degraded once PU effects
@@
   \begin{center}
-\includegraphics[width=0.65\textwidth]{plots/nev2_SKPU80.pdf}
+    \includegraphics[width=0.49\textwidth]{plots/roc_SKPU80.pdf}
+\includegraphics[width=0.49\textwidth]{plots/nev2_SKPU80.pdf}
 \caption{\small Same as Fig.~\ref{fig:nev2} in the
@@
 we still manage to achieve a signal significance of
-around $S/\sqrt{B}\simeq 2.5$ separately for the boosted and resolved
+around $S/\sqrt{B}$ between 2.5 and 3.0
+separately for the boosted and resolved
 categories.
 %
-On the other hand, the intermediate category becomes irrelevant.
+On the other hand, the intermediate category becomes marginal.
 %
@@
 %
-In addition, also the $p_T$ distributions of the AK03
+In addition, also the $p_T$ distributions of the AKT03
 subjets within the large-$R$
@@
 
-At this point, we can finally combine the three categories, resolved,
+We can finally combine the three categories, resolved,
 intermediate and boosted, and determine the overall signal
-significance taking into account all event topologies.
-%
-Adding in quadrature the signal significance from the three
-(exclusive) categories for the corresponding
-optimal value of $y_{\rm cut}$, our final combined result, accounting
-for PU effects, is
+significance, finding
 \be
@@
 well the threshold for evidence, and even meeting the
-requirement for discovery might be within reach.
+requirements for discovery might be within reach provided it is possible
+to suppress the background from light and charm jet mis-identifications.
+
+For the Run II luminosity, $\mathcal{L}=300$ fb$^{-1}$, one finds
+instead $\lp S/\sqrt{B}\rp_{\rm tot} \simeq 1.3$, which increases up to
+$\lp S/\sqrt{B}\rp_{\rm tot} \simeq 2.6$ if only the QCD $4b$ background is included.
 %
-
-In summary, in this section we have demonstrated the robustness
-of our results under the presence of PU conditions as those
-expected at the HL-LHC.
+This indicates that, interestingly, accessing Higgs pair production at Run II,
+while still extremely challenging, does not seem to be completely impossible.
 %
-With a signal significance of $S/\sqrt{B}\sim 4$, is clear that
-the $b\bar{b}b\bar{b}$ final state can be used to claim evidence
-for Higgs pair production at the HL-LHC without the need
-to combine with any other final state.
+In addition, at Run II the average number of PU collisions is substantially
+reduced as compared to the HL-LHC environment.
 %
-Our analysis certainly contains
-room for improvement, in particular by means of a tailored
-study dedicated to optimize PU subtraction in this process.
-%
-It will be important now to quantify the precision of
-a extraction of the Higgs trilinear coupling $\lambda$ using
-the techniques presented here, but this is left for future work.
+Therefore, it will be interesting to see if improvements in experimental $b$-jet
+reconstruction and fake rejection at Run II are able to fulfill this
+potential.
 

### 2015-12-10 paper/sec-mcsamples.tex
polishing paper

@@
 to lead to a mass resolution of
-reconstructed Higgs candidates of around 10 GeV, consistent
-with the hadronic mass resolutions of ATLAS and CMS~\cite{Aad:2012gxa,Chatrchyan:2013zna,Aad:2014xzb}.
+the reconstructed Higgs candidates of around 10 GeV, consistent
+with the hadronic mass resolutions of the
+ATLAS and CMS detectors~\cite{Aad:2012gxa,Chatrchyan:2013zna,Aad:2014xzb}.
 %
-In Fig.~\ref{fig:higgs-mass-resolution} we show the
-invariant mass distributions of 
-Higgs candidate in signal events for the
-resolved category (see Sects.~\ref{sec:analysis}
-and~\ref{sec:results}), together with
-a Gaussian fit,
-used to determine the mass resolution.
+By fitting a Gaussian to the 
+invariant Higgs mass distributions of 
+in signal events, we can 
+determine the effective mass resolution
+in the present analysis.
 %
-We indeed  find a mass resolution of about 8\%, corresponding
-    to around 10 GeV for $m_h=125$ GeV.
+We find a resolution of about 8\% in the resolved
+category, corresponding to a window
+of around 10 GeV for $m_h=125$ GeV.
 %
-    For completeness, in Fig.~\ref{fig:higgs-mass-resolution}
-    we also show the corresponding
-    mass distributions of Higgs candidates
+Fitting the Higgs    mass distributions 
 in the case of $\la n_{\rm PU}\ra=80$ PU events
-    subtracted with {\tt SoftKiller} (see Sect.~\ref{sec:pileup}).
+with subtraction
+(see Sect.~\ref{sec:pileup}),
+the mass resolution is degraded down to
+    around 11\%, corresponding to a windown of
+    14 GeV around the Higgs mass.
     %
-    In the case of PU, the mass resolution is degraded down to
-    around 11\%, corresponding to 
-    14 GeV.
-    %
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-  \begin{center}
-    \vspace{-1cm}
-  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_noPU.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_PU80.pdf}
-  \caption{\small The invariant mass distributions of the leading
-    Higgs candidates in signal events for the resolved category, without
-    PU (left plot) and with PU (right plot),
-    together with Gaussian fits  used to determine the mass resolution.
-    %
-    In the latter case, $\la n_{\rm PU}\ra=80$, with {\tt SoftKiller}
-     used for PU subtraction.
-}
-\label{fig:higgs-mass-resolution}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-12-10 paper/sec-mva.tex
polishing paper

@@
   The $y_{\rm cut}=0$
-  values correspond to the  cut-based analysis
-  results from Table~\ref{tab:cutflow_noPU_1}.
+  results are those at the end of the cut-based
+  analysis.
 }
@@
 The values 
-for $y_{\rm cut}=0$ correspond to those
-the end of the cut-based analysis, see
-Table~\ref{tab:cutflow_noPU_1}.
+for $y_{\rm cut}=0$ correspond to those at
+the end of the cut-based analysis.
 %
@@
 %
-In Table~\ref{tab:cutflow_SKPU80_1} we provide the results
-of the cut-based analysis cut-flow, for the case with $\la n_{\rm PU}\ra=80$+SK.
+In Table~\ref{table:cutflowMVA_PU} we provide the results
+  at the end of the cut-based analysis,
+for the case with $\la n_{\rm PU}\ra=80$+SK.
 %
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[t]
-  \centering
-  \scriptsize
-  \input{tables/table_SKPU80_1.tex}
-  $\,$ \\
-  \vspace{0.5cm}
-  \input{tables/table_SKPU80_2.tex}
-  $\,$ \\
-  \vspace{0.5cm}
-    \input{tables/table_SKPU80_3.tex}
-    \caption{\small
-      Same as Table~\ref{tab:cutflow_noPU_1}, for the analysis
-      including PU with $\la n_{\rm PU}\ra=80$ and SK subtraction.
-      \label{tab:cutflow_SKPU80_1}}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Following the cut-based analysis, the surviving signal and background
+Subsequently to 
+ the cut-based analysis, the surviving signal and background
 MC events in the case of PU are used to re-train the MVA.
@@
 In Table~\ref{table:cutflowMVA_PU}
-we provide  the number of signal and
+we also provide  the number of signal and
     background events expected
@@
 that arises from the mis-identification of light and charm
-fakes, compare for in particular the columns $S/\sqrt{B_{\rm tot}}$
-and  $S/\sqrt{B_{\rm 4b}}$ in  Table~\ref{tab:cutflow_SKPU80_1}.
+fakes.
 

### 2015-12-10 paper/sec-analysis.tex
More work on pheno paper

@@
     in the boosted category at the end of the cut-based
-    analysis, used as input to the MVA.
+    analysis, to be used as input to the MVA.
     %
     From top to bottom and from left to right we show  the
-$k_t$ splitting scale for
-the subleading Higgs, the subjettiness ratio $\tau_{12}$
-for the leading Higgs,
-and the energy correlation double ratio $D_2$
-for the leading and subleading Higgs.
-%
+    $k_t$ splitting scale, the energy correlation double ratio $D_2^{(\beta)}$
+    and the  subjettiness ratio $\tau_{21}$ for the leading
+    Higgs, as well as $\tau_{21}$ also for the subleading Higgs.
 }
@@
 
-Therefore, while we don't explicitely have cuts in the substructure
+Therefore, while we do not explicitly have cuts in the substructure
 variables, their discrimination power between signal and

### 2015-12-10 paper/paperscripts/plotHist_EEC_C2_h0_C1_boost.py

@@ -1,0 +1,135 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "EEC_C2_h0_C1_boost"
+
+linestyles = [ 'solid', 'dashed','solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_C2_fj1_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_C2_fj1_boost_C1e.dat")
+
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+
+# Axis labels
+xLabel = r"ECF ratio $C_2^{(\beta)}$ in leading Higgs candidate"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'b', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,0.5])
+ax.set_ylim([0,8])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-12-10 paper/paperscripts/plotHist_split12_h1_C1_boost.py

@@ -1,0 +1,135 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "split12_h1_C1_boost"
+
+linestyles = [ 'solid', 'dashed','solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_split12_fj1_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_split12_fj1_boost_C1e.dat")
+
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+
+# Axis labels
+xLabel = r"$k_T$ splitting scale $\sqrt{d_{12}}$ in leading Higgs candidate (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'b', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,150])
+ax.set_ylim([0,0.02])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-12-10 paper/sec-conclusions.tex
Work on conclusions

--- 2015-11-17 paper/sec-conclusions.tex
@@
 
-In this work, we have presented a detailed study of the feasibility
-of the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
-final state at the High-Luminosity LHC.
+In this work we have presented a feasibility study for
+ the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
+final state at the High-Luminosity LHC with $\mathcal{L}=3$ ab$^{-1}$.
 %
-Our strategy is based on the combination of a traditional
-cut-based analysis with modern multivariate analyses,
-which allows improving the signal significance of this channel
-as compared to previous studies.
+Our strategy was based on the combination of a traditional
+cut-based analysis with state-of-the-art multivariate techniques.
 %
-Following a careful optimisation of the
-signal reconstruction strategy for different event topologies,
-we find that the highest significance is obtained
-in the 
-boosted category, while complementary information is also provided
-by the intermediate and resolved categories.
+We take into account 
+all relevant backgrounds, in particular
+QCD multijets, both  the irreducible $4b$
+and the reducible 
+$2b2j$ and $4j$ components.
 %
+We illustrate how the $2b2j$ component leads to
+a contribution comparable to that of the $4b$ process,
+due to a combination of  parton shower effects, $b$-quark 
+pair radiation, and selection requirements.
+%
+Since any realistic study of the feasibility of Higgs pair
+production at the HL-LHC should take into account the
+high-PU environment in which such measurement will be performed,
+in this work we have demonstrated the robustness of our analysis strategy
+under high-PU conditions.
 
-Our analysis takes into account 
-all relevant backgrounds, in particular
-the dominant QCD multijets.
+Combining the contributions from the resolved,
+intermediate and boosted categories, we find that, for
+$\mathcal{L}=3$ ab$^{-1}$, the
+signal significance for
+the production of Higgs pairs can be as large as $S/\sqrt{B}\simeq 4.0$.
 %
-We include not only the irreducible $4b$ component, but
-also the $2b2j$ and $4j$ backgrounds, which contribute
-to the yield of reconstructed Higgs candidates
-when light partons are mistagged as $b$-quarks.
-%
-We show that neglecting the contribution
-from  fakes is a poor approximation, specially for the resolved and intermediate
-categories.
-%
-The reason is that
-the impact of fakes
-can be substantially enhanced, when compared to a naive parton
-level estimate, due to combinatorics and $b\bar{b}$
-pair radiation during the parton shower.
-
-A major difficulty in measurements involving relatively low $p_T$
-jets at the HL-LHC is the large
-amount of PU expected.
-%
-To account for this, we have simulated realistic PU conditions
-and used the recently developed {\tt SoftKiller} method to reduce
-the PU contamination.
-%
-We find that, especially in the boosted category, the impact of
-PU after its subtraction is rather mild, and in particular the jet
-substructure variables, which carry substantial
-discrimination information, are reasonably robust against PU effects.
-
-For a PU of $\la n_{\rm PU}\ra=150$, along what is expected
-at the HL-LHC, our main result is that the combined
-signal significance for the three categories is $S/\sqrt{B}\simeq 4.0$,
-substantially improving previous studies.
-%
-Therefore, we conclude that, already from the $b\bar{b}b\bar{b}$
-final state alone,
+This indicates that already from the $b\bar{b}b\bar{b}$
+final state alone
 it should be possible to claim evidence for Higgs pair production at
@@
 %
-This  estimate for $S/\sqrt{B}$  could
-be further enhanced,
-in particular following an optimization of the PU subtraction
-strategy.
+Our study also suggests possible avenues that the LHC experiments
+could explore to further improve this signal significance.
+%
+One handle could be to reduce the contribution from light and charm
+jet mis-identification, ensuring that the
+$2b2j$ component is subdominant over the $4b$ background.
+%
+Another possibility is to improve the mass resolution of the Higgs
+reconstruction
+in high-PU environments, and, more in general,
+to optimize the PU subtraction
+strategy, to reduce the impact of PU in the modelling
+of kinematical variables, an effect that worsens the MVA discrimination.
+%
+Following these and related improvements in the experimental
+analysis, it might be feasible to achieve
+an observation of Higgs pair production even with only
+$\mathcal{L}=300$ fb$^{-1}$.
 
-One important implication of our study is that it should
+One important implication of this work is that it should
 be possible to improve  the accuracy on the extraction of
@@
 %
-A determination of $\lambda$ in our approach would require
- however a substantial
- amount of work, involving
+A determination of $\lambda$ in our approach is rather
+non-trivial, involving
  not only regenerating signal samples
@@
 compare with the corresponding  precision 
-that has been obtained in other final states.
+that has been obtained in other final states such as
+ $b\bar{b}\gamma\gamma$
+and $b\bar{b}\tau\tau$.
 %
-It will be in particular interesting to contrast
-with the extraction of $\lambda$ from the
- $b\bar{b}\gamma\gamma$
-and $b\bar{b}\tau\tau$ final states, that, while having
-smaller rates as compared to $b\bar{b}b\bar{b}$,
-benefit from reduced backgrounds.
+It will also be  interesting to perform
+this exercise for a 100 TeV hadron collider~\cite{Barr:2014sga,
+  Azatov:2015oxa,Papaefstathiou:2015iba,
+  Arkani-Hamed:2015vfh}.
 %
+While signal yields will be certainly increased, also the (gluon-driven) QCD
+multijet background will grow strongly.
+%
+Revisiting
+the present analysis, including the MVA optimization,
+at 100 TeV, will allow us
+to assess the accuracy of an extraction of the trilinear
+coupling $\lambda$ from the $b\bar{b}b\bar{b}$ final state
+at 100 TeV.
 
@@
 operators that can be obtained from measurements
-of various $hh\to b\bar{b}b\bar{b}$ distributions.
+of various kinematical distributions
+in the $hh\to b\bar{b}b\bar{b}$ process.
 %
@@
 that modify the high-energy behavior
-of the theory, in particular
-since it becomes possible
+of the theory, for instance,
+it would become possible
 to access the tail of the $m_{hh}$ distribution.
@@
 %
-In order to explore efficiency the BSM parameters
+In order to explore efficiently the BSM parameters
 without having to repeat the full analysis
-for each point, modern techniques
+for each point, modern statistical techniques
 such as the Cluster Analysis method proposed
-in Ref.~\cite{Dall'Osso:2015aia} could be useful.
-
-Finally, it would be interesting to estimate the prospects for
-Higgs pair production in the $b\bar{b}b\bar{b}$  final
-state at a Future Circular
-Collider (FCC) with a center of mass energy of
-100 TeV~\cite{Barr:2014sga,Azatov:2015oxa,Papaefstathiou:2015iba}.
-%
-While signal yields would be certainly increased, also the QCD
-multijet background would grow, so it would necessary to repeat
-our analysis, including full background simulation, at 100 TeV,
-and assess if the accuracy in the extraction of the trilinear $\lambda$
-is improved or degraded as compared to the 14 TeV case.
-%
+in Ref.~\cite{Dall'Osso:2015aia} might be helpful.
 
@@
 {\bf\noindent  Acknowledgments \\}
-We thank R.~Contino, A.~Papaefstathiou and
+We thank F.~Bishara, R.~Contino, A.~Papaefstathiou and
 G.~Salam for useful discussions on the topic
@@
 %
-We thank E.~Vrodynou and M.~Zaro for assistance with di-Higgs production
+We thank E.~Vrodynou and M.~Zaro for
+assistance with di-Higgs production
   in {\tt MadGraph5\_aMC@NLO}.

### 2015-12-10 paper/sec-mva.tex
work on MVA section

@@
 %
-Following this, the cut-based analysis and the subsequent
-MVA optimization have been applied using the same
+The cut-based analysis and the subsequent
+MVA optimization have been performed using exactly the same
 settings as in the case without PU.
@@
 It is clear that the pre-MVA 
-signal significance have been seriously degraded
+signal significance has been degraded
 as compared to the case without PU.
 %
-We now find values for $S/\sqrt{B}$ of 0.4, 0.3 and 0.9, in the resolved,
+We now find values for $S/\sqrt{B}$ of 0.25, 0.15 and 0.31, in the resolved,
 intermediate and boosted categories, respectively, to be compared
-with the corresponding values without PU, namely 1.6, 1.6 and 2.7.
+with the corresponding values without PU, namely 1.0, 0.9 and 1.0,
+see Table~\ref{table:cutflowMVA}. 
 %

### 2015-12-10 paper/paperscripts/plotMVAdat_PU.py

@@ -15,9 +15,9 @@ datafiles=[ "../plotdata/results_SK_PU80/MVA/nn_13X5X3X1_50000-Gen_SKPU80_res.da
             "../plotdata/results_SK_PU80/MVA/nn_21X5X3X1_50000-Gen_SKPU80_bst.dat"]
 
 datanames=[ "Resolved","Intermediate","Boosted"]
-titlenames=[ "Resolved Category,  $n_{PU}=80$+SK",
-             "Intermediate Category,  $n_{PU}=80$+SK",\
-             "Boosted Category,  $n_{PU}=80$+SK"]
+titlenames=[ r"Resolved Category,  $\langle n_{PU}\rangle =80$+SK",
+             r"Intermediate Category,  $\langle n_{PU}\rangle =80$+SK",\
+             r"Boosted Category,  $\langle n_{PU}\rangle=80$+SK"]
 
 
 # HL-LHC luminosity

### 2015-12-10 paper/sec-analysis.tex
quasi final version of the paper

--- 2015-12-08 paper/sec-analysis.tex
@@
 
+We now study the discrimination power to separate signal
+and background events contained in
+jet substructure
+variables.
+%
+In Fig.~\ref{fig:mva_substructure_1}
+we show the distributions of representative
+ substructure variables for the boosted category: the
+$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), 
+the ECF ratio $C_2^{(\beta)}$,
+Eq.~(\ref{eq:c2}), and
+the 2--to--1 subjettiness ratio $\tau_{12}$, Eq.~(\ref{eq:tau21}),
+all for the leading
+Higgs candidates, as we as also $\tau_{12}$ for the subleading
+Higgs candidates.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{plots/split12_h1_C1_boost.pdf} 
+  \includegraphics[width=0.48\textwidth]{plots/EEC_C2_h0_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_h0_C1_boost.pdf}
+  \includegraphics[width=0.48\textwidth]{plots/tau21_h1_C1_boost.pdf}
+  \caption{\small Distribution of representative substructure variables
+    in the boosted category at the end of the cut-based
+    analysis, to be used as input to the MVA.
+    %
+    From top to bottom and from left to right we show  the
+    $k_t$ splitting scale, the energy correlation ratio $C_2^{(\beta)}$
+    and the  subjettiness ratio $\tau_{21}$ for the leading
+    Higgs, as well as $\tau_{21}$ also for the subleading Higgs.
+}
+\label{fig:mva_substructure_1}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From Fig.~\ref{fig:mva_substructure_1}
+we can observe how for these substructure variables the shapes of the signal
+and background distributions reflect
+the inherent differences in the internal structure of jets
+between QCD jets and jets originated from the Higgs decays.
+%
+Crucially, signal and background distributions peak
+in rather
+different regions: for example, the $k_t$ splitting scale $\sqrt{d_{12}}$
+peaks around 80 GeV (40 GeV) for signal (background) events, while
+the distribution of the
+ECF ratio $C_2^{(\beta)}$ is concentrated at small values
+for signal but is much broader for background events.
+%
+From Fig.~\ref{fig:mva_substructure_1} we also see
+the distributions of the subjettiness ratio $\tau_{12}$ are
+reasonably similar
+for both the leading and in the subleading jets, therefore the information
+contained in
+this (and other substructure variables)
+from each of the two Higgs candidates  will be to some
+extent redundant.
+
+Therefore, while we do not explicitly have cuts in the substructure
+variables, their discrimination power between signal and
+background events is the motivation to include them
+as input to the MVA, as we will explain in Sect.~\ref{sec:mva}.
+
 \subsection{Impact of pile-up}
@@
 is beyond the scope of this paper to fully optimize
-PU subtraction,
+the PU subtraction.
 

### 2015-12-10 paper/paperscripts/plotHist_pt_H0_bst_noPU.py

@@ -124,7 +124,7 @@ ax.xaxis.grid(True)
 ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.25,0.93,"Boosted category, $n_{PU}=0$", fontsize=20)
+fig.text(0.25,0.93,r"Boosted category, $\langle n_{PU}\rangle=0$", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-11 paper/sec-analysis.tex
added table

@@
 
-Finally, can perform a similar comparison for
+We can also perform a similar comparison for
 the resolved category.
@@
 
+To complete this discussion, it is illustrative to determine
+which is the mass resolution obtained for the
+reconstructed Higgs candidates in various cases.
+%
+In Table~\ref{tab:massresolution}
+we indicate the shift of the invariant mass peak as compared
+to the nominal Higgs mass, $\delta m_h$, as well as the
+corresponding width of the distribution, $\sigma_{m_h}$,
+obtained from fitting a Gaussian to the mass distributions
+of both the leading and subleading Higgs candidates in
+the resolved category.
+        %
+        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
+        but without subtraction, and the same with SK subtraction.
+%
+        We find a mass resolution of around 9 GeV in the case
+        without PU, which is only slightly degraded
+        to around 11 GeV in the case of $\la n_{\rm PU}\ra=80$ PU
+        with SK subtraction.
+        %
+        We also note that, after subtraction, the peak of
+        the invariant mass distributions of Higgs candidates
+        coincides with the nominal values of $m_h$ within a few GeV.
+
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{table}[h]
+      \centering
+      \begin{tabular}{|c|c|c|c|}
+        \hline
+        &   &   $\delta m_h$  &  $\sigma_{m_h}$  \\
+        \hline
+        \hline
+        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & 8 GeV   \\
+          & subleading Higgs   & -5.8 GeV  &  9 GeV \\
+        \hline
+          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & 9 GeV   \\
+          & subleading Higgs   & +31 GeV  &  12 GeV \\
+          \hline
+            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & 11 GeV   \\
+          & subleading Higgs   & +2.1 GeV  &  11 GeV \\
+        \hline
+        \end{tabular}
+      \caption{\label{tab:massresolution}
+        Resolution of the invariant mass distribution of
+        reconstructed Higgs candidates in the resolved
+        category.
+        %
+        We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
+        but without subtraction, and the same with SK subtraction.
+        %
+        We indicate the shift of the invariant mass peak as compared
+        to the nominal Higgs mass, $\delta m_h$, as well as the width
+        of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,
+        for both the leading and subleading Higgs candidates.
+      }
+      \end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-11 paper/sec-mcsamples.tex
added table

@@
 to lead to a mass resolution of
-the reconstructed Higgs candidates of around 10 GeV, consistent
+the reconstructed Higgs candidates consistent
 with the hadronic mass resolutions of the
-ATLAS and CMS detectors~\cite{Aad:2012gxa,Chatrchyan:2013zna,Aad:2014xzb}.
+ATLAS and CMS detectors~\cite{Aad:2012gxa,Chatrchyan:2013zna,Aad:2014xzb},
+as discussed in Sect.~\ref{sec:pileup}.
+
 %
-By fitting a Gaussian to the 
-invariant Higgs mass distributions of 
-in signal events, we can 
-determine the effective mass resolution
-in the present analysis.
-%
-We find a resolution of about 8\% in the resolved
-category, corresponding to a window
-of around 10 GeV for $m_h=125$ GeV.
-%
-Fitting the Higgs    mass distributions 
-in the case of $\la n_{\rm PU}\ra=80$ PU events
-with subtraction
-(see Sect.~\ref{sec:pileup}),
-the mass resolution is degraded down to
-    around 11\%, corresponding to a windown of
-    14 GeV around the Higgs mass.
-    %
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-11 paper/sec-conclusions.tex

@@
 all relevant backgrounds, in particular
-QCD multijets, both  the irreducible $4b$
+the irreducible $4b$
 and the reducible 
-$2b2j$ and $4j$ components.
+$2b2j$ and $4j$ QCD multijets.
 %
@@
 %
-Another possibility is to improve the mass resolution of the Higgs
+Another possibility would be to improve the mass resolution of the Higgs
 reconstruction
@@
 to optimize the PU subtraction
-strategy, to reduce the impact of PU in the modelling
-of kinematical variables, an effect that worsens the MVA discrimination.
+strategy, in order
+to reduce the impact of PU in the modelling
+of kinematical variables and the associated
+degradation of the MVA discrimination.
 %
@@
 %
-A determination of $\lambda$ in our approach is rather
+A determination of $\lambda$ in our approach is however
+rather
 non-trivial, involving
@@
 compare with the corresponding  precision 
-that has been obtained in other final states such as
+that has been reported from other final states such as
  $b\bar{b}\gamma\gamma$
@@
 
-Our analysis relies on the careful modeling of kinematical
+Our strategy relies on the modeling of the kinematical
 distributions of signal and background events, since these provide
@@
 %
-We thus plan to study which are the constraints
+We thus plan to study the constraints
 on the coefficients of these effective

### 2015-12-11 paper/sec-mva.tex

@@
   at the end of the cut-based analysis,
-for the case with $\la n_{\rm PU}\ra=80$+SK.
+  for the case with $\la n_{\rm PU}\ra=80$ with SK
+  subtraction.
 %
@@
 Subsequently to 
- the cut-based analysis, the surviving signal and background
-MC events in the case of PU are used to re-train the MVA.
+ the cut-based analysis, the signal and background
+ MC events in the case of PU satisfying all selection cuts
+  are used to re-train the MVA.
 %
@@
     to $y_{\rm cut}=0$) and after the
-    optimal MVA cut, for the simulations
-    with $\la n_{\rm PU}\ra=80$
-    and SK subtraction.
+    optimal MVA cut.
     %
@@
 to the MVA, the signal significance and the
-signal over background ratio are improved from 0.35 and $4\cdot 10^{-4}$
-(0.25 and $1\cdot 10^{-4}$) up to 2.9 and 0.034 (2.5 and 0.15)
+signal over background ratio is improved from 0.31 and $3\cdot 10^{-4}$
+(0.25 and $10^{-4}$) up to 2.9 and 3.4\% (2.5 and 1.5\%)
 in the boosted (resolved) category.
 %
-The intermediate category, on the other hand, exhibits a rather lower post-MVA value of $S/\sqrt{B}$, around
-1.1.
+The intermediate category, on the other hand, exhibits a
+significantly lower post-MVA value of $S/\sqrt{B}\simeq
+1.1$.
 %
@@
 final state
-at the HL-LHC, also for the case of a high-PU environment, and that
+at the HL-LHC, also for the case of a high-PU environment, but that
 important information will also be obtained from
@@
 %
-This is indicates that while this measurement is still very challenging,
-requiring a careful extraction from the data of the QCD
-background, it is certainty within reach.
+This indicates that while this measurement is still highly challenging,
+requiring a careful extraction of the QCD
+background from the data, it is certainty within reach.
 %
 As in the case without PU, 
-this analysis  indicates that a substantial increase in both
-$S/B$ and $S/\sqrt{B}$ could be achieved by reducing the background component
+our analysis  points out that both
+$S/B$ and $S/\sqrt{B}$ could be increased  by reducing the background component
 that arises from the mis-identification of light and charm
-fakes.
+jets as $b$-jets.
 
@@
 are expected at the HL-LHC as a function of
-$y_{\rm cut}$ and the corresponding ROC curve
+$y_{\rm cut}$, as well as the corresponding ROC curve.
 %
@@
 that the intermediate category is substantially degraded once PU effects
-are accounted for, the reason being  sizable
-a reduction in the number of signal
-events that are now assigned to this category.
+are accounted for due to a sizable
+reduction in the number of signal
+events that are now classified in this category.
 %
@@
 In Fig.~\ref{fig:sb_mva_PU} we show the signal significance,
-$S/\sqrt{B}$, as well as the signal over background ratio,
-$S/B$, including now the effects of PU.
+$S/\sqrt{B}$, and the signal over background ratio,
+$S/B$, accounting now for the effects of PU.
 %
@@
 %
-While unsurprisingly there us a degradation as compared to the case wo PU,
-we still manage to achieve a signal significance of
-around $S/\sqrt{B}$ between 2.5 and 3.0
+While as expected there is some degradation as compared to the case
+without PU,
+it is still possible to
+achieve a signal significance of
+around $S/\sqrt{B}$ between 2.5 and 3.0 (depending on the
+specific choice of $y_{\rm cut}$)
 separately for the boosted and resolved
@@
 %
-On the other hand, the intermediate category becomes marginal.
+On the other hand, the intermediate category now becomes marginal.
 %
-We conclude that the qualitative conclusions drawn in
-Sect.~\ref{sec:mva} are robust in the presence
-of realistic PU effects.
+We conclude that the qualitative conclusions drawn
+in the case without PU also hold when the analysis
+is performed in a high-PU environment.
 %
 Since no specific effort has been performed to
-optimize PU subtraction, for example by tuning the value
+optimize PU subtraction, for instance by tuning the value
 of the patch length $a$ in {\tt SoftKiller}, we believe that
-there is
-still room for improvement in this respect.
+there could be still room for further  improvement.
 
@@
 
-It is important to quantify which of the input variables
+It is useful to quantify which of the input variables
 to the MVA carry the highest discrimination power
 in the case of PU,
-and compare it with the corresponding
-results without PU.
+and compare this with the corresponding
+results without PU, by means of
+Eq.~(\ref{eq:totweight}).
 %
-We use the same estimator as in Sect.~\ref{sec:signalsignificance},
-namely the sum
-of the absolute value of all the weights connected to a given
-input neuron $i$, Eq.~(\ref{eq:totweight}).
-%
-The results for the resolved and boosted categories are shown
+The 
+results for the resolved and boosted categories are shown
 on Fig.~\ref{fig:nnweights_PU}.
 %
-As we can see by comparing to the corresponding
-results without PU in Fig.~\ref{fig:nnweights}, 
+As we can see by comparing with Fig.~\ref{fig:nnweights}, 
 in the boosted category, the discrimination power of the invariant
-mass of Higgs candidates is decreased and that of the various substructure
-variables, in particular $C_2^{(\beta)}$ and
-$D^{(\beta)}$, is conversely
+mass of Higgs candidates is decreased, while
+that of  substructure
+variables such as $C_2^{(\beta)}$ and
+$D^{(\beta)}_2$ is conversely
 increased.
-%
-This reflects the fact that these substructure variables are
-relatively robust against PU contamination.
 %
@@
 values of the ANN weights without PU
-were found for the $p_T$ of the leading
-Higgs and for the Higgs invariant masses.
+were found for the $p_T$ of the 
+Higgs candidates and their invariant masses, as well
+as the for invariant mass of the di-Higgs system
+and the $p_T$ of the small-$R$ jets.
 %
-This is also true in the case with PU, but now the rapidity difference
-between the two Higgs candidates, $\Delta y_{hh}$ increases its
-importance, again reflecting that this variable is relatively
-insensitive to PU effects.
-%
+As we can see in Fig.~\ref{fig:nnweights_PU},
+these results  are reasonably stable in the case with PU.
 
@@
 \be
-\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0 \, ,
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0 \, ,\quad
+\mathcal{L}=3\,{\rm ab}^{-1}\, .
 \ee
-to be compared to the value $\lp S/\sqrt{B}\rp_{\rm tot} \simeq 8.5$
-that was obtained in the case without PU.
 %
-We conclude that, even when realistic PU effects are accounted
-for, at the HL-LHC the measurement of
-Higgs pair production in the $b\bar{b}b\bar{b}$ final state should be 
-well the threshold for evidence, and even meeting the
-requirements for discovery might be within reach provided it is possible
+We thus conclude that the measurement of
+Higgs pair production in the $b\bar{b}b\bar{b}$ final state
+should be 
+well above the threshold for evidence, and even meeting the
+requirements for discovery might be within reach, provided it is possible
 to suppress the background from light and charm jet mis-identifications.
-
-For the Run II luminosity, $\mathcal{L}=300$ fb$^{-1}$, one finds
-instead $\lp S/\sqrt{B}\rp_{\rm tot} \simeq 1.3$, which increases up to
-$\lp S/\sqrt{B}\rp_{\rm tot} \simeq 2.6$ if only the QCD $4b$ background is included.
 %
-This indicates that, interestingly, accessing Higgs pair production at Run II,
-while still extremely challenging, does not seem to be completely impossible.
+Extrapolating the above results
+to total integrated luminosity expected at the end of
+LHC Run II, one finds
+instead
+\be
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 1.3(2.6) \, ,\quad
+\mathcal{L}=300\,{\rm fb}^{-1}\, ,
+\ee
+where the number in brackets corresponds to neglecting all backgrounds
+except for the QCD $4b$ multijets.
 %
-In addition, at Run II the average number of PU collisions is substantially
-reduced as compared to the HL-LHC environment.
-%
-Therefore, it will be interesting to see if improvements in experimental $b$-jet
-reconstruction and fake rejection at Run II are able to fulfill this
-potential.
+This suggest that, remarkably, accessing Higgs pair production at Run II
+might not be completely impossible, specially accounting
+for the fact that the mean number of PU events per
+bunch crossing is much smaller
+that at the HL-LHC.
 

### 2015-12-14 paper/sec-analysis.tex
implementing Daniela's comments

@@
   These subjets are constructed by reclustering the constituents
-  of a large-$R$ jet, again with  anti-$k_T$ algorithm,
+  of a large-$R$ jet, again with the
+  anti-$k_T$ algorithm,
   but this time with a smaller radius parameter, namely
@@
 variable-$R$ jets are more suitable when
-the degree of boost of the final state being reconstructed can span
-a wide range~\cite{Cacciari:2008gd}, such as in heavy resonance
+the degree of boost of the final state being reconstructed can
+differ substantially~\cite{Cacciari:2008gd},
+such as in heavy resonance
 searches~\cite{Aad:2015fna},
-where where the degree of boost of the final state
+where the degree of boost of the final state
 is {\it a priori} unknown.
@@
 which involve the use of large-$R$ jets,
-we will use jet substructure variables~\cite{Salam:2009jx,Aad:2013gja} to
+we use jet substructure variables~\cite{Salam:2009jx,Aad:2013gja} to
 improve the significance of the discrimination between signal and background
@@
 %
-In particular we will consider the following jet
+In particular we  consider the following jet
 substructure variables:
@@
   \ee
-  which provides good discrimination power
+  which provides good discrimination 
   between QCD jets and jets arising from the decay of
@@
     %
-    A large-$R$ jet will considered $b$-tagged if both
+    A large-$R$ jet is considered $b$-tagged if both
     the leading and subleading AK03 subjets, where the ordering
@@
 
-The basic idea of the present analysis is similar to the
-scale-invariant resonance tagging introduced
-in Ref.~\cite{Gouzevitch:2013qca}.
+The present analysis follows a strategy similar to the
+scale-invariant resonance tagging of Ref.~\cite{Gouzevitch:2013qca}.
 %
@@
 the three possible topologies: boosted, intermediate and
-resolved.
-%
-The optimal cuts for each category will be determined
-separately, and then
-a exclusive categorisation is defined starting from the category
-with the highest signal significance.
-%
-An advantage of our approach
-the robustness under variations of
+resolved, with the optimal cuts for each category being determined
+separately.
+%
+This approach is robust
+under variations of
 the underlying production model of Higgs pairs is modified,
@@
 
-These three categories are defined as follows:
+The three categories are defined as follows:
 \begin{itemize}
@@
 %
-This cut is substantially looser as the corresponding
+This cut is substantially looser than the corresponding
 cut used in the typical ATLAS and CMS $h\to b\bar{b}$
-analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
-for this choice is that the MVA will take care of the optimisation of this,
-as well as of other cuts that are not explicitly performed.
+analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}.
+%
+The motivation
+for this choice 
+is that further improvements of the
+signal significance will be obtained using an MVA.
 %
@@
 %
+The optimization of the analysis
+of the three categories is performed inclusively, and
+then events are exclusively assigned to specific category
+starting with the one with the highest signal significance.
+
 The separate optimisation of the three categories needs to be performed in
@@
 %
-We find that the category with higher significance turns out to be
+We find that the category with higher significance is
 the boosted one,
@@
 this category, else we check if it suits the intermediate
-requirements, and failing also this, the event is attempted to
-be classified in the
-resolved category.
+requirements.
+%
+It the event also fails the intermediate category
+requirements, we
+then check if it pass the resolved selection criteria.
 %
@@
 %
-First to all, we present results without PU, and in the next
-subsection we discuss the impact of PU
+We first present results without PU, and then
+discuss
+the impact of PU
 on the description of the various kinematic
@@
 
-%
-To begin with,
-in Fig.~\ref{fig:cutplots1} we show
+In Fig.~\ref{fig:cutplots1} we show
 the $p_T$ distributions
@@
   %
-  We see that the background distribution
-  falls off rather steeply than the signal at large $p_T$
-  for the two Higgs candidates.
+  We observe that the background distribution
+falls off more rapidly as a function of $p_T$ than the di-Higgs signal.
   %
@@
 On the other hand, considering the subleading AKT03 subjet,
-this cut in its  $p_T$
+this cut in $p_T$
 cannot be too harsh, to maintain a high signal selection
@@
 %
-These considerations lead to the requirement that the $p_T$ cut
-for the small-$R$ jets cannot be too strong.
+These considerations lead to the requirement that the $p_T$
+selection
+for the small-$R$ jets cannot be too large.
 %
@@
 The feasibility to being able to trigger on four small-$R$ jets with a relatively
-soft $p_T$ distribution is one of the experimental challenges of
+soft $p_T$ distribution is one of the experimental challenges for
 exploiting the resolved category in this final state,
@@
 rapidity distribution of the the small-$R$
-jets in the resolved category: as well know, the production
-is mostly central (more in the case
+jets in the resolved category.
+%
+As expected, the production
+is mostly central, more in the case
 of signal events, since backgrounds are dominated by
-QCD $t$-channel exchange) and thus the standard rapidity cuts
-are relatively harmless.
+QCD $t$-channel exchange, and thus the
+selection criteria on the jet rapidity  are highly efficient.
 
@@
 of the leading reconstructed Higgs candidates, before the Higgs mass window
-cut 
+selection
   is applied, for the resolved and boosted categories.
@@
 
-Another important kinematic distribution of this process is the invariant mass
+Another important kinematic distribution for
+this process is the invariant mass
 of the di-Higgs system.
@@
 enhanced, for instance due to
-of specific $d=6$ EFT operators~\cite{Azatov:2015oxa}.
+specific $d=6$ EFT operators~\cite{Azatov:2015oxa}.
 %
@@
 For the boosted category the overall trend of the $m_{hh}$ distribution
-is different because of the jet selection cuts, with the
-distribution now peaking at higher values of the invariant mass.
+is different because of the jet selection criteria, and the
+distribution now peaks at higher values of the invariant mass.
 %
 In this case, signal and background distributions
-look reasonably similar.
+look similar.
 %
@@
 should provide additional discrimination power, and therefore
-this distribution will be another of the inputs for the MVA.
+this distribution is one of the inputs for the MVA.
 %
 In our LO simulation the $p_T^{hh}$ distribution is generated
-by the parton shower, and and improved theoretical
+by the parton shower, and improved theoretical
 description would require
@@
 all for the leading
-Higgs candidates, as we as also $\tau_{12}$ for the subleading
+Higgs candidates, and also $\tau_{12}$ for the subleading
 Higgs candidates.
@@
 %
-Crucially, signal and background distributions peak
+Signal and background distributions peak
 in rather
@@
 reasonably similar
-for both the leading and in the subleading jets, therefore the information
-contained in
-this (and other substructure variables)
-from each of the two Higgs candidates  will be to some
-extent redundant.
-
+for both the leading and the subleading jets.
+%
 Therefore, while we do not explicitly have cuts in the substructure
@@
 background events is the motivation to include them
-as input to the MVA, as we will explain in Sect.~\ref{sec:mva}.
+as input to the MVA, as discussed in Sect.~\ref{sec:mva}.
 

### 2015-12-14 paper/sec-intro.tex
implementing Daniela's comments

@@
 Feasibility studies in the case of a SM-like Higgs boson
-in gluon fusion at the LHC have been performed for different final states, including
+in the gluon-fusion channel
+at the LHC have been performed for different final states, including
 $b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
@@
 Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
-in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa,Wen-Juan:2015gqg}, or Supersymmetry and
+in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa,Wen-Juan:2015gqg}, and Supersymmetry and
 Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
@@
 Searches for the production of Higgs pairs
-have already been performed at Run I with 8 TeV
+have already been performed with 8 TeV Run I data
 by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
@@
 parton shower, the
-contribution of the $2b2j$ process is actually comparable to
+contribution of the $2b2j$ process is comparable to
 the irreducible $4b$ component.

### 2015-12-14 paper/sec-mcsamples.tex
implementing Daniela's comments

@@
 and the renormalization and factorization
-scales are taken to be $\mu_F=\mu_R=H_T/2$.
+scales are taken to be $\mu_F=\mu_R=H_T/2$,
+with
+\be
+H_T\equiv \sum_i \sqrt{p_{T,i}^2+m_i^2} \, ,
+\ee
+the scalar sum of the
+transverse masses of all final state particles.
 %
@@
     The non-trivial interplay between the diagram with a heavy quark box
-    and that of the triangle, that can lead to either
+    and that of the triangle loop,
+    that can lead to either
     constructive or destructive interference,
@@
 using the {\tt BLACKHAT}~\cite{Bern:2011ep}
-calculation, that indicate
+calculation, that indicates
 a NLO/LO $K$-factor of 0.6.
@@
 hadronic calorimeters by applying a Gaussian smearing of the transverse
-momentum $p_T$ of all
+momentum $p_T$ for all
 final-state particles, before jet clustering,

### 2015-12-14 paper/paperscripts/plotHist_EEC_C2_h0_C1_boost.py

@@ -121,10 +121,6 @@ for idat in xrange(0,len(datafiles)):
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
   icol=icol+1
 
-# Gridlines
-ax.xaxis.grid(True)
-ax.yaxis.grid(True)
-
 plt.rcParams.update({'font.size': 14})
 fig.text(0.28,0.93,"Boosted category, no PU", fontsize=20)
 

### 2015-12-14 paper/paperscripts/plotHist_m_H0_bst_noPU.py

@@ -119,12 +119,8 @@ for idat in xrange(0,len(datafiles)):
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
   icol=icol+1
 
-# Gridlines
-ax.xaxis.grid(True)
-ax.yaxis.grid(True)
-
 plt.rcParams.update({'font.size': 16})
-fig.text(0.28,0.93,"Boosted category, $n_{PU}=0$", fontsize=20)
+fig.text(0.28,0.93,r"Boosted category, $\langle n_{PU}\rangle =0$", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-14 paper/paperscripts/plotHist_ptHH_res_noPU.py

@@ -119,12 +119,8 @@ for idat in xrange(0,len(datafiles)):
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
   icol=icol+1
 
-# Gridlines
-ax.xaxis.grid(True)
-ax.yaxis.grid(True)
-
 plt.rcParams.update({'font.size': 16})
-fig.text(0.25,0.93,"Resolved category, $n_{PU}=0$", fontsize=20)
+fig.text(0.25,0.93,r"Resolved category, $\langle n_{PU}\rangle =0$", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-14 paper/paperscripts/plotHist_split12_h1_C1_boost.py

@@ -121,9 +121,6 @@ for idat in xrange(0,len(datafiles)):
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
   icol=icol+1
 
-# Gridlines
-ax.xaxis.grid(True)
-ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 14})
 fig.text(0.28,0.93,"Boosted category, no PU", fontsize=20)

### 2015-12-14 paper/sec-analysis.tex
more from Daniela's comments

@@
 
-Now we turn to discuss how the description of kinematic
+Here we turn to discuss how the description of kinematic
 distributions for $hh\to 4b$ signal
@@
 %
-In this work, PU  will be subtracted by means
-of the {\tt SoftKiller} (SK)
+In this work, PU  is subtracted
+with the {\tt SoftKiller} (SK)
 method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
@@
 \ee
-where the median is computed over all the patches $i$ with area
+where the median is computed over all the regions $i$ with area
 $A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
@@
 it follows that the value of $p_T^{(\rm cut)}$
-will be dynamically raised until half of the patches have
+will be dynamically raised until half of the regions have
 $p_{Ti}=0$.
 %
-The size and number of these patches is a free parameter of the algorithm -
-here we will use square patches with length $a=0.4$.
+The size and number of these regions is a free parameter of the algorithm -
+here we will use square regions with length $a=0.4$.
 %
@@
 To validate PU subtraction,
-we now compare representative kinematic distributions
-in the case without PU and in the case
-with PU subtracted with {\tt SoftKiller}.
-%
-We compare first
-in Fig.~\ref{fig:PUvalidation} the
+we compare representative kinematic distributions
+without PU, with PU, and with PU after SK subtraction.
+%
+In Fig.~\ref{fig:PUvalidation} we show the
 invariant mass distributions of Higgs candidates for signal
@@
 %
-We show three curves: without PU,
-with PU $\la n_{\rm PU}\ra=80$ but without any subtraction, and the
-same but now with the SK subtraction.
-%
 If PU is not subtracted there is a large shift in the Higgs mass
@@
 Once SK subtraction is performed, we recover a distribution much closer
-to the original ones, with only a small shift of $\simeq 5$ GeV
+to the ones without PU, with only a small shift of $\simeq 5$ GeV
 and a broadening of the mass
@@
 
-Next, we compare additional
- distributions with
-and without PU, with $\la n_{\rm PU}\ra=80$ in the
-former
-case (and SK subtraction).
-%
 In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
@@
 %
-These distributions are plotted after the $b$-tagging, that is,
+These distributions are plotted after
+$b$-tagging, that is,
 before they are used as input to the MVA.
 %
-As we can see, the residual effects of PU
+The residual effects of PU
 after the {\tt SoftKiller} subtraction are smaller
 in the boosted selection as compared to the resolved case,
-with the position of the Higgs mass peaks essentially
+with the position of the Higgs mass peak essentially
 unchanged, and only a moderate broadening of the
@@
 %
-Similar observation can be derived for the case of
-the di-Higgs invariant mass $m_{hh}$ distribution, similar 
-apply.
+A similar behaviour is observed in the di-Higgs invariant mass distribution.
 %
@@
 as validated for the purposes of this study, although
-there could still be room for optimisation.
+further optimisation should be possible.
 
@@
 of energy correlation functions, $D_2^{(\beta)}$,
-Eq.~(\ref{eq:d2}), in both cases
-corresponding to the leading Higgs candidate.
+Eq.~(\ref{eq:d2}), for the leading Higgs candidate.
 %
@@
 was indeed constructed~\cite{Larkoski:2013eya}
-to be resilient
-with respect to PU contamination.
+to be robust against PU contamination.
 %
@@
   \begin{center}
-  \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/pt_h0_bst_comp_back.pdf}
@@
    \includegraphics[width=0.49\textwidth]{plots/split12_h0_bst_comp_back.pdf}
+   \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
    \caption{\small
@@
      the boosted category, for signal and background events
-     with and without PU: the invariant mass,  $p_T$,
+    in the case of PU subtracted with SK:
+     the transverse momentum  $p_T$ and
      and the substructure variables $\tau_{21}$ and $\sqrt{d_{12}}$
-    for the leading Higgs candidate.
+     for the leading Higgs candidate, and the invariant
+     mass of the di-Higgs system $m_{hh}$.
      %

### 2015-12-14 paper/paperscripts/plotHist_m_h0_res_comp_back.py

@@ -15,24 +15,20 @@ outfile = "m_h0_res_comp_back"
 linestyles = [ 'solid', 'dashed','solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H0_res_C1e.dat")
-datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_H0_res_C1e.dat")
-datafiles.append("../plotdata/results_noPU/background/histo_m_H0_res_C1e.dat")
-datafiles.append("../plotdata/results_SK_PU80/background/histo_m_H0_res_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_HH_res_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/background/histo_m_HH_res_C1e.dat")
 
 # Plot labels
-plotnames.append("Signal, no PU")
-plotnames.append("Signal, $n_{PU}=80$ + SK")
-plotnames.append("Background, no PU")
-plotnames.append("Background, $n_{PU}=80$ + SK")
+plotnames.append("Signal")
+plotnames.append("Background")
 
 # Axis labels
-xLabel = "Leading Higgs Candidate Invariant Mass (GeV)"
+xLabel = "d-Higgs Invariant Mass $m_hh$ (GeV)"
 yLabel = "a. u."
 
 # Log axes
 xLog = False
-yLog = True
+yLog = False
 
 # Normalise histograms
 normalise = True
@@ -43,7 +39,7 @@ if len(datafiles)!=len(plotnames):
   print "Error: datafile and plotname arrays are different lengths!"
   exit()
 
-colours = ['r', 'r', 'b', 'b']
+colours = ['r', 'b', 'b', 'b']
 icol = 0
 
 # Setup figure
@@ -57,8 +53,8 @@ ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
 
-ax.set_xlim([90,175])
-ax.set_ylim([1e-3,0.1])
+ax.set_xlim([90,600])
+ax.set_ylim([0,0.007])
 
 
 
@@ -127,12 +123,9 @@ for idat in xrange(0,len(datafiles)):
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
   icol=icol+1
 
[…]

### 2015-12-14 paper/paperscripts/plotHist_tau12_h1_bst_comp_back.py

@@ -15,16 +15,13 @@ outfile = "tau21_h1_bst_comp_back"
 linestyles = [ 'solid', 'dashed','solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_tau21_fj2_boost_C1e.dat")
 datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_tau21_fj2_boost_C1e.dat")
-datafiles.append("../plotdata/results_noPU/background/histo_tau21_fj2_boost_C1e.dat")
 datafiles.append("../plotdata/results_SK_PU80/background/histo_tau21_fj2_boost_C1e.dat")
 
 # Plot labels
-plotnames.append("Signal, no PU")
-plotnames.append("Signal, $n_{PU}=80$ + SK")
-plotnames.append("Background, no PU")
-plotnames.append("Background, $n_{PU}=80$ + SK")
+plotnames.append("Signal")
+plotnames.append("Background")
+
 
 # Axis labels
 xLabel = r"Subjettiness Ratio $\tau_{12}$ for leading Higgs candidate"
@@ -43,7 +40,7 @@ if len(datafiles)!=len(plotnames):
   print "Error: datafile and plotname arrays are different lengths!"
   exit()
 
-colours = ['r', 'r', 'b', 'b']
+colours = ['r', 'b', 'b', 'b']
 icol = 0
 
 # Setup figure
@@ -57,7 +54,7 @@ ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
 ax.set_xlim([0,1])
-ax.set_ylim([0.005,10])
+ax.set_ylim([0.05,20])
 
 for idat in xrange(0,len(datafiles)):
 
@@ -123,12 +120,9 @@ for idat in xrange(0,len(datafiles)):
   ax.plot(xhi,yval/norm,drawstyle = "steps-pre", color = colours[icol], label=plotnames[idat],linestyle=linestyles[idat],linewidth=2.4)
   icol=icol+1
 
-# Gridlines
-ax.xaxis.grid(True)
-ax.yaxis.grid(True)
 
 plt.rcParams.update({'font.size': 14})
-fig.text(0.33,0.93,"Boosted category", fontsize=20)
+fig.text(0.23,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK", fontsize=19)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-14 paper/sec-mva.tex
completed Daniela's comments

@@
 We then introduce the input variables that are
-used the MVA, including the jet substructure
-variables, and then present the results of $S/\sqrt{B}$ including
-the MVA effects.
+used in the MVA, including the jet substructure
+variables, and then present the signal significance obtained
+by applying the MVA.
 %
-Since we find that jet substructure variables are a crucial input
-to the MVA, we show representative kinematic distributions
-for these variables.
-%
-Finally, we assess the robustness of the MVA strategy in
+Then we assess the robustness of the MVA strategy in
 high-PU environments.
@@
 %
-As can be seen,
+We observe that
 in the boosted category, for a value $y_{\rm cut}\simeq 0.8$
@@
 with only a
-moderate reduction of signal efficiency in exchange.
+moderate reduction of signal efficiency.
 
-A useful property of MVAs such as the one used in this work
+A useful property of MVAs, as the one used in our
+analysis,
 is that they provide direct  physical insight about which of the
@@
 We also observe a substantial enhancement in $S/B$, arising
-from the background suppression indeed by the MVA, reaching
+from the background suppression achieved by the MVA, reaching
 values of 1\%, 6\% and 3.5\% in the resolved,
@@
 
-From Table~\ref{table:cutflowMVA} we see that at the end of the
-MVA the signal significance in the boosted category increases
+From Table~\ref{table:cutflowMVA} we see that
+after we apply the MVA
+the signal significance in the boosted category increases
 from 1.2 to 5.4, with $S/B$ increasing from $0.14\%$ to $3.4\%$,
@@
 for the optimal MVA cut, the signal over background ratio
-is not unfeasibly small: we obtain that $S/B$ is 3.4\% (1.5\%)
+is 3.4\% (1.5\%)
 in the boosted (resolved) categories.
@@
 %
-While as expected there is some degradation as compared to the case
+While
+there is some degradation as compared to the case
 without PU,
@@
 %
-On the other hand, the intermediate category now becomes marginal.
+On the other hand, the intermediate category is now marginal.
 %
@@
 As we can see in Fig.~\ref{fig:nnweights_PU},
-these results  are reasonably stable in the case with PU.
+this is the case also with PU.
 
@@
 should be 
-well above the threshold for evidence, and even meeting the
-requirements for discovery might be within reach, provided it is possible
-to suppress the background from light and charm jet mis-identifications.
+well above the threshold for evidence.
+%
+Even
+discovery might be within reach if the
+misidentification of light and charm jets as b-jets can be  reduced.
 %

### 2015-12-14 paper/sec-results.tex
more work on the text
completed Daniela's comments

@@
 %
-We present now the results in the no PU scenario, the impact
-of PU will be discussed in the next section.
+First we present the results without considering PU,
+followed by the corresponding analysis of the PU effect.
 
@@
 we summarize the definition of the different
-levels of the cut-flow of the present analysis,
+steps of the cut-flow of the present analysis,
 separated into the boosted, intermediate,
@@
     %
-    In more details, these different analysis levels are the following:
+    In more details, these different analysis steps are the following:
 
@@
   \end{tabular}
-  \caption{\small Definition of the cut-flow levels for the boosted, intermediate
+  \caption{\small Definition of the cut-flow steps for the boosted, intermediate
     and resolved selections.
@@
     the values for cross-sections for signal and background processes
-    for different levels of the cut flow.
+    for different steps of the cut flow.
     %
@@
   \scriptsize
-  \input{tables/table_noPU_1.tex}
+  \input{table_noPU_1.tex}
   $\,$ \\
   \vspace{0.5cm}
-  \input{tables/table_noPU_2.tex}
+  \input{table_noPU_2.tex}
   $\,$ \\
   \vspace{0.5cm}
-    \input{tables/table_noPU_3.tex}
+    \input{table_noPU_3.tex}
     \caption{\small The cross-sections, in femtobarns,
@@
       %
-      The different levels of the cut-flow are summarized
+      The different steps of the cut-flow are summarized
       in Table~\ref{tab:cutflowdetails}.
@@
  $2b2j$ component is essential to robustly assess the feasibility
- of measuring Higgs pairs in this final state, and this is markedly
- important
+ of measuring Higgs pairs in this final state,
+ specially
  in the boosted category.
@@
 increased substantially in the $2b2j$ component as compared
-to the parton level content, while at the same
+to the parton level, while at the same
 time the number of events in the $4b$ sample
@@
 %
-Similar expressions can be derived to the boosted and intermediate categories.
+Similar expressions can be derived for
+the boosted and intermediate categories.
 %
@@
   This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
-  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
+  in the resolved category before $b$-tagging, shown
+  in Table~\ref{tab:cutflow_noPU_1}.
     %
@@
     %
-    A similar calculation from the numbers of Table~\ref{tab:btaggingcheck} shows
+    A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
     that, on the other hand, the $4j$ component of the background can safely
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%

### 2015-12-14 paper/paperscripts/plotMVAdat_PU.py

@@ -19,6 +19,9 @@ titlenames=[ r"Resolved Category,  $\langle n_{PU}\rangle =80$+SK",
              r"Intermediate Category,  $\langle n_{PU}\rangle =80$+SK",\
              r"Boosted Category,  $\langle n_{PU}\rangle=80$+SK"]
 
+datanamessignal=[ "Signal Res","Signal Int","Signal Boost"]
+datanamesback=[ "Background Res","Background Int","Background Boost"]
+
 
 # HL-LHC luminosity
 hl_lhc_lumi=3000
@@ -71,8 +74,6 @@ rocax.set_ylabel("Background rejection rate",fontsize=17)
 rocax.set_xlabel("Signal efficiency",fontsize=17)
 
 # Gridlines
-rocax.xaxis.grid(True)
-rocax.yaxis.grid(True)
 
 # Setup s/b plot
 sb, sbax = plt.subplots()
@@ -98,21 +99,8 @@ nev3, nevax3 = plt.subplots()
 nevax3.set_ylabel("$N_{ev}$ at HL-LHC after MVA cut")
 nevax3.set_xlabel("ANN output cut")
 
-# Gridlines
-sbax.xaxis.grid(True)
-sbax.yaxis.grid(True)
 sbax.set_yscale('log')
-
-
-ssbax.xaxis.grid(True)
-ssbax.yaxis.grid(True)
-nevax.xaxis.grid(True)
-nevax.yaxis.grid(True)
-nevax3.xaxis.grid(True)
-nevax3.yaxis.grid(True)
-
 nevax3.set_yscale('log')
-
 nevax3.set_ylim([1,1e7])
 
 ######################## Reading data ##############################
@@ -121,6 +109,8 @@ for idat in xrange(0,len(datafiles)):
 	infilenm = os.path.expanduser(datafiles[idat])
 	basename = datanames[idat]
         titlename = titlenames[idat]
+        basenamesignal = datanamessignal[idat]
+        basenameback = datanamesback[idat]
 
 	# Verify paths
 	if os.path.exists(infilenm) == False:
@@ -149,7 +139,7 @@ for idat in xrange(0,len(datafiles)):
 			total_sigweight = total_sigweight + float(line.split()[2]) # Weight
 
 	#### ROC Curve and S/B plot
-	thresholds = numpy.linspace(0, 1, 100)
[…]

### 2015-12-14 paper/sec-mva.tex
updated mva section

@@
 
-We can finally combine the three categories, resolved,
-intermediate and boosted, and determine the overall signal
+Combining the three categories, resolved,
+intermediate and boosted, we determine the overall signal
 significance, finding
 \be
-\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0 \, ,\quad
-\mathcal{L}=3\,{\rm ab}^{-1}\, .
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
+\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, .
 \ee
@@
 We thus conclude that the measurement of
-Higgs pair production in the $b\bar{b}b\bar{b}$ final state
+Higgs pair production in the $b\bar{b}b\bar{b}$ final state at the HL-LHC
 should be 
@@
 %
-Even
-discovery might be within reach if the
-misidentification of light and charm jets as b-jets can be  reduced.
+On the other hand, such measurement seems to be out of reach
+for the total integrated luminosity expected by the end of Run II.
+
+In Table~\ref{table:cutflowMVA_fakes} we compare,
+after the MVA is applied,
+the total
+number of background events, $N_{\rm ev}^{\rm tot}$,
+    expected at the HL-LHC, with
+     $N_{\rm ev}^{\rm 4b}$, the corresponding number
+    from the QCD $4b$ component, in the cases with and without
+    PU.
     %
-Extrapolating the above results
-to total integrated luminosity expected at the end of
-LHC Run II, one finds
-instead
+    The MVA has been trained to the total background sample,
+    though differences
+    in the kinematic distributions of the $4b$ and $2b2j$ processes are small,
+    see Fig.~\ref{fig:histoBack}.
+    %
+    The major improvement of eliminating the contamination
+    of light and charm jet mis-identification is in the boosted category.
+
+    In the case of PU+SK, combining the three categories but assuming that
+    the only relevant background is the irreducible QCD $4b$ component,
+    we obtain
     \be
-\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 1.3(2.6) \, ,\quad
-\mathcal{L}=300\,{\rm fb}^{-1}\, ,
+\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 7.4(2.4) \, ,\quad
+\mathcal{L}=3000 (300)\,{\rm fb}^{-1}\, ,
 \ee
-where the number in brackets corresponds to neglecting all backgrounds
-except for the QCD $4b$ multijets.
+Therefore, a discovery of Higgs pair production at the
+HL-LHC might be possible if the
+mis-identification of light and charm jets as
+$b$-jets can be  reduced.
 %
-This suggest that, remarkably, accessing Higgs pair production at Run II
-might not be completely impossible, specially accounting
-for the fact that the mean number of PU events per
-bunch crossing is much smaller
-that at the HL-LHC.
+With these assumptions, and provided
+the signal efficiency can be further enhanced,
+this measurement might even be feasible
+by the end of Run II.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h]
+  \centering
+  \small
+  \begin{tabular}{|c|c|c|c||c|c||c|c|}
+        \hline
+        Category  &    &  $N_{\rm ev}^{\rm tot}$  &  $N_{\rm ev}^{\rm 4b}$   &
+        $S/\sqrt{B_{\rm tot}}$ & $S/\sqrt{B_{\rm 4b}}$  
+        &  $S/B_{\rm tot}$ & $S/B_{\rm 4b}$\\ 
+    \hline
+    \hline
+    \multirow{2}{*}{Boosted} &  no PU  & $2.2\cdot 10^4$  & 4800    & 
+      5.4 &  11.6 & 0.034 & 0.16 \\
+    & PU+SK & 7300  &  1600  &  2.9  & 6.2 &  0.034 & 0.16 \\
+    \hline
+    \hline
+    \multirow{2}{*}{Intermediate} &  no PU   & $5.5\cdot 10^3$  & 2000    &
+    4.8  &  7.9 &  0.06  &  0.16 \\
+    & PU+SK  & 2600   &  1000  & 1.1  & 1.8 & 0.02 & 0.05 \\
+    \hline
+    \hline
+    \multirow{2}{*}{Resolved} &   no PU  & $8\cdot 10^4$   &
+    $3.7\cdot 10^4$
+    & 4.5  & 6.7  & 0.01 & 0.02 \\
+    & PU+SK  &  $3\cdot 10^4$   &   $1.3\cdot 10^4$ & 2.5    & 3.7  & 0.015 & 0.03 \\
+    \hline
+      \end{tabular}
+  \caption{\small Post-MVA number of total background events, $N_{\rm ev}^{\rm tot}$,
+    expected at the HL-LHC, compared
+    with $N_{\rm ev}^{\rm 4b}$,
+    the number of QCD $4b$ background events.
+    %
+    We also indicate the corresponding signal significance and signal over background
+    ratios.
+        \label{table:cutflowMVA_fakes}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-12-14 paper/sec-analysis.tex
All comments implemented

@@
 \caption{\small  Comparison of the $p_T$ distributions of the
-  leading (left plot) and
-  subleading (right plot) large-$R$ jets in the boosted category,
-  in in signal and background events.
+  leading (left) and
+  subleading (right) large-$R$ jets in the boosted category,
+  in signal and background events.
   %
   Distributions have been normalized to unity.
+  %
+  The total background is the sum of all components
+  listed in Table~\ref{tab:samples}.
 }
@@
     mass distribution of the leading Higgs candidates in the resolved
-    (left plot) and boosted (right plot) selections.
+    (left) and boosted (right) selections.
 }
@@
 mass distribution of the di-Higgs system $m_{hh}$, in
-the resolved (left plot) and boosted (right plot) categories.
+the resolved (left) and boosted (right) categories.
 }
@@
   \includegraphics[width=0.48\textwidth]{plots/pt_HH_C2_bst_noPU.pdf}
-  \caption{\small Same as Fig.~\ref{fig:mhh} for the transverse momentum
+  \caption{\small Same as Fig.~\ref{fig:cutplots1} for the transverse momentum
     distribution of the di-Higgs system $p_T^{hh}$.
@@
     and the  subjettiness ratio $\tau_{21}$ for the leading
-    Higgs, as well as $\tau_{21}$ also for the subleading Higgs.
+    Higgs.
+    %
+    In the case of 
+    $\tau_{21}$  the distributions for the subleading Higgs are also given.
  }
@@
   \caption{\small
-    Comparison of the invariant mass distributions of the leading (left plot)
-    and subleading (right plot) Higgs candidates
+    Comparison of the invariant mass distributions of the leading (left)
+    and subleading (right) Higgs candidates
     in the boosted category,
@@
     of the di-Higgs system (lower plots) in the resolved
-    (left plots) and boosted (right plots) categories,
+    (left) and boosted (right) categories,
     without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
@@
         \hline
-        &   &   $\delta m_h$  &  $\sigma_{m_h}$  \\
-        \hline
-        \hline
-        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & 8 GeV   \\
-          & subleading Higgs   & -5.8 GeV  &  9 GeV \\
-        \hline
-          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & 9 GeV   \\
-          & subleading Higgs   & +31 GeV  &  12 GeV \\
-          \hline
-            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & 11 GeV   \\
-          & subleading Higgs   & +2.1 GeV  &  11 GeV \\
+        \multicolumn{4}{|c|}{Resolved category}\\
+        \hline
+        \hline
+        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
+              \hline
+        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
+          & subleading Higgs   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
+        \hline
+          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
+          & subleading Higgs   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
+          \hline
+            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
+          & subleading Higgs   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
+            \hline
+            \multicolumn{4}{c}{}\\
+             \hline
+        \multicolumn{4}{|c|}{Boosted category}\\
+        \hline
+        \hline
+        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
+              \hline
+        \multirow{2}{*}{no PU}  & leading Higgs  &  +2 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
+          & subleading Higgs   & +1 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
+        \hline
+              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  --   & --   \\
+          & subleading Higgs   & --  &  -- \\
         \hline
@@
         Resolution of the invariant mass distribution of
-        reconstructed Higgs candidates in the resolved
-        category.
+        reconstructed Higgs candidates in the resolved (upper table)
+        and boosted (categories) category.
         %
@@
         %
-        We indicate the shift of the invariant mass peak as compared
-        to the nominal Higgs mass, $\delta m_h$, as well as the width
+        We indicate the shift of the invariant mass peak $\la m_h^{\rm reco}\ra$ as compared
+        to the nominal Higgs mass $m_h=125$ GeV, as well as the width
         of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,

### 2015-12-14 paper/sec-mcsamples.tex
All comments implemented

@@
 \begin{center}
-  \includegraphics[width=0.90\textwidth]{plots/hhFeyn.pdf}
+  \includegraphics[width=0.96\textwidth]{plots/hhFeyn.pdf}
   \caption{\small Representative Feynman diagrams
@@
     %
-    Only the quark triangle diagram (left) is sensitive to the Higgs trilinear coupling
+    Only the fermion triangle loop diagram (right) is
+    directly sensitive to the Higgs trilinear coupling
     $\lambda$.
     %
-    In the SM, the fermion loops are dominated by the top quark contribution.
+    In the SM, the fermion loops are dominated by the
+    contribution from the top quark.
 }
@@
 \hline
-$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.7\cdot10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
+$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 1M & $1.7\cdot10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
 \hline
@@
 \caption{\small Details of the signal and background Monte
-  Carlo samples using in this work.
+  Carlo samples used in this work.
   %
@@
   %
-We also provide in each case the corresponding inclusive $K$-factor
+We also provide the corresponding inclusive $K$-factor
   that is applied to reproduce the known

### 2015-12-14 paper/sec-mva.tex
All comments implemented

@@
   at the end of the GA training,
-  with red indicating larger values and black smaller values.
+  with red indicating larger values and black indicating smaller values.
 }
@@
 %
-In Table~\ref{table:cutflowMVA} where we indicate
+In Table~\ref{table:cutflowMVA} where we quote
 the value of the optimal ANN output
@@
     %
-    We indicate the number of signal and
+    we quote the number of signal and
     background events
@@
 case of events with PU, for
- $\la n_{\rm PU}\ra=80$ 
-  and SK subtraction.
+$\la n_{\rm PU}\ra=80$ using
+{\tt SoftKiller} for PU subtraction.
 }
@@
 $\la n_{\rm PU}\ra=80$
-  and SK subtraction.
+using
+{\tt SoftKiller} for PU subtraction.
 }
@@
     The major improvement of eliminating the contamination
-    of light and charm jet mis-identification is in the boosted category.
-
+    of light and charm jet mis-identification is for the boosted and resolved categories.
+%
     In the case of PU+SK, combining the three categories but assuming that
@@
     \be
-\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 7.4(2.4) \, ,\quad
-\mathcal{L}=3000 (300)\,{\rm fb}^{-1}\, ,
+\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 5.3~(1.8) \, ,\quad
+\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
 \ee
@@
 by the end of Run II.
+%
 
@@
     \hline
-    \multirow{2}{*}{Boosted} &  no PU  & $2.2\cdot 10^4$  & 4800    & 
-      5.4 &  11.6 & 0.034 & 0.16 \\
-    & PU+SK & 7300  &  1600  &  2.9  & 6.2 &  0.034 & 0.16 \\
+    \multirow{2}{*}{Boosted} &  no PU  & $2.2\cdot 10^4$  & $1.5\cdot 10^4$     & 
+      5.4 &  6.5 & 0.034 & 0.05 \\
+    & PU+SK & 7300  &  500  &  2.9  & 3.6 &  0.034 & 0.04 \\
     \hline
     \hline
-    \multirow{2}{*}{Intermediate} &  no PU   & $5.5\cdot 10^3$  & 2000    &
-    4.8  &  7.9 &  0.06  &  0.16 \\
-    & PU+SK  & 2600   &  1000  & 1.1  & 1.8 & 0.02 & 0.05 \\
+    \multirow{2}{*}{Intermediate} &  no PU   & 4500  & 2000    &
+    4.8  &  5.3 &  0.06  &  0.08 \\
+    & PU+SK  & 2600   &  1500  & 1.1  & 1.2 & 0.02 & 0.03 \\
     \hline
@@
     \multirow{2}{*}{Resolved} &   no PU  & $8\cdot 10^4$   &
-    $3.7\cdot 10^4$
-    & 4.5  & 6.7  & 0.01 & 0.02 \\
+    $4.5\cdot 10^4$
+    & 4.5  & 6.6  & 0.01 & 0.03 \\
     & PU+SK  &  $3\cdot 10^4$   &   $1.3\cdot 10^4$ & 2.5    & 3.7  & 0.015 & 0.03 \\

### 2015-12-14 paper/sec-conclusions.tex
completed Daniela's comments
more work in polishing text

@@
 %
-Our strategy was based on the combination of a traditional
+Our strategy is based on the combination of traditional
 cut-based analysis with state-of-the-art multivariate techniques.
@@
 %
-We illustrate how the $2b2j$ component leads to
+We have illustrated how the $2b2j$ component leads to
 a contribution comparable to that of the $4b$ process,
@@
 %
-Since any realistic study of the feasibility of Higgs pair
-production at the HL-LHC should take into account the
-high-PU environment in which such measurement will be performed,
-in this work we have demonstrated the robustness of our analysis strategy
+We have also demonstrated the robustness of our analysis strategy
 under high-PU conditions.
@@
 %
-This indicates that already from the $b\bar{b}b\bar{b}$
-final state alone
+This indicates that, already from the $b\bar{b}b\bar{b}$
+final state alone,
 it should be possible to claim evidence for Higgs pair production at
@@
 %
-One handle could be to reduce the contribution from light and charm
+One handle would be to reduce the contribution from light and charm
 jet mis-identification, ensuring that the
@@
 %
-Following these and related improvements in the experimental
-analysis, it might be feasible to achieve
-an observation of Higgs pair production even with only
+Such experimental improvements might
+even make possible
+an observation of Higgs pair production already at the
+end of Run II with
 $\mathcal{L}=300$ fb$^{-1}$.
@@
 %
-J.~F. and C.~I. are supported by the STFC.
+D.~B., J.~F. and C.~I. are supported by the STFC.

### 2015-12-14 paper/sec-mva.tex
more work in polishing text

@@
 
-In this section we study how the MVA results are modified when
-signal and background events are embedded in a high-PU environment.
-%
-The simulation of PU and the corresponding subtraction with
-{\tt SoftKiller} have been performed as described
-in Sect.~\ref{sec:pileup}.
+In this section we study how the MVA results are modified
+when the analysis is performed in a high-PU environment.
 %
 The cut-based analysis and the subsequent
-MVA optimization have been performed using exactly the same
+MVA optimization have been performed using the same
 settings as in the case without PU.
@@
   for the case with $\la n_{\rm PU}\ra=80$ with SK
-  subtraction.
+  subtraction,
+  as well as the post-MVA results for the
+  corresponding optimal values of $y_{\rm cut}$.
   %
-It is clear that the pre-MVA 
-signal significance has been degraded
+  In addition, we also quote in
+  both cases the number of signal and
+    background events expected
+    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
+    and the values of $S/\sqrt{B}$ and $S/B$
+
+We observe how the pre-MVA 
+signal significance is degraded
 as compared to the case without PU.
@@
 intermediate and boosted categories, respectively, to be compared
-with the corresponding values without PU, namely 1.0, 0.9 and 1.0,
-see Table~\ref{table:cutflowMVA}. 
+with the corresponding values without PU, namely 1.0, 0.9 and 1.0.
 %
-
-Subsequently to 
- the cut-based analysis, the signal and background
- MC events in the case of PU satisfying all selection cuts
-  are used to re-train the MVA.
+Once the MVA is applies, the signal significance in the three
+categories is increased to 2.5, 1.1 and 2.9 respectively.
 %
-In Table~\ref{table:cutflowMVA_PU}
-we also provide  the number of signal and
-    background events expected
-    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$,
-    as well as the
-    corresponding values for $S/\sqrt{B}$ and $S/B$,
-    for both the cut-based analysis (corresponding
-    to $y_{\rm cut}=0$) and after the
-    optimal MVA cut.
-    %
-    From Table~\ref{table:cutflowMVA_PU} we observe that, thanks
+We also observe that, thanks
 to the MVA, the signal significance and the
@@
 
-Combining the three categories, resolved,
-intermediate and boosted, we determine the overall signal
-significance, finding
-\be
-\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
-\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, .
-\ee
-%
-We thus conclude that the measurement of
-Higgs pair production in the $b\bar{b}b\bar{b}$ final state at the HL-LHC
-should be 
-well above the threshold for evidence.
-%
-On the other hand, such measurement seems to be out of reach
-for the total integrated luminosity expected by the end of Run II.
-
 In Table~\ref{table:cutflowMVA_fakes} we compare,
 after the MVA is applied,
-the total
-number of background events, $N_{\rm ev}^{\rm tot}$,
-    expected at the HL-LHC, with
-     $N_{\rm ev}^{\rm 4b}$, the corresponding number
-    from the QCD $4b$ component, in the cases with and without
-    PU.
+the 
+number of background events  expected at the HL-LHC,
+both the total number, $N_{\rm ev}^{\rm tot}$,
+and those from the  QCD $4b$ component
+$N_{\rm ev}^{\rm 4b}$, for the analyses without and
+with PU.
 %
-    The MVA has been trained to the total background sample,
+ We also quote the corresponding values of the signal 
+    significance and the signal over background ratio.
+    %
+    Note that the MVA has been trained to the total background sample,
     though differences
@@
     %
-    The major improvement of eliminating the contamination
-    of light and charm jet mis-identification is for the boosted and resolved categories.
-%
-    In the case of PU+SK, combining the three categories but assuming that
-    the only relevant background is the irreducible QCD $4b$ component,
-    we obtain
-    \be
-\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 5.3~(1.8) \, ,\quad
-\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
-\ee
-Therefore, a discovery of Higgs pair production at the
-HL-LHC might be possible if the
-mis-identification of light and charm jets as
-$b$-jets can be  reduced.
-%
-With these assumptions, and provided
-the signal efficiency can be further enhanced,
-this measurement might even be feasible
-by the end of Run II.
+    The major improvement from eliminating the contamination
+    from light and charm jet mis-identification arises
+    for the boosted and resolved categories.
 %
@@
       \end{tabular}
-  \caption{\small Post-MVA number of total background events, $N_{\rm ev}^{\rm tot}$,
-    expected at the HL-LHC, compared
-    with $N_{\rm ev}^{\rm 4b}$,
-    the number of QCD $4b$ background events.
+  \caption{\small Post-MVA number of background events
+    expected at the HL-LHC, comparing the total number, $N_{\rm ev}^{\rm tot}$,
+    with those from the QCD $4b$ background
+    component only, $N_{\rm ev}^{\rm 4b}$.
      %
-    We also indicate the corresponding signal significance and signal over background
-    ratios.
+    We also quote the values of the signal 
+    significance and signal over background ratios in each case.
         \label{table:cutflowMVA_fakes}
@@
 
+Combining the three categories, taking into
+account all background components, we obtain the overall signal
+significance:
+\be
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
+\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
+\ee
+%
+indicating  that the measurement of
+Higgs pair production in the $b\bar{b}b\bar{b}$ final state at the HL-LHC
+should be 
+well above the threshold for evidence.
+%
+On the other hand, such measurement seems to be
+extremely challenging
+for the total integrated luminosity expected by the end of Run II.
+%
+Under the  assumption that
+    the only relevant background would be the irreducible QCD $4b$ component,
+    we obtain instead:
+    \be
+\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 5.3~(1.8) \, ,\quad
+\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
+\ee
+Therefore, a discovery of Higgs pair production at the
+HL-LHC might be possible if the
+mis-identification of light and charm jets as
+$b$-jets can be  reduced.
+%
+With these assumptions, and provided
+the signal efficiency can be further enhanced,
+this measurement might even be possible
+by the end of Run II.
+%
+The smaller value of $\la n_{\rm PU}\ra$ at Run II as compared
+to the HL-LHC enviroment should be beneficial in this
+respect.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-14 paper/sec-conclusions.tex
conclusion edits

@@
 We take into account 
-all relevant backgrounds, in particular
+the most relevant backgrounds, in particular
 the irreducible $4b$
@@
 We have also demonstrated the robustness of our analysis strategy
-under high-PU conditions.
+under the addition of significant pileup.
 
@@
 One handle would be to reduce the contribution from light and charm
-jet mis-identification, ensuring that the
-$2b2j$ component is subdominant over the $4b$ background.
+jet mis-identification, ensuring that the irreducible $4b$ background 
+ dominates over the $2b2j$ component.
 %
@@
 to optimize the PU subtraction
-strategy, in order
+strategy in order
 to reduce the impact of PU in the modelling
 of kinematical variables and the associated
-degradation of the MVA discrimination.
+degradation in the MVA discrimination.
 %
 Such experimental improvements might
-even make possible
-an observation of Higgs pair production already at the
+even make
+an observation of Higgs pair production possible at the
 end of Run II with
@@
 the present analysis, including the MVA optimization,
-at 100 TeV, will allow us
+at 100 TeV will allow us
 to assess the accuracy of an extraction of the trilinear
@@
 %
-We thus plan to study the constraints
+We therefore plan to study the constraints
 on the coefficients of these effective
@@
 other final states, such as
-$b\bar{b}\gamma\gamma$, allow to better constrain operators
+$b\bar{b}\gamma\gamma$, allow for a better constraint upon operators
 that modify the high-energy behavior
@@
 As in the case of the extraction of the Higgs
-trilinear coupling $\lambda$, such study
+trilinear coupling $\lambda$, such a study
 would be a computationally intensive task, since
 BSM dynamics will modify the shapes of the kinematical
-distributions, and thus in principle each point in the EFT parameter
-space would require a re-optimization with a new training
-of the MVA.
+distributions and thus in principle each point in the EFT parameter
+space would require a re-optimization with a newly trained
+MVA.
 %
@@
 %
-We thank E.~Vrodynou and M.~Zaro for
+We thank E.~Vryonidou and M.~Zaro for
 assistance with di-Higgs production

### 2015-12-15 paper/HH4b.tex

--- 2015-12-07 paper/HH4b.tex
@@
 \abstract{
-  The measurement of Higgs pair production is one of the cornerstones of
-  the LHC program for the next years.
+  The measurement of Higgs pair production will be a cornerstone of
+  the LHC program in the coming years.
   %
-  Double Higgs production provides a unique window to the electroweak
-  symmetry breaking mechanism due to its sensitivity
+  Double Higgs production provides a crucial window upon the mechanism of electroweak
+  symmetry breaking and has a unique sensitivity
   to the Higgs trilinear coupling.
@@
   We account for all relevant
-  backgrounds, including the contribution from light and charm
-  jet mistags that is found to be comparable
+  backgrounds, including the contributions from light and charm
+  jet mistags, which are ultimately comparable in size 
   to the irreducible $4b$ QCD background.
   %
-  We demonstrate the robustness of our analysis in a high pile-up
-  environment.
+  We demonstrate the robustness of our analysis strategy against the
+  effects of pile-up.
   %
   For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
-  an overall signal significance of  $S/\sqrt{B}\simeq 4$ is obtained.
-  %
-  Our analysis indicates
+  a signal significance of  $S/\sqrt{B}\simeq 4$ is obtained,
+  indicating
   that the $b\bar{b}b\bar{b}$ channel
-alone should allow the observation of double Higgs production
+alone could allow for the observation of double Higgs production
   at the High Luminosity LHC.

### 2015-12-15 paper/sec-analysis.tex

@@
 %
-First of all, we discuss the settings
-for jet clustering  and the strategy for $b$-tagging.
-%
-Then we discuss the categorisation of events in different
-topologies and how to prioritise among them.
+First of all we discuss the settings
+for jet clustering and the strategy for jet $b$-tagging.
+%
+Following this we discuss the categorisation of events into different
+topologies, and how the different topologies may be prioritised.
 %
 We motivate our choice of analysis cuts by comparing signal and background
-for representative kinematical distributions.
+distributions for representative kinematic variables.
 %
@@
 jet reconstruction algorithms
-obtained from
+of
 {\tt FastJet}~\cite{Cacciari:2011ma,Cacciari:2005hq},
@@
 %
-We use different types of jet definitions:
+Here we use the following jet definitions:
 \begin{itemize}
@@
   and pseudo-rapidity $|\eta|<2.5$, within the central 
-  acceptance of ATLAS and CMS, the region
+  acceptance of ATLAS and CMS, and therefore within the region
   where $b$-tagging is possible.
@@
   satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}
-  conditions.
-  %
-  We use the {\tt FastJet} default
-  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
-  %
-  Before applying the MDT, the large-$R$ jet
+  conditions, where the {\tt FastJet} default
+  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$ are used.
+  %
+  Before applying the BDRS tagger, the large-$R$ jet
   constituents are reclustered with the Cambridge/Aachen (C/A)
@@
   but this time with a smaller radius parameter, namely
-  $R=0.3$~\cite{Aad:2015uka}.
+  $R=0.3$~\cite{Aad:2015uka}. They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
  %
@@
   %
-  They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
-  %
 \end{itemize}
 
-In addition, we have
+We have
 also explored the possible improvements
@@
 
-  This variable is defined by reclustering the constituents of a jet with the
+  This variable is obtained by reclustering the constituents of a jet with the
   $k_t$ algorithm~\cite{Ellis:1993tq},
@@
   \ee
-  with $p_{T,k}$ is the $p_T$ of the constituent particle $k$ and $\delta R_{ik}$ the distance from
+  where $p_{T,k}$ is the $p_T$ of the constituent particle $k$ and $\delta R_{ik}$ the distance from
   subjet $i$ to constituent $k$.
@@
 %
-For each type of jet definition used, a different
+For each jet definition described above, a different
 $b$-tagging strategy is adopted:
@@
   %
-  Trying to $b$-tag all the
+  Attempting to $b$-tag all of the
   small-$R$ jets that satisfy the acceptance cuts worsens the
-  overall performance
-  due to combinatorics.
+  overall performance as the probability of fake $b$-tags increases
+  substantially.
 
@@
     else one finds a degradation of the
-    signal significance due to combinatorics.
+    signal significance.
     %
@@
 
-Concerning the values of the $b$-tag probability, $f_b$, and
-the $b$-mistag probability of light and charm jets, $f_l$ and  $f_c$
-respectively,
+For the $b$-tagging probability $f_b$, along with
+the $b$-mistag probability of light ($f_l$) and charm ($f_c$) jets,
 we used the values $f_b=0.8$, $f_l=0.01$
@@
 under variations of
-the underlying production model of Higgs pairs is modified,
+the underlying production model of Higgs pairs,
 for instance in the case of
 BSM dynamics, which can substantially increase
-the degree of boost of the final state.
+the degree of boost in the final state.
 
@@
  Each of these two large-$R$, $b$-tagged, jets are 
- thus candidates
+ therefore candidates
  to contain the decay products of a Higgs boson.
@@
 
-  An event with exactly one large-$R$, $b$-tagged, jet, which
+  An event with exactly one large-$R$, $b$-tagged jet, which
   is assigned to be the leading Higgs candidate.
@@
   leading four small-$R$ jets in the event
-  by considering all possibilities of forming two pairs of jets
+  by considering all possible combinations of forming two pairs of jets
   and then choosing the configuration that minimizes the relative difference of
@@
 its invariant mass is required to lie within a fixed window
-around the nominal Higgs boson mass of $m_h= 125$
+of width $80~{\rm GeV}$ around the nominal Higgs boson mass of $m_h= 125$
 GeV.
 %
-In particular we require the condition
+Specifically we require the condition
 \be
@@
 The motivation
-for this choice 
+for such a loose cut 
 is that further improvements of the
@@
 The exception is the boosted and intermediate categories, which have
-orthogonal jet selection requirements.
-%
-The optimization of the analysis
-of the three categories is performed inclusively, and
-then events are exclusively assigned to specific category
-starting with the one with the highest signal significance.
+conflicting jet selection requirements.
+%
 
 The separate optimisation of the three categories needs to be performed in
-a inclusive analysis, and then we introduce a
- priorisation starting with the category of highest signal significance.
+a inclusive analysis, following which we introduce a
+ prioritisation whereby events are assigned an exclusive category starting 
+ with the category of highest signal significance.
 
@@
 %
-We find that the category with higher significance is
+We find that the category with highest significance is
 the boosted one,
-followed by the intermediate and the resolved ones, the latter two
+followed by the intermediate and the resolved topologies, the latter two
 with similar significance.
 %
-Therefore, for the final analysis, we turn to an exclusive approach:
-if an event satisfies the boosted requirements, it is assigned to
+Therefore, when ascertaining which category an event is to be exclusively placed:
+if the event satisfies the boosted requirements, it is assigned to
 this category, else we check if it suits the intermediate
@@
 
-We now motivate the values of
+We now motivate the
 kinematic cuts applied to the different categories, 
@@
 %
-We first present results without PU, and then
+Firstly we present results without PU, and then
 discuss
@@
   subleading (right) large-$R$ jets in the boosted category,
-  in signal and background events.
+  for signal and background events.
   %
@@
 
-Turning to the resolved category, an important aspect to account
+Turning to the resolved category, an important aspect to account for
 in the corresponding selection
@@
 that in general the boost from the Higgs decays is moderate.
-%
-These considerations lead to the requirement that the $p_T$
-selection
-for the small-$R$ jets cannot be too large.
+Therefore the $p_T$ selection cuts for the small-$R$ jets cannot be too large.
 %
@@
 small-$R$ jets in signal and background events: we observe that both
-distributions are peaked at $p_T \le 50$ GeV, with the signal distribution
+distributions peak at $p_T \le 50$ GeV, with the signal distribution
 eventually becoming dominant at large $p_T$.
 %
-The feasibility to being able to trigger on four small-$R$ jets with a relatively
+The feasibility of triggering on four small-$R$ jets with a relatively
 soft $p_T$ distribution is one of the experimental challenges for
@@
 As expected, the production
-is mostly central, more in the case
+is mostly central, more so in the case
 of signal events, since backgrounds are dominated by
-QCD $t$-channel exchange, and thus the
-selection criteria on the jet rapidity  are highly efficient.
+QCD $t$-channel exchange, therefore the
+selection criteria on the jet rapidity are very efficient.
 
@@
 
-One of the selection cuts with highest discrimination power is the requirement
+One of the most discriminating selection cuts is the requirement
 that the invariant mass of the Higgs candidate (di)jets must lie within a window
@@
 %
-While the signal distribution is of course peaked at the
+While the signal distribution naturally peaks at the
 nominal Higgs mass, the background distributions
@@
 and out-of-cone radiation, as well
-as from the four-momenta smearing applied to final state particles.
+as from the four-momentum smearing applied to final state particles
+as part of our minimal detector simulation.
 %
@@
 
-Another important kinematic distribution for
-this process is the invariant mass
-of the di-Higgs system.
-%
-This is a direct measure of the boost of the system,
+The invariant mass of the di-Higgs system is another important
+kinematic distribution for this process.
+%
+Thie di-Higgs invariant mass is a direct measure of the boost of the system,
 which in  BSM scenarios can be substantially
@@
 to the background,
-and thus one expects that cutting in $m_{hh}$ would help signal
+and therefore one expects that cutting in $m_{hh}$ would help signal
 discrimination: we will verify this using the MVA.
@@
 %
-In this case, signal and background distributions
-look similar.
+In this case, signal and background distributions are not significantly
+differentiated.
 %
@@
 %
-Again we see that the background has a steeper $p_T^{hh}$ distribution
-that the signal, in both categories, thus this variable
-should provide additional discrimination power, and therefore
-this distribution is one of the inputs for the MVA.
+Once more we see that the background has a steeper fall-off in $p_T^{hh}$
+than the signal, in both categories, therefore this variable
+should provide additional discrimination power, motivating it's inclusion
+as one of the inputs for the MVA.
 %
@@
 
-We now study the discrimination power to separate signal
-and background events contained in
-jet substructure
-variables.
+We shall now investigate the discrimination power provided by jet substructure
+quantities.
 %
@@
 the inherent differences in the internal structure of jets
-between QCD jets and jets originated from the Higgs decays.
+between QCD jets and jets originating from the Higgs decays.
 %
@@
 in rather
-different regions: for example, the $k_t$ splitting scale $\sqrt{d_{12}}$
+different regions. For example, the $k_t$ splitting scale $\sqrt{d_{12}}$
 peaks around 80 GeV (40 GeV) for signal (background) events, while
@@
 
-Here we turn to discuss how the description of kinematic
+Now we turn to discuss how the description of kinematic
 distributions for $hh\to 4b$ signal
 and background processes are
-modified in a high pile-up (PU) environment.
+modified in the presence of pile-up (PU).
 %
@@
 %
-The idea underlying {\tt SoftKiller} is based on eliminating particles
+The idea underlying {\tt SoftKiller} consists of eliminating particles
 below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
@@
 %
-We apply {\tt SoftKiller}
-to particles at the end of the parton shower, before
+The {\tt SoftKiller} subtraction is applied to particles at the end of the parton shower, before
 jet clustering.
@@
     The invariant mass distributions of Higgs candidates in signal
-events, in the resolved category, comparing the results without PU,
-with PU $\la n_{\rm PU}\ra=80$ but without any subtraction, and the
-corresponding results now with SK subtraction.
+events in the resolved category, comparing the results without PU,
+with PU $\la n_{\rm PU}\ra=80$. The distribution is then compared with and without SK subtraction.
 }
@@
 
-To validate PU subtraction,
+To validate the subtraction of PU,
 we compare representative kinematic distributions
@@
 Once SK subtraction is performed, we recover a distribution much closer
-to the ones without PU, with only a small shift of $\simeq 5$ GeV
+to the no PU case, with only a small shift of $\simeq 5$ GeV
 and a broadening of the mass
@@
 in the boosted selection as compared to the resolved case,
-with the position of the Higgs mass peak essentially
+with the position of the Higgs mass peak being essentially
 unchanged, and only a moderate broadening of the
@@
     both without PU and with
-    PU, $\la n_{PU}\ra=80$, subtracted with {\tt SoftKiller}.
+    PU, $\la n_{PU}\ra=80$, subtracted by {\tt SoftKiller}.
 }
@@
 candidate, $p_t^{h_1}$ and the invariant mass of the di-Higgs system
-$m_{hh}$, in both for the boosted and
-for the resolved categories.
+$m_{hh}$, in both the boosted and resolved categories.
 %
@@
 The effect of PU is small in the boosted case, and generally moderate
-in the resolved case, except for large $p_T$ values.
+in the resolved case, except for at large $p_T$.
 %
@@
 %
-Therefore, we can consider the PU subtraction strategy
+Therefore we can consider the PU subtraction strategy
 as validated for the purposes of this study, although
@@
 with PU subtracted with SK, we observe that both substructure variables
-are reasonably robust in a high-PU environment.
+are reasonably robust in a environment including PU.
 %
 The ratio of energy correlation functions $D_2^{(\beta)}$ 
-was indeed constructed~\cite{Larkoski:2013eya}
+was indeed explicitly constructed~\cite{Larkoski:2013eya}
 to be robust against PU contamination.
@@
 the relative differences between
-signal over background distributions are modified in a high-PU
-environment.
+signal over background distributions are modified by the inclusion of PU.
 %
@@
       %
-      This is specially noticeable for the substructure variables, which
+      This is especially noticeable for the substructure variables, which
       exhibit a similar discrimination power both with and without
@@
         We find a mass resolution of around 9 GeV in the case
-        without PU, which is only slightly degraded
+        without PU, which worsens only slightly
         to around 11 GeV in the case of $\la n_{\rm PU}\ra=80$ PU
@@
         %
-        We also note that, after subtraction, the peak of
+        We also note that after subtraction, the peak of
         the invariant mass distributions of Higgs candidates

### 2015-12-15 paper/sec-intro.tex

@@
 physics goals of the LHC program in its recently started high-energy
-phase, as well as for its future high-luminosity upgrade (HL-LHC),
+phase, as well as for its future high-luminosity upgrade (HL-LHC)
 which aims to accumulate a total integrated
@@
 many Beyond the SM (BSM)
-scenarios predict enhanced rates for double Higgs production, and
-thus searches for this process have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015xja,Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
+scenarios predict enhanced rates for double Higgs production, therefore searches have already been performed by ATLAS and CMS with Run I data~\cite{Aad:2015xja,Aad:2015uka,Aad:2014yja,Khachatryan:2015yea,Chatrchyan:2011wt}
 and will continue at Run II.
 %
-In addition, Higgs pair production will also be of
-crucial relevance at
+The study of Higgs pair production will also be relevant to
 any future high-energy 
@@
 %
-For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the
+For a center-of-mass energy of $\sqrt{s} = 14\,$TeV, the
 next-to-next-to-leading order (NNLO)
@@
 %
-All these channels are challenging due to the small production
+All of these channels are challenging due to the small production
 rates: at 14 TeV, the inclusive total cross-sections are
@@
 While the SM production rates for Higgs
-pairs are small, these can be substantially
+pairs are small, they can be substantially
 enhanced in a variety of BSM scenarios.
@@
 %
-Many other exotic searches involves Higgs pairs in the final
+Many other exotic searches involve Higgs pairs in the final
 state, such as the recent
-searches for heavy Higgs bosons $H$~\cite{Khachatryan:2015tha}.
+search for heavy Higgs bosons $H$~\cite{Khachatryan:2015tha}.
 
@@
 %
-However, a measurement in this channel
+However a measurement in this channel
 needs to deal with an overwhelming QCD multi-jet background.
@@
 %
-As will show, due to both
+As we will show, due to both
 selection effects and $b$-quark radiation in the
 parton shower, the
-contribution of the $2b2j$ process is comparable to
+contribution of the $2b2j$ process is as significant as
 the irreducible $4b$ component.
 
-In this work, we revisit the feasibility of SM Higgs pair production in
+In this work, we revisit the feasibility of SM Higgs pair production by
 gluon-fusion
@@
 %
- Our strategy is based on a combination of traditional cut-based
- methods with multivariate analysis (MVA).
+ Our strategy is based upon a a combination of traditional cut-based
+ methods and multivariate analysis (MVA).
   %
@@
   We also assess the robustness of our analysis strategy in
-  an environment with high pile-up (PU).
+  an environment including pile-up (PU).
   %
@@
   that the $b\bar{b}b\bar{b}$ channel
-alone should allow for the observation of double Higgs production
+alone may allow for the observation of double Higgs production
   at the HL-LHC.
@@
 
-The structure of this paper is the following.
+The structure of this paper proceeds as follows.
 %
@@
 In Sect.~\ref{sec:analysis}
-we introduce our analysis strategy, and in particular
+we introduce our analysis strategy, in particular
 the classification of individual events into
@@
 %
-The results the cut-based analysis
+Results of the cut-based analysis
 are then presented in Sect.~\ref{sec:results}.
@@
 significance using multivariate techniques, and
-assess the robustness of our results in a high-PU environment.
+assess the robustness of our results against the effects of PU.
 %

### 2015-12-15 paper/sec-mcsamples.tex

@@
 
-In this section we discuss the settings of the
-Monte Carlo generation of the signal and background
-processes used in this analysis.
+In this section we discuss the Monte Carlo generation of the signal and background
+process samples used in this analysis.
 %
-We also discuss the modelling of detector
+We shall also discuss the modelling of detector
 resolution effects.
@@
 The calculation is performed in the
-$n_f$=4 scheme,  accounting for  $b$-quarks mass effects,
-and the renormalization and factorization
+$n_f$=4 scheme,  accounting for  $b$-quark mass effects. 
+The renormalization and factorization
 scales are taken to be $\mu_F=\mu_R=H_T/2$,
@@
 %
-For the input parton distribution functions (PDFs), we 
+For the input parton distribution functions (PDFs) we 
 adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
@@
     %
-    The non-trivial interplay between the diagram with a heavy quark box
-    and that of the triangle loop,
-    that can lead to either
-    constructive or destructive interference,
-    complicates the extraction of
+    The non-trivial interplay between the heavy quark box and the triangle loop diagrams
+    can lead to either constructive or destructive interference
+    and complicates the extraction of
     the trilinear coupling
@@
 %
-Single Higgs production processes, such as $Z(\to b\bar{b})h(\to b\bar{b})$
-and $t\bar{t}h(\to b\bar{b})$, and electroweak backgrounds, such $Z(\to b\bar{b})b\bar{b}$,
+Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
+and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
 are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
-and thus not included in the present analysis.
+and are therefore not included in the present analysis.
 %
@@
 %
-For the $4b$ and $2b2j$ samples, a NLO/LO $K$-factor has been determined
-using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, which turns out to be 1.6 and 1.3
-respectively.
+For the $4b$ and $2b2j$ samples NLO/LO $K$-factors of 1.6 and 1.3
+respectively have been determined
+using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
 %
-For the $4j$ sample, we rescale the LO
+For the $4j$ sample, we rescale the LO cross-section
 using the {\tt BLACKHAT}~\cite{Bern:2011ep}
-calculation, that indicates
-a NLO/LO $K$-factor of 0.6.
+calculation, resulting in
+an NLO/LO $K$-factor of 0.6.
 %
 Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
-to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, which leads
+to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, leading
 to a $K$-factor of 1.4.
@@
 The $K$-factors that we use to rescale
-the signal background samples are collected in
+the signal background samples are summarised in
 Table~\ref{tab:samples}.
@@
 We also provide the corresponding inclusive $K$-factor
-  that is applied to reproduce the known
+  which is applied to reproduce the known
   higher-order results. \label{tab:samples}
@@
 %
-In addition, at the matrix-element level
-all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
+At the matrix-element level
+all final state particles must also be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
 %
@@
 From Table~\ref{tab:samples}
-we see that the $t\bar{t}$ and QCD $4b$ samples are of
-the same order of magnitude, however, the former can be efficiently
+we see that the $t\bar{t}$ and QCD $4b$ cross-sections are of
+the same order of magnitude. However the former can be efficiently
 reduced by using top quark reconstruction criteria.
@@
 The $bbjj$ cross-section is more than two orders
-of magnitude larger as compared to the
-$4b$ result, but will be suppressed
+of magnitude larger than the $4b$ result, but will be suppressed
 by the light and charm jet mis-identification rates,
@@
 For comparison with the latter numbers, 
-we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV, and
-also that all jets must be within an acceptance of $|\eta| \le 2.5 $.
+we require that all samples include four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, where the leading jet must have $p_T \ge 100$ GeV, and with all jets within an acceptance of $|\eta| \le 2.5 $.
 %
@@
 detector simulation, it is important to include an estimate of detector
-effects in the analysis, in particular for the finite energy
-and angular resolutions, which directly
+effects in the analysis, particularly for the finite energy
+and angular resolutions which directly
 degrade the reconstruction of important kinematical variables, such as
@@
 %
-In this work, we simulate the finite energy resolution of the ATLAS and CMS
+Here we simulate the finite energy resolution of the ATLAS and CMS
 hadronic calorimeters by applying a Gaussian smearing of the transverse
-momentum $p_T$ for all
-final-state particles, before jet clustering,
-with mean zero and standard deviation $\sigma_E$, that is,
+momentum $p_T$ with mean zero and standard deviation $\sigma_E$ for all
+final-state particles before jet clustering, that is,
 %
@@
 \ee
-with $r_i$ an univariate Gaussian random number, different for each
+with $r_i$ a univariate Gaussian random number, different for each
 of the $N_{\rm part}$ particles in the event.
 %
-We take as baseline value for the transverse momentum smearing a
+We take as a baseline value for the transverse momentum smearing a
 factor of $\sigma_E=5\%$.
@@
 
-In addition, to account for the finite angular resolution of the calorimeter,
+To account for the finite angular resolution of the calorimeter,
 the $\eta$-$\phi$ plane is divided into regions of
 $\Delta \eta \times \Delta \phi=0.1$, and each final state particle
-which falls in each of these cells is set of have the same $\eta$
+which falls in each of these cells is set to the same $\eta$
 and $\phi$ values of the center of the
@@
 four-momentum is that of a light-like particle, since we neglect all
-hadron masses in this analysis.
+jet constituent masses in this analysis.
 

### 2015-12-15 paper/sec-mva.tex

@@
 At the end of the cut-based analysis,
-combining the three categories,
+by combining the three event topologies,
 we obtain a signal significance of $S/\sqrt{B}\simeq 1.7 (3.5)$
@@
  can be enhanced when the cut-based analysis
- is complemented with a multivariate analysis (MVA).
+ is complemented by a multivariate analysis (MVA).
 %
@@
 %
-In particular, the classification of events between signal and
+In particular, the classification of events into signal and
 background processes by means of MVAs is a
@@
 %
-Then we assess the robustness of the MVA strategy in
-high-PU environments.
+Finally we assess the robustness of the MVA strategy in
+the case of significant contamination from pileup.
 
@@
 %
-This family of ANNs is also known as {\it deep} neural networks, since they have
-a richer architecture with hidden layers.
+This family of ANNs are also known as {\it deep} neural networks, due to their multi-layered architecture.
 %
-The input to the MVA are the
+The MVA inputs are a set of kinematic variables describing the
 signal and background
@@
 %
-The output of the trained ANNs allows the identification, in a fully automated way,
-of the most relevant variables to discriminate between 
+The output of the trained ANNs also allows for the identification, in a fully automated way,
+of the most relevant variables in the discrimination between 
 signal and background.
@@
   \vspace{-2cm}
-  \caption{\small Architecture of the Artificial
+  \caption{\small Schematic of the Artificial
     Neural Network (ANN)
@@
 \ee
-which implies that the  error function $E(\{\omega\})$
-that needs to be minimized during the ANN training is 
+consequently we can define an error function $E(\{\omega\})$
+to be minimized during the ANN training. In this case, the error function is
 the cross-entropy function, defined as
@@
  so it is crucial to ensure that the input MC sample is large enough
- to avoid the contamination from MC statistical fluctuations.
+ to avoid contamination from MC statistical fluctuations.
 
- The training of the neural networks thus consist on the
+ The training of the neural networks therefore consists of the
  minimization of the cross-entropy error,
@@
  %
- This cross-validation entails dividing the input MC dataset into two disjoint sets,
- and use one for the training and the other for the validation: the optimal
- stopping point is then indicated by the minimum of the error function
- Eq.~(\ref{cross-entropy}) for the validation sub-sample.
+ This cross-validation proceeds by dividing the input MC dataset into two disjoint sets,
+ using one for training the ANN and the other for validation: the optimal
+ stopping point is then given by the minimum of the error function
+ Eq.~(\ref{cross-entropy}) to the validation sub-sample.
  %
@@
 
- To ensure that we include the variables with higher discriminatory power,
+ To ensure that we include the variables with the most discriminating power,
  we need to train
- the MVA on a large number of kinematic distributions.
+ the MVA on a broad array of kinematic variables.
 %
@@
 In particular, in the case of large-$R$ jets (for the boosted
-and intermediate categories), we are fully exploiting the jet
-substructure information.
+and intermediate categories), we are fully exploiting the available information 
+on jet substructure.
 
@@
  %
- Therefore, we end up with
+ This leads to
  a total of $N_{\mathrm{var}}=13,17$ and 21 variables for the
@@
 in an automated way,
-and to ignore those that have little effect, it is advantageous to
-include as many input variables as possible.
+and to suppress those which have little effect, it is advantageous to
+include a wide array of input variables.
 %
-This is one of the main advantages of ANNs in this context: they are
-inherently redundant, so
+This is one of the main advantages of ANNs in this context: 
+their inherent redundancy means that 
 adding additional information, even if carries very little weight,
 should not degrade
-the classification power of the MVA, other than making the GA
+the classification power of the MVA, aside from making the GA
 minimization somewhat less efficient.
@@
 Therefore,
-the more differentiated is the distribution of the ANN output
+the more differentiated the distribution of the ANN output is
 for signal and background events, the more efficient
@@
 
-From Fig.~\ref{fig:nnresponse} we see that in the boosted category the MVA manages
-to achieve a clear discrimination between signal and background, with the two distributions
-nicely peaking at 1 and at 0 respectively.
+From Fig.~\ref{fig:nnresponse} we see that in the boosted category the MVA can produce
+a clear discrimination between signal and background, with the two distributions
+forming peaks at their respective optimal limits.
 %
@@
 %
-The performance of the MVA discrimination is similar though slightly worse in the intermediate
+The performance of the MVA discrimination is similar, although slightly worse in the intermediate
 and resolved categories.
@@
 It is clear that we can achieve  high signal efficiency by using
-a small value of $y_{\rm cut}$, but this choice will be
-affected from a poor background
+a small value of $y_{\rm cut}$, but such a choice would be
+affected by poor background
 rejection.
@@
 
-It important to verify, for each value of
+It is important to verify for each value of
 the cut in the ANN output $y_{\rm cut}$, how many
@@
 
-A useful property of MVAs, as the one used in our
+A useful property of MVAs such as the one used in our
 analysis,
-is that they provide direct  physical insight about which of the
+is that they can provide direct  physical insight about which of the
 input variables contribute the most to the separation between
@@
 Those input variables with a larger value of $\omega^{\rm (tot)}_i$ will be those
-that play a dominant role in enhancing the signal
+that play a more significant role in enhancing the signal
 discrimination using the MVA.
@@
 %
-The important information
-is contained in the relative strengths of the total associated weight
-for each of the input variables.
+% The important information
+% is contained in the relative strengths of the total associated weight
+% for each of the input variables.
 %
@@
   signal over background ratio, $S/B$, for the boosted, intermediate
-  and resolved categories as  function of the cut
+  and resolved categories as a function of the cut
   $y_{\rm cut}$ in the ANN output.
@@
 $S/B$ as a function of $y_{\rm cut}$
-for the three categories are
+for the three categories are given in 
 Fig.~\ref{fig:sb_mva}.
@@
 uncertainties in the background determination to
-be at the same level of a few percent level.
+be at the same level of a few percent.
 
@@
 ensuring that the number of signal events $N_{\rm ev}$
-expected at the HL-LHC is not too small.
+expected at the HL-LHC does not become too low.
 %
-In  addition, we require
+In  addition we require
 that the number of MC events used to define the signal
 category (events with $y_i \ge y_{\rm cut}$)
-is large enough to avoid the biases and statistical
+is sufficiently large in order to avoid the biases and statistical
 fluctuations associated to a small training sample.
 %
-In Table~\ref{table:cutflowMVA} where we quote
+In Table~\ref{table:cutflowMVA} we quote
 the value of the optimal ANN output
@@
     %
-    we quote the number of signal and
+    We quote the number of signal and
     background events
@@
 From Table~\ref{table:cutflowMVA} we see that
-after we apply the MVA
+after the application of the MVA, 
 the signal significance in the boosted category increases
@@
 %
-For the intermediate and resolved category, $S/\sqrt{B}$
+For the intermediate and resolved categories, $S/\sqrt{B}$
 increases from 0.9 and 1.0 to 4.8 and 4.5, with
@@
 The overall combined significance is thus $S\sqrt{B}\simeq 8$,
-well above the threshold for discovery.
-%
-These remarkable results are however subject to a justified
-criticism:
-the HL-LHC will be a high-PU environment,
+well above the threshold for discovery. However such a significance
+is unrealistic given that the HL-LHC will be a high-PU environment,
 which will affect the description of the various
@@
 %
-Therefore, next we quantify the robustness of the
+Therefore we shall now quantify the robustness of the
 results summarized Table~\ref{fig:sb_mva}
-in a realistic high-PU environment.
+in a realistic environment including the effects of PU.
 
@@
 In this section we study how the MVA results are modified
-when the analysis is performed in a high-PU environment.
+when the analysis is performed including PU.
 %
@@
   %
-  In addition, we also quote in
+  Additionally we quote in
   both cases the number of signal and
@@
 %
-Once the MVA is applies, the signal significance in the three
-categories is increased to 2.5, 1.1 and 2.9 respectively.
+Once the MVA is applied, the signal significance in the three
+categories increases to 2.5, 1.1 and 2.9 respectively.
 %
-We also observe that, thanks
+We also observe that, due
 to the MVA, the signal significance and the
@@
 %
-We thus conclude that, as was already the case
+We can therefore conclude that, as was already the case
 without PU,
 the boosted category is the most promising
-one for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
+topology for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
 final state
-at the HL-LHC, also for the case of a high-PU environment, but that
-important information will also be obtained from
+at the HL-LHC, also in the case of a high-PU environment.
+However important information can also be obtained from
 the resolved category, which has a comparable significance.
@@
 Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we observe
-that the intermediate category is substantially degraded once PU effects
+that the intermediate category is substantially worsened once PU effects
 are accounted for due to a sizable
@@
 %
-As can be seen, the MVA-driven enhancement is robust in the
+As can be seen, the MVA-driven enhancement remains robust in the
 presence of PU.
@@
 achieve a signal significance of
-around $S/\sqrt{B}$ between 2.5 and 3.0 (depending on the
+ $S/\sqrt{B}$ between 2.5 and 3.0 (depending on the
 specific choice of $y_{\rm cut}$)
@@
 %
-On the other hand, the intermediate category is now marginal.
+On the other hand, the significance obtainable from the intermediate category is now marginal.
 %
@@
 in the case without PU also hold when the analysis
-is performed in a high-PU environment.
+is performed in an environment including pileup.
 %
@@
 
-It is useful to quantify which of the input variables
-to the MVA carry the highest discrimination power
+It is useful to quantify which of the MVA input variables
+carry the highest discrimination power
 in the case of PU,
@@
 As we can see in Fig.~\ref{fig:nnweights_PU},
-this is the case also with PU.
+this remains the case under the addition of PU.
 
@@
 the 
-number of background events  expected at the HL-LHC,
-both the total number, $N_{\rm ev}^{\rm tot}$,
+number of background events  expected at the HL-LHC.
+Both the total number, $N_{\rm ev}^{\rm tot}$,
 and those from the  QCD $4b$ component
@@
     %
-    The major improvement from eliminating the contamination
+    The largest improvement from eliminating the contamination
     from light and charm jet mis-identification arises
@@
      %
-    We also quote the values of the signal 
+    Also provided are the values of the signal 
     significance and signal over background ratios in each case.
@@
 %
-On the other hand, such measurement seems to be
+On the other hand, such a measurement seems to be
 extremely challenging

### 2015-12-15 paper/sec-results.tex

@@
 In this section we present the results of the 
-cut-based analysis and provide a
-cut-flow for the different analysis steps.
+cut-based analysis described in the previous section, and provide 
+cut-flows for the different analysis steps.
 %
@@
 is affected if only the $4b$ component of the
-QCD multi-jet background is taken into account but not 
-the $2b2j$ and $4j$ components.
+QCD multi-jet background is taken into account (leaving out the 
+the $2b2j$ and $4j$ components).
 %
-First we present the results without considering PU,
-followed by the corresponding analysis of the PU effect.
+First we present the results in an environment with no pile-up,
+followed by the corresponding analysis including PU effects.
 
@@
 We consider all relevant backgrounds (see Sect.~\ref{mcgeneration}),
-and discuss how results are modified if only the $4b$
-component is kept.
-%
-At each stage of the cut-flow, we also provide the
-the signal significance, $S/\sqrt{B}$, and the signal
-over background ratio, $S/B$, corresponding to the
- HL-LHC with
-an integrated luminosity of $\mathcal{L}
-=3000$ fb$^{-1}$.
+and discuss how results are modified in the case where only the $4b$
+background is considered.
 
 In Table~\ref{tab:cutflowdetails}
-we summarize the definition of the different
-steps of the cut-flow of the present analysis,
+the different
+steps of the cut-flow in the present analysis are summarised,
 separated into the boosted, intermediate,
-    and resolved categories.
+    and resolved topologies.
     %
-    From top to bottom, additional cuts are required in addition
-    to the previous ones.
-    %
-    In more details, these different analysis steps are the following:
+    The different analysis steps proceed as follows:
 
@@
   \end{tabular}
-  \caption{\small Definition of the cut-flow steps for the boosted, intermediate
+  \caption{\small Definition of the cuts imposed successively for the boosted, intermediate
     and resolved selections.
@@
     \item {\bf C1b}: require that the above jets should
-      satisfy the corresponding $p_T$ thresholds,
+      satisfy the corresponding $p_T$ thresholds;
       $p_T \ge 200$ GeV for large-$R$ jets and
       $p_T \ge 50$ GeV for small-$R$ jets.
-    \item {\bf C1c}: same for the
-      rapidity acceptance requirement.
+    \item {\bf C1c}: jets are required to satisfy their associated
+      rapidity acceptance constraints.
     \item {\bf C1d}: the two leading large-$R$ jets must
@@
     \item {\bf C1e}: after the two Higgs candidates  have been reconstructed,
-      their invariant masses are required to lie a window around $m_H$,
+      their invariant masses are required to lie within a window around $m_H$,
       in particular between 85 and 165 GeV.
@@
             $b$-tagging conditions are
-            imposed, see
-            Sect.~\ref{sec:btagging}.
+            imposed (see
+            Sect.~\ref{sec:btagging}), and the event is categorised exclusively
+            into one of the three topologies.
       \end{itemize}
-    Signal and background events satisfying all the analysis cut up to the
+    Signal and background events satisfying all the analysis cuts up to the
     C2 level
@@
     In Table~\ref{tab:cutflow_noPU_1} we collect
-    the values for cross-sections for signal and background processes
-    for different steps of the cut flow.
+    the values for signal and background cross-sections
+    for different steps of the cut-flow.
     %
@@
       %
-      This is done both taking into account all the background components and only
+      These are provided both taking into account all the background components and only
       the $4b$ QCD background.
@@
       This implies that the signal significance at the end of the cut-based
-      analysis is degraded by about a factor two due to the contribution
+      analysis is degraded by about a factor of two due to the contribution
       of light and charm jets being mis-identified as $b$-jets.
@@
       %
-      In each case, we also provide the signal over
-      background ratio, $S/B$, and the signal
-      significance, $S/\sqrt{B}$, considering either
-      the total background or only the $4b$ component, for
-      a total integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
+      For each step, the signal over
+      background ratio $S/B$, and the signal
+      significance $S/\sqrt{B}$ are also provided, considering either
+      the total background or just the $4b$ component. Signal
+      significances are calculated for a total integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
       %
@@
 %
-We emphasize that such signal
-significance could have been enhanced
-by applying tighter selection requirements,
-but this is not needed here thanks to the subsequent
-optimisation  performed with the MVA.
-%
 From  Table~\ref{tab:cutflow_noPU_1}
@@
 %
-
+We emphasize that such signal
+significances could have been enhanced
+by applying tighter selection requirements,
+but our analysis cuts have been left deliberately loose
+in order that such optimsation may be performed by the MVA.
+%
 Both the intermediate and resolved categories benefit from higher signal yields,
-specially in the resolved category, but this enhancement is compensated by the
+specially in the resolved category, but this enhancement is compensated for by the
 corresponding
@@
 the signal significance is similar to that of the boosted category,
-$S\sqrt{B}\simeq 0.9$ in both categories.
+$S\sqrt{B}\simeq 0.9$.
 %
@@
 One of the main differences of the present study as compared
-to previous works is the inclusion of both irreducible
-and reducible background components, which allows
-quantifying
-the impact of the modeling of light and charm jet mistags. 
+to previous works is in the inclusion of both irreducible
+and reducible background components, which allows us to
+quantify
+the impact of light and charm jet mistags. 
 %
@@
 At the HL-LHC, their best result is obtained by requiring two
-SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\simeq 2.1$, with
- slightly inferior performance with the BDRS tagger.
+SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\simeq 2.1$. Using the BDRS tagger
+results in slightly poorer performance.
  %
@@
  of measuring Higgs pairs in this final state,
- specially
+ especially
  in the boosted category.
@@
     %
-    The two components lead to a rather similar shape
-    for the two distributions, with some interesting
-    differences, for instance, in the boosted
+    The two components possess a rather similar shape
+    for the two distributions, albeit with some interesting
+    differences For instance, in the boosted
     category the $4b$ component is harder for the
@@
   %
-    The $2b2j$ component leads to a longer
+    The $2b2j$ component has a longer
     tail at small values of the $m_{hh}$ invariant
@@
 
-The reason why the  $2b2j$ process
-cannot be neglected as compared to the $4b$ component
-is the following.
+% The reason why the  $2b2j$ process
+% cannot be neglected as compared to the $4b$ component
+% is the following.
 %
-In the boosted category, for example,
+In the boosted category 
 the cross-section  before
@@
 %
-Now, after $b$-tagging, the naive expectation would
-be a suppression of the former by a factor $(f_l/f_b)^2 \simeq
+After $b$-tagging, a naive assessment would
+suggest a suppression of the $2b2j$ cross-section by a factor $(f_l/f_b)^2 \simeq
 1.5\cdot 10^{-4}$, as compared to the $4b$ component,
@@
 %
-So the ratio of $2b2j$ over $4b$ should be
+In which case the ratio of $2b2j$ over $4b$ would be
 around $\simeq 3\%$, and therefore negligible.
@@
 we find that  when parton shower effects
-are accounted for, due both to radiation of $b\bar{b}$ pairs
-and from selection effects, the situation is different.
+are accounted for the situation is different, due both to radiation of $b\bar{b}$ pairs
+and from selection effects.
 %
-In this case,
+Due to these effects,
 the
@@
 \ee
-with $n^{\rm (b-jet)}_j$ the fraction of events, satisfying all the selection cuts,
-where $j$ jets, out of the leading four jets of the event,
+with $n^{\rm (b-jet)}_j$ being the fraction of events satisfying all the selection cuts,
+where $j$ jets out of the leading four jets of the event
 contain $b$ quarks (with $p_T^b\ge 15$
@@
 \ee
-However, after the parton shower the above is not a good approximation.
+However, after the parton shower the above approach is no longer accurate.
 %
-First of all, we will have a non-negligible fractions $n^{\rm (b-jet)}_j$
+First of all, we will have a non-negligible fraction $n^{\rm (b-jet)}_j$
 with $j=3,4$ also in the $2b2j$ sample, due to $b$-quark pair radiation
@@
     The relative fractions  $n^{\rm (b-jet)}_j$ of events for the resolved selection
-    for which, out of the four leading small-$R$ jets of the
+    for which out of the four leading small-$R$ jets of the
     event, $j$ jets
@@
 %
-We find that, rather than the estimate Eq.~(\ref{eq:naive}),
+We find that rather than the estimate Eq.~(\ref{eq:naive}),
 the correct ratio of $b$-tagging selection efficiencies is instead
@@
     A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
-    that, on the other hand, the $4j$ component of the background can safely
-    be neglected.
+    that, on the other hand, the $4j$ component of the background can typically
+    be safely neglected.
 

### 2015-12-15 paper/HH4b.tex
working on the text

@@
   %
-  In this work, we study the feasibility of a measurement of
+  We study the feasibility of a measurement of
   Higgs pair production in the
@@
   backgrounds, including the contributions from light and charm
-  jet mistags, which are ultimately comparable in size 
+  jet mis-identification, which are ultimately comparable in size 
   to the irreducible $4b$ QCD background.

### 2015-12-15 paper/sec-analysis.tex
working on the text

@@
 Finally, we describe the simulation of PU and validate
-the PU subtraction strategy that we adopt.
+the PU subtraction strategy.
 
@@
   %
-  In this work we use as input to the MVA the ratio of 2-subjettiness to 1-subjettiness
+  In this work we use as input to the MVA the ratio of 2-subjettiness to 1-subjettiness, namely
   \be
@@
     A large-$R$ jet is considered $b$-tagged if both
-    the leading and subleading AK03 subjets, where the ordering
+    the leading and subleading AKT03 subjets, where the ordering
     is done in the subjet $p_T$, are both individually $b$-tagged,
@@
 the $b$-mistag probability of light ($f_l$) and charm ($f_c$) jets,
-we used the values $f_b=0.8$, $f_l=0.01$
+we use the values $f_b=0.8$, $f_l=0.01$
 and  $f_c=0.1$.
@@
  %
- Each of these two large-$R$, $b$-tagged, jets are 
+ Each of these two  $b$-tagged, large-$R$ jets are 
  therefore candidates
@@
 
-  An event with exactly one large-$R$, $b$-tagged jet, which
+  An event with exactly one  $b$-tagged, large-$R$ jet, which
   is assigned to be the leading Higgs candidate.
   %
-  In addition, we require at least two small-$R$, $b$-tagged, jets,
+  In addition, we require at least two $b$-tagged, small-$R$ jets,
   which must be separated with respect to the large-$R$ jet
@@
 
-The separate optimisation of the three categories needs to be performed in
-a inclusive analysis, following which we introduce a
- prioritisation whereby events are assigned an exclusive category starting 
- with the category of highest signal significance.
-
- This has been achieved as follows.
+This is achieved as follows.
  %
@@
 the impact of PU
-on the description of the various kinematic
+on the description of the kinematic
 distributions.
@@
 In the following, all
-distributions will be normalized to their total integral.
+distributions are normalized to their total integral.
 
@@
 of the
-  leading and subleading large-$R$ jets in the boosted category, comparing
-  the shapes of the distribution in signal and background events.
+  leading and subleading large-$R$ jets in the boosted category.
   %
@@
 Another selection requirement for the boosted category is that the two
-leading AKT03 subjets of the large-$R$ jet must be relatively hard,
-in particular they should satisfy $p_T \ge $ 50 GeV.
+leading AKT03 subjets of the large-$R$ jet
+should satisfy $p_T \ge $ 50 GeV.
 %
@@
  \includegraphics[width=0.48\textwidth]{plots/pt_subleadSJ_fj2_noPU.pdf}
- \caption{\small  Same as Fig.~\ref{fig:cutplots1} for the two leading AKT03
+ \caption{\small  Same as Fig.~\ref{fig:cutplots1} for the leading (left)
+   and subleading (right) AKT03
    subjets in the subleading Higgs candidate large-$R$ jet.
@@
 Turning to the resolved category, an important aspect to account for
-in the corresponding selection
+in the  selection
 cuts is the fact that the $p_T$ distribution
@@
 %
-As noted in~\cite{deLima:2014dta}, this is a consequence of the fact
-that in general the boost from the Higgs decays is moderate.
-Therefore the $p_T$ selection cuts for the small-$R$ jets cannot be too large.
+As noted in~\cite{deLima:2014dta}, this is due to the fact
+that the boost from the Higgs decay is moderate,
+therefore the $p_T$ selection cuts for the small-$R$ jets cannot be too large.
 %
@@
 %
-Thie di-Higgs invariant mass is a direct measure of the boost of the system,
+The di-Higgs invariant mass is a direct measure of the boost of the system,
 which in  BSM scenarios can be substantially
@@
 and therefore one expects that cutting in $m_{hh}$ would help signal
-discrimination: we will verify this using the MVA.
+discrimination.
 %
 For the boosted category the overall trend of the $m_{hh}$ distribution
-is different because of the jet selection criteria, and the
+is different because of the selection criteria, and the
 distribution now peaks at higher values of the invariant mass.
@@
 cut-off at $m_{hh}^{\rm min}=250$ GeV, which is smeared due
-to 
-the parton shower and to detector resolution effects.
-%
+to parton shower and detector resolution effects.
 
@@
 than the signal, in both categories, therefore this variable
-should provide additional discrimination power, motivating it's inclusion
+should provide additional discrimination power, motivating its inclusion
 as one of the inputs for the MVA.
@@
 In our LO simulation the $p_T^{hh}$ distribution is generated
-by the parton shower, and improved theoretical
+by the parton shower, an improved theoretical
 description would require
-either the matching with higher-multiplicity
-matrix elements~\cite{Maierhofer:2013sha} or
-the full NLO calculation~\cite{Frederix:2014hta},
-%
-Nevertheless, as we will show,
-the MVA shows only limited sensitivity to this variable, so its
-modelling is not crucial in this specific application.
+merging higher-multiplicity
+matrix elements~\cite{Maierhofer:2013sha} or matching to
+the NLO calculation~\cite{Frederix:2014hta},
+%
 
@@
 
-We shall now investigate the discrimination power provided by jet substructure
+We shall now investigate the discrimination power
+provided by jet substructure
 quantities.
@@
     From top to bottom and from left to right we show  the
-    $k_t$ splitting scale, the energy correlation ratio $C_2^{(\beta)}$
+    $k_t$ splitting scale $\sqrt{d_{12}}$,
+    the energy correlation ratio $C_2^{(\beta)}$
     and the  subjettiness ratio $\tau_{21}$ for the leading
@@
 From Fig.~\ref{fig:mva_substructure_1}
-we can observe how for these substructure variables the shapes of the signal
+we observe how for these substructure variables the shapes of the signal
 and background distributions reflect
-the inherent differences in the internal structure of jets
-between QCD jets and jets originating from the Higgs decays.
+the inherent differences in the internal structure of
+QCD jets and jets originating from Higgs decays.
 %
@@
 ECF ratio $C_2^{(\beta)}$ is concentrated at small values
-for signal but is much broader for background events.
+for signal and is much broader for background events.
 %
@@
 %
-Therefore, while we do not explicitly have cuts in the substructure
-variables, their discrimination power between signal and
-background events is the motivation to include them
-as input to the MVA, as discussed in Sect.~\ref{sec:mva}.
 
@@
 and background processes are
-modified in the presence of pile-up (PU).
+modified in the presence of pile-up.
 %
 To study the impact of PU,
-Minimum Bias (MB) events,
-including Multiple Parton Interactions (MPI), have been generated
+Minimum Bias events have been generated
 with {\tt Pythia8}, and then
@@
 one with a mean number of
-PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another
+PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$,
+and another
 with $\la n_{\rm PU}\ra=150$.
@@
 %
-These distributions are plotted after
+These distributions are plotted
+after
 $b$-tagging, that is,
@@
 %
-In the case of the $p_T^{h1}$ distribution, the differences between the selection
+In the case of the $p_T^{h_1}$ distribution, the differences between the selection
 criteria for the resolved
@@
 as validated for the purposes of this study, although
-further optimisation should be possible.
+further optimisation should still be possible.
 
@@
   \caption{\small
-    Comparison of the transverse momentum $p_T^h$ of the leading
+    Same as Fig.~\ref{fig:m_H_PU} for
+   the transverse momentum $p_T^h$ of the leading
     Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
     of the di-Higgs system (lower plots) in the resolved
-    (left) and boosted (right) categories,
-    without PU and with $\la n_{PU}\ra=80$ subtracted with {\tt SoftKiller}.
+    (left) and boosted (right) categories.
 }
@@
   \caption{\small
-     Comparison of the substructure variables $D_2^{(\beta)}$ (left)
+    Same as Fig.~\ref{fig:m_H_PU} for the
+    substructure variables $D_2^{(\beta)}$ (left)
      and $\tau_{21}$ (right)
-     for the leading Higgs candidate in the boosted category,
-   without PU and with $\la n_{\rm PU}\ra=80$ subtracted with {\tt SoftKiller}.
+     for the leading Higgs candidates in the boosted category.
 }
@@
      the 2--to--1 subjettiness ratio $\tau_{21}$, and 
-     the $k_T$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}).
+     the $k_T$ splitting scale $\sqrt{d_{12}}$.
      %
@@
       qualitative differences between signal
-      and background distributions are maintained even in the presence of PU.
+      and background distributions are maintained  in the presence of PU.
       %
@@
   \begin{center}
+      \includegraphics[width=0.49\textwidth]{plots/pt_h0_res_comp_back.pdf}
    \includegraphics[width=0.49\textwidth]{plots/m_h0_res_comp_back.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/pt_h0_res_comp_back.pdf}
      \caption{\small
-       Same as Fig.~\ref{fig:signal-vs-back-boosted} for the resolved category,
-       this time without the jet substructure variables.
+       Same as Fig.~\ref{fig:signal-vs-back-boosted} for the resolved category.
 }

### 2015-12-15 paper/sec-intro.tex
working on the text

@@
 %
-Higgs pair production is directly sensitive to the
-Higgs trilinear coupling $\lambda$~\cite{baglio} and 
+Higgs pair production~\cite{baglio} is directly sensitive to the
+Higgs trilinear coupling $\lambda$ and 
 provides crucial
@@
 Higgs bosons at the LHC is 
-gluon fusion (see Refs.~\cite{baglio,Frederix:2014hta} and
+gluon fusion (see~\cite{baglio,Frederix:2014hta} and
 references therein).
@@
 
-In addition to the gluon-fusion production mode, Higgs pairs
+In addition to the gluon-fusion channel, Higgs pairs
 can also be produced in the vector-boson fusion
@@
 While the SM production rates for Higgs
-pairs are small, they can be substantially
+pairs are small, they are substantially
 enhanced in a variety of BSM scenarios.
@@
 enhancement of the signal yield
-from the large branching fraction of Higgs bosons into bottom-anti-bottom
+from the large branching fraction of Higgs bosons into
+$b\bar{b}$
 pairs, ${\rm BR}\lp H\to b\bar{b}\rp\simeq 0.57$~\cite{Dittmaier:2012vm}.
@@
 $\mathcal{L}=3$ ab$^{-1}$,
-a signal significance of around $S/\sqrt{B}\sim 2.0$ could be obtained.
+a signal significance of around $S/\sqrt{B}\sim 2.0$ can be obtained.
 %
-While irreducible backgrounds, such as $4b$ and
-$t\bar{t}$, are included in these analysis, the contribution
-from reducible processes, such as $bbjj$ and
-$jjjj$, which can contribute to the signal yield when 
-light jets are mis-identified as $b$-jets,
-are not accounted for.
+In these analysis, irreducible backgrounds such as $4b$ and
+$t\bar{t}$ are included, however the
+reducible components, in particular as $bbjj$ and
+$jjjj$, are neglected.
 %
-As we will show, due to both
+These can contribute to the signal yield when 
+light and charm jets are mis-identified as $b$-jets.
+%
+Indeed, due to both
 selection effects and $b$-quark radiation in the
@@
 In Sect.~\ref{sec:conclusions} we conclude and outline
-future studies to extend our results to estimate the accuracy
-in the determination of trilinear coupling $\lambda$, as well as
+future studies to estimate the accuracy
+in the determination of the trilinear coupling $\lambda$ and
 to provide

### 2015-12-15 paper/sec-mcsamples.tex
working on the text

@@
 For the input parton distribution functions (PDFs) we 
-adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
+adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
 $\alpha_s(m_Z^2)=0.118$,
@@
 In the SM, the Higgs trilinear coupling
-is given by $\lambda=m_h^2/2v^2$, with $m_h=125$ GeV
-the Higgs boson mass and $v\simeq 246$ GeV the Higgs vacuum expectation
-value (vev).
+is given by $\lambda=m_h^2/2v^2$, with
+$v\simeq 246$ GeV the Higgs vacuum expectation
+value.
 %
@@
     %
-    Higher order corrections~\cite{deFlorian:2013jea,Frederix:2014hta}
+    Higher-order corrections~\cite{deFlorian:2013jea,Frederix:2014hta}
     are dominated by gluon radiation
@@
 in Table~\ref{tab:samples}.
-%
+
 Parton level signal events are then showered with the {\tt Pythia8} Monte
@@
 of the underlying event (UE), multiple parton
-interactions (MPI), and pile-up (PU), by means
+interactions (MPI), and PU, by means
 of the Monash 2013 tune~\cite{Skands:2014pea},
@@
 
-\subsection{Backgrounds: QCD multijet and $t\bar{t}$ production}
+\subsection{Backgrounds}
 
 Background samples are generated at leading order
-with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, {\tt v2.1.1}.
+with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
 %
@@
 The $K$-factors that we use to rescale
-the signal background samples are summarised in
+the signal and background samples are summarised in
 Table~\ref{tab:samples}.
@@
   %
-We also provide the corresponding inclusive $K$-factor
-  which is applied to reproduce the known
+  Also provided are the inclusive $K$-factors
+  which are applied to reproduce the known
   higher-order results. \label{tab:samples}
@@
 %
-Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
+Each final-state particle in the hard process must have $p_T \ge 20$ GeV, and be located
 in the central  rapidity
@@
 At the matrix-element level
-all final state particles must also be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
+all final-state particles must also be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
 %
@@
 To account for the finite angular resolution of the calorimeter,
-the $\eta$-$\phi$ plane is divided into regions of
+the $\lp \eta,\phi\rp$ plane is divided into regions of
 $\Delta \eta \times \Delta \phi=0.1$, and each final state particle

### 2015-12-15 paper/paperscripts/plotHist_m_H1_bst_comp.py

@@ -10,7 +10,7 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "m_H_bst_comp"
+outfile = "m_H1_bst_comp"
 
 linestyles = [ 'solid', 'dashed']
 
@@ -54,7 +54,7 @@ ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
 ax.set_xlim([90,170])
-ax.set_ylim([1e-3,0.1])
+ax.set_ylim([1e-3,0.2])
 
 for idat in xrange(0,len(datafiles)):
 

### 2015-12-15 paper/sec-mva.tex
more edits

@@
 by combining the three event topologies,
-we obtain a signal significance of $S/\sqrt{B}\simeq 1.7 (3.5)$
+we obtain a signal significance of $S/\sqrt{B}\simeq 1.8~(3.5)$
 with all backgrounds (only QCD $4b$) taken into account.
@@
  can be enhanced when the cut-based analysis
- is complemented by a multivariate analysis (MVA).
+ is complemented by a multivariate analysis.
 %
@@
 %
-In particular, the classification of events into signal and
-background processes by means of MVAs is a
-commonly applied strategy in LHC
+In particular, the classification of events into
+signal and
+background processes by means of MVAs is
+commonly used in LHC
 applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
@@
 %
-Finally we assess the robustness of the MVA strategy in
+Then we assess the robustness of the MVA strategy in
 the case of significant contamination from pileup.
@@
 %
-This family of ANNs are also known as {\it deep} neural networks, due to their multi-layered architecture.
+This family of ANNs are also known as {\it deep neural networks},
+due to their multi-layered architecture.
 %
@@
 where $y_i^\prime$ represents the true classification of the event $i$, {\it i.e},
-$y^\prime = 1$ for signal and $y^\prime = 0$ for background events.
+$y^\prime_i = 1$ for signal and $y^\prime_i = 0$ for background events.
 %
@@
  The ANN is trained both on the signal and background MC events,
- so it is crucial to ensure that the input MC sample is large enough
+ so it is important to ensure that the input MC sample is large enough
  to avoid contamination from MC statistical fluctuations.
@@
 
- In order to avoid over-fitting,
+ In addition,
+ in order to avoid the possibility of over-fitting,
  we have used a cross-validation stopping
@@
  %
- This indicates the point where we are training on the statistical fluctuations
- of the input MC samples, rather than in the underlying (smooth) physical
- distributions.
+ This indicates the point where
+the ANN begins to train upon  statistical fluctuations
+in the input MC samples, rather than learning
+the underlying (smooth) physical  distributions.
 
@@
 
- To ensure that we include the variables with the most discriminating power,
- we need to train
- the MVA on a broad array of kinematic variables.
-%
 In this work we use different sets of
@@
 %
-In particular, in the case of large-$R$ jets (for the boosted
-and intermediate categories), we are fully exploiting the available information 
-on jet substructure.
-
+In the case of large-$R$ jets, we  exploit the available
+information  on jet substructure.
+%
 For the three categories, boosted, intermediate and resolved,

### 2015-12-15 paper/sec-results.tex
more edits

@@
 
+\clearpage
 \section{Results of the cut-based analysis}
@@
 is affected if only the $4b$ component of the
-QCD multi-jet background is taken into account (leaving out the 
-the $2b2j$ and $4j$ components).
+QCD multi-jet background is taken into account.
 %
-First we present the results in an environment with no pile-up,
-followed by the corresponding analysis including PU effects.
+Here we present the results in an environment without pile-up,
+followed in the next section by the corresponding analysis including PU.
 
@@
 
-We now compare the cross-sections for
+Here we compare the cross-sections for
 signal and background events at various
@@
 background is considered.
-
+%
 In Table~\ref{tab:cutflowdetails}
@@
 \hline
-{\bf  C1b} & \multicolumn{3}{c|}{+$p_T$ cuts} \\
-{\bf C1c} & \multicolumn{3}{c|}{+rapidity cuts}\\
+{\bf  C1b} & \multicolumn{3}{c|}{+$p_T$ cuts and rapidity cuts} \\
 \hline
- {\bf C1d} & +$N_{\rm MDT}\ge 2$ & +$N_{\rm jets}^{R10}=1$ with MDT  &
+ {\bf C1c} & +$N_{\rm MDT}\ge 2$ & +$N_{\rm jets}^{R10}=1$ with MDT  &
  +Higgs reconstruction \\
  \hline
-{\bf C1e} & \multicolumn{3}{c|}{ +$m_H$ window cut} \\
+{\bf C1d} & \multicolumn{3}{c|}{ +$m_H$ window cut} \\
 \hline
@@
       $p_T \ge 200$ GeV for large-$R$ jets and
-      $p_T \ge 50$ GeV for small-$R$ jets.
-    \item {\bf C1c}: jets are required to satisfy their associated
+      $p_T \ge 50$ GeV for small-$R$ jets, and well as
+      satisfy the associated
       rapidity acceptance constraints.
-    \item {\bf C1d}: the two leading large-$R$ jets must
+    \item {\bf C1c}: the two leading large-$R$ jets must
       be mass-drop tagged in the boosted category.
@@
       %
-    \item {\bf C1e}: after the two Higgs candidates  have been reconstructed,
+    \item {\bf C1d}: after the two Higgs candidates  have been reconstructed,
       their invariant masses are required to lie within a window around $m_H$,
@@
     in Sect.~\ref{sec:mva}.
-    %
+
     In Table~\ref{tab:cutflow_noPU_1} we collect
@@
     %
-
 In Table~\ref{tab:cutflow_noPU_1} we also  provide the signal over
@@
       We find that after $b$-tagging, the  $2b2j$ component is
-      of the same order of magnitude as the $4b$ component.
+      of the same order of magnitude as the $4b$ component in all categories.
       %
       This implies that the signal significance at the end of the cut-based
-      analysis is degraded by about a factor of two due to the contribution
+      analysis is degraded due to the contribution
       of light and charm jets being mis-identified as $b$-jets.
@@
     \input{table_noPU_3.tex}
-    \caption{\small The cross-sections, in femtobarns,
-      for the signal and the various background
+    \caption{\small The cross-sections (fb)
+      for the signal and the background
       processes at different steps of the
@@
       the total background or just the $4b$ component. Signal
-      significances are calculated for a total integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
+      significances are calculated for an
+      integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
       %
-      The different steps of the cut-flow are summarized
+      The different steps of the cut-flow are described
       in Table~\ref{tab:cutflowdetails}.
@@
 $S/\sqrt{B}=1.2$ and a signal over background
-ratio of $S/B=1.4\%$.
+ratio of $S/B=0.14\%$.
 %
@@
 %
-We emphasize that such signal
+Such signal
 significances could have been enhanced
@@
 in order that such optimsation may be performed by the MVA.
-%
-Both the intermediate and resolved categories benefit from higher signal yields,
-specially in the resolved category, but this enhancement is compensated for by the
+
+The resolved category benefits from higher signal yields,
+but this enhancement is compensated for by the
 corresponding
@@
 %
-In both categories
+In both resolved and intermediate categories
 the signal significance is similar to that of the boosted category,
@@
 %
-An important additional
+An further
 drawback of the resolved case is
 that $S/B$
-is one order to magnitude smaller.
+is one order to magnitude smaller than in the boosted case.
 %
 Combining the pre-MVA results
-from the
-of the boosted, intermediate and resolved categories,
+from the boosted, intermediate and resolved categories,
 we obtain an overall
@@
 quantify
-the impact of light and charm jet mistags. 
+the impact of light and charm jet mis-identification. 
 %
@@
 
- From the results of Table~\ref{tab:cutflow_noPU_1}, we observe
+ From our results in Table~\ref{tab:cutflow_noPU_1}, we observe
  that the signal significance for the boosted, intermediate,
@@
  %
- At this level, part of the improvement that we found as compared
- to~\cite{deLima:2014dta,Wardrope:2014kya} arises
+ Part of the improvement 
+with respect to~\cite{deLima:2014dta,Wardrope:2014kya} arises
  from the combination of the three exclusive event topologies,
@@
 
- It is interesting to compare in each category the interplay
+ Also from Table~\ref{tab:cutflow_noPU_1}, we
+ can compare the interplay
  between the reducible and irreducible components of the
@@
  In all cases, the $4b$ and $2b2j$ have comparable
- magnitudes, taking into account the size that the higher-order QCD
- effects could induce in
- the corresponding normalizations.
+ magnitudes within the uncertainties from missing higher-order
+ corrections.
  %
@@
     The two components possess a rather similar shape
-    for the two distributions, albeit with some interesting
-    differences For instance, in the boosted
+    for the two distributions, albeit with some 
+    differences.
+  %
+    For instance, in the boosted
     category the $4b$ component is harder for the
@@
 %
-These fluctuations illustrate the challenge
-of an accurate modelling of the effects
-of $b$-jet mis-identification in QCD processes, which requires
-very large MC samples.
 
@@
 
-% The reason why the  $2b2j$ process
-% cannot be neglected as compared to the $4b$ component
-% is the following.
-%
-In the boosted category 
+In the resolved category 
 the cross-section  before
@@
 \ee
-with $n^{\rm (b-jet)}_j$ being the fraction of events satisfying all the selection cuts,
+with $n^{\rm (b-jet)}_j$ being the fraction of events satisfying all the selection
+requirements,
 where $j$ jets out of the leading four jets of the event
@@
   This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
-  in the resolved category before $b$-tagging, shown
-  in Table~\ref{tab:cutflow_noPU_1}.
+  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
     %

### 2015-12-15 paper/sec-analysis.tex
more edits
Done with corrections

@@
 \end{itemize}
-
-We have
-also explored the possible improvements
-in the analysis from the use
-of variable-$R$ jets~\cite{Krohn:2009zg}, finding
-a similar performance as in the case of fixed-$R$ jets.
-%
-This is explained by the fact that
-variable-$R$ jets are more suitable when
-the degree of boost of the final state being reconstructed can
-differ substantially~\cite{Cacciari:2008gd},
-such as in heavy resonance
-searches~\cite{Aad:2015fna},
-where the degree of boost of the final state
-is {\it a priori} unknown.
 
@@
 distributions peak at $p_T \le 50$ GeV, with the signal distribution
-eventually becoming dominant at large $p_T$.
+falling off less steeply at large $p_T$.
 %
@@
         %
-        We indicate the shift of the invariant mass peak $\la m_h^{\rm reco}\ra$ as compared
+        We indicate the shift of the invariant
+        mass peak $\la m_h^{\rm reco}\ra$ as compared
         to the nominal Higgs mass $m_h=125$ GeV, as well as the width

### 2015-12-15 paper/sec-mcsamples.tex
Done with corrections

@@
 %
-We account for the most relevant background
+We account for all relevant background
 processes that can mimic the
@@
 multi-jet samples
-using {\tt MadGraph5\_aMC@NLO}, and
-benchmarked them with the results for the same processes reported in
+using {\tt MadGraph5\_aMC@NLO},
+benchmarked with the results for the same processes reported in
 Ref.~\cite{Alwall:2014hca}.
 %
-For comparison with the latter numbers, 
-we require that all samples include four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, where the leading jet must have $p_T \ge 100$ GeV, and with all jets within an acceptance of $|\eta| \le 2.5 $.
-%
-Using these common settings,
-we find good agreement,
-within the scale uncertainties, between the
-{\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
-backgrounds.
+Using common settings, we find
+agreement, within scale uncertainties,  between the
+{\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of
+the multi-jet backgrounds.
 

### 2015-12-21 paper/sec-analysis.tex
push textual changes

@@
 %
-Considering first of all the boosted category,
+Considering the boosted category initially,
 in Fig.~\ref{fig:signal-vs-back-boosted} we compare
@@
       This is especially noticeable for the substructure variables, which
-      exhibit a similar discrimination power both with and without
+      exhibit a similar discriminatory power both with and without
       PU.
@@
      %
-     Also in this
-     case the PU-subtracted background distributions appear reasonably close
+%     Also in this
+%     case
+Again, the PU-subtracted background distributions appear reasonably close
      to their no PU counterparts.
@@
 To complete this discussion, it is illustrative to determine
-which is the mass resolution obtained for the
-reconstructed Higgs candidates in various cases.
+the mass resolution obtained for the
+reconstructed Higgs candidates in the various cases.
 %
@@
 we indicate the shift of the invariant mass peak as compared
-to the nominal Higgs mass, $\delta m_h$, as well as the
-corresponding width of the distribution, $\sigma_{m_h}$,
+to the nominal Higgs mass, $\delta m_h$, %as well as the
+and the corresponding width of the distribution, $\sigma_{m_h}$,
 obtained from fitting a Gaussian to the mass distributions

### 2015-12-21 paper/sec-conclusions.tex
Done with corrections
push textual changes

@@
 We take into account 
-the most relevant backgrounds, in particular
+all relevant backgrounds, in particular
 the irreducible $4b$
@@
 %
-We therefore plan to study the constraints
+Therefore, we plan to study the constraints
 on the coefficients of these effective

### 2015-12-21 paper/sec-mva.tex
Done with corrections
push textual changes

@@
 we obtain a signal significance of $S/\sqrt{B}\simeq 1.8~(3.5)$
-with all backgrounds (only QCD $4b$) taken into account.
+with all backgrounds (only QCD $4b$) considered.
 %
-We now show how this signal significance
+This section describes how this signal significance
  can be enhanced when the cut-based analysis
@@
 %
- Multivariate techniques are by now a mature tool
+ Multivariate techniques are a mature tool
  in high-energy physics data analysis, opening
- new avenues for improving the performance
+ new avenues to improve the performance
 of many measurements and searches at high-energy colliders.
@@
 
-In this section, first of all we present the specific MVA that we use,
+In this section, first we present the specific MVA that we use,
 based on feed-forward multi-layer neural networks.
 %
-We then introduce the input variables that are
+Then we introduce the input variables that are
 used in the MVA, including the jet substructure
@@
 %
-The output of the trained ANNs also allows for the identification, in a fully automated way,
+The output of the trained ANNs also allows for the identification,
+in a fully automated way,
 of the most relevant variables in the discrimination between 
@@
 In Fig.~\ref{fig:nnarch} we show an illustrative
-example of a ANN used in this work, corresponding 
+example of an ANN used in this work, corresponding 
 to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).
@@
 the signal over background ratio raising from
-$0.12\%$ and $0.03\%$ to 6\% and 1\$, respectively.
+$0.12\%$ and $0.03\%$ to 6\% and 1\%, respectively.
 %
@@
 resilient against PU contamination,
-as opposed to the resolved and boosted selections.
+in contrast to the resolved and boosted selections.
 
@@
 In Table~\ref{table:cutflowMVA_fakes} we compare,
-after the MVA is applied,
-the 
-number of background events  expected at the HL-LHC.
+number of background events  expected at the HL-LHC, after the MVA is applied.
 Both the total number, $N_{\rm ev}^{\rm tot}$,

### 2015-12-21 paper/sec-results.tex
Done with corrections
push textual changes

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
 \section{Results of the cut-based analysis}
@@
 %
-Here we present the results in an environment without pile-up,
-followed in the next section by the corresponding analysis including PU.
+%Here we present the results in an environment without pile-up,
+%followed in the next section by the corresponding analysis including PU.
+This section presents the results in an environment without significant pile-up; the following one details those obtained includin PU.
 
@@
     the values for signal and background cross-sections
-    for different steps of the cut-flow.
+    at different steps of the cut-flow.
     %
@@
  neglected, the inclusion of the
- $2b2j$ component is essential to robustly assess the feasibility
- of measuring Higgs pairs in this final state,
+ $2b2j$ component is essential to assess the feasibility
+ of measuring Higgs pairs in this final state robustly,
  especially
@@
 %
-To first approximation, and neglecting the contribution from
+To first approximation, neglecting the contribution from
 charm mis-identification,
@@
     A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
-    that, on the other hand, the $4j$ component of the background can typically
-    be safely neglected.
+    that, on the other hand, the $4j$ component of the background is negligible and be neglected. % can typically
+%    be safely neglected.
 

### 2015-12-23 paper/sec-analysis.tex
more work on paper

@@
 
+In addition, trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to all large-$R$ jets in the event.
+The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$~\cite{Ellis:1993tq} 
+subjets with $R_{\textrm{sub}} = 0.2$.
+Subjets with tranverse momentum less than 5\% of the tranverse momentum of the large-$R$ jet are removed.
+The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass, which is particularly susceptible
+to soft, wide-angle contaminations. This is illustrated in Fig.~\ref{fig:m_H_PU_MitiCompare}. The mass distributions for jets to which no trimming
+is applied (red) peaks at around 160~GeV (after PU subtraction with {\tt SoftKiller}). If trimming is applied in addition to {\tt SoftKiller}, 
+the distributions (green) peak close to the Higgs mass of 125~GeV. For comparison, the distributions for trimmed jets are shown for events 
+in which {\tt SoftKiller} is not applied (blue).
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+  \begin{center}
+      \includegraphics[width=0.49\textwidth]{plots/histo_m_H0_boost.pdf}
+      \includegraphics[width=0.49\textwidth]{plots/histo_m_H1_boost.pdf}
+  \caption{\small
+    Comparison of the invariant mass distributions of the leading (left)
+    and subleading (right) Higgs candidates in the boosted category.
+    The distributions are shown for the cases without PU, and with
+    PU, $\la n_{PU}\ra=80$, and applying either only {\tt SoftKiller},
+    or only trimming, or both {\tt SoftKiller} and trimming.
+}
+\label{fig:m_H_PU_MitiCompare}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-23 paper/sec-conclusions.tex
more work on paper

@@
 $\mathcal{L}=300$ fb$^{-1}$.
+
+Efficiently triggering on the $4b$ final state provides a large experimental challenge.
+%
+In order to reduce the rate from background QCD processes sufficiently,
+to access these $p_T$ regimes, (multi-)jet triggers
+using $b$-quark tagging information online for one or more jets are likely to be important.
+%
+The additional rejection provided by this could enable events to be selected efficiently, with four jets down to $p_T=45$ GeV in the resolved category,
+and boosted Higgs decays in large-$R$ jets down to jet transverse momenta of
+$p_T=200$ GeV.
 

### 2015-12-23 paper/paperscripts/plotHist_C2_h0_bst_comp.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "C2_h0_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_C2_fj1_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_C2_fj1_boost_C2.dat")
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK")
+
+# Axis labels
+xLabel = r"Energy Correlation Ratio $C_2^{(\beta)}$ in leading Higgs candidate"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,1])
+ax.set_ylim([0,2.5])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-12-23 paper/paperscripts/plotHist_m_H1_int_comp.py

@@ -1,0 +1,130 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_H1_int_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H1_inter_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_H1_inter_C2.dat")
+
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK")
+
+# Axis labels
+xLabel = "Sub-Leading Higgs Candidate Invariant Mass (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([90,170])
+ax.set_ylim([1e-3,0.2])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-12-23 paper/sec-analysis.tex
updated plots with trimming

--- 2015-12-21 paper/sec-analysis.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-  \begin{center}
-  \includegraphics[width=0.63\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
-    \caption{\small
-    The invariant mass distributions of Higgs candidates in signal
-events in the resolved category, comparing the results without PU,
-with PU $\la n_{\rm PU}\ra=80$. The distribution is then compared with and without SK subtraction.
-}
-\label{fig:PUvalidation}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
+In addition, trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to all large-$R$ jets in the event.
+%
+The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$~\cite{Ellis:1993tq} 
+subjets with $R_{\textrm{sub}} = 0.2$.
+Subjets with transverse momentum less than 5\% of the transverse momentum of the large-$R$ jet are removed.
+%
+The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass in the boosted category,
+which is particularly susceptible
+to soft, wide-angle contaminations.
+%
+No trimming is applied to the small-$R$ jets.
 
@@
 we compare representative kinematic distributions
-without PU, with PU, and with PU after SK subtraction.
+without PU, with PU, and with PU after the combined
+application of {\tt SoftKiller} and trimming (SK+Trim).
 %
 In Fig.~\ref{fig:PUvalidation} we show the
-invariant mass distributions of Higgs candidates for signal
-events in the resolved category.
+invariant mass distributions of the
+Higgs candidates for signal
+events in the resolved and boosted categories.
 %
@@
 %
-
-In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
-of the leading and subleading Higgs candidates,
-this time corresponding
-to the boosted category.
-%
-These distributions are plotted
-after
-$b$-tagging, that is,
-before they are used as input to the MVA.
-%
-The residual effects of PU
-after the {\tt SoftKiller} subtraction are smaller
-in the boosted selection as compared to the resolved case,
-with the position of the Higgs mass peak being essentially
-unchanged, and only a moderate broadening of the
-mass distribution.
-%
+For the boosted category, we find that
+the mass distributions for jets to which no trimming
+is applied peaks at around 160~GeV, even
+after PU subtraction with {\tt SoftKiller}.
+%
+When trimming is applied in addition to {\tt SoftKiller}, 
+the distribution peaks close to the nominal Higgs mass.
 
@@
   \begin{center}
-      \includegraphics[width=0.49\textwidth]{plots/m_H0_bst_comp.pdf}
-      \includegraphics[width=0.49\textwidth]{plots/m_H1_bst_comp.pdf}
+    \includegraphics[width=0.49\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
+    \includegraphics[width=0.49\textwidth]{plots/m_htot_bst_signal_PUnoTrim.pdf}
     \caption{\small
-    Comparison of the invariant mass distributions of the leading (left)
-    and subleading (right) Higgs candidates
-    in the boosted category,
-    both without PU and with
-    PU, $\la n_{PU}\ra=80$, subtracted by {\tt SoftKiller}.
-}
-\label{fig:m_H_PU}
+    The invariant mass distributions of Higgs candidates in signal
+    events in the resolved (left) and boosted
+    (right) categories.
+    %
+    In the resolved category,
+    we compare  the results without PU
+    with those with PU $\la n_{\rm PU}\ra=80$,
+    with and without SK subtraction.
+    %
+    In the boosted case, the comparison is between no PU,
+    PU with only SK subtraction,
+    and PU with both SK and trimming.
+}
+\label{fig:PUvalidation}
 \end{center}
@@
   \caption{\small
-    Same as Fig.~\ref{fig:m_H_PU} for
-   the transverse momentum $p_T^h$ of the leading
+   The
+   transverse momentum $p_T^h$ of the leading
     Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
@@
     (left) and boosted (right) categories.
+    %
+    We compare the results without PU with those with PU,
+    for $\la n_{\rm PU}\ra=80$ and SK+Trim subtraction,
+    as explained in the text.
 }
@@
 $\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
-of energy correlation functions, $D_2^{(\beta)}$,
-Eq.~(\ref{eq:d2}), for the leading Higgs candidate.
+of energy correlation functions, $C_2^{(\beta)}$,
+Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
 %
 Comparing the signal distributions in the cases without PU and
-with PU subtracted with SK, we observe that both substructure variables
+with PU subtracted with SK, we observe that
+the shapes of both substructure variables
 are reasonably robust in a environment including PU.
 %
-The ratio of energy correlation functions $D_2^{(\beta)}$ 
-was indeed explicitly constructed~\cite{Larkoski:2013eya}
-to be robust against PU contamination.
-%
 
@@
   \begin{center}
+    \includegraphics[width=0.49\textwidth]{plots/tau21_h0_bst_comp.pdf}
   \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp.pdf}
-  \includegraphics[width=0.49\textwidth]{plots/tau21_h0_bst_comp.pdf}
     \caption{\small
-    Same as Fig.~\ref{fig:m_H_PU} for the
-    substructure variables $D_2^{(\beta)}$ (left)
-     and $\tau_{21}$ (right)
+    Same as Fig.~\ref{fig:mHH_PU} for the
+    substructure variables $\tau_{21}$  (left)
+     and  $C_2^{(\beta)}$ (right)
      for the leading Higgs candidates in the boosted category.
@@
     \includegraphics[width=0.49\textwidth]{plots/pt_h0_bst_comp_back.pdf}
+    \includegraphics[width=0.49\textwidth]{plots/pt_leadSJ_fj1_bst_comp_back.pdf}
    \includegraphics[width=0.49\textwidth]{plots/tau21_h1_bst_comp_back.pdf}
    \includegraphics[width=0.49\textwidth]{plots/split12_h0_bst_comp_back.pdf}
-   \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
     \caption{\small
-     Comparison of kinematic distributions, in
+      Comparison of kinematic distributions for the leading
+      Higgs candidate, in
      the boosted category, for signal and background events
-    in the case of PU subtracted with SK:
-     the transverse momentum  $p_T$ and
-     and the substructure variables $\tau_{21}$ and $\sqrt{d_{12}}$
-     for the leading Higgs candidate, and the invariant
-     mass of the di-Higgs system $m_{hh}$.
-     %
+    in the case of PU subtracted with SK+Trim:
+    its transverse momentum  $p_T$,
+    the $p_T$ of its leading AKT03 subjet,
+    and the substructure variables $\tau_{21}$ and $\sqrt{d_{12}}$.
   }
@@
      %
-%     Also in this
-%     case
 Again, the PU-subtracted background distributions appear reasonably close
@@
 
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \begin{table}[h]
@@
               \hline
-        \multirow{2}{*}{no PU}  & leading Higgs  &  +2 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
-          & subleading Higgs   & +1 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
-        \hline
-              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  --   & --   \\
-          & subleading Higgs   & --  &  -- \\
+        \multirow{2}{*}{no PU}  & leading Higgs  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
+          & subleading Higgs   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
+        \hline
+              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK+Trim}  & leading Higgs  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
+          & subleading Higgs   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
         \hline
@@
         We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
-        but without subtraction, and the same with SK subtraction.
+        but without subtraction (only for resolved),
+        and the same with SK(+Trim) subtraction.
         %
@@
     \end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-23 paper/paperscripts/plotHist_D2_h0_bst_comp.py

@@ -15,20 +15,20 @@ outfile = "D2_h0_bst_comp"
 linestyles = [ 'solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_noPU/diHiggs/histo_D2_fj1_boost_C2.dat")
-datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_D2_fj1_boost_C2.dat")
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_C2_fj1_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_C2_fj1_boost_C2.dat")
 
 # Plot labels
 plotnames.append("no PU")
-plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK")
+plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK+Trim")
 
 # Axis labels
-xLabel = r"Energy Correlation Ratio $D_2^{(\beta)}$ in leading Higgs candidate"
+xLabel = r"Energy Correlation Ratio $C_2^{(\beta)}$ in leading Higgs candidate"
 yLabel = "A. U."
 
 # Log axes
 xLog = False
-yLog = False
+yLog = True
 
 # Normalise histograms
 normalise = True
@@ -52,8 +52,8 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-ax.set_xlim([0,1])
-ax.set_ylim([0,2.5])
+ax.set_xlim([0,0.5])
+ax.set_ylim([0.03,50])
 
 for idat in xrange(0,len(datafiles)):
 

### 2015-12-23 paper/paperscripts/plotHist_mHH_bst_comp.py

@@ -20,7 +20,7 @@ datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_HH_boost_C2.dat")
 
 # Plot labels
 plotnames.append("no PU")
-plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK")
+plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK+Trim")
 
 # Axis labels
 xLabel = "di-Higgs Invariant Mass $m_{hh}$ (GeV)"

### 2015-12-23 paper/paperscripts/plotHist_m_h0_bst_comp_back.py

@@ -10,25 +10,25 @@ plotnames = []
 ############################## Settings ###############################
 
 # Output filename
-outfile = "m_h0_bst_comp_back"
+outfile = "pt_leadSJ_fj1_bst_comp_back"
 
 linestyles = [ 'solid', 'dashed','solid', 'dashed']
 
 # Datafiles
-datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_HH_boost_C1e.dat")
-datafiles.append("../plotdata/results_SK_PU80/background/histo_m_HH_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_pt_leadSJ_fj1_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/background/histo_pt_leadSJ_fj1_boost_C1e.dat")
 
 # Plot labels
 plotnames.append("Signal")
 plotnames.append("Background")
 
 # Axis labels
-xLabel = "Invariant di-Higgs mass $m_{hh}$ (GeV)"
+xLabel = "Leading AKT03 subjet $p_{T}$ for leading Higgs candidate (GeV)"
 yLabel = "a. u."
 
 # Log axes
 xLog = False
-yLog = False
+yLog = True
 
 # Normalise histograms
 normalise = True
@@ -52,12 +52,8 @@ if yLog == True:
 ax.set_ylabel(yLabel)
 ax.set_xlabel(xLabel)
 
-
-ax.set_xlim([400,600])
-ax.set_ylim([1e-3,0.017])
-
-
-
+ax.set_xlim([33,475])
+ax.set_ylim([2e-4,0.02])
 
 for idat in xrange(0,len(datafiles)):
 
@@ -125,7 +121,7 @@ for idat in xrange(0,len(datafiles)):
 
 
 plt.rcParams.update({'font.size': 14})
-fig.text(0.23,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK", fontsize=19)
+fig.text(0.18,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK+Trim", fontsize=19)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-23 paper/paperscripts/plotHist_ptH0_bst_comp.py

@@ -20,7 +20,7 @@ datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_pt_H0_boost_C2.dat")
 
 # Plot labels
 plotnames.append("no PU")
-plotnames.append(r"$\langle n_{PU}\rangle=80$ + SK")
+plotnames.append(r"$\langle n_{PU}\rangle=80$ + SK+Trim")
 
 # Axis labels
 xLabel = "Leading Higgs Candidate $p_{T}$ (GeV)"

### 2015-12-23 paper/paperscripts/plotHist_pt_h0_bst_comp_back.py

@@ -55,7 +55,7 @@ ax.set_xlabel(xLabel)
 
 
 ax.set_xlim([175,600])
-ax.set_ylim([1e-5,0.05])
+ax.set_ylim([1e-4,0.02])
 
 
 for idat in xrange(0,len(datafiles)):
@@ -124,7 +124,7 @@ for idat in xrange(0,len(datafiles)):
 
 
 plt.rcParams.update({'font.size': 14})
-fig.text(0.23,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK", fontsize=19)
+fig.text(0.18,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK+Trim", fontsize=19)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-23 paper/paperscripts/plotHist_tau12_h1_bst_comp_back.py

@@ -122,7 +122,7 @@ for idat in xrange(0,len(datafiles)):
 
 
 plt.rcParams.update({'font.size': 14})
-fig.text(0.23,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK", fontsize=19)
+fig.text(0.18,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK+Trim", fontsize=19)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-23 paper/sec-mva.tex
updated plots

@@
 The overall combined significance is thus $S\sqrt{B}\simeq 8$,
-well above the threshold for discovery. However such a significance
-is unrealistic given that the HL-LHC will be a high-PU environment,
+well above the threshold for discovery.
+%
+However, given that the HL-LHC will be a high-PU environment,
 which will affect the description of the various
-kinematical distributions used as input to the MVA.
-%
-Therefore we shall now quantify the robustness of the
-results summarized Table~\ref{fig:sb_mva}
+kinematical distributions used as input to the MVA,
+it is essential to quantify the robustness of these
+results
 in a realistic environment including the effects of PU.
@@
         \hline
-     \multicolumn{6}{|c|}{$\la n_{\rm PU}\ra=80$+SK} \\
+     \multicolumn{6}{|c|}{$\la n_{\rm PU}\ra=80$+SK+Trim} \\
      \hline
@@
     \hline
-    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 360   &  $1.4\cdot 10^6$ & 0.31   &
-     $3\cdot 10^{-4}$  \\
-    &  $y_{\rm cut}=0.82$ &  250 & 7300  & 2.9    & 0.034  \\
+    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1000   &  $4.5\cdot 10^5$ & 1.5   & $2\cdot 10^{-3}$  \\
+    &  $y_{\rm cut}=0.7$ &  780  & $4.5\cdot 10^4$  & 3.7    & 0.02  \\
     \hline
     \hline
-    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  150  & $9\cdot 10^5$    & 0.15    &
-     $2\cdot 10^{-4}$ \\
-    &  $y_{\rm cut}=0.80$ & 50 & 2600  &  1.1   & 0.02 \\
+    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  630  & $8.2\cdot 10^5$    & 0.7    &
+     $8\cdot 10^{-4}$ \\
+    &  $y_{\rm cut}=0.7$ & 380 & $8.5\cdot 10^3$  &  4.1   & 0.04 \\
     \hline
     \hline
-    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  1100  & $8.5\cdot 10^6$
-    & 0.25    &  $1.3\cdot 10^{-4}$  \\
-    &  $y_{\rm cut}=0.65$ & 430  & $3\cdot 10^4$  &  2.5   & 0.015  \\
+    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  4500  & $2.7\cdot 10^7$
+    & 0.9    &  $2\cdot 10^{-4}$  \\
+    &  $y_{\rm cut}=0.5$ & 2000  & $2.1\cdot 10^5$  &  4.6   & 0.01  \\
     \hline
@@
   \caption{\small Same as Table~\ref{table:cutflowMVA}, now for the case
-    of PU+SK, with $\la n_{\rm PU}\ra=80$.
+    of PU+SK+Trim, with $\la n_{\rm PU}\ra=80$.
         \label{table:cutflowMVA_PU}
@@
 case of events with PU, for
-$\la n_{\rm PU}\ra=80$ using
-{\tt SoftKiller} for PU subtraction.
+$\la n_{\rm PU}\ra=80$ with SK+Trim.
 }
@@
 case of events with PU, for
-$\la n_{\rm PU}\ra=80$
-using
-{\tt SoftKiller} for PU subtraction.
+$\la n_{\rm PU}\ra=80$ with SK+Trim.
 }
@@
     \multirow{2}{*}{Boosted} &  no PU  & $2.2\cdot 10^4$  & $1.5\cdot 10^4$     & 
-      5.4 &  6.5 & 0.034 & 0.05 \\
-    & PU+SK & 7300  &  500  &  2.9  & 3.6 &  0.034 & 0.04 \\
+      5.4 &  6.5 & 0.03 & 0.05 \\
+    & PU+SK &  $4.5\cdot 10^4$ &  $1.7\cdot 10^4$    &  3.7  & 5.9 &  0.02 & 0.04 \\
     \hline
     \hline
-    \multirow{2}{*}{Intermediate} &  no PU   & 4500  & 2000    &
+    \multirow{2}{*}{Intermediate} &  no PU   & $4.5\cdot 10^3$  & $2.0\cdot 10^3$    &
     4.8  &  5.3 &  0.06  &  0.08 \\
-    & PU+SK  & 2600   &  1500  & 1.1  & 1.2 & 0.02 & 0.03 \\
+    & PU+SK+Trim  & $8.5\cdot 10^3$   &  $4.6\cdot 10^3$  & 4.1  & 5.6 & 0.04 & 0.08 \\
     \hline
     \hline
-    \multirow{2}{*}{Resolved} &   no PU  & $8\cdot 10^4$   &
+    \multirow{2}{*}{Resolved} &   no PU  & $8.1\cdot 10^4$   &
     $4.5\cdot 10^4$
     & 4.5  & 6.6  & 0.01 & 0.03 \\
-    & PU+SK  &  $3\cdot 10^4$   &   $1.3\cdot 10^4$ & 2.5    & 3.7  & 0.015 & 0.03 \\
+    & PU+SK+Trim  &  $2.1\cdot 10^5$   &   $1.1\cdot 10^5$ & 4.6    & 6.2  & 0.01 & 0.02 \\
     \hline
@@
 \be
-\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 7.2~(2.3) \, ,\quad
 \mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
@@
     \be
-\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 5.3~(1.8) \, ,\quad
+\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 10.2~(3.2) \, ,\quad
 \mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
@@
 The smaller value of $\la n_{\rm PU}\ra$ at Run II as compared
-to the HL-LHC enviroment should be beneficial in this
+to the HL-LHC environment should be beneficial in this
 respect.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-23 paper/paperscripts/plotMVAdat_PU_4b.py

@@ -139,7 +139,7 @@ for idat in xrange(0,len(datafiles)):
 			total_sigweight = total_sigweight + float(line.split()[2]) # Weight
 
 	#### ROC Curve and S/B plot
-	thresholds = numpy.linspace(0, 1, 100)
+	thresholds = numpy.linspace(0, 1, 40)
 	falsepos = []
 	truepos = []
 

### 2015-12-23 paper/HH4b.tex
Done with corrections
Completed revision of paper

@@
   %
-  We demonstrate the robustness of our analysis strategy against the
-  effects of pile-up.
+  We demonstrate the robustness of our analysis strategy in
+  a high pile-up environment.
   %
-  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
-  a signal significance of  $S/\sqrt{B}\simeq 4$ is obtained,
+  For an integrated luminosity of $\mathcal{L}=3000~(300)$ fb$^{-1}$,
+  a signal significance of  $S/\sqrt{B}\simeq 7.2~(2.3)$ is obtained,
   indicating
-  that the $b\bar{b}b\bar{b}$ channel
-alone could allow for the observation of double Higgs production
+  that the $b\bar{b}b\bar{b}$ final state
+alone could allow for the discovery of double Higgs production
 at the High Luminosity LHC.
+%
+We also find that, provided light and charm
+jet mis-identification can be reduced, observation of
+Higgs pairs in the $b\bar{b}b\bar{b}$ final state could
+be within reach already at Run II.
 }
@@
 
-\bibliography{HH4b}
+%\bibliography{HH4b}
+\input{HH4b.bbl}
 

### 2015-12-23 paper/sec-analysis.tex
Completed revision of paper

@@
 In order to subtract PU in hadronic collisions, a number of techniques
-are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
+are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Cacciari:2008gd,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
 These techniques have also important applications in the subtraction
@@
 is partitioned.
-%
+
 From its definition in terms of the median,
@@
 
-In addition, trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to all large-$R$ jets in the event.
-%
-The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$~\cite{Ellis:1993tq} 
-subjets with $R_{\textrm{sub}} = 0.2$.
-Subjets with transverse momentum less than 5\% of the transverse momentum of the large-$R$ jet are removed.
+In addition, jet trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to large-$R$ jets.
+%
+The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$ subjets with $R_{\textrm{sub}} = 0.2$.
+Subjets with transverse momentum less than 5\% of the total
+transverse momentum of the large-$R$ jet are then removed.
 %
@@
 No trimming is applied to the small-$R$ jets.
-
-To validate the subtraction of PU,
-we compare representative kinematic distributions
-without PU, with PU, and with PU after the combined
-application of {\tt SoftKiller} and trimming (SK+Trim).
-%
-In Fig.~\ref{fig:PUvalidation} we show the
-invariant mass distributions of the
-Higgs candidates for signal
-events in the resolved and boosted categories.
-%
-If PU is not subtracted there is a large shift in the Higgs mass
-peak, by about 40 GeV.
-%
-Once SK subtraction is performed, we recover a distribution much closer
-to the no PU case, with only a small shift of $\simeq 5$ GeV
-and a broadening of the mass
-distribution.
-%
-For the boosted category, we find that
-the mass distributions for jets to which no trimming
-is applied peaks at around 160~GeV, even
-after PU subtraction with {\tt SoftKiller}.
-%
-When trimming is applied in addition to {\tt SoftKiller}, 
-the distribution peaks close to the nominal Higgs mass.
 
@@
 
+%
+In Fig.~\ref{fig:PUvalidation} we show the
+invariant mass distributions of the
+Higgs candidates for signal
+events in the resolved and boosted categories.
+%
+ In the resolved category,
+    we compare  the results without PU
+    with those with PU $\la n_{\rm PU}\ra=80$,
+    with and without SK subtraction.
+    %
+    If PU is not subtracted, there is a large shift in the Higgs mass
+peak, by more than 30 GeV.
+%
+Once SK subtraction is performed, we recover a distribution much closer
+to the no PU case, with only a small shift of $\simeq 5$ GeV
+and a broadening of the mass
+distribution.
+    %
+    In the boosted case, the comparison is performed between no PU,
+    PU with only SK subtraction,
+    and PU with both SK and trimming.
+%
+We find that
+the mass distribution for jets to which no trimming
+is applied peaks at around 160~GeV, even
+after PU subtraction with {\tt SoftKiller}.
+%
+When trimming is applied in addition to {\tt SoftKiller}, 
+the distribution peaks close to the nominal Higgs mass.
+
 In Fig.~\ref{fig:mHH_PU}
 we compare the transverse momentum of the leading Higgs
-candidate, $p_t^{h_1}$ and the invariant mass of the di-Higgs system
+candidate, $p_t^{h}$ and the invariant mass of the di-Higgs system
 $m_{hh}$, in both the boosted and resolved categories.
 %
-In the case of the $p_T^{h_1}$ distribution, the differences between the selection
+In the case of the $p_T^{h}$ distribution, the differences between the selection
 criteria for the resolved
@@
 %
-The effect of PU is small in the boosted case, and generally moderate
-in the resolved case, except for at large $p_T$.
+After subtraction,
+the effects of PU are small in the two categories.
 %
 A similar behaviour is observed in the di-Higgs invariant mass distribution.
+%
+We can also assess the impact of PU in some of
+substructure variables that will be 
+used as input to the MVA in the boosted category.
+%
+In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
+$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
+of energy correlation functions, $C_2^{(\beta)}$,
+Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
+%
+We observe that
+the shapes of both substructure variables
+are reasonably robust in a environment including PU.
 %
@@
 as validated for the purposes of this study, although
-further optimisation should still be possible.
+further optimisation should still be possible, both
+for the trimming and for the {\tt SoftKiller}
+input settings.
 
@@
 
-We can also assess the impact of PU in some of
-substructure variables that will be 
-used as input to the MVA in the boosted category.
-%
-In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
-$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
-of energy correlation functions, $C_2^{(\beta)}$,
-Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
-%
-Comparing the signal distributions in the cases without PU and
-with PU subtracted with SK, we observe that
-the shapes of both substructure variables
-are reasonably robust in a environment including PU.
-%
-
 %%%%%%%%%%%%%%%%%%%%%%%%
@@
 various kinematic distributions for signal and background events,
-with and without PU for the leading Higgs candidate: the invariant mass, the transverse
+with and without PU for the leading Higgs candidate: the transverse
 momentum distribution $p_T$,
+the $p_T$ of the leading AKT03 subjet,
      the 2--to--1 subjettiness ratio $\tau_{21}$, and 
@@
 the kinematic distributions for signal and background events,
-     with and without PU, for the invariant mass and the $p_T$ of the leading
+with and without PU, for the invariant mass and the
+transverse momentum of the leading
      Higgs candidate.
      %
-Again, the PU-subtracted background distributions appear reasonably close
-     to their no PU counterparts.
+     Again, the PU-subtracted background distributions
+     appear reasonably close
+     to their counterparts without PU, and thus
+     the distinctive features between signal and background
+     are maintained after PU subtraction.
 
@@
 
-To complete this discussion, it is illustrative to determine
+It is illustrative to determine
 the mass resolution obtained for the
@@
 we indicate the shift of the invariant mass peak as compared
-to the nominal Higgs mass, $\delta m_h$, %as well as the
+to the nominal Higgs mass, $\la m_h^{\rm reco}\ra-m_h$,
 and the corresponding width of the distribution, $\sigma_{m_h}$,
@@
         We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
-        but without subtraction, and the same with SK subtraction.
-%
-        We find a mass resolution of around 9 GeV in the case
-        without PU, which worsens only slightly
-        to around 11 GeV in the case of $\la n_{\rm PU}\ra=80$ PU
-        with SK subtraction.
-        %
-        We also note that after subtraction, the peak of
+        but without subtraction (only for the
+        resolved category), and the same with SK(+Trim) subtraction.
+
+        In both categories,
+        we find a mass resolution of around 9 GeV in the case
+        without PU.
+        %
+        In the case of PU
+        with SK(+Trim) subtraction,
+        in the resolved category the mass resolution
+        worsens only slightly
+        to around 11 GeV, while in the boosted category we find
+        the same resolution as in the no PU case.
+        %
+        We also note that after SK(+Trim) subtraction, the peak of
         the invariant mass distributions of Higgs candidates
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{table}[h]
+    \begin{table}[t]
       \centering
@@
               \hline
-        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
-          & subleading Higgs   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
-        \hline
-          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
-          & subleading Higgs   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
-          \hline
-            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
-          & subleading Higgs   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
+        \multirow{2}{*}{no PU}  & leading $h$  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
+          & subleading $h$   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
+        \hline
+          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading $h$  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
+          & subleading $h$   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
+          \hline
+            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading $h$  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
+          & subleading $h$   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
             \hline
@@
               \hline
-        \multirow{2}{*}{no PU}  & leading Higgs  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
-          & subleading Higgs   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
-        \hline
-              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK+Trim}  & leading Higgs  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
-          & subleading Higgs   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
+        \multirow{2}{*}{no PU}  & leading $h$  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
+          & subleading $h$   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
+        \hline
+              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK+Trim}  & leading $h$  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
+          & subleading $h$   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
         \hline

### 2015-12-23 paper/sec-conclusions.tex
Completed revision of paper

--- 2015-12-21 paper/sec-conclusions.tex
@@
  the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
-final state at the High-Luminosity LHC with $\mathcal{L}=3$ ab$^{-1}$.
+final state at the LHC.
 %
@@
 We have also demonstrated the robustness of our analysis strategy
-under the addition of significant pileup.
+under the addition of significant pile-up.
 
@@
 signal significance for
-the production of Higgs pairs can be as large as $S/\sqrt{B}\simeq 4.0$.
+the production of Higgs pairs can be as large as $S/\sqrt{B}\simeq 7$.
 %
@@
 final state alone,
-it should be possible to claim evidence for Higgs pair production at
+it should be possible to claim discovery of Higgs pair production at
 the HL-LHC.
@@
 Such experimental improvements might
-even make
-an observation of Higgs pair production possible at the
+even make possible
+an observation of Higgs pair production at the
 end of Run II with
@@
 
+Another challenging aspect of the measurement of Higgs pairs
+in the $b\bar{b}b\bar{b}$ final state is achieving an efficient
+triggering strategy.
+%
+In order to reduce the rate from background QCD processes sufficiently, while
+being able
+to access the relevant $p_T$ regimes, (multi-)jet triggers
+using $b$-quark tagging information online for one or more jets are
+likely to be
+necessary.
+%
+The additional rejection provided by these triggers could
+enable events to be selected efficiently, with four
+jets down to $p_T=45$ GeV in the resolved category,
+and boosted Higgs decays in large-$R$ jets down to jet transverse momenta of
+$p_T=200$ GeV.
+
 One important implication of this work is that it should
-be possible to improve  the accuracy on the extraction of
+be possible to significantly
+improve  the accuracy on the extraction of
 the Higgs trilinear coupling $\lambda$ from
@@
 %
-While signal yields will be certainly increased, also the (gluon-driven) QCD
-multijet background will grow strongly.
+While at 100 TeV the
+signal yields would be increased, also the (gluon-driven) QCD
+multijet background would grow strongly.
 %
@@
 the present analysis, including the MVA optimization,
-at 100 TeV will allow us
+at 100 TeV would also allow
 to assess the accuracy of an extraction of the trilinear
@@
   in {\tt MadGraph5\_aMC@NLO}.
+
+  \noindent
+  The work of K.~B. is supported by a Rhodes Scholarship.
   %
-  J.~R. is supported by an STFC Rutherford Fellowship and
-  Grant ST/K005227/1 and ST/M003787/1.
+  D.~B., J.~F. and C.~I. are supported by the STFC.
   %
@@
 %
-K.~B. is supported by a Rhodes Scholarship.
-%
-D.~B., J.~F. and C.~I. are supported by the STFC.
+  J.~R. is supported by an STFC Rutherford Fellowship and
+  Grant ST/K005227/1 and ST/M003787/1.

### 2015-12-23 paper/sec-intro.tex
Completed revision of paper

@@
 of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
-and will rely on the combination of all relevant final states.
+and should rely on the combination of all relevant final states.
 
@@
 %
-All of these channels are challenging due to the small production
+All these channels are challenging due to the small production
 rates: at 14 TeV, the inclusive total cross-sections are
@@
 $\mathcal{L}=3$ ab$^{-1}$,
-a signal significance of around $S/\sqrt{B}\sim 2.0$ can be obtained.
+a signal significance of around $S/\sqrt{B}\simeq 2.0$ can be obtained.
 %
@@
   We also assess the robustness of our analysis strategy in
-  an environment including pile-up (PU).
+  an environment with high pile-up (PU).
   %
-  We find an overall signal significance of $S/\sqrt{B}\simeq 4.0$
-  for a total integrated
-  luminosity of $\mathcal{L}=3$ ab$^{-1}$,
-   indicating
-  that the $b\bar{b}b\bar{b}$ channel
-alone may allow for the observation of double Higgs production
+ Our results indicate that 
+  the $b\bar{b}b\bar{b}$ 
+final state
+alone should allow for the discovery of double Higgs production
   at the HL-LHC.
   %
+  We also find that, provided the contamination from light and charm jet
+  mis-identification is reduced, the observation of Higgs pairs
+  in this final state may be within reach already at Run II with
+  $\mathcal{L}=300$ fb$^{-1}$.
 

### 2015-12-23 paper/sec-mva.tex
Completed revision of paper

@@
     \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1070 & $7.6\cdot 10^5$  & 1.2  & $1.4\cdot 10^{-3}$  \\
-    &  $y_{\rm cut}=0.82$ & 790  & $2.2\cdot 10^4$   & 5.4  & 0.034 \\
+    &  $y_{\rm cut}=0.82$ & 790  & $2.2\cdot 10^4$   & 5.4  & 0.03 \\
     \hline
@@
   at the end of the cut-based analysis,
-  for the case with $\la n_{\rm PU}\ra=80$ with SK
+  for the case with $\la n_{\rm PU}\ra=80$ with SK+Trim
   subtraction,
@@
 
-We observe how the pre-MVA 
-signal significance is degraded
-as compared to the case without PU.
+We observe that the pre-MVA 
+signal significance is close
+to the case without PU for the three categories.
 %
-We now find values for $S/\sqrt{B}$ of 0.25, 0.15 and 0.31, in the resolved,
+We now find values for $S/\sqrt{B}$ of 0.9, 0.7 and 1.5, in the resolved,
 intermediate and boosted categories, respectively, to be compared
@@
 %
-Once the MVA is applied, the signal significance in the three
-categories increases to 2.5, 1.1 and 2.9 respectively.
+Likewise, the number of selected
+signal events in each category, at the
+end of the cut-based analysis, is only mildly affected
+by PU.
+%
+The slight pre-MVA improvement in $S/\sqrt{B}$ for the
+boosted case arises from a reduction in the number
+of background events that are classified in this category
+as compared to the case without PU.
+
+Once the MVA is applied, the signal significance in the 
+resolved, intermediate and boosted
+categories increases to 4.6, 4.1 and 3.7 respectively,
+to be compared with 4.5, 4.8 and 5.4 in the case
+without PU.
+%
+Therefore, the post-MVA effects of PU on $S/\sqrt{B}$ is
+a moderate degradation of the boosted and intermediate categories,
+while the resolved category is largely unchanged.
 %
 We also observe that, due
-to the MVA, the signal significance and the
-signal over background ratio is improved from 0.31 and $3\cdot 10^{-4}$
-(0.25 and $10^{-4}$) up to 2.9 and 3.4\% (2.5 and 1.5\%)
-in the boosted (resolved) category.
+to the MVA, the
+signal over background ratio is increased from 0.02\%, 0.08\% and
+0.2\% up to 1\%, 4\% and 2\% in the resolved, intermediate
+and boosted categories respectively.
 %
-The intermediate category, on the other hand, exhibits a
-significantly lower post-MVA value of $S/\sqrt{B}\simeq
-1.1$.
-%
-We can therefore conclude that, as was already the case
-without PU,
-the boosted category is the most promising
-topology for the study of Higgs pair production in the $b\bar{b}b\bar{b}$
-final state
-at the HL-LHC, also in the case of a high-PU environment.
-However important information can also be obtained from
-the resolved category, which has a comparable significance.
+This indicates that while this measurement is still highly challenging,
+requiring a careful extraction of the QCD
+background from the data, it is certainty within reach.
 
@@
 
-Another important result from Table~\ref{table:cutflowMVA_PU} is that,
-for the optimal MVA cut, the signal over background ratio
-is 3.4\% (1.5\%)
-in the boosted (resolved) categories.
-%
-This indicates that while this measurement is still highly challenging,
-requiring a careful extraction of the QCD
-background from the data, it is certainty within reach.
-%
-As in the case without PU, 
-our analysis  points out that both
-$S/B$ and $S/\sqrt{B}$ could be increased  by reducing the background component
-that arises from the mis-identification of light and charm
-jets as $b$-jets.
-
-In Fig.~\ref{fig:nev2_PU}
-we show the number of signal and background events that
-are expected at the HL-LHC as a function of
-$y_{\rm cut}$, as well as the corresponding ROC curve.
-%
-Comparing Figs.~\ref{fig:nev2} and~\ref{fig:nev2_PU}, we observe
-that the intermediate category is substantially worsened once PU effects
-are accounted for due to a sizable
-reduction in the number of signal
-events that are now classified in this category.
-%
-This shows that the selection criteria
-of the intermediate category are less
-resilient against PU contamination,
-in contrast to the resolved and boosted selections.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+In Fig.~\ref{fig:nev2_PU}
+we show the number of signal and background events that
+are expected at the HL-LHC as a function of
+$y_{\rm cut}$, as well as the corresponding ROC curve.
+%
+The slight degradation of the boosted category in the case
+of PU can be seen by comparing with the corresponding
+results without PU in Fig.~\ref{fig:nev2}.
+%
 In Fig.~\ref{fig:sb_mva_PU} we show the signal significance,
@@
 achieve a signal significance of
- $S/\sqrt{B}$ between 2.5 and 3.0 (depending on the
-specific choice of $y_{\rm cut}$)
-separately for the boosted and resolved
-categories.
-%
-On the other hand, the significance obtainable from the intermediate category is now marginal.
+ $S/\sqrt{B}$ between 3.0 and 4.5, depending on the
+specific choice of $y_{\rm cut}$,
+separately for the three categories.
 %
@@
 Since no specific effort has been performed to
-optimize PU subtraction, for instance by tuning the value
-of the patch length $a$ in {\tt SoftKiller}, we believe that
+optimize PU subtraction, for instance by tuning the values
+of the patch length $a$ in {\tt SoftKiller}
+and of the $p_T$ threshold in jet trimming.
+we believe that
 there could be still room for further  improvement.
@@
 As we can see by comparing with Fig.~\ref{fig:nnweights}, 
-in the boosted category, the discrimination power of the invariant
-mass of Higgs candidates is decreased, while
-that of  substructure
-variables such as $C_2^{(\beta)}$ and
-$D^{(\beta)}_2$ is conversely
-increased.
+the relative weight of the different input variables to the MVA
+is mostly unchanged in the case of PU.
 %
-In addition, also the $p_T$ distributions of the AKT03
-subjets within the large-$R$
-jets carry important information.
+In the resolved category, the highest total associated weight is carried
+by the Higgs candidates $p_T$ and invariant mass, as well
+as by the $p_T$ of the individual small-$R$ jets.
 %
-In the case of the resolved category,  the highest
-values of the ANN weights without PU
-were found for the $p_T$ of the 
-Higgs candidates and their invariant masses, as well
-as the for invariant mass of the di-Higgs system
-and the $p_T$ of the small-$R$ jets.
-%
-As we can see in Fig.~\ref{fig:nnweights_PU},
-this remains the case under the addition of PU.
+For the boosted category, the highest weight is carried by the
+Higgs invariant mass, followed by
+the Higgs $p_T$, $m_{hh}$, the $p_T$ of the AKT03 subjets and the
+substructure variables, with a similar weighting among them.
 
@@
 
-In Table~\ref{table:cutflowMVA_fakes} we compare,
-number of background events  expected at the HL-LHC, after the MVA is applied.
-Both the total number, $N_{\rm ev}^{\rm tot}$,
+In Table~\ref{table:cutflowMVA_fakes} we compare
+the  number of background events  expected for
+$\mathcal{L}=3$ ab$^{-1}$,
+after the MVA is applied, both
+the total number, $N_{\rm ev}^{\rm tot}$,
 and those from the  QCD $4b$ component
@@
     from light and charm jet mis-identification arises
-    for the boosted and resolved categories.
+    for the boosted category, the one where the relative size of the
+    $2b2j$ over the $4b$ background components is higher
+    (see Table~\ref{tab:cutflow_noPU_1}), where
+    $S/\sqrt{B}$ increases from 3.7 to 5.9.
 %
@@
     Also provided are the values of the signal 
-    significance and signal over background ratios in each case.
+    significance and signal over background ratios in each case
+    for $\mathcal{L}=3$ ab$^{-1}$.
         \label{table:cutflowMVA_fakes}
@@
 should be 
-well above the threshold for evidence.
+well above the threshold for discovery.
 %
-On the other hand, such a measurement seems to be
-extremely challenging
+Interestingly, such a measurement might also be within reach
 for the total integrated luminosity expected by the end of Run II.
@@
     the only relevant background would be the irreducible QCD $4b$ component,
-    we obtain instead:
+    we obtain
     \be
@@
 \ee
-Therefore, a discovery of Higgs pair production at the
-HL-LHC might be possible if the
-mis-identification of light and charm jets as
+Therefore, observation of Higgs pair production
+in the $b\bar{b}b\bar{b}$ final state might be possible
+already by the end of Run II, provided
+the effects due to mis-identification of light and charm jets as
 $b$-jets can be reduced.
 %
-With these assumptions, and provided
-the signal efficiency can be further enhanced,
-this measurement might even be possible
-by the end of Run II.
-%
-The smaller value of $\la n_{\rm PU}\ra$ at Run II as compared
-to the HL-LHC environment should be beneficial in this
-respect.
+The smaller value of $\la n_{\rm PU}\ra$ expected
+at Run II as compared
+to the HL-LHC environment should be beneficial in this respect.

### 2015-12-23 paper/sec-analysis.tex
Completed revision of paper

@@
 
-\subsection{Impact of pile-up}
+\subsection{Impact of pileup}
 \label{sec:pileup}
@@
 and background processes are
-modified in the presence of pile-up.
+modified in the presence of pileup.
 %

### 2015-12-23 paper/sec-mva.tex
Completed revision of paper

@@
 In this section we study how the MVA results are modified
-when the analysis is performed including PU.
+when the analysis is performed including significant PU.
 %
@@
   both cases the number of signal and
-    background events expected
+    total background events expected
     at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
@@
 %
-Likewise, the number of selected
+The number of selected
 signal events in each category, at the
@@
 categories increases to 4.6, 4.1 and 3.7 respectively,
-to be compared with 4.5, 4.8 and 5.4 in the case
-without PU.
+to be compared with the corresponding values
+without PU, namely 4.5, 4.8 and 5.4.
 %
-Therefore, the post-MVA effects of PU on $S/\sqrt{B}$ is
+Therefore, the post-MVA effect of PU on $S/\sqrt{B}$ is
 a moderate degradation of the boosted and intermediate categories,
@@
 %
-We conclude that the qualitative conclusions drawn
+Therefore, the qualitative conclusions drawn
 in the case without PU also hold when the analysis

### 2015-12-27 paper/sec-mva.tex
Updated cut-flow in the case of PU

@@
 %
+In Table~\ref{tab:cutflow_PU80_1}
+we provide the pre-MVA cut flow in the case of PU,
+the corresponding version without PU is
+Table~\ref{tab:cutflow_noPU_1}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \scriptsize
+      \input{table_PU80.tex}
+    \caption{\small Same as Table~\ref{tab:cutflow_noPU_1}
+for the case  now for the case
+    of PU+SK+Trim with $\la n_{\rm PU}\ra=80$.
+ \label{tab:cutflow_PU80_1}}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In Table~\ref{table:cutflowMVA_PU} we provide the results
@@
 requiring a careful extraction of the QCD
-background from the data, it is certainty within reach.
+background from the data, it is certainly within reach.
 

### 2015-12-30 paper/paperscripts/getCutFlows_check.py
v1 of arxiv submission

@@ -7,11 +7,11 @@ from tabulate import tabulate
 ##################################################################
 
 
-#root = "../../paper/plotdata/results_noPU/"
-#labeltag="noPU"
+root = "../../paper/plotdata/results_noPU/"
+labeltag="noPU"
 
-root = "../../paper/plotdata/results_SK_PU80/"
-labeltag="SKPU80"
+#root = "../../paper/plotdata/results_SK_PU80/"
+#labeltag="SKPU80"
 
 folders = ['diHiggs/', 'background/', 'SHERPA_QCD4b/', 'SHERPA_QCD2b2j/', 'SHERPA_QCD4j/', 'SHERPA_QCDttbar/']
 names = ['signal', 'total bkg', '4b', '2b2j', '4j', 'ttbar']

### 2015-12-30 paper/paperscripts/plotHist_D2_h0_bst_comp.py

@@ -20,11 +20,11 @@ datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_C2_fj1_boost_C2.dat"
 
 # Plot labels
 plotnames.append("no PU")
-plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK+Trim")
+plotnames.append(r"PU80+SK+Trim")
 
 # Axis labels
 xLabel = r"Energy Correlation Ratio $C_2^{(\beta)}$ in leading Higgs candidate"
-yLabel = "A. U."
+yLabel = "a. u."
 
 # Log axes
 xLog = False

### 2015-12-30 paper/paperscripts/plotHist_mHH_bst_comp.py

@@ -20,11 +20,11 @@ datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_HH_boost_C2.dat")
 
 # Plot labels
 plotnames.append("no PU")
-plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK+Trim")
+plotnames.append(r"PU80+SK+Trim")
 
 # Axis labels
 xLabel = "di-Higgs Invariant Mass $m_{hh}$ (GeV)"
-yLabel = "A. U."
+yLabel = "a. u."
 
 # Log axes
 xLog = False

### 2015-12-30 paper/paperscripts/plotHist_mHH_res_comp.py

@@ -20,11 +20,11 @@ datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_HH_res_C2.dat")
 
 # Plot labels
 plotnames.append("no PU")
-plotnames.append(r"$\langle n_{PU}\rangle=80$ + SK")
+plotnames.append(r"PU80+SK")
 
 # Axis labels
 xLabel = "di-Higgs Invariant Mass $m_{hh}$ (GeV)"
-yLabel = "A. U."
+yLabel = "a. u."
 
 # Log axes
 xLog = False

### 2015-12-30 paper/paperscripts/plotHist_m_hh_res_back_noPU.py

@@ -123,7 +123,7 @@ for idat in xrange(0,len(datafiles)):
   icol=icol+1
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.28,0.93,"Resolved category, no PU", fontsize=20)
+fig.text(0.28,0.93,"Boosted category, no PU", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-30 paper/paperscripts/plotHist_pt_H0_bst_noPU.py

@@ -121,7 +121,7 @@ for idat in xrange(0,len(datafiles)):
 
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.25,0.93,r"Boosted category, $\langle n_{PU}\rangle=0$", fontsize=20)
+fig.text(0.25,0.93,r"Boosted category, no PU", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-30 paper/paperscripts/plotHist_pt_h0_bst_comp_back.py

@@ -124,7 +124,7 @@ for idat in xrange(0,len(datafiles)):
 
 
 plt.rcParams.update({'font.size': 14})
-fig.text(0.18,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK+Trim", fontsize=19)
+fig.text(0.23,0.93,r"Boosted category,  PU80+SK+Trim", fontsize=19)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-30 paper/paperscripts/plotHist_pt_smallRjets_res.py

@@ -122,7 +122,7 @@ for idat in xrange(0,len(datafiles)):
 
 
 plt.rcParams.update({'font.size': 16})
-fig.text(0.26,0.93,r"Resolved category, $\langle n_{PU}\rangle =0$", fontsize=20)
+fig.text(0.26,0.93,r"Resolved category, no PU", fontsize=20)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-30 paper/paperscripts/plotHist_tau12_h1_bst_comp_back.py

@@ -122,7 +122,7 @@ for idat in xrange(0,len(datafiles)):
 
 
 plt.rcParams.update({'font.size': 14})
-fig.text(0.18,0.93,r"Boosted category,  $\langle n_{PU}\rangle =80$ + SK+Trim", fontsize=19)
+fig.text(0.23,0.93,r"Boosted category,  PU80+SK+Trim", fontsize=19)
 
 # Legend
 legend = ax.legend(loc='best')

### 2015-12-30 paper/paperscripts/plotMVAdat_PU150_resc_4b.py

@@ -1,0 +1,248 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../plotdata/results_SK_PU150/MVA/nn_13X5X3X1_50000-Gen_SKPU150_res_4b.dat",
+            "../plotdata/results_SK_PU150/MVA/nn_17X5X3X1_50000-Gen_SKPU150_int_4b.dat",
+            "../plotdata/results_SK_PU150/MVA/nn_21X5X3X1_50000-Gen_SKPU150_bst_4b.dat"]
+
+datanames=[ "Resolved","Intermediate","Boosted"]
+titlenames=[ r"Resolved Category,  $\langle n_{PU}\rangle =150$+SK",
+             r"Intermediate Category,  $\langle n_{PU}\rangle =150$+SK",\
+             r"Boosted Category,  $\langle n_{PU}\rangle=150$+SK"]
+
+datanamessignal=[ "Signal Res","Signal Int","Signal Boost"]
+datanamesback=[ "Background Res","Background Int","Background Boost"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_SKPU150_4b"  # Histograms for discriminant
+ROCout = "roc_SKPU150_4b"	  # ROC curve
+SBout = "sb_SKPU150_4b"	  # S/B curve
+SSBout = "ssb_SKPU150_4b"	  # S/Sqrt(B) curve
+NeVout = "nev_SKPU150_4b"	  # Number of events (twin axes)
+NeV2out = "nev2_SKPU150_4b"  # Number of events (single axis)
+
+# Rescaling factor for signal
+resc = 0.41
+
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background,title):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
[…]

### 2015-12-30 paper/paperscripts/plotMVAdat_PU80_resc_4b.py

@@ -1,0 +1,248 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../plotdata/results_SK_PU80/MVA/nn_13X5X3X1_50000-Gen_SKPU80_res_4b.dat",
+            "../plotdata/results_SK_PU80/MVA/nn_17X5X3X1_50000-Gen_SKPU80_int_4b.dat",
+            "../plotdata/results_SK_PU80/MVA/nn_21X5X3X1_50000-Gen_SKPU80_bst_4b.dat"]
+
+datanames=[ "Resolved","Intermediate","Boosted"]
+titlenames=[ r"Resolved Category,  $\langle n_{PU}\rangle =80$+SK",
+             r"Intermediate Category,  $\langle n_{PU}\rangle =80$+SK",\
+             r"Boosted Category,  $\langle n_{PU}\rangle=80$+SK"]
+
+datanamessignal=[ "Signal Res","Signal Int","Signal Boost"]
+datanamesback=[ "Background Res","Background Int","Background Boost"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_SKPU80"  # Histograms for discriminant
+ROCout = "roc_SKPU80"	  # ROC curve
+SBout = "sb_SKPU80"	  # S/B curve
+SSBout = "ssb_SKPU80"	  # S/Sqrt(B) curve
+NeVout = "nev_SKPU80"	  # Number of events (twin axes)
+NeV2out = "nev2_SKPU80"  # Number of events (single axis)
+
+# Rescaling factor for signal
+resc = 0.41
+
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background,title):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
[…]

### 2015-12-30 paper/paperscripts/plotNetwork_int_PU.py

@@ -130,12 +130,10 @@ plt.xticks(numpy.arange(len(kinematics)) + 2.5, kinematics,fontsize=10)
 plt.xlabel('ANN Input Variable',fontsize=17)
 plt.ylabel('Total associated weight',fontsize=17)
 
-plt.text(4,8.5,"Intermediate category, $n_{PU}=80$+SK", fontsize=20)
+plt.text(3,8.3,"Intermediate category, PU80+SK+Trim", fontsize=19)
 
 plt.savefig(histout+".pdf")
 plt.clf()
-
-
 
 nx.draw(G, pos=dict(zip(G.nodes(),posLoc)), labels=dict(zip(G.nodes(),labelList)), edge_color=colorList, node_color=biasList, width=2, with_labels=True)
 plt.savefig(archout+".pdf")

### 2015-12-31 paper-arxiv-v1/HH4b.tex
Added v2 of paper in repo

--- 2015-12-15 paper/HH4b.tex
@@
 
-\author{Katharina Behr, Daniela Bortoletto, James Frost,
+\author{Janna Katharina Behr, Daniela Bortoletto, James A. Frost,
   Nathan P. Hartland, Cigdem Issever and Juan Rojo}
@@
   %
-  We demonstrate the robustness of our analysis strategy against the
-  effects of pile-up.
+  We demonstrate the robustness of our analysis strategy in
+  a high pileup environment.
   %
   For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
-  a signal significance of  $S/\sqrt{B}\simeq 4$ is obtained,
+  a signal significance of  $S/\sqrt{B}\simeq 3$ is obtained,
   indicating
-  that the $b\bar{b}b\bar{b}$ channel
+  that the $b\bar{b}b\bar{b}$ final state
 alone could allow for the observation of double Higgs production

### 2015-12-31 paper-arxiv-v1/sec-analysis.tex
Added v2 of paper in repo

--- 2015-12-23 paper/sec-analysis.tex
@@
   These jets are also constructed with the
-  anti-$k_T$ clustering algorithm, now using a $R=1.2$ radius.
+  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
   %
@@
   conditions, where the {\tt FastJet} default
-  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$ are used.
+  parameters of  $\mu_{\rm mdt} = 0.67$ and $y_{\rm mdt}=0.09$ are used.
   %
@@
   algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}
-  with $R=1.2$.
+  with $R=1.0$.
+
+  In the case of the analysis including PU, a trimming
+  algorithm~\cite{Krohn:2009th}
+  is applied to all large-$R$ jets to mitigate the effects of PU,
+  especially on the jet mass.
+  %
+  For further details see Sect.~\ref{sec:pileup}.
 
@@
 
-  These subjets are constructed by reclustering the constituents
-  of a large-$R$ jet, again with the
-  anti-$k_T$ algorithm,
-  but this time with a smaller radius parameter, namely
-  $R=0.3$~\cite{Aad:2015uka}. They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
- %
-  These small-$R$ subjets will be the main input for
+ All final-state particles are clustered using the
+ anti-$k_T$ algorithm, but this time with
+ a smaller radius parameter, namely $R=0.3$.
+ %
+ The resulting anti-$k_T$ $R=0.3$ (AKT03) jets
+ are then ghost-associated to each large-$R$ jets
+ in order to define its subjets~\cite{Aad:2015uka}.
+
+ These AKT03 subjets
+  are required to satisfy
+  $p_T > 50$~GeV and $|\eta|<2.5$, and
+   will be the main input for
   $b$-tagging in the boosted category.
@@
 %
-In particular we  consider the following jet
+In particular we  consider the following
 substructure variables:
@@
 
-\item The ratio of 2-to-1 subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.
+\item The ratio of 2-to-1 subjettiness $\tau_{21}$~\cite{Thaler:2010tr,Thaler:2011gf}.
 
@@
 \ee
-while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is
+while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is,
 \be
@@
   The free parameter $\beta$ is set to a value of $\beta=2$,
-  as recommended by the authors of Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
+  as recommended by Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
 \end{itemize}
@@
 %
-Rather than restricting to a specific event topology,
+Rather than restricting ourselves to a specific event topology,
 we aim to consistently combine the information from
@@
 \label{higgsmasswindow}
-|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
+|m_{h,j} - 125~{\rm GeV}| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
 \ee
@@
 %
-Therefore, when ascertaining which category an event is to be exclusively placed:
+Therefore, when ascertaining in
+which category an event is to be exclusively placed:
 if the event satisfies the boosted requirements, it is assigned to
@@
 %
-It the event also fails the intermediate category
+If the event also fails the intermediate category
 requirements, we
-then check if it pass the resolved selection criteria.
+then check if it passes the resolved selection criteria.
 %
 The resulting exclusive event samples are then separately processed
-through the MVA, allowing a consistent combination
+through the MVA, allowing for a consistent combination
 of the significance of the three event categories.
@@
 Therefore,
-as for the previous distribution, also here 
+as for the previous distribution, the chosen cut value is
 a compromise between suppressing backgrounds but keeping a large fraction of
@@
 Eq.~(\ref{eq:c2}), and
-the 2--to--1 subjettiness ratio $\tau_{12}$, Eq.~(\ref{eq:tau21}),
+the 2--to--1 subjettiness ratio $\tau_{21}$, Eq.~(\ref{eq:tau21}),
 all for the leading
-Higgs candidates, and also $\tau_{12}$ for the subleading
+Higgs candidates, and also $\tau_{21}$ for the subleading
 Higgs candidates.
@@
 From Fig.~\ref{fig:mva_substructure_1} we also see
-the distributions of the subjettiness ratio $\tau_{12}$ are
+the distributions of the subjettiness ratio $\tau_{21}$ are
 reasonably similar
@@
 Now we turn to discuss how the description of kinematic
-distributions for $hh\to 4b$ signal
+distributions for signal
 and background processes are
@@
 We have explored two scenarios,
-one with a mean number of
-PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$,
+one with a number of
+PU vertices per bunch crossing of $n_{\rm PU}=80$,
 and another
-with $\la n_{\rm PU}\ra=150$.
-%
-While the latter is closer to the HL-LHC forecasts,
-we adopt $\la n_{\rm PU}\ra=80$ as our baseline,
-given that it
-is beyond the scope of this paper to fully optimize
-the PU subtraction.
+with $n_{\rm PU}=150$.
+%
+In the following we adopt $n_{\rm PU}=80$ as our baseline,
+and denote this scenario by PU80.
+%
+We have verified that the combined signal significance is
+similar if $n_{\rm PU}=150$ is adopted instead.
 
@@
 below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
-value is dynamically determined in a way that makes the event-wide
-transverse-momentum flow density $\rho$ vanish.
-%
-This $p_T$ flow density is defined as
+value is dynamically determined so that the event-wide
+transverse-momentum flow density $\rho$ vanishes, where $\rho$ is
+defined as
 \be
@@
 \ee
-where the median is computed over all the regions $i$ with area
+and where the median is computed over all the regions $i$ with area
 $A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
@@
 %
-The {\tt SoftKiller} subtraction is applied to particles at the end of the parton shower, before
+The {\tt SoftKiller} subtraction is then
+applied to particles at the end of the parton shower, before
 jet clustering.
@@
 %
-No trimming is applied to the small-$R$ jets.
+No trimming is applied to the small-$R$ jets and
+to the case without PU.
 
@@
     we compare  the results without PU
-    with those with PU $\la n_{\rm PU}\ra=80$,
+    with those with PU80
     with and without SK subtraction.
     %
-    In the boosted case, the comparison is between no PU,
+    In the boosted case, the comparison is performed between no PU,
     PU with only SK subtraction,
@@
     we compare  the results without PU
-    with those with PU $\la n_{\rm PU}\ra=80$,
-    with and without SK subtraction.
+    with those with PU80, with and without SK subtraction.
     %
@@
 Once SK subtraction is performed, we recover a distribution much closer
-to the no PU case, with only a small shift of $\simeq 5$ GeV
+to the no PU case, with only a small shift of a few GeV
 and a broadening of the mass
@@
 When trimming is applied in addition to {\tt SoftKiller}, 
-the distribution peaks close to the nominal Higgs mass.
+the distribution peaks close to the nominal Higgs mass, as in the case
+of the resolved category.
 
@@
 candidate, $p_t^{h}$ and the invariant mass of the di-Higgs system
-$m_{hh}$, in both the boosted and resolved categories.
+$m_{hh}$, in both the boosted and resolved categories,
+between the no PU and the PU+SK+Trim cases.
 %
@@
 A similar behaviour is observed in the di-Higgs invariant mass distribution.
-%
-We can also assess the impact of PU in some of
+
+We can also assess the impact of PU on the
 substructure variables that will be 
-used as input to the MVA in the boosted category.
+used as input to the MVA in the boosted
+and intermediate categories.
 %
@@
 $\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
-of energy correlation functions, $C_2^{(\beta)}$,
+of energy correlation functions $C_2^{(\beta)}$,
 Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
@@
 the shapes of both substructure variables
-are reasonably robust in a environment including PU.
+are reasonably robust in a environment including significant PU.
 %
@@
 as validated for the purposes of this study, although
-further optimisation should still be possible, both
-for the trimming and for the {\tt SoftKiller}
+further optimisation should still be possible, both in terms of
+the {\tt SoftKiller} and of the trimming
 input settings.
@@
     %
-    We compare the results without PU with those with PU,
-    for $\la n_{\rm PU}\ra=80$ and SK+Trim subtraction,
+    We compare the results without PU with those with PU80
+    and SK+Trim subtraction,
     as explained in the text.
@@
 
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \begin{table}[h]
+      \centering
+      \begin{tabular}{|c|c|c|c|}
+        \hline
+        \multicolumn{4}{|c|}{Resolved category}\\
+        \hline
+        \hline
+        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
+              \hline
+        \multirow{2}{*}{no PU}  & leading $h$  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
+          & subleading $h$   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
+        \hline
+          \multirow{2}{*}{PU80}  & leading $h$  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
+          & subleading $h$   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
+          \hline
+            \multirow{2}{*}{PU80+SK}  & leading $h$  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
+          & subleading $h$   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
+            \hline
+            \multicolumn{4}{c}{}\\
+             \hline
+        \multicolumn{4}{|c|}{Boosted category}\\
+        \hline
+        \hline
+        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
+              \hline
+        \multirow{2}{*}{no PU}  & leading $h$  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
+          & subleading $h$   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
+        \hline
+              \multirow{2}{*}{PU80+SK+Trim}  & leading $h$  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
+          & subleading $h$   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
+        \hline
+        \end{tabular}
+      \caption{\label{tab:massresolution}
+        Resolution of the invariant mass distribution of
+        reconstructed Higgs candidates in the resolved 
+        and boosted  categories.
+        %
+        We show three cases: no PU, with PU80
+        without subtraction (only for resolved),
+        and the same with SK+Trim subtraction.
+        %
+        We indicate the shift of the fitted invariant
+        mass peak $\la m_h^{\rm reco}\ra$ for
+        the Higgs candidates as compared
+        to the nominal Higgs mass $m_h$, as well as the
+        the fitted  Gaussian  width  $\sigma_{m_h}$.
+        }
+    \end{table}
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 It is illustrative to determine
 the mass resolution obtained for the
-reconstructed Higgs candidates in the various cases.
+reconstructed Higgs candidates in the various cases considered in
+the present study.
 %
 In Table~\ref{tab:massresolution}
-we indicate the shift of the invariant mass peak as compared
+we indicate the shift of the fitted invariant mass peak as compared
 to the nominal Higgs mass, $\la m_h^{\rm reco}\ra-m_h$,
@@
 obtained from fitting a Gaussian to the mass distributions
-of both the leading and subleading Higgs candidates in
-the resolved category.
-        %
-        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
+of leading and subleading Higgs candidates in
+the resolved and boosted categories.
+        %
+        We show results for three cases: without PU, with PU80
         but without subtraction (only for the
-        resolved category), and the same with SK(+Trim) subtraction.
+        resolved category), and the same with SK+Trim subtraction.
 
@@
         In the case of PU
-        with SK(+Trim) subtraction,
+        with SK+Trim subtraction,
         in the resolved category the mass resolution
@@
         %
-        We also note that after SK(+Trim) subtraction, the peak of
+        We also note that after SK+Trim subtraction, the peak of
         the invariant mass distributions of Higgs candidates
-        coincides with the nominal values of $m_h$ within a few GeV.
-
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \begin{table}[t]
-      \centering
-      \begin{tabular}{|c|c|c|c|}
-        \hline
-        \multicolumn{4}{|c|}{Resolved category}\\
-        \hline
-        \hline
-        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
-              \hline
-        \multirow{2}{*}{no PU}  & leading $h$  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
-          & subleading $h$   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
-        \hline
-          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading $h$  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
-          & subleading $h$   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
-          \hline
-            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading $h$  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
-          & subleading $h$   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
-            \hline
-            \multicolumn{4}{c}{}\\
-             \hline
-        \multicolumn{4}{|c|}{Boosted category}\\
-        \hline
-        \hline
-        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
-              \hline
-        \multirow{2}{*}{no PU}  & leading $h$  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
-          & subleading $h$   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
-        \hline
-              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK+Trim}  & leading $h$  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
-          & subleading $h$   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
-        \hline
-        \end{tabular}
-      \caption{\label{tab:massresolution}
-        Resolution of the invariant mass distribution of
-        reconstructed Higgs candidates in the resolved (upper table)
-        and boosted (categories) category.
-        %
-        We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
-        but without subtraction (only for resolved),
-        and the same with SK(+Trim) subtraction.
-        %
-        We indicate the shift of the invariant
-        mass peak $\la m_h^{\rm reco}\ra$ as compared
-        to the nominal Higgs mass $m_h=125$ GeV, as well as the width
-        of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,
-        for both the leading and subleading Higgs candidates.
-      }
-    \end{table}
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+        coincides with the nominal values of $m_h$ within a few GeV
+        for the two categories.

### 2015-12-31 paper-arxiv-v1/sec-conclusions.tex
Added v2 of paper in repo

--- 2015-12-23 paper/sec-conclusions.tex
@@
 We have illustrated how the $2b2j$ component leads to
-a contribution comparable to that of the $4b$ process,
+a contribution comparable to that of QCD $4b$ production,
 due to a combination of  parton shower effects, $b$-quark 
@@
 We have also demonstrated the robustness of our analysis strategy
-under the addition of significant pile-up.
+under the addition of significant PU.
+%
+In particular, we have explored two scenarios, $n_{\rm PU}=80$ and
+$n_{\rm PU}=150$, and found a comparable overall signal significance
+in the two cases.
 
@@
 signal significance for
-the production of Higgs pairs can be as large as $S/\sqrt{B}\simeq 7$.
+the production of Higgs pairs turns out to be $S/\sqrt{B}\simeq 3$.
 %
@@
 final state alone,
-it should be possible to claim discovery of Higgs pair production at
+it should be possible to claim observation of Higgs pair production at
 the HL-LHC.
@@
 %
+This would allow to enhance  $S/\sqrt{B}$ almost to the discovery
+level, see Table~\ref{table:cutflowMVA_fakes}.
+%
+It would also be advantageous to improve the $b$-tagging efficiency, allowing
+to achieve higher signal yields.
+%
 Another possibility would be to improve the mass resolution of the Higgs
 reconstruction
-in high-PU environments, and, more in general,
+in high-PU environments, and, more general,
 to optimize the PU subtraction
@@
 to reduce the impact of PU in the modelling
-of kinematical variables and the associated
+of kinematic variables and the associated
 degradation in the MVA discrimination.
 %
-Such experimental improvements might
-even make possible
-an observation of Higgs pair production at the
-end of Run II with
-$\mathcal{L}=300$ fb$^{-1}$.
 
@@
 enable events to be selected efficiently, with four
-jets down to $p_T=45$ GeV in the resolved category,
+jets down to $p_T=40$ GeV in the resolved category,
 and boosted Higgs decays in large-$R$ jets down to jet transverse momenta of
 $p_T=200$ GeV.
+%
+In addition,
+good control of the multijet backgrounds and the
+experimental systematics of the MVA inputs will be important to achieve
+these sensitivities.
+
+Our strategy relies on the modeling of the kinematic
+distributions of signal and background events, since these provide
+the inputs to the MVA discriminant.
+%
+In this respect, it would be important, having established the key
+relevance of the $b\bar{b}b\bar{b}$ channel for the study of
+Higgs pair production, to revisit and improve the
+theoretical modeling of our signal and background simulation,
+in particular using NLO calculations matched to
+parton showers both for signal~\cite{Frederix:2014hta,Maierhofer:2013sha}
+and for backgrounds~\cite{Alwall:2014hca,Gleisberg:2008ta}.
+%
 
@@
 publication, where we will also
-compare with the corresponding  precision 
+compare the precision from the $b\bar{b}b\bar{b}$ final state
+with the corresponding  precision 
 that has been reported from other final states such as
@@
 the present analysis, including the MVA optimization,
-at 100 TeV would also allow
+at 100 TeV would also allow us
 to assess the accuracy of an extraction of the trilinear
@@
 at 100 TeV.
-
-Our strategy relies on the modeling of the kinematical
-distributions of signal and background events, since these provide
-the inputs to the MVA discriminant.
-%
-In this respect, it would be important, having established the key
-relevance of the $b\bar{b}b\bar{b}$ channel for the study of
-Higgs pair production, to revisit and improve the
-theoretical modeling of our signal and background simulation,
-in particular using NLO calculations matched to
-parton showers both for signal~\cite{Frederix:2014hta,Maierhofer:2013sha}
-and for backgrounds~\cite{Alwall:2014hca,Gleisberg:2008ta}.
-%
 
@@
 operators that can be obtained from measurements
-of various kinematical distributions
+of various kinematic distributions
 in the $hh\to b\bar{b}b\bar{b}$ process.
@@
 other final states, such as
-$b\bar{b}\gamma\gamma$, allow for a better constraint upon operators
+$b\bar{b}\gamma\gamma$, allow for better constraints upon operators
 that modify the high-energy behavior
@@
 would be a computationally intensive task, since
-BSM dynamics will modify the shapes of the kinematical
+BSM dynamics will modify the shapes of the kinematic
 distributions and thus in principle each point in the EFT parameter

### 2015-12-31 paper-arxiv-v1/sec-intro.tex
Added v2 of paper in repo

--- 2015-12-23 paper/sec-intro.tex
@@
 of the HL-LHC, $\mathcal{L}=3$ ab$^{-1}$,
-and should rely on the combination of all relevant final states.
+and should rely on the combination of different final states.
+%
+The interplay between  kinematic
+distributions for the
+extraction of $\lambda$ from the measured
+cross-sections, and the role of the associated theoretical
+uncertainties, have been intensely scrutinized
+recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
+  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
+%
 
@@
 and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
-%
-The interplay between  kinematic
-distributions for the
-extraction of $\lambda$ from the measured
-cross-sections, and the role of the associated theoretical
-uncertainties, have been intensely scrutinized
-recently~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
-  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
 %
@@
 $t\bar{t}$ are included, however the
-reducible components, in particular as $bbjj$ and
+reducible components, in particular $bbjj$ and
 $jjjj$, are neglected.
@@
 %
- Our strategy is based upon a a combination of traditional cut-based
+ Our strategy is based upon a combination of traditional cut-based
  methods and multivariate analysis (MVA).
@@
   We also assess the robustness of our analysis strategy in
-  an environment with high pile-up (PU).
+  an environment with high pileup (PU).
   %
@@
 final state
-alone should allow for the discovery of double Higgs production
+alone should allow for the observation of double Higgs production
   at the HL-LHC.
   %
-  We also find that, provided the contamination from light and charm jet
-  mis-identification is reduced, the observation of Higgs pairs
-  in this final state may be within reach already at Run II with
-  $\mathcal{L}=300$ fb$^{-1}$.
 

### 2015-12-31 paper-arxiv-v1/sec-mcsamples.tex
Added v2 of paper in repo

--- 2015-12-15 paper/sec-mcsamples.tex
@@
 the recently available functionalities
-for the calculation of loop-induced processes
-in {\tt MadGraph5\_aMC@NLO}~\cite{Hirschi:2015iia}.
+for the calculation of loop-induced processes~\cite{Hirschi:2015iia}
+in {\tt MadGraph5\_aMC@NLO}.
 %
@@
 %
-For the $4b$ and $2b2j$ samples NLO/LO $K$-factors of 1.6 and 1.3
-respectively have been determined
-using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
-%
 For the $4j$ sample, we rescale the LO cross-section
@@
 an NLO/LO $K$-factor of 0.6.
+%
+For the $4b$ and $2b2j$ samples NLO/LO $K$-factors of 1.6 and 1.3
+respectively have been determined
+using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
 %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[h]
@@
 \hline
-$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 1M & $1.7\cdot10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
+$pp \to hh\to 4b$ &  {\tt MadGraph5\_aMC@NLO} & 1M & $6.2\cdot10^{-3}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
 \hline
 \hline
-$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.1 \cdot10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
-$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.7 \cdot 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
-$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.7\cdot 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
-$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.5\cdot 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
+$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA} & 3M &$1.1 \cdot10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
+$pp \to b\bar{b}jj$ &  {\tt SHERPA} & 3M & $2.7 \cdot 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
+$pp \to jjjj$ &  {\tt SHERPA} & 3M  & $9.7\cdot 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
+$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA} & 3M & $2.5\cdot 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
 \hline
@@
   Carlo samples used in this work.
-  %
-  For top quark production, only the hadronic final state is generated.
   %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 and angular resolutions which directly
-degrade the reconstruction of important kinematical variables, such as
+degrade the reconstruction of important kinematic variables, such as
 the invariant mass of the Higgs candidates.
@@
 the $\lp \eta,\phi\rp$ plane is divided into regions of
-$\Delta \eta \times \Delta \phi=0.1$, and each final state particle
+$\Delta \eta \times \Delta \phi=0.1\times 0.1$,
+and each final state particle
 which falls in each of these cells is set to the same $\eta$
@@
 as discussed in Sect.~\ref{sec:pileup}.
-
-%

### 2015-12-31 paper-arxiv-v2/sec-mva.tex
Added v2 of paper in repo

--- 2015-12-23 paper/sec-mva.tex
@@
 
-At the end of the cut-based analysis,
+At the end of the loose cut-based analysis,
 by combining the three event topologies,
-we obtain a signal significance of $S/\sqrt{B}\simeq 1.8~(3.5)$
+we obtain a signal significance of $S/\sqrt{B}\simeq 0.8~(1.4)$
 with all backgrounds (only QCD $4b$) considered.
@@
  can be enhanced when the cut-based analysis
- is complemented by a multivariate analysis.
+ is complemented by multivariate techniques.
 %
- Multivariate techniques are a mature tool
+ These are by now a mature tool
  in high-energy physics data analysis, opening
@@
 
-%
 The specific type of  MVA that we use to
@@
   The color code in the neuron connections (the weights) is a heat map obtained
-  at the end of the GA training,
+  at the end of the Genetic Algorithms training,
   with red indicating larger values and black indicating smaller values.
@@
 
- \subsection{Input kinematical variables}
+ \subsection{Input kinematic variables}
  \label{sec:input}
@@
 should not degrade
-the classification power of the MVA, aside from making the GA
-minimization somewhat less efficient.
+the classification power of the MVA.
 
@@
 First of all, in Fig.~\ref{fig:nnresponse} we show the distribution of
-the ANN output at the end of the GA minimization, for the exclusive
+the ANN output at the end of the GA minimization,
+separately for the
 boosted, intermediate and resolved categories.
@@
 %
-The performance of the MVA discrimination is similar, although slightly worse in the intermediate
+The performance of the MVA discrimination is similar,
+although slightly worse, in the intermediate
 and resolved categories.
-%
+
 The results for the signal selection efficiency and the 
@@
 and intermediate categories, consistent with the distributions of
-the ANN outputs from
+the ANN outputs in
 Fig.~\ref{fig:nnresponse}.
@@
 
-It is important to verify for each value of
+It is useful to estimate, for each value of
 the cut in the ANN output $y_{\rm cut}$, how many
-signal and background events are expected at the HL-LHC,
-with an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
+signal and background events are expected at the HL-LHC
+with $\mathcal{L}=3$ ab$^{-1}$.
 %
@@
 We observe that
-in the boosted category, for a value $y_{\rm cut}\simeq 0.8$
-we end up with 800 signal events and around $2\cdot 10^4$ background
+in the boosted category, for a value $y_{\rm cut}\simeq 0.9$
+we end up with around 300 signal events and $10^4$ background
 events.
@@
 Similar results are obtained in the intermediate and resolved
-categories: in the former we find 700 ($6\cdot 10^3$) signal (background)
-events for $y_{\rm cut}\simeq 0.8$, and in the latter
-1300 ($8\cdot 10^4$) signal (background) events for
-$y_{\rm cut}\simeq 0.65$.
+categories: in the former we find 130 ($3\cdot 10^3$) signal (background)
+events for $y_{\rm cut}\simeq 0.85$ (0.60), and in the latter
+630 ($10^5$) signal (background) events for
+$y_{\rm cut}\simeq 0.6$.
 %
-Note that the MVA achieves a very substantial background suppression
+Therefore, the MVA achieves a
+substantial background suppression
 with only a
@@
 A useful property of MVAs such as the one used in our
-analysis,
+analysis
 is that they can provide direct  physical insight about which of the
-input variables contribute the most to the separation between
+input variables contribute to the separation between
 signal and background.
@@
 In the case of ANNs, this can be quantified by computing the sum
-of the absolute value of all the weights connected to a given
+of the absolute values of all the weights connected to a given
 input neuron $i$, that is
@@
 discrimination using the MVA.
+%
+We note however
+that the estimate provided
+by Eq.~(\ref{eq:totweight}) is necessarily qualitative.
 
@@
 variables of the three categories, using the
-notation for the various kinematic variables
+notation for the kinematic variables
 as in Sect.~\ref{sec:input}.
-%
-% The important information
-% is contained in the relative strengths of the total associated weight
-% for each of the input variables.
 %
@@
 a higher discrimination power
-are the $p_T$ of the two reconstructed Higgs candidates and
-their invariant masses $m_{h1}$ and $m_{h2}$.
+are the transverse momentum of the two reconstructed Higgs candidates and
+their invariant masses.
 %
@@
 for $y_{\rm cut}=0$ correspond to those at
-the end of the cut-based analysis.
+the end of the loose cut-based analysis.
 %
@@
 uncertainties in the background determination to
-be at the same level of a few percent.
+be at most of a similar size.
 
-We now have all the
-information needed to determine a suitable
-value of the MVA output cut $y_{\rm cut}$ in each
-of the three categories.
 %
-These values can be determined from the maximisation of $S/\sqrt{B}$,
+The optimal value of the cut in the
+ANN output, $y_{\rm cut}$,  can be determined from the maximisation of $S/\sqrt{B}$,
 ensuring that the number of signal events $N_{\rm ev}$
@@
 %
-In  addition we require
+In  addition, we require
 that the number of MC events used to define the signal
@@
 %
-In Table~\ref{table:cutflowMVA} we quote
-the value of the optimal ANN output
-cut in each category,
+In Table~\ref{table:cutflowMVA} we quote, for the optimal
+value of $y_{\rm cut}$
+in each category,
 the number of signal and background events $N_{\rm ev}$ expected
-at the HL-LHC as well as $S/\sqrt{B}$ and $S/B$.
+at the HL-LHC, as well as $S/\sqrt{B}$ and $S/B$.
 %
-For reference, we also include the results at the end of
-the cut-based
-analysis.
+For completeness, we also include the corresponding
+pre-MVA results.
 %
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \hline
-    \multicolumn{6}{|c|}{No PU} \\
+    \multicolumn{6}{|c|}{HL-LHC, no PU} \\
     \hline
@@
     \hline
-    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1070 & $7.6\cdot 10^5$  & 1.2  & $1.4\cdot 10^{-3}$  \\
-    &  $y_{\rm cut}=0.82$ & 790  & $2.2\cdot 10^4$   & 5.4  & 0.03 \\
+    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 440 & $7.6\cdot 10^5$  & 0.5  & $6\cdot 10^{-4}$  \\
+    &  $y_{\rm cut}=0.90$ & 290  & $1.2\cdot 10^4$   & 2.7  & 0.03 \\
     \hline
     \hline
-    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  & 670   & $5.3\cdot 10^5$
-    & 0.9 & $1.2\cdot 10^{-3}$ \\
-    &  $y_{\rm cut}=0.80$ & 360  & $5.5\cdot 10^3$  & 4.8 & 0.06\\
+    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  & 280   & $5.3\cdot 10^5$
+    & 0.4 & $5\cdot 10^{-4}$ \\
+    &  $y_{\rm cut}=0.85$ & 130  & $3.1\cdot 10^3$  & 2.3 & 0.04\\
     \hline
     \hline
-      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  & 3700 &  $1.5\cdot 10^{7}$ &  1.0 &$3\cdot 10^{-4}$ \\
-    &  $y_{\rm cut}=0.65$ & 1300  & $8.3\cdot 10^{4}$ & 4.5 & 0.01 \\
+      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  & 1500 &  $1.5\cdot 10^{7}$ &  0.4 &$1\cdot 10^{-4}$ \\
+    &  $y_{\rm cut}=0.60$ & 630  & $1.1\cdot 10^{5}$ & 1.9 & 0.01 \\
     \hline
@@
     corresponding
-    pre-MVA results $y_{\rm cut}=0$.
+    pre-MVA results ($y_{\rm cut}=0$).
     %
     We quote the number of signal and
-    background events
-    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$,
+    background events expected for $\mathcal{L}=3$ ab$^{-1}$,
     the signal significance $S/\sqrt{B}$ and
@@
     %
-    The pre-MVA results ($y_{\rm cut}=0$) corresponds to row C2 in
+    The pre-MVA results correspond to row C2 in
     Table~\ref{tab:cutflow_noPU_1}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 From Table~\ref{table:cutflowMVA} we see that
-after the application of the MVA, 
+following the application of the MVA, 
 the signal significance in the boosted category increases
-from 1.2 to 5.4, with $S/B$ increasing from $0.14\%$ to $3.4\%$,
-with almost 800 signal events expected at the HL-LHC.
+from 0.5 to 2.7, with $S/B$ increasing from $0.06\%$ to $3\%$.
 %
 For the intermediate and resolved categories, $S/\sqrt{B}$
-increases from 0.9 and 1.0 to 4.8 and 4.5, with
+increases from 0.4 to 2.3 and 1.9 respectively, with
 the signal over background ratio raising from
-$0.12\%$ and $0.03\%$ to 6\% and 1\%, respectively.
+$0.05\%$ and $0.01\%$ to 4\% and 1\%.
 %
-The overall combined significance is thus $S\sqrt{B}\simeq 8$,
-well above the threshold for discovery.
+Combining the three categories, taking into
+account all background components, we obtain the overall signal
+significance:
+\be
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
+\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
+\ee
+%
+The signal significance for
+$\mathcal{L}=3$ ab$^{-1}$
+is thus
+well above the threshold for the observation of Higgs
+pair production.
 %
@@
 which will affect the description of the various
-kinematical distributions used as input to the MVA,
+kinematic distributions used as input to the MVA,
 it is essential to quantify the robustness of these
 results
-in a realistic environment including the effects of PU.
+in a realistic environment including the effects of
+significant PU.
 
@@
 %
-The cut-based analysis and the subsequent
+The loose cut-based analysis and the subsequent
 MVA optimization have been performed using the same
@@
 %
-In Table~\ref{table:cutflowMVA_PU} we provide the results
-  at the end of the cut-based analysis,
-  for the case with $\la n_{\rm PU}\ra=80$ with SK+Trim
-  subtraction,
-  as well as the post-MVA results for the
-  corresponding optimal values of $y_{\rm cut}$.
+In Table~\ref{tab:cutflow_PU80_1}
+we provide the pre-MVA cut flow in the case of PU80,
+the corresponding version without PU being
+Table~\ref{tab:cutflow_noPU_1}.
 %
-  Additionally we quote in
-  both cases the number of signal and
+The interplay between the signal cross-sections and the various
+background components is qualitatively unchanged as compared
+to the no PU case.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[t]
+  \centering
+  \scriptsize
+      \input{table_PU80.tex}
+    \caption{\small Same as Table~\ref{tab:cutflow_noPU_1},
+now for the case
+    of PU80+SK+Trim.
+ \label{tab:cutflow_PU80_1}}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Table~\ref{table:cutflowMVA_PU} we compare the results
+for the PU80+SK+Trim case between
+  the pre-MVA loose cut-based analysis and
+  the post-MVA results for the
+  optimal values of the ANN output cut $y_{\rm cut}$.
+  %
+  As in Table~\ref{table:cutflowMVA}, 
+  we also quote 
+   the number of signal and
     total background events expected
-    at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
-    and the values of $S/\sqrt{B}$ and $S/B$
-
+   for $\mathcal{L}=3$ ab$^{-1}$
+    and the values of $S/\sqrt{B}$ and $S/B$.
+%
 We observe that the pre-MVA 
 signal significance is close
-to the case without PU for the three categories.
+to the results of the simulations
+without PU for the three categories.
 %
-We now find values for $S/\sqrt{B}$ of 0.9, 0.7 and 1.5, in the resolved,
+We now find values for $S/\sqrt{B}$ of 0.4, 0.3 and 0.6, in the resolved,
 intermediate and boosted categories, respectively, to be compared
-with the corresponding values without PU, namely 1.0, 0.9 and 1.0.
+with the corresponding values without PU, namely 0.4, 0.4 and 0.5.
 %
 The number of selected
-signal events in each category, at the
-end of the cut-based analysis, is only mildly affected
+signal events in each category at the
+end of the cut-based analysis is only mildly affected
 by PU.
@@
 resolved, intermediate and boosted
-categories increases to 4.6, 4.1 and 3.7 respectively,
+categories increases to 2.0, 1.9 and 1.5 respectively,
 to be compared with the corresponding values
-without PU, namely 4.5, 4.8 and 5.4.
+without PU, namely 1.9, 2.3 and 2.7.
 %
@@
 a moderate degradation of the boosted and intermediate categories,
-while the resolved category is largely unchanged.
+specially for the former,
+while the resolved category is largely unchanged.\footnote{
+  The impact of PU on the  separate significance of
+  the three categories exhibits some
+  dependence on the specific choice for $n_{\rm PU}$  and on the settings
+  of the PU subtraction strategy.
+  %
+  We find however that the
+  overall signal significance from combining the three
+  categories is similar in the $n_{\rm PU}=80$ and
+  $n_{\rm PU}=150$ cases.
+}
 %
@@
 to the MVA, the
-signal over background ratio is increased from 0.02\%, 0.08\% and
-0.2\% up to 1\%, 4\% and 2\% in the resolved, intermediate
+signal over background ratio is increased from 0.007\%, 0.03\% and
+0.1\% up to 1\%, 3\% and 1\% in the resolved, intermediate
 and boosted categories respectively.
@@
 requiring a careful extraction of the QCD
-background from the data, it is certainty within reach.
+background from the data, it should be within reach.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \hline
-     \multicolumn{6}{|c|}{$\la n_{\rm PU}\ra=80$+SK+Trim} \\
+     \multicolumn{6}{|c|}{HL-LHC, PU80+SK+Trim} \\
      \hline
@@
     \hline
-    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 1000   &  $4.5\cdot 10^5$ & 1.5   & $2\cdot 10^{-3}$  \\
-    &  $y_{\rm cut}=0.7$ &  780  & $4.5\cdot 10^4$  & 3.7    & 0.02  \\
+    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  & 410   &  $4.5\cdot 10^5$ & 0.6   & $ 10^{-3}$  \\
+    &  $y_{\rm cut}=0.8$ &  290  & $3.7\cdot 10^4$  & 1.5    & 0.01  \\
     \hline
     \hline
-    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  630  & $8.2\cdot 10^5$    & 0.7    &
-     $8\cdot 10^{-4}$ \\
-    &  $y_{\rm cut}=0.7$ & 380 & $8.5\cdot 10^3$  &  4.1   & 0.04 \\
+    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &  260  & $7.7\cdot 10^5$    & 0.3    &
+     $3\cdot 10^{-4}$ \\
+    &  $y_{\rm cut}=0.75$ & 140 & $5.6\cdot 10^3$  &  1.9   & 0.03 \\
     \hline
     \hline
-    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  4500  & $2.7\cdot 10^7$
-    & 0.9    &  $2\cdot 10^{-4}$  \\
-    &  $y_{\rm cut}=0.5$ & 2000  & $2.1\cdot 10^5$  &  4.6   & 0.01  \\
+    \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  1800  & $2.7\cdot 10^7$
+    & 0.4    &  $7\cdot 10^{-5}$  \\
+    &  $y_{\rm cut}=0.60$ & 640  & $1.0\cdot 10^5$  &  2.0   & 0.01  \\
     \hline
@@
   \caption{\small Same as Table~\ref{table:cutflowMVA}, now for the case
-    of PU+SK+Trim, with $\la n_{\rm PU}\ra=80$.
+    of PU80+SK+Trim.
         \label{table:cutflowMVA_PU}
@@
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \includegraphics[width=0.49\textwidth]{plots/nev2_SKPU80.pdf}
-\caption{\small Same as Fig.~\ref{fig:nev2} in the
-case of events with PU, for
-$\la n_{\rm PU}\ra=80$ with SK+Trim.
-}
-\label{fig:nev2_PU}
+\caption{\small Same as Fig.~\ref{fig:nev2}
+ for
+ the PU80+SK+Trim case.
+\label{fig:nev2_PU}}
 \end{center}
@@
 we show the number of signal and background events that
-are expected at the HL-LHC as a function of
-$y_{\rm cut}$, as well as the corresponding ROC curve.
+are expected for $\mathcal{L}=3$ ab$^{-1}$
+as a function of
+$y_{\rm cut}$, together with the corresponding ROC curve.
 %
@@
 As can be seen, the MVA-driven enhancement remains robust in the
-presence of PU.
-%
-While
-there is some degradation as compared to the case
-without PU,
-it is still possible to
-achieve a signal significance of
- $S/\sqrt{B}$ between 3.0 and 4.5, depending on the
-specific choice of $y_{\rm cut}$,
-separately for the three categories.
+presence of PU, with $S/\sqrt{B}$ only moderately degraded.
 %
@@
 in the case without PU also hold when the analysis
-is performed in an environment including pileup.
+is performed in a high-PU environment.
 %
@@
 of the patch length $a$ in {\tt SoftKiller}
-and of the $p_T$ threshold in jet trimming.
+or the $p_T$ threshold during jet trimming,
 we believe that
-there could be still room for further  improvement.
+there should be still room for further improvement.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \caption{\small 
-Same as Fig.~\ref{fig:sb_mva} in the
-case of events with PU, for
-$\la n_{\rm PU}\ra=80$ with SK+Trim.
+  Same as Fig.~\ref{fig:sb_mva} for
+  the PU80+SK+Trim case.
 }
@@
 carry the highest discrimination power
-in the case of PU,
+in the case of PU, by means of
+Eq.~(\ref{eq:totweight}),
 and compare this with the corresponding
-results without PU, by means of
-Eq.~(\ref{eq:totweight}).
+results without PU shown in Fig.~\ref{fig:nnweights}.
 %
-The 
-results for the resolved and boosted categories are shown
-on Fig.~\ref{fig:nnweights_PU}.
-%
-As we can see by comparing with Fig.~\ref{fig:nnweights}, 
+We have verified that 
 the relative weight of the different input variables to the MVA
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\begin{center}
-\includegraphics[width=0.49\textwidth]{plots/res_wgthist_SKPU80.pdf}
-\includegraphics[width=0.49\textwidth]{plots/bst_wgthist_SKPU80.pdf}
-\vspace{-0.5cm}
-\caption{\small
-Same as Fig.~\ref{fig:nnweights} in the
-case of events with PU, for
-$\la n_{\rm PU}\ra=80$ with SK+Trim.
-}
-\label{fig:nnweights_PU}
-\end{center}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-In Table~\ref{table:cutflowMVA_fakes} we compare
-the  number of background events  expected for
-$\mathcal{L}=3$ ab$^{-1}$,
-after the MVA is applied, both
+In Table~\ref{table:cutflowMVA_fakes} we provide
+the post-MVA number of signal and background events  expected for
+$\mathcal{L}=3$ ab$^{-1}$.
+%
+For the backgrounds, we quote
+both
 the total number, $N_{\rm ev}^{\rm tot}$,
-and those from the  QCD $4b$ component
-$N_{\rm ev}^{\rm 4b}$, for the analyses without and
-with PU.
+and the  QCD $4b$ component only,
+$N_{\rm ev}^{\rm 4b}$.
 %
- We also quote the corresponding values of the signal 
+We quote results for the no PU and PU80+SK+Trim cases.
+%
+ We also quote in each case the corresponding values for the signal 
     significance and the signal over background ratio.
     %
-    Note that the MVA has been trained to the total background sample,
+    Note that the MVA is always trained to the inclusive background sample,
     though differences
-    in the kinematic distributions of the $4b$ and $2b2j$ processes are small,
+    in the kinematic distributions of the $4b$ and $2b2j$ processes are
+    moderate,
     see Fig.~\ref{fig:histoBack}.
     %
-    The largest improvement from eliminating the contamination
-    from light and charm jet mis-identification arises
-    for the boosted category, the one where the relative size of the
-    $2b2j$ over the $4b$ background components is higher
-    (see Table~\ref{tab:cutflow_noPU_1}), where
-    $S/\sqrt{B}$ increases from 3.7 to 5.9.
+    From Table~\ref{table:cutflowMVA_fakes} one observes that
+    all categories exhibit
+    a marked improvement from eliminating the contamination
+    from light and charm jet mis-identification.
+    %
+    For instance, in the intermediate category,
+    $S/\sqrt{B}$ increases from 2.3 to 3.3 (1.9 to 2.9)
+    in the no PU (PU80) case, with similar improvements in the
+    resolved and boosted categories.
     %
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[h]
+\begin{table}[t]
   \centering
-  \small
-  \begin{tabular}{|c|c|c|c||c|c||c|c|}
+  \scriptsize
+  \begin{tabular}{|c|c|c|c|c||c|c||c|c|}
         \hline
-        Category  &    &  $N_{\rm ev}^{\rm tot}$  &  $N_{\rm ev}^{\rm 4b}$   &
+        Category  &  &  signal  &  \multicolumn{2}{c||}{background}     &
         $S/\sqrt{B_{\rm tot}}$ & $S/\sqrt{B_{\rm 4b}}$  
         &  $S/B_{\rm tot}$ & $S/B_{\rm 4b}$\\
+         &  &  $N_{\rm ev}$  &  $N_{\rm ev}^{\rm tot}$  &  $N_{\rm ev}^{\rm 4b}$   &
+         &     &   &  \\
     \hline
     \hline
-    \multirow{2}{*}{Boosted} &  no PU  & $2.2\cdot 10^4$  & $1.5\cdot 10^4$     & 
-      5.4 &  6.5 & 0.03 & 0.05 \\
-    & PU+SK &  $4.5\cdot 10^4$ &  $1.7\cdot 10^4$    &  3.7  & 5.9 &  0.02 & 0.04 \\
+    \multirow{2}{*}{Boosted} &  no PU  & 290  & $1.2\cdot 10^4$  &  $8.0\cdot 10^3$    & 
+      2.7 &  3.2  & 0.03 & 0.04 \\
+      & PU80+SK+Trim & 290  &$3.7\cdot 10^4$ & $1.2\cdot 10^4$     &  1.5  & 2.7 &  0.01 & 0.02   \\
     \hline
     \hline
-    \multirow{2}{*}{Intermediate} &  no PU   & $4.5\cdot 10^3$  & $2.0\cdot 10^3$    &
-    4.8  &  5.3 &  0.06  &  0.08 \\
-    & PU+SK+Trim  & $8.5\cdot 10^3$   &  $4.6\cdot 10^3$  & 4.1  & 5.6 & 0.04 & 0.08 \\
+    \multirow{2}{*}{Intermediate} &  no PU   & 130   & $3.1\cdot 10^3$  & $1.5\cdot 10^3$    &
+    2.3  & 3.3  &  0.04  & 0.08   \\
+    & PU80+SK+Trim & 140 & $5.6\cdot 10^3$   & $2.4\cdot 10^3$   & 1.9  & 2.9  & 0.03 & 0.06  \\
     \hline
     \hline
-    \multirow{2}{*}{Resolved} &   no PU  & $8.1\cdot 10^4$   &
-    $4.5\cdot 10^4$
-    & 4.5  & 6.6  & 0.01 & 0.03 \\
-    & PU+SK+Trim  &  $2.1\cdot 10^5$   &   $1.1\cdot 10^5$ & 4.6    & 6.2  & 0.01 & 0.02 \\
+    \multirow{2}{*}{Resolved} &   no PU  & 630 & $1.1\cdot 10^5$   & $5.8\cdot 10^4$
+    & 1.9  & 2.7  & 0.01 & 0.01 \\
+    & PU80+SK & 640  & $1.0\cdot 10^5$   & $7.0\cdot 10^4$   & 2.0 & 2.6  & 0.01 & 0.01 \\
+    \hline
+    \hline
+    \multirow{2}{*}{\bf Combined} &   no PU  &  \multicolumn{3}{c||}{} 
+    &  4.0 & 5.3  &   \multicolumn{2}{c|}{}  \\
+    & PU80+SK+Trim &    \multicolumn{3}{c||}{}    & 3.1  & 4.7  &  \multicolumn{2}{c|}{}  \\
     \hline
       \end{tabular}
-  \caption{\small Post-MVA number of background events
-    expected at the HL-LHC, comparing the total number, $N_{\rm ev}^{\rm tot}$,
-    with those from the QCD $4b$ background
-    component only, $N_{\rm ev}^{\rm 4b}$.
+  \caption{\small Post-MVA number of signal and background events
+    with  $\mathcal{L}=3$ ab$^{-1}$.
+    %
+    For the backgrounds, both the total number, $N_{\rm ev}^{\rm tot}$,
+    and the  $4b$ 
+    component only, $N_{\rm ev}^{\rm 4b}$, are shown.
      %
     Also provided are the values of the signal 
-    significance and signal over background ratios in each case
-    for $\mathcal{L}=3$ ab$^{-1}$.
+    significance and the signal over background ratio,
+    both separated in categories and for their combination.
+    %
+    We quote the results without PU and for PU80+SK+Trim.
          \label{table:cutflowMVA_fakes}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Combining the three categories, taking into
-account all background components, we obtain the overall signal
-significance:
+In Table~\ref{table:cutflowMVA_fakes} we also provide
+the results for $S/\sqrt{B}$ obtained by
+combining the three categories.
+%
+Taking into
+account all background components, we obtain for the case
+of $n_{\rm PU}=80$
+an overall signal
+significance of
 \be
-\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 7.2~(2.3) \, ,\quad
+\lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 3.1~(1.0) \, ,\quad
 \mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
@@
 %
-indicating  that the measurement of
+indicating  that a measurement of
 Higgs pair production in the $b\bar{b}b\bar{b}$ final state at the HL-LHC
 should be 
-well above the threshold for discovery.
+above the threshold for observation, even when realistic PU conditions
+are accounted for.
 %
-Interestingly, such a measurement might also be within reach
-for the total integrated luminosity expected by the end of Run II.
+A similar signal significance is obtained in the case of
+$n_{\rm PU}=150$.
 %
@@
     the only relevant background would be the irreducible QCD $4b$ component,
-    we obtain
+    one obtains instead
     \be
-\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 10.2~(3.2) \, ,\quad
-\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, ,
+\lp \frac{S}{\sqrt{B_{\rm 4b}}}\rp_{\rm tot} \simeq 4.7~(1.5) \, ,\quad
+\mathcal{L}=3000~(300)\,{\rm fb}^{-1}\, .
 \ee
-Therefore, observation of Higgs pair production
-in the $b\bar{b}b\bar{b}$ final state might be possible
-already by the end of Run II, provided
+%
+Therefore, a measurement of Higgs pair production
+in the $b\bar{b}b\bar{b}$ final state at the
+HL-LHC  might be even above the threshold for discovery, provided
 the effects due to mis-identification of light and charm jets as
@@
 %
-The smaller value of $\la n_{\rm PU}\ra$ expected
-at Run II as compared
-to the HL-LHC environment should be beneficial in this respect.

### 2015-12-31 paper-arxiv-v2/paperscripts/getCutFlows.py

@@ -1,0 +1,140 @@
+#!/usr/bin/python2.7
+
+import os
+import sys
+import math
+regimes = ['res', 'inter','boost']
+folder = "../../paper/plotdata/results_noPU/"
+print folder
+
+recursive_folders = ['diHiggs', 'background', 'SHERPA_QCD4b', 'SHERPA_QCD2b2j', 'SHERPA_QCD4j', 'SHERPA_QCDttbar']
+file_types = ['res', 'inter', 'boost']
+
+Cnum = ['C0', 'C1a', 'C1b', 'C1c', 'C1d', 'C1e', 'C2' ]
+
+new_data = {}
+luminosity = 3000.0 # used for S/sqrt(B) only.
+
+for type in file_types:
+    new_data[type] = []
+
+for k, recursive_folder in enumerate(recursive_folders):
+
+    for j, file_type in enumerate(file_types):
+
+        filename = 'histo_CF_' + file_type + '.dat'
+        filePath = os.path.join(folder,recursive_folder,filename)
+        print(filePath)
+
+        with open(filePath) as f:
+
+            Cutflow = f.readlines()[4:11]
+
+            for l, line in enumerate(Cutflow):
+                if k == 0:
+                    new_line = []
+                    split_line = line.split('\t')
+                    new_line.append(float(split_line[0]))
+                    new_line.append(split_line[2])           
+                    new_data[file_type].append(new_line)
+                else:
+                    new_data[file_type][l].append(line.split('\t')[2])
+
+for file_type in file_types:
+    list_of_rows = new_data[file_type]
+    outfile = 'cutflow_' + file_type + '.dat'
+    with open(outfile, 'w') as f:
+        # generate header line
+        f.write(file_type+'\t')
+        for recursive_folder in recursive_folders:
+            f.write(recursive_folder+'\t')
+        f.write('\n')
+        for h, row in enumerate(list_of_rows):
+            for i, item in enumerate(row):
+                if i == 0:
+                    f.write(Cnum[int(item)])
+                else:
+                    f.write(str(item))
+                    if h>0:
+                        if float(list_of_rows[h-1][i]) != 0:
+                            cuteff = 100*float(item)/float(list_of_rows[h-1][i])
+                        else:
+                            cuteff = 0
+                        f.write(' ')
+                        f.write('(%.2f' % cuteff)
+                        f.write('%)')
+                if i == len(row) - 1:
+                    f.write('\n')
+                else:
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_C2_h0_bst_comp_back.py

@@ -1,0 +1,131 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "C2_h0_bst_comp_back"
+
+linestyles = [ 'solid', 'dashed','solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_C2_fj1_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/background/histo_C2_fj1_boost_C1e.dat")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+
+# Axis labels
+xLabel = r"ECF ratio $C_{2}^{(\beta)}$ in leading Higgs candidate"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'b', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,0.7])
+ax.set_ylim([0.0001,5])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_D2_h0_bst_comp_back.py

@@ -1,0 +1,137 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "D2_h0_bst_comp_back"
+
+linestyles = [ 'solid', 'dashed','solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_D2_fj1_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_D2_fj1_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_D2_fj1_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/background/histo_D2_fj1_boost_C1e.dat")
+
+# Plot labels
+plotnames.append("Signal, no PU")
+plotnames.append("Signal, $n_{PU}=80$ + SK")
+plotnames.append("Background, no PU")
+plotnames.append("Background, $n_{PU}=80$ + SK")
+
+# Axis labels
+xLabel = r"Energy Correlation Ratio $D_2^{(\beta)}$ in leading Higgs candidate"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'r', 'b', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,1])
+ax.set_ylim([0,4.0])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_m_H0_bst_comp.py

@@ -1,0 +1,132 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_H0_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H0_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_H0_boost_C2.dat")
+
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK")
+
+# Axis labels
+xLabel = "Leading Higgs Candidate Invariant Mass (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([90,170])
+ax.set_ylim([1e-3,0.2])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_m_H0_res_noPU.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_H0_res_C1d_noPU"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H0_res_C1d.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_m_H0_res_C1d.dat")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+# Axis labels
+xLabel = "Invariant Mass of Leading Higgs Candidate (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([50,180])
+ax.set_ylim([1e-4,0.035])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_m_H1_bst_comp.py

@@ -1,0 +1,130 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_H1_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_m_H1_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_H1_boost_C2.dat")
+
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"$\langle n_{PU}\rangle =80$ + SK")
+
+# Axis labels
+xLabel = "Sub-Leading Higgs Candidate Invariant Mass (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([90,170])
+ax.set_ylim([1e-3,0.2])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_ptH0_bst_comp.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_H0_C2_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_H0_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_pt_H0_boost_C2.dat")
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"PU80+SK+Trim")
+
+# Axis labels
+xLabel = "Leading Higgs Candidate $p_{T}$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,700])
+ax.set_ylim([1e-4,0.05])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_pt_H0_bst_noPU.py

@@ -1,0 +1,130 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_H0_bst_C1d_noPU"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_H0_boost_C1d.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_pt_H0_boost_C1d.dat")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+# Axis labels
+xLabel = "Leading Higgs Candidate $p^{h}_T$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([190,600])
+ax.set_ylim([1e-4,0.02])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotHist_pt_subleadSJ_fj1_bst_comp.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_subleadSJ_fj1_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_subleadSJ_fj1_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_pt_subleadSJ_fj1_boost_C2.dat")
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"$\langle n_{PU}\rangle=80$ + SK")
+
+# Axis labels
+xLabel = "$p_{T}$ of Sub-Leading AKT03 Subjet in Leading Higgs Candidate (GeV)"
+yLabel = "A. U."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,700])
+ax.set_ylim([1e-4,0.05])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotMVAdat_PU150.py

@@ -1,0 +1,236 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../plotdata/results_SK_PU150/MVA/nn_13X5X3X1_50000-Gen_resNTuple.dat",
+            "../plotdata/results_SK_PU150/MVA/nn_17X5X3X1_50000-Gen_intNTuple.dat",
+            "../plotdata/results_SK_PU150/MVA/nn_21X5X3X1_50000-Gen_bstNTuple.dat"]
+
+datanames=[ "Resolved","Intermediate","Boosted"]
+titlenames=[ r"Resolved Category,  $\langle n_{PU}\rangle =150$+SK",
+             r"Intermediate Category,  $\langle n_{PU}\rangle =150$+SK",\
+             r"Boosted Category,  $\langle n_{PU}\rangle=150$+SK"]
+
+datanamessignal=[ "Signal Res","Signal Int","Signal Boost"]
+datanamesback=[ "Background Res","Background Int","Background Boost"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_SKPU150"  # Histograms for discriminant
+ROCout = "roc_SKPU8150"	  # ROC curve
+SBout = "sb_SKPU150"	  # S/B curve
+SSBout = "ssb_SKPU150"	  # S/Sqrt(B) curve
+NeVout = "nev_SKPU150"	  # Number of events (twin axes)
+NeV2out = "nev2_SKPU150"  # Number of events (single axis)
+
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background,title):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotMVAdat_comp_int.py

@@ -1,0 +1,234 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../plotdata/results_SK_PU80/MVA/nn_16X5X3X1_50000-Gen_SKPU80_int.dat",
+            "../plotdata/results_noPU/MVA/nn_16X5X3X1_50000-Gen_noPU_int.dat"]
+
+datanames=[ "SKPU80_Intermediate","noPU_intermediate"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_comp_int"  # Histograms for discriminant
+ROCout = "roc_comp_int"	  # ROC curve
+SBout = "sb_comp_int"	  # S/B curve
+SSBout = "ssb_comp_int"	  # S/Sqrt(B) curve
+NeVout = "nev_comp_int"	  # Number of events (twin axes)
+NeV2out = "nev2_comp_int"  # Number of events (single axis)
+
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
+	ax.hist(signal, bins, color='r', alpha=0.8, normed=True, label = "Signal",linewidth=2)
+	ax.hist(background, bins, color='b',fill=False, alpha=0.8, edgecolor='b',normed=True, label = "Background",hatch="//",linewidth=2)
+
+	ax.set_ylim([0,10])
+	ax.set_xlabel("ANN Output")
+        ax.set_ylabel("A. U.")
+
+	# Legend
+	legend = ax.legend(fontsize=18, loc='best')
+	legend.get_frame().set_alpha(0.8)
+
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotMVAdat_comp_res.py

@@ -1,0 +1,234 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../plotdata/results_SK_PU80/MVA/nn_12X5X3X1_50000-Gen_SKPU80_res.dat",
+            "../plotdata/results_noPU/MVA/nn_12X5X3X1_50000-Gen_noPU_res.dat"]
+
+datanames=[ "SKPU80_Resolved","noPU_Resolved"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_comp_res"  # Histograms for discriminant
+ROCout = "roc_comp_res"	  # ROC curve
+SBout = "sb_comp_res"	  # S/B curve
+SSBout = "ssb_comp_res"	  # S/Sqrt(B) curve
+NeVout = "nev_comp_res"	  # Number of events (twin axes)
+NeV2out = "nev2_comp_res"  # Number of events (single axis)
+
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
+	ax.hist(signal, bins, color='r', alpha=0.8, normed=True, label = "Signal",linewidth=2)
+	ax.hist(background, bins, color='b',fill=False, alpha=0.8, edgecolor='b',normed=True, label = "Background",hatch="//",linewidth=2)
+
+	ax.set_ylim([0,10])
+	ax.set_xlabel("ANN Output")
+        ax.set_ylabel("A. U.")
+
+	# Legend
+	legend = ax.legend(fontsize=18, loc='best')
+	legend.get_frame().set_alpha(0.8)
+
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/plotNetwork_int_PU.py

@@ -1,0 +1,140 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+import matplotlib.pyplot as plt
+import networkx as nx
+import os
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+import numpy
+import sys
+
+################################ Settings ###################################
+
+# Init data
+datafile = '../plotdata/results_SK_PU80/MVA/nn_17X5X3X1_50000-Gen_SKPU80_int.net'
+dataname = "Intermediate"
+sourcefile = os.path.expanduser(datafile)
+
+archout = "int_nnarch_SKPU80"
+histout = "int_wgthist_SKPU80"
+
+#############################################################################
+
+# Verify paths
+if os.path.exists(sourcefile) == False:
+  	print "Error: source file" + sourcefile + " not found!"
+  	sys.exit()
+
+infile = open(sourcefile, 'rb')
+print "Processing " + sourcefile + " ..."
+
+# Read architecture
+line = infile.readline()
+arch = []
+for ls in line.split():
+	arch.append(int(ls))
+nNodes = sum(arch)
+
+# Read kinematics names
+line = infile.readline()
+kinematics = []
+for ls in line.split():
+	kinematics.append(ls)
+
+# Init graph
+G=nx.Graph()
+
+weights = []
+thresholds = [0]
+
+line = infile.readline()
+for line in infile:
+	iNode = int(line.split()[0])
+	tNode = int(line.split()[1])
+	threshold = float(line.split()[2])
+	weight = abs(float(line.split()[3]))
+
+	weights.append(weight)
+	thresholds.append(threshold)
+
+	# Add the edge
+	G.add_edge(iNode, tNode, wgt = weight )
+	# Add threshold weight
+	G.node[iNode]['bias'] = threshold
+	if tNode < arch[0]:
+		G.node[tNode]['bias'] = 0
+
+	# Init labels
+	G.node[iNode]['label'] = ''
+	if tNode < arch[0]:
+		G.node[tNode]['label'] = tNode
+	else:
+		G.node[tNode]['label'] = ''
+
+# Get input weights
+sumw = []
+for i in xrange(0,arch[0]):
+	G.node[i]['sumw'] = 0
[…]

### 2015-12-31 paper-arxiv-v2/paperscripts/runall.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+for f in *.py; do 
+	echo "Processing $f.."; 
+	python $f
+done
+

### 2016-01-13 paper-arxiv-v2/sec-mva.tex
Added plots with ANN cut

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+It should be emphasized that MVAs such as the ANNs used in this work can always be understood as
+a combined set of correlated cuts.
+%
+Once the ANNs have been trained, it is possible to compare  kinematical distributions after and before the ANN  cut to verify its impact.
+%
+This information would allow in principle to perform a cut-based analysis, without the need of using ANNs,
+and finding similar results.
+%
+To illustrate this,
+in Fig.~\ref{fig:pt_H0_sub0_res_noPU_ANNcut} we show
+the $p_T$ distribution of the leading AKT04 small-$R$ jets in the resolved
+  category, comparing the pre-MVA results ($y_{\rm cut}=0$) with the post-MVA
+  results ($y_{\rm cut}=0.60$) for signal and background  events.
+  %
+  The distributions are not normalized, to better visualize the effect
+  of the MVA cut.
+  %
+  Unsurprisingly, the ANN cut favors the high-$p_T$ region, in a way
+  that the signal and background shapes end up being reasonably similar.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/pt_H0_sub0_res_noPU_ANNcut.pdf}
+\includegraphics[width=0.48\textwidth]{plots/pt_H0_sub0_res_noPU_ANNcut_back.pdf}
+\caption{\small
+  The $p_T$ distribution of the leading AKT04 small-$R$ jets in the resolved
+  category, comparing the pre-MVA results ($y_{\rm cut}=0$) with the post-MVA
+  results ($y_{\rm cut}=0.60$) for signal (left) and background (right plot) events.
+  %
+  In this case the distributions are not normalized, to better visualize the effects
+  of the MVA cut.
+}
+\label{fig:pt_H0_sub0_res_noPU_ANNcut}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Impact of PU in the MVA}

### 2016-01-13 paper-arxiv-v2/paperscripts/plotHist_pt_H0_sub0_res_noPU_ANNcut_back.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_H0_sub0_res_noPU_ANNcut_back"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("histo_pt_H0_sub0_y00_sig0.dat")
+datafiles.append("histo_pt_H0_sub0_y06_sig0.dat")
+
+# Plot labels
+plotnames.append(r"pre-MVA, $y_{cut}=0.0$")
+plotnames.append(r"post-MVA, $y_{cut}=0.6$")
+
+# Axis labels
+xLabel = r"Leading AKT04 $b$-jet $p_T$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = False
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([50,300])
+ax.set_ylim([0.001,1000])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2016-01-13 paper-arxiv-v2/paperscripts/run-ANNcuts.sh

@@ -1,0 +1,8 @@
+rm -rf *.pdf
+
+./plotHist_m_H0_res_noPU_ANNcut.py
+./plotHist_m_H0_res_noPU_ANNcut_back.py
+./plotHist_pt_H0_res_noPU_ANNcut_back.py
+./plotHist_pt_H0_res_noPU_ANNcut.py
+./plotHist_pt_H0_sub0_res_noPU_ANNcut.py
+./plotHist_pt_H0_sub0_res_noPU_ANNcut_back.py

### 2016-01-14 paper-arxiv-v2/sec-mva.tex
Added plots of ANN cut to the paper

--- 2015-12-31 paper-arxiv-v2/sec-mva.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+It should be emphasized that MVAs such as the ANNs used in this work can always be understood as
+a combined set of correlated cuts.
+%
+Once the ANNs have been trained, it is possible to compare  kinematical distributions after and before the ANN  cut to verify its impact.
+%
+This information would allow in principle to perform a cut-based analysis, without the need of using ANNs,
+and finding similar results.
+
+To illustrate this point,
+in Fig.~\ref{fig:pt_H0_sub0_res_noPU_ANNcut} we show
+the $p_T$ distribution of the leading AKT04 small-$R$ jets
+and the invariant mass of reconstructed Higgs candidates in the resolved
+  category, comparing the pre-MVA results ($y_{\rm cut}=0$) with the post-MVA
+  results ($y_{\rm cut}=0.60$) for signal and background  events.
+  %
+  The distributions are not normalized, to better visualize the effect
+  of the MVA cut.
+  %
+  Unsurprisingly, the ANN cut effectively selects events which
+  lead to similar kinematical distributions between signal
+  and background events.
+  %
+  In the case of the small-$R$ jets $p_T$ distribution, the
+  ANN cuts favors the
+  high-$p_T$ region, while for the invariant mass distribution
+  only the region around the Higgs mass peak is selected for
+  background events.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\begin{center}
+\includegraphics[width=0.48\textwidth]{plots/pt_H0_sub0_res_noPU_ANNcut.pdf}
+\includegraphics[width=0.48\textwidth]{plots/pt_H0_sub0_res_noPU_ANNcut_back_4b.pdf}
+\includegraphics[width=0.48\textwidth]{plots/m_H0_res_noPU_ANNcut.pdf}
+\includegraphics[width=0.48\textwidth]{plots/m_H0_res_noPU_ANNcut_back_4b.pdf}
+\caption{\small
+  The $p_T$ distribution of the leading AKT04 small-$R$ jets (upper plots)
+  and
+  the invariant mass of reconstructed Higgs candidates (lower plots) in the resolved
+  category, comparing the pre-MVA results ($y_{\rm cut}=0$) with the post-MVA
+  results ($y_{\rm cut}=0.60$) for signal (left) and background (right plot) events.
+  %
+  In this case the distributions are not normalized, to better visualize the effects
+  of the MVA cut.
+}
+\label{fig:pt_H0_sub0_res_noPU_ANNcut}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Impact of PU in the MVA}

### 2016-01-21 paper-arxiv-v2/HH4b.tex
Revised version of paper

\documentclass[a4paper,11pt]{article}
\pdfoutput=1
%\usepackage{jheppub}
\usepackage{graphicx}% Include figure files
\usepackage{graphics}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{epstopdf}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage[pdftex]{hyperref}
%\usepackage{natbib}
\usepackage{multirow,cite}

\def\bs{\boldsymbol}
\def\del{\partial}

%\def\p{{\boldsymbol p}_{\perp }}
%\def\pb{\bar {\boldsymbol p}_{\perp }}
%\def\pp{{\boldsymbol p}_{\perp }}
\def\p{{\boldsymbol p}}
\def\pb{\bar {\boldsymbol p}}
\def\pp{{\boldsymbol p}}
%\def\q{{\boldsymbol q}_\perp}
\def\q{{\boldsymbol q}}
\def\l{{\boldsymbol l}_\perp}
%\def\k{{\boldsymbol k}_\perp}
\def\k{{\boldsymbol k}}
\def\m{{\boldsymbol m}_\perp}
%\def\x{{\boldsymbol x}_\perp}
\def\x{{\boldsymbol x}}
\def\y{{\boldsymbol y}_\perp}
\def\X{{\boldsymbol X}_\perp}
\def\Y{{\boldsymbol Y}_\perp}
\def\D{{\boldsymbol D}_\perp}
\def\r{{\boldsymbol r}_\perp}
\def\z{{\boldsymbol z}_\perp}
%\def\v{{\boldsymbol v}_\perp}
\def\v{{\boldsymbol v}}
\def\w{{\boldsymbol w}_\perp}
\def\b{{\boldsymbol b}_\perp}
\def\Q{{\boldsymbol Q}_\perp}
\def\M{{\boldsymbol M}_\perp}
%\def\bkappa{{\boldsymbol \kappa}_\perp}
%\def\bbkappa{\bar{\boldsymbol \kappa}_\perp}
\def\bkappa{{\boldsymbol \kappa}}
\def\bbkappa{\bar{\boldsymbol \kappa}}
\def\bnu{{\boldsymbol \nu}_\perp}
\def\V{\hat{\boldsymbol v}_{1\perp}}
\def\K{\hat{\boldsymbol k}_{1\perp}}
\def\bV{\hat{\boldsymbol v}_{2\perp}}
\def\bK{\hat{\boldsymbol k}_{2\perp}}
\def\qqb{{q\bar q}}
\def\sM{{\scriptscriptstyle M}}

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\nn}{\nonumber\\ }
\newcommand{\labe}{\label}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}

%\bibliographystyle{JHEP}

%\textwidth=15.0cm \textheight=23.5cm
\textwidth=16.0cm \textheight=23.0cm 
\topmargin 0cm \oddsidemargin 0cm 
\setlength{\unitlength}{1mm}

\usepackage{url}
\usepackage{hyperref}

\begin{document}

\vspace{-2.0cm}
\begin{flushright}
OUTP-15-14P
\end{flushright}

\begin{center}
  {\Large \bf Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State\\[0.2cm]
    with
  Multivariate Techniques}
\vspace{.7cm}

J. Katharina Behr, Daniela Bortoletto, James A. Frost,
  Nathan P. Hartland, \\Cigdem Issever and Juan Rojo

\vspace{.3cm}
{\it Physics Department, 1 Keble Road, University of Oxford, United Kingdom }

\vspace{1cm}

{\bf \large Abstract}\\
\end{center}
\vspace{0.1cm}
The measurement of Higgs pair production will be a cornerstone of
  the LHC program in the coming years.
  %
  Double Higgs production provides a crucial window upon the mechanism of electroweak
  symmetry breaking and has a unique sensitivity
  to the Higgs trilinear coupling.
  %
  We study the feasibility of a measurement of
  Higgs pair production in the
  $b\bar{b}b\bar{b}$ final state at the LHC.
  %
  Our analysis is based on a combination of traditional cut-based
  methods with state-of-the-art
  multivariate techniques.
  %
  We account for all relevant
  backgrounds, including the contributions from light and charm
  jet mis-identification, which are ultimately comparable in size 
  to the irreducible $4b$ QCD background.
  %
  We demonstrate the robustness of our analysis strategy in
  a high pileup environment.
  %
  For an integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$,
  a signal significance of  $S/\sqrt{B}\simeq 3$ is obtained,
  indicating
  that the $b\bar{b}b\bar{b}$ final state
alone could allow for the observation of double Higgs production
at the High Luminosity LHC.

\clearpage

\input{sec-intro}
\input{sec-mcsamples}
\input{sec-analysis}
\input{sec-results}
\input{sec-mva}
\input{sec-conclusions}

%%%%%%%%%%%%%%%%%%

\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}

\bibitem{ATLAS:2013hta}
{\bf ATLAS} Collaboration, {\it {Physics at a High-Luminosity LHC with ATLAS}},
   \href{http://arxiv.org/abs/1307.7292}{{\tt arXiv:1307.7292}}.

\bibitem{CMS:2013xfa}
{\bf CMS} Collaboration, {\it {Projected Performance of an Upgraded CMS
  Detector at the LHC and HL-LHC: Contribution to the Snowmass Process}},
  \href{http://arxiv.org/abs/1307.7135}{{\tt arXiv:1307.7135}}.

\bibitem{baglio}
J.~Baglio, A.~Djouadi, R.~Grober, M.~Muhlleitner, J.~Quevillon, et~al., {\it
  {The measurement of the Higgs self-coupling at the LHC: theoretical status}},
   {\em JHEP} {\bf 1304} (2013) 151,
  [\href{http://arxiv.org/abs/1212.5581}{{\tt arXiv:1212.5581}}].

\bibitem{Giudice:2007fh}
G.~Giudice, C.~Grojean, A.~Pomarol, and R.~Rattazzi, {\it {The
  Strongly-Interacting Light Higgs}},  {\em JHEP} {\bf 0706} (2007) 045,
  [\href{http://arxiv.org/abs/hep-ph/0703164}{{\tt hep-ph/0703164}}].

\bibitem{Contino:2010mh}
R.~Contino, C.~Grojean, M.~Moretti, F.~Piccinini, and R.~Rattazzi, {\it {Strong
  Double Higgs Production at the LHC}},  {\em JHEP} {\bf 1005} (2010) 089,
  [\href{http://arxiv.org/abs/1002.1011}{{\tt arXiv:1002.1011}}].

\bibitem{Aad:2015xja}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Searches for Higgs boson pair
  production in the $hh\to bb\tau\tau, \gamma\gamma WW^*, \gamma\gamma bb,
  bbbb$ channels with the ATLAS detector}},  {\em Phys. Rev.} {\bf D92} (2015)
  092004, [\href{http://arxiv.org/abs/1509.04670}{{\tt arXiv:1509.04670}}].

\bibitem{Aad:2015uka}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Search for Higgs boson pair
  production in the $b\bar{b}b\bar{b}$ final state from pp collisions at
  $\sqrt{s} = 8$ TeVwith the ATLAS detector}},  {\em Eur. Phys. J.} {\bf C75}
  (2015), no.~9 412, [\href{http://arxiv.org/abs/1506.00285}{{\tt
  arXiv:1506.00285}}].

\bibitem{Aad:2014yja}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Search For Higgs Boson Pair
  Production in the $\gamma\gamma b\bar{b}$ Final State using $pp$ Collision
  Data at $\sqrt{s}=8$ TeV from the ATLAS Detector}},  {\em Phys.Rev.Lett.}
  {\bf 114} (2015), no.~8 081802, [\href{http://arxiv.org/abs/1406.5053}{{\tt
  arXiv:1406.5053}}].

\bibitem{Khachatryan:2015yea}
{\bf CMS} Collaboration, V.~Khachatryan et~al., {\it {Search for resonant pair
  production of Higgs bosons decaying to two bottom quark–antiquark pairs in
  proton–proton collisions at 8 TeV}},  {\em Phys. Lett.} {\bf B749} (2015)
  560--582, [\href{http://arxiv.org/abs/1503.04114}{{\tt arXiv:1503.04114}}].

\bibitem{Chatrchyan:2011wt}
{\bf CMS} Collaboration, S.~Chatrchyan et~al., {\it {Search for resonant HH
  production in $2\gamma2b$ channel}}, {\tt CMS-PAS-HIG-13-032}.

\bibitem{Arkani-Hamed:2015vfh}
N.~Arkani-Hamed, T.~Han, M.~Mangano, and L.-T. Wang, {\it {Physics
  Opportunities of a 100 TeV Proton-Proton Collider}},
  \href{http://arxiv.org/abs/1511.06495}{{\tt arXiv:1511.06495}}.

\bibitem{Barr:2014sga}
A.~J. Barr, M.~J. Dolan, C.~Englert, D.~E. Ferreira~de Lima, and M.~Spannowsky,
  {\it {Higgs Self-Coupling Measurements at a 100 TeV Hadron Collider}},  {\em
  JHEP} {\bf 1502} (2015) 016, [\href{http://arxiv.org/abs/1412.7154}{{\tt
  arXiv:1412.7154}}].

\bibitem{Papaefstathiou:2015iba}
A.~Papaefstathiou, {\it {Discovering Higgs boson pair production through rare
  final states at a 100 TeV collider}},  {\em Phys.Rev.} {\bf D91} (2015),
  no.~11 113016, [\href{http://arxiv.org/abs/1504.04621}{{\tt
  arXiv:1504.04621}}].

\bibitem{Azatov:2015oxa}
A.~Azatov, R.~Contino, G.~Panico, and M.~Son, {\it {Effective field theory
  analysis of double Higgs boson production via gluon fusion}},  {\em Phys.
  Rev.} {\bf D92} (2015), no.~3 035001,
  [\href{http://arxiv.org/abs/1502.00539}{{\tt arXiv:1502.00539}}].

\bibitem{Contino:2013gna}
R.~Contino, C.~Grojean, D.~Pappadopulo, R.~Rattazzi, and A.~Thamm, {\it {Strong
  Higgs Interactions at a Linear Collider}},  {\em JHEP} {\bf 1402} (2014) 006,
  [\href{http://arxiv.org/abs/1309.7038}{{\tt arXiv:1309.7038}}].

\bibitem{Dittmaier:2012vm}
{LHC Higgs Cross Section Working Group}, S.~Dittmaier, C.~Mariotti,
  G.~Passarino, and R.~Tanaka~(Eds.), {\it {Handbook of LHC Higgs Cross
  Sections: 2. Differential Distributions}},  {\em CERN-2012-002} (CERN,
  Geneva, 2012) [\href{http://arxiv.org/abs/1201.3084}{{\tt arXiv:1201.3084}}].

\bibitem{Frederix:2014hta}
R.~Frederix, S.~Frixione, V.~Hirschi, F.~Maltoni, O.~Mattelaer, P.~Torrielli,
  E.~Vryonidou, and M.~Zaro, {\it {Higgs pair production at the LHC with NLO
  and parton-shower effects}},  {\em Phys. Lett.} {\bf B732} (2014) 142--149,
  [\href{http://arxiv.org/abs/1401.7340}{{\tt arXiv:1401.7340}}].

\bibitem{deFlorian:2013jea}
D.~de~Florian and J.~Mazzitelli, {\it {Higgs Boson Pair Production at
  Next-to-Next-to-Leading Order in QCD}},  {\em Phys. Rev. Lett. 111,} {\bf
  201801} (2013) 201801, [\href{http://arxiv.org/abs/1309.6594}{{\tt
  arXiv:1309.6594}}].

\bibitem{deFlorian:2015moa}
D.~de~Florian and J.~Mazzitelli, {\it {Higgs pair production at
  next-to-next-to-leading logarithmic accuracy at the LHC}},  {\em JHEP} {\bf
  09} (2015) 053, [\href{http://arxiv.org/abs/1505.07122}{{\tt
  arXiv:1505.07122}}].

\bibitem{Baur:2003gp}
U.~Baur, T.~Plehn, and D.~L. Rainwater, {\it {Probing the Higgs selfcoupling at
  hadron colliders using rare decays}},  {\em Phys.Rev.} {\bf D69} (2004)
  053004, [\href{http://arxiv.org/abs/hep-ph/0310056}{{\tt hep-ph/0310056}}].

\bibitem{Barger:2013jfa}
V.~Barger, L.~L. Everett, C.~Jackson, and G.~Shaughnessy, {\it {Higgs-Pair
  Production and Measurement of the Triscalar Coupling at LHC(8,14)}},
  \href{http://arxiv.org/abs/1311.2931}{{\tt arXiv:1311.2931}}.

\bibitem{Lu:2015jza} 
  C.~T.~Lu, J.~Chang, K.~Cheung and J.~S.~Lee,
  {\it An exploratory study of Higgs-boson pair production},
  JHEP {\bf 1508}, 133 (2015),
  \href{http://arxiv.org/abs/1505.00957}{{\tt arXiv:1505.00957}}.

\bibitem{Baur:2003gpa}
U.~Baur, T.~Plehn, and D.~L. Rainwater, {\it {Examining the Higgs boson
  potential at lepton and hadron colliders: A Comparative analysis}},  {\em
  Phys.Rev.} {\bf D68} (2003) 033001,
  [\href{http://arxiv.org/abs/hep-ph/0304015}{{\tt hep-ph/0304015}}].

\bibitem{Barr:2013tda}
A.~J. Barr, M.~J. Dolan, C.~Englert, and M.~Spannowsky, {\it {Di-Higgs final
  states augMT2ed -- selecting $hh$ events at the high luminosity LHC}},  {\em
  Phys. Lett.} {\bf B728} (2014) 308--313,
  [\href{http://arxiv.org/abs/1309.6318}{{\tt arXiv:1309.6318}}].

\bibitem{Dolan:2012rv}
M.~J. Dolan, C.~Englert, and M.~Spannowsky, {\it {Higgs self-coupling
  measurements at the LHC}},  {\em JHEP} {\bf 1210} (2012) 112,
  [\href{http://arxiv.org/abs/1206.5001}{{\tt arXiv:1206.5001}}].

\bibitem{Dolan:2013rja}
M.~J. Dolan, C.~Englert, N.~Greiner, and M.~Spannowsky, {\it {Further on up the
  road: $hhjj$ production at the LHC}},  {\em Phys.Rev.Lett.} {\bf 112} (2014)
  101802, [\href{http://arxiv.org/abs/1310.1084}{{\tt arXiv:1310.1084}}].

\bibitem{Papaefstathiou:2012qe}
A.~Papaefstathiou, L.~L. Yang, and J.~Zurita, {\it {Higgs boson pair production
  at the LHC in the $b \bar{b} W^+ W^-$ channel}},  {\em Phys.Rev.} {\bf D87}
  (2013) 011301, [\href{http://arxiv.org/abs/1209.1489}{{\tt
  arXiv:1209.1489}}].

\bibitem{Wardrope:2014kya}
D.~Wardrope, E.~Jansen, N.~Konstantinidis, B.~Cooper, R.~Falla, et~al., {\it
  {Non-resonant Higgs-pair production in the $b\overline{b}$ $b\overline{b}$
  final state at the LHC}},  {\em Eur.Phys.J.} {\bf C75} (2015), no.~5 219,
  [\href{http://arxiv.org/abs/1410.2794}{{\tt arXiv:1410.2794}}].

\bibitem{deLima:2014dta}
D.~E. Ferreira~de Lima, A.~Papaefstathiou, and M.~Spannowsky, {\it {Standard
  model Higgs boson pair production in the ( $ b\overline{b} $ )( $
  b\overline{b} $ ) final state}},  {\em JHEP} {\bf 1408} (2014) 030,
  [\href{http://arxiv.org/abs/1404.7139}{{\tt arXiv:1404.7139}}].

\bibitem{Dolan:2015zja}
M.~J. Dolan, C.~Englert, N.~Greiner, K.~Nordstrom, and M.~Spannowsky, {\it
  {$hhjj$ production at the LHC}},  {\em Eur. Phys. J.} {\bf C75} (2015), no.~8
  387, [\href{http://arxiv.org/abs/1506.08008}{{\tt arXiv:1506.08008}}].

\bibitem{Brooijmans:2014eja}
G.~Brooijmans, R.~Contino, B.~Fuks, F.~Moortgat, P.~Richardson, et~al., {\it
  {Les Houches 2013: Physics at TeV Colliders: New Physics Working Group
  Report}},  \href{http://arxiv.org/abs/1405.1617}{{\tt arXiv:1405.1617}}.

\bibitem{Barger:1988jk}
V.~D. Barger, T.~Han, and R.~J.~N. Phillips, {\it {Double Higgs Boson
  Bremsstrahlung From $W$ and $Z$ Bosons at Supercolliders}},  {\em Phys. Rev.}
  {\bf D38} (1988) 2766.

\bibitem{Cao:2015oxx}
Q.-H. Cao, Y.~Liu, and B.~Yan, {\it {Measuring Trilinear Higgs Coupling in
  $WHH$ and $ZHH$ Productions at the HL-LHC}},
  \href{http://arxiv.org/abs/1511.03311}{{\tt arXiv:1511.03311}}.

\bibitem{Englert:2014uqa}
C.~Englert, F.~Krauss, M.~Spannowsky, and J.~Thompson, {\it {Di-Higgs
  phenomenology in $t\bar{t}hh$: The forgotten channel}},  {\em Phys.Lett.}
  {\bf B743} (2015) 93--97, [\href{http://arxiv.org/abs/1409.8074}{{\tt
  arXiv:1409.8074}}].

\bibitem{Liu-Sheng:2014gxa}
L.-S. Ling, R.-Y. Zhang, W.-G. Ma, L.~Guo, W.-H. Li, et~al., {\it {NNLO QCD
  corrections to Higgs pair production via vector boson fusion at hadron
  colliders}},  {\em Phys.Rev.} {\bf D89} (2014), no.~7 073001,
  [\href{http://arxiv.org/abs/1401.7754}{{\tt arXiv:1401.7754}}].

\bibitem{Slawinska:2014vpa}
M.~Slawinska, W.~van~den Wollenberg, B.~van Eijk, and S.~Bentvelsen, {\it
  {Phenomenology of the trilinear Higgs coupling at proton-proton colliders}},
  \href{http://arxiv.org/abs/1408.5010}{{\tt arXiv:1408.5010}}.

\bibitem{Chen:2014xra}
C.-R. Chen and I.~Low, {\it {Double take on new physics in double Higgs boson
  production}},  {\em Phys.Rev.} {\bf D90} (2014), no.~1 013018,
  [\href{http://arxiv.org/abs/1405.7040}{{\tt arXiv:1405.7040}}].

\bibitem{Goertz:2013kp}
F.~Goertz, A.~Papaefstathiou, L.~L. Yang, and J.~Zurita, {\it {Higgs Boson
  self-coupling measurements using ratios of cross sections}},  {\em JHEP} {\bf
  1306} (2013) 016, [\href{http://arxiv.org/abs/1301.3492}{{\tt
  arXiv:1301.3492}}].

\bibitem{Dawson:2015oha}
S.~Dawson, A.~Ismail, and I.~Low, {\it {What’s in the loop? The anatomy of
  double Higgs production}},  {\em Phys.Rev.} {\bf D91} (2015), no.~11 115008,
  [\href{http://arxiv.org/abs/1504.05596}{{\tt arXiv:1504.05596}}].

\bibitem{Maltoni:2014eza}
F.~Maltoni, E.~Vryonidou, and M.~Zaro, {\it {Top-quark mass effects in double
  and triple Higgs production in gluon-gluon fusion at NLO}},  {\em JHEP} {\bf
  1411} (2014) 079, [\href{http://arxiv.org/abs/1408.6542}{{\tt
  arXiv:1408.6542}}].

\bibitem{Maierhofer:2013sha}
P.~Maierhöfer and A.~Papaefstathiou, {\it {Higgs Boson pair production merged
  to one jet}},  {\em JHEP} {\bf 1403} (2014) 126,
  [\href{http://arxiv.org/abs/1401.0007}{{\tt arXiv:1401.0007}}].

\bibitem{Grigo:2013rya}
J.~Grigo, J.~Hoff, K.~Melnikov, and M.~Steinhauser, {\it {On the Higgs boson
  pair production at the LHC}},  {\em Nucl.Phys.} {\bf B875} (2013) 1--17,
  [\href{http://arxiv.org/abs/1305.7340}{{\tt arXiv:1305.7340}}].

\bibitem{Grigo:2014jma}
J.~Grigo, K.~Melnikov, and M.~Steinhauser, {\it {Virtual corrections to Higgs
  boson pair production in the large top quark mass limit}},  {\em Nucl. Phys.}
  {\bf B888} (2014) 17--29, [\href{http://arxiv.org/abs/1408.2422}{{\tt
  arXiv:1408.2422}}].

\bibitem{Nishiwaki:2013cma}
K.~Nishiwaki, S.~Niyogi, and A.~Shivaji, {\it {$ttH$ Anomalous Coupling in
  Double Higgs Production}},  {\em JHEP} {\bf 1404} (2014) 011,
  [\href{http://arxiv.org/abs/1309.6907}{{\tt arXiv:1309.6907}}].

\bibitem{Cao:2015oaa} 
  Q.~H.~Cao, B.~Yan, D.~M.~Zhang and H.~Zhang, 
  {\it Resolving the Degeneracy in Single Higgs Production with Higgs Pair Production}, 
  {\em Phys.\ Lett.\ B} {\bf 752}, 285 (2016),
  [\href{http://arxiv.org/abs/1508.06512}{{\tt arXiv:1508.06512}}].

\bibitem{Dall'Osso:2015aia}
M.~Dall'Osso, T.~Dorigo, C.~A. Gottardo, A.~Oliveira, M.~Tosi, et~al., {\it
  {Higgs Pair Production: Choosing Benchmarks With Cluster Analysis}},
  \href{http://arxiv.org/abs/1507.02245}{{\tt arXiv:1507.02245}}.

\bibitem{Liu:2014rba}
N.~Liu, S.~Hu, B.~Yang, and J.~Han, {\it {Impact of top-Higgs couplings on
  Di-Higgs production at future colliders}},  {\em JHEP} {\bf 1501} (2015) 008,
  [\href{http://arxiv.org/abs/1408.4191}{{\tt arXiv:1408.4191}}].

\bibitem{Goertz:2014qta}
F.~Goertz, A.~Papaefstathiou, L.~L. Yang, and J.~Zurita, {\it {Higgs boson pair
  production in the D=6 extension of the SM}},  {\em JHEP} {\bf 1504} (2015)
  167, [\href{http://arxiv.org/abs/1410.3471}{{\tt arXiv:1410.3471}}].

\bibitem{He:2015spf}
H.-J. He, J.~Ren, and W.~Yao, {\it {Probing New Physics of Cubic Higgs
  Interaction via Higgs Pair Production at Hadron Colliders}},
  \href{http://arxiv.org/abs/1506.03302}{{\tt arXiv:1506.03302}}.

\bibitem{Grober:2015cwa}
R.~Grober, M.~Muhlleitner, M.~Spira, and J.~Streicher, {\it {NLO QCD
  Corrections to Higgs Pair Production including Dimension-6 Operators}},  {\em
  JHEP} {\bf 09} (2015) 092, [\href{http://arxiv.org/abs/1504.06577}{{\tt
  arXiv:1504.06577}}].

\bibitem{Gouzevitch:2013qca}
M.~Gouzevitch, A.~Oliveira, J.~Rojo, R.~Rosenfeld, G.~P. Salam, et~al., {\it
  {Scale-invariant resonance tagging in multijet events and new physics in
  Higgs pair production}},  {\em JHEP} {\bf 1307} (2013) 148,
  [\href{http://arxiv.org/abs/1303.6636}{{\tt arXiv:1303.6636}}].

\bibitem{Cooper:2013kia}
B.~Cooper, N.~Konstantinidis, L.~Lambourne, and D.~Wardrope, {\it {Boosted $hh
  → b\overline{b}b\overline{b}$: A new topology in searches for TeV-scale
  resonances at the LHC}},  {\em Phys. Rev.} {\bf D88} (2013), no.~11 114005,
  [\href{http://arxiv.org/abs/1307.0407}{{\tt arXiv:1307.0407}}].

\bibitem{No:2013wsa}
J.~M. No and M.~Ramsey-Musolf, {\it {Probing the Higgs Portal at the LHC
  Through Resonant di-Higgs Production}},  {\em Phys.Rev.} {\bf D89} (2014),
  no.~9 095031, [\href{http://arxiv.org/abs/1310.6035}{{\tt arXiv:1310.6035}}].

\bibitem{Wen-Juan:2015gqg}
Z.~Wen-Juan, M.~Wen-Gan, Z.~Ren-You, L.~Xiao-Zhou, G.~Lei, and C.~Chong, {\it
  {Double Higgs boson production and decay in Randall-Sundrum model at hadron
  colliders}},  \href{http://arxiv.org/abs/1512.01766}{{\tt arXiv:1512.01766}}.

\bibitem{Belyaev:1999kk}
A.~Belyaev, M.~Drees, O.~J. Eboli, J.~Mizukoshi, and S.~Novaes, {\it
  {Supersymmetric Higgs pair discovery prospects at hadron colliders}},
  \href{http://arxiv.org/abs/hep-ph/9910400}{{\tt hep-ph/9910400}}.

\bibitem{Han:2013sga}
C.~Han, X.~Ji, L.~Wu, P.~Wu, and J.~M. Yang, {\it {Higgs pair production with
  SUSY QCD correction: revisited under current experimental constraints}},
  {\em JHEP} {\bf 1404} (2014) 003, [\href{http://arxiv.org/abs/1307.3790}{{\tt
  arXiv:1307.3790}}].

\bibitem{Hespel:2014sla}
B.~Hespel, D.~Lopez-Val, and E.~Vryonidou, {\it {Higgs pair production via
  gluon fusion in the Two-Higgs-Doublet Model}},  {\em JHEP} {\bf 1409} (2014)
  124, [\href{http://arxiv.org/abs/1407.0281}{{\tt arXiv:1407.0281}}].

\bibitem{Wu:2015nba}
L.~Wu, J.~M. Yang, C.-P. Yuan, and M.~Zhang, {\it {Higgs self-coupling in the
  MSSM and NMSSM after the LHC Run 1}},  {\em Phys.Lett.} {\bf B747} (2015)
  378--389, [\href{http://arxiv.org/abs/1504.06932}{{\tt arXiv:1504.06932}}].

\bibitem{Cao:2014kya}
J.~Cao, D.~Li, L.~Shang, P.~Wu, and Y.~Zhang, {\it Exploring the Higgs Sector
  of a Most Natural NMSSM and its Prediction on Higgs Pair Production at the
  LHC},  {\em JHEP} {\bf 1412} (2014) 026,
  [\href{http://arxiv.org/abs/1409.8431}{{\tt arXiv:1409.8431}}].

\bibitem{Ellwanger:2013ova}
U.~Ellwanger, {\it {Higgs pair production in the NMSSM at the LHC}},  {\em
  JHEP} {\bf 1308} (2013) 077, [\href{http://arxiv.org/abs/1306.5541}{{\tt
  arXiv:1306.5541}}].

%\cite{Cao:2013si}
\bibitem{Cao:2013si} 
  J.~Cao, Z.~Heng, L.~Shang, P.~Wan and J.~M.~Yang,
  {\it Pair Production of a 125 GeV Higgs Boson in MSSM and NMSSM at the LHC,}
  {\em JHEP} {\bf 1304}, 134 (2013),
  [\href{http://arxiv.org/abs/1301.6437}{{\tt
  arXiv:1301.6437}}].

\bibitem{Khachatryan:2015tha}
{\bf CMS} Collaboration, V.~Khachatryan et~al., {\it {Searches for a heavy
  scalar boson $ \mathrm{H} $ decaying to a pair of 125 GeV Higgs bosons $
  \mathrm{ hh } $ or for a heavy pseudoscalar boson $ \mathrm{A} $ decaying to
  $ \mathrm{Zh} $, in the final states with $\mathrm{h} \to \tau \tau$}},
  \href{http://arxiv.org/abs/1510.01181}{{\tt arXiv:1510.01181}}.

\bibitem{Alwall:2014hca}
J.~Alwall, R.~Frederix, S.~Frixione, V.~Hirschi, F.~Maltoni, et~al., {\it {The
  automated computation of tree-level and next-to-leading order differential
  cross sections, and their matching to parton shower simulations}},  {\em
  JHEP} {\bf 1407} (2014) 079, [\href{http://arxiv.org/abs/1405.0301}{{\tt
  arXiv:1405.0301}}].

\bibitem{Plehn:1996wb}
T.~Plehn, M.~Spira, and P.~Zerwas, {\it {Pair production of neutral Higgs
  particles in gluon-gluon collisions}},  {\em Nucl.Phys.} {\bf B479} (1996)
  46--64, [\href{http://arxiv.org/abs/hep-ph/9603205}{{\tt hep-ph/9603205}}].

\bibitem{Hirschi:2015iia}
V.~Hirschi and O.~Mattelaer, {\it {Automated event generation for loop-induced
  processes}},  {\em JHEP} {\bf 10} (2015) 146,
  [\href{http://arxiv.org/abs/1507.00020}{{\tt arXiv:1507.00020}}].

\bibitem{Ball:2014uwa}
{\bf NNPDF} Collaboration, R.~D. Ball et~al., {\it {Parton distributions for
  the LHC Run II}},  {\em JHEP} {\bf 1504} (2015) 040,
  [\href{http://arxiv.org/abs/1410.8849}{{\tt arXiv:1410.8849}}].

\bibitem{Buckley:2014ana}
A.~Buckley, J.~Ferrando, S.~Lloyd, K.~Nordström, B.~Page, et~al., {\it
  {LHAPDF6: parton density access in the LHC precision era}},  {\em
  Eur.Phys.J.} {\bf C75} (2015), no.~3 132,
  [\href{http://arxiv.org/abs/1412.7420}{{\tt arXiv:1412.7420}}].

\bibitem{Aad:2014aba}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Measurement of the Higgs boson
  mass from the $H\rightarrow \gamma\gamma$ and $H \rightarrow ZZ^{*}
  \rightarrow 4\ell$ channels with the ATLAS detector using 25 fb$^{-1}$ of
  $pp$ collision data}},  {\em Phys.Rev.} {\bf D90} (2014), no.~5 052004,
  [\href{http://arxiv.org/abs/1406.3827}{{\tt arXiv:1406.3827}}].

\bibitem{Khachatryan:2014jba}
{\bf CMS} Collaboration, V.~Khachatryan et~al., {\it {Precise determination of
  the mass of the Higgs boson and tests of compatibility of its couplings with
  the standard model predictions using proton collisions at 7 and 8 $\,\text
  {TeV}$}},  {\em Eur.Phys.J.} {\bf C75} (2015), no.~5 212,
  [\href{http://arxiv.org/abs/1412.8662}{{\tt arXiv:1412.8662}}].

\bibitem{Aad:2015zhl}
{\bf ATLAS, CMS} Collaboration, G.~Aad et~al., {\it {Combined Measurement of
  the Higgs Boson Mass in $pp$ Collisions at $\sqrt{s}=7$ and 8 TeV with the
  ATLAS and CMS Experiments}},  {\em Phys. Rev. Lett.} {\bf 114} (2015) 191803,
  [\href{http://arxiv.org/abs/1503.07589}{{\tt arXiv:1503.07589}}].

\bibitem{Sjostrand:2007gs}
T.~Sjostrand, S.~Mrenna, and P.~Z. Skands, {\it {A Brief Introduction to PYTHIA
  8.1}},  {\em Comput.Phys.Commun.} {\bf 178} (2008) 852--867,
  [\href{http://arxiv.org/abs/0710.3820}{{\tt arXiv:0710.3820}}].

\bibitem{Sjostrand:2014zea}
T.~Sjöstrand, S.~Ask, J.~R. Christiansen, R.~Corke, N.~Desai, et~al., {\it {An
  Introduction to PYTHIA 8.2}},  {\em Comput.Phys.Commun.} {\bf 191} (2015)
  159--177, [\href{http://arxiv.org/abs/1410.3012}{{\tt arXiv:1410.3012}}].

\bibitem{Skands:2014pea}
P.~Skands, S.~Carrazza, and J.~Rojo, {\it {Tuning PYTHIA 8.1: the Monash 2013
  Tune}},  {\em Eur.Phys.J.} {\bf C74} (2014), no.~8 3024,
  [\href{http://arxiv.org/abs/1404.5630}{{\tt arXiv:1404.5630}}].

\bibitem{Ball:2012cx}
R.~D. Ball, V.~Bertone, S.~Carrazza, C.~S. Deans, L.~Del~Debbio, et~al., {\it
  {Parton distributions with LHC data}},  {\em Nucl.Phys.} {\bf B867} (2013)
  244--289, [\href{http://arxiv.org/abs/1207.1303}{{\tt arXiv:1207.1303}}].

\bibitem{Ball:2013hta}
{\bf NNPDF} Collaboration, R.~D. Ball, V.~Bertone, S.~Carrazza, L.~Del~Debbio,
  S.~Forte, A.~Guffanti, N.~P. Hartland, and J.~Rojo, {\it {Parton
  distributions with QED corrections}},  {\em Nucl. Phys.} {\bf B877} (2013)
  290--320, [\href{http://arxiv.org/abs/1308.0598}{{\tt arXiv:1308.0598}}].

\bibitem{Gleisberg:2008ta}
T.~Gleisberg et~al., {\it {Event generation with SHERPA 1.1}},  {\em JHEP} {\bf
  02} (2009) 007, [\href{http://arxiv.org/abs/0811.4622}{{\tt
  arXiv:0811.4622}}].

\bibitem{Bern:2011ep}
Z.~Bern, G.~Diana, L.~Dixon, F.~Febres~Cordero, S.~Hoeche, et~al., {\it
  {Four-Jet Production at the Large Hadron Collider at Next-to-Leading Order in
  QCD}},  {\em Phys.Rev.Lett.} {\bf 109} (2012) 042001,
  [\href{http://arxiv.org/abs/1112.3940}{{\tt arXiv:1112.3940}}].

\bibitem{Czakon:2013goa}
M.~Czakon, P.~Fiedler, and A.~Mitov, {\it {Total Top-Quark Pair-Production
  Cross Section at Hadron Colliders Through $O(α\frac{4}{S})$}},  {\em Phys.
  Rev. Lett.} {\bf 110} (2013) 252004,
  [\href{http://arxiv.org/abs/1303.6254}{{\tt arXiv:1303.6254}}].

\bibitem{Aad:2012gxa}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Search for the Standard Model
  Higgs boson produced in association with a vector boson and decaying to a
  $b$-quark pair with the ATLAS detector}},  {\em Phys.Lett.} {\bf B718} (2012)
  369--390, [\href{http://arxiv.org/abs/1207.0210}{{\tt arXiv:1207.0210}}].

\bibitem{Chatrchyan:2013zna}
{\bf CMS} Collaboration, S.~Chatrchyan et~al., {\it {Search for the standard
  model Higgs boson produced in association with a W or a Z boson and decaying
  to bottom quarks}},  {\em Phys.Rev.} {\bf D89} (2014), no.~1 012003,
  [\href{http://arxiv.org/abs/1310.3687}{{\tt arXiv:1310.3687}}].

\bibitem{Aad:2014xzb}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Search for the $b\bar{b}$ decay
  of the Standard Model Higgs boson in associated $(W/Z)H$ production with the
  ATLAS detector}},  {\em JHEP} {\bf 01} (2015) 069,
  [\href{http://arxiv.org/abs/1409.6212}{{\tt arXiv:1409.6212}}].

\bibitem{Cacciari:2011ma}
M.~Cacciari, G.~P. Salam, and G.~Soyez, {\it {FastJet User Manual}},  {\em
  Eur.Phys.J.} {\bf C72} (2012) 1896,
  [\href{http://arxiv.org/abs/1111.6097}{{\tt arXiv:1111.6097}}].

\bibitem{Cacciari:2005hq}
M.~Cacciari and G.~P. Salam, {\it {Dispelling the $N^{3}$ myth for the $k_t$
  jet-finder}},  {\em Phys. Lett.} {\bf B641} (2006) 57--61,
  [\href{http://arxiv.org/abs/hep-ph/0512210}{{\tt hep-ph/0512210}}].

\bibitem{Cacciari:2008gp}
M.~Cacciari, G.~P. Salam, and G.~Soyez, {\it {The Anti-k(t) jet clustering
  algorithm}},  {\em JHEP} {\bf 0804} (2008) 063,
  [\href{http://arxiv.org/abs/0802.1189}{{\tt arXiv:0802.1189}}].

\bibitem{Aad:2014bia}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Jet energy measurement and its
  systematic uncertainty in proton-proton collisions at $\sqrt{s}=7$ TeV with
  the ATLAS detector}},  {\em Eur. Phys. J.} {\bf C75} (2015), no.~1 17,
  [\href{http://arxiv.org/abs/1406.0076}{{\tt arXiv:1406.0076}}].

\bibitem{ATLAS:2012kla}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Performance of large-R jets and
  jet substructure reconstruction with the ATLAS detector}},
  \href{http://arxiv.org/abs/ATLAS-CONF-2012-065}{{\tt ATLAS-CONF-2012-065}}.

\bibitem{Butterworth:2008iy}
J.~M. Butterworth, A.~R. Davison, M.~Rubin, and G.~P. Salam, {\it {Jet
  substructure as a new Higgs search channel at the LHC}},  {\em
  Phys.Rev.Lett.} {\bf 100} (2008) 242001,
  [\href{http://arxiv.org/abs/0802.2470}{{\tt arXiv:0802.2470}}].

\bibitem{Dokshitzer:1997in}
Y.~L. Dokshitzer, G.~Leder, S.~Moretti, and B.~Webber, {\it {Better jet
  clustering algorithms}},  {\em JHEP} {\bf 9708} (1997) 001,
  [\href{http://arxiv.org/abs/hep-ph/9707323}{{\tt hep-ph/9707323}}].

\bibitem{Wobisch:1998wt}
M.~Wobisch and T.~Wengler, {\it {Hadronization corrections to jet
  cross-sections in deep inelastic scattering}},
  \href{http://arxiv.org/abs/hep-ph/9907280}{{\tt hep-ph/9907280}}.

\bibitem{Salam:2009jx}
G.~P. Salam, {\it {Towards Jetography}},  {\em Eur.Phys.J.} {\bf C67} (2010)
  637--686, [\href{http://arxiv.org/abs/0906.1833}{{\tt arXiv:0906.1833}}].

\bibitem{Aad:2013gja}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Performance of jet substructure
  techniques for large-$R$ jets in proton-proton collisions at $\sqrt{s}$ = 7
  TeV using the ATLAS detector}},  {\em JHEP} {\bf 1309} (2013) 076,
  [\href{http://arxiv.org/abs/1306.4945}{{\tt arXiv:1306.4945}}].

\bibitem{Butterworth:2002tt}
J.~Butterworth, B.~Cox, and J.~R. Forshaw, {\it {$W W$ scattering at the CERN
  LHC}},  {\em Phys.Rev.} {\bf D65} (2002) 096014,
  [\href{http://arxiv.org/abs/hep-ph/0201098}{{\tt hep-ph/0201098}}].

\bibitem{Ellis:1993tq}
S.~D. Ellis and D.~E. Soper, {\it {Successive combination jet algorithm for
  hadron collisions}},  {\em Phys. Rev.} {\bf D48} (1993) 3160--3166,
  [\href{http://arxiv.org/abs/hep-ph/9305266}{{\tt hep-ph/9305266}}].

\bibitem{Thaler:2010tr}
J.~Thaler and K.~Van~Tilburg, {\it {Identifying Boosted Objects with
  N-subjettiness}},  {\em JHEP} {\bf 1103} (2011) 015,
  [\href{http://arxiv.org/abs/1011.2268}{{\tt arXiv:1011.2268}}].

\bibitem{Thaler:2011gf}
J.~Thaler and K.~Van~Tilburg, {\it {Maximizing Boosted Top Identification by
  Minimizing N-subjettiness}},  {\em JHEP} {\bf 1202} (2012) 093,
  [\href{http://arxiv.org/abs/1108.2701}{{\tt arXiv:1108.2701}}].

\bibitem{Catani:1993hr}
S.~Catani, Y.~L. Dokshitzer, M.~H. Seymour, and B.~R. Webber, {\it
  {Longitudinally invariant $K\_t$ clustering algorithms for hadron hadron
  collisions}},  {\em Nucl. Phys.} {\bf B406} (1993) 187--224.

\bibitem{Larkoski:2013eya}
A.~J. Larkoski, G.~P. Salam, and J.~Thaler, {\it {Energy Correlation Functions
  for Jet Substructure}},  {\em JHEP} {\bf 1306} (2013) 108,
  [\href{http://arxiv.org/abs/1305.0007}{{\tt arXiv:1305.0007}}].

\bibitem{Larkoski:2014gra}
A.~J. Larkoski, I.~Moult, and D.~Neill, {\it {Power Counting to Better Jet
  Observables}},  {\em JHEP} {\bf 1412} (2014) 009,
  [\href{http://arxiv.org/abs/1409.6298}{{\tt arXiv:1409.6298}}].

\bibitem{Aad:2015ydr}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Performance of $b$-Jet
  Identification in the ATLAS Experiment}},
  \href{http://arxiv.org/abs/1512.01094}{{\tt arXiv:1512.01094}}.

\bibitem{Khachatryan:2011wq}
{\bf CMS} Collaboration, V.~Khachatryan et~al., {\it {Measurement of $B\bar{B}$
  Angular Correlations based on Secondary Vertex Reconstruction at $\sqrt{s}=7$
  TeV}},  {\em JHEP} {\bf 1103} (2011) 136,
  [\href{http://arxiv.org/abs/1102.3194}{{\tt arXiv:1102.3194}}].

\bibitem{Chatrchyan:2012jua}
{\bf CMS} Collaboration, S.~Chatrchyan et~al., {\it {Identification of b-quark
  jets with the CMS experiment}},  {\em JINST} {\bf 8} (2013) P04013,
  [\href{http://arxiv.org/abs/1211.4462}{{\tt arXiv:1211.4462}}].

\bibitem{Cacciari:2007fd}
M.~Cacciari and G.~P. Salam, {\it {Pileup subtraction using jet areas}},  {\em
  Phys. Lett.} {\bf B659} (2008) 119--126,
  [\href{http://arxiv.org/abs/0707.1378}{{\tt arXiv:0707.1378}}].

\bibitem{ATLAS-CONF-2014-004}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Calibration of $b$-tagging
  using dileptonic top pair events in a combinatorial likelihood approach with
  the ATLAS experiment}},  \href{http://arxiv.org/abs/ATLAS-CONF-2014-004}{{\tt
  ATLAS-CONF-2014-004}}.

\bibitem{Cacciari:2009dp}
M.~Cacciari, G.~P. Salam, and S.~Sapeta, {\it {On the characterisation of the
  underlying event}},  {\em JHEP} {\bf 1004} (2010) 065,
  [\href{http://arxiv.org/abs/0912.4926}{{\tt arXiv:0912.4926}}].

\bibitem{TheATLAScollaboration:2013pia}
{\bf ATLAS} Collaboration, G.~Aad et~al., {\it {Pile-up subtraction and
  suppression for jets in ATLAS}},
  \href{http://arxiv.org/abs/ATLAS-CONF-2013-083}{{\tt ATLAS-CONF-2013-083}}.

\bibitem{Krohn:2009th}
D.~Krohn, J.~Thaler, and L.-T. Wang, {\it {Jet Trimming}},  {\em JHEP} {\bf 02}
  (2010) 084, [\href{http://arxiv.org/abs/0912.1342}{{\tt arXiv:0912.1342}}].

\bibitem{Krohn:2013lba}
D.~Krohn, M.~D. Schwartz, M.~Low, and L.-T. Wang, {\it {Jet Cleansing: Pileup
  Removal at High Luminosity}},  {\em Phys.Rev.} {\bf D90} (2014), no.~6
  065020, [\href{http://arxiv.org/abs/1309.4777}{{\tt arXiv:1309.4777}}].

\bibitem{Cacciari:2008gd}
M.~Cacciari, J.~Rojo, G.~P. Salam, and G.~Soyez, {\it {Quantifying the
  performance of jet definitions for kinematic reconstruction at the LHC}},
  {\em JHEP} {\bf 12} (2008) 032, [\href{http://arxiv.org/abs/0810.1304}{{\tt
  arXiv:0810.1304}}].

\bibitem{Ellis:2009me}
S.~D. Ellis, C.~K. Vermilion, and J.~R. Walsh, {\it {Recombination Algorithms
  and Jet Substructure: Pruning as a Tool for Heavy Particle Searches}},  {\em
  Phys. Rev.} {\bf D81} (2010) 094023,
  [\href{http://arxiv.org/abs/0912.0033}{{\tt arXiv:0912.0033}}].

\bibitem{Bertolini:2014bba}
D.~Bertolini, P.~Harris, M.~Low, and N.~Tran, {\it {Pileup Per Particle
  Identification}},  {\em JHEP} {\bf 10} (2014) 59,
  [\href{http://arxiv.org/abs/1407.6013}{{\tt arXiv:1407.6013}}].

\bibitem{Cacciari:2014gra}
M.~Cacciari, G.~P. Salam, and G.~Soyez, {\it {SoftKiller, a particle-level
  pileup removal method}},  {\em Eur. Phys. J.} {\bf C75} (2015), no.~2 59,
  [\href{http://arxiv.org/abs/1407.0408}{{\tt arXiv:1407.0408}}].

\bibitem{Cacciari:2014jta}
M.~Cacciari, G.~P. Salam, and G.~Soyez, {\it {Use of charged-track information
  to subtract neutral pileup}},  {\em Phys. Rev.} {\bf D92} (2015), no.~1
  014003, [\href{http://arxiv.org/abs/1404.7353}{{\tt arXiv:1404.7353}}].

\bibitem{Berta:2014eza}
P.~Berta, M.~Spousta, D.~W. Miller, and R.~Leitner, {\it {Particle-level pileup
  subtraction for jets and jet shapes}},  {\em JHEP} {\bf 06} (2014) 092,
  [\href{http://arxiv.org/abs/1403.3108}{{\tt arXiv:1403.3108}}].

\bibitem{Larkoski:2014wba}
A.~J. Larkoski, S.~Marzani, G.~Soyez, and J.~Thaler, {\it {Soft Drop}},  {\em
  JHEP} {\bf 05} (2014) 146, [\href{http://arxiv.org/abs/1402.2657}{{\tt
  arXiv:1402.2657}}].

\bibitem{Cacciari:2010te}
M.~Cacciari, J.~Rojo, G.~P. Salam, and G.~Soyez, {\it {Jet Reconstruction in
  Heavy Ion Collisions}},  {\em Eur. Phys. J.} {\bf C71} (2011) 1539,
  [\href{http://arxiv.org/abs/1010.1759}{{\tt arXiv:1010.1759}}].

\bibitem{Soper:2011cr}
D.~E. Soper and M.~Spannowsky, {\it {Finding physics signals with shower
  deconstruction}},  {\em Phys.Rev.} {\bf D84} (2011) 074002,
  [\href{http://arxiv.org/abs/1102.3480}{{\tt arXiv:1102.3480}}].

\bibitem{Soper:2012pb}
D.~E. Soper and M.~Spannowsky, {\it {Finding top quarks with shower
  deconstruction}},  {\em Phys.Rev.} {\bf D87} (2013) 054012,
  [\href{http://arxiv.org/abs/1211.3140}{{\tt arXiv:1211.3140}}].

\bibitem{Baldi:2014pta}
P.~Baldi, P.~Sadowski, and D.~Whiteson, {\it {Enhanced Higgs Boson to
  $\tau^+\tau^-$ Search with Deep Learning}},  {\em Phys.Rev.Lett.} {\bf 114}
  (2015), no.~11 111801, [\href{http://arxiv.org/abs/1410.3469}{{\tt
  arXiv:1410.3469}}].

\bibitem{Aaltonen:2012qt}
  {\bf CDF} and {\bf D0}
  Collaboration, T.~Aaltonen et~al., {\it {Evidence for a particle
  produced in association with weak bosons and decaying to a bottom-antibottom
  quark pair in Higgs boson searches at the Tevatron}},  {\em Phys. Rev. Lett.}
  {\bf 109} (2012) 071804, [\href{http://arxiv.org/abs/1207.6436}{{\tt
        arXiv:1207.6436}}].

\bibitem{Kang:2015uoc} 
  Z.~Kang, P.~Ko and J.~Li,
  {\it New Avenues to Heavy Right-handed Neutrinos with Pair Production at Hadronic Colliders},
   \href{http://arxiv.org/abs/1512.08373}{{\tt
       arXiv:1512.08373}}.

\bibitem{DelDebbio:2004qj}
{\bf The NNPDF} Collaboration, L.~Del~Debbio, S.~Forte, J.~I. Latorre,
  A.~Piccione, and J.~Rojo, {\it Unbiased determination of the proton structure
  function f2(p) with faithful uncertainty estimation},  {\em JHEP} {\bf 03}
  (2005) 080, [\href{http://arxiv.org/abs/hep-ph/0501067}{{\tt
  hep-ph/0501067}}].

\bibitem{Ball:2008by}
{\bf The NNPDF} Collaboration, R.~D. Ball et~al., {\it {A determination of
  parton distributions with faithful uncertainty estimation}},  {\em Nucl.
  Phys.} {\bf B809} (2009) 1--63, [\href{http://arxiv.org/abs/0808.1231}{{\tt
  arXiv:0808.1231}}].

\bibitem{Ball:2011mu}
{\bf The NNPDF} Collaboration, R.~D. Ball et~al., {\it {Impact of Heavy Quark
  Masses on Parton Distributions and LHC Phenomenology}},  {\em Nucl. Phys.}
  {\bf B849} (2011) 296--363, [\href{http://arxiv.org/abs/1101.1300}{{\tt
  arXiv:1101.1300}}].

\bibitem{Ball:2010de}
{\bf {The NNPDF}} Collaboration, R.~D. Ball et~al., {\it {A first unbiased
  global NLO determination of parton distributions and their uncertainties}},
  {\em Nucl. Phys.} {\bf B838} (2010) 136--206,
  [\href{http://arxiv.org/abs/1002.4407}{{\tt arXiv:1002.4407}}].

\bibitem{quevedo}
B.~C. Allanach, D.~Grellscheid, and F.~Quevedo, {\it Genetic algorithms and
  experimental discrimination of susy models},  {\em JHEP} {\bf 07} (2004) 069,
  [\href{http://arxiv.org/abs/hep-ph/0406277}{{\tt hep-ph/0406277}}].

\bibitem{tau}
J.~Rojo and J.~I. Latorre, {\it Neural network parametrization of spectral
  functions from hadronic tau decays and determination of qcd vacuum
  condensates},  {\em JHEP} {\bf 01} (2004) 055,
  [\href{http://arxiv.org/abs/hep-ph/0401047}{{\tt hep-ph/0401047}}].

\bibitem{Abel:2014xta}
S.~Abel and J.~Rizos, {\it {Genetic Algorithms and the Search for Viable String
  Vacua}},  {\em JHEP} {\bf 08} (2014) 010,
  [\href{http://arxiv.org/abs/1404.7359}{{\tt arXiv:1404.7359}}].

\bibitem{Nesseris:2012tt}
S.~Nesseris and J.~Garcia-Bellido, {\it {A new perspective on Dark Energy
  modeling via Genetic Algorithms}},  {\em JCAP} {\bf 1211} (2012) 033,
  [\href{http://arxiv.org/abs/1205.0364}{{\tt arXiv:1205.0364}}].

\end{thebibliography}\endgroup

\end{document}

### 2016-01-21 paper-arxiv-v2/sec-mva.tex
Revised version of paper

@@
 applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
-  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.
+  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia,Kang:2015uoc}.
 
@@
 \includegraphics[width=0.49\textwidth]{plots/int_wgthist_noPU.pdf}
-\includegraphics[width=0.75\textwidth]{plots/bst_wgthist_noPU.pdf}
+\includegraphics[width=0.60\textwidth]{plots/bst_wgthist_noPU.pdf}
 \vspace{-0.5cm}

### 2016-02-18 paper-lambda/summary/lambda.tex
lambda summary

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Lambda extraction summary}

\begin{document}
\maketitle

In this document we briefly summarise the results of the Higgs trilinear coupling extraction exercise, for the case of the 14TeV HL-LHC and
the 100TeV FCC.
\subsection{Cross-section variation with $\lambda$}
These figures demonstrate the variation of the $HH$ cross-section with the value of the Higgs trilinear coupling, after processing through our analysis
but before the application of the MVA. Results here are given for the resolved~(Fig. \ref{fig:resXsec}), intermediate~(Fig. \ref{fig:interXsec}) and boosted ~(Fig. \ref{fig:boostXsec}) topologies. All figures are shown for the 14TeV LHC on the left, and 100TeV FCC on the right.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/res_xSec_14TeV.pdf}
\includegraphics[width=0.45\textwidth]{plots/res_xSec_100TeV.pdf}
\caption{Pre-MVA cross-section variation with $\lambda$ for resolved channel at 14TeV (left) and 100TeV (right).}
\label{fig:resXsec}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/inter_xSec_14TeV.pdf}
\includegraphics[width=0.45\textwidth]{plots/inter_xSec_100TeV.pdf}
\caption{Pre-MVA cross-section variation with $\lambda$ for intermediate channel at 14TeV (left) and 100TeV (right).}
\label{fig:interXsec}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/boost_xSec_14TeV.pdf}
\includegraphics[width=0.45\textwidth]{plots/boost_xSec_100TeV.pdf}
\caption{Pre-MVA cross-section variation with $\lambda$ for boosted channel at 14TeV (left) and 100TeV (right).}
\label{fig:boostXsec}
\end{center}
\end{figure}

\newpage
\subsection{Trilinear extraction - $\chi2$ profiles}

In this section we show how the trilinear may be extracted under a few assumptions with respect to the systematic uncertainty. Figures are shown for all topologies given a systematic error of zero (Fig. \ref{fig:chi2_0}), 10\% (Fig. \ref{fig:chi2_0_1}) and 100\% (Fig. \ref{fig:chi2_1}).

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/chi2_14TeV_sys0_0.pdf}
\includegraphics[width=0.45\textwidth]{plots/chi2_100TeV_sys0_0.pdf}
\caption{$\chi^2$ profile for all topologies, 14TeV HL-LHC (left) and 100TeV FCC (right), only statistical error.}
\label{fig:chi2_0}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/chi2_14TeV_sys0_1.pdf}
\includegraphics[width=0.45\textwidth]{plots/chi2_100TeV_sys0_1.pdf}
\caption{$\chi^2$ profile for all topologies, 14TeV HL-LHC (left) and 100TeV FCC (right), 10\% systematic error.}
\label{fig:chi2_0_1}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/chi2_14TeV_sys1.pdf}
\includegraphics[width=0.45\textwidth]{plots/chi2_100TeV_sys1.pdf}
\caption{$\chi^2$ profile for all topologies, 14TeV HL-LHC (left) and 100TeV FCC (right), 100\% systematic error.}
\label{fig:chi2_1}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2016-02-18 paper-lambda/paperscripts/lambda_100TeV_cutflow.py

@@ -16,7 +16,7 @@ regimeLong = { 'res': "Resolved", 'inter': "Intermediate", 'boost': "Boosted"}
 Cnum = ['C0', 'C1a', 'C1b', 'C1c', 'C1d', 'C1e', 'C2' ]
 
 lumi = 10000.0
-sysErr = 0.1 # 10%
+sysErr = 0.0 # 10%
 
 def fname(lval):
 	return "diHiggs_LAM"+str(lval).replace(".","_")+"/"
@@ -55,13 +55,14 @@ for regime in regimes:
 	icol=0
 	#axes.set_xlim([xmin,xmax])
 	fig.suptitle(regimeLong[regime] + " topology (100TeV)")
-	ax.set_ylim([1E-1,1E5])
+	ax.set_ylim([1E0,2E4])
 	for cut in range(0,len(Cnum)):
 		xsec = []
 		for lvalue in lvalues:
 			xsec.append(cutflows[fname(lvalue)+regime][cut])
-		ax.plot(lvalues, xsec, color=colours[icol])
+		ax.plot(lvalues, xsec, color=colours[icol], label=Cnum[cut])
 		icol = icol + 1
+	legend = ax.legend(loc='best', shadow=True)
 	fig.savefig(regime+'_xSec_100TeV.pdf')
 
 chi2tab_all = [] # All chi2 tables
@@ -85,9 +86,8 @@ for regime in regimes:
 			SigSM = cutflows[fname(1)+regime][cut]		 # Cross-section at lambda=1
 
 			if SigLam != 0: # Intermediate has a unfilled cut
-				err1 = math.sqrt(SigSM/lumi)
-				err2 = math.sqrt(SigLam/lumi)
-				chi2 = pow(SigSM-SigLam,2)/(pow(err1,2) +pow(err2,2)+ pow(sysErr*SigSM,2))
+				err = math.sqrt(SigLam/lumi)
+				chi2 = pow(SigSM-SigLam,2)/(pow(err,2)+ pow(sysErr*SigSM,2))
 				chi2vals.append(chi2)
 			else: 
 				chi2vals.append(-1)
@@ -101,7 +101,7 @@ fig, ax = plt.subplots()
 ax.set_ylabel("$\chi^2$")
 ax.set_xlabel("$\lambda$")
 ax.set_ylim([0,10])
-fig.suptitle("$\chi^2$ profile for all topologies $\sqrt{s}=100$ TeV L="+str(lumi)+"fb$^{-1}$")
[…]

### 2016-02-18 paper-lambda/paperscripts/lambda_noPU_cutflow.py

@@ -16,7 +16,7 @@ regimeLong = { 'res': "Resolved", 'inter': "Intermediate", 'boost': "Boosted"}
 Cnum = ['C0', 'C1a', 'C1b', 'C1c', 'C1d', 'C1e', 'C2' ]
 
 lumi = 3000.0
-sysErr = 0.1 # 10%
+sysErr = 0.0 # 10%
 
 def fname(lval):
 	return "diHiggs_LAM"+str(lval).replace(".","_")+"/"
@@ -60,8 +60,9 @@ for regime in regimes:
 		xsec = []
 		for lvalue in lvalues:
 			xsec.append(cutflows[fname(lvalue)+regime][cut])
-		ax.plot(lvalues, xsec, color=colours[icol])
+		ax.plot(lvalues, xsec, color=colours[icol], label=Cnum[cut])
 		icol = icol + 1
+	legend = ax.legend(loc='best', shadow=True)
 	fig.savefig(regime+'_xSec_14TeV.pdf')
 
 chi2tab_all = [] # All chi2 tables
@@ -85,9 +86,8 @@ for regime in regimes:
 			SigSM = cutflows[fname(1)+regime][cut]		 # Cross-section at lambda=1
 
 			if SigLam != 0: # Intermediate has a unfilled cut
-				err1 = math.sqrt(SigSM/lumi)
-				err2 = math.sqrt(SigLam/lumi)
-				chi2 = pow(SigSM-SigLam,2)/(pow(err1,2) +pow(err2,2)+ pow(sysErr*SigSM,2))
+				err = math.sqrt(SigLam/lumi)
+				chi2 = pow(SigSM-SigLam,2)/(pow(err,2)+ pow(sysErr*SigSM,2))
 				chi2vals.append(chi2)
 			else: 
 				chi2vals.append(-1)
@@ -101,7 +101,7 @@ fig, ax = plt.subplots()
 ax.set_ylabel("$\chi^2$")
 ax.set_xlabel("$\lambda$")
 ax.set_ylim([0,10])
-fig.suptitle("$\chi^2$ profile for all topologies $\sqrt{s}=14$ TeV L="+str(lumi)+"fb$^{-1}$")
+fig.suptitle("$\chi^2$ profile for all topologies $\sqrt{s}=14$ TeV L="+str(lumi)+"fb$^{-1}$. SysErr="+str(sysErr*100) + "%")
 
 # Print out final values
 ireg=0
[…]

### 2016-02-19 FCCreport/HH4b.tex
Created FCCreport folder

\documentclass[a4paper,11pt]{article}
\pdfoutput=1
%\usepackage{jheppub}
\usepackage{graphicx}% Include figure files
\usepackage{graphics}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{epstopdf}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
%\usepackage[pdftex]{hyperref}
%\usepackage{natbib}
\usepackage{multirow,cite}

\bibliographystyle{JHEP}

\def\bs{\boldsymbol}
\def\del{\partial}

%\def\p{{\boldsymbol p}_{\perp }}
%\def\pb{\bar {\boldsymbol p}_{\perp }}
%\def\pp{{\boldsymbol p}_{\perp }}
\def\p{{\boldsymbol p}}
\def\pb{\bar {\boldsymbol p}}
\def\pp{{\boldsymbol p}}
%\def\q{{\boldsymbol q}_\perp}
\def\q{{\boldsymbol q}}
\def\l{{\boldsymbol l}_\perp}
%\def\k{{\boldsymbol k}_\perp}
\def\k{{\boldsymbol k}}
\def\m{{\boldsymbol m}_\perp}
%\def\x{{\boldsymbol x}_\perp}
\def\x{{\boldsymbol x}}
\def\y{{\boldsymbol y}_\perp}
\def\X{{\boldsymbol X}_\perp}
\def\Y{{\boldsymbol Y}_\perp}
\def\D{{\boldsymbol D}_\perp}
\def\r{{\boldsymbol r}_\perp}
\def\z{{\boldsymbol z}_\perp}
%\def\v{{\boldsymbol v}_\perp}
\def\v{{\boldsymbol v}}
\def\w{{\boldsymbol w}_\perp}
\def\b{{\boldsymbol b}_\perp}
\def\Q{{\boldsymbol Q}_\perp}
\def\M{{\boldsymbol M}_\perp}
%\def\bkappa{{\boldsymbol \kappa}_\perp}
%\def\bbkappa{\bar{\boldsymbol \kappa}_\perp}
\def\bkappa{{\boldsymbol \kappa}}
\def\bbkappa{\bar{\boldsymbol \kappa}}
\def\bnu{{\boldsymbol \nu}_\perp}
\def\V{\hat{\boldsymbol v}_{1\perp}}
\def\K{\hat{\boldsymbol k}_{1\perp}}
\def\bV{\hat{\boldsymbol v}_{2\perp}}
\def\bK{\hat{\boldsymbol k}_{2\perp}}
\def\qqb{{q\bar q}}
\def\sM{{\scriptscriptstyle M}}

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\nn}{\nonumber\\ }
\newcommand{\labe}{\label}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}

%\bibliographystyle{JHEP}

%\textwidth=15.0cm \textheight=23.5cm
\textwidth=16.0cm \textheight=23.0cm 
\topmargin 0cm \oddsidemargin 0cm 
\setlength{\unitlength}{1mm}

\usepackage{url}
\usepackage{hyperref}

\begin{document}

\begin{center}
  {\Large \bf Extracting the Higgs self-coupling at a 100 TeV\\[0.2cm] hadron
  collider in the $b\bar{b}b\bar{b}$ final state}
\vspace{.7cm}

J. Katharina Behr, Daniela Bortoletto, James A. Frost,\\
  Nathan P. Hartland, Cigdem Issever and Juan Rojo

\vspace{.3cm}
{\it Physics Department, 1 Keble Road, University of Oxford, United Kingdom }

\end{center}
\vspace{1cm}

\paragraph{Introduction}

In this contribution, we provide a first estimate of the accuracy
in the Higgs self-coupling that can be achieved at a 100 TeV
hadron collider in the  $b\bar{b}b\bar{b}$ final state.
%
The analysis methodology is based on our recent feasibility
study~\cite{Behr:2015oqq}
for 14 TeV, with suitable modifications for the case of 100 TeV,
as we discuss below.
%
 Our strategy is based upon a combination of traditional cut-based
 methods and multivariate analysis (MVA).
  %
  We account for  all relevant
  backgrounds, including the contribution from mis-identified
  light and charm jets.
  %
  We also assess the robustness of our analysis strategy in
  an environment with high pileup (PU).
  %
 Our results indicate that 
  the $b\bar{b}b\bar{b}$ 
final state
alone should allow for the observation of double Higgs production
  at the HL-LHC.
  %
  We now discuss how our findings apply to the case of a 100
  TeV collider.
  %
  We note that other studies of Higgs pair production in this
final state can be found in Refs.~\cite{Wardrope:2014kya,deLima:2014dta}.

\paragraph{Monte Carlo sampling generation}

Higgs pair production is simulated at leading order (LO) using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored  model~\cite{Maltoni:2014eza}
for gluon-fusion Higgs boson pair production
which includes mass effects
from the
exact form factors for the top-quark triangle and box
loops~\cite{Plehn:1996wb}.
%
The calculation is performed in the
$n_f$=4 scheme,  accounting for  $b$-quark mass effects. 
The renormalization and factorization
scales are taken to be $\mu_F=\mu_R=H_T/2$.
%
For the input parton distribution functions (PDFs) we 
adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$,
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
The Higgs boson couplings
and branching ratios are set to their SM values,
and its mass is taken to be
$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba,Aad:2015zhl}.
%
To achieve the correct higher-order value of the
integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLL
inclusive calculation~\cite{deFlorian:2013jea,deFlorian:2015moa}.
%
Parton level signal events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201},
using the  Monash 2013 tune~\cite{Skands:2014pea},
based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx,Ball:2013hta}.
%
Background samples are generated at leading order
with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
we use as
factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
%
We account for all relevant background
processes that can mimic the
 $hh\to 4b$ signal process.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ production, and top quark pair
production.
%
Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
and are therefore not included in the present analysis.
%
The LO cross-sections for
the background samples have been rescaled so that the integrated
distributions reproduce known higher-order QCD results.
%
We take into account the finite energy and angular resolution of 
hadronic calorimeters.

\paragraph{Analysis strategy.}
After the parton shower, final state particles
are clustered using the
jet reconstruction algorithms
of
{\tt FastJet}~\cite{Cacciari:2011ma,Cacciari:2005hq},
{\tt v3.1.0}.
%
We use the following jet definitions:
\begin{itemize}
\item {\it Small-$R$ jets}, reconstructed with the
  anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with $R=0.4$ radius.
  %
  Small-$R$ jets are required
  to have transverse momentum $p_T \ge 40$~GeV
  and pseudo-rapidity $|\eta|<2.5$,

\item {\it Large-$R$ jets},  reconstructed with 
  anti-$k_T$ with $R=1.0$.
  %
  These are required to have
  $p_T \ge 200$~GeV, lie in the
  $|\eta|<2.0$ region and
  satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}.

\item {\it Small-$R$ subjets}, constructed by 
  by clustering all final-state particles with
 anti-$k_T$ with  $R=0.3$, that are then
 ghost-associated  to the large-$R$ jets~\cite{Aad:2015uka}.
 %
 They
  are required to satisfy
  $p_T > 50$~GeV and $|\eta|<2.5$.
\end{itemize}

For the   boosted and intermediate categories,
which involve large-$R$ jets,
we use a number of jet substructure variables~\cite{Salam:2009jx,Aad:2013gja}:
the $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}, the ratio of 2-to-1 subjettiness $\tau_{21}$~\cite{Thaler:2010tr,Thaler:2011gf}, and the ratios of energy correlation functions (ECFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
$D_2^{(\beta)}$~\cite{Larkoski:2014gra}.
%
For each jet definition described above, a different
$b$-tagging strategy is adopted:

\begin{itemize}

\item {\it Small-$R$ jets}. If a small-$R$ jet has at least one $b$-quark among their constituents,
  it will be tagged as a $b$-jet with probability $f_b$.
  %
  In order to be considered in the $b$-tagging algorithm,
  $b$-quarks inside the small-$R$ jet
  should satisfy $p_T \ge 15$ GeV~\cite{Aad:2015ydr}.
  %
  The probability of tagging a jet is not modified
  if more than one $b$-quark is found among the jet constituents.
  %  
  If no $b$-quarks are found among the constituents
  of this jet, it can be still be tagged as a $b$-jet with
  a mistag rate of $f_l$, unless a charm quark is present instead,
  and in this case the mistag rate is $f_c$.
  %
  Only jets that contain at least one (light or charm)
  constituent
  with $p_T \ge 15$ GeV can induce a fake $b$-tag.
  %

  \item {\it Large-$R$ jets}. Large-$R$ jets are $b$-tagged by
    ghost-associating anti-$k_T$ $R=0.3$ (AKT03)
    subjets to the original large-$R$
    jets~\cite{Cacciari:2007fd,Aad:2013gja,
      ATLAS-CONF-2014-004,Aad:2015uka}.
    %
    A large-$R$ jet is considered $b$-tagged if both
    the leading and subleading AKT03 subjets, where the ordering
    is done in the subjet $p_T$, are both individually $b$-tagged,
    with the same criteria as the small-$R$ jets.
    %
     Therefore, a large-$R$ jet where the two leading
    subjets have at least one $b$-quark will be tagged
    with probability $f_b^2$.
    %
    As in the case
    of small-$R$ jets, we only attempt to $b$-tag the two leading subjets,
    else one finds a degradation of the
    signal significance.
    %
    The treatment of the $b$-jet mis-identification
    from light and charm jets
    is the same as for the small-$R$ jets.

\end{itemize}

For the $b$-tagging probability $f_b$, along with
the $b$-mistag probability of light ($f_l$) and charm ($f_c$) jets,
we use the values $f_b=0.8$, $f_l=0.01$
and  $f_c=0.1$.
%The s
Our analysis strategy follows the
scale-invariant resonance tagging of Ref.~\cite{Gouzevitch:2013qca}.
%
Rather than restricting to a specific event topology,
we consistently combine the information from
the three possible topologies: boosted, intermediate and
resolved, with the optimal cuts for each category being determined
separately.
%
The three categories are defined as follows:
\begin{itemize}
\item {\it Boosted category}. An event which
  contains at least two large-$R$ jets, with the two leading jets
 being $b$-tagged.
\item {\it Intermediate category}. An event with exactly one  $b$-tagged, large-$R$ jet, which
  is assigned to be the leading Higgs candidate.
  %
  In addition, we require at least two $b$-tagged, small-$R$ jets,
  which must be separated with respect to the large-$R$ jet
  by  $\Delta R\ge 1.2$.
  %

\item {\it Resolved category}. An event with at least
  four $b$-tagged small-$R$ jets.
  %
  The two Higgs candidates are reconstructed out of the
  leading four small-$R$ jets in the event by minimizing the relative difference of
  dijet masses.
  %

\end{itemize}
Once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
of width $80~{\rm GeV}$ around the nominal Higgs boson mass of $m_h= 125$
GeV.
%

\paragraph{Results.} We now discuss the results of our analysis
at the end of the MVA.
%
First we discuss the statistical significance of a measurements
of the $hh\to 4b$ cross-section at 100 TeV and then provide
a first estimate on the accuracy of the extraction of the self-coupling.
%
The specific type of  MVA that we use to
disentangle signal and background events is
a multi-layer feed-forward artificial neural network (ANN),
known as a {\it perceptron}.
%
This family of ANNs are also known as {\it deep neural networks},
due to their multi-layered architecture.
%
The MVA inputs are a set of kinematic variables describing the
signal and background
events which satisfy the requirements of the
cut-based analysis.
%
The output of the trained ANNs also allows for the identification,
in a fully automated way,
of the most relevant variables in the discrimination between 
signal and background.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/ssb_noPU.pdf}
\includegraphics[width=0.48\textwidth]{plots/sb_noPU.pdf}
\caption{\small
  The values of the signal significance, $S/\sqrt{B}$, and of the
  signal over background ratio, $S/B$, for the boosted, intermediate
  and resolved categories as a function of the cut
  $y_{\rm cut}$ in the ANN output.
  %
  The $y_{\rm cut}=0$
  results are those at the end of the cut-based
  analysis. {\bf Update with 100 TeV numbers}
}
\label{fig:sb_mva}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

The results for the signal significance $S/\sqrt{B}$ and
the signal over background ratio
$S/B$ as a function of $y_{\rm cut}$
for the three categories are given in 
Fig.~\ref{fig:sb_mva}.
%
The values 
for $y_{\rm cut}=0$ correspond to those at
the end of the loose cut-based analysis.
%
We observe how in the three
 categories there is a marked  improvement in signal
significance as compared to the pre-MVA results.
%
We also observe a substantial enhancement in $S/B$, arising
from the background suppression achieved by the MVA, reaching
values of 1\%, 6\% and 3.5\% in the resolved,
intermediate and boosted categories.
%
This improvement in $S/B$ is crucial to ensure the feasibility
of this measurement, since it allows systematic
uncertainties in the background determination to
be at most of a similar size.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{|c|l|c|c|c|c|}
    \hline
    \multicolumn{6}{|c|}{FCC100, $\mathcal{L}=10$ ab$^{-1}$} \\
    \hline
    \hline
    Category  &   &  $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
    \hline
    \hline
    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  &        &           &          &         \\
    &  $y_{\rm cut}=$ &       &           &          &         \\
    \hline
    \hline
    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &        &           &          &         \\
       &  $y_{\rm cut}=$ &       &           &          &         \\
    \hline
    \hline
      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &         &           &          &         \\
    &  $y_{\rm cut}= $ &        &           &          &         \\
    \hline
      \end{tabular}
  \caption{\small Post-MVA results, for the optimal value of the
    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
    corresponding
    pre-MVA results ($y_{\rm cut}=0$).
    %
    We quote the number of signal and
    background events expected for $\mathcal{L}=10$ ab$^{-1}$,
    the signal significance $S/\sqrt{B}$ and
    the signal over background ratio $S/B$.
    %
    \label{table:cutflowMVA}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

From Table~\ref{table:cutflowMVA} we see that
following the application of the MVA, 
the signal significance in the boosted category increases
from 0.5 to 2.7, with $S/B$ increasing from $0.06\%$ to $3\%$.
%
For the intermediate and resolved categories, $S/\sqrt{B}$
increases from 0.4 to 2.3 and 1.9 respectively, with
the signal over background ratio raising from
$0.05\%$ and $0.01\%$ to 4\% and 1\%.
%
Once the MVA training has been completed, it is possible
to estimate, for each value of
the cut in the ANN output $y_{\rm cut}$, how many
signal and background events are expected at the FCC100
assuming a total integrated luminosity of
 $\mathcal{L}=10$ ab$^{-1}$.
%
We also observe that
in the boosted category, for a value $y_{\rm cut}\simeq 0.9$
we end up with around 300 signal events and $10^4$ background
events.
%
Similar results are obtained in the intermediate and resolved
categories: in the former we find 130 ($3\cdot 10^3$) signal (background)
events for $y_{\rm cut}\simeq 0.85$ (0.60), and in the latter
630 ($10^5$) signal (background) events for
$y_{\rm cut}\simeq 0.6$.
%
Combining the three categories, taking into
account all background components, we obtain for
$\mathcal{L}=10$ ab$^{-1}$ an overall signal
significance of $S/\sqrt{B}\simeq 4.0$.
%
This is a substantial improvement over the corresponding
estimator at 14 TeV.

\paragraph{Extracting the Higgs self-coupling.}  The extraction of the trilinear coupling $\lambda$ from the
  corresponding cross-section is complicated by the
  destructive interference
  between diagrams that depend on $\lambda$ and those that do not.
  %
  Therefore, a measurement of the Higgs pair production
  cross-section does not guarantee an accurate enough determination of the trilinear
  coupling $\lambda$.
  %
 Here we provide a first estimate of the accuracy
  in Higgs self-coupling extraction from the $b\bar{b}b\bar{b}$ final state
  that can be achieved 100 TeV hadron collider.
  %
  A robust estimate of the accuracy of this measurement would requires
  a careful study of the impact 
  experimental systematic uncertainties, which is beyond the scope of this contribution.
  %
  Therefore, we will use a number of simplifying assumptions.

  The sensitivity of in the Higgs self-coupling can be estimated by defining a $\chi^2$
  \be
  \label{eq:chi2profile}
  \chi^2(\lambda) = \frac{\lc \sigma(hh,\lambda) - \sigma(hh,\lambda_{\rm SM})
    \rc^2}{\lp \delta_{\rm stat}\sigma\rp^2+\lp \delta_{\rm sys}\sigma\rp^2 } \, ,
  \ee
  where $\lambda$ is the self-coupling, $\lambda_{\rm SM}$ is the SM value, $\sigma(\lambda)$ is the
  post-MVA signal cross-section for a given value of $\lambda$ and $\delta_{\rm stat}\sigma$ and
  $\delta_{\rm sys}\sigma$ are respectively the statistical and systematic uncertainties in the cross-section
  measurement.
  %
  Signal samples for a range of $\lambda$ values have been generated, and have then been processed
  by the same analysis chain, including the MVA, than the SM samples.
  %
  To avoid introducing theoretical biases, the MVA is non-retrained for the $\lambda\ne \lambda_{\rm SM}$ values.
  %
  The 68\% CL range for the extraction of $\lambda$ can then be found by determining the values $\pm \delta\lambda$
  for which the cross-section satisfies
  \be
  \label{eq:condition}
\chi^2(\lambda_{\rm SM}~^{+\delta\lambda}_{-\delta\lambda})=\chi^2(\lambda_{\rm SM})+1 \, .
\ee
The statistical error is given by $1/\sqrt{N_{\rm ev}}$ with $N_{\rm ev}$ is the post-MVA number of events in each analysis
category.
%
We explore different assumptions on the value of the total systematic uncertainty $\delta_{\rm sys}\sigma$.
%
The final result for the accuracy in the trilinear extraction is obtained by combining the separate results
from the three exclusive categories.

In Fig.~\ref{fig:chi2} we show the post-MVA cross-section in the resolved, intermediate
  and boosted categories as a function of the Higgs self-coupling
  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
  %
  In the same figure we also show the $\chi^2(\lambda)$ profile, Eq.~(\ref{eq:chi2profile})
  for the three categories, assuming a total systematic uncertainty of
  10\%.
  %
  Imposing the condition Eq.~(\ref{eq:condition}), we obtain that at the 68\% CL we can constrain the
  Higgs trilinear to be ....

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/res.pdf}
\includegraphics[width=0.48\textwidth]{plots/chi2.pdf}
\caption{\small
  Left plot: the post-MVA cross-section in the resolved, intermediate
  and boosted categories as a function of the Higgs self-coupling
  $\lambda/lambda_{\rm SM}$ in units of the SM coupling.
  %
  Right plot: the $\chi^2(\lambda)$ profile, Eq.~(\ref{eq:chi2profile})
  for the three categories, assuming a total systematic uncertainty of
  10\%.
  {\bf Update}
}
\label{fig:chi2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Summary.} In this contribution we have performed a first exploration of the accuracy that can be expected
for the extraction of the Higgs self-couplings at a 100 TeV hadron collider using the $b\bar{b}b\bar{b}$ final state.

%%%%%%%%%%%%%%%%%%

\bibliography{HH4b}

\end{document}

### 2016-02-19 FCCreport/paperscripts/plotHist_m_hh_bst_comp_back.py

@@ -1,0 +1,132 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "m_hh_bst_comp_back"
+
+linestyles = [ 'solid', 'dashed','solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_m_HH_boost_C1e.dat")
+datafiles.append("../plotdata/results_SK_PU80/background/histo_m_HH_boost_C1e.dat")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+# Axis labels
+xLabel = "Invariant mass of Di-Higgs (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'b', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+
+ax.set_xlim([400,600])
+ax.set_ylim([1e-5,0.015])
+
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2016-02-19 FCCreport/paperscripts/plotHist_ptH0_res_comp.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_H0_C2_res_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_H0_res_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_pt_H0_res_C2.dat")
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"PU80+SK")
+
+# Axis labels
+xLabel = "Leading Higgs Candidate $p_{T}$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,700])
+ax.set_ylim([1e-4,0.05])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2016-02-19 FCCreport/paperscripts/plotHist_pt_H0_sub0_res_noPU_ANNcut_back_4b.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_H0_sub0_res_noPU_ANNcut_back_4b"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("histo_pt_H0_sub0_y00_back4b.dat")
+datafiles.append("histo_pt_H0_sub0_y06_back4b.dat")
+
+# Plot labels
+plotnames.append(r"pre-MVA, $y_{cut}=0.0$")
+plotnames.append(r"post-MVA, $y_{cut}=0.6$")
+
+# Axis labels
+xLabel = r"Leading AKT04 $b$-jet $p_T$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = False
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([50,300])
+ax.set_ylim([0.001,1000])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2016-02-19 FCCreport/paperscripts/plotHist_pt_H1_bst_noPU.py

@@ -1,0 +1,130 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "pt_H1_bst_C1d_noPU"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_pt_H1_boost_C1d.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_pt_H1_boost_C1d.dat")
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+# Axis labels
+xLabel = "Sub-leading Higgs Candidate $p^{h}_T$ (GeV)"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([190,600])
+ax.set_ylim([1e-4,0.02])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
+      xlo.append(float(linesplit[0]))
[…]

### 2016-02-19 FCCreport/paperscripts/plotHist_tau21_h0_bst_comp.py

@@ -1,0 +1,129 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "tau21_h0_bst_comp"
+
+linestyles = [ 'solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_tau21_fj1_boost_C2.dat")
+datafiles.append("../plotdata/results_SK_PU80/diHiggs/histo_tau21_fj1_boost_C2.dat")
+
+# Plot labels
+plotnames.append("no PU")
+plotnames.append(r"PU80+SK+Trim")
+
+# Axis labels
+xLabel = r"Subjettiness Ratio $\tau_{12}$ for leading Higgs candidate"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = True
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,1])
+ax.set_ylim([0.005,10])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2016-02-19 FCCreport/paperscripts/plotHist_tau21_h1_C1_boost.py

@@ -1,0 +1,131 @@
+#! /usr/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+import sys, os, math
+import numpy as np
+
+datafiles = []
+plotnames = []
+
+############################## Settings ###############################
+
+# Output filename
+outfile = "tau21_h1_C1_boost"
+
+linestyles = [ 'solid', 'dashed','solid', 'dashed']
+
+# Datafiles
+datafiles.append("../plotdata/results_noPU/diHiggs/histo_tau21_fj2_boost_C1e.dat")
+datafiles.append("../plotdata/results_noPU/background/histo_tau21_fj2_boost_C1e.dat")
+
+
+# Plot labels
+plotnames.append("Signal")
+plotnames.append("Background")
+
+
+# Axis labels
+xLabel = r"Subjettiness ratio $\tau_{21}$ in subleading Higgs candidate"
+yLabel = "a. u."
+
+# Log axes
+xLog = False
+yLog = False
+
+# Normalise histograms
+normalise = True
+
+#######################################################################
+
+if len(datafiles)!=len(plotnames):
+  print "Error: datafile and plotname arrays are different lengths!"
+  exit()
+
+colours = ['r', 'b', 'b', 'b']
+icol = 0
+
+# Setup figure
+fig, ax = plt.subplots()
+if xLog == True:
+  ax.set_xscale('log')
+if yLog == True:
+  ax.set_yscale('log')
+
+ax.set_ylabel(yLabel)
+ax.set_xlabel(xLabel)
+
+ax.set_xlim([0,1.0])
+ax.set_ylim([0,3])
+
+for idat in xrange(0,len(datafiles)):
+
+  # Verify paths
+  infilenm = datafiles[idat]
+  if os.path.exists(infilenm) == False:
+    print "Error: source file" + infilenm + " not found!"
+    sys.exit()
+  
+  infile = open(infilenm, 'rb')
+  datafile = open(infilenm, 'rb')
+
+  xhi = []
+  xlo = []
+  yval = []
+
+  errup = []
+  errdn = []
+
+  dataread = False
+  for line in datafile:
+    linesplit = line.split()
+
+    if len(linesplit) == 1:
+      continue
+
+    if linesplit[1] == 'END':
+      break
+
+    if dataread == True:
[…]

### 2016-02-19 FCCreport/paperscripts/plotMVAdat_PU150_resc_4b.py

@@ -1,0 +1,248 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../plotdata/results_SK_PU150_v2/MVA/nn_13X5X3X1_50000-Gen_resNTuple_4b.dat",
+            "../plotdata/results_SK_PU150_v2/MVA/nn_17X5X3X1_50000-Gen_intNTuple_4b.dat",
+            "../plotdata/results_SK_PU150_v2/MVA/nn_21X5X3X1_50000-Gen_bstNTuple_4b.dat"]
+
+datanames=[ "Resolved","Intermediate","Boosted"]
+titlenames=[ r"Resolved Category,  $\langle n_{PU}\rangle =150$+SK",
+             r"Intermediate Category,  $\langle n_{PU}\rangle =150$+SK",\
+             r"Boosted Category,  $\langle n_{PU}\rangle=150$+SK"]
+
+datanamessignal=[ "Signal Res","Signal Int","Signal Boost"]
+datanamesback=[ "Background Res","Background Int","Background Boost"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_SKPU150_4b"  # Histograms for discriminant
+ROCout = "roc_SKPU150_4b"	  # ROC curve
+SBout = "sb_SKPU150_4b"	  # S/B curve
+SSBout = "ssb_SKPU150_4b"	  # S/Sqrt(B) curve
+NeVout = "nev_SKPU150_4b"	  # Number of events (twin axes)
+NeV2out = "nev2_SKPU150_4b"  # Number of events (single axis)
+
+# Rescaling factor for signal
+resc = 0.41
+
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background,title):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
[…]

### 2016-02-19 FCCreport/paperscripts/plotMVAdat_PU80_resc.py

@@ -1,0 +1,249 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../plotdata/results_SK_PU80/MVA/nn_13X5X3X1_50000-Gen_SKPU80_res.dat",
+            "../plotdata/results_SK_PU80/MVA/nn_17X5X3X1_50000-Gen_SKPU80_int.dat",
+            "../plotdata/results_SK_PU80/MVA/nn_21X5X3X1_50000-Gen_SKPU80_bst.dat"]
+
+datanames=[ "Resolved","Intermediate","Boosted"]
+titlenames=[ r"Resolved Category,  $ n_{PU} =80$+SK",
+             r"Intermediate Category,  $ n_{PU} =80$+SK",\
+             r"Boosted Category,  $ n_{PU}=80$+SK"]
+
+datanamessignal=[ "Signal Res","Signal Int","Signal Boost"]
+datanamesback=[ "Background Res","Background Int","Background Boost"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_SKPU80"  # Histograms for discriminant
+ROCout = "roc_SKPU80"	  # ROC curve
+SBout = "sb_SKPU80"	  # S/B curve
+SSBout = "ssb_SKPU80"	  # S/Sqrt(B) curve
+NeVout = "nev_SKPU80"	  # Number of events (twin axes)
+NeV2out = "nev2_SKPU80"  # Number of events (single axis)
+
+# Rescaling factor for signal
+resc = 0.41
+
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background,title):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
+	ax.hist(signal, bins, color='r', alpha=0.8, normed=True, label = "Signal",linewidth=2)
[…]

### 2016-02-19 FCCreport/paperscripts/plotNetwork_bst_noPU.py

@@ -1,0 +1,142 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+import matplotlib.pyplot as plt
+import networkx as nx
+import os
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+import numpy
+import sys
+
+################################ Settings ###################################
+
+# Init data
+datafile = '../plotdata/results_noPU/MVA/nn_21X5X3X1_50000-Gen_noPU_bst.net'
+dataname = "Boosted"
+sourcefile = os.path.expanduser(datafile)
+
+archout = "bst_nnarch_noPU"
+histout = "bst_wgthist_noPU"
+
+#############################################################################
+
+# Verify paths
+if os.path.exists(sourcefile) == False:
+  	print "Error: source file" + sourcefile + " not found!"
+  	sys.exit()
+
+infile = open(sourcefile, 'rb')
+print "Processing " + sourcefile + " ..."
+
+# Read architecture
+line = infile.readline()
+arch = []
+for ls in line.split():
+	arch.append(int(ls))
+nNodes = sum(arch)
+
+# Read kinematics names
+line = infile.readline()
+kinematics = []
+for ls in line.split():
+	kinematics.append(ls)
+
+# Init graph
+G=nx.Graph()
+
+weights = []
+thresholds = [0]
+
+line = infile.readline()
+for line in infile:
+	iNode = int(line.split()[0])
+	tNode = int(line.split()[1])
+	threshold = float(line.split()[2])
+	weight = abs(float(line.split()[3]))
+
+	weights.append(weight)
+	thresholds.append(threshold)
+
+	# Add the edge
+	G.add_edge(iNode, tNode, wgt = weight )
+	# Add threshold weight
+	G.node[iNode]['bias'] = threshold
+	if tNode < arch[0]:
+		G.node[tNode]['bias'] = 0
+
+	# Init labels
+	G.node[iNode]['label'] = ''
+	if tNode < arch[0]:
+		G.node[tNode]['label'] = tNode
+	else:
+		G.node[tNode]['label'] = ''
+
+# Get input weights
+sumw = []
+for i in xrange(0,arch[0]):
+	G.node[i]['sumw'] = 0
+	for j in G.neighbors(i):
[…]

### 2016-02-19 FCCreport/paperscripts/plotNetwork_res_noPU.py

@@ -1,0 +1,142 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+import matplotlib.pyplot as plt
+import networkx as nx
+import os
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+import numpy
+import sys
+
+################################ Settings ###################################
+
+# Init data
+datafile = '../plotdata/results_noPU/MVA/nn_13X5X3X1_50000-Gen_noPU_res.net'
+dataname = "Resolved"
+sourcefile = os.path.expanduser(datafile)
+
+archout = "res_nnarch_noPU"
+histout = "res_wgthist_noPU"
+
+#############################################################################
+
+# Verify paths
+if os.path.exists(sourcefile) == False:
+  	print "Error: source file" + sourcefile + " not found!"
+  	sys.exit()
+
+infile = open(sourcefile, 'rb')
+print "Processing " + sourcefile + " ..."
+
+# Read architecture
+line = infile.readline()
+arch = []
+for ls in line.split():
+	arch.append(int(ls))
+nNodes = sum(arch)
+
+# Read kinematics names
+line = infile.readline()
+kinematics = []
+for ls in line.split():
+	kinematics.append(ls)
+
+# Init graph
+G=nx.Graph()
+
+weights = []
+thresholds = [0]
+
+line = infile.readline()
+for line in infile:
+	iNode = int(line.split()[0])
+	tNode = int(line.split()[1])
+	threshold = float(line.split()[2])
+	weight = abs(float(line.split()[3]))
+
+	weights.append(weight)
+	thresholds.append(threshold)
+
+	# Add the edge
+	G.add_edge(iNode, tNode, wgt = weight )
+	# Add threshold weight
+	G.node[iNode]['bias'] = threshold
+	if tNode < arch[0]:
+		G.node[tNode]['bias'] = 0
+
+	# Init labels
+	G.node[iNode]['label'] = ''
+	if tNode < arch[0]:
+		G.node[tNode]['label'] = tNode
+	else:
+		G.node[tNode]['label'] = ''
+
+# Get input weights
+sumw = []
+for i in xrange(0,arch[0]):
+	G.node[i]['sumw'] = 0
+	for j in G.neighbors(i):
[…]

### 2016-02-19 doc/benchmark/benchmark.tex

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Benchmark of updated code}

\begin{document}
\maketitle

A number of major code changes have taken place since the arXiv release of our paper, most of these
are purely architectural but a few may have physics impacts. Here we shall briefly investigate the impact
of these differences.

The primary physics modifications are:
\begin{itemize}
\item{} Pileup has been improved, now MinBias events are generated on the fly, so there is no longer any re-use of PU events. 
\item{} The previous MinBias events were (erroneously) hadronised, this has now also been corrected.
\item{} PU subtraction via SoftKiller has been moved such that it is performed \emph{after} our detector smearing.
\item{} The correct HH$\to$4b branching ratios have been introduced.
\item{} A degree of MVA tuning to improve learning.
\item{} (extremely minor) RNG for detector smearing has been improved.
\item{} (probably 0 effect) Moved to fastjet to compute most substructure observables.
\end{itemize}

\section{noPU validation}
First we examine the changes outside of PU generation. Here in the figure captions the run `results\_noPU' refer to the old arXiv runs and  `baseline\_noPU\_oxford' refers to the updated runs. In Figure \ref{fig:noPUboost} we compare the two runs for the $HH$ and total background samples. From these plots it is clear that there is no significant change in the results due to the non-PU related modifications.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/diHiggs_noPU_CF.pdf}
\includegraphics[width=0.45\textwidth]{plots/background_noPU_CF.pdf}
\caption{Cutflows for the updated noPU oxford analysis, in the boosted topology for $HH$ samples (left) and total background (right).}
\label{fig:noPUboost}
\end{center}
\end{figure}
\newpage
\section{PU validation}
Now we look at the differences arising due to the new PU handing. In Figure \ref{fig:PU80CF} we show the cutflows for all topologies, once again for the $HH$ and total background samples. Here we see some genuine differences between the old and new analyses. To verify our analyses at the level of signal significances, Figure \ref{fig:PU80sig} shows the $S/\sqrt{B}$ distributions with ANN cut.  There is a significant degree of movement between the old and new analyses, but overall significances are likely to remain similar.

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/diHiggs_PU80_CF_boost.pdf}
\includegraphics[width=0.45\textwidth]{plots/background_PU80_CF_boost.pdf}\\
\includegraphics[width=0.45\textwidth]{plots/diHiggs_PU80_CF_inter.pdf}
\includegraphics[width=0.45\textwidth]{plots/background_PU80_CF_inter.pdf}\\
\includegraphics[width=0.45\textwidth]{plots/diHiggs_PU80_CF_res.pdf}
\includegraphics[width=0.45\textwidth]{plots/background_PU80_CF_res.pdf}
\caption{Cutflows for the updated PU80 oxford analysis, for $HH$ samples (left) and total background (right). Figures are shown for the boosted (top), intermediate (centre) and resolved (bottom) topologies.}
\label{fig:PU80CF}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/ssb_SKPU80.pdf}
\includegraphics[width=0.45\textwidth]{plots/ssb_SKPU80_new.pdf}\\
\caption{Significances after MVA in the old (left) and new (right) analyses.}
\label{fig:PU80sig}
\end{center}
\end{figure}

%\subsection{}

\end{document}

### 2016-02-19 paper-lambda/summary/lambda.tex

@@
 the 100TeV FCC.
-\subsection{Cross-section variation with $\lambda$}
+\section{Cross-section variation with $\lambda$}
 These figures demonstrate the variation of the $HH$ cross-section with the value of the Higgs trilinear coupling, after processing through our analysis
@@
 \newpage
-\subsection{Trilinear extraction - $\chi2$ profiles}
+\section{Trilinear extraction - $\chi2$ profiles}
 

### 2016-02-23 FCCreport/HH4b.tex
Updated FCCreport

@@
-\documentclass[a4paper,11pt]{article}
+\documentclass[a4paper,10pt]{article}
 \pdfoutput=1
@@
 \end{center}
-\vspace{1cm}
+\vspace{0.2cm}
 
@@
 
-In this contribution, we provide a first estimate of the accuracy
-in the Higgs self-coupling that can be achieved at a 100 TeV
+In this contribution we provide an estimate of the accuracy
+in the Higgs self-coupling extraction that can be achieved at a 100 TeV
 hadron collider in the  $b\bar{b}b\bar{b}$ final state.
 %
-The analysis methodology is based on our recent feasibility
-study~\cite{Behr:2015oqq}
-for 14 TeV, with suitable modifications for the case of 100 TeV,
-as we discuss below.
+The analysis methodology is based on our feasibility
+study at 14 TeV~\cite{Behr:2015oqq}, with suitable modifications for the 100 TeV
+case.
 %
- Our strategy is based upon a combination of traditional cut-based
- methods and multivariate analysis (MVA).
+This strategy is based upon a combination of traditional cut-based
+ methods and Multivariate Analysis (MVA).
   %
@@
   %
-  We also assess the robustness of our analysis strategy in
-  an environment with high pileup (PU).
+  Our analysis strategy is found to be robust even in a high pile-up
+  environment.
   %
- Our results indicate that 
+ Our results at 14 TeV~\cite{Behr:2015oqq} indicate that 
   the $b\bar{b}b\bar{b}$ 
@@
 alone should allow for the observation of double Higgs production
-  at the HL-LHC.
-  %
-  We now discuss how our findings apply to the case of a 100
+  at the HL-LHC, and here we study how our findings apply to the case of a 100
   TeV collider.
   %
-  We note that other studies of Higgs pair production in this
+  Other studies of Higgs pair production in the same
 final state can be found in Refs.~\cite{Wardrope:2014kya,deLima:2014dta}.
 
-\paragraph{Monte Carlo sampling generation}
+\paragraph{Monte Carlo samples generation}
 
-Higgs pair production is simulated at leading order (LO) using
-{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
-%
-We use a tailored  model~\cite{Maltoni:2014eza}
-for gluon-fusion Higgs boson pair production
+Higgs pair production in the gluon-fusion
+channel is simulated at leading order (LO) using
+{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca,Maltoni:2014eza}
+using a tailored  model
 which includes mass effects
 from the
-exact form factors for the top-quark triangle and box
-loops~\cite{Plehn:1996wb}.
+exact form factors.
 %
 The calculation is performed in the
-$n_f$=4 scheme,  accounting for  $b$-quark mass effects. 
-The renormalization and factorization
+$n_f$=4 scheme and
+the renormalization and factorization
 scales are taken to be $\mu_F=\mu_R=H_T/2$.
 %
-For the input parton distribution functions (PDFs) we 
+For the input PDFs we 
 adopt the NNPDF 3.0 $n_f=4$ LO set~\cite{Ball:2014uwa} with
@@
 interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
-%
-The Higgs boson couplings
-and branching ratios are set to their SM values,
-and its mass is taken to be
-$m_h=125$ GeV~\cite{Aad:2014aba,Khachatryan:2014jba,Aad:2015zhl}.
 %
@@
 %
-Background samples are generated at leading order
-with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}.
+Background samples are generated at LO
+with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}
+and rescaled to known higher-order results.
 %
-As in the case of the signal generation,
-the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
-$\alpha_s(m_Z^2)=0.118$ is used for all samples, and
-we use as
-factorisation and renormalisation scales $\mu_F=\mu_R=H_T/2$.
+The input PDFs and scales are the same as for
+the signal samples.
 %
-We account for all relevant background
-processes that can mimic the
- $hh\to 4b$ signal process.
+In this study we include the irreducible QCD $4b$ background
+as well as the reducible $2b2j$ component, since the $4j$ processes
+is shown to be negligible.
 %
-This includes  QCD $4b$ multi-jet production, as well as
-QCD $2b2j$ and $4j$ production, and top quark pair
+We also include top quark pair
 production.
 %
-Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
-and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
-are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
-and are therefore not included in the present analysis.
+Single Higgs production processes and electroweak backgrounds
+are much smaller and not included here.
 %
-The LO cross-sections for
-the background samples have been rescaled so that the integrated
-distributions reproduce known higher-order QCD results.
-%
-We take into account the finite energy and angular resolution of 
-hadronic calorimeters.
 
@@
 %
-We use the following jet definitions:
-\begin{itemize}
-\item {\it Small-$R$ jets}, reconstructed with the
-  anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with $R=0.4$ radius.
+First of all, we define {\it small-$R$ jets}, reconstructed with the
+anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with $R=0.4$,
+and  required
+  to have transverse momentum $p_T \ge 40$~GeV
+  and pseudo-rapidity $|\eta|<2.5$.
   %
-  Small-$R$ jets are required
-  to have transverse momentum $p_T \ge 40$~GeV
-  and pseudo-rapidity $|\eta|<2.5$,
-
-\item {\it Large-$R$ jets},  reconstructed with 
-  anti-$k_T$ with $R=1.0$.
-  %
-  These are required to have
+  The we also define {\it large-$R$ jets},  reconstructed with 
+  anti-$k_T$ with $R=1.0$, and
+   required to have
   $p_T \ge 200$~GeV, lie in the
@@
    satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}.
-
-\item {\it Small-$R$ subjets}, constructed by 
+   %
+   Finally, we define
+  {\it small-$R$ subjets}, constructed  
   by clustering all final-state particles with
@@
  %
- They
+ These
   are required to satisfy
   $p_T > 50$~GeV and $|\eta|<2.5$.
-\end{itemize}
-
+  %
+  Our cuts are deliberately loose since their optimization will be
+  performed at the MVA level.
+%
 For the   boosted and intermediate categories,
 which involve large-$R$ jets,
-we use a number of jet substructure variables~\cite{Salam:2009jx,Aad:2013gja}:
+we also use a number of jet substructure variables~\cite{Salam:2009jx,Aad:2013gja}:
 the $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}, the ratio of 2-to-1 subjettiness $\tau_{21}$~\cite{Thaler:2010tr,Thaler:2011gf}, and the ratios of energy correlation functions (ECFs)  $C^{(\beta)}_2$~\cite{Larkoski:2013eya} and
 $D_2^{(\beta)}$~\cite{Larkoski:2014gra}.
+
+For each jet definition described above, a different
+$b$-tagging strategy is adopted.
 %
-For each jet definition described above, a different
-$b$-tagging strategy is adopted:
-
-\begin{itemize}
-
-\item {\it Small-$R$ jets}. If a small-$R$ jet has at least one $b$-quark among their constituents,
-  it will be tagged as a $b$-jet with probability $f_b$.
-  %
-  In order to be considered in the $b$-tagging algorithm,
-  $b$-quarks inside the small-$R$ jet
-  should satisfy $p_T \ge 15$ GeV~\cite{Aad:2015ydr}.
-  %
-  The probability of tagging a jet is not modified
-  if more than one $b$-quark is found among the jet constituents.
+For  {\it small-$R$ jets}, if it contains at least one $b$-quark among its constituents,
+it will be tagged as a $b$-jet with probability $f_b$, provided
+the $p_T$ of the $b$-quark
+  satisfies $p_T \ge 15$ GeV~\cite{Aad:2015ydr}.
   %
@@
   of this jet, it can be still be tagged as a $b$-jet with
-  a mistag rate of $f_l$, unless a charm quark is present instead,
-  and in this case the mistag rate is $f_c$.
+  a mistag rate of $f_l$, provided it has at least one
+  constituent
+  with $p_T \ge 15$ GeV.
   %
-  Only jets that contain at least one (light or charm)
-  constituent
-  with $p_T \ge 15$ GeV can induce a fake $b$-tag.
-  %
-
-  \item {\it Large-$R$ jets}. Large-$R$ jets are $b$-tagged by
+ For {\it large-$R$ jets} instead, they are $b$-tagged by
     ghost-associating anti-$k_T$ $R=0.3$ (AKT03)
@@
     A large-$R$ jet is considered $b$-tagged if both
-    the leading and subleading AKT03 subjets, where the ordering
-    is done in the subjet $p_T$, are both individually $b$-tagged,
+    the leading and subleading AKT03 subjets are both individually $b$-tagged,
     with the same criteria as the small-$R$ jets.
-    %
-     Therefore, a large-$R$ jet where the two leading
-    subjets have at least one $b$-quark will be tagged
-    with probability $f_b^2$.
-    %
-    As in the case
-    of small-$R$ jets, we only attempt to $b$-tag the two leading subjets,
-    else one finds a degradation of the
-    signal significance.
     %
@@
     is the same as for the small-$R$ jets.
-
-\end{itemize}
-
+  %
 For the $b$-tagging probability $f_b$, along with
@@
 and  $f_c=0.1$.
-%The s
+
 Our analysis strategy follows the
-scale-invariant resonance tagging of Ref.~\cite{Gouzevitch:2013qca}.
+scale-invariant resonance tagging method of Ref.~\cite{Gouzevitch:2013qca}.
 %
@@
 %
-The three categories are defined as follows:
-\begin{itemize}
-\item {\it Boosted category}. An event which
-  contains at least two large-$R$ jets, with the two leading jets
+The three categories are defined as follows.
+%
+Events are classified in the {\it boosted category} if they 
+  contain at least two large-$R$ jets, with the two leading jets
   being $b$-tagged.
-\item {\it Intermediate category}. An event with exactly one  $b$-tagged, large-$R$ jet, which
+  %
+  They will be classified in the
+ {\it intermediate category} if there is exactly one  $b$-tagged, large-$R$ jet, which
   is assigned to be the leading Higgs candidate.
@@
   %
-
-\item {\it Resolved category}. An event with at least
+  Finally, events will be assigned to the {\it resolved category}
+  if they contain at least
   four $b$-tagged small-$R$ jets.
@@
   %
-
-\end{itemize}
-Once a Higgs boson candidate has been identified,
+  In all categories, once a Higgs boson candidate has been identified,
 its invariant mass is required to lie within a fixed window
@@
 
-\paragraph{Results.} We now discuss the results of our analysis
-at the end of the MVA.
+\paragraph{Results.}
+As discussed in~\cite{Behr:2015oqq}, at the end of the cut-based
+analysis, events are processed with an MVA to optimise
+the separation between signal and backgrounds.
 %
-First we discuss the statistical significance of a measurements
-of the $hh\to 4b$ cross-section at 100 TeV and then provide
-a first estimate on the accuracy of the extraction of the self-coupling.
+The specific type of  MVA that we use is
+a multi-layer feed-forward artificial neural network (ANN),
+known as {\it perceptrons} or {\it deep neural networks}.
 %
-The specific type of  MVA that we use to
-disentangle signal and background events is
-a multi-layer feed-forward artificial neural network (ANN),
-known as a {\it perceptron}.
-%
-This family of ANNs are also known as {\it deep neural networks},
-due to their multi-layered architecture.
-%
-The MVA inputs are a set of kinematic variables describing the
+The MVA inputs are the set of kinematic variables describing the
 signal and background
 events which satisfy the requirements of the
-cut-based analysis.
+cut-based analysis, including the jet substructure variables.
 %
-The output of the trained ANNs also allows for the identification,
+The output of the trained ANNs allows for the identification,
 in a fully automated way,
-of the most relevant variables in the discrimination between 
+of the most relevant variables for the discrimination between 
 signal and background.
@@
 \begin{center}
-\includegraphics[width=0.48\textwidth]{plots/ssb_noPU.pdf}
-\includegraphics[width=0.48\textwidth]{plots/sb_noPU.pdf}
+\includegraphics[width=0.48\textwidth]{plots/ssb_FCC100_4b.pdf}
+\includegraphics[width=0.48\textwidth]{plots/sb_FCC100_4b.pdf}
 \caption{\small
@@
   %
+  Only the $4b$ QCD background is considered here.
+  %
   The $y_{\rm cut}=0$
   results are those at the end of the cut-based
-  analysis. {\bf Update with 100 TeV numbers}
+  analysis. 
 }
@@
 the signal over background ratio
-$S/B$ as a function of $y_{\rm cut}$
-for the three categories are given in 
+$S/B$ at a 100 TeV collider as a function of the ANN output cut $y_{\rm cut}$
+for the three categories are shown in 
 Fig.~\ref{fig:sb_mva}.
+%
+We have assumed a total integrated luminosity of $\mathcal{L}=10$ ab$^{-1}$.
 %
@@
 We also observe a substantial enhancement in $S/B$, arising
-from the background suppression achieved by the MVA, reaching
-values of 1\%, 6\% and 3.5\% in the resolved,
-intermediate and boosted categories.
+from the background suppression achieved by the MVA.
 %
@@
     \hline
-    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  &        &           &          &         \\
-    &  $y_{\rm cut}=$ &       &           &          &         \\
+    \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  &       $5\cdot 10^4$    &   $8\cdot 10^7$        &  6        &    $6\cdot 10^{-4}$         \\
+    &  $y_{\rm cut}=0.99$ &   $2\cdot 10^4$    &  $1\cdot 10^6$         &      22    &    0.02     \\
     \hline
     \hline
-    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &        &           &          &         \\
-       &  $y_{\rm cut}=$ &       &           &          &         \\
+    \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &   $3\cdot 10^4$     & $1\cdot 10^8$  & 3   &  $3\cdot 10^{-4}$ \\
+       &  $y_{\rm cut}=0.98$ &         $2\cdot 10^4$       &  $2\cdot 10^6$   &  10   & 0.007         \\
     \hline
     \hline
-      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &         &           &          &         \\
-    &  $y_{\rm cut}= $ &        &           &          &         \\
+      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  $1\cdot 10^5$      & $8\cdot 10^8$  &   4  & $1.0\cdot 10^{-4}$  \\
+    &  $y_{\rm cut}=0.95 $ &    $6\cdot 10^4$    &   $2\cdot 10^7$        &    15      &    0.004     \\
     \hline
@@
     %
+    Only the QCD $4b$ background is considered here.
+    %
     \label{table:cutflowMVA}
@@
 
-From Table~\ref{table:cutflowMVA} we see that
-following the application of the MVA, 
-the signal significance in the boosted category increases
-from 0.5 to 2.7, with $S/B$ increasing from $0.06\%$ to $3\%$.
 %
-For the intermediate and resolved categories, $S/\sqrt{B}$
-increases from 0.4 to 2.3 and 1.9 respectively, with
-the signal over background ratio raising from
-$0.05\%$ and $0.01\%$ to 4\% and 1\%.
-%
-Once the MVA training has been completed, it is possible
-to estimate, for each value of
-the cut in the ANN output $y_{\rm cut}$, how many
-signal and background events are expected at the FCC100
-assuming a total integrated luminosity of
- $\mathcal{L}=10$ ab$^{-1}$.
-%
-We also observe that
-in the boosted category, for a value $y_{\rm cut}\simeq 0.9$
-we end up with around 300 signal events and $10^4$ background
+We find that
+in the boosted category, for a value $y_{\rm cut}\simeq $
+we end up with around $bbb$ signal events and $aaa$ background
 events.
@@
 Similar results are obtained in the intermediate and resolved
-categories: in the former we find 130 ($3\cdot 10^3$) signal (background)
-events for $y_{\rm cut}\simeq 0.85$ (0.60), and in the latter
-630 ($10^5$) signal (background) events for
-$y_{\rm cut}\simeq 0.6$.
+categories: in the former we find aaa ($bbb$) signal (background)
+events for $y_{\rm cut}\simeq $ (), and in the latter
+$aaa$ ($bbb$) signal (background) events for
+$y_{\rm cut}\simeq$.
 %
@@
 $\mathcal{L}=10$ ab$^{-1}$ an overall signal
-significance of $S/\sqrt{B}\simeq 4.0$.
+significance of $S/\sqrt{B}\simeq$.
 %
 This is a substantial improvement over the corresponding
-estimator at 14 TeV.
+estimator at 14 TeV, where it was found that for an integrated
+luminosity of $\mathcal{L}=3$ ab$^{-1}$ the signal significance was ...
 
-\paragraph{Extracting the Higgs self-coupling.}  The extraction of the trilinear coupling $\lambda$ from the
+\paragraph{Extracting the Higgs self-coupling.}
+%
+The extraction of the trilinear coupling $\lambda$ from the
   corresponding cross-section is complicated by the
@@
   %
-  Therefore, a measurement of the Higgs pair production
-  cross-section does not guarantee an accurate enough determination of the trilinear
-  coupling $\lambda$.
-  %
  Here we provide a first estimate of the accuracy
   in Higgs self-coupling extraction from the $b\bar{b}b\bar{b}$ final state
-  that can be achieved 100 TeV hadron collider.
+  that can be achieved at a 100 TeV hadron collider.
   %
-  A robust estimate of the accuracy of this measurement would requires
-  a careful study of the impact 
+  A robust estimate  would require
+  a careful study of the impact of
   experimental systematic uncertainties, which is beyond the scope of this contribution.
   %
-  Therefore, we will use a number of simplifying assumptions.
+  Therefore, we will use a number of simplifying assumptions, in particular
+  a very simple estimate of the total systematic uncertainty in the cross-section
+  measurement, the limiting factor in the extraction of $\lambda$.
 
-  The sensitivity of in the Higgs self-coupling can be estimated by defining a $\chi^2$
+  The sensitivity in the Higgs self-coupling is defined by the $\chi^2$ estimator
   \be
   \label{eq:chi2profile}
-  \chi^2(\lambda) = \frac{\lc \sigma(hh,\lambda) - \sigma(hh,\lambda_{\rm SM})
+  \chi^2(\lambda) \equiv \frac{\lc \sigma(hh,\lambda) - \sigma(hh,\lambda_{\rm SM})
     \rc^2}{\lp \delta_{\rm stat}\sigma\rp^2+\lp \delta_{\rm sys}\sigma\rp^2 } \, ,
   \ee
-  where $\lambda$ is the self-coupling, $\lambda_{\rm SM}$ is the SM value, $\sigma(\lambda)$ is the
-  post-MVA signal cross-section for a given value of $\lambda$ and $\delta_{\rm stat}\sigma$ and
+  where $\lambda$ is the Higgs
+  self-coupling, $\lambda_{\rm SM}$ is the SM value, $\sigma(hh,\lambda)$ is the
+  post-MVA signal cross-section for a given value of $\lambda$, and $\delta_{\rm stat}\sigma$ and
   $\delta_{\rm sys}\sigma$ are respectively the statistical and systematic uncertainties in the cross-section
@@
   %
-  Signal samples for a range of $\lambda$ values have been generated, and have then been processed
-  by the same analysis chain, including the MVA, than the SM samples.
+  Signal samples for a range of $\lambda$ values have been  processed
+  by the same analysis chain, including the MVA (which is not
+  retrained), than the SM samples.
   %
-  To avoid introducing theoretical biases, the MVA is non-retrained for the $\lambda\ne \lambda_{\rm SM}$ values.
-  %
-  The 68\% CL range for the extraction of $\lambda$ can then be found by determining the values $\pm \delta\lambda$
+  The 68\% CL range for the extraction of $\lambda$ can then be found using
+  the usual parameter-fitting criterion by determining the values $\pm \delta\lambda$
   for which the cross-section satisfies
@@
 \ee
-The statistical error is given by $1/\sqrt{N_{\rm ev}}$ with $N_{\rm ev}$ is the post-MVA number of events in each analysis
-category.
 %
@@
 %
-The final result for the accuracy in the trilinear extraction is obtained by combining the separate results
+The final result for the accuracy in the trilinear extraction is obtained by combining
+in quadrature the separate results
 from the three exclusive categories.
 
-In Fig.~\ref{fig:chi2} we show the post-MVA cross-section in the resolved, intermediate
-  and boosted categories as a function of the Higgs self-coupling
+In Fig.~\ref{fig:chi2} we show the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
+  various steps of the cut-flow, including after $b$-tagging
+  (before MVA) and after the MVA, in the resolved (left plot)
+  and boosted (right plot) categories, as  as a function of the Higgs self-coupling
   $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
   %
-  In the same figure we also show the $\chi^2(\lambda)$ profile, Eq.~(\ref{eq:chi2profile})
-  for the three categories, assuming a total systematic uncertainty of
-  10\%.
-  %
-  Imposing the condition Eq.~(\ref{eq:condition}), we obtain that at the 68\% CL we can constrain the
+  Imposing the condition Eq.~(\ref{eq:condition}), and combining the
+  results of the three categories, we obtain
+  that at the 68\% CL we can constrain the
   Higgs trilinear to be ....
@@
 \begin{center}
-\includegraphics[width=0.48\textwidth]{plots/res.pdf}
-\includegraphics[width=0.48\textwidth]{plots/chi2.pdf}
+\includegraphics[width=0.48\textwidth]{plots/res_xSec_100TeV.pdf}
+\includegraphics[width=0.48\textwidth]{plots/bst_xSec_100TeV.pdf}
 \caption{\small
-  Left plot: the post-MVA cross-section in the resolved, intermediate
-  and boosted categories as a function of the Higgs self-coupling
-  $\lambda/lambda_{\rm SM}$ in units of the SM coupling.
-  %
-  Right plot: the $\chi^2(\lambda)$ profile, Eq.~(\ref{eq:chi2profile})
-  for the three categories, assuming a total systematic uncertainty of
-  10\%.
-  {\bf Update}
+  The $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
+  various steps of the cut-flow, including after $b$-tagging
+  (before MVA) and after the MVA, in the resolved (left plot)
+  and boosted (right plot) categories, as  as a function of the Higgs self-coupling
+  $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table}[h]
+  \centering
+  \begin{tabular}{|c|c|c|}
+    \hline
+  $\lc \lambda_{\rm min}/\lambda_{\rm SM},\lambda_{\rm max}/\lambda_{\rm SM} \rc$  &  $\delta_{\rm sys}=25\%$ & $\delta_{\rm sys}=100\%$ \\
+    \hline
+    \hline
+Boosted   & $\lc -0.1, 2.2\rc$  & $\lc -1.5, > 9\rc$  \\
+\hline
+Intermediate   & $\lc 0.7, 1.6\rc$  &  $\lc -0.4, > 9\rc$  \\
+\hline
+Resolved   & $\lc 0.9, 1.5\rc$  &  $\lc -0.1, 7\rc$  \\
+\hline
+  \end{tabular}
+  \caption{\label{tab:chi2} The 68\% confidence level intervals
+    on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ obtained from the condition
+    Eq.~(\ref{eq:condition}) in the boosted, resolved and intermediate categories.
+    %
+    We consider two different assumptions on the total systematic error in the measured
+    cross-section,  $\delta_{\rm sys}=25\%$ and $\delta_{\rm sys}=100\%$.
+  }
+  \end{table}
 

### 2016-02-23 FCCreport/HH4b.tex
work on the FCC contribution

@@
 %
-We have assumed a total integrated luminosity of $\mathcal{L}=10$ ab$^{-1}$.
+We have assumed a total integrated luminosity of $\mathcal{L}=10$ ab$^{-1}$, and only the
+irreducible QCD $4b$ background is included.
 %
@@
 We observe how in the three
- categories there is a marked  improvement in signal
-significance as compared to the pre-MVA results.
+ categories there is a marked  improvement both in signal
+ significance and in the signal over
+ background ratio as compared to the pre-MVA results.
  %
-We also observe a substantial enhancement in $S/B$, arising
-from the background suppression achieved by the MVA.
+ In Table~\ref{table:cutflowMVA} we collect
+ the post-MVA results for the optimal value of the
+    ANN discriminant $y_{\rm cut}$ in the three categories, compared with the
+    corresponding
+    pre-MVA results ($y_{\rm cut}=0$).
     %
-This improvement in $S/B$ is crucial to ensure the feasibility
-of this measurement, since it allows systematic
-uncertainties in the background determination to
-be at most of a similar size.
+    We also quote the number of signal and
+    background events expected for an integrated
+    luminosity of $\mathcal{L}=10$ ab$^{-1}$.
 
@@
 
+From Fig.~\ref{fig:sb_mva} and Table~\ref{table:cutflowMVA} we observe that the statistical
+significance of the three categories is very large, with a post-MVA value of
+$S/\sqrt{B}\simeq 20$ in the boosted
+category.
 %
-We find that
-in the boosted category, for a value $y_{\rm cut}\simeq $
-we end up with around $bbb$ signal events and $aaa$ background
-events.
+However, we also find that as compared to 14 TeV, the QCD multijet background increases
+more rapidly than the signal, and thus $S/B$ is actually smaller than at 14 TeV~\cite{Behr:2015oqq}.
 %
-Similar results are obtained in the intermediate and resolved
-categories: in the former we find aaa ($bbb$) signal (background)
-events for $y_{\rm cut}\simeq $ (), and in the latter
-$aaa$ ($bbb$) signal (background) events for
-$y_{\rm cut}\simeq$.
+Achieving  percent values in $S/B$ requires a very hard cuts on the value of the ANN output.
 %
-Combining the three categories, taking into
-account all background components, we obtain for
-$\mathcal{L}=10$ ab$^{-1}$ an overall signal
-significance of $S/\sqrt{B}\simeq$.
+We observe that at 100 TeV the boosted category is the most promising one: not only
+it benefits from the highest signal significances, it also exhibits
+the best signal over background ratio.
 %
-This is a substantial improvement over the corresponding
-estimator at 14 TeV, where it was found that for an integrated
-luminosity of $\mathcal{L}=3$ ab$^{-1}$ the signal significance was ...
+Let us recall that at 14 TeV instead~\cite{Behr:2015oqq}  the higher significance was obtained with the resolved category.
+%
+Unfortunately, as we discuss below, the boosted category is the less sensitive to the Higgs self-coupling,
+and thus a measurement of the trilinear will depend to good extent on the resolved category.
+%
+Therefore, at a 100 TeV collider, even more that at 14 TeV, the feasibility of the measurement
+of $\sigma(hh\to b\bar{b}b\bar{b})$ depends strongly on how small the systematic
+uncertainties can be, in particular for the background determination.
 
@@
   a very simple estimate of the total systematic uncertainty in the cross-section
-  measurement, the limiting factor in the extraction of $\lambda$.
+  measurement, which is the limiting factor in the extraction of $\lambda$.
 
@@
 %
-We explore different assumptions on the value of the total systematic uncertainty $\delta_{\rm sys}\sigma$.
-%
-The final result for the accuracy in the trilinear extraction is obtained by combining
+The final result for the accuracy in the trilinear extraction can be obtained by combining
 in quadrature the separate results
@@
   (before MVA) and after the MVA, in the resolved (left plot)
-  and boosted (right plot) categories, as  as a function of the Higgs self-coupling
+  and boosted (right plot) categories,  as a function of the Higgs self-coupling
   $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
   %
-  Imposing the condition Eq.~(\ref{eq:condition}), and combining the
-  results of the three categories, we obtain
-  that at the 68\% CL we can constrain the
-  Higgs trilinear to be ....
+  See~\cite{Behr:2015oqq} for the definition of the different steps
+  in the analysis chain.
+  %
+  We find that, despite that fact that the MVA is only trained on the SM sample, the signal
+  selection efficiency of the MVA is relatively flat when $\lambda$ is varied, reflecting the fact
+  that the signal kinematics do not change dramatically.
+  %
+  We also see that the resolved category (low and medium Higgs $p_T$) is more sensitive to variations of $\lambda$ than
+  the boosted one (large Higgs $p_T$), as indicated by the shallower minimum of the latter after the MVA.
+  %
+  This reflects the well-known fact that the triangle diagram (which depends on the Higgs self-coupling) is
+  dominant near the threshold region.
 
@@
 
+ %
+  Imposing the condition Eq.~(\ref{eq:condition}) we can derive the 68\% confidence level intervals
+  on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ (in units of the SM value) in the boosted, resolved and intermediate categories, for  different assumptions on the total systematic error in the measured
+  cross-section.
+  %
+  The ranges that are found are reported in Table~\ref{tab:chi2}.
+  %
+  As expected, the results depend very strongly on the assumption for the systematic uncertainty
+  on the measured cross-section.
+  %
+  In the optimistic scenario of a measurement with $\delta_{\rm sys}\sigma=25\%$,
+  the best performance comes from the resolved category, where at the 68\% CL the trilinear
+  can be determined to lie in the interval $\lambda/\lambda_{SM}\in \lc 0.9, 1.5\rc$.
+  %
+  Looser constrains are derived from the intermediate and specially from the boosted category.
+  %
+  On the other hand, for $\delta_{\rm sys}\sigma=100\%$, the constraints in all three categories
+  become very loose, specially for $\lambda/\lambda_{\rm SM}\ge 1$, due to the negative interference effects.
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{table}[h]
@@
     \hline
-  $\lc \lambda_{\rm min}/\lambda_{\rm SM},\lambda_{\rm max}/\lambda_{\rm SM} \rc$  &  $\delta_{\rm sys}=25\%$ & $\delta_{\rm sys}=100\%$ \\
+  $\lc \lambda_{\rm min}/\lambda_{\rm SM},\lambda_{\rm max}/\lambda_{\rm SM} \rc$  &  $\delta_{\rm sys}\sigma=25\%$ & $\delta_{\rm sys}\sigma=100\%$ \\
     \hline
@@
   \end{tabular}
-  \caption{\label{tab:chi2} The 68\% confidence level intervals
-    on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ obtained from the condition
+  \caption{\small \label{tab:chi2} The 68\% confidence level intervals
+    on the Higgs self-coupling $\lambda_{\rm min}/\lambda_{\rm SM}$ (in units of the SM value)
+    obtained from the condition
     Eq.~(\ref{eq:condition}) in the boosted, resolved and intermediate categories.
@@
 \end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \paragraph{Summary.} In this contribution we have performed a first exploration of the accuracy that can be expected
-for the extraction of the Higgs self-couplings at a 100 TeV hadron collider using the $b\bar{b}b\bar{b}$ final state.
+for the extraction of the Higgs self-coupling at a 100 TeV hadron collider using the $b\bar{b}b\bar{b}$ final state.
+%
+We find that while the statistical significance of the measurement of the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section
+is very large, the $S/B$ ratio is quite low (and in particular worse than at 14 TeV),
+specially in the resolved category, the one with the highest sensitivity
+to the self-coupling.
+%
+This is a consequence of the fact that from 14 TeV to 100 TeV the QCD multijet background increases more rapidly than
+the di-Higgs signal.
+%
+Our estimate of the expected precision on the Higgs trilinear depends strongly on the assumptions
+about the experimental systematics.
+%
+For a measurement with a 25\% systematic uncertainty, the self-coupling can be determined
+with accuracy $^{+50\%}_{-10\%}$ at the 68\% CL using the resolved category, but these constraints become substantially
+looser if the systematic uncertainties are increased.
 

### 2016-02-24 FCCreport/HH4b.tex
FCC report

@@
 
-J. Katharina Behr, Daniela Bortoletto, James A. Frost,\\
-  Nathan P. Hartland, Cigdem Issever and Juan Rojo
+J. Katharina Behr$^{1,2}$, Daniela Bortoletto$^1$, James A. Frost$^1$,\\[0.1cm]
+  Nathan P. Hartland$^1$, Cigdem Issever$^1$, and Juan Rojo$^1$
 
 \vspace{.3cm}
-{\it Physics Department, 1 Keble Road, University of Oxford, United Kingdom }
+       {\it ~$^1$ Physics Department, 1 Keble Road, University of Oxford, United Kingdom. \\[0.1cm]
+       ~$^2$ Deutsches Elektronen-Synchrotron (DESY),
+Notkestrasse 85, D-22607 Hamburg,
+Germany.}
 
@@
 
-In this contribution we provide an estimate of the accuracy
+In this contribution we provide a first estimate of the accuracy
 in the Higgs self-coupling extraction that can be achieved at a 100 TeV
@@
 %
-The analysis methodology is based on our feasibility
+The analysis methodology is based on our recent feasibility
 study at 14 TeV~\cite{Behr:2015oqq}, with suitable modifications for the 100 TeV
@@
  %
-  We account for  all relevant
+ In our 14 TeV study~\cite{Behr:2015oqq},  we accounted for  all relevant
   backgrounds, including the contribution from mis-identified
-  light and charm jets.
-  %
-  Our analysis strategy is found to be robust even in a high pile-up
+  light and charm jets, and showed that our
+  analysis strategy was robust even in a high pile-up (PU)
   environment.
   %
- Our results at 14 TeV~\cite{Behr:2015oqq} indicate that 
+ Our results indicate that 
   the $b\bar{b}b\bar{b}$ 
@@
 alone should allow for the observation of double Higgs production
-  at the HL-LHC, and here we study how our findings apply to the case of a 100
+at the HL-LHC.
+%
+Here we study how our findings apply to the case of a 100
 TeV collider.
+%
+For simplicity, we will consider only the irreducible
+QCD $4b$ background, and present results for the simulations without PU.
   %
@@
 {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca,Maltoni:2014eza}
-using a tailored  model
-which includes mass effects
-from the
-exact form factors.
+using the recently developed functionalities for
+loop-induced processes~\cite{Hirschi:2015iia}.
 %
@@
 %
-Parton level signal events are then showered with the {\tt Pythia8} Monte
-Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201},
+Parton level signal events are then showered with
+{\tt Pythia8}~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, version {\tt v8.201},
 using the  Monash 2013 tune~\cite{Skands:2014pea},
@@
 with {\tt SHERPA}~\cite{Gleisberg:2008ta} {\tt v2.1.1}
-and rescaled to known higher-order results.
+and rescaled to known higher-order results, using
+the same $K$-factors as in~\cite{Behr:2015oqq}. 
 %
@@
 %
-In this study we include the irreducible QCD $4b$ background
-as well as the reducible $2b2j$ component, since the $4j$ processes
-is shown to be negligible.
-%
-We also include top quark pair
-production.
+In order to provide an estimate of signal significance at 100 TeV,
+we shall consider in this
+contribution only the irreducible QCD $4b$ background.
 %
 Single Higgs production processes and electroweak backgrounds
-are much smaller and not included here.
+are much smaller and are also not included here.
 %
@@
 %
-First of all, we define {\it small-$R$ jets}, reconstructed with the
+First of all, we reconstruct {\it small-$R$ jets} with the
 anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with $R=0.4$,
-and  required
+and  require them
   to have transverse momentum $p_T \ge 40$~GeV
@@
   %
-  The we also define {\it large-$R$ jets},  reconstructed with 
-  anti-$k_T$ with $R=1.0$, and
+  We also define {\it large-$R$ jets},  reconstructed with 
+  anti-$k_T$ with $R=1.0$.
+  %
+  These
+ are
    required to have
@@
   %
-  Our cuts are deliberately loose since their optimization will be
-  performed at the MVA level.
-%
 For the   boosted and intermediate categories,
@@
 
-For each jet definition described above, a different
+For each jet definition a different
 $b$-tagging strategy is adopted.
 %
-For  {\it small-$R$ jets}, if it contains at least one $b$-quark among its constituents,
+For a {\it small-$R$ jet}, if it contains at least one $b$-quark among its constituents,
 it will be tagged as a $b$-jet with probability $f_b$, provided
@@
   constituent
-  with $p_T \ge 15$ GeV.
+  with $p_T \ge 15$ GeV, unless this constituent
+  is a charm quark, and then the mistag rate is instead $f_c$.
   %
- For {\it large-$R$ jets} instead, they are $b$-tagged by
+ {\it Large-$R$ jets} are $b$-tagged by
     ghost-associating anti-$k_T$ $R=0.3$ (AKT03)
@@
 its invariant mass is required to lie within a fixed window
-of width $80~{\rm GeV}$ around the nominal Higgs boson mass of $m_h= 125$
+of width $80~{\rm GeV}$,
+symmetric around the nominal Higgs boson mass of $m_h= 125$
 GeV.
 %
+ Our object and event selection are deliberately loose since their optimization will be
+  performed at the MVA level.
 
@@
 a multi-layer feed-forward artificial neural network (ANN),
-known as {\it perceptrons} or {\it deep neural networks}.
+known as {\it perceptron} or {\it deep neural network}.
 %
@@
     \multirow{2}{*}{Boosted} &  $y_{\rm cut}=0$  &       $5\cdot 10^4$    &   $8\cdot 10^7$        &  6        &    $6\cdot 10^{-4}$         \\
-    &  $y_{\rm cut}=0.99$ &   $2\cdot 10^4$    &  $1\cdot 10^6$         &      22    &    0.02     \\
+    &  $y_{\rm cut}=0.99$ &   $2\cdot 10^4$    &  $1\cdot 10^6$         &      22    &    $2\cdot 10^{-2}$     \\
     \hline
@@
     \multirow{2}{*}{Intermediate} &  $y_{\rm cut}=0$  &   $3\cdot 10^4$     & $1\cdot 10^8$  & 3   &  $3\cdot 10^{-4}$ \\
-       &  $y_{\rm cut}=0.98$ &         $2\cdot 10^4$       &  $2\cdot 10^6$   &  10   & 0.007         \\
+       &  $y_{\rm cut}=0.98$ &         $2\cdot 10^4$       &  $2\cdot 10^6$   &  10   & $7\cdot 10^{-3}$        \\
     \hline
     \hline
-      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  $1\cdot 10^5$      & $8\cdot 10^8$  &   4  & $1.0\cdot 10^{-4}$  \\
-    &  $y_{\rm cut}=0.95 $ &    $6\cdot 10^4$    &   $2\cdot 10^7$        &    15      &    0.004     \\
+      \multirow{2}{*}{Resolved} &  $y_{\rm cut}=0$  &  $1\cdot 10^5$      & $8\cdot 10^8$  &   4  & $1\cdot 10^{-4}$  \\
+    &  $y_{\rm cut}=0.95 $ &    $6\cdot 10^4$    &   $2\cdot 10^7$        &    15      &    $4\cdot 10^{-3}$     \\
     \hline
@@
     %
-    Only the QCD $4b$ background is considered here.
+    In this table, only the irreducible
+    QCD $4b$ background has been considered.
     %
@@
 %
-However, we also find that as compared to 14 TeV, the QCD multijet background increases
+However, we also find that as compared to 14 TeV, the QCD
+$4b$ multijet background increases
 more rapidly than the signal, and thus $S/B$ is actually smaller than at 14 TeV~\cite{Behr:2015oqq}.
 %
-Achieving  percent values in $S/B$ requires a very hard cuts on the value of the ANN output.
+Achieving  percent values in $S/B$ requires very hard cuts on the value of the ANN output $y_{\rm cut}$.
 %
@@
 %
-Let us recall that at 14 TeV instead~\cite{Behr:2015oqq}  the higher significance was obtained with the resolved category.
+Let us recall that at 14 TeV~\cite{Behr:2015oqq} the  significance
+of the three categories was quite similar, with the boosted one being the best without PU, and
+the resolved one
+exhibiting the higher significance in the simulations with PU.
 %
@@
 %
-Therefore, at a 100 TeV collider, even more that at 14 TeV, the feasibility of the measurement
-of $\sigma(hh\to b\bar{b}b\bar{b})$ depends strongly on how small the systematic
-uncertainties can be, in particular for the background determination.
+The smallness of $S/B$ indicates that
+at a 100 TeV collider, even more that at 14 TeV, the feasibility of the measurement
+of the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section
+will depend strongly on how small the systematic
+uncertainties will be, in particular those associated to the background determination.
 
@@
   by the same analysis chain, including the MVA (which is not
-  retrained), than the SM samples.
+  retrained), as the SM samples.
   %
   The 68\% CL range for the extraction of $\lambda$ can then be found using
-  the usual parameter-fitting criterion by determining the values $\pm \delta\lambda$
+  the usual parameter-fitting criterion to determine the values $\pm \delta\lambda$
   for which the cross-section satisfies
@@
 %
-The final result for the accuracy in the trilinear extraction can be obtained by combining
-in quadrature the separate results
-from the three exclusive categories.
 
-In Fig.~\ref{fig:chi2} we show the $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
-  various steps of the cut-flow, including after $b$-tagging
-  (before MVA) and after the MVA, in the resolved (left plot)
-  and boosted (right plot) categories,  as a function of the Higgs self-coupling
+In Fig.~\ref{fig:chi2} we show the
+ $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
+  various steps of the cut-flow: generator level, after
+  kinematical cuts~\cite{Behr:2015oqq}, after $b$-tagging
+  and finally after the MVA.
+  %
+  We show the results
+  in the resolved (left plot)
+  and boosted (right plot) categories,
+  as  as a function of the Higgs self-coupling
   $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
   %
-  See~\cite{Behr:2015oqq} for the definition of the different steps
-  in the analysis chain.
+  For the MVA cut,  a representative value of $y_{\rm cut}\simeq 0.7$
+  has been used.
   %
@@
   We also see that the resolved category (low and medium Higgs $p_T$) is more sensitive to variations of $\lambda$ than
-  the boosted one (large Higgs $p_T$), as indicated by the shallower minimum of the latter after the MVA.
+  the boosted one (large Higgs $p_T$), as indicated by the shallower minimum of the latter after
+  the $b$-tagging and MVA cuts.
   %
-  This reflects the well-known fact that the triangle diagram (which depends on the Higgs self-coupling) is
+  This reflects the fact that the triangle diagram (which depends on the Higgs self-coupling) is
   dominant near the threshold region.
@@
   The $\sigma(hh\to b\bar{b}b\bar{b})$ cross-section at
-  various steps of the cut-flow, including after $b$-tagging
-  (before MVA) and after the MVA, in the resolved (left plot)
-  and boosted (right plot) categories, as  as a function of the Higgs self-coupling
+  various steps of the cut-flow: generator level, after
+  kinematical cuts, after $b$-tagging
+  and finally after the MVA.
+  %
+  We show the results
+  in the resolved (left plot)
+  and boosted (right plot) categories,
+  as  as a function of the Higgs self-coupling
   $\lambda/\lambda_{\rm SM}$ in units of the SM coupling.
+  %
+  For the MVA, a representative value of the ANN output of $y_{\rm cut}\simeq 0.7$
+  has been used in this plot.
 }
@@
   %
-  As expected, the results depend very strongly on the assumption for the systematic uncertainty
+  As expected, the results depend
+  strongly on the assumption for the systematic uncertainty
   on the measured cross-section.
@@
   the best performance comes from the resolved category, where at the 68\% CL the trilinear
-  can be determined to lie in the interval $\lambda/\lambda_{SM}\in \lc 0.9, 1.5\rc$.
+  can be determined to lie in the interval $\lambda/\lambda_{\rm SM}\in \lc 0.9, 1.5\rc$.
   %
@@
   On the other hand, for $\delta_{\rm sys}\sigma=100\%$, the constraints in all three categories
-  become very loose, specially for $\lambda/\lambda_{\rm SM}\ge 1$, due to the negative interference effects.
+  degrade substantially, specially for $\lambda/\lambda_{\rm SM}\ge 1$, due to the negative interference effects.
 
@@
 %
-This is a consequence of the fact that from 14 TeV to 100 TeV the QCD multijet background increases more rapidly than
-the di-Higgs signal.
-%
-Our estimate of the expected precision on the Higgs trilinear depends strongly on the assumptions
-about the experimental systematics.
+Our estimate of the expected precision on the Higgs trilinear thus depends strongly on the assumptions
+about the experimental systematic uncertainty.
 %

### 2016-03-02 doc/kfactors/Kfactors.tex
multiplicative factors doc

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Multiplicative factors for H backgrounds}
\begin{document}
\maketitle

\begin{table}[htp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Sample & LO & NLO & K & Ref\\
\hline\hline
$ZH$ (13 TeV) & $6.468 \cdot 10^{-1}$ pb & $ 7.674 \cdot 10^{-1}$ pb & 1.186 & \cite{Alwall:2014hca}\\
$ttH$ (13 TeV) & $3.579 \cdot 10^{-1}$ pb & $4.608 \cdot 10^{-1}$ pb & 1.287 &  \cite{Alwall:2014hca}\\
$bbH$ (13 TeV) &  $4.983 \cdot 10^{-1}$ pb & $6.085 \cdot 10^{-1}$ pb & 1.221 & \cite{Alwall:2014hca}\\
\hline
\end{tabular}
\end{center}
\label{HK}
\caption{NLO K-factors for single Higgs backgrounds.}
\end{table}%

\begin{table}[htp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Sample & Decay & BF & Ref\\
\hline\hline
$ZH$ & ($Z\to b\bar{b}$)($H\to b\bar{b}$) & 0.0861 & \cite{Agashe:2014kda}\\
$ttH$ & $(W\to q\bar{q})^2$($H\to b\bar{b}$) & 0.259 & \cite{Agashe:2014kda}\\
\hline
\end{tabular}
\end{center}
\label{HBF}
\caption{Branching fractions for single Higgs backgrounds.}
\end{table}%
\begin{thebibliography}{9}

\bibitem{Alwall:2014hca}
  J.~Alwall {\it et al.},
  ``The automated computation of tree-level and next-to-leading order differential cross sections, and their matching to parton shower simulations,''
  JHEP {\bf 1407} (2014) 079
  doi:10.1007/JHEP07(2014)079
  [arXiv:1405.0301 [hep-ph]].
  %%CITATION = doi:10.1007/JHEP07(2014)079;%%
  %759 citations counted in INSPIRE as of 01 Mar 2016

\bibitem{Agashe:2014kda}
  K.~A.~Olive {\it et al.} [Particle Data Group Collaboration],
  %``Review of Particle Physics,''
  Chin.\ Phys.\ C {\bf 38} (2014) 090001.
  doi:10.1088/1674-1137/38/9/090001
  %%CITATION = doi:10.1088/1674-1137/38/9/090001;%%
  %3117 citations counted in INSPIRE as of 01 Mar 2016

\end{thebibliography}

%\subsection{}

\end{document}

### 2016-03-02 doc/singleHbkgs/singleHbkgs.tex
single H background docs

--- 2016-03-02 doc/kfactors/Kfactors.tex
@@
 
-\title{Multiplicative factors for H backgrounds}
+\title{Single Higgs backgrounds for $HH\to4b$}
 \begin{document}
@@
 $ttH$ & $(W\to q\bar{q})^2$($H\to b\bar{b}$) & 0.259 & \cite{Agashe:2014kda}\\
+$bbH$ & $H\to b\bar{b}$ & 0.57 & \cite{Agashe:2014kda} \\
 \hline
@@
 \end{table}%
+
+\begin{table}[htp]
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+Sample & Boosted (fb) & Intermediate (fb) & Resolved (fb) \\
+\hline\hline
+$ZH$ & $2.014\cdot 10^{-2}$ & $1.208\cdot 10^{-1}$ & $7.490\cdot 10^{-1}$ \\
+$ttH$ & $5.058\cdot 10^{-2}$ & $6.325\cdot 10^{-3}$ & $4.054\cdot 10^{-1}$ \\
+$bbH$ & $2.282\cdot 10^{-3}$ & $5.548\cdot 10^{-3}$ & $2.609\cdot 10^{-1}$\\
+\hline\hline
+$HH$ & $3.556\cdot 10^{-1}$  & $2.238\cdot 10^{-1}$ &  $1.237\cdot 10^{0}$ \\
+QCD &  $2.533\cdot 10^{2}$ & $1.771\cdot 10^{2}$ & $4.866\cdot 10^{3}$ \\
+\hline
+\end{tabular}
+\end{center}
+\label{HBF}
+\caption{ Results of running the OHH4b analysis code over the single Higgs background samples (noPU, pre-MVA).
+The numbers here are the cross sections remaining in the various channels and topologies after all analysis cuts.
+Also given for comparison are the post-analysis cross sections for the diHiggs signal and QCD background.}
+\end{table}%
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.45\textwidth]{plots/res.pdf}
+\includegraphics[width=0.45\textwidth]{plots/inter.pdf}
+\includegraphics[width=\textwidth]{plots/boost.pdf}
+\caption{Cutflows for the resolved (top-left), intermediate (top-right) and boosted (bottom) analyses of single Higgs backgrounds.}
+\end{center}
+\end{figure}
+
 \begin{thebibliography}{9}

### 2016-05-17 referee/Referee-Reply.tex
Start to work in the referee reply

%\special{!userdict begin /bop-hook{gsave 200 30 translate
%       65 rotate /Times-Roman findfont 216 scalefont setfont
%       0 0 moveto 0.85 setgray (DRAFT) show grestore}def end}

\documentclass[11pt,a4paper]{article}

\usepackage{graphicx}
\usepackage{float}
\usepackage{afterpage}
\usepackage{epsfig,cite}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage{multirow}
\usepackage{epstopdf}
\usepackage{url,hyperref}
\usepackage{listings}

\lstset{frame=tb,
  language=bash,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

%\textwidth=15.0cm \textheight=23.5cm
\textwidth=16.5cm \textheight=23.5cm 
\topmargin 0cm \oddsidemargin 0cm 
\setlength{\unitlength}{1mm}

\usepackage{url}
\usepackage{hyperref}

\bibliographystyle{JHEP}
%\bibliographystyle{plain}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\smallfrac#1#2{\hbox{$\frac{#1}{#2}$}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\la}{\left\langle}
\newcommand{\ra}{\right\rangle}
\newcommand{\lc}{\left[}
\newcommand{\rc}{\right]}
\newcommand{\lp}{\left(}
\newcommand{\rp}{\right)}
\newcommand{\as}{\alpha_s}
\newcommand{\aq}{\alpha_s\left( Q^2 \right)}
\newcommand{\amz}{\alpha_s\left( M_Z^2 \right)}
\newcommand{\aqq}{\alpha_s \left( Q^2_0 \right)}
\newcommand{\aqz}{\alpha_s \left( Q^2_0 \right)}
\def\toinf#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow\infty }}}}
\def\tozero#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow0 }}}}
\def\toone#1{\mathrel{\mathop{\sim}\limits_{\scriptscriptstyle
{#1\rightarrow1 }}}}
\def\frac#1#2{{{#1}\over {#2}}}
\def\gsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$>$}}}         %greater than or approx. symbol
\def\lsim{\mathrel{\rlap{\lower4pt\hbox{\hskip1pt$\sim$}}
    \raise1pt\hbox{$<$}}}         %less than or approx. symbol
\newcommand{\mrexp}{\mathrm{exp}}
\newcommand{\dat}{\mathrm{dat}}
\newcommand{\one}{\mathrm{(1)}}
\newcommand{\two}{\mathrm{(2)}}
\newcommand{\art}{\mathrm{art}} 
\newcommand{\rep}{\mathrm{rep}}
\newcommand{\net}{\mathrm{net}}
\newcommand{\stopp}{\mathrm{stop}}
\newcommand{\sys}{\mathrm{sys}}
\newcommand{\stat}{\mathrm{stat}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\pdf}{\mathrm{pdf}}
\newcommand{\tot}{\mathrm{tot}}
\newcommand{\minn}{\mathrm{min}}
\newcommand{\mut}{\mathrm{mut}}
\newcommand{\partt}{\mathrm{part}}
\newcommand{\dof}{\mathrm{dof}}
\newcommand{\NS}{\mathrm{NS}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\gen}{\mathrm{gen}}
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\parr}{\mathrm{par}}
\newcommand{\val}{\mathrm{val}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\checkk}{\mathrm{check}}
\newcommand{\reff}{\mathrm{ref}}
\newcommand{\extra}{\mathrm{extra}}
\newcommand{\draft}[1]{}
\newcommand{\comment}[1]{{\bf \it  #1}}
\def\beq{\begin{equation}}  
\def\eeq{\end{equation}}

% Added by MU for the fast evolution section
\def\bgamma{\boldsymbol{\gamma}}
\def\nn{\nonumber}
\def \so{\sigma_I^{DIS}(x_I,Q^2_I)}
\def \sh{\frac{d\sigma^{hh}}{dX}}
\def\sdy{\frac{d\sigma^{\mathrm{DY}}}{dQ_I^2dY_I}}
\def \npdf{N_{\mathrm{pdf}}}
\def \gtilda{\tilde\Gamma_J^{\mathrm{OBS}}}
\def \n0{N_j^{(0)}}
\def \a{\alpha}
\def \b{\beta}
\def \g{\gamma}
\def \c{\xi}
\def \z{\zeta}
% Added by JR
\def\lapprox{\lower .7ex\hbox{$\;\stackrel{\textstyle <}{\sim}\;$}}
\def\gapprox{\lower .7ex\hbox{$\;\stackrel{\textstyle >}{\sim}\;$}}
\def\half{\smallfrac{1}{2}}
\def\GeV{{\rm GeV}}
\def\TeV{{\rm TeV}}
\def\ap{{a'}}
\def\vp{{v'}}
\def\e{\epsilon}
\def\d{{\rm d}}
\def\calN{{\cal N}}
\def\shat{\hat{s}}
\def\barq{\bar{q}}
\def\qq{q \bar q}
\def\uu{u \bar u}
\def\dd{d \bar d}
\def\pp{p \bar p}
\def\xa{x_{1}}
\def\xb{x_{2}}
\def\xaa{x_{1}^{0}}
\def\xbb{x_{2}^{0}}
\def\smx{\stackrel{x\to 0}{\longrightarrow}}
\def\Li{{\rm Li}}

\newcommand{\tmop}[1]{\ensuremath{\operatorname{#1}}}
\newcommand{\tmtextit}[1]{{\itshape{#1}}}
\newcommand{\tmtextrm}[1]{{\rmfamily{#1}}}
\newcommand{\tmtexttt}[1]{{\ttfamily{#1}}}
\begin{document}

We thank the referee for the careful reading of our manuscript
and her/his insightful comments, which have prompted us to study
in some detail some of the aspects of our analysis.
%
In the following we reply to each of the points raised by the
referee in turn, and indicate the modifications
that have been performed in the revised version of the paper.

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-05-19 referee/Referee-Reply.tex
Updated referee reply

@@
 \usepackage{afterpage}
-\usepackage{epsfig,cite}
+\usepackage{epsfig,cite,multirow}
 \usepackage{amssymb}
@@
 
-We thank the referee for the careful reading of our manuscript
-and her/his insightful comments, which have prompted us to study
-in some detail some of the aspects of our analysis.
+We thank the referee for the careful reading of our manuscript,
+her/his positive appreciation of our work as well as for
+her/his insightful comments, which have prompted us to study
+in some detail some important aspects of our analysis.
 %
-In the following we reply to each of the points raised by the
-referee in turn, and indicate the modifications
-that have been performed in the revised version of the paper.
+In the following, we reply to each of the points raised by the
+referee in turn.
+
+\begin{itemize}
+
+\item In the first comment, the referee states that:
+
+  \begin{quote}
+    \it
+``It is certainly true that electroweak backgrounds such as $b\bar{b}Z(\to b\bar{b})$, $tth$ or $HZ$ are smaller than the QCD backgrounds, but they are also much bigger than the signal.
+A priori it is not clear to me that they can be neglected.
+Previous analyses, with which the authors compare their study, have included such backgrounds and found them relevant.
+I would ask the authors to show that after their reconstruction these backgrounds are significantly smaller than their signal process to be irrelevant for their significance.
+If the authors do not want to do a full study including those backgrounds it should suffice to use their final cuts and run over a set of events for each of these processes to show that they are well under control.''
+    \end{quote}
+
+  To address this point, we have generated additional background samples for
+  the following single-Higgs
+  processes:
+  \begin{enumerate}
+  \item $Z(\to b\bar{b})h(\to b\bar{b})$ (electroweak)
+  \item $t\bar{t}h(\to b\bar{b})$
+    \item $b\bar{b}h(\to b\bar{b})$ (QCD)
+  \end{enumerate}
+  For each of these additional background processes, we have generated 1M events using
+  {\tt MadGraph5\_aMC@NLO} at leading order.
+  %
+  In Table~\ref{HK} of this note we list the
+  LO and NLO cross-sections at the generation level for the single-Higgs background
+  processes listed above.
+  %
+  The subsequent decays and the corresponding branching fractions are not included here, since
+  these are taken care by the {\tt Pythia8} parton shower.
+  %
+  The values of these branching fractions applied to the single-Higgs
+  background processes from Table~\ref{HK} of this note
+  are listed in Table~\ref{HBF} below.
+  %
+  The values that we used are the most recent averages from the PDG.
+  %
+  In the case of the $t\bar{t}h$ process, we consider only the fully hadronic decays
+  of the top quark, since leptonic and semi-leptonic decays can be discriminated
+  by means of a lepton veto.
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+Sample & LO & NLO & K-factor\\
+\hline\hline
+$Zh$ (13 TeV) & $6.5 \cdot 10^{-1}$ pb & $ 7.7 \cdot 10^{-1}$ pb & 1.19 \\
+$t\bar{t}h$ (13 TeV) & $3.8 \cdot 10^{-1}$ pb & $4.6 \cdot 10^{-1}$ pb & 1.29 \\
+$b\bar{b}h$ (13 TeV) &  $4.9 \cdot 10^{-1}$ pb & $6.1 \cdot 10^{-1}$ pb & 1.22 \\
+\hline
+\end{tabular}
+\caption{\small LO and NLO cross-sections at the generation level for the single-Higgs background
+  processes listed above, computed using {\tt MadGraph5\_aMC@NLO}.
+  %
+  The subsequent decays and the corresponding branching fractions are not included in these generation-level cross-sections. \label{HK}
+}
+\end{center}
+  \end{table}%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+Sample & Decay & Branching Fraction\\
+\hline\hline
+$Zh$ & ($Z\to b\bar{b}$)($h\to b\bar{b}$) & 0.086 \\
+$t\bar{t}h$ & $(W\to q\bar{q})^2$($h\to b\bar{b}$) & 0.26 \\
+$b\bar{h}h$ & $h\to b\bar{b}$ & 0.57 \\
+\hline
+\end{tabular}
+\caption{\small The values of the branching fractions applied to the single-Higgs
+background processes from Table~\ref{HK}, taken from the most updated PDG values. \label{HBF}}
+\end{center}
+  \end{table}%
+   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+  In order to compare the relevance of the single-Higgs production processes of Table~\ref{HK} above
+  with the signal and background processes of the original manuscript, in
+  Table~\ref{HBxsec} below we show the signal and background cross-sections at the end of the cut-based analysis
+  (before the MVA is applied), in the case without PU.
+  %
+  We separate the results into the three exclusive categories used in our analysis.
+  %
+  From this comparison, we see that as expected, at the end of the cut-based analysis, the single-Higgs
+  backgrounds are smaller than the QCD multijet background by several orders of magnitude.
+  %
+  Perhaps more interestingly, we find that already at the end of the cut-based analysis the di-Higgs
+  signal is also larger than all the single-Higgs backgrounds in all the selection categories.
+  %
+  Since this discrimination can only be improved by the MVA, we find justified our original
+  assumption of neglecting single-Higgs backgrounds in the original analysis.
+%
+  From Table~\ref{HBxsec} we also observe that, for all categories, $Zh\to b\bar{b}b\bar{b}$ is
+  the dominant single-Higgs background.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{table}[h]
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+& Sample &  \multicolumn{3}{c|}{Pre-MVA cross-section (fb)}\\
+ & &  Boosted  & Intermediate & Resolved \\
+\hline\hline
+Signal & $hh\to b\bar{b}b\bar{b}$ & $3.5\cdot 10^{-1}$  & $2.2\cdot 10^{-1}$ &  $1.2\cdot 10^{0}$ \\
+\hline
+\multirow{4}{*}{Backgrounds} & QCD multijet &  $2.5\cdot 10^{+2}$ & $1.8\cdot 10^{+2}$ & $4.9\cdot 10^{+3}$ \\
+&$Z(\to b\bar{b})h(\to b\bar{b})$ & $2.0\cdot 10^{-2}$ & $1.2\cdot 10^{-1}$ & $7.5\cdot 10^{-1}$ \\
+&$t\bar{t}h(\to b\bar{b})$ & $5.1\cdot 10^{-2}$ & $6.3\cdot 10^{-3}$ & $4.0\cdot 10^{-1}$ \\
+&$b\bar{b}h(\to b\bar{b})$ & $2.3\cdot 10^{-3}$ & $5.5\cdot 10^{-3}$ & $2.6\cdot 10^{-1}$\\
+\hline
+\end{tabular}
+\end{center}
+\caption{\small \label{HBxsec} The signal and background cross-sections at the end of the cut-based analysis
+  (level C2, before the MVA is applied), in the case without PU.
+  %
+  We separate the results into the three exclusive categories used in our analysis.
+  %
+  The QCD multijet background was already included in the original analysis,
+  while the single-Higgs backgrounds are new.
+}
+  \end{table}%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+  In any case, as we report below, for completeness we have redone the entire analysis
+  including also the single-Higgs background processes, and verify that
+  the overall signal significance is not modified in any sizable way, thus our original
+  conclusions are robust upon the addition of the new single-Higgs background processes.
+
+\item The second point raised by the referee is the following:
+
+  \begin{quote}
+    \it ``Depending on how $b$-tagging has been performed and event weights have been calculated, I suspect that the number of generated background events is not sufficient in the analysis.
+If I am reading Table 1 correctly, the authors generated for each of the backgrounds 3 million unweighted events.
+However, these backgrounds have very different total cross sections.
+For example, the $4$j background has a total cross section of $10^6$ pb, which means that an individual event that passes all reconstruction cuts carries a weight of $O(0.1)$ pb.
+However, the total signal cross section is only $10^-3$ pb.
+I do not see how so few events for $4j$ can give a reliable estimate of the signal to background ratio.
+....
+Hence, it would be good if the authors could show the number of events after their cuts C1a-C2 and after their neural-net cuts ''.
+  \end{quote}
+
+  Following these remarks from the referee, we investigated in more detail the statistics of our
+  background samples and found that while for the $2b2j$ sample the statistics were probably
+  enough to provide a sensible estimate of the cross-section, for the $4j$ sample this was not quite
+  the case.
+
+  To illustrate this problem, in Fig.~\ref{fig:evgen} we show
+  the number of MC events from the $4j$ background sample at the end of
+   the cut-based analysis, in the resolved (upper plot) and boosted (category), distributed
+   according to their associated MVA output value.
+   %
+   We see that in the resolved category we have 79 events after cuts, and only 4 in the boosted.
+   %
+   In the latter case, these events are localized at very small values of the MVA discriminant,
+   so they are safely removed by the MVA cut.
+
+   So while this situation
+   is not ideal, the fact that the $4j$ cross-sections at the end of the cut-based
+   analysis (Table 4 of the paper) are always quite smaller than the $4b$+$2b2j$ sum, suggest that
+   our limited statistics do not affect significantly the results of the analysis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+\begin{center}
+ \includegraphics[width=0.90\textwidth]{evgen1.pdf}
+ \includegraphics[width=0.60\textwidth]{evgen2.pdf}
+ \caption{\small The number of MC events from the $4j$ background sample at the end of
+   the cut-based analysis, in the resolved (upper plot) and boosted (category), distributed
+   according to their associated MVA output.
+}
+\label{fig:evgen}
+\end{center}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+   However, it is always important to validate expectations in a explicit way, so we have increased
+   by a factor 10 the size of our $2b2j$ and $4j$ Monte Carlo background samples, up to a total
+   of 30M each.
+   %
+   These have been used to repeat the analysis with a more reliable estimate of the $2b2j$ and $4j$
+   background cross-sections, specially  relevant for the later.
+   %
+   In this case, the number of $4j$ signal events
+   that pass the cuts (level C2, before MVA) is around 1000 in the resolved category
+   and around 100 in the boosted,
+   which provides a  more robust estimate of the multijet background cross-section.
+
+   We would like to emphasize here that repeating the full analysis with the high-statistics background samples would be already very
+   CPU-time intensive, and a further increase of the background stats is beyond our
+   computing power.
+For instance, generating  300M events of the $2b2j$ and $4j$ samples would take around a couple months running on 50 cores.
+And for at analysis level, already with O(100M) background events the analysis
+   time with PU included
+   would take around one month running on 25 cores full time, becoming clearly unfeasibly
+   if the number of background events is further increased to  O(1000M).
+
+ \item The final remark from the referee is the following:
+
+   \begin{quote}
+     \it ``Along the same line, the authors give fake-rates for the different backgrounds in Table 5 and conclude at the end of section 4.2 that the multi-jet backgrounds can be neglected.
+However, with a fake rate of
+     $10^{-4}$ \%, the $4j$ background would still correspond to 1 pb I do not see how this can be neglected when studying a signal of few fb.''
+   \end{quote}
+
+   We agree that this statement is not as precise as it could be.
+   %
+   What we meant here was the following: consider for instance Table 4, in the resolved category,
+   before the application of $b$-tagging.
+   %
+   At this level of the cut flow,
+   the cross-sections in fb for the QCD multijet background are
+   $1.6\cdot 10^4$, $3.2\cdot 10^6$ and $2.1\cdot 10^7$ fb for $4b$, $2b2j$ and $4j$
+   respectively.
+   %
+   Now, after the application of naive fake $b$-tagging probabilities, these numbers
+   should be multiplied by $1,10^{-4},10^{-8}$ respectively, which would make
+   the $2b2j$ and $4j$ cross-sections
+   much smaller than $4b$.
+
+   However the actual probabilities are those of Table 5 of the
+   original manuscript: applying these
+   we find cross-sections after $b$-tagging of around 1.2 pb, 1.3 pb and 50 fb respectively.
+   %
+   This means that in the resolved category, chosen here for illustration, the $4j$ background
+   is smaller than the $2b2j$ and $4b$ backgrounds by at least an order of magnitude (consistent
+   with the row C2 of the resolved category of C2) and thus is unlikely to play a major
+   role in the estimation of the overall signal significance.
+
+\end{itemize}
+
+To validate the robustness of our original results, 
+we have redone the complete analysis with the updated background samples
+in the case without PU, including
+the MVA (re-)training.
+%
+This way, it is possible to compare the signal significances found
+in this updated analysis with those that are reported in the original manuscript.
+
+  First of all, in Table~\ref{tab:cutflow_noPU_1} of this reply
+  we show the comparison of the signal and total background
+      cross-sections at the end of the cut-based analysis (level C2),
+      between the original and the updated analysis,  for the resolved (upper),
+      intermediate (middle) and boosted
+      (lower table) categories, in the case of the analysis
+      without PU.
+      %
+      As can be seen, there is good agreement between the original and the updated
+      estimates of the background cross-sections at the end of the cut-based analysis,
+      with the updated values being somewhat larger due to both the additional single-Higgs
+      backgrounds included and the improved modelling of the QCD multijet component.
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h!]
+  \centering \small
+   \begin{tabular}{|l|cc|}
+  \hline
+\multicolumn{3}{|c|}{HL-LHC, Resolved category, no PU}\\
+\hline
+&  \multicolumn{2}{c|}{Cross-section [fb]}  \\
+   &  $hh4b$ &  total bkg \\
+  \hline
+  C2, original analysis    & 0.5  &   $4.9\cdot 10^3$        \\
+  C2, updated analysis    & 0.5  &   $7.0\cdot 10^3$        \\
+\hline
+   \end{tabular}\\
+   \vspace{0.5cm}
+    \begin{tabular}{|l|cc|}
+  \hline
+\multicolumn{3}{|c|}{HL-LHC, Intermediate category, no PU}\\
+\hline
+&  \multicolumn{2}{c|}{Cross-section [fb]}  \\
+   &  $hh4b$ &  total bkg \\
+  \hline
+  C2, original analysis    &  0.09  &  $1.8\cdot 10^2$        \\
+  C2, updated analysis    &  0.09  &  $2.8\cdot 10^2$      \\
+\hline
+    \end{tabular}\\
+     \vspace{0.5cm}
+    \begin{tabular}{|l|cc|}
+  \hline
+\multicolumn{3}{|c|}{HL-LHC, Boosted category, no PU}\\
+\hline
+&  \multicolumn{2}{c|}{Cross-section [fb]}  \\
+   &  $hh4b$ &  total bkg \\
+  \hline
+  C2, original analysis    &   0.16  &   $2.5\cdot 10^2$       \\
+  C2, updated analysis    &    0.16  &   $3.1\cdot 10^2$       \\
+\hline
+   \end{tabular}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    \caption{\small Comparison of the signal and total background
+      cross-sections at the end of the cut-based analysis (level C2),
+      between the original and the updated analysis,  for the resolved (upper),
+      intermediate (middle) and boosted
+      (lower table) categories, in the case of the analysis
+      without PU.
+      %
+ \label{tab:cutflow_noPU_1}}
+\end{table}
+
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h]
+  \centering
+  \begin{tabular}{|c|l|c|c|c|c|c|}
+    \hline
+    \multicolumn{7}{|c|}{HL-LHC, no PU} \\
+    \hline
+    \hline
+    Category  &  Analysis & ANN cut & $N_{\rm ev}$ signal &  $N_{\rm ev}$ back  &  $S/\sqrt{B}$ & $S/B$ \\ 
+    \hline
+    \hline
+    \multirow{2}{*}{Boosted} & Original & $y_{\rm cut}=0.90$ &  290  & $1.2\cdot 10^4$   & 2.7  & 0.03 \\
+    & Updated & $y_{\rm cut}=0.80$ & 140    &   $1.9\cdot 10^3$   &  3.2   &  0.07  \\
+    \hline
+    \hline
+    \multirow{2}{*}{Intermediate} &   Original & $y_{\rm cut}=0.85$ & 130  & 3100  & 2.3 & 0.04\\
+     &   Updated & $y_{\rm cut}=0.75$ & 30  &  260  & 1.7   & 0.11 \\
+    \hline
+    \hline
+    \multirow{2}{*}{Resolved} & Original  & $y_{\rm cut}=0.60$ & 630 & $1.1\cdot 10^{5}$  & 1.9 & 0.01 \\
+        & Updated & $y_{\rm cut}=0.50$ & 230  & $2.7\cdot 10^{5}$   & 1.4  & 0.01  \\
+    \hline
+      \end{tabular}
+  \caption{\small
+Same as Table 6 of the original paper, containing the post-MVA
+results for the optimal value of the
+ANN discriminant, where we now compare the numbers from the original
+analysis with those of the updated analysis described in this reply.
+    %
+    We quote the number of signal and
+    background events expected for $\mathcal{L}=3$ ab$^{-1}$,
+    the signal significance $S/\sqrt{B}$ and
+    the signal over background ratio $S/B$.
+    %
+    We also quote the value of the ANN cut $y_{\rm cut}$ used in this case, though their
+    values are not quite comparable since the distribution of the events in the ANN output
+    is different in the updated analysis as compared to the original analysis (different MVA training).
+    %
+    \label{tab:mva}
+  }
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%
+Next, in Table~\ref{tab:mva} we provide the same
+information as Table 6 of the original paper, containing the post-MVA
+results for the optimal value of the
+ANN discriminant, where we now compare the numbers from the original
+analysis with those of the updated analysis described in this note.
+    %
+    We quote the number of signal and
+    background events expected for $\mathcal{L}=3$ ab$^{-1}$,
+    the signal significance $S/\sqrt{B}$ and
+    the signal over background ratio $S/B$.
+    %
+    Note that due to the MVA re-training on the updated background samples
+    (both the high-stats QCD multijets and the single-higgs background) the determination
+    of the optimal value of the cut on the ANN discriminant on each category needs
+    to be performed again independently.
+    %
+    In particular, we find that now tighter cuts (leading to a reduced number
+    of signal events passing the MVA cut) are
+    required to achieve similar signal significance, most likely
+    due to the more robust population of the phase space from the
+    QCD multijet backgrounds.
+    %
+    This reduces the overall number of signal events to be observed
+    at the HL-LHC down to around 400, though we also now find larger values
+    of $S/B$ in the boosted and resolved categories,
+    which is also an important requirement.
+
+    As we can read from Table~\ref{tab:mva}, we achieve a similar signal significance combining the three
+    categories:
+    \be
+   \lp \frac{S}{\sqrt{B}}\rp_{\rm tot} = 4.0 \quad {\rm original~analysis}
+   \ee
+    \be
+   \lp \frac{S}{\sqrt{B}}\rp_{\rm tot} = 3.9 \quad {\rm updated~analysis}
+   \ee
+   implying that the conclusions derived
+   in the original analysis are essentially unchanged following the improved treatment
+   of the background processes.
+
+   All the cross-checks listed in this note
+   make us confident that the signal significances claimed in our
+   manuscript are robust enough, and therefore there is no need to update all the tables
+   and plots in our analysis (which in the case of PU is beyond our computing resources),
+   due to the fact that the overall physics message would be unchanged.
+%
+  In any case, we are already working on a follow-up paper about the determination of the Higgs trilinear coupling, and there all the modifications that are reported here will be documented in detail.
 

### 2016-05-19 referee/scripts/plotMVAdat_highstat.py

@@ -1,0 +1,241 @@
+#! /usr/local/Cellar/python/2.7.10/bin/python
+from matplotlib import pyplot as plt
+from operator import add, sub
+from math import sqrt
+import sys, os, math
+import numpy
+
+print "Warning: This script might take a minute or two depending on the density of thresholds"
+
+################################ Settings ###################################
+
+# Source files
+datafiles=[ "../../paper-arxiv-v2/plotdata/baseline_noPU_oxford_hiStats/MVA/nn_14X5X3X1_50000-Gen_resNTuple_wSH.dat",
+			"../../paper-arxiv-v2/plotdata/baseline_noPU_oxford_hiStats/MVA/nn_18X5X3X1_50000-Gen_intNTuple_wSH.dat",
+			"../../paper-arxiv-v2/plotdata/baseline_noPU_oxford_hiStats/MVA/nn_22X5X3X1_50000-Gen_bstNTuple_wSH.dat"]
+
+datanames=[ "Resolved","Intermediate","Boosted"]
+titlenames=[ "Resolved Category, no PU","Intermediate Category, no PU",\
+             "Boosted Category, no PU"]
+
+datanamessignal=[ "Signal Res","Signal Int","Signal Boost"]
+datanamesback=[ "Background Res","Background Int","Background Boost"]
+
+
+# HL-LHC luminosity
+hl_lhc_lumi=3000
+
+colours = ['r', 'b', 'g', 'm', 'c', 'y', 'k']
+
+linestyles = ['dashed','dotted','solid']
+
+# Histogram names
+Histout = "disc_noPU_hiStat"  # Histograms for discriminant
+ROCout = "roc_noPU_hiStat"	  # ROC curve
+SBout = "sb_noPU_hiStat"	  # S/B curve
+SSBout = "ssb_noPU_hiStat"	  # S/Sqrt(B) curve
+NeVout = "nev_noPU_hiStat"	  # Number of events (twin axes)
+NeV2out = "nev2_noPU_hiStat"  # Number of events (single axis)
+
+resc=1.1  #  to account for different total cross-section of QCD background samples
+ 
+#############################################################################
+
+# Plot the individual discriminant histograms
+def plotDiscriminantHisto(name, signal, background,title):
+        plt.rcParams.update({'font.size': 16})
+	bins = numpy.linspace(0, 1, 20) # Binning density
+	fig, ax = plt.subplots()
+
[…]

### 2016-06-13 paper-arxiv-v3/sec-intro.tex
added v3 of the paper

--- 2015-12-31 paper-arxiv-v1/sec-intro.tex
@@
 at the LHC have been performed for different final states, including
-$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
+$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa,Lu:2015jza},
 $b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
@@
 operators and anomalous 
-Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
+Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa,Cao:2015oaa}, resonant production
 in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa,Wen-Juan:2015gqg}, and Supersymmetry and
-Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
+Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova,Cao:2013si}.
 %

### 2016-06-13 paper-arxiv-v3/sec-results.tex
added v3 of the paper

--- 2015-12-21 paper/sec-results.tex
@@
-\section{Results of the cut-based analysis}
+\section{Pre-MVA loose cut-based analysis}
 
@@
 
-In this section we present the results of the 
-cut-based analysis described in the previous section, and provide 
+In this section we present the results of the pre-MVA
+loose cut-based analysis described in the previous section, and provide 
 cut-flows for the different analysis steps.
 %
-We
-compare our results with other recent studies,
-and assess how the signal significance
+We study how the signal significance
 is affected if only the $4b$ component of the
@@
 %
-%Here we present the results in an environment without pile-up,
-%followed in the next section by the corresponding analysis including PU.
-This section presents the results in an environment without significant pile-up; the following one details those obtained includin PU.
+This section presents the results in an environment
+without pileup; the following one contains those
+obtained including significant PU.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
 \begin{table}[t]
@@
 \hline
-{\bf C0} &  \multicolumn{3}{c|}{Generator level} \\
+\multirow{2}{*}{{\bf C1a}} & $N_{\rm jets}^{R10}\ge 2$ & $N_{\rm jets}^{R04}\ge 2$, $N_{\rm jets}^{R10}=1$  &
+$N_{\rm jets}^{R04}\ge 4$ \\
+ & \multicolumn{3}{c|}{+$p_T$ cuts and rapidity cuts} \\
 \hline
-{\bf C1a} & $N_{\rm jets}^{R10}\ge 2$ & $N_{\rm jets}^{R04}\ge 2$, $N_{\rm jets}^{R10}=1$  &
-$N_{\rm jets}^{R04}\ge 4$ \\
+\multirow{2}{*}{{\bf C1b}} & +$N_{\rm MDT}\ge 2$ & +$N_{\rm jets}^{R10}=1$ with MDT  &
+ +Higgs reconstruction \\
+  &  &
+ +Higgs reconstruction  & \\
  \hline
-{\bf  C1b} & \multicolumn{3}{c|}{+$p_T$ cuts and rapidity cuts} \\
-\hline
- {\bf C1c} & +$N_{\rm MDT}\ge 2$ & +$N_{\rm jets}^{R10}=1$ with MDT  &
- +Higgs reconstruction \\
- \hline
-{\bf C1d} & \multicolumn{3}{c|}{ +$m_H$ window cut} \\
+{\bf C1c} & \multicolumn{3}{c|}{ +$m_h$ window cut} \\
 \hline
@@
   \end{tabular}
-  \caption{\small Definition of the cuts imposed successively for the boosted, intermediate
-    and resolved selections.
+  \caption{\small Definition of the cuts imposed successively for the three selections.
     %
@@
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%
 
 \begin{itemize}
-    \item {\bf C0}:  generator level cross-sections, with
-      mild generation cuts in the case of the background processes, and no
-      generation cuts
-      for the signal events.
      %
@@
       case) and at least four small-$R$ jets (in the resolved case).
-      %
-      No acceptance requirements are imposed.
-    \item {\bf C1b}: require that the above jets should
+
+      In addition,
+  require that these jets 
       satisfy the corresponding $p_T$ thresholds;
       $p_T \ge 200$ GeV for large-$R$ jets and
-      $p_T \ge 50$ GeV for small-$R$ jets, and well as
-      satisfy the associated
+      $p_T \ge 40$ GeV for small-$R$ jets, as well as
+      the associated
       rapidity acceptance constraints.
-    \item {\bf C1c}: the two leading large-$R$ jets must
+    \item {\bf C1b}: the two leading large-$R$ jets must
       be mass-drop tagged in the boosted category.
       %
-      In the intermediate category, the large-$R$ jet must also be mass-drop tagged.
+      In the intermediate category, the large-$R$ jet
+      must also be mass-drop tagged.
       %
-    \item {\bf C1d}: after the two Higgs candidates  have been reconstructed,
+    \item {\bf C1c}: after the two Higgs candidates  have been reconstructed,
       their invariant masses are required to lie within a window around $m_H$,
-      in particular between 85 and 165 GeV.
+      in particular between 85 and 165 GeV, Eq.~(\ref{higgsmasswindow}).
           \item {\bf C2}: the
@@
             Sect.~\ref{sec:btagging}), and the event is categorised exclusively
-            into one of the three topologies.
+            into one of the three topologies, according
+            to the hierarchy determined in Sect.~\ref{sec:categorisation}.
       \end{itemize}
@@
     In Table~\ref{tab:cutflow_noPU_1} we collect
-    the values for signal and background cross-sections
-    at different steps of the cut-flow.
+    the values for the signal and background cross-sections
+    at the different analysis steps.
     %
@@
       %
-      These are provided both taking into account all the background components and only
-      the $4b$ QCD background.
+      These are computed either
+      taking into account all the background components or
+      the $4b$ QCD background only.
         %
@@
     \input{table_noPU_3.tex}
-    \caption{\small The cross-sections (fb)
+    \caption{\small The cross-sections
       for the signal and the background
       processes at different steps of the
-      cut-flow, for the resolved (upper table),
-      intermediate (middle table) and boosted
+      analysis (see Table~\ref{tab:cutflowdetails}), for the resolved (upper),
+      intermediate (middle) and boosted
       (lower table) categories, for the analysis
@@
       background ratio $S/B$, and the signal
-      significance $S/\sqrt{B}$ are also provided, considering either
-      the total background or just the $4b$ component. Signal
-      significances are calculated for an
-      integrated luminosity of $\mathcal{L}=3$ ab$^{-1}$.
+      significance $S/\sqrt{B}$ for
+       $\mathcal{L}=3$ ab$^{-1}$ are also provided, considering either
+      the total background or only the $4b$ component.
       %
-      The different steps of the cut-flow are described
-      in Table~\ref{tab:cutflowdetails}.
  \label{tab:cutflow_noPU_1}}
@@
 %
-In the boosted category, at the end of the cut-based
-analysis, we find that around $10^3$ events
+In the boosted category, at the end of the loose cut-based
+analysis, we find that around 500 events
 are expected
-at the HL-LHC, with however a very large number,
-$\simeq 10^6$, of QCD background events.
+at the HL-LHC, with a large number,
+$\simeq 10^6$, of background events.
 %
 This leads to a pre-MVA signal significance of
-$S/\sqrt{B}=1.2$ and a signal over background
-ratio of $S/B=0.14\%$.
+$S/\sqrt{B}=0.5$ and a signal over background
+ratio of $S/B=0.06\%$.
 %
@@
 expectations for the LHC Run II with
-$\mathcal{L}=300$ fb$^{-1}$: one expects around
-120 signal events, with signal significance dropping down to
-$S/\sqrt{B}\sim 0.3$.
+$\mathcal{L}=300$ fb$^{-1}$: one expects in the boosted
+category around
+50 signal events, with signal significance dropping down to
+$S/\sqrt{B}\simeq 0.16$.
 %
@@
 but our analysis cuts have been left deliberately loose
-in order that such optimsation may be performed by the MVA.
+so that such optimisation may be performed by the MVA.
 
@@
 In both resolved and intermediate categories
-the signal significance is similar to that of the boosted category,
-$S\sqrt{B}\simeq 0.9$.
+the signal significance is
+$S/\sqrt{B}\simeq 0.4$,
+similar to that of the boosted category.
 %
-An further
+A further
 drawback of the resolved case is
 that $S/B$
-is one order to magnitude smaller than in the boosted case.
-%
-Combining the pre-MVA results
+is substantially reduced as compared to the boosted and
+intermediate cases.
+
+Combining the results
 from the boosted, intermediate and resolved categories,
-we obtain an overall
+we obtain an overall pre-MVA 
 significance for the observation of the Higgs pair production
 in the $b\bar{b}b\bar{b}$ final
-state at the HL-LHC with $\mathcal{L}=3$ ab$^{-1}$
-of  $S/\sqrt{B} \simeq 1.8$.
+state at the HL-LHC 
+of  $(S/\sqrt{B})_{\rm tot} \simeq 0.8$.
 
@@
 
-One of the main differences of the present study as compared
-to previous works is in the inclusion of both irreducible
+One of the main differences in the present study as compared
+to previous works is the inclusion of both irreducible
 and reducible background components, which allows us to
@@
 $2b2c$ QCD multijets, as well as
-$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$,
-and a signal significance of $S/\sqrt{B}\simeq 2.1$ for the HL-LHC
+$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$.
+%
+For the HL-LHC, a signal significance of $S/\sqrt{B}\simeq 2.1$ 
 is obtained.
@@
 The Durham group study~\cite{deLima:2014dta} requires events
-to have two $R=1.2$ C/A jets with $p_T\ge 200$ GeV, with
+to have two $R=1.2$ C/A jets with $p_T\ge 200$ GeV, and in
+addition
 two $b$-tagged subjets inside each large-$R$ jet with
@@
 At the HL-LHC, their best result is obtained by requiring two
-SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\simeq 2.1$. Using the BDRS tagger
+SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\simeq 2.1$.
+%
+Using the BDRS tagger
 results in slightly poorer performance.
@@
  that the signal significance for the boosted, intermediate,
- and resolved categories is increased to 2.7, 1.6 and 1.6, respectively,
+ and resolved categories is increased to 1.1, 0.6 and 0.6, respectively,
  when only the QCD $4b$ background is included.
  %
- Combining in this
- case the signal significance in the three categories,
+ Combining
+ the signal significance in the three categories,
  we
- obtain $S/\sqrt{B_{\rm 4b}}\simeq 3.5$, which is twice
+ obtain $(S/\sqrt{B_{\rm 4b}})_{\rm tot}\simeq 1.4$, twice
  as large as the result found when
@@
  %
- Part of the improvement 
-with respect to~\cite{deLima:2014dta,Wardrope:2014kya} arises
- from the combination of the three exclusive event topologies,
+ Note the importance of
+ the combination of the three exclusive event topologies,
  as opposed the exploitation of a single specific category.
+ %
+ Taking into account the loose selection cuts, we
+ see that
+ our pre-MVA results including only the $4b$ background are consistent
+ with those reported in previous studies.
 
- Also from Table~\ref{tab:cutflow_noPU_1}, we
+ From Table~\ref{tab:cutflow_noPU_1} we
  can compare the interplay
@@
  %
- In all cases, the $4b$ and $2b2j$ have comparable
+ In all cases, the $4b$ and $2b2j$ components have comparable
  magnitudes within the uncertainties from missing higher-order
@@
  On the other hand, the $4j$ component
-is always smaller by at least
- one order of magnitude.
+is always substantially smaller.
  %
@@
     components of the QCD background for the transverse momentum
-    $p_T$ of the leading
-Higgs candidate in the resolved
-and boosted  categories, and the same
- for the invariant
+    $p_T^h$ of the leading
+Higgs candidate and for invariant
 mass $m_{hh}$ of the
-    reconstructed di-Higgs system.
+    reconstructed di-Higgs system in the resolved
+    and boosted  categories.
      %
@@
   %
-    For instance, in the boosted
-    category the $4b$ component is harder for the
-    $p_T^h$ distribution.
-  %
-    The $2b2j$ component has a longer
-    tail at small values of the $m_{hh}$ invariant
-    mass distribution.
+    In the boosted
+    category, the $4b$ component exhibits a less steep fall-off of
+    the $p_T^h$ distribution at large $p_T$,
+    while in the resolved case
+    the $2b2j$ component has a slightly harder
+    distribution of the  invariant
+    mass $m_{hh}$.
 %
@@
     of the shapes of the $4b$ and $2b2j$
-components of the QCD background for the $p_T$ of the leading
+components of the QCD background for the $p_T^h$ of the leading
 Higgs candidate in the resolved
@@
 
-In the resolved category 
+In the resolved category, 
 the cross-section  before
-$b$-tagging is more than two orders
+$b$-tagging is two orders
 of magnitude larger in the $2b2j$
@@
 %
-In which case the ratio of $2b2j$ over $4b$ would be
+In this case the ratio of $2b2j$ over $4b$ would be
 around $\simeq 3\%$, and therefore negligible.
@@
 %
-Due to these effects,
+Due to these,
 the
@@
 time the number of events in the $4b$ sample
-with 4 $b$-jets is reduced.
+with 4 $b$-jets passing selection cuts is reduced.
 
@@
 %
+
 The naive expectation is that all events in the $4b$ sample have $n^{\rm (b-jet)}_4\simeq 1$
@@
 \ee
-However, after the parton shower the above approach is no longer accurate.
+However, after the parton shower, the above estimate is no longer accurate.
 %
@@
     %
-    The last column indicates the overall predicted
-    selection efficiency of the $b$-tagging procedure following
+    The last column indicates the overall 
+    selection efficiency as defined in
     Eq.~(\ref{btaggingeff})
@@
   \ee
-  This suppression factor is of the same order of the ratio of $4b$ to $2b2j$ cross-sections
-  in the resolved category before $b$-tagging, see Table~\ref{tab:cutflow_noPU_1}.
+  This suppression factor is of the same order as
+  the ratio of $4b$ to $2b2j$ cross-sections
+  in the resolved category before $b$-tagging.
     %
@@
     %
-    A similar calculation from the numbers in Table~\ref{tab:btaggingcheck} shows
-    that, on the other hand, the $4j$ component of the background is negligible and be neglected. % can typically
-%    be safely neglected.
-
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    A similar calculation from the numbers in Table~\ref{tab:btaggingcheck}
+    shows
+    that, on the other hand, the $4j$ component of the background
+    can be neglected.

### 2016-06-13 paper-arxiv-v3/sec-mcsamples.tex
revised paper

--- 2015-12-31 paper-arxiv-v1/sec-mcsamples.tex
@@
 Single Higgs production processes such as $Z(\to b\bar{b})h(\to b\bar{b})$
-and $t\bar{t}h(\to b\bar{b})$ along with electroweak backgrounds e.g $Z(\to b\bar{b})b\bar{b}$,
-are much smaller than the QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
+and $t\bar{t}h(\to b\bar{b})$ (see Appendix~\ref{app:singlehiggs})
+along with electroweak backgrounds {\it e.g} $Z(\to b\bar{b})b\bar{b}$,
+are much smaller than the
+QCD backgrounds~\cite{Wardrope:2014kya,deLima:2014dta}
 and are therefore not included in the present analysis.
-%
 

### 2016-06-13 paper-arxiv-v3/sec-mva.tex
revised paper

--- 2016-01-21 paper-arxiv-v2/sec-mva.tex
@@
 \be
+\label{eq:soverb}
 \lp \frac{S}{\sqrt{B}}\rp_{\rm tot} \simeq 4.0~(1.3) \, ,\quad
@@
 %%%%%%%%%%%%%%%%%%%%%%%
+
+A particularly challenging aspect of our analysis is the modeling of the $2b2j$ and $4j$ background,
+specially of the latter, which require extremely large MC samples.
+%
+In the analysis reported here, out of the original 3M $4j$ generated events, only around 100
+survive the analysis cuts, and thus
+these low statistics have associated a potentially large uncertainty
+in the calculation of the post-MVA $4j$ cross-section.
+%
+On the other hand, since the $4j$ cross-sections
+are always quite smaller than the sum of the $4b$ of the $2b2j$ components,
+this low statistics should not modify qualitatively our conclusions above.
+%
+To verify explicitly this expectation, and obtain a more
+robust estimate of the  background cross-section from mis-identified jets,
+we have increased by a factor 10 the size of the $2b2j$ and $4j$
+background samples, up to a total of 30M each.
+%
+Processing these events though our analysis, including retraining the MVA, we find
+$(S/\sqrt{B})_{\rm tot}=3.9$, consistent with Eq.~(\ref{eq:soverb}), indicating that the low
+statistics of the $4j$ background is not a limiting factor.
 

### 2016-06-13 paper-arxiv-v3/sec-singlehiggs.tex
revised paper

\appendix

\section{Single Higgs backgrounds}
\label{app:singlehiggs}

As discussed in Sect.~\ref{mcgeneration},
in our analysis we neglect single Higgs production processes,
since they are much smaller than both the signal and the main
QCD multijet backgrounds.
%
To explicitly demonstrate this, we have generated LO samples
using  {\tt MadGraph5\_aMC@NLO}
for the
following single-Higgs processes:
  \begin{enumerate}
  \item $Z(\to b\bar{b})h(\to b\bar{b})$ (electroweak)
  \item $t\bar{t}h(\to b\bar{b})$
    \item $b\bar{b}h(\to b\bar{b})$ (QCD)
  \end{enumerate}
  For each processes, we have  generated 1M events, and in
 Table~\ref{HK}  we list resulting the
  LO and NLO cross-sections at the generation level.
  %
  The subsequent decays and the
  corresponding branching fractions are not included in these cross-sections,
  since
  these are taken care by the {\tt Pythia8} parton shower.
  %
  The values of these branching fractions 
  are listed in Table~\ref{HBF}, corresponding
  to the  most recent averages from the PDG.
  %
  In the case of the $t\bar{t}h$ process, we
  consider only the fully hadronic decays
  of the top quark, since leptonic and semi-leptonic decays
  can be suppressed
  by means of a lepton veto.

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
Sample & LO & NLO & $K$-factor\\
\hline\hline
$Zh$ (13 TeV) & $6.5 \cdot 10^{-1}$ pb & $ 7.7 \cdot 10^{-1}$ pb & 1.19 \\
$t\bar{t}h$ (13 TeV) & $3.8 \cdot 10^{-1}$ pb & $4.6 \cdot 10^{-1}$ pb & 1.29 \\
$b\bar{b}h$ (13 TeV) &  $4.9 \cdot 10^{-1}$ pb & $6.1 \cdot 10^{-1}$ pb & 1.22 \\
\hline
\end{tabular}
\caption{\small LO and NLO cross-sections at the generation level for the single-Higgs background
  processes listed above, computed using {\tt MadGraph5\_aMC@NLO}.
  %
  The subsequent decays and the corresponding branching fractions are not included in these generation-level cross-sections. \label{HK}
}
\end{center}
  \end{table}%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
Sample & Decay & Branching Fraction\\
\hline\hline
$Zh$ & ($Z\to b\bar{b}$)($h\to b\bar{b}$) & 0.086 \\
$t\bar{t}h$ & $(W\to q\bar{q})^2$($h\to b\bar{b}$) & 0.26 \\
$b\bar{h}h$ & $h\to b\bar{b}$ & 0.57 \\
\hline
\end{tabular}
\caption{\small The values of the branching fractions applied to the single-Higgs
  background processes from Table~\ref{HK}, corresponding to
  the most updated PDG values. \label{HBF}}
\end{center}
  \end{table}%
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  In Table~\ref{HBxsec}
  we show the signal and background cross-sections at the end of the cut-based analysis, before the MVA is applied,
  in the case without PU.
  %
  We separate the results into the three exclusive categories used in our analysis.
  %
  From this comparison, we see that as expected, at the end of the cut-based analysis, the single-Higgs
  backgrounds are smaller than the QCD multijet background by several orders of magnitude.
  %
  In addition, we find that already at the end of the cut-based analysis the di-Higgs
  signal is also larger than all the single-Higgs backgrounds in all the selection categories.
  %
  Since this discrimination can only be improved by the MVA, we
  conclude that neglecting single-Higgs backgrounds is a reasonable
  approximation.
%
  From Table~\ref{HBxsec} we also observe that in the resolved
  and intermediate categories $Zh\to b\bar{b}b\bar{b}$ is
  the dominant single-Higgs background, while $t\bar{t}h(\to b\bar{b})$ is
  instead the most important one in the boosted category.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
& Sample &  \multicolumn{3}{c|}{Pre-MVA cross-section (fb)}\\
 & &  Boosted  & Intermediate & Resolved \\[0.1cm]
\hline\hline
Signal & $hh\to b\bar{b}b\bar{b}$ & $3.5\cdot 10^{-1}$  & $2.2\cdot 10^{-1}$ &  $1.2\cdot 10^{0}$ \\[0.1cm]
\hline
\multirow{4}{*}{Backgrounds} & QCD multijet &  $2.5\cdot 10^{+2}$ & $1.8\cdot 10^{+2}$ & $4.9\cdot 10^{+3}$ \\
&$Z(\to b\bar{b})h(\to b\bar{b})$ & $2.0\cdot 10^{-2}$ & $1.2\cdot 10^{-1}$ & $7.5\cdot 10^{-1}$ \\
&$t\bar{t}h(\to b\bar{b})$ & $5.1\cdot 10^{-2}$ & $6.3\cdot 10^{-3}$ & $4.0\cdot 10^{-1}$ \\
&$b\bar{b}h(\to b\bar{b})$ & $2.3\cdot 10^{-3}$ & $5.5\cdot 10^{-3}$ & $2.6\cdot 10^{-1}$\\
\hline
\end{tabular}
\end{center}
\caption{\small \label{HBxsec} Signal and background cross-sections at the end of the cut-based analysis
  (before the MVA is applied), in the case without PU.
  %
  We separate the results into the three exclusive categories used in our analysis.
  %
}
  \end{table}%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
